### 2013-01-29 analysis/SandboxMax/Test.Rmd
Updates after 1/29 meeting with Aaron.

Max's First Analysis
========================================================

This is an R Markdown document. Markdown is a simple formatting syntax for authoring web pages (click the **MD** toolbar button for help on Markdown).

When you click the **Knit HTML** button a web page will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r, cache=TRUE}
getwd()

library (foreign)
workingdata <- read.dbf("../../../Data//R2GIS/CleanData/Sales20052007.dbf")
names(workingdata)
summary(workingdata)

###Preparation for regression analysis, load packages for tests

require(zoo)
require(lmtest)
require(car)

```

You can also embed plots, for example:

```{r fig.width=7, fig.height=6}
hist(workingdata$SALE_VALUE)
```

Here, let's go ahead and run a regression.

```{r}
model.SaleValue1 <- lm (SALE_VALUE ~ COUNTY_ID + CITY + SALE_YR + SDNUM + GARAGE + ACRES_POLY+HOMESTEAD+FIN_SQ_FT+YEAR_BUILT+MAX+PARK_dist+LAKE_dist+MCA3+MCA5+SHOP_dist+CBD_dist, data=workingdata)
summary(model.SaleValue1)
```

### 2013-01-29 analysis/MaxSandbox20052007.R

@@ -20,7 +20,7 @@ summary(model.SaleValue1)
 anova(model.SaleValue1)
 #Diagnostics
 plot(model.SaleValue1) #Normality issues once again #926, 19852 large leverage
-vif(model.SaleValue1) #multicollinearity #No real signs of severe multicollinearity
+vif(model.SaleValue1) #multicollinearity #SDNUM VIF above 10
 dwtest (model.SaleValue1) #autocorrelation # Signs of autocorrelation since DW value is less than 1.5 (1.2974)
 bptest(model.SaleValue1)
 outlierTest(model.SaleValue1)
@@ -66,9 +66,15 @@ plot(model.logSaleValue1)
 
 ceresPlots(model.logSaleValue1)
 
-workingdata [-c(16294,16293, 24494), ]
+workingdata = workingdata [-c(16299,17134, 24492), ]
 
 ###Dependent variable: Sales Value (log transformed) w/o MCA5, PARK_dist, SHOP_dist SDNUM | inclusion of Acres2, logMax, logFIN_SQ_FT
-model.logSaleValue2 <- lm (logSALE_VA ~ COUNTY_ID + CITY + SALE_YR + GARAGE + GARSQFT + ACRES_POLY + ACRES2 + HOMESTEAD+ logFIN_SQ_+YEAR_BUILT+logMAX+LAKE_dist+MCA3+SHOP_dist+CBD_dist, data=workingdata)
+model.logSaleValue2 <- lm (logSALE_VA ~ COUNTY_ID + CITY + SALE_YR + ACRES_POLY + ACRES2 + HOMESTEAD+ logFIN_SQ_+YEAR_BUILT+logMAX+LAKE_dist+MCA3+SHOP_dist+CBD_dist, data=workingdata)
 summary(model.logSaleValue2)
+#Create a residual table with PIN ID number in order to investigate clusters of over/under- estimation parcels
+Residuals20052007 = data.frame(PIN = workingdata$UNIQID, Res = model.logSaleValue2$residuals)
+write.dbf(Residuals20052007, "../Data/R2GIS/ResidualLogSale0507.dbf" )
+
+
+
 plot(model.logSaleValue2)

### 2013-01-29 munge/ResDataMaker.R

@@ -1,0 +1,17 @@
+##Issue: In a model that excludes some observations (such as if we included GARAGE dummy) we had trouble
+#creating the .dbf file because: arguments imply differing number of rows. This script grabs row names and merges with working data
+#in order to create a field with the PIN (now we can join resids with parcels in GIS)
+
+#Grab residual from model and row name from the model
+resData = data.frame(Res = model.SaleValue3$residuals, RowName = names(model.SaleValue3$residuals))
+
+#Add column of row names to the workingdata
+workingdata$RowName = row.names(workingdata)
+
+#Merge the resData table from model with workingdata table
+temp = merge(resData, workingdata, all = TRUE)
+
+#From temporary table that merged resData table and workingdata table, extract residuals and PIN
+names(temp)
+temp = temp[, c(2, 4)]
+write.dbf(temp, "../Data/R2GIS/Model3.dbf")

### 2013-01-29 munge/Sales20052007_munge.R

@@ -4,9 +4,10 @@ summary(sales0507)
 
 
 #Pulling the variables we WANT into a new, working dataframe.
-sales0507$GARSQFT <- as.numeric(sales0507$GARAGESQFT) #Converting factor to numeric
+sales0507$GARSQFT <- as.numeric(as.character(sales0507$GARAGESQFT)) #Converting factor to numeric
+sales0507$SALE_SEASON <- factor(sales0507$SALE_QRT)
 dataNames <- names (sales0507)
-VarsIWant <- which(dataNames %in% c("COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "TOTAL_TAX", "HOME_STYLE", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "SALE_VALUE", "SALE_YR", "BEDS", "BATH", "MAX", "TRACTCE10", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "GARSQFT", "SALE_QRT", "SDNUM", "MCA3", "MCA5", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "CBD_dist", "PIN"))
+VarsIWant <- which(dataNames %in% c("COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "TOTAL_TAX", "HOME_STYLE", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "SALE_VALUE", "SALE_YR", "BEDS", "BATH", "MAX", "TRACTCE10", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "GARSQFT", "SALE_SEASON", "SDNUM", "MCA3", "MCA5", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "CBD_dist", "PIN"))
 workingdata = sales0507[ , VarsIWant]
 summary (workingdata)
 workingdata$logSALE_VALUE = log(workingdata$SALE_VALUE) #Transforming sales values into logs
@@ -31,7 +32,11 @@ workingdata <- workingdata [-OutlierParcels, ] #Excludes observations that are o
 plot (workingdata$ACRES_POLY, workingdata$SALE_VALUE) #Possibility for x^2 relationship or log transformation
 plot (workingdata$FIN_SQ_FT, workingdata$SALE_VALUE) #Linear relationship
 plot (workingdata$MAX, workingdata$SALE_VALUE) #Not a clear linear relationship, possiblity for x^2 relationship
[…]

### 2013-01-30 analysis/SandboxMax/20052007SalesData.Rmd
Updated changes from 1/30. Restricted outlier constraints more, included more fixed effects variables for timing of sale, included more nonlinear relationships. Summarized in .html RMarkdown in Analysis/MaxSandbox/20052007Sales_1_30

Max's Analysis -- 2005-2007 SalesData 1/30/13
========================================================

This is a test run of analysis through RMarkdown using 2005-2007 sales dataset.

Preparation for regression analysis...
```{r, cache=TRUE}
getwd()

library (foreign)
workingdata <- read.dbf("../../../Data//R2GIS/CleanData/Sales20052007.dbf")
require(zoo)
require(lmtest)
require(car)

```

In order to improve the model, I did three things:

(1) After normality issues arose in preliminary regressions, used more restrictive constraints on outliers to make distributions to key variables more normal.
Limited parcels to under 4000 square feet in living area, less than .6 acres, experiencing more than 25 dBA in traffic noise and sales values between $100k and $675k
Sample size went from ~28k to 25,994

(2) Along with restricting dataset to exclude outliers, we also transformed structural and distance variables to logarithms when appropriate in order to better fit the nonlinear relationship they had with the log transformed dependent variables (sales value).

(3) Included more fixed effect variables related to the timing of the sale (either by month or season)

```{r fig.width=7, fig.height=6}
hist(workingdata$logSALE_VA)
hist(workingdata$logFIN_SQ_)
hist(workingdata$logMAX)
```

The first regression will be a baseline without any log transformations.

```{r}
model.SaleValue1 <- lm (SALE_VALUE ~ COUNTY_ID + CITY + SALE_YR + SDNUM + ACRES_POLY + HOMESTEAD + FIN_SQ_FT + YEAR_BUILT + MAX + PARK_dist + LAKE_dist + MCA3 + MCA5 + SHOP_dist + CBD_dist +SALE_SEASO +SALE_MO, data=workingdata)
summary(model.SaleValue1)
```

Looking at the residual and qqplot, notice that there may be some pattern in the variance as well as a violation of normality.

```{r}
unlogged = data.frame (yhat = model.SaleValue1$fitted.values, rr = model.SaleValue1$residuals)
plot (unlogged$yhat, unlogged$rr)
qqnorm(unlogged$rr)
qqline(unlogged$rr)
```

The second regression implements the log transformations to sales value and the explanatory variables that have a nonlinear relationship with logged sales value.

```{r}
model.logSaleValue2 <- lm (logSALE_VA ~ COUNTY_ID + CITY + SALE_YR  + ACRES_POLY + ACRES2 + HOMESTEAD + logFIN_SQ_ + YEAR_BUILT + logMAX + logPARK  + MCA3 + logSHOP + logCBD + SALE_MO +SALE_SEASO, data=workingdata)
summary(model.logSaleValue2)
```

Looking at the residual and qqplot, note that the residuals seem to follow a more pronounced pattern that is in violation with homoscedasticity. However, normality conditions improve, yet there are still some issues. I am joining the residuals with the shapefile in order to see if these observations with either large over- or under-estimates are clustered.

```{r}
logged = data.frame (yhat = model.logSaleValue2$fitted.values, rr = model.logSaleValue2$residuals)
plot (logged$yhat, unlogged$rr)
qqnorm(logged$rr)
qqline(logged$rr)
```

The last regression inputs the dummy variable for GARAGE. The inclusion of this variable excludes ~ 4k parcels mostly in Dakota County which brings the sample size to ~21k. This regression has similar looking residual and qqplots.

```{r}
model.logSaleValue3 <- lm (logSALE_VA ~ COUNTY_ID + CITY + SALE_YR  + GARAGE + ACRES_POLY + ACRES2 + HOMESTEAD + logFIN_SQ_ + YEAR_BUILT + logMAX + logPARK  + MCA3 + logSHOP + logCBD + SALE_MO +SALE_SEASO, data=workingdata)
summary(model.logSaleValue3)
```

### 2013-01-30 analysis/MaxSandbox20052007.R

@@ -4,9 +4,6 @@ names(workingdata)
 summary(workingdata)
 
 ###Preparation for regression analysis, load packages for tests
-install.packages ("zoo")
-install.packages ("lmtest")
-install.packages ("car")
 require(zoo)
 require(lmtest)
 require(car)
@@ -15,22 +12,23 @@ require(car)
 
 ####Linear model investigation
 ##Dependent variable: Sales Value (untransformed)
-model.SaleValue1 <- lm (SALE_VALUE ~ COUNTY_ID + CITY + SALE_YR + SDNUM + GARAGE + ACRES_POLY+HOMESTEAD+FIN_SQ_FT+YEAR_BUILT+MAX+PARK_dist+LAKE_dist+MCA3+MCA5+SHOP_dist+CBD_dist, data=workingdata)
+model.SaleValue1 <- lm (SALE_VALUE ~ COUNTY_ID + CITY + SALE_YR + SDNUM + ACRES_POLY + HOMESTEAD + FIN_SQ_FT + YEAR_BUILT + MAX + PARK_dist + LAKE_dist + MCA3 + MCA5 + SHOP_dist + CBD_dist +SALE_SEASO +SALE_MO, data=workingdata)
 summary(model.SaleValue1)
-anova(model.SaleValue1)
+anova(model.SaleValue1) #MCA5 and SALE_MO 
 #Diagnostics
-plot(model.SaleValue1) #Normality issues once again #926, 19852 large leverage
+plot(model.SaleValue1) #Normality issues once again #3156 large leverage
 vif(model.SaleValue1) #multicollinearity #SDNUM VIF above 10
 dwtest (model.SaleValue1) #autocorrelation # Signs of autocorrelation since DW value is less than 1.5 (1.2974)
 bptest(model.SaleValue1)
 outlierTest(model.SaleValue1)
 
 
-workingdata = workingdata[-c(926, 19852), ] #Removed influential observations
 
-##Dependent variable: Sales Value (untransformed) w/o MCA5, SDNUM, PARK_dist
-model.SaleValue2 <- lm (SALE_VALUE ~ COUNTY_ID + CITY + SALE_YR + GARAGE + ACRES_POLY + HOMESTEAD+FIN_SQ_FT+YEAR_BUILT+MAX+LAKE_dist+MCA3+SHOP_dist+CBD_dist, data=workingdata)
+
+##Dependent variable: Sales Value (untransformed) w/o MCA5, SDNUM
[…]

### 2013-01-30 munge/Sales20052007_munge.R

@@ -6,8 +6,9 @@ summary(sales0507)
 #Pulling the variables we WANT into a new, working dataframe.
 sales0507$GARSQFT <- as.numeric(as.character(sales0507$GARAGESQFT)) #Converting factor to numeric
 sales0507$SALE_SEASON <- factor(sales0507$SALE_QRT)
+sales0507$SALE_MO <- factor(sales0507$SALE_MONTH)
 dataNames <- names (sales0507)
-VarsIWant <- which(dataNames %in% c("COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "TOTAL_TAX", "HOME_STYLE", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "SALE_VALUE", "SALE_YR", "BEDS", "BATH", "MAX", "TRACTCE10", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "GARSQFT", "SALE_SEASON", "SDNUM", "MCA3", "MCA5", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "CBD_dist", "PIN"))
+VarsIWant <- which(dataNames %in% c("COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "TOTAL_TAX", "HOME_STYLE", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "SALE_VALUE", "SALE_YR", "BEDS", "BATH", "MAX", "TRACTCE10", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "GARSQFT", "SALE_SEASON", "SDNUM", "MCA3", "MCA5", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "CBD_dist", "PIN", "SALE_MO"))
 workingdata = sales0507[ , VarsIWant]
 summary (workingdata)
 workingdata$logSALE_VALUE = log(workingdata$SALE_VALUE) #Transforming sales values into logs
@@ -18,13 +19,19 @@ hist(workingdata$FIN_SQ_FT) #Also right skewed
 hist(workingdata$MAX) #Left skewed
 hist(workingdata$SALE_VALUE) #Right skewed
 #Limit Dataset
-LivingAreaOutliers = which (workingdata$FIN_SQ_FT > 5000) #Limit dataset to houses with less than 5000 sq ft.
-AcreageOutliers = which (workingdata$ACRES_POLY > 1) #Limit dataset to parcels less than one acre
[…]

### 2013-01-30 analysis/SandboxMax/20082010SalesData.Rmd
Updated 1/30. See previous update and RMarkdown.html file 20082010Sales_1_30 for details.

--- 2013-01-30 analysis/SandboxMax/20052007SalesData.Rmd
@@
-Max's Analysis -- 2005-2007 SalesData 1/30/13
+Max's Analysis -- 2008-2010 SalesData 1/30/13
 ========================================================
 
-This is a test run of analysis through RMarkdown using 2005-2007 sales dataset.
+This is a test run of analysis through RMarkdown using 2008-2010 Sales dataset.
 
@@
 library (foreign)
-workingdata <- read.dbf("../../../Data//R2GIS/CleanData/Sales20052007.dbf")
+workingdata <- read.dbf("../../../Data//R2GIS/CleanData/Sales20082010.dbf")
 require(zoo)
@@
 Limited parcels to under 4000 square feet in living area, less than .6 acres, experiencing more than 25 dBA in traffic noise and sales values between $100k and $675k
-Sample size went from ~28k to 25,994
+Sample size went from ~19k to 15,587
 
@@
 
-(3) Included more fixed effect variables related to the timing of the sale (either by month or season)
+(3) Included more fixed effect variables related to the timing of the sale (either by month or season).
+In the regression we only included fixed effect for season because there is perfect multicollinearity between sales month and sales season.
 
@@
 
-The first regression will be a baseline without any log transformations.
+The first regression will be a baseline without any log transformations. Notice that this regression does not explain as much of the variation seen in sales value as the 2005-2007 based regression.
 
 ```{r}
-model.SaleValue1 <- lm (SALE_VALUE ~ COUNTY_ID + CITY + SALE_YR + SDNUM + ACRES_POLY + HOMESTEAD + FIN_SQ_FT + YEAR_BUILT + MAX + PARK_dist + LAKE_dist + MCA3 + MCA5 + SHOP_dist + CBD_dist +SALE_SEASO +SALE_MO, data=workingdata)
+model.SaleValue1 <- lm (SALE_VALUE ~ COUNTY_ID + CITY + SALE_YR + SDNUM + ACRES_POLY + HOMESTEAD + FIN_SQ_FT + YEAR_BUILT + MAX + PARK_dist + LAKE_dist + MCA3 + MCA5 + SHOP_dist + CBD_dist +SALE_SEASO, data=workingdata)
 summary(model.SaleValue1)
@@
 
-Looking at the residual and qqplot, notice that there may be some pattern in the variance as well as a violation of normality.
+Looking at the residual and qqplot, notice that there is a greater threat to homoscedasticity than in the 2005-2007 model and normality issues are still a problem.
 
@@
 ```{r}
-model.logSaleValue2 <- lm (logSALE_VA ~ COUNTY_ID + CITY + SALE_YR  + ACRES_POLY + ACRES2 + HOMESTEAD + logFIN_SQ_ + YEAR_BUILT + logMAX + logPARK  + MCA3 + logSHOP + logCBD + SALE_MO +SALE_SEASO, data=workingdata)
+model.logSaleValue2 <- lm (logSALE_VA ~ COUNTY_ID + CITY + SALE_YR  + ACRES_POLY + ACRES2 + HOMESTEAD + logFIN_SQ_ + YEAR_BUILT + logMAX + logPARK  + MCA3 + logSHOP + logCBD +SALE_SEASO, data=workingdata)
 summary(model.logSaleValue2)
@@
 
-Looking at the residual and qqplot, note that the residuals seem to follow a more pronounced pattern that is in violation with homoscedasticity.
-However, normality conditions improve, yet there are still some issues.
+Looking at the residual and qqplot, note non constant variance and normality conditions improve, yet there are still some issues.
 I am joining the residuals with the shapefile in order to see if these observations with either large over- or under-estimates are clustered.
@@
 The last regression inputs the dummy variable for GARAGE.
-The inclusion of this variable excludes ~ 4k parcels mostly in Dakota County which brings the sample size to ~21k.
+The inclusion of this variable excludes ~ 1500 parcels mostly in Dakota County which brings the sample size to ~14k.
 This regression has similar looking residual and qqplots.
@@
 ```{r}
-model.logSaleValue3 <- lm (logSALE_VA ~ COUNTY_ID + CITY + SALE_YR  + GARAGE + ACRES_POLY + ACRES2 + HOMESTEAD + logFIN_SQ_ + YEAR_BUILT + logMAX + logPARK  + MCA3 + logSHOP + logCBD + SALE_MO +SALE_SEASO, data=workingdata)
+model.logSaleValue3 <- lm (logSALE_VA ~ COUNTY_ID + CITY + SALE_YR  + GARAGE + ACRES_POLY + ACRES2 + HOMESTEAD + logFIN_SQ_ + YEAR_BUILT + logMAX + logPARK  + MCA3 + logSHOP + logCBD +SALE_SEASO, data=workingdata)
 summary(model.logSaleValue3)

### 2013-01-30 analysis/MaxSandbox20082010.R

@@ -3,9 +3,6 @@ workingdata <- read.dbf("../Data/R2GIS/CleanData/Sales20082010.dbf")
 summary(workingdata)
 
 ###Preparation for regression analysis, load packages for tests
-install.packages ("zoo")
-install.packages ("lmtest")
-install.packages ("car")
 require(zoo)
 require(lmtest)
 require(car)
@@ -14,52 +11,73 @@ require(car)
 
 ####Linear model investigation
 ##Dependent variable: Sales Value (untransformed)
-model.SaleValue1 <- lm (SALE_VALUE ~ CITY + SALE_YR + SDNUM + ACRES_POLY+HOMESTEAD+FIN_SQ_FT+YEAR_BUILT+MAX+PARK_dist+LAKE_dist+MCA3+MCA5+SHOP_dist+CBD_dist, data=workingdata)
+model.SaleValue1 <- lm (SALE_VALUE ~ COUNTY_ID + CITY + SALE_YR + SDNUM + ACRES_POLY + HOMESTEAD + FIN_SQ_FT + YEAR_BUILT + MAX + PARK_dist + LAKE_dist + MCA3 + MCA5 + SHOP_dist + CBD_dist +SALE_SEASO, data=workingdata)
 summary(model.SaleValue1)
-anova(model.SaleValue1)
+anova(model.SaleValue1) #MCA5 and SALE_MO 
 #Diagnostics
-plot(model.SaleValue1) #Normality issues once again #Observation 4067 high leverage
-vif(model.SaleValue1) #multicollinearity #SDNUM shows multicollinearity (probably with MCA scores)
-dwtest (model.SaleValue1) #autocorrelation # Signs of autocorrelation since DW value is less than 1.5 (1.4266)
-bptest(model.SaleValue1) 
-outlierTest(model.SaleValue1) #15579 13619 11911 5390 11994 5604 13873 13870 14681  14680 
-ncvTest(model.SaleValue1) #nonconstant variance
+plot(model.SaleValue1) #Normality issues once again #5222 large leverage
+vif(model.SaleValue1) #multicollinearity #SDNUM VIF above 10 #aliased coefficients means that there is perfect multicollinearity with one of the variables. In the summary table the variable will be NA
+dwtest (model.SaleValue1) #autocorrelation # Signs of autocorrelation since DW value is less than 1.5 (1.4538)
+bptest(model.SaleValue1)
+outlierTest(model.SaleValue1)
 
[…]

### 2013-01-30 munge/Sales20082010_munge.R

@@ -1,10 +1,15 @@
 library (foreign)
 sales0810 <- read.dbf("../Data/GIS2R/Sales20082010.dbf")
-summary(sales0810)
+summary(sales0810) #found that some observations have a 0 or negative sales value
+t <- which(sales0810$SALE_VALUE < 1)
+sales0810 = sales0810 [-t, ] #Excludes observations without sales value information
 
 #Pulling the variables we WANT into a new, working dataframe.
+sales0810$GARSQFT <- as.numeric(as.character(sales0810$GARAGESQFT)) #Converting factor to numeric
+sales0810$SALE_SEASON <- factor(sales0810$SALE_QRT)
+sales0810$SALE_MO <- factor(sales0810$SALE_MONTH)
 dataNames <- names (sales0810)
-VarsIWant <- which(dataNames %in% c("COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "TOTAL_TAX", "HOME_STYLE", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "SALE_VALUE", "SALE_YR", "BEDS", "BATH", "MAX", "TRACTCE10", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "GARAGESQFT", "SALE_QRT", "SDNUM", "MCA3", "MCA5", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "CBD_dist", "PIN"))
+VarsIWant <- which(dataNames %in% c("GARSQFT","SALE_SEASON", "SALE_MO","COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "TOTAL_TAX", "HOME_STYLE", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "SALE_VALUE", "SALE_YR", "BEDS", "BATH", "MAX", "TRACTCE10", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "SDNUM", "MCA3", "MCA5", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "CBD_dist", "PIN"))
 workingdata = sales0810[ , VarsIWant]
 summary (workingdata)
 workingdata$logSALE_VALUE = log(workingdata$SALE_VALUE) #Transforming sales values into logs
@@ -14,13 +19,19 @@ hist(workingdata$ACRES_POLY) #Large outliers -- very right skewed
[…]

### 2013-01-31 analysis/SandboxAaron/CopyOf20052007SalesData.Rmd
created SandboxAaron folder (like Max's)

--- 2013-01-30 analysis/SandboxMax/20082010SalesData.Rmd
@@
-Max's Analysis -- 2008-2010 SalesData 1/30/13
+Max's Analysis -- 2005-2007 SalesData 1/30/13
 ========================================================
 
-This is a test run of analysis through RMarkdown using 2008-2010 Sales dataset.
+This is a test run of analysis through RMarkdown using 2005-2007 Sales dataset. And Aaron is making a few small changes.
 
 Preparation for regression analysis...
-```{r, cache=TRUE}
+```{r, cache=FALSE}
 getwd()
@@
 library (foreign)
-workingdata <- read.dbf("../../../Data//R2GIS/CleanData/Sales20082010.dbf")
+workingdata <- read.dbf("../../../Data/R2GIS/CleanData/Sales20052007.dbf")
 require(zoo)
@@
 Limited parcels to under 4000 square feet in living area, less than .6 acres, experiencing more than 25 dBA in traffic noise and sales values between $100k and $675k
-Sample size went from ~19k to 15,587
+Sample size went from ~28k to 25,994
 
@@
 
-Looking at the residual and qqplot, notice that there is a greater threat to homoscedasticity than in the 2005-2007 model and normality issues are still a problem.
+Looking at the residual and qqplot, notice that there may be some pattern in the variance as well as a violation of normality.
 
@@
 
-Looking at the residual and qqplot, note non constant variance and normality conditions improve, yet there are still some issues.
+Looking at the residual and qqplot, note that the residuals seem to follow a more pronounced pattern that is in violation with homoscedasticity.
+However, normality conditions improve, yet there are still some issues.
 I am joining the residuals with the shapefile in order to see if these observations with either large over- or under-estimates are clustered.
@@
 The last regression inputs the dummy variable for GARAGE.
-The inclusion of this variable excludes ~ 1500 parcels mostly in Dakota County which brings the sample size to ~14k.
+The inclusion of this variable excludes ~ 4k parcels mostly in Dakota County which brings the sample size to ~21k.
 This regression has similar looking residual and qqplots.

### 2013-01-31 analysis/SandboxMax/20052007SalesData.Rmd
added some regressions with interaction terms between acreage and cbd distance

@@
 
-This is a test run of analysis through RMarkdown using 2005-2007 sales dataset.
+This is a test run of analysis through RMarkdown using 2005-2007 Sales dataset. And Aaron is making a few small changes.
 
@@
 library (foreign)
-workingdata <- read.dbf("../../../Data//R2GIS/CleanData/Sales20052007.dbf")
+workingdata <- read.dbf("../../../Data/R2GIS/CleanData/Sales20052007.dbf")
 require(zoo)
@@
 ```{r}
-model.logSaleValue3 <- lm (logSALE_VA ~ COUNTY_ID + CITY + SALE_YR  + GARAGE + ACRES_POLY + ACRES2 + HOMESTEAD + logFIN_SQ_ + YEAR_BUILT + logMAX + logPARK  + MCA3 + logSHOP + logCBD + SALE_MO +SALE_SEASO, data=workingdata)
+model.logSaleValue3 <- lm (logSALE_VA ~ COUNTY_ID + CITY + SALE_YR  + GARAGE + ACRES_POLY + ACRES2 + HOMESTEAD + logFIN_SQ_ + YEAR_BUILT + logMAX + logPARK  + MCA3 + logSHOP + logCBD +SALE_SEASO, data=workingdata)
 summary(model.logSaleValue3)
 ```
+
+Allowing the marginal effect of lot size to vary
+-------
+We have seen that including a quadratic term in lot size is useful.
+However, the value of additional lot size is likely to vary over space.
+This is one of the reasons we'll want to run LWR.
+In the meantime, we can interact lot size with our location variables, like distance to the St.
+Paul CBD and Minneapolis CBD.
+And, given that we have seen a quadratic relationship between distance to CBD and house prices (signifying and 'optimal' distance to live at), perhaps we can even interact lot size with distance to CBD and distance to CBD squared.
+
+Let's first rerun a simple semi-log regression
+```{r}
+model.logSaleValue3 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY + CBD_dist + HOMESTEAD + FIN_SQ_FT + YEAR_BUILT + logMAX + logPARK  + MCA3 + logSHOP  +SALE_SEASO, data=workingdata)
+summary(model.logSaleValue3)
+```
+
+Now let's interact lot size with CBD to see how the price of land might change over space
+```{r}
+model.logSaleValue4 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY*CBD_dist + HOMESTEAD + FIN_SQ_FT + YEAR_BUILT + logMAX + logPARK  + MCA3 + logSHOP +  +SALE_SEASO, data=workingdata)
+summary(model.logSaleValue4)
+```
+
+And now let's include acres squared
+```{r}
+model.logSaleValue5 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + I(ACRES_POLY^2) * CBD_dist + HOMESTEAD + FIN_SQ_FT + YEAR_BUILT + logMAX + logPARK  + MCA3 + logSHOP  +SALE_SEASO, data=workingdata)
+summary(model.logSaleValue5)
+```
+
+AND CBD distance squared
+```{r}
+model.logSaleValue6 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + I(ACRES_POLY^2) * CBD_dist + ACRES_POLY*I(CBD_dist^2) + I(ACRES_POLY^2)*I(CBD_dist^2)+ HOMESTEAD + FIN_SQ_FT + YEAR_BUILT + logMAX + logPARK  + MCA3 + logSHOP  +SALE_SEASO, data=workingdata)
+summary(model.logSaleValue6)
+```

### 2013-02-01 analysis/SandboxMax/20082010SalesData_Interaction.Rmd
1/31

Max's Analysis -- 2008-2010 SalesData 1/31/13
========================================================
Today we are looking at interaction terms and whether attributes such as land size and traffic noise have a marginal effect that varies over space. Our goal is to map these marginal effects to show the need for locally-weighted regression.

Although using a linear dependent variable would be easier to interpret, the model assumptions are violated and some of the explanatory variables do not fit/explain the variation in sales value as well as they do when the sales value is transformed into log.

To find the marginal effect of an attribute that includes quadratic relationships and interaction terms requires a little more math.

Lets look at an example equation: log (y) = a + b1(x) + b2 (x^2) + b3 (x*z)
In order to get y by itself, we need to take the exponent of both sides:
y = exp^[a + b1(x) + b2 (x^2) + b3 (x*z)]

Now, to estimate the marginal effect x has on y, we take the derivative of both sides with respect to x:
dy/dx = (b1 + 2(b2) + b3(z)) * exp ^ [a + b1(x) + b2 (x^2) + b3 (x*z)]

Preparation for regression analysis...
```{r, cache=TRUE}
getwd()

library (foreign)
workingdata <- read.dbf("../../../Data/R2GIS/CleanData/Sales20082010.dbf")
require(zoo)
require(lmtest)
require(car)

```

After the Thursday, 1/31 morning meeting with Aaron, found that most of the extreme over/under estimation of sales values occur in the city of St. Paul, where one neighborhood is 'good' (Hihgland Park) and another is riddled with crime/lower income. In order to account for these features we added three variables to the model:

(1) Distance to nearest residential college (2) Median income ($2011) in Census Tract based on American Community Survey administered through US Census Bureau (3) Distance to Minneapolis & St. Paul, not just nearest CBD

In this first model, we include these three variables as well as exclude CITY variable so we can assess if there is multicollinearity present through vif(). We see that the inclusion of distance to St. Paul, Minneapolis, and nearest CBD are all closely correlated.

```{r}
model.SaleValue1 <- lm (logSALE_VA ~ COUNTY_ID + factor(SALE_YR) + SDNUM + ACRES_POLY + I(ACRES_POLY^2) + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + MAX + PARK_dist + I(PARK_dist^2)+ LAKE_dist +I(LAKE_dist^2) + MCA3 + MCA5 + SHOP_dist+I(SHOP_dist^2)  + COLLEGE_di + SP_dist + MPS_dist + CBD_dist +I(CBD_dist^2)+ MED_INCOME +SALE_SEASO, data=workingdata)

vif(model.SaleValue1)
```

The second model will exclude the St. Paul and Minneapolis distances. We see that there is no large violation of multicollinearity anymore.

```{r}
model.SaleValue2 <- lm (logSALE_VA ~ COUNTY_ID + factor(SALE_YR) + ACRES_POLY + I(ACRES_POLY^2) + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + MAX + PARK_dist + I(PARK_dist^2)+ LAKE_dist +I(LAKE_dist^2) + MCA3 + MCA5 + SHOP_dist+I(SHOP_dist^2)  + COLLEGE_di + CBD_dist +I(CBD_dist^2)+ MED_INCOME +SALE_SEASO, data=workingdata)

vif(model.SaleValue2)
```

Now we include interaction terms to view if there is an interaction effect between distance to the CBD and (1) Land Size and (2) Traffic Noise. Note that all quadratic relationships and interaction terms are significant.

```{r}
model.SaleValue3 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + log(MAX) * CBD_dist + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)

summary(model.SaleValue3)

```

Since all interaction terms were significant, we include more interaction terms that resemble the nonlinear relationship land size and distance to the central business district have with logged sales value. Note that the inclusion of more interaction terms that reflect the nonlinear relationship makes all interactions non-significant, perhaps multicollinearity is present.

```{r}
model.SaleValue4 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + ACRES_POLY*I(CBD_dist^2)+I(ACRES_POLY^2)*I(CBD_dist^2)+ I(ACRES_POLY^2)*CBD_dist + log(MAX) * CBD_dist +log(MAX)*I(CBD_dist^2) + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)

summary(model.SaleValue4)
```

The last model keeps the interaction terms as well as Acres * CBD^2, which was closest to signficance level in the preceding model. We see that all interaction terms are significant. These coefficients suggest that the value of land increases as a parcel is closer to the central business district, at a decreasing rate. Also, the value of traffic noise disturbance increases as a parcel get farther away from the central business district.

```{r}
model.SaleValue5 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + I(ACRES_POLY^2)+ACRES_POLY*I(CBD_dist^2)+ log(MAX) * CBD_dist +  HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)

summary(model.SaleValue5)
```

### 2013-02-01 analysis/MaxSandbox20052007.R

@@ -84,3 +84,31 @@ temp1 = merge(resData2, workingdata, all = TRUE)
 names(temp1)
 temp1 = temp1[, c(2, 4)]
 write.dbf(temp1, "../Data/R2GIS/20052007logSales_GARAGE.dbf")
+
+
+
+#########From 20082010SalesData_Interaction.Rmd, takes into account interaction terms
+model.SaleValue4 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + ACRES_POLY*I(CBD_dist^2)+I(ACRES_POLY^2)*I(CBD_dist^2)+ I(ACRES_POLY^2)*CBD_dist + log(MAX) + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)
+summary(model.SaleValue4)
+
+#Acquire marginal effect for Acres and Traffic Noise and place it into a table
+mfx.TRAFFIC = (model.SaleValue5$coefficients["MAX"]+(model.SaleValue5$coefficients["CBD_dist:MAX"]*workingdata$CBD_dist)) * 
+  exp(model.SaleValue5$coefficients["(Intercept)"]+(model.SaleValue5$coefficients["MAX"]*workingdata$MAX) +(model.SaleValue5$coefficients["CBD_dist:MAX"]*workingdata$MAX*workingdata$CBD_dist))
+
+mfx.LAND = (model.SaleValue5$coefficients["ACRES_POLY"]+ (2*model.SaleValue5$coefficients["I(ACRES_POLY^2)"])+
+  (model.SaleValue5$coefficients["ACRES_POLY:CBD_dist"]*workingdata$CBD_dist) + (model.SaleValue5$coefficients["ACRES_POLY:I(CBD_dist^2)"]*(workingdata$CBD_dist ^2))) *
+  exp(model.SaleValue5$coefficients["(Intercept)"]+(model.SaleValue5$coefficients["ACRES_POLY"]*workingdata$ACRES_POLY) +
+  (model.SaleValue5$coefficients["I(ACRES_POLY^2)"]*(workingdata$ACRES_POLY ^2)) + 
[…]

### 2013-02-01 analysis/MaxSandbox20082010.R

@@ -11,17 +11,16 @@ require(car)
 
 ####Linear model investigation
 ##Dependent variable: Sales Value (untransformed)
-model.SaleValue1 <- lm (SALE_VALUE ~ COUNTY_ID + CITY + SALE_YR + SDNUM + ACRES_POLY + HOMESTEAD + FIN_SQ_FT + YEAR_BUILT + MAX + PARK_dist + LAKE_dist + MCA3 + MCA5 + SHOP_dist + CBD_dist +SALE_SEASO, data=workingdata)
+model.SaleValue1 <- lm (SALE_VALUE ~ COUNTY_ID + CITY + SALE_YR + SDNUM + ACRES_POLY + HOMESTEAD + FIN_SQ_FT + YEAR_BUILT + MAX + PARK_dist + LAKE_dist + MCA3 + MCA5 + SHOP_dist  + COLLEGE_di + CBD_dist + MED_INCOME +SALE_SEASO, data=workingdata)
 summary(model.SaleValue1)
 anova(model.SaleValue1) #MCA5 and SALE_MO 
 #Diagnostics
-plot(model.SaleValue1) #Normality issues once again #5222 large leverage
+plot(model.SaleValue1) #Normality issues once again
 vif(model.SaleValue1) #multicollinearity #SDNUM VIF above 10 #aliased coefficients means that there is perfect multicollinearity with one of the variables. In the summary table the variable will be NA
 dwtest (model.SaleValue1) #autocorrelation # Signs of autocorrelation since DW value is less than 1.5 (1.4538)
 bptest(model.SaleValue1)
 outlierTest(model.SaleValue1)
 
-workingdata = workingdata [-5222, ]
 
 ##Dependent variable: Sales Value (untransformed) w/o MCA5, SDNUM
 model.SaleValue2 <- lm (SALE_VALUE ~ COUNTY_ID + CITY + SALE_YR  + ACRES_POLY + HOMESTEAD + FIN_SQ_FT + YEAR_BUILT + MAX + PARK_dist + LAKE_dist + MCA3 + SHOP_dist + CBD_dist  +SALE_SEASO, data=workingdata)
@@ -81,3 +80,30 @@ temp1 = merge(resData2, workingdata, all = TRUE)
 names(temp1)
 temp1 = temp1[, c(2, 4)]
 write.dbf(temp1, "../Data/R2GIS/20082010logSales_GARAGE.dbf")
+
+
[…]

### 2013-02-01 munge/Sales20052007_munge.R

@@ -8,7 +8,7 @@ sales0507$GARSQFT <- as.numeric(as.character(sales0507$GARAGESQFT)) #Converting 
 sales0507$SALE_SEASON <- factor(sales0507$SALE_QRT)
 sales0507$SALE_MO <- factor(sales0507$SALE_MONTH)
 dataNames <- names (sales0507)
-VarsIWant <- which(dataNames %in% c("COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "TOTAL_TAX", "HOME_STYLE", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "SALE_VALUE", "SALE_YR", "BEDS", "BATH", "MAX", "TRACTCE10", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "GARSQFT", "SALE_SEASON", "SDNUM", "MCA3", "MCA5", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "CBD_dist", "PIN", "SALE_MO"))
+VarsIWant <- which(dataNames %in% c("GARSQFT","SALE_SEASON", "SALE_MO","COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "TOTAL_TAX", "HOME_STYLE", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "SALE_VALUE", "SALE_YR", "BEDS", "BATH", "MAX", "TRACTCE10", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "SDNUM", "MCA3", "MCA5", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "CBD_dist", "PIN", "SP_dist", "MPS_dist", "COLLEGE_di", "MED_INCOME"))
 workingdata = sales0507[ , VarsIWant]
 summary (workingdata)
 workingdata$logSALE_VALUE = log(workingdata$SALE_VALUE) #Transforming sales values into logs

### 2013-02-01 munge/Sales20082010_munge.R

@@ -9,7 +9,7 @@ sales0810$GARSQFT <- as.numeric(as.character(sales0810$GARAGESQFT)) #Converting 
 sales0810$SALE_SEASON <- factor(sales0810$SALE_QRT)
 sales0810$SALE_MO <- factor(sales0810$SALE_MONTH)
 dataNames <- names (sales0810)
-VarsIWant <- which(dataNames %in% c("GARSQFT","SALE_SEASON", "SALE_MO","COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "TOTAL_TAX", "HOME_STYLE", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "SALE_VALUE", "SALE_YR", "BEDS", "BATH", "MAX", "TRACTCE10", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "SDNUM", "MCA3", "MCA5", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "CBD_dist", "PIN"))
+VarsIWant <- which(dataNames %in% c("GARSQFT","SALE_SEASON", "SALE_MO","COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "TOTAL_TAX", "HOME_STYLE", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "SALE_VALUE", "SALE_YR", "BEDS", "BATH", "MAX", "TRACTCE10", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "SDNUM", "MCA3", "MCA5", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "CBD_dist", "PIN", "SP_dist", "MPS_dist", "COLLEGE_di", "MED_INCOME"))
 workingdata = sales0810[ , VarsIWant]
 summary (workingdata)
 workingdata$logSALE_VALUE = log(workingdata$SALE_VALUE) #Transforming sales values into logs

### 2013-02-01 analysis/SandboxMax/20052007SalesData_Interaction.Rmd
2/1/2013

--- 2013-02-01 analysis/SandboxMax/20082010SalesData_Interaction.Rmd
@@
 library (foreign)
-workingdata <- read.dbf("../../../Data/R2GIS/CleanData/Sales20082010.dbf")
+workingdata <- read.dbf("../../../Data/R2GIS/CleanData/Sales20052007.dbf")
 require(zoo)
@@
 Now we include interaction terms to view if there is an interaction effect between distance to the CBD and (1) Land Size and (2) Traffic Noise.
-Note that all quadratic relationships and interaction terms are significant.
+Note that all non linear relationships are significant except for CBD distance.
+Also, both interaction effects are insignificant however I believe that getting rid of the insignificant quadratic term for CBD will yield significant results for the interaction between land size and location.
 
 ```{r}
-model.SaleValue3 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + log(MAX) * CBD_dist + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)
+model.SaleValue3 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist +I(CBD_dist^2)+I(ACRES_POLY^2)+ log(MAX) * CBD_dist + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)
 
@@
 
-Since all interaction terms were significant, we include more interaction terms that resemble the nonlinear relationship land size and distance to the central business district have with logged sales value.
-Note that the inclusion of more interaction terms that reflect the nonlinear relationship makes all interactions non-significant, perhaps multicollinearity is present.
-
+Excluding the quadratic term for CBD distance and the interaction effect between traffic noise and CBD distance did not make the interaction effect between land size and distance significant.
 ```{r}
-model.SaleValue4 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + ACRES_POLY*I(CBD_dist^2)+I(ACRES_POLY^2)*I(CBD_dist^2)+ I(ACRES_POLY^2)*CBD_dist + log(MAX) * CBD_dist +log(MAX)*I(CBD_dist^2) + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)
+model.SaleValue4 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist+I(ACRES_POLY^2)+ log(MAX) + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)
 
 summary(model.SaleValue4)
+
 ```
 
-The last model keeps the interaction terms as well as Acres * CBD^2, which was closest to signficance level in the preceding model.
-We see that all interaction terms are significant.
-These coefficients suggest that the value of land increases as a parcel is closer to the central business district, at a decreasing rate.
-Also, the value of traffic noise disturbance increases as a parcel get farther away from the central business district.
-
+Including all possible interaction effects between land size and distance to CBD yields significant results.
 ```{r}
-model.SaleValue5 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + I(ACRES_POLY^2)+ACRES_POLY*I(CBD_dist^2)+ log(MAX) * CBD_dist +  HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)
+model.SaleValue5 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + I(ACRES_POLY^2) * CBD_dist + I(ACRES_POLY^2) * I(CBD_dist^2)+ ACRES_POLY * I(CBD_dist^2)+log(MAX) + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)
 
 summary(model.SaleValue5)
+
 ```

### 2013-02-01 analysis/MaxSandbox20082010.R

@@ -83,12 +83,13 @@ write.dbf(temp1, "../Data/R2GIS/20082010logSales_GARAGE.dbf")
 
 
 #########From 20082010SalesData_Interaction.Rmd, takes into account interaction terms
-model.SaleValue5 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + I(ACRES_POLY^2)+ACRES_POLY*I(CBD_dist^2)+ log (MAX) +  HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)
+model.SaleValue5 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + I(ACRES_POLY^2)+ACRES_POLY*I(CBD_dist^2)+ log(MAX) * CBD_dist +  HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_SEASO, data=workingdata)
 summary(model.SaleValue5)
 
 #Acquire marginal effect for Acres and Traffic Noise and place it into a table
-mfx.TRAFFIC = (model.SaleValue5$coefficients["MAX"]+(model.SaleValue5$coefficients["CBD_dist:MAX"]*workingdata$CBD_dist)) * 
-  exp(model.SaleValue5$coefficients["(Intercept)"]+(model.SaleValue5$coefficients["MAX"]*workingdata$MAX) +(model.SaleValue5$coefficients["CBD_dist:MAX"]*workingdata$MAX*workingdata$CBD_dist))
+mfx.TRAFFIC = ((model.SaleValue5$coefficients["log(MAX)"]*(log(workingdata$MAX)^(model.SaleValue5$coefficients["log(MAX)"]-1))) +
[…]

### 2013-02-01 analysis/MaxSandbox20082010.R
2/1

@@ -87,24 +87,19 @@ model.SaleValue5 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES
 summary(model.SaleValue5)
 
 #Acquire marginal effect for Acres and Traffic Noise and place it into a table
-mfx.TRAFFIC = ((model.SaleValue5$coefficients["log(MAX)"]*(log(workingdata$MAX)^(model.SaleValue5$coefficients["log(MAX)"]-1))) +
-  (workingdata$CBD_dist * model.SaleValue5$coefficients["CBD_dist:log(MAX)"]* (log(workingdata$MAX)^(model.SaleValue5$coefficients["CBD_dist:log(MAX)"]-1))) * 
-  exp(model.SaleValue5$coefficients["(Intercept)"])
+mfx.TRAFFIC = ((model.SaleValue5$coefficients["log(MAX)"]*(1/(workingdata$MAX))) + (model.SaleValue5$coefficients["CBD_dist:log(MAX)"]*(workingdata$CBD_dist/workingdata$MAX))) * (workingdata$SALE_VALUE)
 
-mfx.LAND = (model.SaleValue5$coefficients["ACRES_POLY"]+ (2*model.SaleValue5$coefficients["I(ACRES_POLY^2)"])+
-  (model.SaleValue5$coefficients["ACRES_POLY:CBD_dist"]*workingdata$CBD_dist) + (model.SaleValue5$coefficients["ACRES_POLY:I(CBD_dist^2)"]*(workingdata$CBD_dist ^2))) *
-  exp(model.SaleValue5$coefficients["(Intercept)"]+(model.SaleValue5$coefficients["ACRES_POLY"]*workingdata$ACRES_POLY) +
-  (model.SaleValue5$coefficients["I(ACRES_POLY^2)"]*(workingdata$ACRES_POLY ^2)) + 
-  (model.SaleValue5$coefficients["ACRES_POLY:CBD_dist"]*workingdata$ACRES_POLY*workingdata$CBD_dist) + 
-  (model.SaleValue5$coefficients["ACRES_POLY:I(CBD_dist^2)"]*workingdata$ACRES_POLY*(workingdata$CBD_dist ^2)))
+mfx.LAND = (model.SaleValue5$coefficients["ACRES_POLY"]+ (2*workingdata$ACRES_POLY * model.SaleValue5$coefficients["I(ACRES_POLY^2)"])+
[…]

### 2013-02-02 analysis/01LWR/firstLWR.R
creating our first LWR script

@@ -1,0 +1,134 @@
+
+
+# The goal of this script is to run a basic LWR model using the St. Paul working data...
+
+
+# What working directory will it be in?
+# Try to put it in an "LWR" folder inside analysis.
+# Remember to save the data to "Data/R2GIS"
+require(foreign)
+mydata = read.dbf("../Data/R2GIS/CleanData/Sales20052007.dbf")
+my.observation = 1
+DATAFRAME = mydata[sample(1:dim(mydata)[1], 500), ]
+MYMODEL = "logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT"
+KVECTOR = c(50, 75, 100)
+
+
+Data.Frame = DATAFRAME
+my.model = MYMODEL
+kvector = KVECTOR
+# Model in quotes is default model, don't need anything entered for it to run
+LWR = function(my.observation, 
+               Data.Frame, 
+               my.model = "dep.var~indep.var1i+ndep.var2",
+               kvector) {
+  #my.observation = 2
+  #Data.Frame = test.data
+  #my.model = "dep.var ~ indep.var1 + indep.var2"
+  sample.size = dim(Data.Frame)[1]
+  
+
+  numK <- length(kvector)
+  
+  temp = strsplit(my.model, "~")
+  temp2 = strsplit(temp[[1]][2], "\\+")
+  numBetas = length(temp2[[1]]) + 1
+  myvars = gsub(" ", "", temp2[[1]])
+  
+  
+  # Creates containers for our parameters/metrics. 
+  temp.est.betas = matrix(-99, numBetas, numK) # Need a matrix, row for each B, columns for each k
+  temp.st.errors = matrix(-99, numBetas, numK) # Same as above
+  temp.est.dep.var = matrix(-99, 1, numK ) # Matrix to be consistent with above, but only 1 value per k
+  temp.leverage = matrix(-99, 1, numK) # Same as temp.est.dep.var
+  temp.est.dep.var.without = matrix(-99, 1, numK)
+  # Calculate distance
+  # locations are "Long_X" and "Lat_Y" and are decimal degrees
+  # first step is to calculate the distance all other observations are from this observation
+  require(fields)
+  
+  Di=t(rdist.earth(cbind(Data.Frame$Long_X[my.observation], Data.Frame$Lat_Y[my.observation]),
+                   cbind(Data.Frame$Long_X, Data.Frame$Lat_Y)))
+  
[…]

### 2013-02-02 analysis/01LWR/firstLWRMC.R

@@ -1,0 +1,145 @@
+
+
+# The goal of this script is to run a basic LWR model using the St. Paul working data...
+
+
+# What working directory will it be in?
+# Try to put it in an "LWR" folder inside analysis.
+# Remember to save the data to "Data/R2GIS"
+require(foreign)
+require(multicore, quietly = TRUE)
+mydata = read.dbf("../Data/R2GIS/CleanData/Sales20052007.dbf")
+my.observation = 1
+DATAFRAME = mydata
+MYMODEL = "logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT"
+KVECTOR = c(50, 100, 200, 500, 1000, 5000)
+
+
+Data.Frame = DATAFRAME
+my.model = MYMODEL
+kvector = KVECTOR
+
+#print(summary(DATAFRAME))
+# Model in quotes is default model, don't need anything entered for it to run
+LWR = function(my.observation, 
+               Data.Frame, 
+               my.model = "dep.var~indep.var1i+ndep.var2",
+               kvector) {
+  #my.observation = 2
+  #Data.Frame = test.data
+  #my.model = "dep.var ~ indep.var1 + indep.var2"
+  sample.size = dim(Data.Frame)[1]
+  
+
+  numK <- length(kvector)
+  
+  temp = strsplit(my.model, "~")
+  temp2 = strsplit(temp[[1]][2], "\\+")
+  numBetas = length(temp2[[1]]) + 1
+  myvars = gsub(" ", "", temp2[[1]])
+  
+  
+  # Creates containers for our parameters/metrics. 
+  temp.est.betas = matrix(-99, numBetas, numK) # Need a matrix, row for each B, columns for each k
+  temp.st.errors = matrix(-99, numBetas, numK) # Same as above
+  temp.est.dep.var = matrix(-99, 1, numK ) # Matrix to be consistent with above, but only 1 value per k
+  temp.leverage = matrix(-99, 1, numK) # Same as temp.est.dep.var
+  temp.est.dep.var.without = matrix(-99, 1, numK)
+  # Calculate distance
+  # locations are "Long_X" and "Lat_Y" and are decimal degrees
+  # first step is to calculate the distance all other observations are from this observation
+  require(fields)
+  
+  Di=t(rdist.earth(cbind(Data.Frame$Long_X[my.observation], Data.Frame$Lat_Y[my.observation]),
+                   cbind(Data.Frame$Long_X, Data.Frame$Lat_Y)))
+  
[…]

### 2013-02-04 analysis/01LWR/firstLWRMC.R
script to run our first LWR on the data

@@ -8,54 +8,56 @@
 # Remember to save the data to "Data/R2GIS"
 require(foreign)
 require(multicore, quietly = TRUE)
-mydata = read.dbf("../Data/R2GIS/CleanData/Sales20052007.dbf")
-my.observation = 1
-DATAFRAME = mydata
-MYMODEL = "logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT"
-KVECTOR = c(50, 100, 200, 500, 1000, 5000)
+require(fields, quietly = TRUE)
 
-
-Data.Frame = DATAFRAME
-my.model = MYMODEL
-kvector = KVECTOR
-
-#print(summary(DATAFRAME))
-# Model in quotes is default model, don't need anything entered for it to run
 LWR = function(my.observation, 
                Data.Frame, 
-               my.model = "dep.var~indep.var1i+ndep.var2",
+               my.model,
                kvector) {
-  #my.observation = 2
-  #Data.Frame = test.data
-  #my.model = "dep.var ~ indep.var1 + indep.var2"
-  sample.size = dim(Data.Frame)[1]
   
-
+  # These four lines let you work within the function rather than having to run the function (helpful for debugging)
+#     Data.Frame = DATAFRAME
+#     my.model = MYMODEL
+#     kvector = KVECTOR
+#     my.observation = 3
+  
+  # grab some dimensions for creating our containers
+  sample.size = dim(Data.Frame)[1]
   numK <- length(kvector)
   
-  temp = strsplit(my.model, "~")
-  temp2 = strsplit(temp[[1]][2], "\\+")
-  numBetas = length(temp2[[1]]) + 1
-  myvars = gsub(" ", "", temp2[[1]])
-  
+  # temp = strsplit(my.model, "~")
+  # temp2 = strsplit(temp[[1]][2], "\\+")
+  # numBetas = length(temp2[[1]]) + 1
+  # myvars = gsub(" ", "", temp2[[1]])
+  lmreg = lm(my.model, data = Data.Frame)
+  numBetas = length(lmreg$coefficients)
+  coefNames = names(lmreg$coefficients)
   
   # Creates containers for our parameters/metrics. 
   temp.est.betas = matrix(-99, numBetas, numK) # Need a matrix, row for each B, columns for each k
+  rownames(temp.est.betas) = coefNames
+  colnames(temp.est.betas) = kvector
   temp.st.errors = matrix(-99, numBetas, numK) # Same as above
+  rownames(temp.st.errors) = coefNames
[…]

### 2013-02-04 analysis/01LWR/firstLWRMC.R
created helper folder and moved code to "helper/LWRfunctions.R"

@@ -1,7 +1,4 @@
-
-
 # The goal of this script is to run a basic LWR model using the St. Paul working data...
-
 
 # What working directory will it be in?
 # Try to put it in an "LWR" folder inside analysis.
@@ -10,155 +7,14 @@ require(foreign)
 require(multicore, quietly = TRUE)
 require(fields, quietly = TRUE)
 
-LWR = function(my.observation, 
-               Data.Frame, 
-               my.model,
-               kvector) {
-  
-  # These four lines let you work within the function rather than having to run the function (helpful for debugging)
-#     Data.Frame = DATAFRAME
-#     my.model = MYMODEL
-#     kvector = KVECTOR
-#     my.observation = 3
-  
-  # grab some dimensions for creating our containers
-  sample.size = dim(Data.Frame)[1]
-  numK <- length(kvector)
-  
-  # temp = strsplit(my.model, "~")
-  # temp2 = strsplit(temp[[1]][2], "\\+")
-  # numBetas = length(temp2[[1]]) + 1
-  # myvars = gsub(" ", "", temp2[[1]])
-  lmreg = lm(my.model, data = Data.Frame)
-  numBetas = length(lmreg$coefficients)
-  coefNames = names(lmreg$coefficients)
-  
-  # Creates containers for our parameters/metrics. 
-  temp.est.betas = matrix(-99, numBetas, numK) # Need a matrix, row for each B, columns for each k
-  rownames(temp.est.betas) = coefNames
-  colnames(temp.est.betas) = kvector
-  temp.st.errors = matrix(-99, numBetas, numK) # Same as above
-  rownames(temp.st.errors) = coefNames
-  colnames(temp.st.errors) = kvector  
-  temp.est.dep.var = matrix(-99, 1, numK ) # Matrix to be consistent with above, but only 1 value per k
-  colnames(temp.est.dep.var) = kvector
-  temp.leverage = matrix(-99, 1, numK) # Same as temp.est.dep.var
-  colnames(temp.leverage) = kvector
-  temp.est.dep.var.without = matrix(-99, 1, numK)
-  colnames(temp.est.dep.var.without) = kvector
-  
-  # Before we run LWR on an observation using different bandwidths we calculate distances
-  # locations are expected to be "Long_X" and "Lat_Y" and are decimal degrees
-  # require(fields)
-  
[…]

### 2013-02-04 helper/LWRfunctions.R
added GCV function

@@ -145,3 +145,12 @@ Reorganizer = function(lapplyoutput) {
   
   outputList
 }
+
+# Generalized Cross Validation for each k
+GCV = function(leverages, yhats, dep.var) {
+  sample.size = dim(yhats)[1]
+  v1 <- colSums(leverages)
+  SE <- colSums((dep.var-yhats)^2)
+  gcv <- sample.size*SE/(sample.size-v1)^2   
+  gcv
+}

### 2013-02-04 analysis/01LWR/01GCVcalcs.R
calculated GCV for our initial LWR run and for a basic OLS model... we should be doing LWR!

@@ -1,0 +1,14 @@
+
+
+load("~/Noise Hedonic Project/Data/R2GIS/LWRoutput/Sales20052007LWRoutput2013-02-03.RData")
+filePrefix = "../Data/R2GIS/CleanData/"
+inputFile = "Sales20052007.dbf"
+DATAFRAME = read.dbf(paste0(filePrefix, inputFile))
+
+GCV(output$leverages, output$yhats, DATAFRAME$logSALE_VA)
+
+OLS.lm = lm(MYMODEL, data = DATAFRAME)
+
+OLS.leverages = lm.influence(OLS.lm)$hat
+GCV(matrix(OLS.leverages, ncol = 1), matrix(OLS.lm$fitted.values, ncol= 1), DATAFRAME$logSALE_VA)
+

### 2013-02-04 munge/EMV2006_munge.R
updated save filename (was incorrect) and ran the EMV2006_munge.R file (Creating the PairsPlot.png file)

@@ -77,4 +77,4 @@ cor(workingdata[, c("logSALE_VALUE", "logFIN_SQ_FT", "logMAX", "ACRES_POLY", "lo
 
 ##Write new .dbf table and store it in 'CleanData' folder
 EMV2006Clean = data.frame(workingdata)
-write.dbf(EMV2006Clean, "../Data/R2GIS/CleanData/Sales20082010.dbf" )
+write.dbf(EMV2006Clean, "../Data/R2GIS/CleanData/EMV2006.dbf" )

### 2013-02-04 analysis/01LWR/firstLWRMC.R
added TODO items for Max and experimented with LWR on EMV2006 data

@@ -10,15 +10,15 @@ require(fields, quietly = TRUE)
 # the following command loads up some functions we'll use
 source("helper/LWRfunctions.R")
 
-MYMODEL = "logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT"
+MYMODEL = "logEMV~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT"
 KVECTOR = c(100, 200, 500, 1000, 5000)
 
 filePrefix = "../Data/R2GIS/CleanData/"
-inputFile = "Sales20082010.dbf" # "Sales20052007.dbf"
+inputFile = "Sales20052007.dbf"
 DATAFRAME = read.dbf(paste0(filePrefix, inputFile))
 start = Sys.time()
-N = dim(DATAFRAME)[1]
-output.raw = mclapply(1:N,
+N = 10 # dim(DATAFRAME)[1]
+output.raw = lapply(1:N,
                       LWR,
                       Data.Frame = DATAFRAME,
                       my.model = MYMODEL,

### 2013-02-04 analysis/01GlobalRegression/GlobalRegression_2_04_2013.R
Created global regression script that pulls best model from Max's sandbox into one short script that writes .dbf tables ready for GIS analysis

@@ -1,0 +1,46 @@
+#This script runs the most up to date global regression models that include interaction effects and non linear relationships.
+#After running the model, the script calculates the marginal effects for land and traffic noise.
+#Lastly, the script writes a .dbf table that includes marginal effects for land and traffic noise, residuals, xy coordinates (in meters) and a Unique ID that is ready for analysis in ArcGIS
+
+##Preparation for regression
+require(zoo)
+require(lmtest)
+require(car)
+
+####### 2005 to 2007 Sales Model ########
+workingdata2005 <- read.dbf("../Data/R2GIS/CleanData/Sales20052007.dbf")
+##Run model
+model.SaleValue2005 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + I(ACRES_POLY^2) * CBD_dist + I(ACRES_POLY^2) * I(CBD_dist^2)+ ACRES_POLY * I(CBD_dist^2)+log(MAX) + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_MO, data=workingdata2005)
+summary(model.SaleValue2005)
+##Calculating marginal effects for land and traffic noise
+mfx.LAND.2005 = (model.SaleValue2005$coefficients["ACRES_POLY"]+ (2*workingdata2005$ACRES_POLY * model.SaleValue2005$coefficients["I(ACRES_POLY^2)"])+
+  (model.SaleValue2005$coefficients["ACRES_POLY:CBD_dist"]*workingdata2005$CBD_dist) + (model.SaleValue2005$coefficients["ACRES_POLY:I(CBD_dist^2)"]*(workingdata2005$CBD_dist ^2)) + 
+  (model.SaleValue2005$coefficients["CBD_dist:I(ACRES_POLY^2)"]*2*workingdata2005$CBD_dist*workingdata2005$ACRES_POLY)+
[…]

### 2013-02-04 analysis/MaxSandbox20082010.R

@@ -113,5 +113,5 @@ workingdata$RowName = row.names(workingdata)
 temp = merge(resData3, workingdata, all = TRUE)
 #From temporary table that merged resData table and workingdata table, extract residuals and PIN
 names(temp)
-temp = temp[, c(2, 4, 27)]
+temp = temp[, c(2, 4, 25:27)]
 write.dbf(temp, "../Data/R2GIS/20082010logSales_Modelbuilder.dbf")

### 2013-02-04 munge/EMV2006_munge.R

@@ -7,7 +7,7 @@ names(emv2006) #found that some observations have a 0 or negative sales value
 emv2006$GARSQFT <- as.numeric(as.character(emv2006$GARAGESQFT)) #Converting factor to numeric
 emv2006$MCA3 <- emv2006$X3_MCA
 dataNames <- names (emv2006)
-VarsIWant <- which(dataNames %in% c("GARSQFT","COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "EMV_TOTAL", "BEDS", "BATH", "MAX", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "MCA3", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "PIN", "SP_dist", "MPS_dist" ))
+VarsIWant <- which(dataNames %in% c("GARSQFT","COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "EMV_TOTAL", "BEDS", "BATH", "MAX", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "MCA3", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "PIN", "SP_dist", "MPS_dist","X_Meter", "Y_Meter"))
 workingdata = emv2006[ , VarsIWant]
 summary (workingdata)
 workingdata$logEMV = log(workingdata$EMV_TOTAL) #Transforming sales values into logs
@@ -60,17 +60,6 @@ plot (workingdata$logCBD, workingdata$logSALE_VALUE) #improved
 plot (workingdata$logSHOP, workingdata$logSALE_VALUE) #improved
 plot (workingdata$logPARK, workingdata$logSALE_VALUE)
 plot (workingdata$logLAKE, workingdata$logSALE_VALUE)
-
-#Second round of outlier cuts after looking at histograms of distances
-hist(workingdata$logCBD)
-hist(workingdata$logSHOP)
-hist(workingdata$logPARK)
-hist(workingdata$logLAKE)
-SHOPoutlier = which (workingdata$logSHOP < 4)
-PARKoutlier = which (workingdata$logPARK < 3)
-LAKEoutlier = which (workingdata$logLAKE < 3)
[…]

### 2013-02-04 munge/Sales20052007_munge.R

@@ -8,7 +8,7 @@ sales0507$GARSQFT <- as.numeric(as.character(sales0507$GARAGESQFT)) #Converting 
 sales0507$SALE_SEASON <- factor(sales0507$SALE_QRT)
 sales0507$SALE_MO <- factor(sales0507$SALE_MONTH)
 dataNames <- names (sales0507)
-VarsIWant <- which(dataNames %in% c("GARSQFT","SALE_SEASON", "SALE_MO","COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "TOTAL_TAX", "HOME_STYLE", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "SALE_VALUE", "SALE_YR", "BEDS", "BATH", "MAX", "TRACTCE10", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "SDNUM", "MCA3", "MCA5", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "CBD_dist", "PIN", "SP_dist", "MPS_dist", "COLLEGE_di", "MED_INCOME"))
+VarsIWant <- which(dataNames %in% c("GARSQFT","SALE_SEASON", "SALE_MO","COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "TOTAL_TAX", "HOME_STYLE", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "SALE_VALUE", "SALE_YR", "BEDS", "BATH", "MAX", "TRACTCE10", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "SDNUM", "MCA3", "MCA5", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "CBD_dist", "PIN", "SP_dist", "MPS_dist", "COLLEGE_di", "MED_INCOME", "X_Meter", "Y_Meter"))
 workingdata = sales0507[ , VarsIWant]
 summary (workingdata)
 workingdata$logSALE_VALUE = log(workingdata$SALE_VALUE) #Transforming sales values into logs
@@ -65,17 +65,6 @@ plot (workingdata$logCBD, workingdata$logSALE_VALUE) #improved
 plot (workingdata$logSHOP, workingdata$logSALE_VALUE) #improved
 plot (workingdata$logPARK, workingdata$logSALE_VALUE)
 plot (workingdata$logLAKE, workingdata$logSALE_VALUE)
-
[…]

### 2013-02-04 munge/Sales20082010_munge.R

@@ -9,7 +9,7 @@ sales0810$GARSQFT <- as.numeric(as.character(sales0810$GARAGESQFT)) #Converting 
 sales0810$SALE_SEASON <- factor(sales0810$SALE_QRT)
 sales0810$SALE_MO <- factor(sales0810$SALE_MONTH)
 dataNames <- names (sales0810)
-VarsIWant <- which(dataNames %in% c("GARSQFT","SALE_SEASON", "SALE_MO","COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "TOTAL_TAX", "HOME_STYLE", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "SALE_VALUE", "SALE_YR", "BEDS", "BATH", "MAX", "TRACTCE10", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "SDNUM", "MCA3", "MCA5", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "CBD_dist", "PIN", "SP_dist", "MPS_dist", "COLLEGE_di", "MED_INCOME"))
+VarsIWant <- which(dataNames %in% c("GARSQFT","SALE_SEASON", "SALE_MO","COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "TOTAL_TAX", "HOME_STYLE", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "SALE_VALUE", "SALE_YR", "BEDS", "BATH", "MAX", "TRACTCE10", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "SDNUM", "MCA3", "MCA5", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "CBD_dist", "PIN", "SP_dist", "MPS_dist", "COLLEGE_di", "MED_INCOME","X_Meter", "Y_Meter"))
 workingdata = sales0810[ , VarsIWant]
 summary (workingdata)
 workingdata$logSALE_VALUE = log(workingdata$SALE_VALUE) #Transforming sales values into logs
@@ -65,16 +65,6 @@ plot (workingdata$logSHOP, workingdata$logSALE_VALUE) #improved
 plot (workingdata$logPARK, workingdata$logSALE_VALUE)
 plot (workingdata$logLAKE, workingdata$logSALE_VALUE)
 
-#Second round of outlier cuts after looking at histograms of distances
-hist(workingdata$logCBD)
[…]

### 2013-02-08 analysis/01GlobalRegression/GlobalRegression.Rmd
Created Global Regression R Markdown file and created munging/regression model script for Dakota county parcel shapefile that includes beds, baths, and building quality.

Global Regression Models -- 2005 to 2010
========================================================

This file displays two global regression models from the 2005 to 2010 dataset: (1) that does not include beds, baths, and measurement of building quality (2) includes beds, baths, and measurement of building quality. The latter model only contains properties in Dakota County.

```{r}
library(foreign)
require(zoo)
require(lmtest)
require(car)
workingdata20052010 <- read.dbf("../../../Data/R2GIS/CleanData/Sales20052010.dbf")
workingdata20052010.Dakota <- read.dbf("../../../Data/R2GIS/CleanData/Sales20052010_Dakota.dbf")
model.SaleValue20052010 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + I(ACRES_POLY^2)* I(CBD_dist ^2) +ACRES_POLY*I(CBD_dist^2) +I(ACRES_POLY^2)*CBD_dist + log(MAX) + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_MO, data= workingdata20052010)
model.SaleValue20052010.Dakota <- lm (logSALE_VA ~  CITY + factor(SALE_YR)  + (ACRES_POLY*CBD_dist) + I(ACRES_POLY ^2)*I(CBD_dist ^2) + ACRES_POLY*I(CBD_dist ^2)+ I(ACRES_POLY ^2)*CBD_dist +HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + log(MAX) * I(CBD_dist ^2)+ log(MAX)*CBD_dist + PARK_dist  + LAKE_dist+ I(LAKE_dist ^2) + MCA3 + MED_INCOME + COLLEGE_di+ I(COLLEGE_di ^2) + SHOP_dist + SALE_MO+BEDS + BATH + I(BATH^2) + BLDG_QUAL, data=workingdata20052010.Dakota)
mfx.TRAFFIC.20052010 = (model.SaleValue20052010$coefficients["log(MAX)"]/workingdata20052010$MAX) * (workingdata20052010$SALE_VALUE)
mfx.LAND.20052010 = (model.SaleValue20052010$coefficients["ACRES_POLY"]+ (2*workingdata20052010$ACRES_POLY * model.SaleValue20052010$coefficients["I(ACRES_POLY^2)"])+
  (model.SaleValue20052010$coefficients["ACRES_POLY:CBD_dist"]*workingdata20052010$CBD_dist) + (model.SaleValue20052010$coefficients["ACRES_POLY:I(CBD_dist^2)"]*(workingdata20052010$CBD_dist ^2)) + 
  (model.SaleValue20052010$coefficients["CBD_dist:I(ACRES_POLY^2)"]*2*workingdata20052010$CBD_dist*workingdata20052010$ACRES_POLY)+
  (model.SaleValue20052010$coefficients["I(ACRES_POLY^2):I(CBD_dist^2)"]*2*workingdata20052010$ACRES_POLY*(workingdata20052010$CBD_dist ^2))) * (workingdata20052010$SALE_VALUE)
mfx.TRAFFIC.20052010.Dakota = ((model.SaleValue20052010.Dakota$coefficients["log(MAX)"]/workingdata20052010.Dakota$MAX)+((workingdata20052010.Dakota$CBD_dist * model.SaleValue20052010.Dakota$coefficients["CBD_dist:log(MAX)"])/workingdata20052010.Dakota$MAX)+
  ((workingdata20052010.Dakota$CBD_dist^2 * model.SaleValue20052010.Dakota$coefficients["I(CBD_dist^2):log(MAX)"])/workingdata20052010.Dakota$MAX)) * (workingdata20052010.Dakota$SALE_VALUE)
mfx.LAND.20052010.Dakota = (model.SaleValue20052010.Dakota$coefficients["ACRES_POLY"]+ (2*workingdata20052010.Dakota$ACRES_POLY * model.SaleValue20052010.Dakota$coefficients["I(ACRES_POLY^2)"])+
  (model.SaleValue20052010.Dakota$coefficients["ACRES_POLY:CBD_dist"]*workingdata20052010.Dakota$CBD_dist) + (model.SaleValue20052010.Dakota$coefficients["ACRES_POLY:I(CBD_dist^2)"]*(workingdata20052010.Dakota$CBD_dist ^2)) + 
  (model.SaleValue20052010.Dakota$coefficients["CBD_dist:I(ACRES_POLY^2)"]*2*workingdata20052010.Dakota$CBD_dist*workingdata20052010.Dakota$ACRES_POLY)+
  (model.SaleValue20052010.Dakota$coefficients["I(ACRES_POLY^2):I(CBD_dist^2)"]*2*workingdata20052010.Dakota$ACRES_POLY*(workingdata20052010.Dakota$CBD_dist ^2))) * (workingdata20052010.Dakota$SALE_VALUE)

```

Here we compare the two outputs from the regression models. Note that the inclusion of beds, baths, and building quality causes a large increase in the amount of variance in log(Sale Value) explained by the model. Also, the model that includes beds and baths has significant interaction terms with traffic noise whereas the other model does not.

```{r}
summary(model.SaleValue20052010)
summary(model.SaleValue20052010.Dakota)
```

Looking at the marginal effects of the two models, note that the marginal effect for both land and traffic noise decreases on average in the model that includes beds, baths, and building quality.

```{r}
#Traffic Noise
summary(mfx.TRAFFIC.20052010)
summary(mfx.TRAFFIC.20052010.Dakota)
#Land Size
summary(mfx.LAND.20052010)
summary(mfx.LAND.20052010.Dakota)
```

### 2013-02-08 analysis/01GlobalRegression/GlobalRegression_2_04_2013.R

@@ -67,3 +67,27 @@ dataNames <- names(temp)
 Output <- which(dataNames %in% c("Res", "mfxTRAFFIC", "mfxLAND", "PIN", "X_Meter", "Y_Meter", "UNIQID"))
 temp = temp[, Output]
 write.dbf(temp, "../Data/R2GIS/GlobalRegressionOutput/Sales20052010.dbf")
+
+
+####### 2005 to 2010 Sales Model for Dakota County########
+workingdata20052010.Dakota <- read.dbf("../Data/R2GIS/CleanData/Sales20052010_Dakota.dbf")
+##Run model
+model.SaleValue20052010.Dakota <- lm (logSALE_VA ~  CITY + factor(SALE_YR)  + (ACRES_POLY*CBD_dist) + I(ACRES_POLY ^2)*I(CBD_dist ^2) + ACRES_POLY*I(CBD_dist ^2)+ I(ACRES_POLY ^2)*CBD_dist +HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + log(MAX) * I(CBD_dist ^2)+ log(MAX)*CBD_dist + PARK_dist  + LAKE_dist+ I(LAKE_dist ^2) + MCA3 + MED_INCOME + COLLEGE_di+ I(COLLEGE_di ^2) + SHOP_dist + SALE_MO+BEDS + BATH + I(BATH^2) + BLDG_QUAL, data=workingdata20052010.Dakota)
+summary(model.SaleValue20052010.Dakota)
+##Calculating marginal effects for land and traffic noise
+mfx.TRAFFIC.20052010.Dakota = ((model.SaleValue20052010.Dakota$coefficients["log(MAX)"]/workingdata20052010.Dakota$MAX)+((workingdata20052010.Dakota$CBD_dist * model.SaleValue20052010.Dakota$coefficients["CBD_dist:log(MAX)"])/workingdata20052010.Dakota$MAX)+
+  ((workingdata20052010.Dakota$CBD_dist^2 * model.SaleValue20052010.Dakota$coefficients["I(CBD_dist^2):log(MAX)"])/workingdata20052010.Dakota$MAX)) * (workingdata20052010.Dakota$SALE_VALUE)
+mfx.LAND.20052010.Dakota = (model.SaleValue20052010.Dakota$coefficients["ACRES_POLY"]+ (2*workingdata20052010.Dakota$ACRES_POLY * model.SaleValue20052010.Dakota$coefficients["I(ACRES_POLY^2)"])+
[…]

### 2013-02-08 analysis/MaxSandBox20052010_Dakota.R

@@ -1,0 +1,73 @@
+library (foreign)
+workingdata <- read.dbf("../Data/R2GIS/CleanData/Sales20052010_Dakota.dbf")
+summary(workingdata)
+
+###Preparation for regression analysis, load packages for tests
+require(zoo)
+require(lmtest)
+require(car)
+
+
+
+######Normality Issues arise so we investigate with the log transformation on the dependent variable
+##Dependent variable: Sales Value (log transformed) w/o MCA5, SDNUM
+model.logSaleValue1 <- lm (logSALE_VA ~  CITY + factor(SALE_YR)  + ACRES_POLY+ HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + log(MAX) + PARK_dist + LAKE_dist + MCA3 + MED_INCOME+COLLEGE_di+ SHOP_dist + CBD_dist + SALE_MO+BEDS+BATH+BLDG_QUAL, data=workingdata)
+summary(model.logSaleValue1)
+anova(model.logSaleValue1)
+#Diagnostics
+outlierTest(model.logSaleValue1)
+ncvTest(model.logSaleValue1) #
+dwtest (model.logSaleValue1) #autocorrelation
+bptest(model.logSaleValue1)
+plot(model.logSaleValue1) 
+
+###Dependent variable: Sales Value (log transformed) w/o MCA5, SDNUM, SALE_MO
+model.logSaleValue2 <- lm (logSALE_VA ~ CITY + factor(SALE_YR)  + ACRES_POLY+ I(ACRES_POLY ^2) + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + log(MAX) + PARK_dist + I(PARK_dist ^2) + LAKE_dist+ I(LAKE_dist ^2) + MCA3 + MED_INCOME + COLLEGE_di+ I(COLLEGE_di ^2) + SHOP_dist+ I(SHOP_dist^2) + CBD_dist + I(CBD_dist ^2)+ SALE_MO + BEDS + I(BEDS^2) + BATH + I(BATH^2) + BLDG_QUAL, data=workingdata)
+summary(model.logSaleValue2)
+anova( model.logSaleValue2)
+plot(model.logSaleValue2)
+
+
+###Dependent variable: Sales Value (log transformed) w/ GARAGE
[…]

### 2013-02-08 munge/Sales20052010_munge_Dakota.R

@@ -1,0 +1,76 @@
+library (foreign)
+salesdak <- read.dbf("../Data/GIS2R/Sales20052010.dbf")
+summary(salesdak) #found that some observations have a 0 or negative sales value
+t <- which(salesdak$SALE_VALUE < 1)
+salesdak = salesdak [-t, ] #Excludes observations without sales value information
+beds <- which(salesdak$BEDS > 0)
+salesdak = salesdak [beds, ]
+
+#Pulling the variables we WANT into a new, working dataframe.
+salesdak$GARSQFT <- as.numeric(as.character(salesdak$GARAGESQFT)) #Converting factor to numeric
+salesdak$SALE_SEASON <- factor(salesdak$SALE_QRT)
+salesdak$SALE_MO <- factor(salesdak$SALE_MONTH)
+dataNames <- names (salesdak)
+VarsIWant <- which(dataNames %in% c("GARSQFT","SALE_SEASON", "SALE_MO","COUNTY_ID", "CITY", "ZIP", "ACRES_POLY", "HOMESTEAD", "TOTAL_TAX", "HOME_STYLE", "FIN_SQ_FT", "GARAGE", "YEAR_BUILT", "SALE_VALUE", "SALE_YR", "BEDS", "BATH", "MAX", "TRACTCE10", "BLDG_QUAL", "PARK_dist", "LAKE_dist", "SDNUM", "MCA3", "MCA5", "UNIQID", "Long_X", "Lat_Y", "SHOP_dist", "CBD_dist", "PIN", "SP_dist", "MPS_dist", "COLLEGE_di", "MED_INCOME","X_Meter", "Y_Meter"))
+workingdata = salesdak[ , VarsIWant]
+summary (workingdata)
+workingdata$logSALE_VALUE = log(workingdata$SALE_VALUE) #Transforming sales values into logs
+
+##Outlier Investigation -- Looking to not violate normality assumption by looking at histograms
+#hist(workingdata$ACRES_POLY) #Large outliers -- very right skewed
+#hist(workingdata$FIN_SQ_FT) #Also right skewed
+#hist(workingdata$MAX) #Left skewed
+#hist(workingdata$SALE_VALUE) #Right skewed
+LivingAreaOutliers = which (workingdata$FIN_SQ_FT > 4000) #Limit dataset to houses with less than 5000 sq ft.
+AcreageOutliers = which (workingdata$ACRES_POLY > .6) #Limit dataset to parcels less than one acre
[…]

### 2013-03-20 analysis/01GlobalRegression/GlobalRegression.Rmd
Fix the marginal effects in noise variable

@@
 workingdata20052010.Dakota <- read.dbf("../../../Data/R2GIS/CleanData/Sales20052010_Dakota.dbf")
-model.SaleValue20052010 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + I(ACRES_POLY^2)* I(CBD_dist ^2) +ACRES_POLY*I(CBD_dist^2) +I(ACRES_POLY^2)*CBD_dist + log(MAX) + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_MO, data= workingdata20052010)
-model.SaleValue20052010.Dakota <- lm (logSALE_VA ~  CITY + factor(SALE_YR)  + (ACRES_POLY*CBD_dist) + I(ACRES_POLY ^2)*I(CBD_dist ^2) + ACRES_POLY*I(CBD_dist ^2)+ I(ACRES_POLY ^2)*CBD_dist +HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + log(MAX) * I(CBD_dist ^2)+ log(MAX)*CBD_dist + PARK_dist  + LAKE_dist+ I(LAKE_dist ^2) + MCA3 + MED_INCOME + COLLEGE_di+ I(COLLEGE_di ^2) + SHOP_dist + SALE_MO+BEDS + BATH + I(BATH^2) + BLDG_QUAL, data=workingdata20052010.Dakota)
-mfx.TRAFFIC.20052010 = (model.SaleValue20052010$coefficients["log(MAX)"]/workingdata20052010$MAX) * (workingdata20052010$SALE_VALUE)
+model.SaleValue20052010 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)  + ACRES_POLY * CBD_dist + I(ACRES_POLY^2)* I(CBD_dist ^2) +ACRES_POLY*I(CBD_dist^2) +I(ACRES_POLY^2)*CBD_dist + MAX + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_MO, data= workingdata20052010)
+model.SaleValue20052010.Dakota <- lm (logSALE_VA ~  CITY + factor(SALE_YR)  + (ACRES_POLY*CBD_dist) + I(ACRES_POLY ^2)*I(CBD_dist ^2) + ACRES_POLY*I(CBD_dist ^2)+ I(ACRES_POLY ^2)*CBD_dist +HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + MAX * I(CBD_dist ^2)+ MAX*CBD_dist + PARK_dist  + LAKE_dist+ I(LAKE_dist ^2) + MCA3 + MED_INCOME + COLLEGE_di+ I(COLLEGE_di ^2) + SHOP_dist + SALE_MO+BEDS + BATH + I(BATH^2) + BLDG_QUAL, data=workingdata20052010.Dakota)
+mfx.TRAFFIC.20052010 = (model.SaleValue20052010$coefficients["MAX"]) * (workingdata20052010$SALE_VALUE)
 mfx.LAND.20052010 = (model.SaleValue20052010$coefficients["ACRES_POLY"]+ (2*workingdata20052010$ACRES_POLY * model.SaleValue20052010$coefficients["I(ACRES_POLY^2)"])+
@@
   (model.SaleValue20052010$coefficients["I(ACRES_POLY^2):I(CBD_dist^2)"]*2*workingdata20052010$ACRES_POLY*(workingdata20052010$CBD_dist ^2))) * (workingdata20052010$SALE_VALUE)
-mfx.TRAFFIC.20052010.Dakota = ((model.SaleValue20052010.Dakota$coefficients["log(MAX)"]/workingdata20052010.Dakota$MAX)+((workingdata20052010.Dakota$CBD_dist * model.SaleValue20052010.Dakota$coefficients["CBD_dist:log(MAX)"])/workingdata20052010.Dakota$MAX)+
-  ((workingdata20052010.Dakota$CBD_dist^2 * model.SaleValue20052010.Dakota$coefficients["I(CBD_dist^2):log(MAX)"])/workingdata20052010.Dakota$MAX)) * (workingdata20052010.Dakota$SALE_VALUE)
+mfx.TRAFFIC.20052010.Dakota = ((model.SaleValue20052010.Dakota$coefficients["MAX"])+((workingdata20052010.Dakota$CBD_dist * model.SaleValue20052010.Dakota$coefficients["CBD_dist:MAX"])+
+  ((workingdata20052010.Dakota$CBD_dist^2 * model.SaleValue20052010.Dakota$coefficients["I(CBD_dist^2):MAX"])))) * (workingdata20052010.Dakota$SALE_VALUE)
 mfx.LAND.20052010.Dakota = (model.SaleValue20052010.Dakota$coefficients["ACRES_POLY"]+ (2*workingdata20052010.Dakota$ACRES_POLY * model.SaleValue20052010.Dakota$coefficients["I(ACRES_POLY^2)"])+

### 2013-03-20 analysis/01GlobalRegression/GlobalRegression_2_04_2013.R

@@ -10,10 +10,10 @@ require(car)
 ####### 2005 to 2010 Sales Model ########
 workingdata20052010 <- read.dbf("../Data/R2GIS/CleanData/Sales20052010.dbf")
 ##Run model
-model.SaleValue20052010 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)+log(MAX)  + ACRES_POLY * CBD_dist + I(ACRES_POLY^2)* I(CBD_dist ^2) +ACRES_POLY*I(CBD_dist^2) +I(ACRES_POLY^2)*CBD_dist + log(MAX) + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_MO, data= workingdata20052010)
+model.SaleValue20052010 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)+ ACRES_POLY * CBD_dist + I(ACRES_POLY^2)* I(CBD_dist ^2) +ACRES_POLY*I(CBD_dist^2) +I(ACRES_POLY^2)*CBD_dist + MAX + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_MO, data= workingdata20052010)
 summary(model.SaleValue20052010)
 ##Calculating marginal effects for land and traffic noise
-mfx.TRAFFIC.20052010 = (model.SaleValue20052010$coefficients["log(MAX)"]/workingdata20052010$MAX) * (workingdata20052010$SALE_VALUE)
+mfx.TRAFFIC.20052010 = (model.SaleValue20052010$coefficients["MAX"]) * (workingdata20052010$SALE_VALUE)
 mfx.LAND.20052010 = (model.SaleValue20052010$coefficients["ACRES_POLY"]+ (2*workingdata20052010$ACRES_POLY * model.SaleValue20052010$coefficients["I(ACRES_POLY^2)"])+
[…]

### 2013-03-20 analysis/SandboxMax/CoefTimeMedianSandbox.R

@@ -25,25 +25,25 @@ load(paste0(dataPath, files2open[myFile], sep = ""))
 # 3) add a linear best fit line to look for a trend
 # 4) repeat above with different combinations of coefficients, bandwidths, and models
 
-###########################Log-transformed noise variable
+###########################'Linear' noise variable
 names(output)
-beta.noise = which(names(output)=="beta.log(MAX)") #find which column beta noise is in
-ses.noise = which(names(output)=="ses.log(MAX)") #find which column standard error noise is in
+beta.noise = which(names(output)=="beta.MAX") #find which column beta noise is in
+ses.noise = which(names(output)=="ses.MAX") #find which column standard error noise is in
 myCoeff.beta = names(output)[beta.noise]# choose a coefficient to work with
 myCoeff.ses = names(output)[ses.noise]
 test.table <- data.frame (time = DATAFRAME$TimePeriod[obs2run], coef = output[myCoeff.beta], se = output[myCoeff.ses], noise = DATAFRAME$MAX[obs2run], Sale.Val= DATAFRAME$SALE_VALUE[obs2run])
 head(test.table)
 #Calculate marginal effects for log-transformed noise variable.
-test.table$mfx.MAX.k25 <- (test.table$coef.beta.log.MAX..k25/test.table$noise) * test.table$Sale.Val
-test.table$mfx.MAX.k50 <- (test.table$coef.beta.log.MAX..k50/test.table$noise) * test.table$Sale.Val
-test.table$mfx.MAX.k75 <- (test.table$coef.beta.log.MAX..k75/test.table$noise) * test.table$Sale.Val
-test.table$mfx.MAX.k100 <- (test.table$coef.beta.log.MAX..k100/test.table$noise) * test.table$Sale.Val
-test.table$mfx.MAX.k150 <- (test.table$coef.beta.log.MAX..k150/test.table$noise) * test.table$Sale.Val
-test.table$mfx.MAX.k200 <- (test.table$coef.beta.log.MAX..k200/test.table$noise) * test.table$Sale.Val
-test.table$mfx.MAX.k400 <- (test.table$coef.beta.log.MAX..k400/test.table$noise) * test.table$Sale.Val
[…]

### 2013-03-20 analysis/SandboxMax/CoefTimePlot.R

@@ -25,25 +25,25 @@ load(paste0(dataPath, files2open[myFile], sep = ""))
 # 3) add a linear best fit line to look for a trend
 # 4) repeat above with different combinations of coefficients, bandwidths, and models
 
-####Log-transformed noise variable
+####'Linear' noise variable
 names(output)
-beta.noise = which(names(output)=="beta.log(MAX)") #find which column beta noise is in
-ses.noise = which(names(output)=="ses.log(MAX)") #find which column standard error noise is in
+beta.noise = which(names(output)=="beta.MAX") #find which column beta noise is in
+ses.noise = which(names(output)=="ses.MAX") #find which column standard error noise is in
 myCoeff.beta = names(output)[beta.noise]# choose a coefficient to work with
 myCoeff.ses = names(output)[ses.noise]
 test.table <- data.frame (coef = output[myCoeff.beta], se = output[myCoeff.ses], noise = DATAFRAME$MAX[obs2run], Sale.Val= DATAFRAME$SALE_VALUE[obs2run])
 head(test.table)
 #Calculate marginal effects for log-transformed noise variable.
-test.table$mfx.MAX.k25 <- (test.table$coef.beta.log.MAX..k25/test.table$noise) * test.table$Sale.Val
-test.table$mfx.MAX.k50 <- (test.table$coef.beta.log.MAX..k50/test.table$noise) * test.table$Sale.Val
-test.table$mfx.MAX.k75 <- (test.table$coef.beta.log.MAX..k75/test.table$noise) * test.table$Sale.Val
-test.table$mfx.MAX.k100 <- (test.table$coef.beta.log.MAX..k100/test.table$noise) * test.table$Sale.Val
-test.table$mfx.MAX.k150 <- (test.table$coef.beta.log.MAX..k150/test.table$noise) * test.table$Sale.Val
-test.table$mfx.MAX.k200 <- (test.table$coef.beta.log.MAX..k200/test.table$noise) * test.table$Sale.Val
-test.table$mfx.MAX.k400 <- (test.table$coef.beta.log.MAX..k400/test.table$noise) * test.table$Sale.Val
-test.table$mfx.MAX.k600 <- (test.table$coef.beta.log.MAX..k600/test.table$noise) * test.table$Sale.Val
[…]

### 2013-03-20 analysis/03DakotaLWR/LWRMC.R
ran models for Dakota County

@@ -1,0 +1,43 @@
+# The goal of this script is to run a basic LWR model using the St. Paul working data...
+
+# What working directory will it be in?
+# Try to put it in an "LWR" folder inside analysis.
+# Remember to save the data to "Data/R2GIS"
+require(foreign)
+require(multicore, quietly = TRUE)
+require(fields, quietly = TRUE)
+
+# the following command loads up some functions we'll use
+source("helper/LWRfunctions.R")
+
+MYMODEL = "logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+MED_INCOME+HOME_STYLE+ELEM"
+MYMODELsmall = "logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+MED_INCOME+HOME_STYLE"
+KVECTOR = c(25, 50, 75, 100, 150, 200, 400, 600, 800, 1000)
+
+filePrefix = "../Data/R2GIS/CleanData/"
+# inputFile = "Sales20052010.dbf"
+# DATAFRAME = read.dbf(paste0(filePrefix, inputFile))
+# dakOBS = which(DATAFRAME$COUNTY_ID == "037" & DATAFRAME$BEDS > 0 & DATAFRAME$GARSQFT>175)
+# dakDATA = DATAFRAME[dakOBS, ]
+outputFile = "dakotaCLEAN.dbf"
+# write.dbf(dakDATA, file = paste0(filePrefix, outputFile))
+dakDATA = read.dbf(paste0(filePrefix, outputFile))
+
+start = Sys.time()
+obs2run = rownames(dakDATA)[which(dakDATA$TimePeriod>11)]
+output.raw = mclapply(obs2run,
+                      LWRyear2,
+                      Data.Frame = dakDATA,
+                      my.model = MYMODEL, my.modelSMALL = MYMODELsmall,
+                      kvector = KVECTOR
+                      )
+end = Sys.time()
+print(end - start)
+dataSource = strsplit(inputFile, "\\.")[[1]][1]
+# save the output in case something goes wrong later
+save(output.raw, inputFile, MYMODEL, file = paste0(filePrefix, dataSource, "LWRoutputRAW", Sys.Date(), ".RData"))
+
+names(output.raw) = DATAFRAME$UNIQID[obs2run]
+output = Reorganizer(output.raw)
[…]

### 2013-03-20 analysis/03DakotaLWR/gcvFiguresDakota.R

@@ -1,0 +1,35 @@
+
+
+getwd() #assume I'm in the project default working directory "Noise Hedonic Project"
+
+require(foreign)
+source("helper/LWRfunctions.R")
+
+filePrefix = "../Data/R2GIS/CleanData/"
+inputFile = "dakotaCLEAN.dbf"
+DATAFRAME = read.dbf(paste0(filePrefix, inputFile))
+obs2run = which(DATAFRAME$TimePeriod>11)
+
+dataPath = "../Data/R2GIS/LWRoutput/Dakota/TimeLag24Months/"
+filelist = list.files(path = dataPath)
+
+files2open = filelist[which(substr(filelist, 1, 26) == "Sales20052010LWRoutput2013")]
+myFile = 7
+pdf("analysis/03DakotaLWR/GCVplotsTimeLag24Months.pdf")
+for (myFile in 1:length(files2open)) {
+  load(paste0(dataPath, files2open[myFile], sep = ""))
+  gcvs = GCV(output$leverages, output$yhats, DATAFRAME$logSALE_VA[obs2run])
+#   print(files2open[myFile])
+#   print(min(gcvs))
+  ks = as.numeric(substr(colnames(output[[1]]), 2, 5))
+  plot(ks, gcvs, type = "l", main = "")
+  title(MYMODEL, cex.main = .5)
+  title(paste0("N = ", dim(output[[1]])[1]), line = .5)
+  title(paste("data: ", substr(files2open[myFile], 28, nchar(files2open[myFile]))), line = -1)
+  lmreg = lm(MYMODEL, data = DATAFRAME[obs2run, ])
+  levs = lm.influence(lmreg)$hat
+  globalGCV = GCV(cbind(levs), cbind(lmreg$fitted.values), DATAFRAME$logSALE_VA[obs2run])
+  title(paste("global model gcv:", round(globalGCV, 3)), line = -2)
+  title(paste("min gcv:", round(min(gcvs), 4)), line = -3)
+}
+dev.off()

### 2013-03-20 analysis/01LWR/firstLWRMC.R
reran some full-study models with two-year and one-year sale lags

@@ -10,8 +10,8 @@ require(fields, quietly = TRUE)
 # the following command loads up some functions we'll use
 source("helper/LWRfunctions.R")
 
-MYMODEL = "logSALE_VA~log(MAX)+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+MED_INCOME+HIGH"
-MYMODELsmall = "logSALE_VA~log(MAX)+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+MED_INCOME"
+MYMODEL = "logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+MED_INCOME+MCA3+HOME_STYLE+PARK_dist+LAKE_dist+SHOP_dist+CITY"
+MYMODELsmall = "logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+MED_INCOME+MCA3+HOME_STYLE+PARK_dist+LAKE_dist+SHOP_dist"
 KVECTOR = c(25, 50, 75, 100, 150, 200, 400, 600, 800, 1000)
 
 filePrefix = "../Data/R2GIS/CleanData/"

### 2013-03-20 helper/LWRfunctions.R

@@ -205,7 +205,7 @@ LWRyear2 = function(my.observation,
   # then we calculate distances (locations are expected to be "Long_X" and "Lat_Y" and are decimal degrees)
   # require(fields)
   Data.Frame = subset(Data.Frame, TimePeriod<Data.Frame[as.character(my.observation), "TimePeriod"]+1 & 
-    TimePeriod>Data.Frame[as.character(my.observation), "TimePeriod"]-25)
+    TimePeriod>Data.Frame[as.character(my.observation), "TimePeriod"]-13)
   
   Di=t(rdist.earth(cbind(Data.Frame[as.character(my.observation), "Long_X"], Data.Frame[as.character(my.observation), "Lat_Y"]),
                    cbind(Data.Frame$Long_X, Data.Frame$Lat_Y)))

### 2013-03-20 analysis/SandboxMax/CoefTimeMedianDakota.R
median coef plot for dakota

@@ -1,0 +1,251 @@
+
+
+# starting to make figures comparing the LWR coefficients over time
+
+require(foreign)
+source("helper/LWRfunctions.R")
+
+filePrefix = "../Data/R2GIS/CleanData/"
+inputFile = "Sales20052010_Dakota.dbf"
+DATAFRAME = read.dbf(paste0(filePrefix, inputFile))
+obs2run = which(DATAFRAME$TimePeriod>11)
+
+dataPath = "../Data/R2GIS/LWRoutput/Dakota/TimeLag06Months/"
+filelist = list.files(path = dataPath)
+
+files2open = filelist[which(substr(filelist, 1, 26) == "Sales20052010LWRoutput2013")]
+myFile = 2 # this determines which file we're opening
+
+load(paste0(dataPath, files2open[myFile], sep = ""))
+# now we should have "output" loaded in our workspace and "MYMODEL" telling us which regression we ran
+
+# the basic idea is to 
+# 1) choose a coefficient and bandwidth
+# 2) plot the coefficient value vs. the month of sale
+# 3) add a linear best fit line to look for a trend
+# 4) repeat above with different combinations of coefficients, bandwidths, and models
+
+###########################'Linear' noise variable
+names(output)
+beta.noise = which(names(output)=="beta.MAX") #find which column beta noise is in
+ses.noise = which(names(output)=="ses.MAX") #find which column standard error noise is in
+myCoeff.beta = names(output)[beta.noise]# choose a coefficient to work with
+myCoeff.ses = names(output)[ses.noise]
+#Problem with test.table -- <NA> produced for row names in output file
+test.table <- data.frame (time = DATAFRAME$TimePeriod[obs2run], coef = output[myCoeff.beta], se = output[myCoeff.ses], noise = DATAFRAME$MAX[obs2run], Sale.Val= DATAFRAME$SALE_VALUE[obs2run])
+head(test.table)
+#Calculate marginal effects for log-transformed noise variable.
+test.table$mfx.MAX.k25 <- (test.table$coef.beta.MAX..k25) * test.table$Sale.Val
[…]

### 2013-03-20 analysis/SandboxMax/gcvFiguresAcrossModelsSandbox.R

@@ -1,0 +1,36 @@
+
+
+getwd() #assume I'm in the project default working directory "Noise Hedonic Project"
+
+require(foreign)
+source("helper/LWRfunctions.R")
+
+filePrefix = "../Data/R2GIS/CleanData/"
+inputFile = "Sales20052010.dbf"
+DATAFRAME = read.dbf(paste0(filePrefix, inputFile))
+obs2run = which(DATAFRAME$TimePeriod>11)
+
+dataPath = "../Data/R2GIS/LWRoutput/TimeLag06months/"
+filelist = list.files(path = dataPath)
+
+files2open = filelist[which(substr(filelist, 1, 26) == "Sales20052010LWRoutput2013")]
+
+myFile = 8 # this determines which file we're opening
+
+load(paste0(dataPath, files2open[myFile], sep = ""))
+# now we should have "output" loaded in our workspace and "MYMODEL" telling us which regression we ran
+
+
+pdf("analysis/02LWRComparisons/GCVplotsTimeLag06Months.pdf")
+gcvs = GCV(output$leverages, output$yhats, DATAFRAME$logSALE_VA[obs2run])
+ks = as.numeric(substr(colnames(output[[1]]), 2, 5))
+plot(ks, gcvs, type = "l", main = "")
+title(MYMODEL, cex.main = .5)
+title(paste0("N = ", dim(output[[1]])[1]), line = .5)
+title(paste("data: ", substr(files2open[myFile], 28, nchar(files2open[myFile]))), line = -1)
+lmreg = lm(MYMODEL, data = DATAFRAME[obs2run, ])
+levs = lm.influence(lmreg)$hat
+globalGCV = GCV(cbind(levs), cbind(lmreg$fitted.values), DATAFRAME$logSALE_VA[obs2run])
+title(paste("global model gcv:", round(globalGCV, 3)), line = -2)
+title(paste("min gcv:", round(min(gcvs), 4)), line = -3)
+dev.off()

### 2013-03-21 analysis/01GlobalRegression/GlobalRegression_2_04_2013.R
modeled after williamson (2000) looking at two different time periods in global regression to compare across time

@@ -9,16 +9,27 @@ require(car)
 
 ####### 2005 to 2010 Sales Model ########
 workingdata20052010 <- read.dbf("../Data/R2GIS/CleanData/Sales20052010.dbf")
-##Run model
-model.SaleValue20052010 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)+ ACRES_POLY * CBD_dist + I(ACRES_POLY^2)* I(CBD_dist ^2) +ACRES_POLY*I(CBD_dist^2) +I(ACRES_POLY^2)*CBD_dist + MAX + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_MO, data= workingdata20052010)
+workingdata20052010$PostCrash = 0
+crashobs <- which(workingdata20052010$TimePeriod>46)
+workingdata20052010$PostCrash[crashobs] = 1
+
+##Run model (All)
+model.SaleValue20052010 <- lm (logSALE_VA ~ COUNTY_ID + CITY + factor(SALE_YR)+ ACRES_POLY+ ACRES_POLY * CBD_dist + I(ACRES_POLY^2)* I(CBD_dist ^2) +ACRES_POLY*I(CBD_dist^2) +I(ACRES_POLY^2)*CBD_dist + MAX + HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + LAKE_dist + I(LAKE_dist^2) + PARK_dist + I(PARK_dist^2)  + MCA3 + SHOP_dist + I(SHOP_dist^2) + MED_INCOME + COLLEGE_di + SALE_MO, data= workingdata20052010)
 summary(model.SaleValue20052010)
-##Calculating marginal effects for land and traffic noise
+##Calculating marginal effects for land and traffic noise (All)
 mfx.TRAFFIC.20052010 = (model.SaleValue20052010$coefficients["MAX"]) * (workingdata20052010$SALE_VALUE)
 mfx.LAND.20052010 = (model.SaleValue20052010$coefficients["ACRES_POLY"]+ (2*workingdata20052010$ACRES_POLY * model.SaleValue20052010$coefficients["I(ACRES_POLY^2)"])+
[…]

### 2013-03-21 analysis/SandboxMax/CoefTimeMedianSandbox.R

@@ -95,6 +95,7 @@ for (i in bandwidths2plot) {
        ylab = myCoeff.beta,
        main = myBandwidth)
   abline(lm(myY ~ myX), col = "red")
+  #points(x,y)
 }
 dev.off()
 

### 2013-03-21 analysis/SandboxAaron/aaronSandbox.R
deleted some code from Aaron's Sandbox

@@ -10,39 +10,5 @@ inputFile = "Sales20052010.dbf"
 DATAFRAME = read.dbf(paste0(filePrefix, inputFile))
 obs2run = which(DATAFRAME$TimePeriod>11)
 
-dataPath = "../Data/R2GIS/LWRoutput/"
-filelist = list.files(path = dataPath)
-
-files2open = filelist[which(substr(filelist, 1, 26) == "Sales20052010LWRoutput2013")]
-myFile = 12 # this determines which file we're opening
-
-load(paste0(dataPath, files2open[myFile], sep = ""))
-# now we should have "output" loaded in our workspace and "MYMODEL" telling us which regression we ran
-
-# the basic idea is to 
-# 1) choose a coefficient and bandwidth
-# 2) plot the coefficient value vs. the month of sale
-# 3) add a linear best fit line to look for a trend
-# 4) repeat above with different combinations of coefficients, bandwidths, and models
-
-names(output)
-myCoeff = names(output)[2] # choose a coefficient to work with
-colnames(output[[myCoeff]])
-bandwidths2plot = c(2, 3, 4, 6, 8, 10)
-
-pdf("analysis/02LWRComparisons/LWRcoefPlotOverTime.pdf", height = 8, width = 12)
-par(mfrow = c(2, 3))
-for (i in bandwidths2plot) {
-  myBandwidth = colnames(output[[myCoeff]])[i] # choose a bandwidth
-  myX = DATAFRAME$TimePeriod[obs2run]
-  myY = output[[myCoeff]][, myBandwidth]
-  plot(myX, myY, cex = .2,
-       xlab = "Time",
-       ylab = myCoeff,
-       main = myBandwidth)
-  abline(lm(myY ~ myX), col = "red")
-}
-dev.off()
-
 
 

### 2013-03-21 analysis/01GlobalRegression/GlobalRegression.Rmd

@@
   (model.SaleValue20052010.Dakota$coefficients["I(ACRES_POLY^2):I(CBD_dist^2)"]*2*workingdata20052010.Dakota$ACRES_POLY*(workingdata20052010.Dakota$CBD_dist ^2))) * (workingdata20052010.Dakota$SALE_VALUE)
+model.SaleValue20052010.Dakota.NoBeds <- lm (logSALE_VA ~  CITY + factor(SALE_YR)  + (ACRES_POLY*CBD_dist) + I(ACRES_POLY ^2)*I(CBD_dist ^2) + ACRES_POLY*I(CBD_dist ^2)+ I(ACRES_POLY ^2)*CBD_dist +HOMESTEAD + log(FIN_SQ_FT) + YEAR_BUILT + MAX * I(CBD_dist ^2)+ MAX*CBD_dist + PARK_dist  + LAKE_dist+ I(LAKE_dist ^2) + MCA3 + MED_INCOME + COLLEGE_di+ I(COLLEGE_di ^2) + SHOP_dist + SALE_MO, data=workingdata20052010.Dakota)
+mfx.TRAFFIC.20052010.Dakota.NoBeds = ((model.SaleValue20052010.Dakota.NoBeds$coefficients["MAX"])+((workingdata20052010.Dakota$CBD_dist * model.SaleValue20052010.Dakota.NoBeds$coefficients["CBD_dist:MAX"])+
+  ((workingdata20052010.Dakota$CBD_dist^2 * model.SaleValue20052010.Dakota.NoBeds$coefficients["I(CBD_dist^2):MAX"])))) * (workingdata20052010.Dakota$SALE_VALUE)
 
@@
 summary(model.SaleValue20052010.Dakota)
+summary(model.SaleValue20052010.Dakota.NoBeds)
 ```
@@
 summary(mfx.TRAFFIC.20052010.Dakota)
+summary(mfx.TRAFFIC.20052010.Dakota.NoBeds)
 #Land Size

### 2013-06-24 reports/Draft.Rnw
added draft of paper to reports folder

\documentclass{article}
\usepackage[round]{natbib}
\usepackage{amsmath, graphicx}

\title{A Hedonic Price Analysis of Traffic Noise in the Twin Cities Housing Market}
\begin{document}
\maketitle

\section{Introduction}

\begin{itemize}
\item Introduction to environmental amenities of a property
\item Outline how the impact of environmental quality on the value of a property is specific depending on locational factors.
\item Intro to traffic noise as an environmental good.
\item Brief description regarding the negative impacts of traffic noise (brief summaries of past studies on the topic)
\item Outline how traffic noise is measured – decibel levels on a logarithmic scale
\item Description of the housing market crash in the fall of 2008
\item How the crash effected Twin Cities metro real estate market
\item Research question: Does traffic noise have a significant impact on properties within the Twin Cities’ metro real-estate market and if so, does this effect vary across space while accounting for time?
\end{itemize}

\section{Past Research}\label{sec:lit}
Given the public policy ramifications of the issue, it is not surprising that multiple reviews of the economic impacts of traffic noise exist. \citet{Nelson1982} is perhaps the best known earliest review of 14 studies in Canada and the United States. More recently, a number of reviews have been produced for European government agencies. \citet{Bateman2001} reviewed the literature for the Scottish Government while \citet{Navrud2002} provided a ``state of the art'' review for the European Commission Environment Directorate General.

Since no explicit private market for noise abatement exists, the value of noise pollution is typically estimated through simulated or related markets. The Hedonic Price Method is commonly used to value noise by examining real estate price fluctuations as a function of noise levels. The estimation of the noise impact in the literature is typically reported as a percentage decrease in house price per one decibal (dB) increase in local traffic noise. According to \citet{Batemen2001}, the negative effect of traffic noise has ranged from 0.08\% to 2.22\% per dB with a mean around 0.55. \citet{Navrud2002} found an average decrease of 0.64\% per dB in a review of 65 noise evaluation studies. \citet{Nelson2008} produced an updated review of the traffic noise literature for the edited volume \underline{Hedonic Methods in Housing Markets Economics}. Nelson describes several areas of interest in the empirical literature, most notably: spatial modeling of the hedonic price function, long-run vs. short-run housing dynamics, and the appropriate measure of traffic noise. We now explain each of these areas in turn and our work's contribution to the field.

\subsection{Spatial Analysis}
Advances in Geographic Information System (GIS) technology and digitized datasets have made research easier to conduct over larger geographies, with larger samples, and while explicitly considering the spatial nature of the housing market. Ordinarly Least Squares estimation of hedonic functions commonly violate standard assumptions of uncorrelated error terms.

\citet{Theebe2004} econometrically estimates a spatial error model

Researchers such as , and \citet{Andersson2010} attempt to correct for spatial autocorrelation through the use of spatial

One challenge and opportunity for researchers is to properly define the spatial extent at which to conduct their analysis.

Spatial heterogeneity

Spatial autocorrelation

 data collection and spatial modeling easier than in the past. However, the larger sample sizes and spatial extents create issues of heterogeneity as the relationship between characteristics and housing prices may differ across housing submarkets.   Day (2003) investigated the impact of traffic noise in Glasgow, Scotland and found four separate submarkets with varying relationships between noise and prices. Interestingly, traffic noise coefficients were estimated to be negative in three out of four submarkets, while the fourth revealed a significantly positive relationship. The positive relationship is hypothesized to be related to increased transportation access and mobility in an outer suburb of the city. In a similar study, Day et. al (2007) found traffic noise estimates to be significantly negative in five of eight submarkets using appriximately 10 thousand residential sales in 1997 in Birmingham, England.

Most researchers who allow the hedonic function to vary over geography do so through explicit parameterization done by the researchers (usually using political boundaries).

Theebe (2004) also used market segmentation to estimate more than 160,000 property sale values in the western part of the Netherlands sold between 1997 and 1999.  First, Theebe split the full sample into five parts according to political jurisdictions. Through spatial autoregression techniques, Theebe’s results indicated that sales values are unaffected by noise levels below 65 dB. Above 65 dB, NDSI is relatively small, ranging from 0.3 to 0.5\% per dB. An analysis of submarket data yielded larger results although these findings are less precise. While Theebe covered a large study area, the noise levels are obtained for square areas of 100 x 100m using the cumulative 24 hours energy level index Leq. This study uses a Leq index at a square area of 10 x 10m, therefore each property has a unique and continuous noise decibel measurement. Consequentially, the analysis on smaller submarket samples will be relatively more precise in terms of traffic noise estimates than Theebe (2004).

While Day (2003) and Theebe (2004) considered the existence of submarkets through market segmentation and used estimators that accounted for spatial autocorrelation, these segmentations are limited by space. By defining clear boundaries of submarkets, Duarte et. al (2009) noted that this clear delimitation does not allow interdependence between submarkets to be considered. Through locally weighted regression (LWR), the authors resolved the issue of spatial autocorrelation and considered the existence of submarkets while providing a ‘soft’ border between localities. By examining 3,196 appraisals of multifamily dwellings assessed in 2005 in Barcelona, Spain, Duarte et. al investigated a range of neighborhood and environmental attributes.  A Monte Carlo test statistically validated the spatial variation of local factors. The results from the LWR indicate that the average NDSI for observations located in the 65-70 dB is negative  while average NDSI for observations exposed to 70-75 dB is 0.26\%. Finally, dwellings exposed to higher levels of noise (75-80 dB) have an average -0.40\% NDSI. The authors explained this paradox by considering areas with intermediate levels of noise have closer access to services and transport within the city without experiencing an extreme noise externality. In this study, a similar implementation of locally weighted regression is utilized in order to resolve for spatial autocorrelation while allowing for interdependency across submarkets. Furthermore, two Monte Carlo tests are utilized to statistically support (1) the use of a non-global model and (2) the spatial variation of estimated parameters.

\section{Data}
The 2010 US Census lists the population of the Minneapolis and St. Paul Metropolitan area in Minnesota as almost 3 million residents spread over seven counties. This study examines single family residential home transactions in the Census-defined urban areas of the three of the seven counties – Dakota, Ramsey and Washington County (see Figure 1). We obtained data from approximately forty thousand transactions between 2005 and 2010 (n=42,095) from the 2010 MetroGIS Regional Parcel Dataset published by the Metropolitan Council. In addition to the geographic location and date of the house sale, we collected structural and locational variables commonly used in the hedonic literature. See Table 1 for a complete list of the explanatory variables and their descriptive statistics.

\subsection{Structural Attributes}
According to \cite{Wilhelmsson2000}, the most common structural attributes included in real-estate hedonic pricing studies are living area, number of bathrooms, age, garage and lot size.  Although the 2010 MetroGIS Regional Parcel Dataset includes structural data on living area, age, garage presence, lot size and owner occupancy for every transaction, we have variables for the number of bedrooms, bathrooms, and size of the garage only for those house sales in one county. We feel confident in our results even without these variables for most of our study data because sensitivity analysis conducted in areas with the additional structural variables revealed very similar estimates when the variables were included and excluded. Additionally, other hedonic work has been published using a similar set of explanatory variables in this area, see for instance, \citet{Sander2009b}.

\subsection{Noise Data}
Insert noise data description and methodology here.

\subsection{Other Locational Attributes}
A common real estate addage states that the three most important things about real estate are: location, location and location. Knowing where each house is located allows us to also construct a vector of other attributes associated with the sales transaction. For instance, using GIS software we are able to calculate the Euclidean distance to numerous points of interest within the dataset, such as central business districts, shopping centers, parks, and lakes.

We also associate each transaction with its elementary school and include the average 3rd grade Minnesota Comprehensive Assessment (MCA) score for the local elementary school during the year of purchase. Test scores were obtained from the Minnesota Department of Education website. The school district and elementary school attendance boundary spatial information was taken from the Minnesota Geospatial Information Office Clearinghouse Data Catalog. Lastly, a variable denoting the median household income for the surrounding census tract is created through the use of TIGER shapefiles from the 2010 Census Bureau and data from the 2010 American Community Survey (ACS).

\subsection{Time}
Given that we have data from before and after the recession of 2008-09, we subset the data in Table 2 by year of sale to look for differences. In addition to the noticeable decline in nominal sales values, there is also a drop in the number of sales across years. For example, in 2010 there were only 4,206 qualified property sales within the dataset, a more than 50\% reduction from 2005. While the mean sale price declined from roughly \$280,000 pre-crash to \$230,000 post-crash, most of the structural and neighborhood variables are relatively consistent across years. However, traffic noise displays a noticeable difference in the pre- and post-crash market transactions (the mean drops from 58 dB to 52 dB).

\section{Basic Econometric Model}\label{basicModel}
Consistent with past research, this study implements a standard semi-logarithmic hedonic pricing model. Our aim is to estimate the marginal willingness to pay for different attributes, in particular changes in the traffic noise associated with the house. Equation~\eqref{eq:model} expresses the basic hedonic model.
\begin{equation}\label{eq:model}	
ln \textrm{ Sale Price}_i = \beta _0 + \beta _1 \textrm{Noise}_i+ \beta _2 S_i+ \beta _3 N_i + \beta _4 T_i + \textrm{error}_i
\end{equation}
Where Noise$_i$ is the noise level for house $i$, $S_i$ is a vector of the house's structural attributes, $N_i$ is a vector of the neighborhood attributes, and $T_i$ is a vector of year fixed effects. We can interpret the regression model coefficients as the price semi-elasticities of the underlying attributes. For instance, we can interpret the coefficient on noise as the percentage increase in price for a one decibal increase in the traffic noise associated with the transaction in our dataset.

Standard urban economic theory\footnote{Cite Muth, Mills, etc. here.} predicts that the price of land will vary over space within our dataset to account for locational ameinities. As such, we add interaction terms between lot size and distance to the nearest central business district to account for spatial variation in the price of land. The first column in Table XXX shows the results of this regression. The negative coefficient of -0.0027 on the noise variable (a one dB increase in noise decreases house price by 0.27 percent) is in line with the estimates described earlier in the literature. The significant coefficients on the lot size interaction terms suggest that the value of land varies over space. The significant coefficients on the non-linear interaction terms suggests that the nature of the spatial variation in the value of land may be complex.

Table XXX also attempts to begin to understand how the economic recession may have influenced the hedonic function in our study area. The other columns in the table show the regression output from separating the data into sales before and after September of 2008 (the month that the US Federal government took over Fannie Mae and Freddi Mac, Lehman Brothers filed for bankruptcy, and the American International Group (AIG) narrowly avoided bankruptcy only through a \$85 billion loan from the US Federal government). The coefficients for some of the hedonic variables of interest (noise, schools, land, for instance) appear different across the two time periods.

Taken in aggregate, the results in Table XXX suggest that the hedonic price function may vary over space and time. While methods exist for parameterizing this variation (such as spatial expansion as suggested by \citet{Casetti1974}), we have no a priori knowledge of how to parameterize the variation over space and time. As such, we turn to a semi-parametric form of hedonic regression, a flexible modeling approach which lets the data reveal how relationships vary, rather than specifying them beforehand.

\section{Locally Weighted Regression Model}
Locally Weighted Regression (LWR) techniques (also known as Geographically Weighted Regression) are described in detail by \citet{Brunsdon1998b}. It is a weighted least squares methodology in which regression coefficients are estimated over space as a function of the local data as described in Equation~\eqref{eq:LWRbeta},
\begin{equation}\label{eq:LWRbeta}
\hat{\beta}_i = (X'W_iX)^{-1}X'W_iY,
\end{equation}
where X is a $n \times m$ matrix of independent variables, $W_i$ is the $n \times n$ weights matrix, and Y is the $n \times 1$ vector of dependent variable values. The weights matrix, $W_i$ is a diagonal matrix where element $w_{jj}$ denotes the weight that the $j^{th}$ data point will receive in the regression coefficients estimated at location $i$ in the dataset. We employ a bi-square weights function and a k-nearest neighbor bandwidth approach as described in equation~\eqref{eq:weights}, 
\begin{equation}\label{eq:weights}
w_{jj}=\left[1-\left(\frac{d_{ij}}{d_{k}}\right)^2 \right]^2 \textrm{ if  }d_{ij}<d_{ik}\textrm{, otherwise = 0},
\end{equation}
where $d_{ij}$ denotes the distance between observations $i$ and $j$, and $d_{ik}$ is the distance from observation $i$ to the $k^{th}$ nearest observation. This function assigns weights close to 1 for data points near observation $i$, weights positive but closer to zero for observations farther away, and zero for all $n-k$ observations farther away than the $k^{th}$ nearest observation. 
We estimate LWR coefficients using bandwidths ranging from as small as 50 observations and as large as 10,000 observations. We choose the LWR bandwidth my minimizing the Generalized Cross Validation score as detailed in equation~\eqref{eq:GCV},
\begin{equation}\label{eq:GCV}
n*\sum_{i=1}^{n}\frac{(y_i-\hat{y}_i)^2}{(n-v_1)^2}, 
\end{equation} 
where $y_i$ is the dependent variable value, $\hat{y}_i$ is the predicted dependent variable value for observation $i$, and $v_1$ is the ``effective number of model parameters.''
$v_1=$tr(\textbf{S}), where the matrix \textbf{S} is the ``hat matrix'' which maps $y$ onto $\hat{y}$,
                   \begin{equation*}
                   \hat{y}=\textbf{S}y,
                   \end{equation*}
                   and each row of \textbf{S}, $r_i$ is given by:
                     \begin{equation*}
                   r_i=X_i(X'W_iX)^{-1}X'W_i.
                   \end{equation*}                
\section{Results}
Similar to the basic econometric model described in Section \ref{basicModel}, the LWR model estimates the logged sales price of a house as a function of structural, locational and temporal variables. In order to account for changing market conditions over time in our data, when estimating LWR coefficients we use only houses sold within the past 12 months. Thus, the coefficient estimates at a particular house are estimated using data from other sales nearby in both time and geography. We also estimated the models using sales within the past 6 and 24 months.

Figure XXX shows the relationship between the number of nearest neighbors receiving positive weights in the Locally Weighted Regression and the Generalized Cross Validation score.

Regression output from the LWR model is voluminous in comparison to a standard regression model, as coefficients are estimated at each location within the dataset. We report our results in a manner similar to \citet{MarmolejoDuarteCarlos;GonzalezTamez2009}. Table XXX displays the results of our prefered LWR model and a similar global regression model.

The first column in Table XXX displays the estimates from a standard semi-log OLS regression with traffice noise, structural characteristics, location-based amenities, and both city and year of sale dummy variables. The coefficient in the second row of the table shows the estimated impact of an additional dB of traffic noise on the natural log of the house sale price to be -.23 percent. This value is within the range of other estimates as described earlier in section \ref{sec:lit}. Coefficients for the dummy variables (on house style, city, and year of sale) are not reported for the sake of brevity, but are available upon request. The second column in the table reports the estimated coefficient standard errors. With the exception of the coefficient on the distance to the nearest park, all reported coefficients are statistically different from zero at conventional levels.

The third column displays the mean estimated coefficients from the LWR model. In this model coefficients are estimated at each observation within the dataset using the nearest 200 house sales within the past 12 months. The third column displays the standard deviation of the estimated coefficients to give a sense of how the coefficients vary when allowed to do so through the use of locally weighted regression techniques. The fourth column shows the percentage of the local regressions for which the coefficient's p-value is less than 0.1. All regressions contained statistically significant estimates of the impact of increased living space, and a majority contained significant estimates for lot size and year of construction. Roughly half of the regressions estimated an impact of traffic noise statistically different from zero, while approximately one-third of the local regressions estimated statistically significant estimates of the locational variables (school test scores, census tract median income, distance to local amenities).

The lack of statistical significance for many of the local regression coefficients could be due to multiple factors. First, because we are estimating local regressions with only the nearest 200 data points, rather than over 30,000 sales as in the global model, we might be estimating the coefficients with less precision and are unable to differentiate the coefficients from zero. Alternatively, the coefficients themselves might vary, sometimes being close to zero and other times not. This variation might be due to random chance (after all, we have estimated tens of thousands of regressions), or it could be the result of true spatial non-stationarity on the part of the coefficients.

We believe the use of a LWR estimation procedure is appropriate after conducting two different Monte Carlo simulations with the data. In each simulation we resampled (with replacement) the location of each house in the study and then re-estimated the LWR model with the resampled data. In the first simulation we estimated the LWR model using bandwidths ranging from the nearest 50 to 10,000 sales. In 100 consecutive simulations, the smallest Generalized Cross-Validation score was obtained at the largest bandwidth. In other words, the LWR model never performed better than the global model when the locations of the data were randomized. This seems to be strong evidence that the increased ability to predict house prices with a local model is not due to chance.

Second, we ran a Monte Carlo simulation as described in \citet{Fotheringham2002} and performed in a similar context by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009}. The simulation is as follows:
\begin{enumerate}
\item Sample with replacement the location of each data point within the study. (just as in the previous simulation)
\item Estimate a Locally Weighted Regression model on the sampled data \emph{using the optimal bandwidth calculated in original LWR model.}
\item Calculate the mean coefficient estimates as well as the standard deviation of the estimates from the sampled data LWR estimates.
\item Repeat Steps 1-3 $M$ times. (we set $M = 100$)
\item Compare the LWR coefficient means and standard deviations from the real data to the simulated values.
\end{enumerate}
Of particular interest is the standard deviation of the LWR coefficients for a variable as compared to the distribution of simulated standard deviations. If the standard deviation of the actual LWR estimates is larger than the standard deviations from the simulations, this is interpretted as evidence of spatial non-stationarity in the coefficients. The intuition is as follows. Imagine that the coefficients are constant across space. Then, running local regressions will yield different coefficient estimates across space, not because the coefficients are truly different over space, but purely due to chance and noise in the data. Resampling the location of the data and estimating LWR models repeatedly will generate a distribution of how much the coefficients will vary across space due to chance. If the standard deviation of the LWR coefficients is larger than the standard deviations seen from the resampled data, this is consistent with the hypothesis that the coefficients vary over space more than they would due to random chance and noise within the data.

The results of the second Monte Carlo simulation are presented in columns 5 and 6 of Table XXX. Column 5 displays the standard deviation of the estimated coefficients from the LWR model estimated and presented in column 3. Column 6 displays the probability of obtaining a larger standard deviation of LWR coefficient estimates based on the 100 simulations performed. For most variables, we never obtained a larger coefficient standard deviation in the simulation than we obtained from the LWR model with the true data. However, the values associated with the traffic noise and owner occupancy variables suggest that the variation in LWR coefficients in our data may have been due to random chance. These coefficients may in fact be stationary across the study area, while the other coefficients appear to be non-stationary. Future work may want to estimate a mixed-LWR model in which the coefficients on traffic noise and owner occupancy remain stationary while the other coefficients are allowed to vary over space. See \citet{Fotheringham2002} for a description of a mixed-LWR estimation algorithm.

\begin{figure}
 \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{CopyOfMCsimResultsSDs}}
 \caption{The Monte Carlo Simulation Distribution of LWR Coefficient Standard Deviations and True Coefficient Standard Deviations.}
\end{figure}

In addition to the LWR model with a bandwidth of the nearest 200 houses and a temporal lag of 12 months performing better than other bandwidths and model specifications on in terms of the smallest GCV score, it also exhibits far less spatial autocorrelation within the model residuals. We calculate the Moran’s I statistic to be 0.199 for the global model while our prefered LWR specification reduces the Moran's I statistic to 0.012, a nearly twenty-fold reduction.

Coefficients over time.

\bibliographystyle{plainnat}
\bibliography{NoiseBibliography}
\end{document}

### 2013-06-24 analysis/04MonteCarloSim/ModelBigCity/MCsimVisualizer.R

@@ -20,9 +20,10 @@ MCplotter = function(outputcoefficient, statcoefficient, meanORsd = "mean") {
   temp = density(MCMaster200[, statcoefficient])
   plot(temp, 
        xlim = c(min(c(range(temp$x), actual), na.rm = T), max(c(range(temp$x), actual), na.rm = T)),
-       main = paste(meanORsd, outputcoefficient),
-       axes = F, ylab = "relative frequency", xlab = "")
+       main = paste(meanORsd, sub("beta.", "", outputcoefficient)),
+       axes = F, ylab = "", xlab = "")
   axis(1)
+  mtext("relative frequency", 2, 1, cex = .7)
   abline(v = actual, col = "red")
 }
 
@@ -33,6 +34,14 @@ meanORsds = rep(c("mean", "sd"), c(12, 12))
 pdf("MCsimResults.pdf", height = 6, width = 24)
 par(mfrow = c(2, 12))
 for (i in 1:length(outputCOEFS)) {
+  MCplotter(outputCOEFS[i], statCOEFS[i], meanORsds[i])
+  title(MYMODEL, line = 1, outer = T)
+}
+dev.off()
+
+pdf("MCsimResultsSDs.pdf", height = 6, width = 8)
+par(mfrow = c(3, 4))
+for (i in 13:24) {
   MCplotter(outputCOEFS[i], statCOEFS[i], meanORsds[i])
   title(MYMODEL, line = 1, outer = T)
 }

### 2013-06-24 analysis/06Dakota/MAXcoeffsPlotter.R

@@ -1,0 +1,75 @@
+# GOAL: compare LWR MAX coefficients across Dakota County under alternative specifications
+
+# Load all the .RData files for Dakota County
+# Grab the MAX coefficients for the optimal bandwith in the given model output
+# plot the Max coefficients for the three paired specifications (with beds/baths/garagesqft vs. without)
+
+setwd("~/NoiseHedonicProject/Noise-Hedonic/analysis/06Dakota/") #assume I'm in the project default working directory "Noise Hedonic Project"
+require(foreign)
+source("../../helper/LWRfunctions.R")
+
+DATAFRAME = read.dbf("~/NoiseHedonicProject/Data/R2GIS/CleanData/Sales20052010.dbf")
+obs2run = which(DATAFRAME$COUNTY_ID == "037" & DATAFRAME$BATH>.8 & DATAFRAME$TimePeriod>11)
+
+#dataPath = "../Data/R2GIS/CleanData/"
+filelist = list.files()
+files2open = filelist[which(substr(filelist, 1, 6) == "Dakota")]
+
+numFiles = length(files2open)
+
+MAXcoeffs = matrix(NA, length(obs2run), numFiles)
+models = c()
+gcvs = matrix(NA, 15, numFiles)
+
+for (myFile in 1:numFiles) {
+  load(files2open[myFile])
+  models = c(models, MYMODEL)
+  gcvs[, myFile] = GCV(output$leverages, output$yhats, DATAFRAME$logSALE_VA[obs2run])
+  print(gcvs)
+  ks = colnames(output[[1]])
+  MAXcoeffs[, myFile] = output$beta.MAX[, which.min(gcvs[, myFile])]
+  #colnames(MAXcoeffs)[myFile] = paste0("Mod", myFile, ks[which.min(gcvs)])
+}
+
+MAXcoeffs.d = as.data.frame(MAXcoeffs)
+
+par(mfrow = c(3, 1))
+par(mar = c(4, 5, 4, 2))
+lm.structural = lm(V2 ~ V1, data = MAXcoeffs.d)
+plot(MAXcoeffs.d$V1, MAXcoeffs.d$V2, cex = .2, 
+     xlim = range(MAXcoeffs), ylim = range(MAXcoeffs), las = 1,
+     main = models[2], cex.main = .75,
+     xlab = "",
+     ylab = "")
+abline(0, 1, col = "blue")
[…]

### 2013-06-24 analysis/07TimeLagExploration/ModelTimeExplorer.R

@@ -1,0 +1,48 @@
+# The goal of this script is to run multiple LWR models using the St. Paul working data to find the best model
+
+require(foreign)
+require(multicore, quietly = TRUE)
+require(fields, quietly = TRUE)
+
+# the following command loads up some functions we'll use
+source("helper/LWRfunctions.R")
+
+MYMODELS = c("logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+HOME_STYLE+OWNOCC",
+             "logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+HOME_STYLE+OWNOCC+MED_INCOME+MCA3+LAKE_dist+PARK_dist+SHOP_dist+CBD_dist",
+             "logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+HOME_STYLE+OWNOCC+MED_INCOME+MCA3+LAKE_dist+PARK_dist+SHOP_dist+CBD_dist+CITY")
+KVECTOR = c(25, 50, 75, 100, 125, 150, 175, 200, 225, 300, 400, 600, 800, 1000, 2000, 4000)
+
+filePrefix = "../Data/R2GIS/CleanData/"
+inputFile = "Sales20052010.dbf"
+dataSource = strsplit(inputFile, "\\.")[[1]][1]
+
+DATAFRAME = read.dbf(paste0(filePrefix, inputFile))
+N =  dim(DATAFRAME)[1]
+
+TIMELAGS = c(6, 12, 24)
+inputVARS = expand.grid(models = MYMODELS, lags = TIMELAGS)
+
+for (combo in 1:dim(inputVARS)[1]) { #
+  MYMODEL = as.character(inputVARS$models[combo])
+  TIMELAG = inputVARS$lags[combo]
+  obs2run = which(DATAFRAME$TimePeriod>(TIMELAG-1))
+  start = Sys.time()
+  output.raw = mclapply(obs2run,
+                        LWRtimelag,
+                        Data.Frame = DATAFRAME,
+                        my.model = MYMODEL, 
+                        my.modelSMALL = "logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+HOME_STYLE+OWNOCC+MED_INCOME+MCA3+LAKE_dist+PARK_dist+SHOP_dist+CBD_dist", #substr(MYMODEL, 1, nchar(MYMODEL)-5),
+                        kvector = KVECTOR,
[…]

### 2013-06-24 analysis/07TimeLagExploration/TimeModelGCVvisualizer.R

@@ -1,0 +1,29 @@
+
+# Goal here is to create the GCV plots by model and time lag
+
+# 3 plots (one for each time lag) with 3 lines in the plot (one for each model)
+# 3 plots (one for each model) with 3 lines in the plot (one for each time lag)
+
+
+# need to create a matrix/data.frame/array for the nine different time lag and model combinations
+
+setwd("~/NoiseHedonicProject/Data/R2GIS/CleanData/")
+file.list = list.files()
+
+myfiles = file.list[which(substr(file.list, nchar(file.list)-15, nchar(file.list)-6 ) == "2013-06-23")]
+
+source("~/NoiseHedonicProject/Noise-Hedonic/helper/LWRfunctions.R")
+require(foreign)
+DATAFRAME = read.dbf("~/NoiseHedonicProject/Data/R2GIS/CleanData/Sales20052010.dbf")
+load(myfiles[1])
+
+obs2run = which(DATAFRAME$TimePeriod>(TIMELAG-1))
+
+gcvs = GCV(output$leverages, output$yhats, DATAFRAME$logSALE_VA[obs2run])
+ks = as.numeric(substr(names(gcvs), 2, 6))
+
+plot(ks, gcvs, type = "o", pch = 16, cex = .5, las = 1)
+text(3000, mean(gcvs), paste("optimal bandwidth =", ks[which.min(gcvs)]))
+text(3000, min(gcvs), paste("GCV =", round(min(gcvs), 4)), pos = 3)
+mtext(MYMODEL, 3, line = 3, cex = .4)
+mtext(TIMELAG, 3, line = 1)

### 2013-06-24 reports/code/mainResultsTables.R

@@ -1,0 +1,160 @@
+# Goal is to make a table of LWR results for the paper...
+
+# columns
+# global model coefficients and se's
+# mean LWR Beta hats
+# sd of LWR beta hats
+# monte carlo p-value
+
+# load the dataframe and helper functions
+require(foreign)
+DATAFRAME = read.dbf("~/NoiseHedonicProject/Data/R2GIS/CleanData/Sales20052010.dbf")
+obs2run = which(DATAFRAME$TimePeriod>11)
+source("~/NoiseHedonicProject/Noise-Hedonic/helper/LWRfunctions.R")
+
+# load the LWR results
+# load the Monte Carlo Results
+####################
+# Kitchen Sink Model
+####################
+load("~/NoiseHedonicProject/Noise-Hedonic/analysis/04MonteCarloSim/ModelBigCity/CopyOfSales20052010LWRmodel18-2013-04-13.RData")
+LWRMCstats = read.csv("~/NoiseHedonicProject/Noise-Hedonic/analysis/04MonteCarloSim/ModelBigCity/bandwidth200/LWRMonteCarloStats2013-05-10.csv")
+
+lm.global = lm(paste0(MYMODEL, "+factor(SALE_YR)"), data = DATAFRAME[obs2run, ])
+GlobalModel = summary(lm.global)
+global.leverages = lm.influence(lm.global, do.coef = FALSE)$hat
+
+GCV(leverages = matrix(global.leverages, ncol = 1), 
+    yhats = matrix(lm.global$fitted.values, ncol = 1), 
+    dep.var = DATAFRAME$logSALE_VA[obs2run])
+
+vars = c("(Intercept)", "MAX", "FIN_SQ_FT", "ACRES_POLY", "YEAR_BUILT", "OWNOCC", 
+         "MCA3", "MED_INCOME", "CBD_dist", "PARK_dist", "LAKE_dist", "SHOP_dist" )
+
+LWRtable = matrix(NA, length(vars), 6)
+rownames(LWRtable) = vars
+LWRtable[, 1:2] = signif(GlobalModel$coefficients[vars , 1:2], 2)
+
+# populate the rest of the table
+for (i in 1:length(vars)) {
+  # put the mean and sd of LWR beta hats in the table
+  LWRtable[i, 3] = signif(mean(output[[paste0("beta.", vars[i])]][, "k200"], na.rm = T), 2)
[…]

### 2013-06-24 analysis/07TimeLagExploration/TimeModelGCVvisualizer.R
worked to graph GCV by Model for paper

@@ -10,20 +10,56 @@
 setwd("~/NoiseHedonicProject/Data/R2GIS/CleanData/")
 file.list = list.files()
 
-myfiles = file.list[which(substr(file.list, nchar(file.list)-15, nchar(file.list)-6 ) == "2013-06-23")]
+myfiles = file.list[which(substr(file.list, nchar(file.list)-15, nchar(file.list)-6 ) == "2013-06-24")]
 
 source("~/NoiseHedonicProject/Noise-Hedonic/helper/LWRfunctions.R")
 require(foreign)
 DATAFRAME = read.dbf("~/NoiseHedonicProject/Data/R2GIS/CleanData/Sales20052010.dbf")
-load(myfiles[1])
 
-obs2run = which(DATAFRAME$TimePeriod>(TIMELAG-1))
+gcvs.global = c()
+gcvs = c()
+for (i in 4:6) {
+  load(myfiles[i])
+  
+  obs2run = which(DATAFRAME$TimePeriod>(TIMELAG-1))
+  gcv.vec = GCV(output$leverages, output$yhats, DATAFRAME$logSALE_VA[obs2run])
+  gcvs = cbind(gcvs, gcv.vec)
+  ks = as.numeric(substr(names(gcv.vec), 2, 6))
+  
+  lm.global = lm(paste0(MYMODEL, "+factor(SALE_YR)"), data = DATAFRAME[obs2run, ])
+  GlobalModel = summary(lm.global)
+  global.leverages = lm.influence(lm.global, do.coef = FALSE)$hat
+  
+  gcvs.global = c(gcvs.global, GCV(leverages = matrix(global.leverages, ncol = 1),
+                                   yhats = matrix(lm.global$fitted.values, ncol = 1),
+                                   dep.var = DATAFRAME$logSALE_VA[obs2run]))
+}
 
-gcvs = GCV(output$leverages, output$yhats, DATAFRAME$logSALE_VA[obs2run])
-ks = as.numeric(substr(names(gcvs), 2, 6))
 
-plot(ks, gcvs, type = "o", pch = 16, cex = .5, las = 1)
-text(3000, mean(gcvs), paste("optimal bandwidth =", ks[which.min(gcvs)]))
-text(3000, min(gcvs), paste("GCV =", round(min(gcvs), 4)), pos = 3)
-mtext(MYMODEL, 3, line = 3, cex = .4)
[…]

### 2013-06-24 reports/Draft.Rnw
continued working on draft of paper

@@
 \title{A Hedonic Price Analysis of Traffic Noise in the Twin Cities Housing Market}
+\date{}
 \begin{document}
@@
 \section{Past Research}\label{sec:lit}
-Given the public policy ramifications of the issue, it is not surprising that multiple reviews of the economic impacts of traffic noise exist.
-\citet{Nelson1982} is perhaps the best known earliest review of 14 studies in Canada and the United States.
+The value of noise pollution is typically estimated through simulated or related markets because no explicit private market for noise abatement exists.
+\citet{Nelson1982} is perhaps the best known earliest review of 14 studies of the economic impact of traffic noise on property values in Canada and the United States.
 More recently, a number of reviews have been produced for European government agencies.
@@
 
-Since no explicit private market for noise abatement exists, the value of noise pollution is typically estimated through simulated or related markets.
 The Hedonic Price Method is commonly used to value noise by examining real estate price fluctuations as a function of noise levels.
-The estimation of the noise impact in the literature is typically reported as a percentage decrease in house price per one decibal (dB) increase in local traffic noise.
-According to \citet{Batemen2001}, the negative effect of traffic noise has ranged from 0.08\% to 2.22\% per dB with a mean around 0.55.
+Based on the canonical work by \citet{Rosen1974}, researchers commonly estimate a hedonic price function specifying the logged sale price of a property as a linear function of the traffic noise exhibited at the house.
+Such a specification leads to reporting the impact of traffic noise as a percentage decrease in house price per one decibal (dB) increase in traffic noise.
+According to \citet{Batemen2001}, the negative effect of traffic noise has ranged from 0.08\% to 2.22\% per dB with a mean around 0.55 percent per dB.
 \citet{Navrud2002} found an average decrease of 0.64\% per dB in a review of 65 noise evaluation studies.
+
 \citet{Nelson2008} produced an updated review of the traffic noise literature for the edited volume \underline{Hedonic Methods in Housing Markets Economics}.
-Nelson describes several areas of interest in the empirical literature, most notably: spatial modeling of the hedonic price function, long-run vs.
+Nelson describes several areas of continued interest in the empirical literature, most notably: spatial modeling of the hedonic price function, long-run vs.
 short-run housing dynamics, and the appropriate measure of traffic noise.
@@
 Advances in Geographic Information System (GIS) technology and digitized datasets have made research easier to conduct over larger geographies, with larger samples, and while explicitly considering the spatial nature of the housing market.
-Ordinarly Least Squares estimation of hedonic functions commonly violate standard assumptions of uncorrelated error terms.
+Estimation of the hedonic function using Ordinarly Least Squares (OLS) is typically inappropriate because the housing data commonly exhibit spatial autocorrelation.
+In particular, spatially autocorrelated error terms will lead to inconsistent estimates of OLS regression standard errors and inappropriate measures of statistical inference.
+
+One common reason for significant spatially autocorrelated error terms is hedonic function misspecification.
+First, a portion of the hedonic regression errors may be explained by omitted spatial variables.
+Thus, nearby houses will tend to have similar spatial variable values and then similar error terms.
+Second, model misspecification can occur due to spatial non-stationarity of the hedonic function.
+That is, housing submarkets exist and the impact of changing housing characteristics will vary across submarkets.
+Failing to properly account for such heterogeneity will lead to spatially autocorrelated error estimates.
+
+How do people do submarkets? 
+\begin{itemize}
+  \item Geography 
+    \begin{itemize}
+      \item census tracts
+    \end{itemize}
+  \item Political Boundaries
+    \begin{itemize}
+      \item city boundaries
+    \end{itemize}
+  \item Other (Data Mining)
+\end{itemize}
 
@@
 
-One challenge and opportunity for researchers is to properly define the spatial extent at which to conduct their analysis.
-
-Spatial heterogeneity
-
-Spatial autocorrelation
-
- data collection and spatial modeling easier than in the past.
-However, the larger sample sizes and spatial extents create issues of heterogeneity as the relationship between characteristics and housing prices may differ across housing submarkets.
 Day (2003) investigated the impact of traffic noise in Glasgow, Scotland and found four separate submarkets with varying relationships between noise and prices.
@@
 Theebe (2004) also used market segmentation to estimate more than 160,000 property sale values in the western part of the Netherlands sold between 1997 and 1999.
-First, Theebe split the full sample into five parts according to political jurisdictions.
+First, the data were split into five parts according to political jurisdictions.
 Through spatial autoregression techniques, Theebe’s results indicated that sales values are unaffected by noise levels below 65 dB.
@@
 
+\subsection{Temporal Variation}
+A common strategy is to analyze cross-sectional data.
+However, housing transactions take place at a specific point in time and the vast majority of data sets will contain some temporal variation.
+Some researchers may simply assume the hedonic function is constant thoughout their timespan.
+Others allow the function to shift up or down through the use of temporally varying intercept terms.
+
+Few researchers allow the hedonic function to change over time.
+\citet{Cho} is a recent example of work allowing the hedonic regression coefficients to change over time, thereby estimating the changes in the implicit prices of hedonic characteristics over time.
+
+\citet{Wilhelmsson2000} split his 290 Swedish house sales into two separate time periods: 1986-89 and 1990-95.
+A Chow test revealed that the impact of traffic noise was different in the earlier vs.
+later time period, with noise being considered more of a nuisance in the 1990s in the suburb of Stockholm.
+
+We estimate regression coefficients using only sales within the past 12 months over the years 2005 - 2010.
+Such an analysis allows us to see if and when the implicit price of traffic noises changes within our study area.
+
+\subsection{Measure of Traffic Noise}
+
+\citet{HughsSirmans} use traffic volume.
+
+Spatial resolution
+
 \section{Data}
@@
 This study examines single family residential home transactions in the Census-defined urban areas of the three of the seven counties – Dakota, Ramsey and Washington County (see Figure 1).
-We obtained data from approximately forty thousand transactions between 2005 and 2010 (n=42,095) from the 2010 MetroGIS Regional Parcel Dataset published by the Metropolitan Council.
+We obtained data from approximately forty thousand sales transactions between 2005 and 2010 (n=42,095) from the 2010 MetroGIS Regional Parcel Dataset published by the Metropolitan Council.
 In addition to the geographic location and date of the house sale, we collected structural and locational variables commonly used in the hedonic literature.
@@
 Knowing where each house is located allows us to also construct a vector of other attributes associated with the sales transaction.
-For instance, using GIS software we are able to calculate the Euclidean distance to numerous points of interest within the dataset, such as central business districts, shopping centers, parks, and lakes.
+For instance, using GIS software we are able to calculate the Euclidean distance to numerous points of interest within the dataset, such as the nearest central business district, shopping centers, parks, and lakes.
 
@@
 In addition to the noticeable decline in nominal sales values, there is also a drop in the number of sales across years.
-For example, in 2010 there were only 4,206 qualified property sales within the dataset, a more than 50\% reduction from 2005.
+For example, in 2010 there were only 4,206 property sales within the dataset, a more than 50\% reduction from 2005.
 While the mean sale price declined from roughly \$280,000 pre-crash to \$230,000 post-crash, most of the structural and neighborhood variables are relatively consistent across years.
@@
 \section{Basic Econometric Model}\label{basicModel}
-Consistent with past research, this study implements a standard semi-logarithmic hedonic pricing model.
+Consistent with past research, this study implements a semi-logarithmic hedonic pricing model.
 Our aim is to estimate the marginal willingness to pay for different attributes, in particular changes in the traffic noise associated with the house.

### 2013-06-24 reports/Draft.tex
added draft of paper to reports folder
continued working on draft of paper

--- 2013-06-24 reports/Draft.Rnw
@@
-\documentclass{article}
+\documentclass{article}\usepackage{graphicx, color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
+\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
+\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
+\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
+\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
+\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
+\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
+\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
+\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
+\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
+\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
+\newcommand{\hlslot}[1]{\textit{#1}}%
+\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 \usepackage[round]{natbib}

### 2013-06-26 analysis/08LWRcoefficientsOverTime/CoefficientsOverTime.R
made a few graphs and uploaded some others

@@ -1,0 +1,60 @@
+# Do the LWR coefficients seem to vary over time?
+# the results of these regressions get plopped into the appropriate sections and tables in the article
+# ultimately might want to create a bigger table
+
+load("~/Noise Hedonic Project/Noise-Hedonic/analysis/04MonteCarloSim/ModelBigCity/CopyOfSales20052010LWRmodel18-2013-04-13.RData")
+source("~/Noise Hedonic Project/Noise-Hedonic/helper/LWRfunctions.R")
+require(foreign)
+DATAFRAME = read.dbf("~/Noise Hedonic Project/Data/R2GIS/CleanData/Sales20052010.dbf")
+
+optimalK = "k200"
+TIMELAG = 12
+obs2run = which(DATAFRAME$TimePeriod > (TIMELAG -1))
+breakMonth = 45 #september 2008
+
+tempData = data.frame(betaMAX = output$beta.MAX[, optimalK],
+                      betaSQFT = output$beta.FIN_SQ_FT[, optimalK],
+                      betaACRES = output$beta.ACRES_POLY[, optimalK],
+                      betaINT = output[["beta.(Intercept)"]][, optimalK],
+                      TimePeriod = DATAFRAME$TimePeriod[obs2run])
+tempData$Post = ifelse(tempData$TimePeriod > breakMonth, 1, 0)
+tempData$month = tempData$TimePeriod - breakMonth
+
+
+lm.MAX = lm(betaMAX ~ month*Post, data = tempData)
+summary(lm.MAX)
+
+lm.INT = lm(betaINT ~ month*Post, data = tempData)
+summary(lm.INT)
+
+# what about some crazy outliers? doesn't matter
+# INTz = (tempData$betaINT - mean(tempData$betaINT))/sd(tempData$betaINT)
+# lm.INT = lm(betaINT ~ month*Post, data = tempData, subset = abs(INTz)<10)
+# summary(lm.INT)
+
+
+lm.SQFT = lm(betaSQFT ~ month*Post, data = tempData)
+summary(lm.SQFT)
+
+lm.ACRES = lm(betaACRES ~ month*Post, data = tempData)
+summary(lm.ACRES)
+
+
+# dataByMonth = data.frame(TimePeriod = TIMELAG:72,
+#                          betaMAX = tapply(tempData$betaMAX, tempData$TimePeriod, median),
+#                          betaSQFT = tapply(tempData$betaSQFT, tempData$TimePeriod, median),
[…]

### 2013-06-26 analysis/08LWRcoefficientsOverTime/NoiseCoefficientsOverTimeAndNoise.R

@@ -1,0 +1,81 @@
+
+
+# Does the impact of traffic noise vary with the level of traffic noise?
+
+# plot the LWR noise coefficients against the MAX levels and see if there are any differences
+
+# Do the LWR coefficients seem to vary over time?
+# the results of these regressions get plopped into the appropriate sections and tables in the article
+# ultimately might want to create a bigger table
+
+load("~/Noise Hedonic Project/Noise-Hedonic/analysis/04MonteCarloSim/ModelBigCity/CopyOfSales20052010LWRmodel18-2013-04-13.RData")
+source("~/Noise Hedonic Project/Noise-Hedonic/helper/LWRfunctions.R")
+require(foreign)
+DATAFRAME = read.dbf("~/Noise Hedonic Project/Data/R2GIS/CleanData/Sales20052010.dbf")
+
+optimalK = "k200"
+TIMELAG = 12
+obs2run = which(DATAFRAME$TimePeriod > (TIMELAG -1))
+breakMonth = 45 #september 2008
+
+tempData = data.frame(betaMAX = output$beta.MAX[, optimalK],
+                      MAX = DATAFRAME$MAX[obs2run],
+                      TimePeriod = DATAFRAME$TimePeriod[obs2run])
+tempData$Post = ifelse(tempData$TimePeriod > breakMonth, 1, 0)
+tempData$month = tempData$TimePeriod - breakMonth
+tempData$MAXcat = cut(tempData$MAX, breaks = seq(25, 100, 5))
+
+lm.mod = lm(betaMAX ~ MAX*Post, data = tempData)
+predict(object = lm.mod, newdata = data.frame(MAX = c(50, 50, 75, 75), Post = c(1, 0, 1, 0)), se.fit= T)
+
+MAXcat.model = summary(lm(betaMAX ~ MAXcat-1, data = tempData)) #, subset = tempData$MAX > 50
+MAXmeans = MAXcat.model$coefficients[, 1]
+MAXlow = MAXcat.model$coefficients[, 1] - abs(MAXcat.model$coefficients[, 2])
+MAXhigh = MAXcat.model$coefficients[, 1] + abs(MAXcat.model$coefficients[, 2])
+plot(MAXmeans, ylim = c(-.005, 0), las = 1)
[…]

### 2013-06-26 reports/Draft.Rnw
updated the draft in preparation for meeting with Tsegaye

@@
 \usepackage[round]{natbib}
-\usepackage{amsmath, graphicx}
+\usepackage{caption, amsmath, graphicx}
 
@@
 \date{}
+
 \begin{document}
@@
 
-\section{Introduction}
+\begin{abstract}
+This paper implements the hedonic price method to estimate the impact of traffic noise on properties within the St.
+Paul, Minnesota metropolitan real-estate market over the time period from 2005 - 2010.
+We use Locally Weighted Regression (LWR) estimation techniques in order to allow the hedonic function to vary over time and space.
+Significant evidence suggests spatial and temporal non-stationarity in the hedonic price function within our study area.
+In contrast to previous research, we find little evidence that the impact of traffic noise exhibits a significant non-linear relationship with the decibel level of the traffic noise, nor does the impact seem to vary over space.
+Our results suggest that an increase in traffic noise of one decibel decreases house prices by an average of 0.19 percent before September, 2008, and an average of 0.37 percent after September, 2008.
+Both of these estimates are within the range estimated by previous research on the topic in other areas.
+\end{abstract}
 
-\begin{itemize}
-\item Introduction to environmental amenities of a property
-\item Outline how the impact of environmental quality on the value of a property is specific depending on locational factors.
-\item Intro to traffic noise as an environmental good.
-\item Brief description regarding the negative impacts of traffic noise (brief summaries of past studies on the topic)
-\item Outline how traffic noise is measured – decibel levels on a logarithmic scale
-\item Description of the housing market crash in the fall of 2008
-\item How the crash effected Twin Cities metro real estate market
-\item Research question: Does traffic noise have a significant impact on properties within the Twin Cities’ metro real-estate market and if so, does this effect vary across space while accounting for time?
-\end{itemize}
-
-\section{Past Research}\label{sec:lit}
+\section{Introduction and Past Research}\label{sec:lit}
 The value of noise pollution is typically estimated through simulated or related markets because no explicit private market for noise abatement exists.
@@
 The Hedonic Price Method is commonly used to value noise by examining real estate price fluctuations as a function of noise levels.
-Based on the canonical work by \citet{Rosen1974}, researchers commonly estimate a hedonic price function specifying the logged sale price of a property as a linear function of the traffic noise exhibited at the house.
-Such a specification leads to reporting the impact of traffic noise as a percentage decrease in house price per one decibal (dB) increase in traffic noise.
-According to \citet{Batemen2001}, the negative effect of traffic noise has ranged from 0.08\% to 2.22\% per dB with a mean around 0.55 percent per dB.
-\citet{Navrud2002} found an average decrease of 0.64\% per dB in a review of 65 noise evaluation studies.
+Based on the canonical work by \citet{Rosen1974}, researchers typically estimate a hedonic price function specifying the logged sale price of a property as a linear function of the traffic noise exhibited at the house.
+Such a specification leads to reporting the impact of traffic noise as a percentage decrease in house price per one decibel (dB) increase in traffic noise.
+According to \citet{Bateman2001}, the negative effect of traffic noise has ranged from 0.08\% to 2.22\% per dB with a mean around 0.55\% per dB.
+In a review of 65 noise evaluation studies \citet{Navrud2002} found an average decrease of 0.64\% per dB.
 
 \citet{Nelson2008} produced an updated review of the traffic noise literature for the edited volume \underline{Hedonic Methods in Housing Markets Economics}.
-Nelson describes several areas of continued interest in the empirical literature, most notably: spatial modeling of the hedonic price function, long-run vs.
-short-run housing dynamics, and the appropriate measure of traffic noise.
+The chapter describes several areas of continued interest in the empirical literature, most notably: the appropriate measure of traffic noise, spatial modeling of the hedonic price function, and housing market dynamics.
 We now explain each of these areas in turn and our work's contribution to the field.
+
+\subsection{Measure of Traffic Noise}
+
+Beyond the fact that no direct natural economic markets exist in which consumers can reveal their willingness to pay to avoid traffic noise, researchers also must choose how to measure the nuisance itself.
+Sound levels are commonly measured in decibels (dB), but traffic noise at a house can vary significantly depending on changing traffic conditions.
+
+Some researchers (see, for instance, \citet{HughesJr.1992}) measure the negative externality of traffic by correlating traffic volume with house prices.
+However, traffic may generate other externalities beyond noise (such as local air pollution and reduced safety for pedestrians and drivers).
+Given the interest in government policymakers in traffic noise mitigation (cite some data here), we focus on the negative externality stemming specifically from the traffic noise itself.
+Additionally, until 2011, the Minnesota Department of Transportation used a cost effectiveness threshold for noise mitigation of \$3,250 per dB reduced.
+Given that some of the benefits of noise reductions are capitalized in house prices, we are curious to see how our estimated magnitudes compare to the state cost effectiveness cutoff.
+
+I'm going to need some help writing about noise measures. Perhaps Tsegaye can lend a hand?
+
+\citet{Huang;Palmquist2001} collect noise data using 128 monitoring stations throughout a suburb of Seattle, WA.
+They use dBA $L_{10}$ as their noise measure, where $L_{10}$ denotes the value that is exceeded 10 percent of the time.
+They collapse the noise readings into 2.5 dBA wide bins and report noise impact estimates of roughly 1.4\% decrease in house sales price per category increase in noise (or about 0.4\% per dBA $L_{10}$).
 
@@
 One common reason for significant spatially autocorrelated error terms is hedonic function misspecification.
-First, a portion of the hedonic regression errors may be explained by omitted spatial variables.
+A portion of the hedonic regression errors may be explained by omitted spatial variables.
 Thus, nearby houses will tend to have similar spatial variable values and then similar error terms.
@@
 
-\citet{Theebe2004} econometrically estimates a spatial error model
+\citet{Theebe2004a} econometrically estimates a spatial error model
 
@@
 A common strategy is to analyze cross-sectional data.
-However, housing transactions take place at a specific point in time and the vast majority of data sets will contain some temporal variation.
+However, housing transactions take place at a specific point in time and the vast majority of data sets will contain some temporal variation in house sales.
 Some researchers may simply assume the hedonic function is constant thoughout their timespan.
@@
 Few researchers allow the hedonic function to change over time.
-\citet{Cho} is a recent example of work allowing the hedonic regression coefficients to change over time, thereby estimating the changes in the implicit prices of hedonic characteristics over time.
+\citet{Cho2011b} is a recent example of work allowing the hedonic regression coefficients to change over time, thereby estimating the changes in the implicit prices of hedonic characteristics over time.
 
@@
 A Chow test revealed that the impact of traffic noise was different in the earlier vs.
-later time period, with noise being considered more of a nuisance in the 1990s in the suburb of Stockholm.
+later time period, with noise being considered more of a nuisance in the suburb of Stockholm during the 1990s.
 
-We estimate regression coefficients using only sales within the past 12 months over the years 2005 - 2010.
+We estimate regression coefficients over time using a moving window of 12 months in the hedonic analysis over the years 2005 - 2010.
 Such an analysis allows us to see if and when the implicit price of traffic noises changes within our study area.
-
-\subsection{Measure of Traffic Noise}
-
-\citet{HughsSirmans} use traffic volume.
-
-Spatial resolution
+Our results suggest that the percentage change in house price from an extra decibel of traffic noise actually became more negative after the Great Recession than before.
+These results are different from other hedonic work such as \citet{Cho2011b} who found that environmental amenities in the Nashville, TN area mattered less during the Great Recession compared to before it.
 
@@
 Paul Metropolitan area in Minnesota as almost 3 million residents spread over seven counties.
-This study examines single family residential home transactions in the Census-defined urban areas of the three of the seven counties – Dakota, Ramsey and Washington County (see Figure 1).
+This study examines single family residential home transactions in the Census-defined urban areas of three of the seven counties – Dakota, Ramsey and Washington County (see Figure 1).
 We obtained data from approximately forty thousand sales transactions between 2005 and 2010 (n=42,095) from the 2010 MetroGIS Regional Parcel Dataset published by the Metropolitan Council.
 In addition to the geographic location and date of the house sale, we collected structural and locational variables commonly used in the hedonic literature.
-See Table 1 for a complete list of the explanatory variables and their descriptive statistics.
+
+\begin{figure}
+\includegraphics[width = \textwidth]{../graphs/StudyArea_SaleValueDistribution}
+\caption{This figure shows the spatial extent of our study area as well as the significant spatial variation in single family house sales prices.}
+\end{figure}
+
+\begin{table}
+\caption{Simple Correlation Matrix of Quantitative Variables}\label{tab:cor}
+\includegraphics[width = \textwidth]{../graphs/CorrelationMatrix}
+\end{table}
 
@@
 \subsection{Noise Data}
-Insert noise data description and methodology here.
+Insert noise data description and methodology here. \citet{Nega2012}
 
@@
 \subsection{Time}
-Given that we have data from before and after the recession of 2008-09, we subset the data in Table 2 by year of sale to look for differences.
+Given that we have data from before and after the recession of 2008-09, we subset the data in Table \ref{tab:SumStatsTime} by year of sale to look for differences.
 In addition to the noticeable decline in nominal sales values, there is also a drop in the number of sales across years.
@@
 However, traffic noise displays a noticeable difference in the pre- and post-crash market transactions (the mean drops from 58 dB to 52 dB).
+
+\begin{table}
+\caption{Mean Variable Values Across Time}\label{tab:SumStatsTime}
+\includegraphics[width = \textwidth]{../graphs/DescriptiveStatsByYear}
+\end{table}
 
@@
 We can interpret the regression model coefficients as the price semi-elasticities of the underlying attributes.
-For instance, we can interpret the coefficient on noise as the percentage increase in price for a one decibal increase in the traffic noise associated with the transaction in our dataset.
+For instance, we can interpret the coefficient on noise as the percentage increase in price for a one decibel increase in the traffic noise associated with the transaction in our dataset.
+
+\begin{table}
+\caption{Basic Regression Results- Dependent Variable = $ln$ Sale Price}\label{tab:globalRegression}
+
+\makebox[\textwidth][c]{\includegraphics[width = 1.3\textwidth]{../graphs/GlobalRegression}}
+\end{table}
 
@@
 As such, we add interaction terms between lot size and distance to the nearest central business district to account for spatial variation in the price of land.
-The first column in Table XXX shows the results of this regression.
+The first column in Table \ref{tab:globalRegression} shows the results of this regression.
 The negative coefficient of -0.0027 on the noise variable (a one dB increase in noise decreases house price by 0.27 percent) is in line with the estimates described earlier in the literature.
@@
 
-Table XXX also attempts to begin to understand how the economic recession may have influenced the hedonic function in our study area.
-The other columns in the table show the regression output from separating the data into sales before and after September of 2008 (the month that the US Federal government took over Fannie Mae and Freddi Mac, Lehman Brothers filed for bankruptcy, and the American International Group (AIG) narrowly avoided bankruptcy only through a \$85 billion loan from the US Federal government).
+Table \ref{tab:globalRegression} also attempts to begin to understand how the economic recession may have influenced the hedonic function in our study area.
+The other columns in the table show the regression output from separating the data into sales before and after September of 2008 (the month that the US Federal government took over Fannie Mae and Freddie Mac, Lehman Brothers filed for bankruptcy, and the American International Group (AIG) narrowly avoided bankruptcy only through a \$85 billion loan from the US Federal government).
 The coefficients for some of the hedonic variables of interest (noise, schools, land, for instance) appear different across the two time periods.
 
-Taken in aggregate, the results in Table XXX suggest that the hedonic price function may vary over space and time.
+Taken in aggregate, the results in Table \ref{tab:globalRegression} suggest that the hedonic price function may vary over space and time.
 While methods exist for parameterizing this variation (such as spatial expansion as suggested by \citet{Casetti1974}), we have no a priori knowledge of how to parameterize the variation over space and time.
@@
 Thus, the coefficient estimates at a particular house are estimated using data from other sales nearby in both time and geography.
-We also estimated the models using sales within the past 6 and 24 months.
 
-Figure XXX shows the relationship between the number of nearest neighbors receiving positive weights in the Locally Weighted Regression and the Generalized Cross Validation score.
+Figure \ref{fig:GCVmodel} shows the relationship between the number of nearest houses receiving positive weights in the Locally Weighted Regression and the Generalized Cross Validation score across three different models.
+The first model simply uses the basic structural characteristics as the explanatory variables (size of the house in square feet, size of the lot in acres, a categorical variable denoting the architectural style of the house, and whether or not the house is owner-occupied).
+The second model adds locational variables to the previously described model (test scores at the local elementary school, census tract median income, and distances to the central business district, nearest park, nearest shopping center, and nearest lake).
+The third model adds city fixed effects.
+Generally speaking, the third model performs slightly better than the second model, which performs better than the first model.
+The minimum GCV score is obtained using a bandwidth of 200 nearest houses and Model (3).
+\begin{figure}
+  \makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/GCVbyModel}}
+\caption{This figure shows the relationship between bandwidth size and the GCV score for three different Locally Weighted Regression (LWR) models.
+For comparison, the GCV scores for each model when estimated at a global scale are also shown.
+Note that the LWR models all have significantly smaller GCV scores than the global models.
+The minimum GCV score is obtained by LWR Model (3) at a bandwidth of 200 nearest houses.}\label{fig:GCVmodel}
+\end{figure}
 
-Regression output from the LWR model is voluminous in comparison to a standard regression model, as coefficients are estimated at each location within the dataset.
+Figure \ref{fig:GCVmodel} also displays the GCV scores for the three models estimated at the global scale.
+The GCV scores for the global models follow a similar patter as the LWR models, with Model (3) performing better than Model (2) and Model (1) having the highest GCV score.
+It is also worth noting that the LWR models have significantly lower GCV scores for a range of bandwidths when compared to the global models.
+These results suggest that it is important to model our data in a spatially explicit manner.
+
+Regression output from a LWR model is voluminous in comparison to a standard regression model, as coefficients are estimated at each location within the dataset.
 We report our results in a manner similar to \citet{MarmolejoDuarteCarlos;GonzalezTamez2009}.
-Table XXX displays the results of our prefered LWR model and a similar global regression model.
+Table \ref{tab:mainresults} displays the results of LWR Model 3 and the similar global regression model.
+Again, note that the LWR model yields a substantially smaller GCV score (0.027 vs.
+0.041).
 
-The first column in Table XXX displays the estimates from a standard semi-log OLS regression with traffice noise, structural characteristics, location-based amenities, and both city and year of sale dummy variables.
+% latex table generated in R 2.15.2 by xtable 1.7-0 package
+% Mon Jun 24 16:36:58 2013
+
+\begin{table}[ht]
+\caption{Hedonic Regression Results (dependent variable = $ln(\textrm{Sale Price})$)} \label{tab:mainresults} 
+\makebox[\linewidth]{
+\small
+\begin{tabular}{lrrrrrr} \\
+ & \multicolumn{2}{c}{Global Model} & \multicolumn{4}{c}{Locally Weighted Regression Model} \\
+ & \multicolumn{1}{c}{$\hat{\beta}$} & \multicolumn{1}{c}{$\hat{\sigma}_{\hat{\beta}}$} & mean $\hat{\beta}$ & \multicolumn{1}{c}{$\sigma_{\hat{\beta}}$} & (5) & (6) \\ 
+  \hline
+(Intercept) & 8.4E+00 & 1.3E-01 & 2.9E+00 & 1.5E+01 & 0.64 & 0.00 \\ 
+  Traffic Noise & -2.6E-03 & 1.6E-04 & -2.5E-03 & 3.0E-03 & 0.47 & 0.67 \\ 
+  House Size & 3.0E-04 & 2.7E-06 & 2.6E-04 & 9.1E-05 & 1.00 & 0.00 \\ 
+  Lot Size & 2.6E-01 & 1.5E-02 & 4.0E-01 & 3.7E-01 & 0.67 & 0.00 \\ 
+  Year of Construction & 1.2E-03 & 6.5E-05 & 4.5E-03 & 5.4E-03 & 0.79 & 0.00 \\ 
+  Owner Occupancy & 2.7E-02 & 3.2E-03 & 2.3E-02 & 6.4E-02 & 0.37 & 1.00 \\ 
+  Elementary Test Scores & 1.5E-03 & 1.2E-04 & 2.4E-04 & 3.1E-02 & 0.30 & 0.00 \\ 
+  Median Income & 3.3E-06 & 7.7E-08 & 9.6E-07 & 8.1E-06 & 0.35 & 0.00 \\ 
+  distance to CBD & 1.3E-05 & 6.3E-07 & 1.1E-05 & 1.0E-04 & 0.30 & 0.00 \\ 
+  `` nearest Park & -3.7E-07 & 1.1E-06 & -1.6E-05 & 1.3E-04 & 0.32 & 0.00 \\ 
+  `` nearest Lake & 2.5E-05 & 2.1E-06 & -2.8E-05 & 1.4E-04 & 0.35 & 0.00 \\ 
+  `` nearest Shopping Center & -5.3E-06 & 1.3E-06 & 1.5E-05 & 8.8E-05 & 0.29 & 0.00 \\  
+  location of sale & \multicolumn{2}{c}{city fixed effects} & \multicolumn{4}{c}{\footnotesize city fixed effects and nearest 200 sales} \\
+  timing of sale & \multicolumn{2}{c}{year fixed effects} & \multicolumn{4}{c}{within last 12 months} \\
+ \hline
+  GCV score & \multicolumn{2}{c}{0.041} & \multicolumn{2}{c}{0.027}  &  & \\
+  Moran's I statistic & \multicolumn{2}{c}{0.199} & \multicolumn{2}{c}{0.012} & & \\
+\end{tabular}
+}
+ \caption*{\small (5) displays the proportion of $\hat{\beta}_{LWR}$ that can reject the null hypthesis of $\beta =0$.\\ (6) displays the proportion of Monte Carlo simulations with larger standard deviations of the LWR coefficients than $\sigma_{\hat{\beta}}$}
+\end{table}
+
+The first column in Table \ref{tab:mainresults} displays the estimates from a standard semi-log OLS regression with traffice noise, structural characteristics, location-based amenities, and both city and year of sale dummy variables.
 The coefficient in the second row of the table shows the estimated impact of an additional dB of traffic noise on the natural log of the house sale price to be -.23 percent.
@@
 In this model coefficients are estimated at each observation within the dataset using the nearest 200 house sales within the past 12 months.
-The third column displays the standard deviation of the estimated coefficients to give a sense of how the coefficients vary when allowed to do so through the use of locally weighted regression techniques.
-The fourth column shows the percentage of the local regressions for which the coefficient's p-value is less than 0.1.
+The fourth column displays the standard deviation of the estimated coefficients to give a sense of how the coefficients vary when allowed to do so through the use of locally weighted regression techniques.
+
+Column (5) in Table \ref{tab:mainresults} shows the percentage of the local regressions for which the coefficient's p-value is less than 0.1.
 All regressions contained statistically significant estimates of the impact of increased living space, and a majority contained significant estimates for lot size and year of construction.
@@
 
+\subsection{Does Space Matter?}
 We believe the use of a LWR estimation procedure is appropriate after conducting two different Monte Carlo simulations with the data.
-In each simulation we resampled (with replacement) the location of each house in the study and then re-estimated the LWR model with the resampled data.
-In the first simulation we estimated the LWR model using bandwidths ranging from the nearest 50 to 10,000 sales.
+In each simulation we resampled (without replacement) the location of each house in the study and then re-estimated the LWR model with the resampled data.
+In the first simulation we estimated the LWR model using bandwidths ranging from the nearest 50 to 10,000 sales as before.
 In 100 consecutive simulations, the smallest Generalized Cross-Validation score was obtained at the largest bandwidth.
+The smallest of these GCV scores was 0.041, just as was the case with the global (non-LWR) model.
 In other words, the LWR model never performed better than the global model when the locations of the data were randomized.
@@
 \item Calculate the mean coefficient estimates as well as the standard deviation of the estimates from the sampled data LWR estimates.
-\item Repeat Steps 1-3 $M$ times. (we set $M = 100$)
-\item Compare the LWR coefficient means and standard deviations from the real data to the simulated values.
+\item Repeat Steps 1.--3. $M$ times.
 \end{enumerate}
-Of particular interest is the standard deviation of the LWR coefficients for a variable as compared to the distribution of simulated standard deviations.
-If the standard deviation of the actual LWR estimates is larger than the standard deviations from the simulations, this is interpretted as evidence of spatial non-stationarity in the coefficients.
+After 100 iterations of this simulation, the minimum GCV score for these resampled LWR models is 0.060, substantially larger than all models (global and local) with the actual data.
+Again, this seems to suggest that our data exhibit spatial non-stationarity in the regression coefficients.
+
+We are also interested in the standard deviation of our estimated LWR coefficients (the fourth column in Table \ref{tab:mainresults} as compared to the distribution of simulated standard deviations.
+If the standard deviation of the LWR estimates with the true data is larger than the standard deviations from the simulations, this is interpretted as evidence of spatial non-stationarity in the coefficients.
 The intuition is as follows.
@@
 Resampling the location of the data and estimating LWR models repeatedly will generate a distribution of how much the coefficients will vary across space due to chance.
-If the standard deviation of the LWR coefficients is larger than the standard deviations seen from the resampled data, this is consistent with the hypothesis that the coefficients vary over space more than they would due to random chance and noise within the data.
+However, if the standard deviation of the LWR coefficients is larger than the standard deviations seen from the resampled data, this is consistent with the hypothesis that the coefficients vary over space more than they would due to random chance and noise within the data.
 
-The results of the second Monte Carlo simulation are presented in columns 5 and 6 of Table XXX.
-Column 5 displays the standard deviation of the estimated coefficients from the LWR model estimated and presented in column 3.
-Column 6 displays the probability of obtaining a larger standard deviation of LWR coefficient estimates based on the 100 simulations performed.
-For most variables, we never obtained a larger coefficient standard deviation in the simulation than we obtained from the LWR model with the true data.
+The results of the second Monte Carlo simulation are presented in column (6) of Table \ref{tab:mainresults}.
+Column (6) displays the probability of obtaining a larger standard deviation of LWR coefficient estimates based on the 100 simulations performed.
+For most variables, we never obtained a larger coefficient standard deviation in the simulation than we obtained from the LWR model with the actual data.
 However, the values associated with the traffic noise and owner occupancy variables suggest that the variation in LWR coefficients in our data may have been due to random chance.
@@
 
+Figure \ref{fig:MCsds} visually shows the results presented in column (6) of Table \ref{tab:mainresults} another way.
+Each subfigure displays the distribution of LWR coefficient standard deviations obtained from the 100 iterations of the Monte Carlo simulation and the standard deviation obtained with the actual data (in red).
+Note that it is the case that the standard deviations obtained with the actual data are substantially larger than those obtained in the simulation for most of the variables.
+
 \begin{figure}
- \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{CopyOfMCsimResultsSDs}}
- \caption{The Monte Carlo Simulation Distribution of LWR Coefficient Standard Deviations and True Coefficient Standard Deviations.}
+ \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{../graphs/CopyOfMCsimResultsSDs}}
+ \caption{The Monte Carlo Simulation Distribution of LWR Coefficient Standard Deviations and True Coefficient Standard Deviations.}\label{fig:MCsds}
 \end{figure}
 
-In addition to the LWR model with a bandwidth of the nearest 200 houses and a temporal lag of 12 months performing better than other bandwidths and model specifications on in terms of the smallest GCV score, it also exhibits far less spatial autocorrelation within the model residuals.
+In addition to the LWR model with a bandwidth of the nearest 200 houses and a temporal lag of 12 months performing better than other bandwidths and model specifications in terms of the smallest GCV score, it also exhibits far less spatial autocorrelation within the model residuals.
 We calculate the Moran’s I statistic to be 0.199 for the global model while our prefered LWR specification reduces the Moran's I statistic to 0.012, a nearly twenty-fold reduction.
 
-Coefficients over time.
+\subsection{Do the Regression Coefficients Vary over Time}
+
+We know that house prices fell dramatically during and after the Great Recession of 2008-09.
+We know less about the patterns of change in the hedonic price functions during and after the fall in prices.
+For instance, did all house prices simply drop (mostly affecting the intercept term of the hedonic function), or did the implicit price of structural characteristics like the size of the house or its lot decrease, or perhaps the value of environmental amenities disproportionately dropped?
+This section presents some of the first evidence of how the hedonic price function for housing changed over time surrounding the Great Recession of 2008-09.
+We ask whether the LWR coefficients exhibit a temporal pattern.
+
+Specifically, we create two new variables, ``\texttt{months since September 2008}'' and a dummy variable ``\texttt{post}'' for all sales after September 2008.
+We then regress our LWR coefficients on these two variables and their interaction term as shown in equation \eqref{eq:LWRinteraction}.
+\begin{equation}\label{eq:LWRinteraction}
+\hat{\beta}_{LWR} = \alpha _0 + \alpha _1 \texttt{*month} + \alpha _2  \texttt{*post} + \alpha _3 \texttt{*post*month} + \epsilon
+\end{equation}
+
+The results of these regressions will help us understand the patterns of change in the hedonic price of different characteristics.
+In particular, significant values for $\hat{\alpha}_2$ suggest that there was a structural break in the LWR coefficients post September 2008, and significant values for $\hat{\alpha}_3$ will imply a difference in the temporal trend of the LWR coefficients.
+
+Note that the tables have not yet been formatted.
+
+\subsubsection{Traffic Noise}
+
+We know of no published research that shows how the hedonic price estimates of traffic noise vary over time surrounding the Great Recession.
+In this section we show that accounting for the month of the house sale significantly predicts to the estimated LWR coefficients for traffic noise.
+The linear regression results presented in Table \ref{tab:betaMAX} show that there is a significant negative shock to the estimated LWR coefficients for traffic noise after September 2008.
+Additionally, the coefficients also begin to a significant negative trend.
+\begin{table}[h]
+\caption{Regression Results: Dependent Variable = Traffic Noise LWR Coefficients}\label{tab:betaMAX}
+\begin{verbatim}
+(Intercept) -1.781e-03  4.100e-05 -43.436  < 2e-16 ***
+month        6.982e-06  2.005e-06   3.482 0.000498 ***
+Post        -7.998e-04  7.209e-05 -11.094  < 2e-16 ***
+month:Post  -8.868e-05  4.484e-06 -19.776  < 2e-16 ***
+---
+Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+
+Residual standard error: 0.002814 on 31744 degrees of freedom
+Multiple R-squared: 0.09289,  Adjusted R-squared: 0.09281 
+F-statistic:  1084 on 3 and 31744 DF,  p-value: < 2.2e-16 
+\end{verbatim}
+\end{table}
+
+The results in Table \ref{tab:betaMAX} contradict the a priori assumption that environmental amenities will ``matter'' less during and after the Great Recession.
+In fact, these results suggest that the penalty for homes exposed to higher levels of traffic noise increased.
+That is, the negative hedonic coefficients on traffic noise got more negative after September 2008.
+It should be noted that our model can explain almost 10 percent of the variation in traffic noise LWR coefficient estimates.
+
+\subsubsection{House Size}
+
+In this section we show how the hedonic coefficients on house size (as measured in square feet) change over time.
+Table \ref{tab:betaSQFT} shows that the LWR coefficients on house size were positive and trending up before September 2008, then the coefficients drop significantly in both absolute value and their time trend.
+These results are consistent with the belief that the Great Recession would reduce consumer's marginal willingness to pay for increases in the size of a house.
+It should be noted that the model presented in Table \ref{tab:betaSQFT} explains less than one percent of the variation in our house size LWR coefficients.
+
+\begin{table}[h]
+\caption{Regression Results: Dependent Variable = House Size LWR Coefficients}\label{tab:betaSQFT}
+\begin{verbatim}
+              Estimate Std. Error t value Pr(>|t|)    
+(Intercept)  2.741e-04  1.317e-06 208.097  < 2e-16 ***
+month        8.742e-07  6.441e-08  13.573  < 2e-16 ***
+Post        -1.678e-05  2.316e-06  -7.245 4.43e-13 ***
+month:Post  -5.989e-07  1.440e-07  -4.157 3.23e-05 ***
+---
+Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+
+Residual standard error: 9.04e-05 on 31744 degrees of freedom
+Multiple R-squared: 0.006092,  Adjusted R-squared: 0.005998 
+F-statistic: 64.85 on 3 and 31744 DF,  p-value: < 2.2e-16 
+\end{verbatim}
+\end{table}
+
+\subsubsection{Lot Size}
+
+Table \ref{tab:betaACRES} shows interesting results that are qualitatively different from our previous results.
+The post-September 2008 dummy variable coefficient is only marginally significant and small in absolute value (when compared to the regression Intercept term).
+There is no discernable change in the temporal trend of the lot size LWR coefficients.
+The model presented in Table \ref{tab:betaACRES} explains less than a half of one percent of the variation in lot size LWR coefficients.
+
+\begin{table}[h]
+\caption{Regression Results: Dependent Variable = Lot Size LWR Coefficients}\label{tab:betaACRES}
+\begin{verbatim}
+(Intercept)  0.3828690  0.0054089  70.785  < 2e-16 ***
+month       -0.0015113  0.0002645  -5.713 1.12e-08 ***
+Post         0.0190349  0.0095117   2.001   0.0454 *  
+month:Post  -0.0001358  0.0005916  -0.229   0.8185    
+---
+Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+
+Residual standard error: 0.3713 on 31744 degrees of freedom
+Multiple R-squared: 0.002806,  Adjusted R-squared: 0.002711 
+F-statistic: 29.77 on 3 and 31744 DF,  p-value: < 2.2e-16 
+\end{verbatim}
+\end{table}
+
+\subsubsection{Intercept}
+We were also interested in how the LWR regression intercept changed over time.
+For instance, perhaps the house price drops of the Great Recession were manifested primarily through reduced intercept terms.
+Table \ref{tab:betaINT} is not consistent with that hypothesis.
+In fact, our results show that the estimated LWR intercept terms are on average significantly higher post-September 2008.
+\begin{table}[h]
+\caption{Regression Results: Dependent Variable = LWR Intercept Estimates}\label{tab:betaINT}
+\begin{verbatim}
+(Intercept)  1.575488   0.213779   7.370 1.75e-13 ***
+month       -0.043836   0.010455  -4.193 2.76e-05 ***
+Post         2.845774   0.375939   7.570 3.84e-14 ***
+month:Post   0.007397   0.023383   0.316    0.752    
+---
+Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+
+Residual standard error: 14.67 on 31744 degrees of freedom
+Multiple R-squared: 0.003282,  Adjusted R-squared: 0.003188 
+F-statistic: 34.84 on 3 and 31744 DF,  p-value: < 2.2e-16  
+\end{verbatim}
+\end{table}
+
+\subsection{Does the Impact of Traffic Noise Vary Non-linearly?}
+
+Some researchers, such as \citet{Theebe2004a} conclude that the impact of traffic noise is non-linear in the level of the noise, while others, such as \citet{Huang;Palmquist2001} report a constant impact per decibel increase.
+In this section we compare the mean LWR noise coefficient estimates across noise levels to look for non-linearities in the impact of traffic noise.
+
+\begin{table}
+\caption{LWR Coefficients vs. Noise Levels}\label{tab:LWRnonlinear}
+\begin{verbatim}
+              Estimate Std. Error t value Pr(>|t|)    
+(Intercept) -1.748e-03  1.314e-04 -13.301   <2e-16 ***
+Noise       -2.760e-06  2.267e-06  -1.218    0.223    
+Post        -3.553e-03  2.198e-04 -16.165   <2e-16 ***
+Noise:Post   3.386e-05  4.006e-06   8.453   <2e-16 ***
+---
+Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+
+Residual standard error: 0.002829 on 31744 degrees of freedom
+Multiple R-squared: 0.08329,  Adjusted R-squared: 0.08321 
+F-statistic: 961.4 on 3 and 31744 DF,  p-value: < 2.2e-16 
+\end{verbatim}
+\end{table}
+
+Table \ref{tab:LWRnonlinear} estimates the predicted LWR noise coefficient as a linear function of the noise level in decibels and whether or not the sale took place before or after September 2008.
+The table reveals no statistically measurable linear relationship between the noise coefficient for sales before September 2008 and the level of the noise (that is, the marginal effect is no different at low levels of noise than at high levels of noise).
+The positive and significant interaction term suggests that the impact may be different for high vs.
+low levels of noise post-September 2008, but the difference in the predicted marginal effects is so small, that it works about to be a roughly \$25 difference for a \$300,000 house at 50 vs.
+75 dB.
+
+Figure \ref{fig:betaMAXvCat} visually displays the estimated relationship between the level of traffic noise, time, and the estimated LWR traffic noise coefficients.
+We categorize the traffic noise data in 5 dB wide bins like \citet{Theebe2004a} and then estimate the mean LWR traffic noise coefficients in each category while also controlling for whether the sales took place pre- or post-September 2008.
+We see little to suggest any meaningful non-linearities in the effect of traffic noise on house prices, once we have controlled for the timing of the sales.
+
+\begin{figure}
+\makebox[\textwidth][c]{\includegraphics[width = 1.1\textwidth]{../graphs/LWRbetaMAXbyCatTime}}
+\caption{The mean LWR traffic noise coefficient by 5 decibel category and pre- vs.
+post-September 2008.
+The vertical lines denote the standard error of the estimated mean by time and level category.
+Note that over 99 percent of our data have Noise levels between 35 and 80 dB and no houses were sold post-September 2008 with noise levels above 85 dB.}\label{fig:betaMAXvCat}
+\end{figure}
+
+\section{Discussion}
+
+Our work suffers from at least two noticeable weaknesses.
+First, we are missing some important structural variables that are commonly used in the real estate hedonic literature.
+To the extent that structural variables like the number of bedrooms, bathrooms, garage size, or construction quality covary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias.
+We are somewhat comforted, however, because we do have some additional variables for a subset of our data.
+We have the number of bedrooms, bathrooms, and garage area for our houses located within Dakota County.
+Our analysis (Models 1, 2, and 3 described earlier) was repeated on this geographic subset of the data and the results were compared to the estimates obtained from the same analysis when these additional structural variables were omitted.
+We found strikingly similar estimates of the impact of traffic noise.
+
+\begin{table}[ht]
+\begin{center}
+\caption{Mean and (Standard Deviation) LWR Noise Coefficients in Dakota County both with and without the additional structural variables available only for the county.}\label{tab:Dak}
+\begin{tabular}{lll}
+ & \multicolumn{2}{c}{Additional variables?} \\
+Locally Weighted Regression Model & \multicolumn{1}{c}{no} & \multicolumn{1}{c}{yes} \\ \hline
+Model (1) = Structural Variables & -0.00149 & -0.00147 \\ 
+   & (0.00226) & (0.00309) \\ 
+Model (2) = (1) + Locational Variables & -0.00136 & -0.00140 \\ 
+   & (0.00184) & (0.00218) \\ 
+Model (3) = (2) + City Fixed Effects & -0.00140 & -0.00137 \\ 
+   & (0.00219) & (0.00176) \\ 
+\end{tabular}
+\end{center}
+\end{table}
+
+Table \ref{tab:Dak} shows that the traffic noise coefficients estimated by our LWR models are similar regardless of whether the additional structural variables were included or not.
+Welch two-sample t-tests fail to reject the null hypothesis of zero means across our three models (comparing LWR estimates with vs.
+without the additional structural variables included in the model).
+Paired t-tests find differences for Model 2 and 3, but the estimated differences are zero to four decimal places and in one case the noise impact estimates with the additional variables are slightly larger and in the other case they are slightly smaller.
+We also conducted simple linear egressions of the noise coefficients without the additional structural variables on the noise coefficients obtained with the additional structural variables.
+In all three cases the intercept estimates were close zero with slopes almost exactly equal to one and each also had $R^2$ values over 0.7.
+
+The timing of our independent variable collection is also a potential problem.
+While our house sales data are collected over the course of six years, some of our other variables were collected at specific points in time and assumed to be constant over the study period.
+In particular, the traffic noise estimates taken from \citet{Nega2012} are for the year 2007.
+To the extent that traffic flows and composition signicantly changed over time, our traffic noise variables may be inaccurate for those time periods.
+For instance, the US Department of Transportation reports that total vehicle miles travelled decreased by up to 2 percent year-on-year during the Great Recession.
+Thus, our noise estimates may be inaccurate for later time periods and this may bias our estimates of the impact of noise on house values.
+Future work may better estimate the impact of traffic noise over time by generating noise data to reflect changing traffic patterns.
+
+What other weaknesses should we discuss?
+
+\section{Conclusion}
+
+We estimated the impact of traffic noise on housing prices using Locally Weighted Regression techniques in the St.
+Paul, MN metropolitan area.
+Specifically, we estimate linear regressions at each house within our dataset using only information contained in geographically nearby houses sold within the last 12 months.
+We find strong evidence that the hedonic function in our study area differs over space and time.
+Local regressions using only information contained in the nearest 200 houses generate a substantially smaller Generalized Cross Validation score (0.266) compared to the same model assuming geographical stationarity in the regression coefficients (0.401).
+
+Monte Carlo simulations suggest that the better goodness-of-fit provided by the local models are not due to chance and that many hedonic impact estimates vary over space within our study area.
+When the location of our data was randomly assigned and our LWR model was re-estimated, in 100 consecutive simulations the smallest GCV score was  obtained when the data were analyzed at a global level rather than local.
+Additionally, re-estimating the LWR model using a local bandwidth of 200 nearest house sales when the location was randomly assigned yielded substantially smaller standard deviations for the majority of our regression coefficients.
+This larger variation within our true data suggests spatial non-stationarity in the regression coefficients.
+That is, after trying thousands of different combinations of varying levels of local analysis with the spatially redistributed data, we never came close to estimating our observed housing sales prices as well as we can with the local analysis on the actual data.
+
+Contrary to the previous results presented by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} and \citet{Theebe2004a}, we find little evidence to suggest that the impact of traffic noise varies over space or by level of noise within our study area.
+The traffic noise coefficient was one of only two variables with regression coefficient standard deviations smaller than or similar to the simulated distributions obtained from Monte Carlo experiments.
+We do, however, find significant temporal variation in the impact of traffic noise in our data.
+The estimated impact of one additional decibel of traffic noise is a 0.19 percent reduction in the sale price of houses before September 2008, vs.
+0.37 percent after September 2008.
+Lastly, after controlling for the Great Recession, we find no significant differences in the impact of traffic noise across the range of commonly seen noise levels (50-70 dB).
 
@@
 \end{document}
+
+% \begin{table}
+% \caption{Data Description}\label{tab:descriptive}
+% \begin{tabular}{lp{3in}r}
+% Variable & Description  & Expected Hedonic Impact \\ \
+% 
+% Sale Price &   Price of most recent sale  (in \$) & \\
+% 
+% Home Size	& Area of finished space in the home (in square feet)	& (+) \\
+% Lot Size	& Area of land house sits on (in acres)	& (+) \\
+% Year Built & Year home was constructed &	(+) \\
+% Owner	Occupancy & Does the owner occupy the house? (0 or 1) &	(+) \\
+% 
+% Traffic Noise	& Maximum decibel level of traffic noise (dB) measured within parcel &	(-) \\
+% MCA 3  & Average 3rd grade Minnesota Comprehensive Assessment (MCA) score for local elementary school &	(+) \\
+% Median Income	& Median household income (in dollars) for 2010 Census tract &	(+) \\
+% Dist. to CBD &	Distance (in meters) to nearest central business district	& (-) \\
+% Dist. to shop &	Distance (in meters) to nearest major shopping center	& (+)/(-) \\
+% Dist. to lake &	Distance (in meters) to nearest public lake	& (-) \\
+% Dist. to park	& Distance (in meters) to nearest public park	& (-) \\
+% City &	City a parcel resides in	& (+)/(-) \\ \hline
+% \multicolumn{3}{l}{Total number of house sales between 2005 and 2010 (n = 42,095) }
+% \end{tabular}
+% \end{table}

### 2013-06-27 analysis/00DescriptiveStats/DescriptiveMaker.R
adding a script to make some descriptive stats tables

@@ -1,0 +1,4 @@
+
+
+# goal of this fle is to create some descriptive stats for the paper
+

### 2013-06-27 analysis/07TimeLagExploration/ModelTimeExplorer.R
added some shorter timelags to explore

@@ -19,10 +19,10 @@ dataSource = strsplit(inputFile, "\\.")[[1]][1]
 DATAFRAME = read.dbf(paste0(filePrefix, inputFile))
 N =  dim(DATAFRAME)[1]
 
-TIMELAGS = c(6, 12, 24)
+TIMELAGS = c(6, 12, 24, 9, 4)
 inputVARS = expand.grid(models = MYMODELS, lags = TIMELAGS)
 
-for (combo in 6:7) { #
+for (combo in 13:15) { #
   MYMODEL = as.character(inputVARS$models[combo])
   TIMELAG = inputVARS$lags[combo]
   obs2run = which(DATAFRAME$TimePeriod>(TIMELAG-1))

### 2013-06-27 reports/code/mainResultsTables.R
cleaned up the main results table

@@ -24,33 +24,42 @@ lm.global = lm(paste0(MYMODEL, "+factor(SALE_YR)"), data = DATAFRAME[obs2run, ])
 GlobalModel = summary(lm.global)
 global.leverages = lm.influence(lm.global, do.coef = FALSE)$hat
 
-GCV(leverages = matrix(global.leverages, ncol = 1), 
-    yhats = matrix(lm.global$fitted.values, ncol = 1), 
-    dep.var = DATAFRAME$logSALE_VA[obs2run])
-
 vars = c("(Intercept)", "MAX", "FIN_SQ_FT", "ACRES_POLY", "YEAR_BUILT", "OWNOCC", 
          "MCA3", "MED_INCOME", "CBD_dist", "PARK_dist", "LAKE_dist", "SHOP_dist" )
 
-LWRtable = matrix(NA, length(vars), 6)
-rownames(LWRtable) = vars
-LWRtable[, 1:2] = signif(GlobalModel$coefficients[vars , 1:2], 2)
+numvars = length(vars)
+LWRtable = matrix(NA, numvars+2, 6)
+rownames(LWRtable) = c("(Intercept)", "Traffic Noise", "House Size", "Lot Size", "Year of Construction", 
+                       "Owner Occupancy", "Elementary Test Scores", "Median Income", 
+                       "distance to CBD", "distance to nearest Park", "distance to nearest Lake", 
+                       "dist. to nearest Shopping Center", "GCV score")
+LWRtable[1:numvars, 1:2] = signif(GlobalModel$coefficients[vars , 1:2], 2)
+
+LWRtable[numvars + 1, 1] = GCV(leverages = matrix(global.leverages, ncol = 1), 
+                               yhats = matrix(lm.global$fitted.values, ncol = 1), 
+                               dep.var = DATAFRAME$logSALE_VA[obs2run])
+
+LWRtable[numvars + 1, 3] = min(GCV(output$leverages, output$yhats, DATAFRAME$logSALE_VA[obs2run]))
+
+LWRtable[numvars + 2, 1] = signif(GlobalModel$r.squared, 2)
+
 
 # populate the rest of the table
-for (i in 1:length(vars)) {
+for (i in 1:numvars) {
   # put the mean and sd of LWR beta hats in the table
   LWRtable[i, 3] = signif(mean(output[[paste0("beta.", vars[i])]][, "k200"], na.rm = T), 2)
[…]

### 2013-06-27 reports/Draft.Rnw

@@
 \title{A Hedonic Price Analysis of Traffic Noise in the Twin Cities Housing Market}
-\date{}
+\date{\today}
 
@@
 \begin{abstract}
-This paper implements the hedonic price method to estimate the impact of traffic noise on properties within the St.
-Paul, Minnesota metropolitan real-estate market over the time period from 2005 - 2010.
+This paper implements the hedonic price method to estimate the impact of traffic noise on properties within the St.\ Paul, Minnesota metropolitan real-estate market over the time period from 2005 - 2010.
 We use Locally Weighted Regression (LWR) estimation techniques in order to allow the hedonic function to vary over time and space.
 Significant evidence suggests spatial and temporal non-stationarity in the hedonic price function within our study area.
-In contrast to previous research, we find little evidence that the impact of traffic noise exhibits a significant non-linear relationship with the decibel level of the traffic noise, nor does the impact seem to vary over space.
+In contrast to previous research, however, we find little evidence that the impact of traffic noise exhibits a significant non-linear relationship with the decibel level of the traffic noise, nor does the impact seem to vary over space.
+We find significant differences in the impact of traffic noise from the beginning to the end of our sample.
 Our results suggest that an increase in traffic noise of one decibel decreases house prices by an average of 0.19 percent before September, 2008, and an average of 0.37 percent after September, 2008.
-Both of these estimates are within the range estimated by previous research on the topic in other areas.
+While significantly different, both of these estimates are still within the typical range of previous estimates in the literature.
 \end{abstract}
@@
 The value of noise pollution is typically estimated through simulated or related markets because no explicit private market for noise abatement exists.
-\citet{Nelson1982} is perhaps the best known earliest review of 14 studies of the economic impact of traffic noise on property values in Canada and the United States.
+\citet{Nelson1982} is perhaps the best known earliest review of 14 housing market studies of the economic impact of traffic noise on property values in Canada and the United States.
 More recently, a number of reviews have been produced for European government agencies.
@@
 \citet{Nelson2008} produced an updated review of the traffic noise literature for the edited volume \underline{Hedonic Methods in Housing Markets Economics}.
-The chapter describes several areas of continued interest in the empirical literature, most notably: the appropriate measure of traffic noise, spatial modeling of the hedonic price function, and housing market dynamics.
-We now explain each of these areas in turn and our work's contribution to the field.
+The chapter describes several areas of continued interest in the empirical literature, most notably: the measure of traffic noise, spatial modeling of the hedonic price function, and housing market dynamics.
 
 \subsection{Measure of Traffic Noise}
-
-Beyond the fact that no direct natural economic markets exist in which consumers can reveal their willingness to pay to avoid traffic noise, researchers also must choose how to measure the nuisance itself.
-Sound levels are commonly measured in decibels (dB), but traffic noise at a house can vary significantly depending on changing traffic conditions.
-
-Some researchers (see, for instance, \citet{HughesJr.1992}) measure the negative externality of traffic by correlating traffic volume with house prices.
-However, traffic may generate other externalities beyond noise (such as local air pollution and reduced safety for pedestrians and drivers).
-Given the interest in government policymakers in traffic noise mitigation (cite some data here), we focus on the negative externality stemming specifically from the traffic noise itself.
-Additionally, until 2011, the Minnesota Department of Transportation used a cost effectiveness threshold for noise mitigation of \$3,250 per dB reduced.
-Given that some of the benefits of noise reductions are capitalized in house prices, we are curious to see how our estimated magnitudes compare to the state cost effectiveness cutoff.
-
 I'm going to need some help writing about noise measures. Perhaps Tsegaye can lend a hand?
 
-\citet{Huang;Palmquist2001} collect noise data using 128 monitoring stations throughout a suburb of Seattle, WA.
-They use dBA $L_{10}$ as their noise measure, where $L_{10}$ denotes the value that is exceeded 10 percent of the time.
-They collapse the noise readings into 2.5 dBA wide bins and report noise impact estimates of roughly 1.4\% decrease in house sales price per category increase in noise (or about 0.4\% per dBA $L_{10}$).
+Noise data is typically not collected for each every house in a hedonic study.
+For example, \citet{Huang;Palmquist2001} collect noise data using 128 monitoring stations throughout a suburb of Seattle, WA.
+Such a strategy forces the researchers to interpolate the data between the monitoring stations in order to associate each house with a noise level.
+While the researchers do not describe how the interpolation was done, they implicitly admit the potential uncertainty of the method by categorizing traffic noise exposure into 2.5 dB wide categories.
+Other researchers, such as \citet{Theebe2004a} use 5 dB wide bins, and \citet{Nelson2008} even claims that some studies use bins as wide as 10 dB.
+Such coarse measurements can lead to serious errors in variables and imprecise estimates of the impact of noise.
+
+Other researchers obtain noise levels from external sources without much description of the variable source.
+For instance, \cite{MarmolejoDuarteCarlos;GonzalezTamez2009} simply list a ``City Council Sonic Map'',  \citet{Blanco2011} cite the Department for Environment Food and Rural Affairs Noise mapping England project.
+\citet{Andersson2010} state, ``Information about noise levels is from a study on the health effects of traffic noise conducted in Lerum [Sweden] in 2004 (Ohrstrom et al.
+2005).
+Separate noise calculations were made for railway and road noise for all the houses in Lerum.''
+
+Traffic noise at a location can vary significantly depending on changing traffic conditions.
+Such variation has led to multiple measures of noise.
+Some measures eliminate the fluctuations in sound and instead represent the equivalent continuous constant sound pressure at a site.
+Other indices use noise values that are only exceeded a given percentage of time.
+For instance, \citet{Huang;Palmquist2001} use dB $L_{10}$ as their noise measure, where $L_{10}$ denotes the value that is exceeded only 10 percent of the time.
+Still others adjust nighttime noise exposure levels to account for potential increased perceived nuisance.
+\citet{Baranzini2010} even surveyed inhabitants about their perceptions of the level of noise and their annoyance.
+The work finds similar results for significant levels of measured noise as compared subjective measures of noise.
+
+\emph{What do we have?
+There is still a lot of work to be done in this area, better understanding the measures others use as well as what we have and how they compare.
+I'm surprised at how little information people actually provide about their noise data.}
+
+Spatial resolution of the data. \citet{Theebe2004a} had noise levels for square areas of 100 x 100m.
+
+% Beyond the fact that no direct natural economic markets exist in which consumers can reveal their willingness to pay to avoid traffic noise, researchers also must choose how to measure the nuisance itself.
+Some researchers (see, for instance, \citet{HughesJr.1992}, \citet{Li2012} \citet{Larsen2012}) attempt to measure the negative externality of traffic by correlating traffic volume with house prices.
+However, traffic may generate other externalities beyond noise (such as local air pollution and reduced safety for pedestrians and drivers) and so these strategies overestimate the size of the noise externality.
+% 
+% The value of traffic noise is important in and of itself.
+Governments routinely erect noise barriers to shield residential areas from traffic noise.
+(cite some numbers here!).
+To aid such work, it is important to understand the benefits of these policies.
+For instance, until 2011, the Minnesota Department of Transportation used a cost effectiveness threshold for noise mitigation projects of \$3,250 per dB reduced per house.
+Given that some of the benefits of noise reductions are capitalized in house prices, we are curious to see how our estimated magnitudes compare to the state cost effectiveness cutoff.
 
@@
 In particular, spatially autocorrelated error terms will lead to inconsistent estimates of OLS regression standard errors and inappropriate measures of statistical inference.
+
+It is now common to use spatial econometric techniques in the hedonic literature, for instance estimating a spatial lag (in which house prices are modeled as a function of neighboring house prices), or a spatial error model (in which the degree of spatial autocorrelation is also estimated).
+In the noise literature, for example, \citet{Theebe2004a} econometrically estimates a spatial error model, while \citet{Andersson2010} uses a spatial lag model.
 
@@
 
-How do people do submarkets? 
-\begin{itemize}
-  \item Geography 
-    \begin{itemize}
-      \item census tracts
-    \end{itemize}
-  \item Political Boundaries
-    \begin{itemize}
-      \item city boundaries
-    \end{itemize}
-  \item Other (Data Mining)
-\end{itemize}
+Some traffic noise research simply explicitly assumes that their data comprise a single market.
+For example, \citet{Kim2007} assumes that by restricting analysis to residential properties surrounding the Inner Circular highway in the central area of Seoul from 2002 to 2004, that the price of traffic noise will be constant.
+Other research, such as \citet{Theebe2004a} used political boundaries to segment the market into five separate subarkets in the western part of the Netherlands.
 
-\citet{Theebe2004a} econometrically estimates a spatial error model
-
-Researchers such as , and \citet{Andersson2010} attempt to correct for spatial autocorrelation through the use of spatial
-
-Day (2003) investigated the impact of traffic noise in Glasgow, Scotland and found four separate submarkets with varying relationships between noise and prices.
-Interestingly, traffic noise coefficients were estimated to be negative in three out of four submarkets, while the fourth revealed a significantly positive relationship.
-The positive relationship is hypothesized to be related to increased transportation access and mobility in an outer suburb of the city.
-In a similar study, Day et.
-al (2007) found traffic noise estimates to be significantly negative in five of eight submarkets using appriximately 10 thousand residential sales in 1997 in Birmingham, England.
-
-Most researchers who allow the hedonic function to vary over geography do so through explicit parameterization done by the researchers (usually using political boundaries).
-
-Theebe (2004) also used market segmentation to estimate more than 160,000 property sale values in the western part of the Netherlands sold between 1997 and 1999.
-First, the data were split into five parts according to political jurisdictions.
-Through spatial autoregression techniques, Theebe’s results indicated that sales values are unaffected by noise levels below 65 dB.
-Above 65 dB, NDSI is relatively small, ranging from 0.3 to 0.5\% per dB.
-An analysis of submarket data yielded larger results although these findings are less precise.
-While Theebe covered a large study area, the noise levels are obtained for square areas of 100 x 100m using the cumulative 24 hours energy level index Leq.
-This study uses a Leq index at a square area of 10 x 10m, therefore each property has a unique and continuous noise decibel measurement.
-Consequentially, the analysis on smaller submarket samples will be relatively more precise in terms of traffic noise estimates than Theebe (2004).
-
-While Day (2003) and Theebe (2004) considered the existence of submarkets through market segmentation and used estimators that accounted for spatial autocorrelation, these segmentations are limited by space.
-By defining clear boundaries of submarkets, Duarte et.
-al (2009) noted that this clear delimitation does not allow interdependence between submarkets to be considered.
-Through locally weighted regression (LWR), the authors resolved the issue of spatial autocorrelation and considered the existence of submarkets while providing a ‘soft’ border between localities.
-By examining 3,196 appraisals of multifamily dwellings assessed in 2005 in Barcelona, Spain, Duarte et.
-al investigated a range of neighborhood and environmental attributes.
-A Monte Carlo test statistically validated the spatial variation of local factors.
-The results from the LWR indicate that the average NDSI for observations located in the 65-70 dB is negative  while average NDSI for observations exposed to 70-75 dB is 0.26\%.
-Finally, dwellings exposed to higher levels of noise (75-80 dB) have an average -0.40\% NDSI.
-The authors explained this paradox by considering areas with intermediate levels of noise have closer access to services and transport within the city without experiencing an extreme noise externality.
-In this study, a similar implementation of locally weighted regression is utilized in order to resolve for spatial autocorrelation while allowing for interdependency across submarkets.
-Furthermore, two Monte Carlo tests are utilized to statistically support (1) the use of a non-global model and (2) the spatial variation of estimated parameters.
+Another strategy is to let the data reveal different relationships within smaller areas of the study.
+For instance, \citet{Day2007} and \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} use semi-parametric techniques to allow the hedonic relationship to smoothly vary over space.
+We use techniques similar to the Geographically Weighted Regression method described in \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} to allow the hedonic function to vary over space without having a priori conceptions of where the function will be different.
 
 \subsection{Temporal Variation}
-A common strategy is to analyze cross-sectional data.
-However, housing transactions take place at a specific point in time and the vast majority of data sets will contain some temporal variation in house sales.
-Some researchers may simply assume the hedonic function is constant thoughout their timespan.
-Others allow the function to shift up or down through the use of temporally varying intercept terms.
+Little work has been done estimating the changes in hedonic environmental (dis)amenities like noise over time.
+An event-study literature exists using temporal variation in noise, especially noise from airports (see, for example, \citet{Cohen2009}, ).
+However, these articles usually use the change in noise over time to identify the hedonic price of noise, rather than ask whether the hedonic price has changed.
 
-Few researchers allow the hedonic function to change over time.
-\citet{Cho2011b} is a recent example of work allowing the hedonic regression coefficients to change over time, thereby estimating the changes in the implicit prices of hedonic characteristics over time.
-
-\citet{Wilhelmsson2000} split his 290 Swedish house sales into two separate time periods: 1986-89 and 1990-95.
+\citet{Wilhelmsson2000} is one example of research asking whether the implicit price of noise has changed over time.
+The study splits the 290 Swedish house sales into two separate time periods: 1986-89 and 1990-95.
 A Chow test revealed that the impact of traffic noise was different in the earlier vs.
@@
 
+\citet{Cho2011b} is a recent example of work asking whether the hedonic regression coefficients change over time in the Nashville, TN area.
+In particular, the study uses a repeat sales methodology to estimate changes in the implicit prices of hedonic characteristics as a result of the Great Recession of 2008-09 in the United States.
+The work finds that environmental amenities matter less in sales during the year 2008 when compared to pre-recession sales.
+
 We estimate regression coefficients over time using a moving window of 12 months in the hedonic analysis over the years 2005 - 2010.
-Such an analysis allows us to see if and when the implicit price of traffic noises changes within our study area.
+Such an analysis allows us to see if and when the implicit price of traffic noise changes within our study timeframe.
 Our results suggest that the percentage change in house price from an extra decibel of traffic noise actually became more negative after the Great Recession than before.
-These results are different from other hedonic work such as \citet{Cho2011b} who found that environmental amenities in the Nashville, TN area mattered less during the Great Recession compared to before it.
+
+Our work makes three contributions to the field.
+First, we utilize new estimates of traffic noise that has never before been used in the hedonic literature.
+The data explicitly model noise propagation as a function of nearby buildings and landcover, as well as present the results at a fine spatial resolution (10m x 10m).
+Such estimates, combined with sptially explicit modeling techniques allow us to make our second contribution to the literature.
+We present one of the first estimates of how the impact of traffic noiseeee varies over space.
+We find that while the impact of other important control variables in the hedonic function vary over space, the impact of traffic noise does not.
+Lastly, we present the first estimates of how the Great Recession has affected the hedonic price of traffic noise.
 
@@
 Standard urban economic theory\footnote{Cite Muth, Mills, etc.
-here.} predicts that the price of land will vary over space within our dataset to account for locational ameinities.
+here.} predicts that the price of land will vary over space within our dataset to account for locational amenities.
 As such, we add interaction terms between lot size and distance to the nearest central business district to account for spatial variation in the price of land.
@@
 
+We didn't explicitly model spatial autocorrelation in the error terms.
+
+We might want to further reduce the number of parameters to estimate through the use of either mixed-LWR or running separate regressions for submarkets determined through hierarchical clustering like \citet{Day2003}.
+
 \section{Conclusion}
 
-We estimated the impact of traffic noise on housing prices using Locally Weighted Regression techniques in the St.
-Paul, MN metropolitan area.
+We estimated the impact of traffic noise on housing prices using Locally Weighted Regression techniques in the St.\ Paul, MN metropolitan area.
 Specifically, we estimate linear regressions at each house within our dataset using only information contained in geographically nearby houses sold within the last 12 months.

### 2013-06-27 analysis/00DescriptiveStats/DescriptiveMaker.R
started the DescriptiveMaker file to make a table of descriptive stats

@@ -1,4 +1,35 @@
 
 
-# goal of this fle is to create some descriptive stats for the paper
+# goal of this file is to create some descriptive stats for the paper
+
+require(foreign)
+DATAFRAME = read.dbf("~/NoiseHedonicProject/Data/R2GIS/CleanData/Sales20052010.dbf")
+
+myvars = c("SALE_VALUE", "FIN_SQ_FT", "ACRES_POLY", "OWNOCC", "YEAR_BUILT", "MAX", "MED_INCOME", "MCA3",
+           "CBD_dist", "PARK_dist", "LAKE_dist", "SHOP_dist")
+
+sumStats = matrix(NA, length(myvars), 7)
+
+for (i in 1:length(myvars)) {
+  sumStats[i, 1:6] = summary(DATAFRAME[ , myvars[i]])  
+  sumStats[i, 7] = sd(DATAFRAME[ , myvars[i]])
+}
+
+
+                
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
 

### 2013-06-27 reports/Draft.Rnw

@@
 In addition to the geographic location and date of the house sale, we collected structural and locational variables commonly used in the hedonic literature.
+Table \ref{tab:sumStats} provides a brief description of the variables and some basic summary statistics.
+Figure \ref{fig:overview} shows an overview of the study area as well as the spatial distribution of the house sales prices.
+Table \ref{tab:cor} shows a simple correlation matrix of the quantitative variables.
 
@@
 \includegraphics[width = \textwidth]{../graphs/StudyArea_SaleValueDistribution}
-\caption{This figure shows the spatial extent of our study area as well as the significant spatial variation in single family house sales prices.}
+\caption{This figure shows the spatial extent of our study area as well as the significant spatial variation in single family house sales prices.}\label{fig:overview}
 \end{figure}
+
+\begin{table}[htb]
+\caption{Variable Description and Summary Statistics}\label{tab:sumStats}
+\makebox[\linewidth][c]{
+\small
+\begin{tabular}{lrrrrrrr}
+
+ & min & 25\% & 50\% & mean & 75\% & max & $\sigma$ \\ 
+  \hline
+  Sale Price (thousands \$) & 98.8 & 195.0 & 241.0 & 265.5 & 314.9 & 675.0 & 102.8 \\ 
+  House Size (thousands square feet) & 390 & 1158 & 1628 & 1750 & 2188 & 4000 & 704 \\ 
+  Lot Size (acres) & 0.02 & 0.17 & 0.25 & 0.25 & 0.31 & 0.60 & 0.11 \\ 
+  Owner Occupancy Dummy & 0.0 & 1.0 & 1.0 & 0.8 & 1.0 & 1.0 & 0.4 \\ 
+  Year House was Built & 1850 & 1950 & 1973 & 1967 & 1993 & 2010 & 32 \\ 
+  Traffic Noise (dB) & 25.1 & 50.5 & 55.3 & 56.4 & 62.2 & 91.5 & 8.8 \\ 
+  Median Income in Census Tract (thousands \$) & 13.9 & 54.6 & 69.1 & 72.6 & 89.7 & 143.3 & 23.6 \\ 
+  Elementary Test Scores & 335.6 & 359.8 & 365.4 & 364.5 & 370.4 & 551.7 & 10.6 \\ 
+  Distance to Central Business District (km) & 1.1 & 6.8 & 13.2 & 14.7 & 21.8 & 37.1 & 8.9 \\ 
+  Distance to nearest Park (km) & 0.0 & 1.1 & 2.2 & 2.6 & 3.8 & 9.7 & 1.9 \\ 
+  Distance to nearest Lake (km) & 0.0 & 0.4 & 0.8 & 0.9 & 1.3 & 4.4 & 0.7 \\ 
+  Distance to nearest Shopping Center (km) & 0.0 & 0.9 & 1.5 & 1.9 & 2.3 & 10.8 & 1.6 \\ 
+   \hline
+\end{tabular}
+}
+\end{table}
 
@@
 
-\begin{table}[ht]
+\begin{table}[bp]
 \caption{Hedonic Regression Results (dependent variable = $ln(\textrm{Sale Price})$)} \label{tab:mainresults} 

### 2013-06-27 analysis/00DescriptiveStats/DescriptiveMaker.R
updated the DescriptiveMaker file

@@ -5,8 +5,13 @@
 require(foreign)
 DATAFRAME = read.dbf("~/NoiseHedonicProject/Data/R2GIS/CleanData/Sales20052010.dbf")
 
-myvars = c("SALE_VALUE", "FIN_SQ_FT", "ACRES_POLY", "OWNOCC", "YEAR_BUILT", "MAX", "MED_INCOME", "MCA3",
-           "CBD_dist", "PARK_dist", "LAKE_dist", "SHOP_dist")
+myvars = c("SALE_VALUE", "FIN_SQ_FT", "ACRES_POLY", "OWNOCC", "YEAR_BUILT", "MAX", 
+           "MED_INCOME", "MCA3", "CBD_dist", "PARK_dist", "LAKE_dist", "SHOP_dist")
+
+mynames = c("Sale Price (thousands)", "House Size (thousands square feet)", "Lot Size (acres)", "Owner Occupancy Dummy",
+            "Year House was Built", "Traffic Noise (dB)", "Median Income in Census Tract (thousands)", 
+            "Elementary Test Scores", "Distance to Central Business District (km)",
+            "Distance to nearest Park (km)", "Distance to nearest Lake (km)", "Distance to nearest Shopping Center (km)")
 
 sumStats = matrix(NA, length(myvars), 7)
 
@@ -15,8 +20,18 @@ for (i in 1:length(myvars)) {
   sumStats[i, 7] = sd(DATAFRAME[ , myvars[i]])
 }
 
+sumStats
 
-                
+sumStats = sumStats/c(1000, 1, 1, 1, 1, 1, 
+                      1000, 1, 1000, 1000, 1000, 1000)
+
+rownames(sumStats) = mynames
+
+
+mydig = matrix(rep(c(1, 0, 2, 1, 0, 1, 1, 1, 1, 1, 1, 1), 8), length(myvars), 8)
+
+require(xtable)
+xtable(sumStats, digits = mydig)
 
 
 

### 2013-08-27 reports/Draft.Rnw
started revamping draft for Journal of Regional Science

@@
 \section{Introduction and Past Research}\label{sec:lit}
-The value of noise pollution is typically estimated through simulated or related markets because no explicit private market for noise abatement exists.
-\citet{Nelson1982} is perhaps the best known earliest review of 14 housing market studies of the economic impact of traffic noise on property values in Canada and the United States.
-More recently, a number of reviews have been produced for European government agencies.
-\citet{Bateman2001} reviewed the literature for the Scottish Government while \citet{Navrud2002} provided a ``state of the art'' review for the European Commission Environment Directorate General.
+Prolonged exposure to traffic noise affects people in a number of ways, ranging from simple annoyance (Miedema and Oudshoorn 2001; Ouis 2001), to sleep disturbance (Netherlands 2004), to increasing risk for stroke (Sorensen, Hvidberg et al.
+2011), hypertension(Jarup, Babishch et al.
+2008; Bodin, Albin et al.
+2009), and myocardial infarction (Babisch, Beule et al.
+2005).
+The noise level at which such effects are observed does not have to be high.
+It has been shown that people exposed to traffic noise with a 24-hour average of 55 dBA are found to be at a higher risk for hypertension (Barregard, Bonde et al.
+2009; Bodin, Albin et al.
+2009), and those exposed to 60 dBA or greater are found to be at a higher risk for stroke (Sorensen, Hvidberg et al.
+2011).
+This impact is expected to grow worse with the increasing number of vehicles in the urban road network and the diminishing number of night-time quiet hours unless mitigating measures are put in place (XXX).
+Given that much of this increased exposure occurs in areas where people live and work any mitigating measures must be based on a cost-benefit analysis.
 
-The Hedonic Price Method is commonly used to value noise by examining real estate price fluctuations as a function of noise levels.
-Based on the canonical work by \citet{Rosen1974}, researchers typically estimate a hedonic price function specifying the logged sale price of a property as a linear function of the traffic noise exhibited at the house.
-Such a specification leads to reporting the impact of traffic noise as a percentage decrease in house price per one decibel (dB) increase in traffic noise.
-According to \citet{Bateman2001}, the negative effect of traffic noise has ranged from 0.08\% to 2.22\% per dB with a mean around 0.55\% per dB.
-In a review of 65 noise evaluation studies \citet{Navrud2002} found an average decrease of 0.64\% per dB.
+An important first step towards such an analysis is to examine real estate price fluctuations as a function of noise levels using hedonic regression.
+Such work has provided important insight on the nature of this relationship.
+Thus, Bateman et al.
+(2001) found that the negative eﬀect of traﬃc noise ranged from 0.08\% to 2.22\% per dB with a mean around 0.55\% per dB.
+In a review of 65 noise evaluation studies Navrud (2002) found an average decrease of 0.64\% per dB.
+\textbf{We need to briefly review other relevant papers here.}  However, with the exception of a few studies that have focused on air traffic noise exposure (we should check on this), the relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).
+One major reason for the thinness of the scholarly literature on this topic in the US lies in the difficulty of modeling noise propagation over the landscape.
 
-\citet{Nelson2008} produced an updated review of the traffic noise literature for the edited volume \underline{Hedonic Methods in Housing Markets Economics}.
-The chapter describes several areas of continued interest in the empirical literature, most notably: the measure of traffic noise, spatial modeling of the hedonic price function, and housing market dynamics.
+To properly analyze the spatial association between real estate prices and exposure to traffic noise at a landscape level, it is necessary to create a noise surface map at sufficiently detailed spatial resolution to account for the complex and heterogeneous interaction between the noise source and the resistance of the landscape to noise propagation.
+Implementing such a model can be very difficult.
+For one thing, the data needed for the model is very extensive and may not even be readily available (e.g., building footprint and height data).
+Furthermore, it is computationally very intensive.
+Fortunately, recent developments in Geographic Information Systems and distributive computing have reduced these difficulties, making it much easier to create a noise surface map at landscape level.
 
-\subsection{Measure of Traffic Noise}
-I'm going to need some help writing about noise measures. Perhaps Tsegaye can lend a hand?
-
-Noise data is typically not collected for each every house in a hedonic study.
-For example, \citet{Huang;Palmquist2001} collect noise data using 128 monitoring stations throughout a suburb of Seattle, WA.
-Such a strategy forces the researchers to interpolate the data between the monitoring stations in order to associate each house with a noise level.
-While the researchers do not describe how the interpolation was done, they implicitly admit the potential uncertainty of the method by categorizing traffic noise exposure into 2.5 dB wide categories.
-Other researchers, such as \citet{Theebe2004a} use 5 dB wide bins, and \citet{Nelson2008} even claims that some studies use bins as wide as 10 dB.
-Such coarse measurements can lead to serious errors in variables and imprecise estimates of the impact of noise.
-
-Other researchers obtain noise levels from external sources without much description of the variable source.
-For instance, \cite{MarmolejoDuarteCarlos;GonzalezTamez2009} simply list a ``City Council Sonic Map'',  \citet{Blanco2011} cite the Department for Environment Food and Rural Affairs Noise mapping England project.
-\citet{Andersson2010} state, ``Information about noise levels is from a study on the health effects of traffic noise conducted in Lerum [Sweden] in 2004 (Ohrstrom et al.
-2005).
-Separate noise calculations were made for railway and road noise for all the houses in Lerum.''
-
-Traffic noise at a location can vary significantly depending on changing traffic conditions.
-Such variation has led to multiple measures of noise.
-Some measures eliminate the fluctuations in sound and instead represent the equivalent continuous constant sound pressure at a site.
-Other indices use noise values that are only exceeded a given percentage of time.
-For instance, \citet{Huang;Palmquist2001} use dB $L_{10}$ as their noise measure, where $L_{10}$ denotes the value that is exceeded only 10 percent of the time.
-Still others adjust nighttime noise exposure levels to account for potential increased perceived nuisance.
-\citet{Baranzini2010} even surveyed inhabitants about their perceptions of the level of noise and their annoyance.
-The work finds similar results for significant levels of measured noise as compared subjective measures of noise.
-
-\emph{What do we have?
-There is still a lot of work to be done in this area, better understanding the measures others use as well as what we have and how they compare.
-I'm surprised at how little information people actually provide about their noise data.}
-
-Spatial resolution of the data. \citet{Theebe2004a} had noise levels for square areas of 100 x 100m.
-
-% Beyond the fact that no direct natural economic markets exist in which consumers can reveal their willingness to pay to avoid traffic noise, researchers also must choose how to measure the nuisance itself.
-Some researchers (see, for instance, \citet{HughesJr.1992}, \citet{Li2012} \citet{Larsen2012}) attempt to measure the negative externality of traffic by correlating traffic volume with house prices.
-However, traffic may generate other externalities beyond noise (such as local air pollution and reduced safety for pedestrians and drivers) and so these strategies overestimate the size of the noise externality.
-% 
-% The value of traffic noise is important in and of itself.
-Governments routinely erect noise barriers to shield residential areas from traffic noise.
-(cite some numbers here!).
-To aid such work, it is important to understand the benefits of these policies.
-For instance, until 2011, the Minnesota Department of Transportation used a cost effectiveness threshold for noise mitigation projects of \$3,250 per dB reduced per house.
-Given that some of the benefits of noise reductions are capitalized in house prices, we are curious to see how our estimated magnitudes compare to the state cost effectiveness cutoff.
-
-\subsection{Spatial Analysis}
-Advances in Geographic Information System (GIS) technology and digitized datasets have made research easier to conduct over larger geographies, with larger samples, and while explicitly considering the spatial nature of the housing market.
-Estimation of the hedonic function using Ordinarly Least Squares (OLS) is typically inappropriate because the housing data commonly exhibit spatial autocorrelation.
-In particular, spatially autocorrelated error terms will lead to inconsistent estimates of OLS regression standard errors and inappropriate measures of statistical inference.
-
-It is now common to use spatial econometric techniques in the hedonic literature, for instance estimating a spatial lag (in which house prices are modeled as a function of neighboring house prices), or a spatial error model (in which the degree of spatial autocorrelation is also estimated).
-In the noise literature, for example, \citet{Theebe2004a} econometrically estimates a spatial error model, while \citet{Andersson2010} uses a spatial lag model.
-
-One common reason for significant spatially autocorrelated error terms is hedonic function misspecification.
-A portion of the hedonic regression errors may be explained by omitted spatial variables.
-Thus, nearby houses will tend to have similar spatial variable values and then similar error terms.
-Second, model misspecification can occur due to spatial non-stationarity of the hedonic function.
-That is, housing submarkets exist and the impact of changing housing characteristics will vary across submarkets.
-Failing to properly account for such heterogeneity will lead to spatially autocorrelated error estimates.
-
-Some traffic noise research simply explicitly assumes that their data comprise a single market.
-For example, \citet{Kim2007} assumes that by restricting analysis to residential properties surrounding the Inner Circular highway in the central area of Seoul from 2002 to 2004, that the price of traffic noise will be constant.
-Other research, such as \citet{Theebe2004a} used political boundaries to segment the market into five separate subarkets in the western part of the Netherlands.
-
-Another strategy is to let the data reveal different relationships within smaller areas of the study.
-For instance, \citet{Day2007} and \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} use semi-parametric techniques to allow the hedonic relationship to smoothly vary over space.
-We use techniques similar to the Geographically Weighted Regression method described in \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} to allow the hedonic function to vary over space without having a priori conceptions of where the function will be different.
-
-\subsection{Temporal Variation}
-Little work has been done estimating the changes in hedonic environmental (dis)amenities like noise over time.
-An event-study literature exists using temporal variation in noise, especially noise from airports (see, for example, \citet{Cohen2009}, ).
-However, these articles usually use the change in noise over time to identify the hedonic price of noise, rather than ask whether the hedonic price has changed.
-
-\citet{Wilhelmsson2000} is one example of research asking whether the implicit price of noise has changed over time.
-The study splits the 290 Swedish house sales into two separate time periods: 1986-89 and 1990-95.
-A Chow test revealed that the impact of traffic noise was different in the earlier vs.
-later time period, with noise being considered more of a nuisance in the suburb of Stockholm during the 1990s.
-
-\citet{Cho2011b} is a recent example of work asking whether the hedonic regression coefficients change over time in the Nashville, TN area.
-In particular, the study uses a repeat sales methodology to estimate changes in the implicit prices of hedonic characteristics as a result of the Great Recession of 2008-09 in the United States.
-The work finds that environmental amenities matter less in sales during the year 2008 when compared to pre-recession sales.
-
-We estimate regression coefficients over time using a moving window of 12 months in the hedonic analysis over the years 2005 - 2010.
-Such an analysis allows us to see if and when the implicit price of traffic noise changes within our study timeframe.
-Our results suggest that the percentage change in house price from an extra decibel of traffic noise actually became more negative after the Great Recession than before.
+In this paper, we seek to contribute to the hedonic literature by examining the relationship between real estate prices and variation in road traffic noise exposure.
+We approach this issue by means of an empirical case study of the St.\ Paul, Minnesota urban area.
+In particular, we construct a locally flexible model that allows for a non-stationary relationship between house prices and our explanatory variables over geography and time.
+Such Locally Weighted Regression (LWR) models have become increasingly common in published work and have been shown to be more accurate than spatial autoregressive models with misspecified weights matrices.
 
@@
 \section{Data}
-The 2010 US Census lists the population of the Minneapolis and St.
-Paul Metropolitan area in Minnesota as almost 3 million residents spread over seven counties.
+The 2010 US Census lists the population of the Twin Cities Metropolitan Region (Minneapolis and St.
+Paul and their surrounding areas)  as almost 3 million residents spread over seven counties.
 This study examines single family residential home transactions in the Census-defined urban areas of three of the seven counties – Dakota, Ramsey and Washington County (see Figure 1).
@@
 \begin{table}
-\caption{Simple Correlation Matrix of Quantitative Variables}\label{tab:cor}
+\caption{Pearson Correlation Coefficient Matrix of Quantitative Variables}\label{tab:cor}
 \includegraphics[width = \textwidth]{../graphs/CorrelationMatrix}
@@
 Although the 2010 MetroGIS Regional Parcel Dataset includes structural data on living area, age, garage presence, lot size and owner occupancy for every transaction, we have variables for the number of bedrooms, bathrooms, and size of the garage only for those house sales in one county.
-We feel confident in our results even without these variables for most of our study data because sensitivity analysis conducted in areas with the additional structural variables revealed very similar estimates when the variables were included and excluded.
+We feel confident in our results even without these independent variables for most of our study data because sensitivity analysis conducted in areas with the additional structural variables revealed very similar estimates when the variables were included and excluded.
+These results are in section \ref{Discussion} of the the paper.
 Additionally, other hedonic work has been published using a similar set of explanatory variables in this area, see for instance, \citet{Sander2009b}.
@@
 For instance, using GIS software we are able to calculate the Euclidean distance to numerous points of interest within the dataset, such as the nearest central business district, shopping centers, parks, and lakes.
-
-We also associate each transaction with its elementary school and include the average 3rd grade Minnesota Comprehensive Assessment (MCA) score for the local elementary school during the year of purchase.
+Additionally, a variable denoting the median household income for the surrounding census tract is created through the use of TIGER shapefiles from the 2010 Census Bureau and data from the 2010 American Community Survey (ACS).
+Lastly, we associate each transaction with its elementary school and include the average 3rd grade Minnesota Comprehensive Assessment (MCA) score for the local elementary school during the year of purchase.
 Test scores were obtained from the Minnesota Department of Education website.
 The school district and elementary school attendance boundary spatial information was taken from the Minnesota Geospatial Information Office Clearinghouse Data Catalog.
-Lastly, a variable denoting the median household income for the surrounding census tract is created through the use of TIGER shapefiles from the 2010 Census Bureau and data from the 2010 American Community Survey (ACS).
 
@@
 
-\section{Discussion}
+\section{Discussion}\label{Discussion}
 

### 2013-08-27 reports/Draft.tex
started revamping draft for Journal of Regional Science

@@
 \section{Introduction and Past Research}\label{sec:lit}
+Prolonged exposure to traffic noise affects people in a number of ways, ranging from simple annoyance (Miedema and Oudshoorn 2001; Ouis 2001), to sleep disturbance (Netherlands 2004), to increasing risk for stroke (Sorensen, Hvidberg et al.
+2011), hypertension(Jarup, Babishch et al.
+2008; Bodin, Albin et al.
+2009), and myocardial infarction (Babisch, Beule et al.
+2005).
+The noise level at which such effects are observed does not have to be high.
+It has been shown that people exposed to traffic noise with a 24-hour average of 55 dBA are found to be at a higher risk for hypertension (Barregard, Bonde et al.
+2009; Bodin, Albin et al.
+2009), and those exposed to 60 dBA or greater are found to be at a higher risk for stroke (Sorensen, Hvidberg et al.
+2011).
+This impact is expected to grow worse with the increasing number of vehicles in the urban road network and the diminishing number of night-time quiet hours unless mitigating measures are put in place (XXX).
+Given that much of this increased exposure occurs in areas where people live and work any mitigating measures must be based on a cost-benefit analysis.
+
+An important first step towards such an analysis is to examine real estate price fluctuations as a function of noise levels using hedonic regression.
+Such work has provided important insight on the nature of this relationship.
+Thus, Bateman et al.
+(2001) found that the negative eﬀect of traﬃc noise ranged from 0.08\% to 2.22\% per dB with a mean around 0.55\% per dB.
+In a review of 65 noise evaluation studies Navrud (2002) found an average decrease of 0.64\% per dB.
+\textbf{We need to briefly review other relevant papers here.}  However, with the exception of a few studies that have focused on air traffic noise exposure (we should check on this), the relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).
+One major reason for the thinness of the scholarly literature on this topic in the US lies in the difficulty of modeling noise propagation over the landscape.
+
+To properly analyze the spatial association between real estate prices and exposure to traffic noise at a landscape level, it is necessary to create a noise surface map at sufficiently detailed spatial resolution to account for the complex and heterogeneous interaction between the noise source and the resistance of the landscape to noise propagation.
+Implementing such a model can be very difficult.
+For one thing, the data needed for the model is very extensive and may not even be readily available (e.g., building footprint and height data).
+Furthermore, it is computationally very intensive, requiring more computing resources than a desktop.
+Fortunately, recent developments in GIS and distributive computing have reduced these difficulties, making it much easier to create a noise surface map at landscape level.
+
+In this paper, we seek to contribute to the hedonic literature by examining the relationship between real estate prices and variation in road traffic noise exposure.
+We approach this issue by means of an empirical case study of the Twin Cities Metro Region (TCMR), Minnesota.
+In particular, we model traffic noise propagation at landscape level using a spatially explicit approach instead of relying on (what?)…
+
 The value of noise pollution is typically estimated through simulated or related markets because no explicit private market for noise abatement exists.

### 2013-08-28 reports/Draft.Rnw
working on draft

@@
 \usepackage[round]{natbib}
-\usepackage{caption, amsmath, graphicx}
+\usepackage{caption, amsmath, graphicx, hyperref}
 
@@
 Such work has provided important insight on the nature of this relationship.
-Thus, Bateman et al.
-(2001) found that the negative eﬀect of traﬃc noise ranged from 0.08\% to 2.22\% per dB with a mean around 0.55\% per dB.
-In a review of 65 noise evaluation studies Navrud (2002) found an average decrease of 0.64\% per dB.
-\textbf{We need to briefly review other relevant papers here.}  However, with the exception of a few studies that have focused on air traffic noise exposure (we should check on this), the relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).
+Thus, \citet{Bateman2001} found that the negative eﬀect of traﬃc noise ranged from 0.08\% to 2.22\% per dB with a mean around 0.55\% per dB.
+In a review of 65 noise evaluation studies \citet{Navrud2002} found an average decrease of 0.64\% per dB.
+\textbf{We need to briefly review other relevant papers here.}  However, with the exception of a few studies that have focused on air traffic noise exposure \textbf{(we should check on this)}, the relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).
 One major reason for the thinness of the scholarly literature on this topic in the US lies in the difficulty of modeling noise propagation over the landscape.
@@
 The data explicitly model noise propagation as a function of nearby buildings and landcover, as well as present the results at a fine spatial resolution (10m x 10m).
-Such estimates, combined with sptially explicit modeling techniques allow us to make our second contribution to the literature.
-We present one of the first estimates of how the impact of traffic noiseeee varies over space.
+Such estimates, combined with spatially explicit modeling techniques allow us to make our second contribution to the literature.
+We present some of the first non-parametric estimates of how the impact of traffic noise spatially varies within an urban area in the United States.
 We find that while the impact of other important control variables in the hedonic function vary over space, the impact of traffic noise does not.
-Lastly, we present the first estimates of how the Great Recession has affected the hedonic price of traffic noise.
+Lastly, we present the first estimates of how the Great Recession has affected the implicit price of traffic noise.
+Contrary to other published work, our results suggest that consumers' marginal willingness to pay to avoid traffic noise actually increased after the recession.
 
@@
 We obtained data from approximately forty thousand sales transactions between 2005 and 2010 (n=42,095) from the 2010 MetroGIS Regional Parcel Dataset published by the Metropolitan Council.
-In addition to the geographic location and date of the house sale, we collected structural and locational variables commonly used in the hedonic literature.
+In addition to the geographic location and date of the house sale, we collected and/or constructed structural and locational variables commonly used in the hedonic literature.
 Table \ref{tab:sumStats} provides a brief description of the variables and some basic summary statistics.
@@
   Sale Price (thousands \$) & 98.8 & 195.0 & 241.0 & 265.5 & 314.9 & 675.0 & 102.8 \\ 
-  House Size (thousands square feet) & 390 & 1158 & 1628 & 1750 & 2188 & 4000 & 704 \\ 
+  House Size (feet$^2$) & 390 & 1158 & 1628 & 1750 & 2188 & 4000 & 704 \\ 
   Lot Size (acres) & 0.02 & 0.17 & 0.25 & 0.25 & 0.31 & 0.60 & 0.11 \\ 
-  Owner Occupancy Dummy & 0.0 & 1.0 & 1.0 & 0.8 & 1.0 & 1.0 & 0.4 \\ 
+  Owner Occupancy (0 = no, 1 = yes) & 0.0 & 1.0 & 1.0 & 0.8 & 1.0 & 1.0 & 0.4 \\ 
   Year House was Built & 1850 & 1950 & 1973 & 1967 & 1993 & 2010 & 32 \\ 
@@
   Median Income in Census Tract (thousands \$) & 13.9 & 54.6 & 69.1 & 72.6 & 89.7 & 143.3 & 23.6 \\ 
-  Elementary Test Scores & 335.6 & 359.8 & 365.4 & 364.5 & 370.4 & 551.7 & 10.6 \\ 
+  Elementary School Standardized Test Scores & 336 & 360 & 365 & 365 & 370 & 552 & 11 \\ 
   Distance to Central Business District (km) & 1.1 & 6.8 & 13.2 & 14.7 & 21.8 & 37.1 & 8.9 \\ 
@@
 Test scores were obtained from the Minnesota Department of Education website.
-The school district and elementary school attendance boundary spatial information was taken from the Minnesota Geospatial Information Office Clearinghouse Data Catalog.
+The school district and elementary school attendance boundary spatial information was taken from the Minnesota Geospatial Information Office Clearinghouse Data Catalog.\footnote{\url{http://www.mngeo.state.mn.us/chouse/data.html}}
 
@@
 While the mean sale price declined from roughly \$280,000 pre-crash to \$230,000 post-crash, most of the structural and neighborhood variables are relatively consistent across years.
-However, traffic noise displays a noticeable difference in the pre- and post-crash market transactions (the mean drops from 58 dB to 52 dB).
+However, traffic noise is noticeable different in the pre- and post-crash market transactions (the mean drops from 58 dB to 52 dB).
 
@@
 Our aim is to estimate the marginal willingness to pay for different attributes, in particular changes in the traffic noise associated with the house.
-Equation~\eqref{eq:model} expresses the basic hedonic model.
+Equation~\eqref{eq:model} expresses the basic hedonic model,
 \begin{equation}\label{eq:model}	
-ln \textrm{ Sale Price}_i = \beta _0 + \beta _1 \textrm{Noise}_i+ \beta _2 S_i+ \beta _3 N_i + \beta _4 T_i + \textrm{error}_i
+ln \textrm{ Sale Price}_i = \beta _0 + \beta _1 \textrm{Noise}_i+ \beta _2 S_i+ \beta _3 N_i + \beta _4 T_i + \textrm{error}_i,
 \end{equation}
-Where Noise$_i$ is the noise level for house $i$, $S_i$ is a vector of the house's structural attributes, $N_i$ is a vector of the neighborhood attributes, and $T_i$ is a vector of year fixed effects.
-We can interpret the regression model coefficients as the price semi-elasticities of the underlying attributes.
-For instance, we can interpret the coefficient on noise as the percentage increase in price for a one decibel increase in the traffic noise associated with the transaction in our dataset.
+where Noise$_i$ is the noise level for house $i$, $S_i$ is a vector of the house's structural attributes, $N_i$ is a vector of the neighborhood attributes, and $T_i$ is a vector of year fixed effects.
+This functional form allows us to interpret the regression coefficients as price semi-elasticities for the underlying attributes.
+For instance, we can interpret the coefficient on noise as the average percentage change in price for a one decibel increase in the traffic noise in our dataset.
 
@@
 Taken in aggregate, the results in Table \ref{tab:globalRegression} suggest that the hedonic price function may vary over space and time.
-While methods exist for parameterizing this variation (such as spatial expansion as suggested by \citet{Casetti1974}), we have no a priori knowledge of how to parameterize the variation over space and time.
+While methods exist for parameterizing this variation (such as spatial expansion as suggested by \citet{Casetti1972}), we have no a priori knowledge of how to parameterize the variation over space and time.
 As such, we turn to a semi-parametric form of hedonic regression, a flexible modeling approach which lets the data reveal how relationships vary, rather than specifying them beforehand.
@@
 In order to account for changing market conditions over time in our data, when estimating LWR coefficients we use only houses sold within the past 12 months.
-Thus, the coefficient estimates at a particular house are estimated using data from other sales nearby in both time and geography.
+Thus, the coefficient estimates at a particular house are estimated using data from other sales nearby in both time and geography, similar to the methodology used by \citet{Nappi-Choulet2011}.
 
@@
 Generally speaking, the third model performs slightly better than the second model, which performs better than the first model.
-The minimum GCV score is obtained using a bandwidth of 200 nearest houses and Model (3).
+The minimum GCV score is obtained using Model (3) and a bandwidth of 200 nearest houses.
+These results suggest that we are better able to predict house prices using the information contained in nearby (in both time and space) house transactions.
+They are also roughly similar to the results of \citet{Nappi-Choulet2011}, who reported results using the geographically nearest 300 to 500 observations rather than all across Paris.
 \begin{figure}
@@
 The lack of statistical significance for many of the local regression coefficients could be due to multiple factors.
-First, because we are estimating local regressions with only the nearest 200 data points, rather than over 30,000 sales as in the global model, we might be estimating the coefficients with less precision and are unable to differentiate the coefficients from zero.
+First, because we are estimating local regressions with only the nearest 200 data points, rather than tens of thousands sales as in the global model, we might be estimating the coefficients with less precision and are unable to differentiate the coefficients from zero.
 Alternatively, the coefficients themselves might vary, sometimes being close to zero and other times not.
@@
 
-\subsection{Does Space Matter?}
+\subsection{Does the Hedonic Function Vary over Space?}
+
 We believe the use of a LWR estimation procedure is appropriate after conducting two different Monte Carlo simulations with the data.
@@
 In other words, the LWR model never performed better than the global model when the locations of the data were randomized.
-This seems to be strong evidence that the increased ability to predict house prices with a local model is not due to chance.
+This seems to be strong evidence that the increased ability to predict our house prices with a local model is not due to chance.
 
-Second, we ran a Monte Carlo simulation as described in \citet{Fotheringham2002} and performed in a similar context by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009}. The simulation is as follows:
+Second, we ran a Monte Carlo simulation as described in \citet{Fotheringham2002} and performed in a similar context by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} and \citet{Cho2009}.
+The simulation is as follows:
 \begin{enumerate}
@@
 \end{enumerate}
-After 100 iterations of this simulation, the minimum GCV score for these resampled LWR models is 0.060, substantially larger than all models (global and local) with the actual data.
+After $M = 100$ iterations of this simulation, the minimum GCV score for these resampled LWR models is 0.060, substantially larger than all models (global and local) with the actual data.
 Again, this seems to suggest that our data exhibit spatial non-stationarity in the regression coefficients.
@@
 
-The results of the second Monte Carlo simulation are presented in column (6) of Table \ref{tab:mainresults}.
-Column (6) displays the probability of obtaining a larger standard deviation of LWR coefficient estimates based on the 100 simulations performed.
-For most variables, we never obtained a larger coefficient standard deviation in the simulation than we obtained from the LWR model with the actual data.
-However, the values associated with the traffic noise and owner occupancy variables suggest that the variation in LWR coefficients in our data may have been due to random chance.
+The results of the second Monte Carlo simulation are presented in column (6) of Table \ref{tab:mainresults} and in Figure \ref{fig:MCsds}.
+Column (6) of Table \ref{tab:mainresults} displays the proportion of Monte Carlo replications that resulted in larger standard deviations of the LWR coefficient estimates based.
+For most variables, we never obtained a larger standard deviation of LWR coefficients in the simulation than we obtained from the LWR model with the actual data.
+However, the values associated with the traffic noise and owner occupancy variables suggest that the variation in LWR coefficients for these variables in our data may have been due to random chance.
 These coefficients may in fact be stationary across the study area, while the other coefficients appear to be non-stationary.
@@
 
-Figure \ref{fig:MCsds} visually shows the results presented in column (6) of Table \ref{tab:mainresults} another way.
+Figure \ref{fig:MCsds} visually shows the results presented in column (6) of Table \ref{tab:mainresults}.
 Each subfigure displays the distribution of LWR coefficient standard deviations obtained from the 100 iterations of the Monte Carlo simulation and the standard deviation obtained with the actual data (in red).
-Note that it is the case that the standard deviations obtained with the actual data are substantially larger than those obtained in the simulation for most of the variables.
+Note that it is the case that the standard deviations obtained with the actual data are well to the right of the distribution obtained in the simulation for most of the variables.
 
 \begin{figure}
- \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{../graphs/CopyOfMCsimResultsSDs}}
+ \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{../graphs/MCsimResultsSDsClean}}
  \caption{The Monte Carlo Simulation Distribution of LWR Coefficient Standard Deviations and True Coefficient Standard Deviations.}\label{fig:MCsds}
@@
 
-\subsection{Do the Regression Coefficients Vary over Time}
+\subsection{Does the Impact of Traffic Noise Vary over Time?}
+Little work has been done estimating the changes in hedonic environmental (dis)amenities like noise over time.
+An event-study literature exists using temporal variation in noise, especially noise from airports (see, for example, \citet{Cohen2009}).
+However, these articles usually use the change in noise over time to identify the hedonic price of noise, rather than ask whether the hedonic price has changed.
 
-We know that house prices fell dramatically during and after the Great Recession of 2008-09.
-We know less about the patterns of change in the hedonic price functions during and after the fall in prices.
-For instance, did all house prices simply drop (mostly affecting the intercept term of the hedonic function), or did the implicit price of structural characteristics like the size of the house or its lot decrease, or perhaps the value of environmental amenities disproportionately dropped?
-This section presents some of the first evidence of how the hedonic price function for housing changed over time surrounding the Great Recession of 2008-09.
-We ask whether the LWR coefficients exhibit a temporal pattern.
+\citet{Wilhelmsson2000} is one example of research asking whether the implicit price of noise has changed over time.
+The study splits the 290 Swedish house sales into two separate time periods: 1986-89 and 1990-95.
+A Chow test revealed that the impact of traffic noise was different in the earlier vs.
+later time period, with noise being considered more of a nuisance in the suburb of Stockholm during the 1990s.
 
-Specifically, we create two new variables, ``\texttt{months since September 2008}'' and a dummy variable ``\texttt{post}'' for all sales after September 2008.
+\citet{Cho2011b} is a recent example of work asking whether the hedonic regression coefficients change over time in the Nashville, TN area.
+In particular, the study uses a repeat sales methodology to estimate changes in the implicit prices of hedonic characteristics as a result of the Great Recession of 2008-09 in the United States.
+The work finds that environmental amenities matter less in sales during the year 2008 when compared to pre-recession sales.
+
+We know of no published research that shows how the hedonic price estimates of traffic noise vary over time surrounding the Great Recession.
+In this section we seek to compare consumers' willingness to pay for reduced traffic noise exposure before and after the recession.
+Specifically, we create two new variables, ``\texttt{months since September 2008}'' and a dummy variable, ``\texttt{post},'' for all sales after September 2008.
 We then regress our LWR coefficients on these two variables and their interaction term as shown in equation \eqref{eq:LWRinteraction}.
@@
 
-The results of these regressions will help us understand the patterns of change in the hedonic price of different characteristics.
-In particular, significant values for $\hat{\alpha}_2$ suggest that there was a structural break in the LWR coefficients post September 2008, and significant values for $\hat{\alpha}_3$ will imply a difference in the temporal trend of the LWR coefficients.
-
-Note that the tables have not yet been formatted.
-
-\subsubsection{Traffic Noise}
-
-We know of no published research that shows how the hedonic price estimates of traffic noise vary over time surrounding the Great Recession.
-In this section we show that accounting for the month of the house sale significantly predicts to the estimated LWR coefficients for traffic noise.
+The results of this regression will help us understand the patterns of change (if any) in the marginal willingness to pay to avoid traffic noise.
+In particular, $\hat{\alpha _1} \neq 0$ suggests a linear temporal trend in the implicit price of traffic noise, $\hat{\alpha}_2 \neq 0$ suggests that there was a structural break in the LWR coefficients post September 2008, and $\hat{\alpha}_3 \neq 0$ implies a difference in the temporal trend of the LWR coefficients before and after September 2008.
 The linear regression results presented in Table \ref{tab:betaMAX} show that there is a significant negative shock to the estimated LWR coefficients for traffic noise after September 2008.
-Additionally, the coefficients also begin to a significant negative trend.
+Additionally, the coefficients also begin to show a significant negative monthly trend after September 2008.
 \begin{table}[h]
@@
 (Intercept) -1.781e-03  4.100e-05 -43.436  < 2e-16 ***
-month        6.982e-06  2.005e-06   3.482 0.000498 ***
+Month        6.982e-06  2.005e-06   3.482 0.000498 ***
 Post        -7.998e-04  7.209e-05 -11.094  < 2e-16 ***
-month:Post  -8.868e-05  4.484e-06 -19.776  < 2e-16 ***
+Month:Post  -8.868e-05  4.484e-06 -19.776  < 2e-16 ***
 ---
@@
 
-The results in Table \ref{tab:betaMAX} contradict the a priori assumption that environmental amenities will ``matter'' less during and after the Great Recession.
+The results in Table \ref{tab:betaMAX} contradict the a priori expectation that environmental amenities ``matter'' less during and after the Great Recession.
 In fact, these results suggest that the penalty for homes exposed to higher levels of traffic noise increased.
 That is, the negative hedonic coefficients on traffic noise got more negative after September 2008.
-It should be noted that our model can explain almost 10 percent of the variation in traffic noise LWR coefficient estimates.
+It should be noted that this simple model can explain almost 10 percent of the variation in traffic noise LWR coefficient estimates.
+Future work should investigate how other hedonic coefficients changed during and after the bursting of the housing bubble and resulting economic recession.
 
-\subsubsection{House Size}
-
-In this section we show how the hedonic coefficients on house size (as measured in square feet) change over time.
+% \subsubsection{House Size}
+% 
+% In this section we show how the hedonic coefficients on house size (as measured in square feet) change over time.
 Table \ref{tab:betaSQFT} shows that the LWR coefficients on house size were positive and trending up before September 2008, then the coefficients drop significantly in both absolute value and their time trend.
@@
 It should be noted that the model presented in Table \ref{tab:betaSQFT} explains less than one percent of the variation in our house size LWR coefficients.
-
-\begin{table}[h]
-\caption{Regression Results: Dependent Variable = House Size LWR Coefficients}\label{tab:betaSQFT}
-\begin{verbatim}
-              Estimate Std. Error t value Pr(>|t|)    
-(Intercept)  2.741e-04  1.317e-06 208.097  < 2e-16 ***
-month        8.742e-07  6.441e-08  13.573  < 2e-16 ***
-Post        -1.678e-05  2.316e-06  -7.245 4.43e-13 ***
-month:Post  -5.989e-07  1.440e-07  -4.157 3.23e-05 ***
----
-Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
-
-Residual standard error: 9.04e-05 on 31744 degrees of freedom
-Multiple R-squared: 0.006092,  Adjusted R-squared: 0.005998 
-F-statistic: 64.85 on 3 and 31744 DF,  p-value: < 2.2e-16 
-\end{verbatim}
-\end{table}
-
-\subsubsection{Lot Size}
-
-Table \ref{tab:betaACRES} shows interesting results that are qualitatively different from our previous results.
+% 
+% \begin{table}[h]
+% \caption{Regression Results: Dependent Variable = House Size LWR Coefficients}\label{tab:betaSQFT}
+% \begin{verbatim}
+%               Estimate Std. Error t value Pr(>|t|)    
+% (Intercept)  2.741e-04  1.317e-06 208.097  < 2e-16 ***
+% month        8.742e-07  6.441e-08  13.573  < 2e-16 ***
+% Post        -1.678e-05  2.316e-06  -7.245 4.43e-13 ***
+% month:Post  -5.989e-07  1.440e-07  -4.157 3.23e-05 ***
+% ---
+% Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1 
+% 
+% Residual standard error: 9.04e-05 on 31744 degrees of freedom
+% Multiple R-squared: 0.006092,  Adjusted R-squared: 0.005998 
+% F-statistic: 64.85 on 3 and 31744 DF,  p-value: < 2.2e-16 
+% \end{verbatim}
+% \end{table}
+% 
+% \subsubsection{Lot Size}
+% 
+% Table \ref{tab:betaACRES} shows interesting results that are qualitatively different from our previous results.
 The post-September 2008 dummy variable coefficient is only marginally significant and small in absolute value (when compared to the regression Intercept term).
@@
 The model presented in Table \ref{tab:betaACRES} explains less than a half of one percent of the variation in lot size LWR coefficients.
-
-\begin{table}[h]
-\caption{Regression Results: Dependent Variable = Lot Size LWR Coefficients}\label{tab:betaACRES}
-\begin{verbatim}
-(Intercept)  0.3828690  0.0054089  70.785  < 2e-16 ***
-month       -0.0015113  0.0002645  -5.713 1.12e-08 ***
-Post         0.0190349  0.0095117   2.001   0.0454 *  
-month:Post  -0.0001358  0.0005916  -0.229   0.8185    
----
-Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
-
-Residual standard error: 0.3713 on 31744 degrees of freedom
-Multiple R-squared: 0.002806,  Adjusted R-squared: 0.002711 
-F-statistic: 29.77 on 3 and 31744 DF,  p-value: < 2.2e-16 
-\end{verbatim}
-\end{table}
-
-\subsubsection{Intercept}
-We were also interested in how the LWR regression intercept changed over time.
+% 
+% \begin{table}[h]
+% \caption{Regression Results: Dependent Variable = Lot Size LWR Coefficients}\label{tab:betaACRES}
+% \begin{verbatim}
+% (Intercept)  0.3828690  0.0054089  70.785  < 2e-16 ***
+% month       -0.0015113  0.0002645  -5.713 1.12e-08 ***
+% Post         0.0190349  0.0095117   2.001   0.0454 *  
+% month:Post  -0.0001358  0.0005916  -0.229   0.8185    
+% ---
+% Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1 
+% 
+% Residual standard error: 0.3713 on 31744 degrees of freedom
+% Multiple R-squared: 0.002806,  Adjusted R-squared: 0.002711 
+% F-statistic: 29.77 on 3 and 31744 DF,  p-value: < 2.2e-16 
+% \end{verbatim}
+% \end{table}
+% 
+% \subsubsection{Intercept}
+% We were also interested in how the LWR regression intercept changed over time.
 For instance, perhaps the house price drops of the Great Recession were manifested primarily through reduced intercept terms.
@@
 In fact, our results show that the estimated LWR intercept terms are on average significantly higher post-September 2008.
-\begin{table}[h]
-\caption{Regression Results: Dependent Variable = LWR Intercept Estimates}\label{tab:betaINT}
-\begin{verbatim}
-(Intercept)  1.575488   0.213779   7.370 1.75e-13 ***
-month       -0.043836   0.010455  -4.193 2.76e-05 ***
-Post         2.845774   0.375939   7.570 3.84e-14 ***
-month:Post   0.007397   0.023383   0.316    0.752    
----
-Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
-
-Residual standard error: 14.67 on 31744 degrees of freedom
-Multiple R-squared: 0.003282,  Adjusted R-squared: 0.003188 
-F-statistic: 34.84 on 3 and 31744 DF,  p-value: < 2.2e-16  
-\end{verbatim}
-\end{table}
+% \begin{table}[h]
+% \caption{Regression Results: Dependent Variable = LWR Intercept Estimates}\label{tab:betaINT}
+% \begin{verbatim}
+% (Intercept)  1.575488   0.213779   7.370 1.75e-13 ***
+% month       -0.043836   0.010455  -4.193 2.76e-05 ***
+% Post         2.845774   0.375939   7.570 3.84e-14 ***
+% month:Post   0.007397   0.023383   0.316    0.752    
+% ---
+% Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1 
+% 
+% Residual standard error: 14.67 on 31744 degrees of freedom
+% Multiple R-squared: 0.003282,  Adjusted R-squared: 0.003188 
+% F-statistic: 34.84 on 3 and 31744 DF,  p-value: < 2.2e-16  
+% \end{verbatim}
+% \end{table}
 
@@
 The positive and significant interaction term suggests that the impact may be different for high vs.
-low levels of noise post-September 2008, but the difference in the predicted marginal effects is so small, that it works about to be a roughly \$25 difference for a \$300,000 house at 50 vs.
+low levels of noise post-September 2008, but the difference in the predicted marginal effects is so small, that it works about to be a difference of roughly \$25 for a \$300,000 house at 50 vs.
 75 dB.
@@
 We categorize the traffic noise data in 5 dB wide bins like \citet{Theebe2004a} and then estimate the mean LWR traffic noise coefficients in each category while also controlling for whether the sales took place pre- or post-September 2008.
-We see little to suggest any meaningful non-linearities in the effect of traffic noise on house prices, once we have controlled for the timing of the sales.
+We see little to suggest any meaningful non-linearities in the effect of traffic noise on house prices once we have controlled for the timing of the sales.
 
@@
 The vertical lines denote the standard error of the estimated mean by time and level category.
-Note that over 99 percent of our data have Noise levels between 35 and 80 dB and no houses were sold post-September 2008 with noise levels above 85 dB.}\label{fig:betaMAXvCat}
+Note that over 99 percent of our data have traffic noise levels between 35 and 80 dB and no houses were sold post-September 2008 with noise levels above 85 dB.}\label{fig:betaMAXvCat}
 \end{figure}
@@
 To the extent that structural variables like the number of bedrooms, bathrooms, garage size, or construction quality covary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias.
-We are somewhat comforted, however, because we do have some additional variables for a subset of our data.
-We have the number of bedrooms, bathrooms, and garage area for our houses located within Dakota County.
-Our analysis (Models 1, 2, and 3 described earlier) was repeated on this geographic subset of the data and the results were compared to the estimates obtained from the same analysis when these additional structural variables were omitted.
-We found strikingly similar estimates of the impact of traffic noise.
+
+We are somewhat comforted, however, because we do have some additional variables for a subset of our data and their inclusion does not change our results.
+We have variables for the number of bedrooms, number of bathrooms, and garage size for houses located within Dakota County.
+Our analysis (Models 1, 2, and 3 described earlier) was repeated for sales located within Dakota County and the results were compared to the estimates obtained from the same analysis when these additional structural variables were omitted.
+We found strikingly similar estimates of the impact of traffic noise for these data, regardless of whether or not the additional structural variables were included.
 
@@
 \begin{center}
-\caption{Mean and (Standard Deviation) LWR Noise Coefficients in Dakota County both with and without the additional structural variables available only for the county.}\label{tab:Dak}
-\begin{tabular}{lll}
- & \multicolumn{2}{c}{Additional variables?} \\
+\caption{Mean (Standard Deviation) LWR Traffic Noise Coefficient Estimates in Dakota County with and without Additional Structural Control Variables in Regression.}\label{tab:Dak}
+\begin{tabular}{lcc}
+ & \multicolumn{2}{p{1.3in}}{Additional structural variables included in regression?} \\
 Locally Weighted Regression Model & \multicolumn{1}{c}{no} & \multicolumn{1}{c}{yes} \\ \hline
@@
    & (0.00226) & (0.00309) \\ 
-Model (2) = (1) + Locational Variables & -0.00136 & -0.00140 \\ 
+Model (2) = Model (1) + Locational Variables & -0.00136 & -0.00140 \\ 
    & (0.00184) & (0.00218) \\ 
-Model (3) = (2) + City Fixed Effects & -0.00140 & -0.00137 \\ 
+Model (3) = Model (2) + City Fixed Effects & -0.00140 & -0.00137 \\ 
    & (0.00219) & (0.00176) \\ 
@@
 
-Table \ref{tab:Dak} shows that the traffic noise coefficients estimated by our LWR models are similar regardless of whether the additional structural variables were included or not.
-Welch two-sample t-tests fail to reject the null hypothesis of zero means across our three models (comparing LWR estimates with vs.
+Table \ref{tab:Dak} shows that the traffic noise coefficients estimated by our LWR models are similar regardless of whether or not the additional structural variables were included as control variables in the regressions.
+Welch two-sample t-tests fail to reject the null hypothesis of zero mean differences across our three models (comparing LWR estimates with vs.
 without the additional structural variables included in the model).
 Paired t-tests find differences for Model 2 and 3, but the estimated differences are zero to four decimal places and in one case the noise impact estimates with the additional variables are slightly larger and in the other case they are slightly smaller.
-We also conducted simple linear egressions of the noise coefficients without the additional structural variables on the noise coefficients obtained with the additional structural variables.
-In all three cases the intercept estimates were close zero with slopes almost exactly equal to one and each also had $R^2$ values over 0.7.
+We also conducted simple linear regressions of the traffic noise coefficients without the additional structural variables on the noise coefficients obtained with the additional structural variables.
+In all three cases the intercept estimates were close zero and the slope terms almost exactly equal to one.
+Each regression also had $R^2$ values over 0.7, suggesting that the coefficient estimates obtained with the additional structural explanatory variables are similar to the results obtained without the explanatory variables for Dakota County.
+We have no reason to believe that our results would be different in the other two counties (Ramsey and Washington) in our study.
 
@@
 To the extent that traffic flows and composition signicantly changed over time, our traffic noise variables may be inaccurate for those time periods.
-For instance, the US Department of Transportation reports that total vehicle miles travelled decreased by up to 2 percent year-on-year during the Great Recession.
-Thus, our noise estimates may be inaccurate for later time periods and this may bias our estimates of the impact of noise on house values.
-Future work may better estimate the impact of traffic noise over time by generating noise data to reflect changing traffic patterns.
-
-What other weaknesses should we discuss?
-
-We didn't explicitly model spatial autocorrelation in the error terms.
-
-We might want to further reduce the number of parameters to estimate through the use of either mixed-LWR or running separate regressions for submarkets determined through hierarchical clustering like \citet{Day2003}.
+For instance, the US Department of Transportation reports that total vehicle miles travelled decreased by almost 4 percent year-on-year during the Great Recession.\footnote{See for instance, \url{http://www.fhwa.dot.gov/ohim/tvtw/08dectvt}.} Thus, our noise estimates may be inaccurate for later time periods and this may bias our estimates of the impact of noise on house values.
+Future work may seek to better estimate the impact of traffic noise over time by generating noise data to reflect changing traffic patterns.
 
@@
 We estimated the impact of traffic noise on housing prices using Locally Weighted Regression techniques in the St.\ Paul, MN metropolitan area.
-Specifically, we estimate linear regressions at each house within our dataset using only information contained in geographically nearby houses sold within the last 12 months.
+Specifically, we report estimates obtained from regressing the logged sales price on traffic noise and other independent variables at each house within our dataset using only information contained in  neighboring houses sold within the last 12 months.
 We find strong evidence that the hedonic function in our study area differs over space and time.
@@
 
-Monte Carlo simulations suggest that the better goodness-of-fit provided by the local models are not due to chance and that many hedonic impact estimates vary over space within our study area.
+Monte Carlo simulations suggest that the better goodness-of-fit provided by the local models are not likely due to chance and many hedonic impact estimates vary over space within our study area.
 When the location of our data was randomly assigned and our LWR model was re-estimated, in 100 consecutive simulations the smallest GCV score was  obtained when the data were analyzed at a global level rather than local.
-Additionally, re-estimating the LWR model using a local bandwidth of 200 nearest house sales when the location was randomly assigned yielded substantially smaller standard deviations for the majority of our regression coefficients.
-This larger variation within our true data suggests spatial non-stationarity in the regression coefficients.
+Additionally, re-estimating the LWR model using a local bandwidth of 200 nearest house sales when the location was randomly assigned yielded substantially smaller standard deviations (i.e.
+less spatial variation) for the majority of our regression coefficients.
+This larger variation within our actual location-based data suggests spatial non-stationarity in the regression coefficients.
 That is, after trying thousands of different combinations of varying levels of local analysis with the spatially redistributed data, we never came close to estimating our observed housing sales prices as well as we can with the local analysis on the actual data.
 
-Contrary to the previous results presented by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} and \citet{Theebe2004a}, we find little evidence to suggest that the impact of traffic noise varies over space or by level of noise within our study area.
-The traffic noise coefficient was one of only two variables with regression coefficient standard deviations smaller than or similar to the simulated distributions obtained from Monte Carlo experiments.
+The impact of traffic noise was one of the few regression coefficients for which we did not find strong evidence of spatial non-stationarity.
+Such results are contradictory to those presented by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} and \citet{HughesJr.1992}, which found evidence of spatial non-stationarity in the impact of traffic noise in their respective study areas (Barcelona, Spain and Baton Rouge, Louisiana).
+Additionally, whereas some researchers such as \citet{Theebe2004a} suggest that the impact of traffic noise varies with the level of traffic noise, we find little evidence to suggest that the impact of increased traffic noise is different when starting at a low or high noise level.
 We do, however, find significant temporal variation in the impact of traffic noise in our data.
-The estimated impact of one additional decibel of traffic noise is a 0.19 percent reduction in the sale price of houses before September 2008, vs.
+The estimated impact of one additional decibel of traffic noise is a 0.19 percent reduction on average in the sale price of houses before September 2008, vs.
 0.37 percent after September 2008.
-Lastly, after controlling for the Great Recession, we find no significant differences in the impact of traffic noise across the range of commonly seen noise levels (50-70 dB).
+
+As mentioned previously, there are multiple areas in which this paper suggests future work on the topic.
+We found evidence to suggest that, while the locally weighted regression and its associated spatial non-stationarity of the hedonic function are warranted, not all coefficients seem to vary over space.
+A ``mixed'' locally weighted regression, in which some variable coefficients vary over space while others are constant, could allow future researchers to more precisely estimate the marginal implicit prices in the hedonic analysis.
+Second, given our findings of temporal variation in the hedonic function, future researchers may strive to construct datasets reflecting changing economic conditions to estimate the hedonic relationship between housing prices and its constituent characteristics.
+Lastly, future research should consider applying the findings of \citet{Carruthers2010}, which suggest that locally weighted regressions may allow researchers to more accurately identify the second-stage hedonic functions and thereby better understand the demand for environmental and other non-market goods.
+Such results will be valuable in future cost-benefit analysis and policy discussions.
 
@@
 \end{document}
-
-% \begin{table}
-% \caption{Data Description}\label{tab:descriptive}
-% \begin{tabular}{lp{3in}r}
-% Variable & Description  & Expected Hedonic Impact \\ \
-% 
-% Sale Price &   Price of most recent sale  (in \$) & \\
-% 
-% Home Size	& Area of finished space in the home (in square feet)	& (+) \\
-% Lot Size	& Area of land house sits on (in acres)	& (+) \\
-% Year Built & Year home was constructed &	(+) \\
-% Owner	Occupancy & Does the owner occupy the house? (0 or 1) &	(+) \\
-% 
-% Traffic Noise	& Maximum decibel level of traffic noise (dB) measured within parcel &	(-) \\
-% MCA 3  & Average 3rd grade Minnesota Comprehensive Assessment (MCA) score for local elementary school &	(+) \\
-% Median Income	& Median household income (in dollars) for 2010 Census tract &	(+) \\
-% Dist. to CBD &	Distance (in meters) to nearest central business district	& (-) \\
-% Dist. to shop &	Distance (in meters) to nearest major shopping center	& (+)/(-) \\
-% Dist. to lake &	Distance (in meters) to nearest public lake	& (-) \\
-% Dist. to park	& Distance (in meters) to nearest public park	& (-) \\
-% City &	City a parcel resides in	& (+)/(-) \\ \hline
-% \multicolumn{3}{l}{Total number of house sales between 2005 and 2010 (n = 42,095) }
-% \end{tabular}
-% \end{table}

### 2013-08-28 reports/Draft.tex
working on draft

@@
 For one thing, the data needed for the model is very extensive and may not even be readily available (e.g., building footprint and height data).
-Furthermore, it is computationally very intensive, requiring more computing resources than a desktop.
-Fortunately, recent developments in GIS and distributive computing have reduced these difficulties, making it much easier to create a noise surface map at landscape level.
+Furthermore, it is computationally very intensive.
+Fortunately, recent developments in Geographic Information Systems and distributive computing have reduced these difficulties, making it much easier to create a noise surface map at landscape level.
 
 In this paper, we seek to contribute to the hedonic literature by examining the relationship between real estate prices and variation in road traffic noise exposure.
-We approach this issue by means of an empirical case study of the Twin Cities Metro Region (TCMR), Minnesota.
-In particular, we model traffic noise propagation at landscape level using a spatially explicit approach instead of relying on (what?)…
-
-The value of noise pollution is typically estimated through simulated or related markets because no explicit private market for noise abatement exists.
-\citet{Nelson1982} is perhaps the best known earliest review of 14 housing market studies of the economic impact of traffic noise on property values in Canada and the United States.
-More recently, a number of reviews have been produced for European government agencies.
-\citet{Bateman2001} reviewed the literature for the Scottish Government while \citet{Navrud2002} provided a ``state of the art'' review for the European Commission Environment Directorate General.
-
-The Hedonic Price Method is commonly used to value noise by examining real estate price fluctuations as a function of noise levels.
-Based on the canonical work by \citet{Rosen1974}, researchers typically estimate a hedonic price function specifying the logged sale price of a property as a linear function of the traffic noise exhibited at the house.
-Such a specification leads to reporting the impact of traffic noise as a percentage decrease in house price per one decibel (dB) increase in traffic noise.
-According to \citet{Bateman2001}, the negative effect of traffic noise has ranged from 0.08\% to 2.22\% per dB with a mean around 0.55\% per dB.
-In a review of 65 noise evaluation studies \citet{Navrud2002} found an average decrease of 0.64\% per dB.
-
-\citet{Nelson2008} produced an updated review of the traffic noise literature for the edited volume \underline{Hedonic Methods in Housing Markets Economics}.
-The chapter describes several areas of continued interest in the empirical literature, most notably: the measure of traffic noise, spatial modeling of the hedonic price function, and housing market dynamics.
-
-\subsection{Measure of Traffic Noise}
-I'm going to need some help writing about noise measures. Perhaps Tsegaye can lend a hand?
-
-Noise data is typically not collected for each every house in a hedonic study.
-For example, \citet{Huang;Palmquist2001} collect noise data using 128 monitoring stations throughout a suburb of Seattle, WA.
-Such a strategy forces the researchers to interpolate the data between the monitoring stations in order to associate each house with a noise level.
-While the researchers do not describe how the interpolation was done, they implicitly admit the potential uncertainty of the method by categorizing traffic noise exposure into 2.5 dB wide categories.
-Other researchers, such as \citet{Theebe2004a} use 5 dB wide bins, and \citet{Nelson2008} even claims that some studies use bins as wide as 10 dB.
-Such coarse measurements can lead to serious errors in variables and imprecise estimates of the impact of noise.
-
-Other researchers obtain noise levels from external sources without much description of the variable source.
-For instance, \cite{MarmolejoDuarteCarlos;GonzalezTamez2009} simply list a ``City Council Sonic Map'',  \citet{Blanco2011} cite the Department for Environment Food and Rural Affairs Noise mapping England project.
-\citet{Andersson2010} state, ``Information about noise levels is from a study on the health effects of traffic noise conducted in Lerum [Sweden] in 2004 (Ohrstrom et al.
-2005).
-Separate noise calculations were made for railway and road noise for all the houses in Lerum.''
-
-Traffic noise at a location can vary significantly depending on changing traffic conditions.
-Such variation has led to multiple measures of noise.
-Some measures eliminate the fluctuations in sound and instead represent the equivalent continuous constant sound pressure at a site.
-Other indices use noise values that are only exceeded a given percentage of time.
-For instance, \citet{Huang;Palmquist2001} use dB $L_{10}$ as their noise measure, where $L_{10}$ denotes the value that is exceeded only 10 percent of the time.
-Still others adjust nighttime noise exposure levels to account for potential increased perceived nuisance.
-\citet{Baranzini2010} even surveyed inhabitants about their perceptions of the level of noise and their annoyance.
-The work finds similar results for significant levels of measured noise as compared subjective measures of noise.
-
-\emph{What do we have?
-There is still a lot of work to be done in this area, better understanding the measures others use as well as what we have and how they compare.
-I'm surprised at how little information people actually provide about their noise data.}
-
-Spatial resolution of the data. \citet{Theebe2004a} had noise levels for square areas of 100 x 100m.
-
-% Beyond the fact that no direct natural economic markets exist in which consumers can reveal their willingness to pay to avoid traffic noise, researchers also must choose how to measure the nuisance itself.
-Some researchers (see, for instance, \citet{HughesJr.1992}, \citet{Li2012} \citet{Larsen2012}) attempt to measure the negative externality of traffic by correlating traffic volume with house prices.
-However, traffic may generate other externalities beyond noise (such as local air pollution and reduced safety for pedestrians and drivers) and so these strategies overestimate the size of the noise externality.
-% 
-% The value of traffic noise is important in and of itself.
-Governments routinely erect noise barriers to shield residential areas from traffic noise.
-(cite some numbers here!).
-To aid such work, it is important to understand the benefits of these policies.
-For instance, until 2011, the Minnesota Department of Transportation used a cost effectiveness threshold for noise mitigation projects of \$3,250 per dB reduced per house.
-Given that some of the benefits of noise reductions are capitalized in house prices, we are curious to see how our estimated magnitudes compare to the state cost effectiveness cutoff.
-
-\subsection{Spatial Analysis}
-Advances in Geographic Information System (GIS) technology and digitized datasets have made research easier to conduct over larger geographies, with larger samples, and while explicitly considering the spatial nature of the housing market.
-Estimation of the hedonic function using Ordinarly Least Squares (OLS) is typically inappropriate because the housing data commonly exhibit spatial autocorrelation.
-In particular, spatially autocorrelated error terms will lead to inconsistent estimates of OLS regression standard errors and inappropriate measures of statistical inference.
-
-It is now common to use spatial econometric techniques in the hedonic literature, for instance estimating a spatial lag (in which house prices are modeled as a function of neighboring house prices), or a spatial error model (in which the degree of spatial autocorrelation is also estimated).
-In the noise literature, for example, \citet{Theebe2004a} econometrically estimates a spatial error model, while \citet{Andersson2010} uses a spatial lag model.
-
-One common reason for significant spatially autocorrelated error terms is hedonic function misspecification.
-A portion of the hedonic regression errors may be explained by omitted spatial variables.
-Thus, nearby houses will tend to have similar spatial variable values and then similar error terms.
-Second, model misspecification can occur due to spatial non-stationarity of the hedonic function.
-That is, housing submarkets exist and the impact of changing housing characteristics will vary across submarkets.
-Failing to properly account for such heterogeneity will lead to spatially autocorrelated error estimates.
-
-Some traffic noise research simply explicitly assumes that their data comprise a single market.
-For example, \citet{Kim2007} assumes that by restricting analysis to residential properties surrounding the Inner Circular highway in the central area of Seoul from 2002 to 2004, that the price of traffic noise will be constant.
-Other research, such as \citet{Theebe2004a} used political boundaries to segment the market into five separate subarkets in the western part of the Netherlands.
-
-Another strategy is to let the data reveal different relationships within smaller areas of the study.
-For instance, \citet{Day2007} and \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} use semi-parametric techniques to allow the hedonic relationship to smoothly vary over space.
-We use techniques similar to the Geographically Weighted Regression method described in \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} to allow the hedonic function to vary over space without having a priori conceptions of where the function will be different.
-
-\subsection{Temporal Variation}
-Little work has been done estimating the changes in hedonic environmental (dis)amenities like noise over time.
-An event-study literature exists using temporal variation in noise, especially noise from airports (see, for example, \citet{Cohen2009}, ).
-However, these articles usually use the change in noise over time to identify the hedonic price of noise, rather than ask whether the hedonic price has changed.
-
-\citet{Wilhelmsson2000} is one example of research asking whether the implicit price of noise has changed over time.
-The study splits the 290 Swedish house sales into two separate time periods: 1986-89 and 1990-95.
-A Chow test revealed that the impact of traffic noise was different in the earlier vs.
-later time period, with noise being considered more of a nuisance in the suburb of Stockholm during the 1990s.
-
-\citet{Cho2011b} is a recent example of work asking whether the hedonic regression coefficients change over time in the Nashville, TN area.
-In particular, the study uses a repeat sales methodology to estimate changes in the implicit prices of hedonic characteristics as a result of the Great Recession of 2008-09 in the United States.
-The work finds that environmental amenities matter less in sales during the year 2008 when compared to pre-recession sales.
-
-We estimate regression coefficients over time using a moving window of 12 months in the hedonic analysis over the years 2005 - 2010.
-Such an analysis allows us to see if and when the implicit price of traffic noise changes within our study timeframe.
-Our results suggest that the percentage change in house price from an extra decibel of traffic noise actually became more negative after the Great Recession than before.
+We approach this issue by means of an empirical case study of the St.\ Paul, Minnesota urban area.
+In particular, we construct a locally flexible model that allows for a non-stationary relationship between house prices and our explanatory variables over geography and time.
+Such Locally Weighted Regression (LWR) models have become increasingly common in published work and have been shown to be more accurate than spatial autoregressive models with misspecified weights matrices.
 
@@
 The data explicitly model noise propagation as a function of nearby buildings and landcover, as well as present the results at a fine spatial resolution (10m x 10m).
-Such estimates, combined with sptially explicit modeling techniques allow us to make our second contribution to the literature.
-We present one of the first estimates of how the impact of traffic noiseeee varies over space.
+Such estimates, combined with spatially explicit modeling techniques allow us to make our second contribution to the literature.
+We present some of the first non-parametric estimates of how the impact of traffic noise spatially varies within an urban area in the United States.
 We find that while the impact of other important control variables in the hedonic function vary over space, the impact of traffic noise does not.
-Lastly, we present the first estimates of how the Great Recession has affected the hedonic price of traffic noise.
+Lastly, we present the first estimates of how the Great Recession has affected the implicit price of traffic noise.
+Contrary to other published work, our results suggest that consumers' marginal willingness to pay to avoid traffic noise actually increased after the recession.
 
 \section{Data}
-The 2010 US Census lists the population of the Minneapolis and St.
-Paul Metropolitan area in Minnesota as almost 3 million residents spread over seven counties.
+The 2010 US Census lists the population of the Twin Cities Metropolitan Region (Minneapolis and St.
+Paul and their surrounding areas) as almost 3 million residents spread over seven counties.
 This study examines single family residential home transactions in the Census-defined urban areas of three of the seven counties – Dakota, Ramsey and Washington County (see Figure 1).
 We obtained data from approximately forty thousand sales transactions between 2005 and 2010 (n=42,095) from the 2010 MetroGIS Regional Parcel Dataset published by the Metropolitan Council.
-In addition to the geographic location and date of the house sale, we collected structural and locational variables commonly used in the hedonic literature.
+In addition to the geographic location and date of the house sale, we collected and/or constructed structural and locational variables commonly used in the hedonic literature.
 Table \ref{tab:sumStats} provides a brief description of the variables and some basic summary statistics.
@@
 For instance, using GIS software we are able to calculate the Euclidean distance to numerous points of interest within the dataset, such as the nearest central business district, shopping centers, parks, and lakes.
-
-We also associate each transaction with its elementary school and include the average 3rd grade Minnesota Comprehensive Assessment (MCA) score for the local elementary school during the year of purchase.
+Additionally, a variable denoting the median household income for the surrounding census tract is created through the use of TIGER shapefiles from the 2010 Census Bureau and data from the 2010 American Community Survey (ACS).
+Lastly, we associate each transaction with its elementary school and include the average 3rd grade Minnesota Comprehensive Assessment (MCA) score for the local elementary school during the year of purchase.
 Test scores were obtained from the Minnesota Department of Education website.
-The school district and elementary school attendance boundary spatial information was taken from the Minnesota Geospatial Information Office Clearinghouse Data Catalog.
-Lastly, a variable denoting the median household income for the surrounding census tract is created through the use of TIGER shapefiles from the 2010 Census Bureau and data from the 2010 American Community Survey (ACS).
+The school district and elementary school attendance boundary spatial information was taken from the Minnesota Geospatial Information Office Clearinghouse Data Catalog.\footnote{\url{http://www.mngeo.state.mn.us/chouse/data.html}}
 
@@
 The vertical lines denote the standard error of the estimated mean by time and level category.
-Note that over 99 percent of our data have Noise levels between 35 and 80 dB and no houses were sold post-September 2008 with noise levels above 85 dB.}\label{fig:betaMAXvCat}
+Note that over 99 percent of our data have traffic noise levels between 35 and 80 dB and no houses were sold post-September 2008 with noise levels above 85 dB.}\label{fig:betaMAXvCat}
 \end{figure}
 
-\section{Discussion}
+\section{Discussion}\label{Discussion}
 

### 2013-08-29 reports/Draft.Rnw
worked on the draft a bit

@@
 Significant evidence suggests spatial and temporal non-stationarity in the hedonic price function within our study area.
-In contrast to previous research, however, we find little evidence that the impact of traffic noise exhibits a significant non-linear relationship with the decibel level of the traffic noise, nor does the impact seem to vary over space.
+In contrast to previous research, however, we find little evidence that the price semi-elasticity of traffic noise varies with the decibel level of the traffic noise, nor does the impact seem to exhibit spatial non-stationarity.
 We find significant differences in the impact of traffic noise from the beginning to the end of our sample.
@@
 Such work has provided important insight on the nature of this relationship.
-Thus, \citet{Bateman2001} found that the negative eﬀect of traﬃc noise ranged from 0.08\% to 2.22\% per dB with a mean around 0.55\% per dB.
-In a review of 65 noise evaluation studies \citet{Navrud2002} found an average decrease of 0.64\% per dB.
-\textbf{We need to briefly review other relevant papers here.}  However, with the exception of a few studies that have focused on air traffic noise exposure \textbf{(we should check on this)}, the relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).
+Thus, \citet{Bateman2001} found that the negative eﬀect of traﬃc noise ranged from 0.08 to 2.22 percent per dB with a mean around 0.55 percent per dB.
+In a review of 65 noise evaluation studies \citet{Navrud2002} found an average decrease of 0.64 percent per dB.
+\textbf{We need to briefly review other relevant papers here.}  However, with the exception of a few studies that have focused on air traffic noise exposure \textbf{(see, for instance, \citet{coh})}, the relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).
 One major reason for the thinness of the scholarly literature on this topic in the US lies in the difficulty of modeling noise propagation over the landscape.

### 2013-08-29 reports/Draft.Rnw

--- 2013-08-27 reports/Draft.Rnw
@@
 Such work has provided important insight on the nature of this relationship.
-Thus, Bateman et al.
-(2001) found that the negative eﬀect of traﬃc noise ranged from 0.08\% to 2.22\% per dB with a mean around 0.55\% per dB.
-In a review of 65 noise evaluation studies Navrud (2002) found an average decrease of 0.64\% per dB.
-\textbf{We need to briefly review other relevant papers here.}  However, with the exception of a few studies that have focused on air traffic noise exposure (we should check on this), the relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).
+Thus, \citet{Bateman2001} found that the negative eﬀect of traﬃc noise ranged from 0.08 to 2.22 percent per dB with a mean around 0.55 percent per dB.
+In a review of 65 noise evaluation studies \citet{Navrud2002} found an average decrease of 0.64 percent per dB.
+\textbf{We need to briefly review other relevant papers here.}  However, with the exception of a few studies that have focused on air traffic noise exposure \textbf{(see, for instance, \citet{coh})}, the relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).
 One major reason for the thinness of the scholarly literature on this topic in the US lies in the difficulty of modeling noise propagation over the landscape.
+>>>>>>> 4543f31da98e1080a1ead85b6607230c99f3c848
 

### 2013-08-29 reports/Draft.Rnw
resolved conflict
working on lit review section

@@
 \section{Introduction and Past Research}\label{sec:lit}
-Prolonged exposure to traffic noise affects people in a number of ways, ranging from simple annoyance (Miedema and Oudshoorn 2001; Ouis 2001), to sleep disturbance (Netherlands 2004), to increasing risk for stroke (Sorensen, Hvidberg et al.
+Prolonged exposure to traffic noise affects people in a number of ways, ranging from simple annoyance \citep{Weinhold2013, Miedema2001} (Miedema and Oudshoorn 2001; Ouis 2001), to sleep disturbance (Netherlands 2004), to increasing risk for stroke (Sorensen, Hvidberg et al.
 2011), hypertension(Jarup, Babishch et al.
@@
 An important first step towards such an analysis is to examine real estate price fluctuations as a function of noise levels using hedonic regression.
-Such work has provided important insight on the nature of this relationship.
-Thus, \citet{Bateman2001} found that the negative eﬀect of traﬃc noise ranged from 0.08 to 2.22 percent per dB with a mean around 0.55 percent per dB.
-In a review of 65 noise evaluation studies \citet{Navrud2002} found an average decrease of 0.64 percent per dB.
-\textbf{We need to briefly review other relevant papers here.}  However, with the exception of a few studies that have focused on air traffic noise exposure \textbf{(see, for instance, \citet{coh})}, the relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).
+\citet{Nelson1982} reviewed early work in this area, but many early studies were limited by small sample sizes and narrow spatial scopes.
+A review by \citet{Bateman2001} found that the negative eﬀect of traﬃc noise ranged from 0.08 to 2.22 percent per dB with a mean around 0.55 percent per dB, while \citet{Navrud2002} found an average decrease of 0.64 percent per dB.
+More recent work has tended to focus on the European experience with noise, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Netherlands \citep{Theebe2004a}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, and Switzerland \citep{Baranzini2010}.
+
+Work examining the negative effects of noise in the United States have tended to concentrate on noise from airports \citep{Espey2000, McMillen2004, Cohen2008a} or indirect effects of traffic noise, such as proximity to highways \citep{Matthews2007, Chernobai2009, Li2012}, or traffic counts \citep{Highes1992, Larsen2012}.
+the relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).
 One major reason for the thinness of the scholarly literature on this topic in the US lies in the difficulty of modeling noise propagation over the landscape.
->>>>>>> 4543f31da98e1080a1ead85b6607230c99f3c848
 

### 2013-08-29 reports/Draft.tex
working on lit review section

--- 2013-08-27 reports/Draft.tex
@@
 An important first step towards such an analysis is to examine real estate price fluctuations as a function of noise levels using hedonic regression.
-Such work has provided important insight on the nature of this relationship.
-Thus, Bateman et al.
-(2001) found that the negative eﬀect of traﬃc noise ranged from 0.08\% to 2.22\% per dB with a mean around 0.55\% per dB.
-In a review of 65 noise evaluation studies Navrud (2002) found an average decrease of 0.64\% per dB.
-\textbf{We need to briefly review other relevant papers here.}  However, with the exception of a few studies that have focused on air traffic noise exposure (we should check on this), the relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).
+\citet{Nelson1982} reviewed early work in this area, but many early studies were limited by small sample sizes and narrow spatial scopes.
+A review by \citet{Bateman2001} found that the negative eﬀect of traﬃc noise ranged from 0.08 to 2.22 percent per dB with a mean around 0.55 percent per dB, while \citet{Navrud2002} found an average decrease of 0.64 percent per dB.
+More recent work has tended to focus on the European experience with noise, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Netherlands \citep{Theebe2004a}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, and Switzerland \citep{Baranzini2010}.
+
+Work examining the negative effects of noise in the United States have tended to concentrate on noise from airports \citep{Espey2000, McMillen2004, Cohen2008a} or indirect effects of traffic noise, such as proximity to highways \citep{Matthews2007, Chernobai2009, Li2012}, or traffic counts \citep{Highes1992, Larsen2012}.
+the relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).
 One major reason for the thinness of the scholarly literature on this topic in the US lies in the difficulty of modeling noise propagation over the landscape.

### 2013-08-30 reports/Draft.Rnw
worked on the Dakota County table and future research

@@
 \citet{Nelson1982} reviewed early work in this area, but many early studies were limited by small sample sizes and narrow spatial scopes.
-A review by \citet{Bateman2001} found that the negative eﬀect of traﬃc noise ranged from 0.08 to 2.22 percent per dB with a mean around 0.55 percent per dB, while \citet{Navrud2002} found an average decrease of 0.64 percent per dB.
+A review by \citet{Bateman2001} found that the negative effect of traffic noise ranged from 0.08 to 2.22 percent per dB with a mean around 0.55 percent per dB, while \citet{Navrud2002} found an average decrease of 0.64 percent per dB.
 More recent work has tended to focus on the European experience with noise, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Netherlands \citep{Theebe2004a}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, and Switzerland \citep{Baranzini2010}.
 
-Work examining the negative effects of noise in the United States have tended to concentrate on noise from airports \citep{Espey2000, McMillen2004, Cohen2008a} or indirect effects of traffic noise, such as proximity to highways \citep{Matthews2007, Chernobai2009, Li2012}, or traffic counts \citep{Highes1992, Larsen2012}.
-the relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).
+The relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).
+Work examining the negative effects of noise in the US has instead tended to concentrate on noise from airports \citep{Espey2000, McMillen2004, Cohen2008a} or indirect effects of traffic noise, such as proximity to highways \citep{Matthews2007, Chernobai2009, Li2012}, or traffic counts \citep{HughesJr.1992, Larsen2012}.
 One major reason for the thinness of the scholarly literature on this topic in the US lies in the difficulty of modeling noise propagation over the landscape.
@@
 In particular, we construct a locally flexible model that allows for a non-stationary relationship between house prices and our explanatory variables over geography and time.
-Such Locally Weighted Regression (LWR) models have become increasingly common in published work and have been shown to be more accurate than spatial autoregressive models with misspecified weights matrices.
+Such Locally Weighted Regression (LWR) models have become increasingly common in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than spatial autoregressive models with misspecified weights matrices \citep{McMillen2012}.
 
@@
 Such estimates, combined with sptially explicit modeling techniques allow us to make our second contribution to the literature.
-We present one of the first estimates of how the impact of traffic noiseeee varies over space.
-We find that while the impact of other important control variables in the hedonic function vary over space, the impact of traffic noise does not.
+We present one of the first non-parametric estimates of how the impact of traffic noise varies over space within an urban area in the United States.
+Contrary to previous work, we find that while the impact of other important control variables in the hedonic function vary over space, the impact of traffic noise does not.
 Lastly, we present the first estimates of how the Great Recession has affected the hedonic price of traffic noise.
@@
 Taken in aggregate, the results in Table \ref{tab:globalRegression} suggest that the hedonic price function may vary over space and time.
-While methods exist for parameterizing this variation (such as spatial expansion as suggested by \citet{Casetti1974}), we have no a priori knowledge of how to parameterize the variation over space and time.
+While methods exist for parameterizing this variation \citep[such as spatial expansion as suggested by][]{Casetti1972}, we have no a priori knowledge of how to parameterize the variation over space and time.
 As such, we turn to a semi-parametric form of hedonic regression, a flexible modeling approach which lets the data reveal how relationships vary, rather than specifying them beforehand.
@@
 }
- \caption*{\small (5) displays the proportion of $\hat{\beta}_{LWR}$ that can reject the null hypthesis of $\beta =0$.\\ (6) displays the proportion of Monte Carlo simulations with larger standard deviations of the LWR coefficients than $\sigma_{\hat{\beta}}$}
+ \caption*{\small Column (5) displays the proportion of $\hat{\beta}_{LWR}$ that can reject the null hypthesis of $\beta =0$.\\ Column (6) displays the proportion of Monte Carlo simulations with larger standard deviations of the LWR coefficients than $\sigma_{\hat{\beta}}$}
 \end{table}
@@
 
-\subsection{Does Space Matter?}
+\subsection{How Does the Hedonic Function Vary over Space?}
 We believe the use of a LWR estimation procedure is appropriate after conducting two different Monte Carlo simulations with the data.
@@
 
-\subsection{Do the Regression Coefficients Vary over Time}
+\subsection{Does Traffic Noise Penalty Change over Time?}
 
-We know that house prices fell dramatically during and after the Great Recession of 2008-09.
+Previous research has suggested that the impact of noise can change with time and economic conditions.
+For instance, \citet{Wilhelmsson2000} found that the traffic noise penalty to be stronger in the 1990s near Stockholm, Sweden compared to the 1980s.
+\citet{Cohen2009} also found the (airport) noise penalty to be larger in the early 2000s compared to the late 1990s in Atlanta, Georgia.
+We know that house prices in the United States fell dramatically during and after the Great Recession of 2008-09.
 We know less about the patterns of change in the hedonic price functions during and after the fall in prices.
-For instance, did all house prices simply drop (mostly affecting the intercept term of the hedonic function), or did the implicit price of structural characteristics like the size of the house or its lot decrease, or perhaps the value of environmental amenities disproportionately dropped?
-This section presents some of the first evidence of how the hedonic price function for housing changed over time surrounding the Great Recession of 2008-09.
-We ask whether the LWR coefficients exhibit a temporal pattern.
+\citet{Cho2011b} found evidence from hedonic analysis in the Nashville, Tennessee area that consumers' willingness to pay for environmental amenities (such as proximity to open space and water views) decreased during the recession as compared to the previous economic boom.
 
+In this section we look for evidence of temporal non-stationarity in the hedonic coefficient on traffic noise within our data.
 Specifically, we create two new variables, ``\texttt{months since September 2008}'' and a dummy variable ``\texttt{post}'' for all sales after September 2008.
-We then regress our LWR coefficients on these two variables and their interaction term as shown in equation \eqref{eq:LWRinteraction}.
+We then regress our LWR noise coefficients on these two variables and their interaction term as shown in equation \eqref{eq:LWRinteraction},
 \begin{equation}\label{eq:LWRinteraction}
-\hat{\beta}_{LWR} = \alpha _0 + \alpha _1 \texttt{*month} + \alpha _2  \texttt{*post} + \alpha _3 \texttt{*post*month} + \epsilon
+\hat{\beta}_{LWR} = \alpha _0 + \alpha _1 \texttt{*month} + \alpha _2  \texttt{*post} + \alpha _3 \texttt{*post*month} + \epsilon.
 \end{equation}
-
-The results of these regressions will help us understand the patterns of change in the hedonic price of different characteristics.
-In particular, significant values for $\hat{\alpha}_2$ suggest that there was a structural break in the LWR coefficients post September 2008, and significant values for $\hat{\alpha}_3$ will imply a difference in the temporal trend of the LWR coefficients.
-
-Note that the tables have not yet been formatted.
-
-\subsubsection{Traffic Noise}
-
-We know of no published research that shows how the hedonic price estimates of traffic noise vary over time surrounding the Great Recession.
-In this section we show that accounting for the month of the house sale significantly predicts to the estimated LWR coefficients for traffic noise.
+The results of this regression will help us understand the patterns of change in the implicit price of traffic noise.
+In particular, $\hat{\alpha}_1 \neq 0$ suggests a linear temporal trend in the marginal willingness to pay to avoid traffic noise, while $\hat{\alpha}_2 \neq 0$ suggests that there was a structural break after September 2008, and $\hat{\alpha}_3 \neq 0$ will imply a change in the temporal trend after September 2008.
 The linear regression results presented in Table \ref{tab:betaMAX} show that there is a significant negative shock to the estimated LWR coefficients for traffic noise after September 2008.
@@
 \begin{verbatim}
-(Intercept) -1.781e-03  4.100e-05 -43.436  < 2e-16 ***
-month        6.982e-06  2.005e-06   3.482 0.000498 ***
-Post        -7.998e-04  7.209e-05 -11.094  < 2e-16 ***
-month:Post  -8.868e-05  4.484e-06 -19.776  < 2e-16 ***
+            Estimate Std. Error t value Pr(>|t|)   
+(Intercept) -1.7e-03   4.1e-05   -43.4   < 2e-16 ***
+Month        6.9e-06   2.0e-06     3.5  0.000498 ***
+Post        -8.0e-04   7.2e-05   -11.1   < 2e-16 ***
+Month*Post  -8.9e-05   4.5e-06   -19.7   < 2e-16 ***
 ---
@@
 
-The results in Table \ref{tab:betaMAX} contradict the a priori assumption that environmental amenities will ``matter'' less during and after the Great Recession.
+The results in Table \ref{tab:betaMAX} contradict the a priori expectation that environmental amenities will ``matter'' less during and after the Great Recession.
 In fact, these results suggest that the penalty for homes exposed to higher levels of traffic noise increased.
@@
 
-\subsubsection{House Size}
-
-In this section we show how the hedonic coefficients on house size (as measured in square feet) change over time.
+% \subsubsection{House Size}
+% 
+% In this section we show how the hedonic coefficients on house size (as measured in square feet) change over time.
 Table \ref{tab:betaSQFT} shows that the LWR coefficients on house size were positive and trending up before September 2008, then the coefficients drop significantly in both absolute value and their time trend.
@@
 
-Some researchers, such as \citet{Theebe2004a} conclude that the impact of traffic noise is non-linear in the level of the noise, while others, such as \citet{Huang;Palmquist2001} report a constant impact per decibel increase.
-In this section we compare the mean LWR noise coefficient estimates across noise levels to look for non-linearities in the impact of traffic noise.
+Some researchers conclude that the semi-elasticity of noise varies with the level of noise \citep{Andersson2010, MarmolejoDuarteCarlos;GonzalezTamez2009, Theebe2004a, Miedema2001, Wilhelmsson2000}, such as a ``threshold''' effect at 70dB \citep{Wilhelmsson2000, Cohen2009}.
+Other researchers report no evidence of varying impacts at higher or lower noise intensities \citep{Blanco2011, Baranzini2010, Kim2007, Huang;Palmquist2001}.
+In this section we compare our mean LWR noise coefficient estimates across noise levels to look for threshold effects of traffic noise.
 
@@
 
-Table \ref{tab:LWRnonlinear} estimates the predicted LWR noise coefficient as a linear function of the noise level in decibels and whether or not the sale took place before or after September 2008.
-The table reveals no statistically measurable linear relationship between the noise coefficient for sales before September 2008 and the level of the noise (that is, the marginal effect is no different at low levels of noise than at high levels of noise).
+Table \ref{tab:LWRnonlinear} reports the results of a simple linear regression of the LWR noise coefficients on the noise levels and whether or not the sale took place before or after September 2008 (as well as their interaction).
+The table reveals no statistically measurable linear relationship between the noise coefficient and the noise level for sales before September 2008.
+That is, the semi-elasticity is no different in our data at low levels of noise than at high levels of noise.
 The positive and significant interaction term suggests that the impact may be different for high vs.
-low levels of noise post-September 2008, but the difference in the predicted marginal effects is so small, that it works about to be a roughly \$25 difference for a \$300,000 house at 50 vs.
+low levels of noise post-September 2008, but the difference in the predicted marginal effects is so small that it works about to be a roughly \$25 difference for a \$300,000 house at 50 vs.
 75 dB.
+Thus, while other researchers report finding impact thresholds at 70dB, we cannot corroborate such findings with our data.
 
@@
 Our work suffers from at least two noticeable weaknesses.
-First, we are missing some important structural variables that are commonly used in the real estate hedonic literature.
+First, we are missing some important structural variables that are commonly used in the housing hedonic literature.
 To the extent that structural variables like the number of bedrooms, bathrooms, garage size, or construction quality covary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias.
 We are somewhat comforted, however, because we do have some additional variables for a subset of our data.
-We have the number of bedrooms, bathrooms, and garage area for our houses located within Dakota County.
+We obtained the number of bedrooms, bathrooms, and garage area for our houses located within Dakota County from the Dakota County Assessor's Office.
 Our analysis (Models 1, 2, and 3 described earlier) was repeated on this geographic subset of the data and the results were compared to the estimates obtained from the same analysis when these additional structural variables were omitted.
@@
 \begin{center}
-\caption{Mean and (Standard Deviation) LWR Noise Coefficients in Dakota County both with and without the additional structural variables available only for the county.}\label{tab:Dak}
-\begin{tabular}{lll}
- & \multicolumn{2}{c}{Additional variables?} \\
-Locally Weighted Regression Model & \multicolumn{1}{c}{no} & \multicolumn{1}{c}{yes} \\ \hline
-Model (1) = Structural Variables & -0.00149 & -0.00147 \\ 
-   & (0.00226) & (0.00309) \\ 
-Model (2) = (1) + Locational Variables & -0.00136 & -0.00140 \\ 
-   & (0.00184) & (0.00218) \\ 
-Model (3) = (2) + City Fixed Effects & -0.00140 & -0.00137 \\ 
-   & (0.00219) & (0.00176) \\ 
+\caption{A Comparison of the Noise Regression Coefficient Estimates in Dakota County with and without Additional Structural Variables}\label{tab:Dak}
+\begin{tabular}{lllc}
+ & \multicolumn{2}{p{1.25in}}{Additional Variables Included in LWR?} & \\
+Locally Weighted Regression Model & \multicolumn{1}{c}{no} & \multicolumn{1}{c}{yes} & \\ \cline{1-3}
+Model (1) = Structural Variables & -0.0015 & -0.0015 & mean\\ 
+   & (0.0023) & (0.0031) & (st.\ dev.) \\ 
+Model (2) = Model (1) + Locational Variables & -0.0014 & -0.0014  & \\ 
+   & (0.0018) & (0.0022) &  \\ 
+Model (3) = Model (2) + City Fixed Effects & -0.0014 & -0.0014 & \\ 
+   & (0.0022) & (0.0018) & \\ 
 \end{tabular}
@@
 Table \ref{tab:Dak} shows that the traffic noise coefficients estimated by our LWR models are similar regardless of whether the additional structural variables were included or not.
-Welch two-sample t-tests fail to reject the null hypothesis of zero means across our three models (comparing LWR estimates with vs.
+Welch two-sample t-tests fail to reject the null hypothesis of zero mean differences across our three models (comparing LWR estimates with vs.
 without the additional structural variables included in the model).
 Paired t-tests find differences for Model 2 and 3, but the estimated differences are zero to four decimal places and in one case the noise impact estimates with the additional variables are slightly larger and in the other case they are slightly smaller.
-We also conducted simple linear egressions of the noise coefficients without the additional structural variables on the noise coefficients obtained with the additional structural variables.
-In all three cases the intercept estimates were close zero with slopes almost exactly equal to one and each also had $R^2$ values over 0.7.
+We also conducted simple linear regressions of the noise coefficients without the additional structural variables on the noise coefficients obtained with the additional structural variables for each of our three models.
+In all cases the intercept estimates were close zero with slopes almost exactly equal to one and each also had $R^2$ values over 0.7, signifying that the hedonic coefficients for the traffic noise variable are unaffected by omitted variable bias from common structural variables.
+While we cannot confirm that this lack of ommitted variable bias also occurs elsewhere in our data, the results from Dakota County are promising.
 
@@
 To the extent that traffic flows and composition signicantly changed over time, our traffic noise variables may be inaccurate for those time periods.
-For instance, the US Department of Transportation reports that total vehicle miles travelled decreased by up to 2 percent year-on-year during the Great Recession.
-Thus, our noise estimates may be inaccurate for later time periods and this may bias our estimates of the impact of noise on house values.
-Future work may better estimate the impact of traffic noise over time by generating noise data to reflect changing traffic patterns.
-
-What other weaknesses should we discuss?
-
-We didn't explicitly model spatial autocorrelation in the error terms.
-
-We might want to further reduce the number of parameters to estimate through the use of either mixed-LWR or running separate regressions for submarkets determined through hierarchical clustering like \citet{Day2003}.
+For instance, the US Department of Transportation reports that total vehicle miles travelled decreased by up to 4 percent year-on-year during the Great Recession.\footnote{\url{http://www.fhwa.dot.gov/ohim/tvtw/08dectvt}} Thus, our noise estimates may be inaccurate for later time periods and this may bias our estimates of the impact of noise on house values.
+Future work may seek to obtain time-series noise data in order to obtain even better estimates of the impact of traffic noise over time.
+Given the computational complexity of re-estimating the landscape noise surface, such work is beyond the scope of this paper.
 
@@
 
-We estimated the impact of traffic noise on housing prices using Locally Weighted Regression techniques in the St.\ Paul, MN metropolitan area.
-Specifically, we estimate linear regressions at each house within our dataset using only information contained in geographically nearby houses sold within the last 12 months.
-We find strong evidence that the hedonic function in our study area differs over space and time.
-Local regressions using only information contained in the nearest 200 houses generate a substantially smaller Generalized Cross Validation score (0.266) compared to the same model assuming geographical stationarity in the regression coefficients (0.401).
+We estimated the impact of traffic noise on housing prices using Locally Weighted Regression techniques in the St.\ Paul, Minnesota urban area.
+Specifically, we estimate semi-logarithmic regressions at each house within our dataset using only information contained in ``local'' house sales (where local is defined both geographically and temporally).
+We find strong evidence that the hedonic function in our study area varies over space and time.
 
-Monte Carlo simulations suggest that the better goodness-of-fit provided by the local models are not due to chance and that many hedonic impact estimates vary over space within our study area.
-When the location of our data was randomly assigned and our LWR model was re-estimated, in 100 consecutive simulations the smallest GCV score was  obtained when the data were analyzed at a global level rather than local.
-Additionally, re-estimating the LWR model using a local bandwidth of 200 nearest house sales when the location was randomly assigned yielded substantially smaller standard deviations for the majority of our regression coefficients.
-This larger variation within our true data suggests spatial non-stationarity in the regression coefficients.
+Monte Carlo simulations suggest that the better goodness-of-fit provided by the local models are not due to chance and that many hedonic implicit prices vary over space within our study area.
+When the location of our data was randomly assigned and our LWR model was re-estimated across more than a dozen diferent bandwidths, in 100 consecutive simulations the smallest GCV score was obtained when the data were analyzed at a pooled/global level rather than local.
 That is, after trying thousands of different combinations of varying levels of local analysis with the spatially redistributed data, we never came close to estimating our observed housing sales prices as well as we can with the local analysis on the actual data.
+Additionally, re-estimating the LWR model using a local bandwidth of 200 nearest house sales but randomly assigned locations yielded substantially smaller standard deviations for the majority of our regression coefficients.
+Such differences suggest that the variation exhibited by most of our regression coefficients was not due to simple random chance, but instead is consistent with spatial non-stationarity.
 
@@
 Lastly, after controlling for the Great Recession, we find no significant differences in the impact of traffic noise across the range of commonly seen noise levels (50-70 dB).
+
+Finally, the results of this work suggest multiple areas of fruitful future research to better help policymakers weigh the costs and benefits of traffic noise.
+First, we suggest research be conducted in more housing markets, as the potential to apply the results of analysis in one set of geographical and economic circumstances may be limited.
+Second, ``mixed'' regression techniques (in which some regression coefficients are constrained to remain constant across the study area while others are alowed to vary) may allow researchers to obtain more precise estimates of the impact of hedonic characteristics by increasing the degrees of freedom in the regression.
+As mentioned previously, future work may also seek to re-estimate traffic noise models over time to better account for changes in traffic flows associated with macroeconomic conditions.
+Lastly, researchers may want to take advantage of the findings of \citet{Carruthers2010} and use the spatial variation in regression coefficients to help estimate the second-stage hedonic regressions to identify consumer demand curves for these characteristics.
 

### 2013-08-30 reports/Draft.Rnw
continued progress on draft

@@
 \usepackage[round]{natbib}
-\usepackage{caption, amsmath, graphicx, hyperref}
+\usepackage{caption, amsmath, graphicx, hyperref, setspace, multirow, color}
 
@@
 
+\doublespacing
 \begin{document}
 \maketitle
-
+\begin{singlespace}
 \begin{abstract}
-This paper implements the hedonic price method to estimate the impact of traffic noise on properties within the St.\ Paul, Minnesota metropolitan real-estate market over the time period from 2005 - 2010.
-We use Locally Weighted Regression (LWR) estimation techniques in order to allow the hedonic function to vary over time and space.
-Significant evidence suggests spatial and temporal non-stationarity in the hedonic price function within our study area.
-In contrast to previous research, however, we find little evidence that the price semi-elasticity of traffic noise varies with the decibel level of the traffic noise, nor does the impact seem to exhibit spatial non-stationarity.
-We find significant differences in the impact of traffic noise from the beginning to the end of our sample.
-Our results suggest that an increase in traffic noise of one decibel decreases house prices by an average of 0.19 percent before September, 2008, and an average of 0.37 percent after September, 2008.
-While significantly different, both of these estimates are still within the typical range of previous estimates in the literature.
+One consequence of the expanding road network and its associated traffic is increased levels of traffic noise.
+While the hedonic literature has consistently shown a negative effect of this phenomenon on the real estate market, the relationship between housing prices and automobile traffic noise has rarely been explored at landscape level, especially in the United States.
+Here, we show this relationship by modeling the propagation of traffic noise over the landscape and by analyzing the extent of its impact on single-family home transactions in the urban area surrounding St.
+Paul, Minnesota using spatially explicit local regression techniques.
+Our estimate of the negative relationship between traffic noise levels and house prices are smaller in magnitude than most of the relevant published literature.
+We find no evidence that the effect of traffic noise varies significantly by geography, nor by traffic noise levels.
+We find significant differences in the impact of traffic noise before and after the economic recession of 2008-09.
+Our results suggest that an increase in traffic noise of one decibel decreases house prices by an average of 0.19 percent before September 2008, and an average of 0.37 percent after September 2008.
 \end{abstract}
+\end{singlespace}
 
 \section{Introduction and Past Research}\label{sec:lit}
-Prolonged exposure to traffic noise affects people in a number of ways, ranging from simple annoyance \citep{Weinhold2013, Miedema2001} (Miedema and Oudshoorn 2001; Ouis 2001), to sleep disturbance (Netherlands 2004), to increasing risk for stroke (Sorensen, Hvidberg et al.
+Prolonged exposure to traffic noise affects people in a number of ways, ranging from simple annoyance \citep{Weinhold2013, Miedema2001} (Ouis 2001), to sleep disturbance (Netherlands 2004), to increasing risk for stroke (Sorensen, Hvidberg et al.
 2011), hypertension(Jarup, Babishch et al.
@@
 We obtained data from approximately forty thousand sales transactions between 2005 and 2010 (n=42,095) from the 2010 MetroGIS Regional Parcel Dataset published by the Metropolitan Council.
-In addition to the geographic location and date of the house sale, we collected structural and locational variables commonly used in the hedonic literature.
-Table \ref{tab:sumStats} provides a brief description of the variables and some basic summary statistics.
+In addition to the geographic location and date of the house sale, we collected or created structural and locational variables commonly used in the hedonic literature.
+Table \ref{tab:sumStats} provides a brief description of the variables in our data and some basic summary statistics.
 Figure \ref{fig:overview} shows an overview of the study area as well as the spatial distribution of the house sales prices.
@@
 \begin{figure}
-\includegraphics[width = \textwidth]{../graphs/StudyArea_SaleValueDistribution}
+\makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/StudyArea_SaleValueDistribution}}
 \caption{This figure shows the spatial extent of our study area as well as the significant spatial variation in single family house sales prices.}\label{fig:overview}
@@
   Sale Price (thousands \$) & 98.8 & 195.0 & 241.0 & 265.5 & 314.9 & 675.0 & 102.8 \\ 
-  House Size (thousands square feet) & 390 & 1158 & 1628 & 1750 & 2188 & 4000 & 704 \\ 
+  House Size (feet$^2$) & 390 & 1158 & 1628 & 1750 & 2188 & 4000 & 704 \\ 
   Lot Size (acres) & 0.02 & 0.17 & 0.25 & 0.25 & 0.31 & 0.60 & 0.11 \\ 
-  Owner Occupancy Dummy & 0.0 & 1.0 & 1.0 & 0.8 & 1.0 & 1.0 & 0.4 \\ 
-  Year House was Built & 1850 & 1950 & 1973 & 1967 & 1993 & 2010 & 32 \\ 
+  Owner Occupancy (no = 0, yes = 1) & 0.0 & 1.0 & 1.0 & 0.8 & 1.0 & 1.0 & 0.4 \\ 
+  Year of House Construction & 1850 & 1950 & 1973 & 1967 & 1993 & 2010 & 32 \\ 
   Traffic Noise (dB) & 25.1 & 50.5 & 55.3 & 56.4 & 62.2 & 91.5 & 8.8 \\ 
   Median Income in Census Tract (thousands \$) & 13.9 & 54.6 & 69.1 & 72.6 & 89.7 & 143.3 & 23.6 \\ 
-  Elementary Test Scores & 335.6 & 359.8 & 365.4 & 364.5 & 370.4 & 551.7 & 10.6 \\ 
+  Average 3rd Grade Standardized Test Scores & 335.6 & 359.8 & 365.4 & 364.5 & 370.4 & 551.7 & 10.6 \\ 
   Distance to Central Business District (km) & 1.1 & 6.8 & 13.2 & 14.7 & 21.8 & 37.1 & 8.9 \\ 
@@
 \begin{table}
-\caption{Pearson Correlation Coefficient Matrix of Quantitative Variables}\label{tab:cor}
+\caption{Matrix of Pearson Correlation Coefficients for Quantitative Variables}\label{tab:cor}
 \includegraphics[width = \textwidth]{../graphs/CorrelationMatrix}
@@
 In addition to the noticeable decline in nominal sales values, there is also a drop in the number of sales across years.
-For example, in 2010 there were only 4,206 property sales within the dataset, a more than 50\% reduction from 2005.
+For example, in 2010 there were only 4,206 property sales within the dataset, a more than 50 percent reduction from 2005.
 While the mean sale price declined from roughly \$280,000 pre-crash to \$230,000 post-crash, most of the structural and neighborhood variables are relatively consistent across years.
@@
 Table \ref{tab:globalRegression} also attempts to begin to understand how the economic recession may have influenced the hedonic function in our study area.
-The other columns in the table show the regression output from separating the data into sales before and after September of 2008 (the month that the US Federal government took over Fannie Mae and Freddie Mac, Lehman Brothers filed for bankruptcy, and the American International Group (AIG) narrowly avoided bankruptcy only through a \$85 billion loan from the US Federal government).
-The coefficients for some of the hedonic variables of interest (noise, schools, land, for instance) appear different across the two time periods.
+The other columns in the table show the regression output from separating the data into sales before and after September of 2008 (the month that the US Federal government took over Fannie Mae and Freddie Mac, Lehman Brothers filed for bankruptcy, and the American International Group (AIG) narrowly avoided bankruptcy only through a \$85 billion loan from the US Federal government).\footnote{\url{http://www.federalreserve.gov/newsevents/press/other/20080916a.htm}} The coefficients for some of the hedonic variables of interest (noise, schools, land, for instance) appear different across the two time periods.
 
@@
 \section{Locally Weighted Regression Model}
-Locally Weighted Regression (LWR) techniques (also known as Geographically Weighted Regression) are described in detail by \citet{Brunsdon1998b}.
+Locally Weighted Regression (LWR) techniques (also known as Geographically Weighted Regression) are described in detail by \citet{Cleveland1988}, \citet{Brunsdon1998b}, \citet{Fotheringham2002}, and others.
 It is a weighted least squares methodology in which regression coefficients are estimated over space as a function of the local data as described in Equation~\eqref{eq:LWRbeta},
@@
 These results suggest that it is important to model our data in a spatially explicit manner.
-
-Regression output from a LWR model is voluminous in comparison to a standard regression model, as coefficients are estimated at each location within the dataset.
-We report our results in a manner similar to \citet{MarmolejoDuarteCarlos;GonzalezTamez2009}.
-Table \ref{tab:mainresults} displays the results of LWR Model 3 and the similar global regression model.
-Again, note that the LWR model yields a substantially smaller GCV score (0.027 vs.
-0.041).
+Table \ref{tab:mainresults} displays a summary of the results of LWR Model 3 and a similar regression model run without allowing for spatial variation in the regression coefficients.
+Again, note that the LWR model yields a substantially smaller GCV score (0.027 vs.\ 0.041).
 
@@
 }
- \caption*{\small Column (5) displays the proportion of $\hat{\beta}_{LWR}$ that can reject the null hypthesis of $\beta =0$.\\ Column (6) displays the proportion of Monte Carlo simulations with larger standard deviations of the LWR coefficients than $\sigma_{\hat{\beta}}$}
+ \caption*{\footnotesize Column (5) displays the proportion of $\hat{\beta}_{LWR}$ that can reject the null hypthesis of $\beta =0$.\\ Column (6) displays the proportion of Monte Carlo simulations with larger standard deviations of the LWR coefficients than $\sigma_{\hat{\beta}}$}
 \end{table}
@@
 Column (5) in Table \ref{tab:mainresults} shows the percentage of the local regressions for which the coefficient's p-value is less than 0.1.
-All regressions contained statistically significant estimates of the impact of increased living space, and a majority contained significant estimates for lot size and year of construction.
+All regressions contained statistically significant estimates of the impact of increased living space and a majority contained significant estimates for lot size and year of construction.
 Roughly half of the regressions estimated an impact of traffic noise statistically different from zero, while approximately one-third of the local regressions estimated statistically significant estimates of the locational variables (school test scores, census tract median income, distance to local amenities).
@@
 
-\subsection{How Does the Hedonic Function Vary over Space?}
-We believe the use of a LWR estimation procedure is appropriate after conducting two different Monte Carlo simulations with the data.
-In each simulation we resampled (without replacement) the location of each house in the study and then re-estimated the LWR model with the resampled data.
-In the first simulation we estimated the LWR model using bandwidths ranging from the nearest 50 to 10,000 sales as before.
+\subsection{Does the Hedonic Function Vary over Space?}
+We believe the use of a LWR estimation procedure is appropriate after conducting two different Monte Carlo simulations with the data as described in \citet{Fotheringham2002}.
+In each simulation we resampled (without replacement) the location of each house in the study and then re-estimated the LWR model with the locationally ``shuffled'' data.
+In the first simulation we estimated the LWR model using bandwidths ranging from the nearest 50 to 10,000 sales just as before.
 In 100 consecutive simulations, the smallest Generalized Cross-Validation score was obtained at the largest bandwidth.
 The smallest of these GCV scores was 0.041, just as was the case with the global (non-LWR) model.
-In other words, the LWR model never performed better than the global model when the locations of the data were randomized.
+In other words, after running thousands of regressions on the shuffled data, we never obtained results anywhere near LWR model with our true locational data.
 This seems to be strong evidence that the increased ability to predict house prices with a local model is not due to chance.
 
-Second, we ran a Monte Carlo simulation as described in \citet{Fotheringham2002} and performed in a similar context by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009}. The simulation is as follows:
-\begin{enumerate}
-\item Sample with replacement the location of each data point within the study. (just as in the previous simulation)
-\item Estimate a Locally Weighted Regression model on the sampled data \emph{using the optimal bandwidth calculated in original LWR model.}
-\item Calculate the mean coefficient estimates as well as the standard deviation of the estimates from the sampled data LWR estimates.
-\item Repeat Steps 1.--3. $M$ times.
-\end{enumerate}
-After 100 iterations of this simulation, the minimum GCV score for these resampled LWR models is 0.060, substantially larger than all models (global and local) with the actual data.
-Again, this seems to suggest that our data exhibit spatial non-stationarity in the regression coefficients.
+In the previous simulation we found that the hedonic regression function indeed exhibits spatial non-stationarity.
+However, we have not yet established which variables have spatially varying coefficients.
+In the second simulation, we seek to explore which of the hedonic regression coefficients exhibit spatial non-stationarity.
+We repeat the Monte Carlo simulation described earlier, but only at the optimal bandwidth calculated in original LWR model and we also kept track of the standard deviation of the estimated LWR coefficients for each variable.
+The intuition of the simulation is as follows: a variable might truly exert a spatially stationary effect on house prices, but our estimates vary over space due to chance.
+If this is the case, by shuffling the location of our observations and rerunning the LWR model, we should see a similar dispersion in regression coefficients over space.
+However, if the coefficient exhibits true spatial non-stationarity, it is unlikely that we will see as large of a standard deviation in the coefficient estimates after having reshuffled the data (because now the houses for which a coefficient exerts a strong effect are now no longer near each other).
 
-We are also interested in the standard deviation of our estimated LWR coefficients (the fourth column in Table \ref{tab:mainresults} as compared to the distribution of simulated standard deviations.
-If the standard deviation of the LWR estimates with the true data is larger than the standard deviations from the simulations, this is interpretted as evidence of spatial non-stationarity in the coefficients.
-The intuition is as follows.
-Imagine that the coefficients are constant across space.
-Then, running local regressions will yield different coefficient estimates across space, not because the coefficients are truly different over space, but purely due to chance and noise in the data.
-Resampling the location of the data and estimating LWR models repeatedly will generate a distribution of how much the coefficients will vary across space due to chance.
-However, if the standard deviation of the LWR coefficients is larger than the standard deviations seen from the resampled data, this is consistent with the hypothesis that the coefficients vary over space more than they would due to random chance and noise within the data.
-
-The results of the second Monte Carlo simulation are presented in column (6) of Table \ref{tab:mainresults}.
-Column (6) displays the probability of obtaining a larger standard deviation of LWR coefficient estimates based on the 100 simulations performed.
+After $M = 100$ iterations of this simulation, the minimum GCV score for these resampled LWR models is 0.060, substantially larger than all models (global and local) with the actual data.
+The fourth column in Table \ref{tab:mainresults} displays the standard deviations of the LWR regression coefficients obtained with our data.
+Column (6) displays the proportion of Monte Carlo simulatons that yielded larger standard deviations of LWR coefficient estimates than those shown in column (4).
 For most variables, we never obtained a larger coefficient standard deviation in the simulation than we obtained from the LWR model with the actual data.
@@
 \begin{figure}
- \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{../graphs/CopyOfMCsimResultsSDs}}
- \caption{The Monte Carlo Simulation Distribution of LWR Coefficient Standard Deviations and True Coefficient Standard Deviations.}\label{fig:MCsds}
+ \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{../graphs/MCsimResultsSDsClean}}
+ \caption{Actual LWR Coefficient Standard Deviations \textcolor{red}{(red line)} vs.\ Distribution of Monte Carlo Simulation Standard Deviations by Variable.}\label{fig:MCsds}
 \end{figure}
@@
 
-\subsection{Does Traffic Noise Penalty Change over Time?}
+\subsection{Does the Implicit Price of Traffic Noise Change over Time?}
 
@@
 \begin{equation}\label{eq:LWRinteraction}
-\hat{\beta}_{LWR} = \alpha _0 + \alpha _1 \texttt{*month} + \alpha _2  \texttt{*post} + \alpha _3 \texttt{*post*month} + \epsilon.
+\hat{\beta}_{LWR} = \alpha _0 + \alpha _1 \texttt{*Month} + \alpha _2  \texttt{*Post} + \alpha _3 \texttt{*Post*Month} + \epsilon.
 \end{equation}
 The results of this regression will help us understand the patterns of change in the implicit price of traffic noise.
-In particular, $\hat{\alpha}_1 \neq 0$ suggests a linear temporal trend in the marginal willingness to pay to avoid traffic noise, while $\hat{\alpha}_2 \neq 0$ suggests that there was a structural break after September 2008, and $\hat{\alpha}_3 \neq 0$ will imply a change in the temporal trend after September 2008.
+In particular, $\alpha_1 \neq 0$ suggests a linear temporal trend in the marginal willingness to pay to avoid traffic noise, while $\alpha_2 \neq 0$ suggests that there was a structural break after September 2008, and $\alpha_3 \neq 0$ will imply a change in the temporal trend after September 2008.
 The linear regression results presented in Table \ref{tab:betaMAX} show that there is a significant negative shock to the estimated LWR coefficients for traffic noise after September 2008.
@@
 \begin{table}
-\caption{LWR Coefficients vs. Noise Levels}\label{tab:LWRnonlinear}
+\caption{LWR Noise Coefficients vs.\ Noise Levels}\label{tab:LWRnonlinear}
 \begin{verbatim}
             Estimate Std. Error t value Pr(>|t|)    
-(Intercept) -1.748e-03  1.314e-04 -13.301   <2e-16 ***
-Noise       -2.760e-06  2.267e-06  -1.218    0.223    
-Post        -3.553e-03  2.198e-04 -16.165   <2e-16 ***
-Noise:Post   3.386e-05  4.006e-06   8.453   <2e-16 ***
+(Intercept) -1.75e-03  1.31e-04  -13.3   <2e-16 ***
+Noise       -2.76e-06  2.27e-06   -1.2    0.223    
+Post        -3.55e-03  2.20e-04  -16.2   <2e-16 ***
+Noise:Post   3.39e-05  4.01e-06    8.5   <2e-16 ***
 ---
@@
 
-Residual standard error: 0.002829 on 31744 degrees of freedom
+Residual standard error: 0.002829 on 31,744 degrees of freedom
 Multiple R-squared: 0.08329,  Adjusted R-squared: 0.08321 
@@
 That is, the semi-elasticity is no different in our data at low levels of noise than at high levels of noise.
-The positive and significant interaction term suggests that the impact may be different for high vs.
-low levels of noise post-September 2008, but the difference in the predicted marginal effects is so small that it works about to be a roughly \$25 difference for a \$300,000 house at 50 vs.
-75 dB.
+The positive and significant interaction term suggests that the impact may be different for high vs.\ low levels of noise post-September 2008, but the difference in the predicted marginal effects is so small that it works about to be a roughly \$25 difference for a \$300,000 house at 50 vs.\ 75 dB.
 Thus, while other researchers report finding impact thresholds at 70dB, we cannot corroborate such findings with our data.
@@
 We categorize the traffic noise data in 5 dB wide bins like \citet{Theebe2004a} and then estimate the mean LWR traffic noise coefficients in each category while also controlling for whether the sales took place pre- or post-September 2008.
-We see little to suggest any meaningful non-linearities in the effect of traffic noise on house prices, once we have controlled for the timing of the sales.
+We see little to suggest any meaningful non-linearities in the regression coefficients of traffic noise on house prices, once we have controlled for the timing of the sales.
 
@@
 \makebox[\textwidth][c]{\includegraphics[width = 1.1\textwidth]{../graphs/LWRbetaMAXbyCatTime}}
-\caption{The mean LWR traffic noise coefficient by 5 decibel category and pre- vs.
-post-September 2008.
+\caption{The mean LWR traffic noise coefficient by 5 decibel category and pre- vs.\ post-September 2008.
 The vertical lines denote the standard error of the estimated mean by time and level category.
@@
 Locally Weighted Regression Model & \multicolumn{1}{c}{no} & \multicolumn{1}{c}{yes} & \\ \cline{1-3}
-Model (1) = Structural Variables & -0.0015 & -0.0015 & mean\\ 
-   & (0.0023) & (0.0031) & (st.\ dev.) \\ 
-Model (2) = Model (1) + Locational Variables & -0.0014 & -0.0014  & \\ 
-   & (0.0018) & (0.0022) &  \\ 
-Model (3) = Model (2) + City Fixed Effects & -0.0014 & -0.0014 & \\ 
+\multirow{2}{*}{Model (1) = Structural Variables} & -0.0015 & -0.0015 & mean\\ 
+   & (0.0023) & (0.0031) & (st.\ dev.) \\[.2cm]
+\multirow{2}{*}{Model (2) = Model (1) + Locational Variables} & -0.0014 & -0.0014  & \\ 
+   & (0.0018) & (0.0022) &  \\[.2cm] 
+\multirow{2}{*}{Model (3) = Model (2) + City Fixed Effects} & -0.0014 & -0.0014 & \\ 
    & (0.0022) & (0.0018) & \\ 
@@
 Table \ref{tab:Dak} shows that the traffic noise coefficients estimated by our LWR models are similar regardless of whether the additional structural variables were included or not.
-Welch two-sample t-tests fail to reject the null hypothesis of zero mean differences across our three models (comparing LWR estimates with vs.
-without the additional structural variables included in the model).
+Welch two-sample t-tests fail to reject the null hypothesis of zero mean differences across our three models (comparing LWR estimates with vs.\ without the additional structural variables included in the model).
 Paired t-tests find differences for Model 2 and 3, but the estimated differences are zero to four decimal places and in one case the noise impact estimates with the additional variables are slightly larger and in the other case they are slightly smaller.
@@
 We do, however, find significant temporal variation in the impact of traffic noise in our data.
-The estimated impact of one additional decibel of traffic noise is a 0.19 percent reduction in the sale price of houses before September 2008, vs.
-0.37 percent after September 2008.
+The estimated impact of one additional decibel of traffic noise is a 0.19 percent reduction in the sale price of houses before September 2008, vs.\ 0.37 percent after September 2008.
 Lastly, after controlling for the Great Recession, we find no significant differences in the impact of traffic noise across the range of commonly seen noise levels (50-70 dB).

### 2013-09-11 reports/Draft.Rnw
Draft2013-08-29.pdf to Tsegaye
updated bibliography and worked on lit and noise sections

@@
 \usepackage[round]{natbib}
-\usepackage{caption, amsmath, graphicx, hyperref, setspace, multirow, color}
+\usepackage{caption, amsmath, graphicx, setspace, multirow, color, hyperref}
 
@@
 \section{Introduction and Past Research}\label{sec:lit}
-Prolonged exposure to traffic noise affects people in a number of ways, ranging from simple annoyance \citep{Weinhold2013, Miedema2001} (Ouis 2001), to sleep disturbance (Netherlands 2004), to increasing risk for stroke (Sorensen, Hvidberg et al.
-2011), hypertension(Jarup, Babishch et al.
-2008; Bodin, Albin et al.
-2009), and myocardial infarction (Babisch, Beule et al.
-2005).
+Prolonged exposure to traffic noise affects people in a number of ways, ranging from simple annoyance \citep{Miedema2001, Ouis2001, Ohrstrom2007, DeKluizenaar2013, Weinhold2013}, to sleep disturbance \citep{Netherlands2004}, to increasing risk for stroke \citep{Sorensen2011}, hypertension \citep{Jarup2008, Bodin2009}, myocardial infarction \citep{Babisch2005}, and overall quality of life \citep{Shepherd2013}.
 The noise level at which such effects are observed does not have to be high.
-It has been shown that people exposed to traffic noise with a 24-hour average of 55 dBA are found to be at a higher risk for hypertension (Barregard, Bonde et al.
-2009; Bodin, Albin et al.
-2009), and those exposed to 60 dBA or greater are found to be at a higher risk for stroke (Sorensen, Hvidberg et al.
-2011).
-This impact is expected to grow worse with the increasing number of vehicles in the urban road network and the diminishing number of night-time quiet hours unless mitigating measures are put in place (XXX).
-Given that much of this increased exposure occurs in areas where people live and work any mitigating measures must be based on a cost-benefit analysis.
+It has been shown that people exposed to traffic noise with a 24-hour average of 55 decibels (dBA) are found to be at a higher risk for hypertension \citep{Barregard2009, Bodin2009}, and those exposed to 60 dBA or greater are found to be at a higher risk for stroke \citep{Sorensen2011}.
 
-An important first step towards such an analysis is to examine real estate price fluctuations as a function of noise levels using hedonic regression.
-\citet{Nelson1982} reviewed early work in this area, but many early studies were limited by small sample sizes and narrow spatial scopes.
-A review by \citet{Bateman2001} found that the negative effect of traffic noise ranged from 0.08 to 2.22 percent per dB with a mean around 0.55 percent per dB, while \citet{Navrud2002} found an average decrease of 0.64 percent per dB.
-More recent work has tended to focus on the European experience with noise, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Netherlands \citep{Theebe2004a}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, and Switzerland \citep{Baranzini2010}.
+Automobile traffic is perhaps the greatest source of noise in residential neighborhoods \citep{Barber2010} and is expected to grow worse \citep{Goines2007}.
+For instance, \citet{Dargay2007} expect the global number of personal vehicles to grow from roughly 800 million in 2002 to over two billion units by 2030.
+The global urbanization trend is expected to continue, increasing the proportion of the population living in cities from roughly half now to over two-thirds by the middle of the century \citep{UNDESA2012}.
 
-The relationship between road traffic noise levels and real estate prices has rarely been explored in the United States, even though the former is perhaps the greatest source of noise in residential neighborhoods (XXX).
-Work examining the negative effects of noise in the US has instead tended to concentrate on noise from airports \citep{Espey2000, McMillen2004, Cohen2008a} or indirect effects of traffic noise, such as proximity to highways \citep{Matthews2007, Chernobai2009, Li2012}, or traffic counts \citep{HughesJr.1992, Larsen2012}.
-One major reason for the thinness of the scholarly literature on this topic in the US lies in the difficulty of modeling noise propagation over the landscape.
+\citet{Delucchi1998} conducts a cost-benefit analysis of the external damage cost of traffic noise in the United States.
+The estimated range of results is wide (less than \$100 million to over \$40 billion in year 1991 dollars) due to uncertainty surrounding the degree of noise propagation over space in the urban built environment and the effect of noise on house prices.
+Indeed, one of the main conclusions of the \citet{Delucchi1998} is that more research should be done to better understand the impact of noise on house prices and that better noise data are needed for such work to occur.
+%Governments are taking action to try to protect their citizens from the ill effects of noise.
+The US Federal Highway Admistration reports that 47 states have constructed noise barriers to dampen noise propagation, spending over a half a billion dollars from 2008-2010 \citep{USFHA2012}.
+A complete cost-benefit analysis of such projects requires up-to-date measurements of the economic impact of traffic noise.
 
+\citet{Nelson1982} was the first to review some of the earliest noise hedonic work in the United States and Canada.
+The review of roughly ten studies found an average estimated impact of traffic noise to be a reduction in house prices of approximately 0.4 percent per additional decibel.
+More recently, \citet{Nelson2008} notes that many of these early studies \citep[such as][]{Gamble1974, Langley1976} are plagued by issues of small sample sizes (in the hundreds) and limited spatial extents (one or a handful of cities).
+
+Recent reviews of the research by \citet{Bateman2001} found that the negative effect of traffic noise on house prices ranged from 0.08 to 2.22 percent per decibel with a mean around 0.55 percent per decibel, while \citet{Navrud2002} found an average decrease of 0.64 percent per decibel.
+However, much of the research in these reviews and subsequent work has tended to focus on the European experience with noise, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Switzerland \citep{Baranzini2010}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, Netherlands \citep{Theebe2004a}, and Germany \citep{Brandt2011}.
+
+Instead of focusing on the impact of automobile traffic, work in the United States has instead tended to concentrate on noise from airports \citep{Espey2000, McMillen2004, Cohen2008a} or indirect effects of traffic noise, such as proximity to highways \citep{Matthews2007, Chernobai2009, Li2012}, or traffic counts \citep{HughesJr.1992, Larsen2012}.
+One exception is \citet{Cheng2008}, which, using micro data in Louisville, TN during 2007, finds that an additional decibel of traffic noise reduced house prices by 0.34 percent.
+However, this research is based on less than a thousand transactions.
+
+One major reason for the thinness of the scholarly literature on this topic in the US lies in the difficulty of modeling traffic noise propagation over the landscape.
 To properly analyze the spatial association between real estate prices and exposure to traffic noise at a landscape level, it is necessary to create a noise surface map at sufficiently detailed spatial resolution to account for the complex and heterogeneous interaction between the noise source and the resistance of the landscape to noise propagation.
@@
 
-In this paper, we seek to contribute to the hedonic literature by examining the relationship between real estate prices and variation in road traffic noise exposure.
-We approach this issue by means of an empirical case study of the St.\ Paul, Minnesota urban area.
-In particular, we construct a locally flexible model that allows for a non-stationary relationship between house prices and our explanatory variables over geography and time.
-Such Locally Weighted Regression (LWR) models have become increasingly common in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than spatial autoregressive models with misspecified weights matrices \citep{McMillen2012}.
-
+In this paper, we seek to contribute to the noise hedonic literature by examining the relationship between single family home prices and variation in road traffic noise exposure.
+We approach this issue by means of an empirical case study of the St.\ Paul, Minnesota urban area using recent sales transactions.
 Our work makes three contributions to the field.
 First, we utilize new estimates of traffic noise that has never before been used in the hedonic literature.
-The data explicitly model noise propagation as a function of nearby buildings and landcover, as well as present the results at a fine spatial resolution (10m x 10m).
-Such estimates, combined with sptially explicit modeling techniques allow us to make our second contribution to the literature.
-We present one of the first non-parametric estimates of how the impact of traffic noise varies over space within an urban area in the United States.
+The noise propagation model estimates traffic noise levels at a high spatial resolution (10m x 10m) while also incorporating the effects of nearby buildings and landcover.
+
+We also construct a flexible hedonic model that allows for a non-stationary relationship between house prices and our explanatory variables over geography and time.
+Such Locally Weighted Regression (LWR) models have become increasingly common in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than other spatial econometric models under common circumstances \citep{McMillen2012}.
 Contrary to previous work, we find that while the impact of other important control variables in the hedonic function vary over space, the impact of traffic noise does not.
-Lastly, we present the first estimates of how the Great Recession has affected the hedonic price of traffic noise.
+Lastly, we present the first estimates of the implicit price of traffic noise after the Great Recession and the housing bubble collapse.
 
@@
 Paul and their surrounding areas)  as almost 3 million residents spread over seven counties.
-This study examines single family residential home transactions in the Census-defined urban areas of three of the seven counties – Dakota, Ramsey and Washington County (see Figure 1).
+This study examines single family residential home transactions in the Census-defined urban areas of three of the seven counties – Dakota, Ramsey and Washington County (see Figure \ref{fig:overview}).
 We obtained data from approximately forty thousand sales transactions between 2005 and 2010 (n=42,095) from the 2010 MetroGIS Regional Parcel Dataset published by the Metropolitan Council.
-In addition to the geographic location and date of the house sale, we collected or created structural and locational variables commonly used in the hedonic literature.
+Figure \ref{fig:overview} shows an overview of the study area as well as the spatial distribution of the house sales prices.
+In addition to the geographic location and date of the house sale, we collected or calculated structural and locational variables commonly used in the hedonic literature.
 Table \ref{tab:sumStats} provides a brief description of the variables in our data and some basic summary statistics.
-Figure \ref{fig:overview} shows an overview of the study area as well as the spatial distribution of the house sales prices.
 Table \ref{tab:cor} shows a simple correlation matrix of the quantitative variables.
@@
 Insert noise data description and methodology here. \citet{Nega2012}
+To determine the relationship between real estate price and road traffic noise levels, we first created a traffic noise exposure surface for the entire Twin Cities Metro Region (TCMR) by calculating the propagation of traffic noise over the landscape using the FHWA (Federal Highway Authority) 1978 standard \citep{Barry1978}.
+Following \citet{Barry1978}, the traffic noise level at any given location on the landscape is given by:
+\begin{eqnarray}\label{eq:noise}
+L_{EQ}(i) &=& \bar{L}_0(i) + 0.115 \sigma _i^2 + 10 log \frac{N_i \pi D_0}{T*S_i} + 10 log \left[ \frac{D_0}{D}\right]^{1 + \alpha}  \nonumber \\
+&& + 10 log \left( \frac{\psi _{\alpha (\phi _1, \phi _2)}}{\pi}\right) + \Delta _{gradient} + \Delta _{shielding}
+\end{eqnarray}
+where $L_{EQ}(i)$ is A-weighted hourly energy equivalent noise level in dBA, which is calculated for each class $i$ of vehicle (automobile and trucks); $\bar{L}_0(i)$ is the mean Sound Pressure Level (SPL) at the reference distance for class $i$; $\sigma _i$ is the standard deviation of the SPL for each class of vehicle; $N_i$ is the number of vehicles of the $i^{th}$ class passing during the relevant hour; $D_0$ is the reference distance (usually 15 m); $D$ is the perpendicular distance from the road center line to the receiver; $\alpha$ is a site parameter (soft and hard surface), $0 < \alpha < 1$; $S_i$ is the mean speed of the $i^{th}$ class; $T$ is the duration, usually 1 hour; $\phi _1$ and $\phi _2$ are the angles from the perpendicular of the limits of the observer's view of a section of the road.
+They are used to account for only the energy coming from a portion of the roadway; $\Delta _{gradient}$ is an adjustment for road surface gradient; $\Delta _{shielding}$ is a shielding adjustment (land cover, buildings, noise barriers).
+
+To calculate the traffic noise map for the region using the above model, several data sources were used.
+A 2007 road centerline and the associated traffic characteristics (volume and proportion of trucks and vehicles) for the region were obtained from the Minnesota Department of Transportation (MNDoT).
+We converted the posted speed of each road into a GIS layer.
+For all roads without recorded traffic volume (i.e., residential), we assigned 100 vehicles/day as a minimum estimate.
+This estimate was based on factors identified in the literature as important for estimating traffic volume, such as census data on commuting population, tract area, the size of a standard street block, and road type \citep{Cheng1992, Fricker1986}.
+In order to assess the sensitivity of our results to our estimate of traffic volume for local roads, we conducted a sensitivity analysis by running the model using 200 and 300 vehicles/day for one of the counties that make up the TCMR.
+With the exception of a few areas in the rural part of the county, there was less than 0.05 dBA difference at 30 m from the road centerline, suggesting that the estimated values are not sensitive to the traffic volume variations used for the sensitivity analysis.
+
+Data on traffic volume and the proportion of trucks and vehicles on each segment of the road were averaged over a 24-hour period, making it impossible to account for a day and night time variation in traffic noise.
+Following Arditi et al.
+(2007), we divided the total traffic volume into day and nighttime periods by assuming that 80 percent of vehicles and 65 percent of trucks are driven during the daytime (6am–10pm) and 35 percent of trucks and 20 percent of vehicles are driven during the nighttime (10pm-6am).
+Values for ground absorption were chosen by assuming that all road surfaces consisted of impervious bitumen.
+For computational simplicity, we created the road surface gradient by re-sampling U.S.
+Geological Survey 30 m resolution Digital Elevation Model (DEM) to 100 m resolution.
+
+We used three data sources for the shielding adjustment: buildings, foliage, and noise barriers.
+We extracted the perimeter and height of 818,500 buildings using aerial photography and LiDAR data.
+For the areas where LiDAR data are available, we used LiDAR Analyst$^{TM}$ software to extract buildings’ footprints.
+For the areas of the region where only aerial photos are available, we used Feature Analyst$^{TM}$ software to extract building footprints.
+For measurements extracted using aerial photography, height was determined using a combination of parcel data and field measurements.
+
+The locations chosen for the traffic noise levels were the 818,500 buildings in the TCMR.
+Thus, we used the perimeter and height of these buildings to account for the shielding effect of buildings.
+To account for foliage shielding (and to make the computation manageable), we assumed that only forest patches that are at least 10 m high and have an area greater than 10,000 m$^2$ will have a significant effect on noise attenuation.
+Accordingly, we extracted forest polygons with these characteristics using a combination of year 2005 land use data and 2001 National Land Cover Data (NLCD).
+To account for noise barrier shielding, we used a noise barrier layer obtained from MNDoT, which contains the locations, width, and height of noise barriers in the region.
+
+We used the SoundPlan$^{TM}$ noise modeling software to implement the model given by Equation \ref{eq:noise}.
+Predicted traffic noise output is calculated at a grid resolution of 10 m$^2$.
+Once the noise surface for the entire region was developed, we extracted the noise surface for the present study area.
+
+We conducted a preliminary validation of the model output by comparing it with observed noise levels at 134 locations that were sampled along major highways.
+For each location, two readings were taken very close to the highway, one between 9am and 10am and another between 1pm and 2pm.
+The noise level for each location is then determined by averaging the two observed values, and this average is then compared with the predicted noise level.
+
+The relationship between the mean observed and predicted noise levels is linear and moderately strong with a correlation of 0.76 (Figure 1).
+It is not surprising that the relationship is not stronger given the size and complexity of the model.
+In particular, the traffic volume data that we used for modeling traffic noise propagation is a 24-hour average, which requires more time-interval sampling per location than just the two used in the validation.
+Still, this preliminary comparison serves as a good indicator of how well this model captures traffic noise levels.
 
 \subsection{Other Locational Attributes}
-A common real estate addage states that the three most important things about real estate are: location, location and location.
+A common real estate addage states that the three most important real estate attributes are: location, location and location.
 Knowing where each house is located allows us to also construct a vector of other attributes associated with the sales transaction.
@@
 Additionally, a variable denoting the median household income for the surrounding census tract is created through the use of TIGER shapefiles from the 2010 Census Bureau and data from the 2010 American Community Survey (ACS).
-Lastly, we associate each transaction with its elementary school and include the average 3rd grade Minnesota Comprehensive Assessment (MCA) score for the local elementary school during the year of purchase.
-Test scores were obtained from the Minnesota Department of Education website.
-The school district and elementary school attendance boundary spatial information was taken from the Minnesota Geospatial Information Office Clearinghouse Data Catalog.
+Lastly, we associate each transaction with its elementary school and include the average 3rd grade Minnesota Comprehensive Assessment (MCA) score for the local elementary school during the year of purchase.\footnote{Test scores were obtained from the Minnesota Department of Education website.
+The school district and elementary school attendance boundary spatial information was taken from the Minnesota Geospatial Information Office Clearinghouse Data Catalog.}
 
 \subsection{Time}
-Given that we have data from before and after the recession of 2008-09, we subset the data in Table \ref{tab:SumStatsTime} by year of sale to look for differences.
+Given that we have data from before and after the recession of 2008-09, we subset the data in Table \ref{tab:SumStatsTime} by year of sale to look for differences over time.
 In addition to the noticeable decline in nominal sales values, there is also a drop in the number of sales across years.
-For example, in 2010 there were only 4,206 property sales within the dataset, a more than 50 percent reduction from 2005.
+For example, in 2010 there were only 4,206 property sales within the dataset, less than half as many in 2005.
 While the mean sale price declined from roughly \$280,000 pre-crash to \$230,000 post-crash, most of the structural and neighborhood variables are relatively consistent across years.
@@
 
+\begin{singlespace}
 \bibliographystyle{plainnat}
 \bibliography{NoiseBibliography}
+\end{singlespace}
 \end{document}

### 2013-09-12 reports/Draft.Rnw
prepping for Excel2Latex changes to tables

@@
 
+\defcitealias{Netherlands2004}{Netherlands, 2004}
+\defcitealias{UNDESA2012}{United Nations, 2012}
 \title{A Hedonic Price Analysis of Traffic Noise in the Twin Cities Housing Market}
@@
 Paul, Minnesota using spatially explicit local regression techniques.
-Our estimate of the negative relationship between traffic noise levels and house prices are smaller in magnitude than most of the relevant published literature.
+Our estimate of the negative relationship between traffic noise levels and house prices is smaller in magnitude than most of the relevant published literature.
 We find no evidence that the effect of traffic noise varies significantly by geography, nor by traffic noise levels.
@@
 \section{Introduction and Past Research}\label{sec:lit}
-Prolonged exposure to traffic noise affects people in a number of ways, ranging from simple annoyance \citep{Miedema2001, Ouis2001, Ohrstrom2007, DeKluizenaar2013, Weinhold2013}, to sleep disturbance \citep{Netherlands2004}, to increasing risk for stroke \citep{Sorensen2011}, hypertension \citep{Jarup2008, Bodin2009}, myocardial infarction \citep{Babisch2005}, and overall quality of life \citep{Shepherd2013}.
+Prolonged exposure to traffic noise affects people in a number of ways, ranging from simple annoyance \citep{Miedema2001, Ouis2001, Ohrstrom2007, DeKluizenaar2013, Weinhold2013}, to sleep disturbance \citepalias{Netherlands2004}, to increasing risk for stroke \citep{Sorensen2011}, hypertension \citep{Jarup2008, Bodin2009}, myocardial infarction \citep{Babisch2005}, and overall quality of life \citep{Shepherd2013}.
 The noise level at which such effects are observed does not have to be high.
@@
 
-Automobile traffic is perhaps the greatest source of noise in residential neighborhoods \citep{Barber2010} and is expected to grow worse \citep{Goines2007}.
-For instance, \citet{Dargay2007} expect the global number of personal vehicles to grow from roughly 800 million in 2002 to over two billion units by 2030.
-The global urbanization trend is expected to continue, increasing the proportion of the population living in cities from roughly half now to over two-thirds by the middle of the century \citep{UNDESA2012}.
+Automobiles are already perhaps the greatest source of noise in residential neighborhoods \citep{Barber2010} and traffic noise was estimated to cause around three billion dollars worth of external damage to the United States economy alone in 1991 \citep{Delucchi1998}.
+Traffic noise and its attendent problems are greater now than they were in the 1990s and predicted to worsen in the future \citep{Goines2007}.
+With the exception of a slight dip during the economic recession in the late 2000s, the number of vehicle miles traveled in the United States has steadily increased for the past 50 years.\footnote{\url{http://www.fhwa.dot.gov/policyinformation/statistics/2011/pdf/rc1c.pdf}} Globally, \citet{Dargay2007} predict the number of personal vehicles to grow from roughly 800 million in 2002 to over two billion units by 2030.
+Additionally, the global trend of increased urbanization is expected to continue, with the proportion of the population living in cities growing from roughly half now to over two-thirds by the middle of the century \citepalias{UNDESA2012}.
 
-\citet{Delucchi1998} conducts a cost-benefit analysis of the external damage cost of traffic noise in the United States.
-The estimated range of results is wide (less than \$100 million to over \$40 billion in year 1991 dollars) due to uncertainty surrounding the degree of noise propagation over space in the urban built environment and the effect of noise on house prices.
-Indeed, one of the main conclusions of the \citet{Delucchi1998} is that more research should be done to better understand the impact of noise on house prices and that better noise data are needed for such work to occur.
-%Governments are taking action to try to protect their citizens from the ill effects of noise.
-The US Federal Highway Admistration reports that 47 states have constructed noise barriers to dampen noise propagation, spending over a half a billion dollars from 2008-2010 \citep{USFHA2012}.
-A complete cost-benefit analysis of such projects requires up-to-date measurements of the economic impact of traffic noise.
+Policies at the local, state, and federal level can influence the level and effect of traffic noise.
+For instance, the US Federal Highway Admistration reports that 47 states have constructed noise barriers to reduce noise propagation, spending over a half a billion dollars from 2008-2010 \citep{USFHA2012}.
+The efficiency of such projects requires an understanding of the economic cost of traffic noise.
 
+One way to estimate some of the costs of traffic noise (and therefore the economic benefits of policies that reduce noise) is through hedonic regression, examining the relationship between house prices and noise levels.
 \citet{Nelson1982} was the first to review some of the earliest noise hedonic work in the United States and Canada.
@@
 
-Recent reviews of the research by \citet{Bateman2001} found that the negative effect of traffic noise on house prices ranged from 0.08 to 2.22 percent per decibel with a mean around 0.55 percent per decibel, while \citet{Navrud2002} found an average decrease of 0.64 percent per decibel.
+Reviews of the research by \citet{Bateman2001} found that the negative effect of traffic noise on house prices ranged from 0.08 to 2.22 percent per decibel with a mean around 0.55 percent per decibel, while \citet{Navrud2002} found an average decrease of 0.64 percent per decibel.
 However, much of the research in these reviews and subsequent work has tended to focus on the European experience with noise, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Switzerland \citep{Baranzini2010}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, Netherlands \citep{Theebe2004a}, and Germany \citep{Brandt2011}.
@@
 However, this research is based on less than a thousand transactions.
+
+\citet{Delucchi1998} used an estimate of 0.85 percent reduction in house prices per additional decibel of traffic noise in their cost-benefit analysis of traffic noise.
+While their preferred estimate of the total damage cost to the United States in 1991 is \$3 billion, they report a possible range of less than \$100 million to over \$40 billion due to uncertainty surrounding the degree of noise propagation over space in the urban built environment and the effect of noise on house prices.
+Indeed, one of the main conclusions of the \citet{Delucchi1998} is that more research should be done to better understand the impact of noise on house prices and that better noise data are needed for such work to occur.
 
@@
 
-In this paper, we seek to contribute to the noise hedonic literature by examining the relationship between single family home prices and variation in road traffic noise exposure.
-We approach this issue by means of an empirical case study of the St.\ Paul, Minnesota urban area using recent sales transactions.
+In this paper, we seek to contribute to the noise hedonic literature by examining the relationship between single family home prices from 2005 to 2010 and variation in road traffic noise exposure in the St.\ Paul, Minnesota urban area.
 Our work makes three contributions to the field.
@@
 The noise propagation model estimates traffic noise levels at a high spatial resolution (10m x 10m) while also incorporating the effects of nearby buildings and landcover.
-
 We also construct a flexible hedonic model that allows for a non-stationary relationship between house prices and our explanatory variables over geography and time.
 Such Locally Weighted Regression (LWR) models have become increasingly common in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than other spatial econometric models under common circumstances \citep{McMillen2012}.
-Contrary to previous work, we find that while the impact of other important control variables in the hedonic function vary over space, the impact of traffic noise does not.
+Contrary to previous work \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, we find that while the impact of other important control variables in the hedonic function vary over space, the impact of traffic noise does not.
 Lastly, we present the first estimates of the implicit price of traffic noise after the Great Recession and the housing bubble collapse.
@@
 Paul and their surrounding areas)  as almost 3 million residents spread over seven counties.
-This study examines single family residential home transactions in the Census-defined urban areas of three of the seven counties – Dakota, Ramsey and Washington County (see Figure \ref{fig:overview}).
+This study examines single family residential home transactions in the Census-defined urban areas of three of the seven counties: Dakota, Ramsey and Washington County (see Figure \ref{fig:overview}).
 We obtained data from approximately forty thousand sales transactions between 2005 and 2010 (n=42,095) from the 2010 MetroGIS Regional Parcel Dataset published by the Metropolitan Council.
@@
 
- & min & 25\% & 50\% & mean & 75\% & max & $\sigma$ \\ 
+ & min & 25\% & 50\% & mean & 75\% & max & st. dev. \\ 
   \hline
@@
 \subsection{Structural Attributes}
-According to \cite{Wilhelmsson2000}, the most common structural attributes included in real-estate hedonic pricing studies are living area, number of bathrooms, age, garage and lot size.
+According to a review by \cite{Wilhelmsson2000}, the most common structural attributes included in real-estate hedonic pricing studies are living area, number of bathrooms, age, garage and lot size.
 Although the 2010 MetroGIS Regional Parcel Dataset includes structural data on living area, age, garage presence, lot size and owner occupancy for every transaction, we have variables for the number of bedrooms, bathrooms, and size of the garage only for those house sales in one county.
@@
 For all roads without recorded traffic volume (i.e., residential), we assigned 100 vehicles/day as a minimum estimate.
-This estimate was based on factors identified in the literature as important for estimating traffic volume, such as census data on commuting population, tract area, the size of a standard street block, and road type \citep{Cheng1992, Fricker1986}.
-In order to assess the sensitivity of our results to our estimate of traffic volume for local roads, we conducted a sensitivity analysis by running the model using 200 and 300 vehicles/day for one of the counties that make up the TCMR.
-With the exception of a few areas in the rural part of the county, there was less than 0.05 dBA difference at 30 m from the road centerline, suggesting that the estimated values are not sensitive to the traffic volume variations used for the sensitivity analysis.
+This estimate was based on factors identified in the literature as important for estimating traffic volume, such as census data on commuting population, tract area, the size of a standard street block, and road type \citep{Cheng1992, Fricker1986}.\footnote{In order to assess the sensitivity of our results to our estimate of traffic volume for local roads, we conducted a sensitivity analysis by running the model using 200 and 300 vehicles/day for one of the counties that make up the TCMR.
+With the exception of a few areas in the rural part of the county, there was less than 0.05 dBA difference at 30 m from the road centerline, suggesting that the estimated values are not sensitive to the traffic volume variations used for the sensitivity analysis.}
 
 Data on traffic volume and the proportion of trucks and vehicles on each segment of the road were averaged over a 24-hour period, making it impossible to account for a day and night time variation in traffic noise.
-Following Arditi et al.
-(2007), we divided the total traffic volume into day and nighttime periods by assuming that 80 percent of vehicles and 65 percent of trucks are driven during the daytime (6am–10pm) and 35 percent of trucks and 20 percent of vehicles are driven during the nighttime (10pm-6am).
+Following \citet{Arditi2007}, we divided the total traffic volume into day and nighttime periods by assuming that 80 percent of vehicles and 65 percent of trucks are driven during the daytime (6am–10pm) and 35 percent of trucks and 20 percent of vehicles are driven during the nighttime (10pm-6am).
 Values for ground absorption were chosen by assuming that all road surfaces consisted of impervious bitumen.
@@
 We used the SoundPlan$^{TM}$ noise modeling software to implement the model given by Equation \ref{eq:noise}.
-Predicted traffic noise output is calculated at a grid resolution of 10 m$^2$.
-Once the noise surface for the entire region was developed, we extracted the noise surface for the present study area.
-
-We conducted a preliminary validation of the model output by comparing it with observed noise levels at 134 locations that were sampled along major highways.
+Predicted traffic noise output is calculated at a grid resolution of 10 m$^2$.\footnote{We conducted a preliminary validation of the model output by comparing it with observed noise levels at 134 locations that were sampled along major highways.
 For each location, two readings were taken very close to the highway, one between 9am and 10am and another between 1pm and 2pm.
 The noise level for each location is then determined by averaging the two observed values, and this average is then compared with the predicted noise level.
-
-The relationship between the mean observed and predicted noise levels is linear and moderately strong with a correlation of 0.76 (Figure 1).
+The relationship between the mean observed and predicted noise levels is linear and moderately strong with a correlation of 0.76.
 It is not surprising that the relationship is not stronger given the size and complexity of the model.
 In particular, the traffic volume data that we used for modeling traffic noise propagation is a 24-hour average, which requires more time-interval sampling per location than just the two used in the validation.
-Still, this preliminary comparison serves as a good indicator of how well this model captures traffic noise levels.
+Still, this preliminary comparison serves as a good indicator of how well this model captures traffic noise levels.} Once the noise surface for the entire region was developed, we extracted the noise surface for the present study area by overlaying the housing parcel boundaries and calculating the maximum noise level within the parcel.
 

### 2013-09-12 analysis/01GlobalRegression/GlobalRegression_2013_09_12.R
updated global regressions for the paper

@@ -1,10 +1,7 @@
-Global Regression Model Results
-========================================================
-
-#This script runs the most up to date global regression models that include interaction effects.
-```{r}
+#This script runs the most up to date global regression models that include interaction effects and non linear relationships.
 require(foreign)
-workingdata20052010 <- read.dbf("../../../Data/R2GIS/CleanData/Sales20052010.dbf")
+####### 2005 to 2010 Sales Model ########
+workingdata20052010 <- read.dbf("../Data/R2GIS/CleanData/Sales20052010.dbf")
 workingdata20052010$PostCrash = 0
 crashobs <- which(workingdata20052010$TimePeriod>46)
 workingdata20052010$PostCrash[crashobs] = 1
@@ -12,19 +9,19 @@ workingdata20052010$PostCrash[crashobs] = 1
 myModel = "logSALE_VA ~ FIN_SQ_FT + ACRES_POLY +  HOMESTEAD +  YEAR_BUILT + MAX +
  MED_INCOME + MCA3 + CBD_dist + LAKE_dist + PARK_dist + SHOP_dist  + COUNTY_ID +  factor(SALE_YR) + SALE_MO"
 
+#ACRES_POLY * CBD_dist I(ACRES_POLY^2)* I(CBD_dist ^2)
+##Run model (All)
 lm.mini = lm(myModel, data = workingdata20052010)
-summary(lm.mini)
+summary(lm.mini, digits = 2)
 
 ModelBig = paste0(myModel, " + ACRES_POLY * CBD_dist")
 lm.big = lm(ModelBig, data = workingdata20052010)
 summary(lm.big)
-```
 
-Now run model pre- and post- crash
-```{r}
+## Run model (Pre- and Post- Crash)
+
 lm.bigPre = lm(ModelBig, data = workingdata20052010, subset = (PostCrash == 0))
 summary(lm.bigPre)
 
 lm.bigPost = lm(ModelBig, data = workingdata20052010, subset = (PostCrash == 1))
 summary(lm.bigPost)
-```

### 2013-09-12 reports/Draft.Rnw
updated correlation matrix code and in paper

@@
 \usepackage[round]{natbib}
-\usepackage{caption, amsmath, graphicx, setspace, multirow, color, hyperref}
+\usepackage{caption, amsmath, graphicx, setspace, multirow, color, hyperref, array}
+
+\newcolumntype{x}[1]{%
+>{\centering\hspace{0pt}}p{#1}}%
 
@@
 \caption{Matrix of Pearson Correlation Coefficients for Quantitative Variables}\label{tab:cor}
-\includegraphics[width = \textwidth]{../graphs/CorrelationMatrix}
+%\includegraphics[width = \textwidth]{../graphs/CorrelationMatrix}
+\begin{center}
+\small
+\tabcolsep=0.05cm
+\begin{tabular}{lrrrrrrrrrrr}
+  \hline
+ & \multicolumn{1}{x{.35in}}{Price} & \multicolumn{1}{x{.38in}}{House} & \multicolumn{1}{x{.35in}}{Lot} & 
+ \multicolumn{1}{x{.35in}}{Built} & \multicolumn{1}{x{.35in}}{Noise} & \multicolumn{1}{x{.35in}}{Inc.} & 
+ \multicolumn{1}{x{.35in}}{Test} & \multicolumn{1}{x{.35in}}{CBD} & \multicolumn{1}{x{.35in}}{Park} & \multicolumn{1}{x{.35in}}{Lake} & \multicolumn{1}{x{.35in}}{Shop} \tabularnewline 
+  \hline
+ln Sale Price & 1 &  &  &  &  &  &  &  &  &  &  \tabularnewline 
+  House Size & 0.74 & 1 &  &  &  &  &  &  &  &  &  \tabularnewline 
+  Lot Size & 0.40 & 0.45 & 1 &  &  &  &  &  &  &  &  \tabularnewline 
+  Year Built & 0.49 & 0.52 & 0.47 & 1 &  &  &  &  &  &  &  \tabularnewline 
+  Noise & -0.12 & -0.07 & 0.00 & -0.19 & 1 &  &  &  &  &  &  \tabularnewline 
+  Income & 0.55 & 0.50 & 0.41 & 0.57 & -0.18 & 1 &  &  &  &  &  \tabularnewline
+  Elem. Test Scores & 0.33 & 0.28 & 0.29 & 0.34 & -0.04 & 0.44 & 1 &  &  &  &  \tabularnewline 
+  Distance to CBD & 0.35 & 0.45 & 0.43 & 0.58 & -0.04 & 0.53 & 0.35 & 1 &  &  &  \tabularnewline
+  Distance to Park & 0.27 & 0.28 & 0.22 & 0.42 & -0.13 & 0.38 & 0.22 & 0.57 & 1 &  &  \tabularnewline
+  Distance to Lake & -0.05 & -0.10 & -0.25 & -0.17 & -0.03 & -0.12 & -0.10 & -0.09 & 0.20 & 1 &  \tabularnewline
+  Distance to Shop & 0.28 & 0.27 & 0.15 & 0.37 & -0.19 & 0.36 & 0.18 & 0.46 & 0.38 & 0.15 & 1 \tabularnewline
+   \hline
+\end{tabular}
+\end{center} 
 \end{table}

### 2013-09-12 analysis/Data Description/CorMatrix.R

@@ -1,0 +1,23 @@
+
+library (foreign)
+workingdata <- read.dbf("../Data/R2GIS/CleanData/Sales20052010.dbf")
+
+
+quantVars = c("logSALE_VA", "FIN_SQ_FT", "ACRES_POLY", "YEAR_BUILT", 
+              "MAX", "MED_INCOME", "MCA3", "CBD_dist", "PARK_dist", "LAKE_dist",  "SHOP_dist")
+
+corMat = cor(workingdata[, quantVars])
+
+corMat = round(corMat, 2)
+
+corMat[upper.tri(corMat)] <- ""
+corMat
+
+rownames(corMat) = c("ln Sale Price", "House Size", "Lot Size", "Year Built", "Noise", "Income", "Elementary Test Scores",
+                     "Distance to CBD", "Distance to Park", "Distance to Lake", "Distance to Shop")
+colnames(corMat) = c("Price", "House", "Lot", "Built", "Noise", "Income", "Test", "CBD", "Park", "Lake", "Shop")
+
+require(xtable)
+print(xtable(corMat, align = "lrrrrrrrrrrr"))
+
+cor(workingdata$ACRES_POLY, workingdata$MAX)

### 2013-09-14 reports/Draft.Rnw
added text about GCV score and updated bibliography

@@
 \defcitealias{UNDESA2012}{United Nations, 2012}
+\defcitealias{USFHA2012}{USFHWA, 2012}
+
 \title{A Hedonic Price Analysis of Traffic Noise in the Twin Cities Housing Market}
@@
 Policies at the local, state, and federal level can influence the level and effect of traffic noise.
-For instance, the US Federal Highway Admistration reports that 47 states have constructed noise barriers to reduce noise propagation, spending over a half a billion dollars from 2008-2010 \citep{USFHA2012}.
+For instance, the US Federal Highway Admistration reports that 47 states have constructed noise barriers to reduce noise propagation, spending over a half a billion dollars from 2008-2010 \citepalias{USFHA2012}.
 The efficiency of such projects requires an understanding of the economic cost of traffic noise.
@@
 \citet{Nelson1982} was the first to review some of the earliest noise hedonic work in the United States and Canada.
-The review of roughly ten studies found an average estimated impact of traffic noise to be a reduction in house prices of approximately 0.4 percent per additional decibel.
+The review of nine studies found an average estimated impact of traffic noise to be a reduction in house prices of approximately 0.4 percent per additional decibel.
 More recently, \citet{Nelson2008} notes that many of these early studies \citep[such as][]{Gamble1974, Langley1976} are plagued by issues of small sample sizes (in the hundreds) and limited spatial extents (one or a handful of cities).
@@
 
-Instead of focusing on the impact of automobile traffic, work in the United States has instead tended to concentrate on noise from airports \citep{Espey2000, McMillen2004, Cohen2008a} or indirect effects of traffic noise, such as proximity to highways \citep{Matthews2007, Chernobai2009, Li2012}, or traffic counts \citep{HughesJr.1992, Larsen2012}.
+Instead of focusing on the impact of automobile traffic, work in the United States has tended to concentrate on noise from airports \citep{Espey2000, McMillen2004, Cohen2008a} or indirect effects of traffic noise, such as proximity to highways \citep{Matthews2007, Chernobai2009, Li2012}, or traffic counts \citep{HughesJr.1992, Larsen2012}.
 One exception is \citet{Cheng2008}, which, using micro data in Louisville, TN during 2007, finds that an additional decibel of traffic noise reduced house prices by 0.34 percent.
-However, this research is based on less than a thousand transactions.
+However, this research is based on less than a thousand transactions in just one city.
 
-\citet{Delucchi1998} used an estimate of 0.85 percent reduction in house prices per additional decibel of traffic noise in their cost-benefit analysis of traffic noise.
+\citet{Delucchi1998} used an estimate of 0.85 percent reduction in house prices per additional decibel in their cost-benefit analysis of traffic noise.
 While their preferred estimate of the total damage cost to the United States in 1991 is \$3 billion, they report a possible range of less than \$100 million to over \$40 billion due to uncertainty surrounding the degree of noise propagation over space in the urban built environment and the effect of noise on house prices.
-Indeed, one of the main conclusions of the \citet{Delucchi1998} is that more research should be done to better understand the impact of noise on house prices and that better noise data are needed for such work to occur.
+Indeed, one of the main conclusions of their work is that more research should be done to better understand the impact of noise on house prices and that better noise data are needed for such work to occur.
 
@@
 In this paper, we seek to contribute to the noise hedonic literature by examining the relationship between single family home prices from 2005 to 2010 and variation in road traffic noise exposure in the St.\ Paul, Minnesota urban area.
-Our work makes three contributions to the field.
+Our work makes multiple contributions to the field.
 First, we utilize new estimates of traffic noise that has never before been used in the hedonic literature.
 The noise propagation model estimates traffic noise levels at a high spatial resolution (10m x 10m) while also incorporating the effects of nearby buildings and landcover.
+
 We also construct a flexible hedonic model that allows for a non-stationary relationship between house prices and our explanatory variables over geography and time.
 Such Locally Weighted Regression (LWR) models have become increasingly common in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than other spatial econometric models under common circumstances \citep{McMillen2012}.
-Contrary to previous work \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, we find that while the impact of other important control variables in the hedonic function vary over space, the impact of traffic noise does not.
-Lastly, we present the first estimates of the implicit price of traffic noise after the Great Recession and the housing bubble collapse.
+\citet{MarmolejoDuarteCarlos;GonzalezTamez2009} used a LWR model to estimate the impact of traffic noise on housing prices in Barcelona, Spain and found evidence of a non-stationary relationship over the study area.
+We find that while the impact of other important control variables in the hedonic function vary over space, the impact of traffic noise does not.
+
+Lastly, we present the first estimates of the implicit price of traffic noise after the Great Recession and the housing bubble collapse of 2008-09.
+Contrary to work such as \citet{Cho2011b}, which found that environmental amenities mattered less after the housing crash, our estimated effect of traffic noise mattered more after the recession (0.37 percent reduction in house prices per additional decibel) compared to beforehand (0.19 percent per decibel).
 
@@
 \tabcolsep=0.05cm
-\begin{tabular}{lrrrrrrrrrrr}
-  \hline
+\makebox[\linewidth][c]{
+\begin{tabular}{l|rrrrrrrrrrr}
  & \multicolumn{1}{x{.35in}}{Price} & \multicolumn{1}{x{.38in}}{House} & \multicolumn{1}{x{.35in}}{Lot} & 
@@
   Distance to Shop & 0.28 & 0.27 & 0.15 & 0.37 & -0.19 & 0.36 & 0.18 & 0.46 & 0.38 & 0.15 & 1 \tabularnewline
-   \hline
-\end{tabular}
+\end{tabular} }
 \end{center} 
@@
 \subsection{Noise Data}
-Insert noise data description and methodology here. \citet{Nega2012}
 To determine the relationship between real estate price and road traffic noise levels, we first created a traffic noise exposure surface for the entire Twin Cities Metro Region (TCMR) by calculating the propagation of traffic noise over the landscape using the FHWA (Federal Highway Authority) 1978 standard \citep{Barry1978}.
@@
 For all roads without recorded traffic volume (i.e., residential), we assigned 100 vehicles/day as a minimum estimate.
-This estimate was based on factors identified in the literature as important for estimating traffic volume, such as census data on commuting population, tract area, the size of a standard street block, and road type \citep{Cheng1992, Fricker1986}.\footnote{In order to assess the sensitivity of our results to our estimate of traffic volume for local roads, we conducted a sensitivity analysis by running the model using 200 and 300 vehicles/day for one of the counties that make up the TCMR.
-With the exception of a few areas in the rural part of the county, there was less than 0.05 dBA difference at 30 m from the road centerline, suggesting that the estimated values are not sensitive to the traffic volume variations used for the sensitivity analysis.}
+This estimate was based on factors identified in the literature as important for estimating traffic volume, such as census data on commuting population, tract area, the size of a standard street block, and road type \citep{Cheng1992, Fricker1986}.\footnote{In order to assess the sensitivity of our results to our estimate of traffic volume for local roads, we also ran the model using 200 and 300 vehicles/day for one of the counties that make up the TCMR.
+With the exception of a few areas in the rural part of the county, there was less than 0.05 dBA difference at 30 m from the road centerline.}
 
 Data on traffic volume and the proportion of trucks and vehicles on each segment of the road were averaged over a 24-hour period, making it impossible to account for a day and night time variation in traffic noise.
-Following \citet{Arditi2007}, we divided the total traffic volume into day and nighttime periods by assuming that 80 percent of vehicles and 65 percent of trucks are driven during the daytime (6am–10pm) and 35 percent of trucks and 20 percent of vehicles are driven during the nighttime (10pm-6am).
+Following \citet{Arditi2007}, we divided the total traffic volume into day and nighttime periods by assuming that 80 percent of vehicles and 65 percent of trucks are driven during the daytime (6am -- 10pm) and 35 percent of trucks and 20 percent of vehicles are driven during the nighttime (10pm--6am).
 Values for ground absorption were chosen by assuming that all road surfaces consisted of impervious bitumen.
@@
 \end{equation}
-Where Noise$_i$ is the noise level for house $i$, $S_i$ is a vector of the house's structural attributes, $N_i$ is a vector of the neighborhood attributes, and $T_i$ is a vector of year fixed effects.
+Where Noise$_i$ is the noise level for house $i$, $S_i$ is a vector of the house's structural attributes, $N_i$ is a vector of the neighborhood attributes, and $T_i$ is a vector of time fixed effects.
 We can interpret the regression model coefficients as the price semi-elasticities of the underlying attributes.
@@
 
-Standard urban economic theory\footnote{Cite Muth, Mills, etc.
-here.} predicts that the price of land will vary over space within our dataset to account for locational amenities.
+Standard urban economic theory \citep{Alonso1964, Mills1967, Muth1969} predicts that the price of land will vary over space within our dataset to account for locational amenities.
 As such, we add interaction terms between lot size and distance to the nearest central business district to account for spatial variation in the price of land.
@@
 The significant coefficients on the lot size interaction terms suggest that the value of land varies over space.
-The significant coefficients on the non-linear interaction terms suggests that the nature of the spatial variation in the value of land may be complex.
 
@@
                    \end{equation*}
+The GCV score is a convenient model selection metric that rewards models that provide a good fit to the data, while penalizing models with a greater number of model parameters \citep{Loader1999, McMillen2010}.
+Such semi-parametric models have been shown to discern whether spatially varying relationships exist, accurately estimate spatially varying coefficients, even outperform other spatial econometric techniques, and do so without wasting degrees of freedom \citep{Paez2011, McMillen2010, McMillen2012}.
+
 \section{Results}
@@
   `` nearest Lake & 2.5E-05 & 2.1E-06 & -2.8E-05 & 1.4E-04 & 0.35 & 0.00 \\ 
-  `` nearest Shopping Center & -5.3E-06 & 1.3E-06 & 1.5E-05 & 8.8E-05 & 0.29 & 0.00 \\  
+  `` nearest Shop & -5.3E-06 & 1.3E-06 & 1.5E-05 & 8.8E-05 & 0.29 & 0.00 \\  
   location of sale & \multicolumn{2}{c}{city fixed effects} & \multicolumn{4}{c}{\footnotesize city fixed effects and nearest 200 sales} \\
@@
 The smallest of these GCV scores was 0.041, just as was the case with the global (non-LWR) model.
-In other words, after running thousands of regressions on the shuffled data, we never obtained results anywhere near LWR model with our true locational data.
+In other words, after running thousands of regressions on the shuffled data, we never obtained model performance anywhere near the LWR model with our true locational data.
 This seems to be strong evidence that the increased ability to predict house prices with a local model is not due to chance.
@@
 In the second simulation, we seek to explore which of the hedonic regression coefficients exhibit spatial non-stationarity.
-We repeat the Monte Carlo simulation described earlier, but only at the optimal bandwidth calculated in original LWR model and we also kept track of the standard deviation of the estimated LWR coefficients for each variable.
+We repeat the Monte Carlo simulation described earlier, but only at the optimal bandwidth from the original LWR model.
+We collected the standard deviation of the estimated LWR coefficients for each variable in each iteration of the simulation.
 The intuition of the simulation is as follows: a variable might truly exert a spatially stationary effect on house prices, but our estimates vary over space due to chance.
@@
 Additionally, the coefficients also begin to a significant negative trend.
-\begin{table}[h]
-\caption{Regression Results: Dependent Variable = Traffic Noise LWR Coefficients}\label{tab:betaMAX}
-\begin{verbatim}
-            Estimate Std. Error t value Pr(>|t|)   
-(Intercept) -1.7e-03   4.1e-05   -43.4   < 2e-16 ***
-Month        6.9e-06   2.0e-06     3.5  0.000498 ***
-Post        -8.0e-04   7.2e-05   -11.1   < 2e-16 ***
-Month*Post  -8.9e-05   4.5e-06   -19.7   < 2e-16 ***
----
-Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
-
-Residual standard error: 0.002814 on 31744 degrees of freedom
-Multiple R-squared: 0.09289,  Adjusted R-squared: 0.09281 
-F-statistic:  1084 on 3 and 31744 DF,  p-value: < 2.2e-16 
-\end{verbatim}
+\begin{table}[htb]
+\caption{Dependent Variable = Traffic Noise LWR Coefficients}\label{tab:betaMAX}
+\begin{center}
+\begin{tabular}{lrrr}
+           & Estimate & Std.\ Err. & t-stat  \\  \hline
+(Intercept) & -1.7e-03 &  4.1e-05 &  -43.4   \\
+Month       & 6.9e-06 &  2.0e-06  &   3.5    \\
+Post        &-8.0e-04 &  7.2e-05  & -11.1    \\
+Month*Post  &-8.9e-05 &  4.5e-06  & -19.7    \\ \hline
+%\multicolumn{5}{l}{Residual standard error: 0.0028 with df = 31,744} \\
+\multicolumn{4}{l}{R$^2$: 0.093,  Adjusted R$^2$: 0.093} \\
+%\multicolumn{4}{l}{Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1}
+\end{tabular}
+\end{center}
 \end{table}
 
-The results in Table \ref{tab:betaMAX} contradict the a priori expectation that environmental amenities will ``matter'' less during and after the Great Recession.
+The results in Table \ref{tab:betaMAX} contradict the a priori expectation that environmental amenities will ``matter'' less during and after the Great Recession compared to the housing boom.
 In fact, these results suggest that the penalty for homes exposed to higher levels of traffic noise increased.
 That is, the negative hedonic coefficients on traffic noise got more negative after September 2008.
-It should be noted that our model can explain almost 10 percent of the variation in traffic noise LWR coefficient estimates.
+It should be noted that our simple model can explain almost 10 percent of the variation in traffic noise LWR coefficient estimates.
 
@@
 \begin{table}
+\begin{center}
 \caption{LWR Noise Coefficients vs.\ Noise Levels}\label{tab:LWRnonlinear}
-\begin{verbatim}
-            Estimate Std. Error t value Pr(>|t|)    
-(Intercept) -1.75e-03  1.31e-04  -13.3   <2e-16 ***
-Noise       -2.76e-06  2.27e-06   -1.2    0.223    
-Post        -3.55e-03  2.20e-04  -16.2   <2e-16 ***
-Noise:Post   3.39e-05  4.01e-06    8.5   <2e-16 ***
----
-Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
-
-Residual standard error: 0.002829 on 31,744 degrees of freedom
-Multiple R-squared: 0.08329,  Adjusted R-squared: 0.08321 
-F-statistic: 961.4 on 3 and 31744 DF,  p-value: < 2.2e-16 
-\end{verbatim}
+\begin{tabular}{lrrr}
+         &   Estimate & Std.\ Err. & t-value \\ \hline
+(Intercept) & -1.8e-03 & 1.3e-04  &-13.3 \\
+Noise       & -2.8e-06 & 2.3e-06  & -1.2 \\  
+Post        & -3.6e-03 & 2.2e-04  &-16.2 \\
+Noise:Post  &  3.4e-05 & 4.0e-06  &  8.5 \\ \hline
+%\multicolumn{4}{Residual standard error: 0.003 with df = 31,744}
+\multicolumn{4}{l}{R$^2$: 0.083,  Adjusted R$^2$: 0.083} 
+%F-statistic: 961.4 on 3 and 31744 DF,  p-value: < 2.2e-16 
+\end{tabular}
+\end{center}
 \end{table}

### 2013-09-14 reports/Draft.Rnw
updated descriptive stats by year table

@@
 \begin{table}
-\caption{Mean Variable Values Across Time}\label{tab:SumStatsTime}
-\includegraphics[width = \textwidth]{../graphs/DescriptiveStatsByYear}
+\begin{center}
+\caption{Mean Variable Values by Year}\label{tab:SumStatsTime}
+\small
+%\includegraphics[width = \textwidth]{../graphs/DescriptiveStatsByYear}
+% Table generated by Excel2LaTeX from sheet 'Descriptive StatisticsYear'
+    \begin{tabular}{lrrrrrrr}
+    Variable & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & All \\ \hline
+    Sales Value (\$1000s) & 279   & 282   & 275   & 263   & 231   & 233   & 266 \\
+    House Size (ft$^2$) & 1737  & 1736  & 1743  & 1813  & 1727  & 1775  & 1750 \\
+    Lot Size (acres) & 0.25  & 0.25  & 0.25  & 0.26  & 0.25  & 0.26  & 0.25 \\
+    Year Built  & 1967  & 1966  & 1966  & 1971  & 1968  & 1968  & 1967 \\
+    Traffic Noise (dB) & 58.5  & 58.6  & 58.6  & 52.5  & 52.8  & 52.8  & 56.4 \\
+    Median Income (\$1000s) & 72.0  & 72.1  & 72.3  & 74.8  & 72.6  & 73.2  & 72.6 \\
+    Elem. Test Scores & 364.8 & 364.8 & 365.2 & 363.5 & 362.3 & 366.1 & 364.5 \\
+    Dist. to CBD (km) & 14.7  & 14.6  & 14.8  & 15.0  & 14.3  & 14.5  & 14.7 \\
+    Dist. to Park (km) & 2.6   & 2.6   & 2.6   & 2.8   & 2.6   & 2.6   & 2.6 \\
+    Dist. to Lake (km) & 0.9   & 0.9   & 0.9   & 0.9   & 0.9   & 0.9   & 0.9 \\
+    Dist. to Shop (km) & 1.9   & 1.9   & 1.8   & 2.0   & 1.9   & 1.9   & 1.9 \\ \hline
+    Number of observations &          10,991  &          8,885  &          6,549  &          5,503  &          5,961  &          4,206  &          42,095  \\
+    \end{tabular}%
+\end{center}
 \end{table}

### 2013-09-15 reports/Draft.Rnw
added global regression table
few more edits to intro

@@
 
+\newcommand\T{\rule{0pt}{2.6ex}}       % Top strut
+\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} % Bottom strut
 \newcolumntype{x}[1]{%
@@
 While the hedonic literature has consistently shown a negative effect of this phenomenon on the real estate market, the relationship between housing prices and automobile traffic noise has rarely been explored at landscape level, especially in the United States.
-Here, we show this relationship by modeling the propagation of traffic noise over the landscape and by analyzing the extent of its impact on single-family home transactions in the urban area surrounding St.
-Paul, Minnesota using spatially explicit local regression techniques.
+Here, we show this relationship by modeling the propagation of traffic noise over the landscape and by analyzing the extent of its impact on single-family home transactions in the urban area surrounding St.\ Paul, Minnesota using spatially explicit local regression techniques.
 Our estimate of the negative relationship between traffic noise levels and house prices is smaller in magnitude than most of the relevant published literature.
@@
 Reviews of the research by \citet{Bateman2001} found that the negative effect of traffic noise on house prices ranged from 0.08 to 2.22 percent per decibel with a mean around 0.55 percent per decibel, while \citet{Navrud2002} found an average decrease of 0.64 percent per decibel.
-However, much of the research in these reviews and subsequent work has tended to focus on the European experience with noise, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Switzerland \citep{Baranzini2010}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, Netherlands \citep{Theebe2004a}, and Germany \citep{Brandt2011}.
+Much of the research in this literature has tended to focus on the European experience with noise, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Switzerland \citep{Baranzini2010}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, Netherlands \citep{Theebe2004a}, and Germany \citep{Brandt2011}.
 
@@
 
-In this paper, we seek to contribute to the noise hedonic literature by examining the relationship between single family home prices from 2005 to 2010 and variation in road traffic noise exposure in the St.\ Paul, Minnesota urban area.
-Our work makes multiple contributions to the field.
-First, we utilize new estimates of traffic noise that has never before been used in the hedonic literature.
+In this paper, we contribute to the noise hedonic literature by examining the relationship between single family home prices from 2005 to 2010 and variation in road traffic noise exposure in the St.\ Paul, Minnesota urban area across 44 different cities.
+First, we utilize new estimates of traffic noise that have never before been used in the hedonic literature.
 The noise propagation model estimates traffic noise levels at a high spatial resolution (10m x 10m) while also incorporating the effects of nearby buildings and landcover.
@@
 Lastly, we present the first estimates of the implicit price of traffic noise after the Great Recession and the housing bubble collapse of 2008-09.
-Contrary to work such as \citet{Cho2011b}, which found that environmental amenities mattered less after the housing crash, our estimated effect of traffic noise mattered more after the recession (0.37 percent reduction in house prices per additional decibel) compared to beforehand (0.19 percent per decibel).
+Contrary to work such as \citet{Cho2011b}, which found that environmental amenities mattered less after the housing crash, our estimated effect of traffic noise mattered more after the recession (0.37 percent reduction in house prices per additional decibel) compared to only 0.19 percent per decibel beforehand.
 
@@
 
-\makebox[\textwidth][c]{\includegraphics[width = 1.3\textwidth]{../graphs/GlobalRegression}}
+\makebox[\textwidth][c]{%\includegraphics[width = 1.3\textwidth]{../graphs/GlobalRegression}}
+% Table generated by Excel2LaTeX from sheet 'Sheet1'
+  \centering
+  \tabcolsep=0.03cm
+    \begin{tabular}{lclcclcclccl}
+   & (1)   &       &       & (2)   &       &       & (3)   &       &       & (4)   &  \\ \hline
+\T  Intercept & 9.37E+00 & ***   & \hspace{.5cm} & 9.49E+00 & ***   & \hspace{.5cm}   & 8.55E+00 & ***   & \hspace{.5cm}   & 1.10E+01 & *** \\
+          & (9.48E-02) &    &   & (9.62E-02) &   &   & (1.11E-01) &       &       & (2.12E-01) &  \\
+\T   House Size & 3.38E-04 & ***   &   & 3.39E-04 & ***   &   & 3.35E-04 & ***   &   & 3.50E-04 & *** \\
+          & (1.85E-06) &   &   & (1.86E-06) &       &       & (1.99E-06) &       &       & (4.26E-06) &  \\
+\T  Lot Size & 1.42E-01 & ***   &    & 2.74E-01 & ***   &   & 2.31E-01 & ***   &      & 2.74E-01 & *** \\
+          & (1.14E-02) &     &   & (2.12E-02) &     &      & (2.29E-02) &       &       & (4.99E-02) &  \\
+\T  Owner Occupancy & 3.22E-02 & ***   &   & 3.23E-02 & ***   &     & 3.38E-02 & ***  & & 2.61E-02 & *** \\
+          & (2.80E-03) &  &   & (2.79E-03) &       &       & (3.24E-03) &       &       & (6.41E-03) &  \\
+\T  Year Built & 7.82E-04 & ***   &   & 7.17E-04 & ***   &    & 9.68E-04 & ***   &   & 2.15E-06 &  \\
+          & (4.57E-05) &       &       & (4.65E-05) &   &   & (5.06E-05) &    &   & (1.05E-04) &  \\
+\T  Traffic Noise & -2.02E-03 & *** &   & -2.00E-03 & ***   &   & -1.63E-03 & ***  & & -3.08E-03 & *** \\
+          & (1.32E-04) &   &   & (1.32E-04) &       &       & (1.38E-04) &       &       & (3.29E-04) &  \\
+\T  Median Income & 3.03E-06 & ***  & & 3.31E-06 & ***  &   & 2.86E-06 & ***   &       & 4.06E-06 & *** \\
+          & (5.87E-08) &       &       & (5.87E-08) &   &   & (6.56E-08) &       &       & (1.35E-07) &  \\
+\T  Elem. Test Scores & 1.88E-03 & *** &   & 1.81E-03 & ***   &   & 3.11E-03 & *** & & 1.21E-03 & *** \\
+          & (1.06E-04) &  &   & (1.06E-04) &   &       & (1.75E-04) &       &       & (1.55E-04) &  \\
+\T  Distance to CBD & -1.56E-06 & ***  &  & 7.46E-07 & *     &  & -1.57E-07 &   &       & 1.40E-06 &  \\
+          & (1.97E-07) &       &       & (3.70E-07) &       &       & (3.95E-07) &   &   & (8.98E-07) &  \\
+\T  Distance to Park & -2.38E-07 &   &    & -5.48E-07 &    &   & -6.37E-07 &  &   & -4.01E-07 &  \\
+          & (6.82E-07) & &   & (6.83E-07) &       &       & (7.33E-07) &       &       & (1.58E-06) &  \\
+\T  Distance to Lake & 2.12E-05 & ***   &   & 2.36E-05 & ***   &   & 2.22E-05 & ***   & & 2.79E-05 & *** \\
+          & (1.68E-06) &       &    & (1.71E-06) &   &    & (1.83E-06) & &  & (4.03E-06) &  \\
+\T  Distance to Shop & 3.01E-06 & ***   &    & 3.12E-06 & ***   & & 4.16E-06 & ***   &    & 1.88E-06 &  \\
+          & (7.67E-07) &       &       & (7.66E-07) &       &       & (8.17E-07) &  & & (1.82E-06) &  \\
+\T  Lot size * Distance to CBD &  &   & & -8.81E-06 & *** & & -6.66E-06 & ***   &       & -9.55E-06 & ** \\
+          &   &   &   & (1.19E-06) &       &       & (1.27E-06) &       &       & (2.94E-06) &  \\
+\T  County Fixed Effects & yes   &   &   & yes   &       &       & yes   &       &       & yes   &  \\
+    Year of Sale Fixed Effects & yes   &   &   & yes   &   &       & yes   &       &       & yes   &  \\
+    Month of Sale Fixed Effects & yes   &   &   & yes   &   &       & yes   &       &       & yes   &  \\ \hline
+\T  Number of Observations &        42,095  &   &  &    42,095  & & &   31,253  & & &    10,842  &  \\
+    R$^2$   & 0.696 &       &       & 0.696 &       &       & 0.714 &       &       & 0.613 &  \\
+ \multicolumn{12}{c}{(standard errors) ***$p<.001$; **$p<.01$; *$p<.05$}  \\
+    \end{tabular}%
+}
 \end{table}
 
+The results of four regression models are displayed in Table \ref{tab:globalRegression}.
+The first column implements a basic regression as described in equation \eqref{eq:model} and estimates the impact of traffic noise to be roughly 0.002, or a 0.2 percent reduction in house prices for each additional decibel of traffic noise.
 Standard urban economic theory \citep{Alonso1964, Mills1967, Muth1969} predicts that the price of land will vary over space within our dataset to account for locational amenities.
-As such, we add interaction terms between lot size and distance to the nearest central business district to account for spatial variation in the price of land.
-The first column in Table \ref{tab:globalRegression} shows the results of this regression.
-The negative coefficient of -0.0027 on the noise variable (a one dB increase in noise decreases house price by 0.27 percent) is in line with the estimates described earlier in the literature.
-The significant coefficients on the lot size interaction terms suggest that the value of land varies over space.
+As such, we add interaction terms between lot size and distance to the Central Business District to account for spatial variation in the price of land in the second column in Table \ref{tab:globalRegression}.
+The significant coefficients on the interaction term suggest that the value of land varies over space.
+We also find significant coefficients in regressions including interaction terms between quadratic forumations of distance to the Central Business District and lot size, thereby suggesting that the relationship between lot size and house prices exhibits non-linearities over space.
 
 Table \ref{tab:globalRegression} also attempts to begin to understand how the economic recession may have influenced the hedonic function in our study area.
-The other columns in the table show the regression output from separating the data into sales before and after September of 2008 (the month that the US Federal government took over Fannie Mae and Freddie Mac, Lehman Brothers filed for bankruptcy, and the American International Group (AIG) narrowly avoided bankruptcy only through a \$85 billion loan from the US Federal government).\footnote{\url{http://www.federalreserve.gov/newsevents/press/other/20080916a.htm}} The coefficients for some of the hedonic variables of interest (noise, schools, land, for instance) appear different across the two time periods.
+Columns (3) and (4) in the table show the regression output from separating the data into sales before and after September of 2008 (the month that the US Federal government took over Fannie Mae and Freddie Mac, Lehman Brothers filed for bankruptcy, and the American International Group (AIG) narrowly avoided bankruptcy only through a \$85 billion loan from the US Federal government).\footnote{\url{http://www.federalreserve.gov/newsevents/press/other/20080916a.htm}} The coefficients for some of the hedonic variables of interest (noise, income, and schools, for instance) appear different across the two time periods.
 

### 2013-09-30 reports/Draft.Rnw
another round of editing, updated correlation matrix, etc.

--- 2013-09-14 reports/Draft.Rnw
@@
 
-\title{A Hedonic Price Analysis of Traffic Noise in the Twin Cities Housing Market}
+\title{The Negative Effect of Traffic Noise on House Prices: A Landscape Hedonic Analysis}
 \date{\today}
@@
 \citet{Delucchi1998} used an estimate of 0.85 percent reduction in house prices per additional decibel in their cost-benefit analysis of traffic noise.
-While their preferred estimate of the total damage cost to the United States in 1991 is \$3 billion, they report a possible range of less than \$100 million to over \$40 billion due to uncertainty surrounding the degree of noise propagation over space in the urban built environment and the effect of noise on house prices.
+While their preferred estimate of the total damage cost to the United States in 1991 is \$3 billion, they report a possible range of less than \$100 million to over \$40 billion due in part to uncertainty surrounding the degree of noise propagation over space in the urban built environment and the effect of noise on house prices.
 Indeed, one of the main conclusions of their work is that more research should be done to better understand the impact of noise on house prices and that better noise data are needed for such work to occur.
@@
 Furthermore, it is computationally very intensive.
-Fortunately, recent developments in Geographic Information Systems and distributive computing have reduced these difficulties, making it much easier to create a noise surface map at landscape level.
+Fortunately, recent developments in Geographic Information Systems and distributive computing have reduced these difficulties, making it much easier to create a noise surface map at landscape level with high spatial resolution.
 
@@
 Our work makes multiple contributions to the field.
-First, we utilize new estimates of traffic noise that has never before been used in the hedonic literature.
+First, we utilize new estimates of traffic noise that have never before been used in the hedonic literature.
 The noise propagation model estimates traffic noise levels at a high spatial resolution (10m x 10m) while also incorporating the effects of nearby buildings and landcover.
@@
 
-Lastly, we present the first estimates of the implicit price of traffic noise after the Great Recession and the housing bubble collapse of 2008-09.
+Lastly, we present the first estimates of the implicit price of traffic noise after the housing market collapse and Great Recession of 2008-09.
 Contrary to work such as \citet{Cho2011b}, which found that environmental amenities mattered less after the housing crash, our estimated effect of traffic noise mattered more after the recession (0.37 percent reduction in house prices per additional decibel) compared to beforehand (0.19 percent per decibel).
@@
 Table \ref{tab:sumStats} provides a brief description of the variables in our data and some basic summary statistics.
-Table \ref{tab:cor} shows a simple correlation matrix of the quantitative variables.
+Table \ref{tab:cor} displays a simple correlation matrix of the quantitative variables.
 
@@
   \hline
-  Sale Price (thousands \$) & 98.8 & 195.0 & 241.0 & 265.5 & 314.9 & 675.0 & 102.8 \\ 
-  House Size (feet$^2$) & 390 & 1158 & 1628 & 1750 & 2188 & 4000 & 704 \\ 
+  Sale Price (\$1,000s) & 98.8 & 195.0 & 241.0 & 265.5 & 314.9 & 675.0 & 102.8 \\ 
+  House Size (square feet) & 390 & 1158 & 1628 & 1750 & 2188 & 4000 & 704 \\ 
   Lot Size (acres) & 0.02 & 0.17 & 0.25 & 0.25 & 0.31 & 0.60 & 0.11 \\ 
@@
   Traffic Noise (dB) & 25.1 & 50.5 & 55.3 & 56.4 & 62.2 & 91.5 & 8.8 \\ 
-  Median Income in Census Tract (thousands \$) & 13.9 & 54.6 & 69.1 & 72.6 & 89.7 & 143.3 & 23.6 \\ 
+  Median Income in Census Tract (\$1,000s) & 13.9 & 54.6 & 69.1 & 72.6 & 89.7 & 143.3 & 23.6 \\ 
   Average 3rd Grade Standardized Test Scores & 335.6 & 359.8 & 365.4 & 364.5 & 370.4 & 551.7 & 10.6 \\ 
@@
   \hline
-ln Sale Price & 1 &  &  &  &  &  &  &  &  &  &  \tabularnewline 
+Sale Price & 1 &  &  &  &  &  &  &  &  &  &  \tabularnewline 
   House Size & 0.74 & 1 &  &  &  &  &  &  &  &  &  \tabularnewline
-  Lot Size & 0.40 & 0.45 & 1 &  &  &  &  &  &  &  &  \tabularnewline 
-  Year Built & 0.49 & 0.52 & 0.47 & 1 &  &  &  &  &  &  &  \tabularnewline 
-  Noise & -0.12 & -0.07 & 0.00 & -0.19 & 1 &  &  &  &  &  &  \tabularnewline 
-  Income & 0.55 & 0.50 & 0.41 & 0.57 & -0.18 & 1 &  &  &  &  &  \tabularnewline
-  Elem. Test Scores & 0.33 & 0.28 & 0.29 & 0.34 & -0.04 & 0.44 & 1 &  &  &  &  \tabularnewline 
-  Distance to CBD & 0.35 & 0.45 & 0.43 & 0.58 & -0.04 & 0.53 & 0.35 & 1 &  &  &  \tabularnewline
-  Distance to Park & 0.27 & 0.28 & 0.22 & 0.42 & -0.13 & 0.38 & 0.22 & 0.57 & 1 &  &  \tabularnewline
-  Distance to Lake & -0.05 & -0.10 & -0.25 & -0.17 & -0.03 & -0.12 & -0.10 & -0.09 & 0.20 & 1 &  \tabularnewline
-  Distance to Shop & 0.28 & 0.27 & 0.15 & 0.37 & -0.19 & 0.36 & 0.18 & 0.46 & 0.38 & 0.15 & 1 \tabularnewline
+  Lot Size & 0.38 & 0.45 & 1 &  &  &  &  &  &  &  &  \tabularnewline
+  Year Built & 0.45 & 0.52 & 0.47 & 1 &  &  &  &  &  &  &  \tabularnewline
+  Noise & -0.13 & -0.07 & 0.00 & -0.19 & 1 &  &  &  &  &  &  \tabularnewline
+  Income & 0.52 & 0.50 & 0.41 & 0.57 & -0.18 & 1 &  &  &  &  &  \tabularnewline
+  Elem.\ Test Scores & 0.29 & 0.28 & 0.29 & 0.34 & -0.04 & 0.44 & 1 &  &  &  &  \tabularnewline 
+  Distance to CBD & 0.31 & 0.45 & 0.43 & 0.58 & -0.04 & 0.53 & 0.35 & 1 &  &  &  \tabularnewline
+  Distance to Park & 0.25 & 0.28 & 0.22 & 0.42 & -0.13 & 0.38 & 0.22 & 0.57 & 1 &  &  \tabularnewline
+  Distance to Lake & -0.04 & -0.10 & -0.25 & -0.17 & -0.03 & -0.12 & -0.10 & -0.09 & 0.20 & 1 &  \tabularnewline
+  Distance to Shop & 0.27 & 0.27 & 0.15 & 0.37 & -0.19 & 0.36 & 0.18 & 0.46 & 0.38 & 0.15 & 1 \tabularnewline
 \end{tabular} }
@@
 According to a review by \cite{Wilhelmsson2000}, the most common structural attributes included in real-estate hedonic pricing studies are living area, number of bathrooms, age, garage and lot size.
-Although the 2010 MetroGIS Regional Parcel Dataset includes structural data on living area, age, garage presence, lot size and owner occupancy for every transaction, we have variables for the number of bedrooms, bathrooms, and size of the garage only for those house sales in one county.
+Although the 2010 MetroGIS Regional Parcel Dataset includes structural data on living area, age, garage presence, lot size, owner-occupancy and house architectural style for every transaction, we have variables for the number of bedrooms, bathrooms, and size of the garage for house sales in one county.
 We feel confident in our results even without these independent variables for most of our study data because sensitivity analysis conducted in areas with the additional structural variables revealed very similar estimates when the variables were included and excluded.
@@
 \subsection{Noise Data}
+Should we cite previous work that uses these data?
+
 To determine the relationship between real estate price and road traffic noise levels, we first created a traffic noise exposure surface for the entire Twin Cities Metro Region (TCMR) by calculating the propagation of traffic noise over the landscape using the FHWA (Federal Highway Authority) 1978 standard \citep{Barry1978}.
@@
 While the mean sale price declined from roughly \$280,000 pre-crash to \$230,000 post-crash, most of the structural and neighborhood variables are relatively consistent across years.
-However, traffic noise displays a noticeable difference in the pre- and post-crash market transactions (the mean drops from 58 dB to 52 dB).
+However, traffic noise displays a noticeable difference in the pre- and post-crash market transactions (the mean drops from over 58 dB to less than 53 dB).
 
 \begin{table}
-\caption{Mean Variable Values Across Time}\label{tab:SumStatsTime}
-\includegraphics[width = \textwidth]{../graphs/DescriptiveStatsByYear}
+\begin{center}
+\caption{Mean Variable Values by Year}\label{tab:SumStatsTime}
+\small
+%\includegraphics[width = \textwidth]{../graphs/DescriptiveStatsByYear}
+% Table generated by Excel2LaTeX from sheet 'Descriptive StatisticsYear'
+    \begin{tabular}{lrrrrrr|r}
+    Variable & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2005-10\\ \hline
+    Sales Value (\$1000s) & 279   & 282   & 275   & 263   & 231   & 233   & 266 \\
+    House Size (ft$^2$) & 1737  & 1736  & 1743  & 1813  & 1727  & 1775  & 1750 \\
+    Lot Size (acres) & 0.25  & 0.25  & 0.25  & 0.26  & 0.25  & 0.26  & 0.25 \\
+    Year Built  & 1967  & 1966  & 1966  & 1971  & 1968  & 1968  & 1967 \\
+    Traffic Noise (dB) & 58.5  & 58.6  & 58.6  & 52.5  & 52.8  & 52.8  & 56.4 \\
+    Median Income (\$1000s) & 72.0  & 72.1  & 72.3  & 74.8  & 72.6  & 73.2  & 72.6 \\
+    Elem. Test Scores & 364.8 & 364.8 & 365.2 & 363.5 & 362.3 & 366.1 & 364.5 \\
+    Dist. to CBD (km) & 14.7  & 14.6  & 14.8  & 15.0  & 14.3  & 14.5  & 14.7 \\
+    Dist. to Park (km) & 2.6   & 2.6   & 2.6   & 2.8   & 2.6   & 2.6   & 2.6 \\
+    Dist. to Lake (km) & 0.9   & 0.9   & 0.9   & 0.9   & 0.9   & 0.9   & 0.9 \\
+    Dist. to Shop (km) & 1.9   & 1.9   & 1.8   & 2.0   & 1.9   & 1.9   & 1.9 \\ \hline
+    Number of Observations &  10,991  & 8,885  &  6,549  &  5,503  &  5,961  & 4,206  & 42,095  \\
+    \end{tabular}%
+\end{center}
 \end{table}
@@
 
-\makebox[\textwidth][c]{\includegraphics[width = 1.3\textwidth]{../graphs/GlobalRegression}}
+\makebox[\textwidth][c]{%\includegraphics[width = 1.3\textwidth]{../graphs/GlobalRegression}}
+% Table generated by Excel2LaTeX from sheet 'Sheet1'
+  \centering
+  \tabcolsep=0.03cm
+    \begin{tabular}{lclcclcclccl}
+   & (1)   &       &       & (2)   &       &       & Pre-Crash   &       &       & Post-Crash   &  \\ \hline
+\T  Intercept & 9.37E+00 & ***   & \hspace{.5cm} & 9.49E+00 & ***   & \hspace{.5cm}   & 8.55E+00 & ***   & \hspace{.5cm}   & 1.10E+01 & *** \\
+          & (9.48E-02) &    &   & (9.62E-02) &   &   & (1.11E-01) &       &       & (2.12E-01) &  \\
+\T   House Size & 3.38E-04 & ***   &   & 3.39E-04 & ***   &   & 3.35E-04 & ***   &   & 3.50E-04 & *** \\
+          & (1.85E-06) &   &   & (1.86E-06) &       &       & (1.99E-06) &       &       & (4.26E-06) &  \\
+\T  Lot Size & 1.42E-01 & ***   &    & 2.74E-01 & ***   &   & 2.31E-01 & ***   &      & 2.74E-01 & *** \\
+          & (1.14E-02) &     &   & (2.12E-02) &     &      & (2.29E-02) &       &       & (4.99E-02) &  \\
+\T  Owner Occupancy & 3.22E-02 & ***   &   & 3.23E-02 & ***   &     & 3.38E-02 & ***  & & 2.61E-02 & *** \\
+          & (2.80E-03) &  &   & (2.79E-03) &       &       & (3.24E-03) &       &       & (6.41E-03) &  \\
+\T  Year Built & 7.82E-04 & ***   &   & 7.17E-04 & ***   &    & 9.68E-04 & ***   &   & 2.15E-06 &  \\
+          & (4.57E-05) &       &       & (4.65E-05) &   &   & (5.06E-05) &    &   & (1.05E-04) &  \\
+\T  Traffic Noise & -2.02E-03 & *** &   & -2.00E-03 & ***   &   & -1.63E-03 & ***  & & -3.08E-03 & *** \\
+          & (1.32E-04) &   &   & (1.32E-04) &       &       & (1.38E-04) &       &       & (3.29E-04) &  \\
+\T  Median Income & 3.03E-06 & ***  & & 3.31E-06 & ***  &   & 2.86E-06 & ***   &       & 4.06E-06 & *** \\
+          & (5.87E-08) &       &       & (5.87E-08) &   &   & (6.56E-08) &       &       & (1.35E-07) &  \\
+\T  Elem. Test Scores & 1.88E-03 & *** &   & 1.81E-03 & ***   &   & 3.11E-03 & *** & & 1.21E-03 & *** \\
+          & (1.06E-04) &  &   & (1.06E-04) &   &       & (1.75E-04) &       &       & (1.55E-04) &  \\
+\T  Distance to CBD & -1.56E-06 & ***  &  & 7.46E-07 & *     &  & -1.57E-07 &   &       & 1.40E-06 &  \\
+          & (1.97E-07) &       &       & (3.70E-07) &       &       & (3.95E-07) &   &   & (8.98E-07) &  \\
+\T  Distance to Park & -2.38E-07 &   &    & -5.48E-07 &    &   & -6.37E-07 &  &   & -4.01E-07 &  \\
+          & (6.82E-07) & &   & (6.83E-07) &       &       & (7.33E-07) &       &       & (1.58E-06) &  \\
+\T  Distance to Lake & 2.12E-05 & ***   &   & 2.36E-05 & ***   &   & 2.22E-05 & ***   & & 2.79E-05 & *** \\
+          & (1.68E-06) &       &    & (1.71E-06) &   &    & (1.83E-06) & &  & (4.03E-06) &  \\
+\T  Distance to Shop & 3.01E-06 & ***   &    & 3.12E-06 & ***   & & 4.16E-06 & ***   &    & 1.88E-06 &  \\
+          & (7.67E-07) &       &       & (7.66E-07) &       &       & (8.17E-07) &  & & (1.82E-06) &  \\
+\T  Lot Size * Distance to CBD &  &   & & -8.81E-06 & *** & & -6.66E-06 & ***   &       & -9.55E-06 & ** \\
+          &   &   &   & (1.19E-06) &       &       & (1.27E-06) &       &       & (2.94E-06) &  \\
+\T  County Fixed Effects & yes   &   &   & yes   &       &       & yes   &       &       & yes   &  \\
+    Year of Sale Fixed Effects & yes   &   &   & yes   &   &       & yes   &       &       & yes   &  \\
+    Month of Sale Fixed Effects & yes   &   &   & yes   &   &       & yes   &       &       & yes   &  \\ \hline
+\T  Number of Observations &        42,095  &   &  &    42,095  & & &   31,253  & & &    10,842  &  \\
+    R$^2$   & 0.696 &       &       & 0.696 &       &       & 0.714 &       &       & 0.613 &  \\
+ \multicolumn{12}{l}{(standard errors) ***$p<.001$; **$p<.01$; *$p<.05$}  \\
+    \end{tabular}%
+}
 \end{table}
 
+Column (1) in Table \ref{tab:globalRegression} displays the results of our basic regression model.
+All coefficients but one are significantly different from zero at convential significance levels.
+The traffic noise coefficient suggests that a one decibel increase traffic noise is on average associated with a 0.2 percent reduction in housing sales prices.
 Standard urban economic theory \citep{Alonso1964, Mills1967, Muth1969} predicts that the price of land will vary over space within our dataset to account for locational amenities.
-As such, we add interaction terms between lot size and distance to the nearest central business district to account for spatial variation in the price of land.
-The first column in Table \ref{tab:globalRegression} shows the results of this regression.
-The negative coefficient of -0.0027 on the noise variable (a one dB increase in noise decreases house price by 0.27 percent) is in line with the estimates described earlier in the literature.
+As such, we add an interaction term between lot size and distance to the nearest central business district to account for spatial variation in the price of land.
+The second column in Table \ref{tab:globalRegression} shows the results of this regression.
 The significant coefficients on the lot size interaction terms suggest that the value of land varies over space.
@@
 Table \ref{tab:globalRegression} also attempts to begin to understand how the economic recession may have influenced the hedonic function in our study area.
-The other columns in the table show the regression output from separating the data into sales before and after September of 2008 (the month that the US Federal government took over Fannie Mae and Freddie Mac, Lehman Brothers filed for bankruptcy, and the American International Group (AIG) narrowly avoided bankruptcy only through a \$85 billion loan from the US Federal government).\footnote{\url{http://www.federalreserve.gov/newsevents/press/other/20080916a.htm}} The coefficients for some of the hedonic variables of interest (noise, schools, land, for instance) appear different across the two time periods.
+Columns three and four estimate the same regression as (2) but subset the sales before and after September of 2008 (the month that Lehman Brothers filed for bankruptcy, the US Federal government took over Fannie Mae and Freddie Mac, and the American International Group (AIG) narrowly avoided bankruptcy only through a \$85 billion loan from the US Federal government).\footnote{\url{http://www.federalreserve.gov/newsevents/press/other/20080916a.htm}} The coefficients for some of the hedonic variables of interest (noise, schools, land, for instance) appear different across the two time periods.
 
-Taken in aggregate, the results in Table \ref{tab:globalRegression} suggest that the hedonic price function may vary over space and time.
+Taken in aggregate, the results in Table \ref{tab:globalRegression} suggest that the hedonic price function likely varies over space and time.
 While methods exist for parameterizing this variation \citep[such as spatial expansion as suggested by][]{Casetti1972}, we have no a priori knowledge of how to parameterize the variation over space and time.
@@
 This function assigns weights close to 1 for data points near observation $i$, weights positive but closer to zero for observations farther away, and zero for all $n-k$ observations farther away than the $k^{th}$ nearest observation.
-We estimate LWR coefficients using bandwidths ranging from as small as 50 observations and as large as 10,000 observations.
+We estimate LWR coefficients using bandwidths ranging from as small as $k=50$ observations and as large as 10,000 observations.
 We choose the LWR bandwidth my minimizing the Generalized Cross Validation score as detailed in equation~\eqref{eq:GCV},
@@
   Lot Size & 2.6E-01 & 1.5E-02 & 4.0E-01 & 3.7E-01 & 0.67 & 0.00 \\ 
-  Year of Construction & 1.2E-03 & 6.5E-05 & 4.5E-03 & 5.4E-03 & 0.79 & 0.00 \\ 
+  Year Built & 1.2E-03 & 6.5E-05 & 4.5E-03 & 5.4E-03 & 0.79 & 0.00 \\ 
   Owner Occupancy & 2.7E-02 & 3.2E-03 & 2.3E-02 & 6.4E-02 & 0.37 & 1.00 \\ 
-  Elementary Test Scores & 1.5E-03 & 1.2E-04 & 2.4E-04 & 3.1E-02 & 0.30 & 0.00 \\ 
+  Elem.\ Test Scores & 1.5E-03 & 1.2E-04 & 2.4E-04 & 3.1E-02 & 0.30 & 0.00 \\ 
   Median Income & 3.3E-06 & 7.7E-08 & 9.6E-07 & 8.1E-06 & 0.35 & 0.00 \\ 
-  distance to CBD & 1.3E-05 & 6.3E-07 & 1.1E-05 & 1.0E-04 & 0.30 & 0.00 \\ 
-  `` nearest Park & -3.7E-07 & 1.1E-06 & -1.6E-05 & 1.3E-04 & 0.32 & 0.00 \\ 
-  `` nearest Lake & 2.5E-05 & 2.1E-06 & -2.8E-05 & 1.4E-04 & 0.35 & 0.00 \\ 
-  `` nearest Shop & -5.3E-06 & 1.3E-06 & 1.5E-05 & 8.8E-05 & 0.29 & 0.00 \\  
-  location of sale & \multicolumn{2}{c}{city fixed effects} & \multicolumn{4}{c}{\footnotesize city fixed effects and nearest 200 sales} \\
-  timing of sale & \multicolumn{2}{c}{year fixed effects} & \multicolumn{4}{c}{within last 12 months} \\
+  Dist.\ to CBD & 1.3E-05 & 6.3E-07 & 1.1E-05 & 1.0E-04 & 0.30 & 0.00 \\ 
+  Dist.\ to Park & -3.7E-07 & 1.1E-06 & -1.6E-05 & 1.3E-04 & 0.32 & 0.00 \\ 
+  Dist.\ to Lake & 2.5E-05 & 2.1E-06 & -2.8E-05 & 1.4E-04 & 0.35 & 0.00 \\ 
+  Dist.\ to Shop & -5.3E-06 & 1.3E-06 & 1.5E-05 & 8.8E-05 & 0.29 & 0.00 \\  
+  Location of Sale & \multicolumn{2}{c}{city fixed effects} & \multicolumn{4}{c}{\footnotesize city fixed effects and nearest 200 sales} \\
+  Timing of Sale & \multicolumn{2}{c}{year fixed effects} & \multicolumn{4}{c}{within last 12 months} \\
  \hline
@@
 
-The first column in Table \ref{tab:mainresults} displays the estimates from a standard semi-log OLS regression with traffice noise, structural characteristics, location-based amenities, and both city and year of sale dummy variables.
-The coefficient in the second row of the table shows the estimated impact of an additional dB of traffic noise on the natural log of the house sale price to be -.23 percent.
-This value is within the range of other estimates as described earlier in section \ref{sec:lit}.
-Coefficients for the dummy variables (on house style, city, and year of sale) are not reported for the sake of brevity, but are available upon request.
-The second column in the table reports the estimated coefficient standard errors.
-With the exception of the coefficient on the distance to the nearest park, all reported coefficients are statistically different from zero at conventional levels.
-
+Table \ref{tab:mainresults} presents the results of our preferred LWR model as well as a basic global OLS model for comparison.
+The first two columns display the estimates and standard errors from a basic semi-log OLS regression with traffic noise, structural characteristics, location-based amenities, and both city and year of sale dummy variables.
 The third column displays the mean estimated coefficients from the LWR model.
@@
 The fourth column displays the standard deviation of the estimated coefficients to give a sense of how the coefficients vary when allowed to do so through the use of locally weighted regression techniques.
+In addition to the significant reduction in the GCV score (0.041 vs.
+0.027) obtained with the use of LWR, we also see a substantal reduction in the degree of spatial autocorrlation in the model residuals.
+We calculate the Moran’s I statistic to be 0.199 for the global model while our prefered LWR specification reduces the Moran's I statistic to 0.012, a nearly twenty-fold reduction.
 
@@
 \subsection{Does the Hedonic Function Vary over Space?}
-We believe the use of a LWR estimation procedure is appropriate after conducting two different Monte Carlo simulations with the data as described in \citet{Fotheringham2002}.
+We believe the hedonic function varies significantly over space and the use of a LWR estimation procedure is appropriate.
+We conducted two different Monte Carlo simulations with the data as described in \citet{Fotheringham2002}.
 In each simulation we resampled (without replacement) the location of each house in the study and then re-estimated the LWR model with the locationally ``shuffled'' data.
+In both cases the results strongly suggest spatial non-stationarity in the hedonic function.
+
 In the first simulation we estimated the LWR model using bandwidths ranging from the nearest 50 to 10,000 sales just as before.
@@
 We collected the standard deviation of the estimated LWR coefficients for each variable in each iteration of the simulation.
-The intuition of the simulation is as follows: a variable might truly exert a spatially stationary effect on house prices, but our estimates vary over space due to chance.
-If this is the case, by shuffling the location of our observations and rerunning the LWR model, we should see a similar dispersion in regression coefficients over space.
-However, if the coefficient exhibits true spatial non-stationarity, it is unlikely that we will see as large of a standard deviation in the coefficient estimates after having reshuffled the data (because now the houses for which a coefficient exerts a strong effect are now no longer near each other).
+The intuition of this simulation is as follows: a variable might truly exert a spatially \emph{stationary} effect on house prices, but our estimates vary over space due to chance.
+If this is the case, by shuffling the location of our observations and rerunning the LWR model, we should see a similar dispersion in regression coefficients over space with the reshuffled data as with our actual data.
+However, if the coefficient exhibits true spatial \emph{non-stationarity}, it is unlikely that we will see such a large of a standard deviation in the coefficient estimates after having reshuffled the data (because now the houses for which a coefficient exerts a strong effect are probably no longer near each other).
 
-After $M = 100$ iterations of this simulation, the minimum GCV score for these resampled LWR models is 0.060, substantially larger than all models (global and local) with the actual data.
+After 100 iterations of this second simulation, the minimum GCV score for these resampled LWR models is 0.060, substantially larger than all models (global and local) with the actual data.
 The fourth column in Table \ref{tab:mainresults} displays the standard deviations of the LWR regression coefficients obtained with our data.
-Column (6) displays the proportion of Monte Carlo simulatons that yielded larger standard deviations of LWR coefficient estimates than those shown in column (4).
-For most variables, we never obtained a larger coefficient standard deviation in the simulation than we obtained from the LWR model with the actual data.
+Column (6) displays the proportion of Monte Carlo simulatons that yielded larger standard deviations of LWR coefficient estimates than those shown in column $\sigma_{\hat{\beta}}$.
+For most variables, we never obtained a larger standard deviation in the simulation than we obtained from the LWR model with the actual data.
 However, the values associated with the traffic noise and owner occupancy variables suggest that the variation in LWR coefficients in our data may have been due to random chance.
@@
 
-Figure \ref{fig:MCsds} visually shows the results presented in column (6) of Table \ref{tab:mainresults} another way.
+Figure \ref{fig:MCsds} visualizes the results of the second simulation.
 Each subfigure displays the distribution of LWR coefficient standard deviations obtained from the 100 iterations of the Monte Carlo simulation and the standard deviation obtained with the actual data (in red).
-Note that it is the case that the standard deviations obtained with the actual data are substantially larger than those obtained in the simulation for most of the variables.
+Note that it is the case that the standard deviations obtained with the actual data are typically substantially larger than those obtained in the simulation for most of the variables.
+However, the variation obtained in the traffic noise coefficients simulations is similar with our actual LWR results, suggesting that the spatial non-stationarity exhibited in this coefficient is likely due to chance and not true spatial non-stationarity in the effect of traffic noise on house prices.
 
@@
  \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{../graphs/MCsimResultsSDsClean}}
- \caption{Actual LWR Coefficient Standard Deviations \textcolor{red}{(red line)} vs.\ Distribution of Monte Carlo Simulation Standard Deviations by Variable.}\label{fig:MCsds}
+ \caption{Actual LWR Coefficient Standard Deviations \textcolor{red}{(red line)} vs.\ Distribution of Monte Carlo Simulation Standard Deviations by Variable.
+Figures in which the red line is to the right of the black distribution suggest spatial non-stationarity in effect of the variable on house prices in our study region.}\label{fig:MCsds}
 \end{figure}
 
-In addition to the LWR model with a bandwidth of the nearest 200 houses and a temporal lag of 12 months performing better than other bandwidths and model specifications in terms of the smallest GCV score, it also exhibits far less spatial autocorrelation within the model residuals.
-We calculate the Moran’s I statistic to be 0.199 for the global model while our prefered LWR specification reduces the Moran's I statistic to 0.012, a nearly twenty-fold reduction.
+The results of these simulations suggest that spatial non-stationarity exists in the hedonic function and that LWR techniques are able to capture a significant portion of the non-stationarity.
+Using a bandwidth of the nearest 200 houses and a temporal lag of 12 months not only yielded significantly smaller GCV scores compared to other bandwidths and model specifications, but such performance does not seem to be a result of a chance spatial arrangement of the data.
 
@@
 We know that house prices in the United States fell dramatically during and after the Great Recession of 2008-09.
-We know less about the patterns of change in the hedonic price functions during and after the fall in prices.
-\citet{Cho2011b} found evidence from hedonic analysis in the Nashville, Tennessee area that consumers' willingness to pay for environmental amenities (such as proximity to open space and water views) decreased during the recession as compared to the previous economic boom.
+We know less about the patterns of change in the hedonic price functions during and after the fall in house prices.
+\citet{Cho2011b} found evidence from hedonic analysis in Nashville, Tennessee,  that consumers' willingness to pay for environmental amenities (such as proximity to open space and water views) decreased during the recession as compared to the previous economic boom.
 
 In this section we look for evidence of temporal non-stationarity in the hedonic coefficient on traffic noise within our data.
-Specifically, we create two new variables, ``\texttt{months since September 2008}'' and a dummy variable ``\texttt{post}'' for all sales after September 2008.
+Specifically, we create two new variables, ``\texttt{months since September 2008}'' and a dummy variable ``\texttt{post}=1'' for all sales after September 2008.
 We then regress our LWR noise coefficients on these two variables and their interaction term as shown in equation \eqref{eq:LWRinteraction},
@@
 In particular, $\alpha_1 \neq 0$ suggests a linear temporal trend in the marginal willingness to pay to avoid traffic noise, while $\alpha_2 \neq 0$ suggests that there was a structural break after September 2008, and $\alpha_3 \neq 0$ will imply a change in the temporal trend after September 2008.
-The linear regression results presented in Table \ref{tab:betaMAX} show that there is a significant negative shock to the estimated LWR coefficients for traffic noise after September 2008.
-Additionally, the coefficients also begin to a significant negative trend.
+The linear regression results presented in Table \ref{tab:betaMAX} show that there the estimated LWR coefficients for traffic noise are significantly smaller after September 2008.
 \begin{table}[htb]
@@
 Month*Post  &-8.9e-05 &  4.5e-06  & -19.7    \\ \hline
-%\multicolumn{5}{l}{Residual standard error: 0.0028 with df = 31,744} \\
-\multicolumn{4}{l}{R$^2$: 0.093,  Adjusted R$^2$: 0.093} \\
+\multicolumn{4}{l}{Residual standard error: 0.003} \\
+\multicolumn{4}{l}{N = 31,748, R$^2$: 0.093} \\ %,  Adjusted R$^2$: 0.093
 %\multicolumn{4}{l}{Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1}
@@
 
-The results in Table \ref{tab:betaMAX} contradict the a priori expectation that environmental amenities will ``matter'' less during and after the Great Recession compared to the housing boom.
-In fact, these results suggest that the penalty for homes exposed to higher levels of traffic noise increased.
+The results in Table \ref{tab:betaMAX} contradict the expectation that environmental amenities will ``matter'' less during and after the Great Recession compared to the housing boom.
+In fact, these results suggest that the penalty for homes exposed to higher levels of traffic noise became more severe.
 That is, the negative hedonic coefficients on traffic noise got more negative after September 2008.
-It should be noted that our simple model can explain almost 10 percent of the variation in traffic noise LWR coefficient estimates.
 
-% \subsubsection{House Size}
-% 
-% In this section we show how the hedonic coefficients on house size (as measured in square feet) change over time.
-Table \ref{tab:betaSQFT} shows that the LWR coefficients on house size were positive and trending up before September 2008, then the coefficients drop significantly in both absolute value and their time trend.
-These results are consistent with the belief that the Great Recession would reduce consumer's marginal willingness to pay for increases in the size of a house.
-It should be noted that the model presented in Table \ref{tab:betaSQFT} explains less than one percent of the variation in our house size LWR coefficients.
-% 
-% \begin{table}[h]
-% \caption{Regression Results: Dependent Variable = House Size LWR Coefficients}\label{tab:betaSQFT}
-% \begin{verbatim}
-%               Estimate Std. Error t value Pr(>|t|)    
-% (Intercept)  2.741e-04  1.317e-06 208.097  < 2e-16 ***
-% month        8.742e-07  6.441e-08  13.573  < 2e-16 ***
-% Post        -1.678e-05  2.316e-06  -7.245 4.43e-13 ***
-% month:Post  -5.989e-07  1.440e-07  -4.157 3.23e-05 ***
-% ---
-% Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1 
-% 
-% Residual standard error: 9.04e-05 on 31744 degrees of freedom
-% Multiple R-squared: 0.006092,  Adjusted R-squared: 0.005998 
-% F-statistic: 64.85 on 3 and 31744 DF,  p-value: < 2.2e-16 
-% \end{verbatim}
-% \end{table}
-% 
-% \subsubsection{Lot Size}
-% 
-% Table \ref{tab:betaACRES} shows interesting results that are qualitatively different from our previous results.
-The post-September 2008 dummy variable coefficient is only marginally significant and small in absolute value (when compared to the regression Intercept term).
-There is no discernable change in the temporal trend of the lot size LWR coefficients.
-The model presented in Table \ref{tab:betaACRES} explains less than a half of one percent of the variation in lot size LWR coefficients.
-% 
-% \begin{table}[h]
-% \caption{Regression Results: Dependent Variable = Lot Size LWR Coefficients}\label{tab:betaACRES}
-% \begin{verbatim}
-% (Intercept)  0.3828690  0.0054089  70.785  < 2e-16 ***
-% month       -0.0015113  0.0002645  -5.713 1.12e-08 ***
-% Post         0.0190349  0.0095117   2.001   0.0454 *  
-% month:Post  -0.0001358  0.0005916  -0.229   0.8185    
-% ---
-% Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1 
-% 
-% Residual standard error: 0.3713 on 31744 degrees of freedom
-% Multiple R-squared: 0.002806,  Adjusted R-squared: 0.002711 
-% F-statistic: 29.77 on 3 and 31744 DF,  p-value: < 2.2e-16 
-% \end{verbatim}
-% \end{table}
-% 
-% \subsubsection{Intercept}
-% We were also interested in how the LWR regression intercept changed over time.
-For instance, perhaps the house price drops of the Great Recession were manifested primarily through reduced intercept terms.
-Table \ref{tab:betaINT} is not consistent with that hypothesis.
-In fact, our results show that the estimated LWR intercept terms are on average significantly higher post-September 2008.
-% \begin{table}[h]
-% \caption{Regression Results: Dependent Variable = LWR Intercept Estimates}\label{tab:betaINT}
-% \begin{verbatim}
-% (Intercept)  1.575488   0.213779   7.370 1.75e-13 ***
-% month       -0.043836   0.010455  -4.193 2.76e-05 ***
-% Post         2.845774   0.375939   7.570 3.84e-14 ***
-% month:Post   0.007397   0.023383   0.316    0.752    
-% ---
-% Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1 
-% 
-% Residual standard error: 14.67 on 31744 degrees of freedom
-% Multiple R-squared: 0.003282,  Adjusted R-squared: 0.003188 
-% F-statistic: 34.84 on 3 and 31744 DF,  p-value: < 2.2e-16  
-% \end{verbatim}
-% \end{table}
-
-\subsection{Does the Impact of Traffic Noise Vary Non-linearly?}
+\subsection{Are There Threshold Effects of Traffic Noise?}
 
@@
 Post        & -3.6e-03 & 2.2e-04  &-16.2 \\
-Noise:Post  &  3.4e-05 & 4.0e-06  &  8.5 \\ \hline
-%\multicolumn{4}{Residual standard error: 0.003 with df = 31,744}
-\multicolumn{4}{l}{R$^2$: 0.083,  Adjusted R$^2$: 0.083} 
+Noise*Post  &  3.4e-05 & 4.0e-06  &  8.5 \\ \hline
+\multicolumn{4}{l}{Residual standard error: 0.003} \\
+\multicolumn{4}{l}{N: 31,748, R$^2$: 0.083} \\
 %F-statistic: 961.4 on 3 and 31744 DF,  p-value: < 2.2e-16 
@@
 
-Our work suffers from at least two noticeable weaknesses.
-First, we are missing some important structural variables that are commonly used in the housing hedonic literature.
+The hedonic analysis results presented suggest that traffic noise exhibits a significant negative effect on house prices and that the hedonic function varies over space and time.
+These results and analysis rest on important assumptions, which if violated, may change the results.
+This section describes two assumptions that we think are most noteworthy of discussion: lack of omitted variable bias and temporal non-stationarity in the level of several variables across the region during our study period.
+
+Our data lack some important structural variables that are commonly used in the housing hedonic literature.
 To the extent that structural variables like the number of bedrooms, bathrooms, garage size, or construction quality covary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias.
@@
 \begin{center}
-\caption{A Comparison of the Noise Regression Coefficient Estimates in Dakota County with and without Additional Structural Variables}\label{tab:Dak}
-\begin{tabular}{lllc}
- & \multicolumn{2}{p{1.25in}}{Additional Variables Included in LWR?} & \\
-Locally Weighted Regression Model & \multicolumn{1}{c}{no} & \multicolumn{1}{c}{yes} & \\ \cline{1-3}
-\multirow{2}{*}{Model (1) = Structural Variables} & -0.0015 & -0.0015 & mean\\ 
-   & (0.0023) & (0.0031) & (st.\ dev.) \\[.2cm]
-\multirow{2}{*}{Model (2) = Model (1) + Locational Variables} & -0.0014 & -0.0014  & \\ 
-   & (0.0018) & (0.0022) &  \\[.2cm] 
-\multirow{2}{*}{Model (3) = Model (2) + City Fixed Effects} & -0.0014 & -0.0014 & \\ 
-   & (0.0022) & (0.0018) & \\ 
+\caption{Noise Regression Coefficient Estimates in Dakota County with and without Additional Structural Variables}\label{tab:Dak}
+\begin{tabular}{lll}
+ & \multicolumn{2}{p{1.25in}}{Additional Variables Included in LWR?} \\
+Locally Weighted Regression Model & \multicolumn{1}{c}{no} & \multicolumn{1}{c}{yes} \\ \cline{1-3}
+\multirow{2}{*}{Model (1) = Structural Variables} & -0.0015 & -0.0015 \\ 
+   & (0.0023) & (0.0031)  \\[.2cm]
+\multirow{2}{*}{Model (2) = Model (1) + Locational Variables} & -0.0014 & -0.0014  \\ 
+   & (0.0018) & (0.0022)  \\[.2cm] 
+\multirow{2}{*}{Model (3) = Model (2) + City Fixed Effects} & -0.0014 & -0.0014 \\ 
+   & (0.0022) & (0.0018) \\[.2cm] \cline{1-3}
+\multicolumn{3}{p{4.25in}}{Mean and (standard deviation) LWR traffic noise coefficients when the number of bedrooms, bathrooms, and garage size are included as additional control variables in the regression.}
 \end{tabular}
@@
 We also conducted simple linear regressions of the noise coefficients without the additional structural variables on the noise coefficients obtained with the additional structural variables for each of our three models.
-In all cases the intercept estimates were close zero with slopes almost exactly equal to one and each also had $R^2$ values over 0.7, signifying that the hedonic coefficients for the traffic noise variable are unaffected by omitted variable bias from common structural variables.
-While we cannot confirm that this lack of ommitted variable bias also occurs elsewhere in our data, the results from Dakota County are promising.
+In all cases the model intercept estimates were close zero, the slopes almost exactly equal to one, and $R^2$ values over 0.7.
+These results suggest the hedonic coefficients for traffic noise are unaffected by omitted variable bias from common structural variables.
+While we cannot confirm that this lack of omitted variable bias also occurs elsewhere in our data, the results from Dakota County are promising.
 
@@
 For instance, the US Department of Transportation reports that total vehicle miles travelled decreased by up to 4 percent year-on-year during the Great Recession.\footnote{\url{http://www.fhwa.dot.gov/ohim/tvtw/08dectvt}} Thus, our noise estimates may be inaccurate for later time periods and this may bias our estimates of the impact of noise on house values.
-Future work may seek to obtain time-series noise data in order to obtain even better estimates of the impact of traffic noise over time.
+Future work may seek to create time-series noise data in order to obtain even better estimates of the impact of traffic noise over time.
 Given the computational complexity of re-estimating the landscape noise surface, such work is beyond the scope of this paper.
@@
 
-Contrary to the previous results presented by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} and \citet{Theebe2004a}, we find little evidence to suggest that the impact of traffic noise varies over space or by level of noise within our study area.
+Contrary to the previous results presented by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} and \citet{Theebe2004a}, we find little evidence to suggest that the impact of traffic noise varies geographically or by the level of noise within our study area.
 The traffic noise coefficient was one of only two variables with regression coefficient standard deviations smaller than or similar to the simulated distributions obtained from Monte Carlo experiments.
@@
 Second, ``mixed'' regression techniques (in which some regression coefficients are constrained to remain constant across the study area while others are alowed to vary) may allow researchers to obtain more precise estimates of the impact of hedonic characteristics by increasing the degrees of freedom in the regression.
-As mentioned previously, future work may also seek to re-estimate traffic noise models over time to better account for changes in traffic flows associated with macroeconomic conditions.
-Lastly, researchers may want to take advantage of the findings of \citet{Carruthers2010} and use the spatial variation in regression coefficients to help estimate the second-stage hedonic regressions to identify consumer demand curves for these characteristics.
+Future work may also seek to re-estimate traffic noise models over time to better account for changes in traffic flows associated with macroeconomic conditions.
+Lastly, researchers should take advantage of the recent suggestions in \citet{Carruthers2010} and use the spatial variation in regression coefficients obtained from LWR models to estimate the second-stage hedonic regressions to identify consumer demand curves for these characteristics.
 

### 2013-09-30 reports/Draft.tex
another round of editing, updated correlation matrix, etc.

--- 2013-09-14 reports/Draft.tex
@@
 While the mean sale price declined from roughly \$280,000 pre-crash to \$230,000 post-crash, most of the structural and neighborhood variables are relatively consistent across years.
-However, traffic noise displays a noticeable difference in the pre- and post-crash market transactions (the mean drops from 58 dB to 52 dB).
+However, traffic noise displays a noticeable difference in the pre- and post-crash market transactions (the mean drops from over 58 dB to less than 53 dB).
 
 \begin{table}
-\caption{Mean Variable Values Across Time}\label{tab:SumStatsTime}
-\includegraphics[width = \textwidth]{../graphs/DescriptiveStatsByYear}
+\begin{center}
+\caption{Mean Variable Values by Year}\label{tab:SumStatsTime}
+\small
+%\includegraphics[width = \textwidth]{../graphs/DescriptiveStatsByYear}
+% Table generated by Excel2LaTeX from sheet 'Descriptive StatisticsYear'
+    \begin{tabular}{lrrrrrr|r}
+    Variable & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2005-10\\ \hline
+    Sales Value (\$1000s) & 279   & 282   & 275   & 263   & 231   & 233   & 266 \\
+    House Size (ft$^2$) & 1737  & 1736  & 1743  & 1813  & 1727  & 1775  & 1750 \\
+    Lot Size (acres) & 0.25  & 0.25  & 0.25  & 0.26  & 0.25  & 0.26  & 0.25 \\
+    Year Built  & 1967  & 1966  & 1966  & 1971  & 1968  & 1968  & 1967 \\
+    Traffic Noise (dB) & 58.5  & 58.6  & 58.6  & 52.5  & 52.8  & 52.8  & 56.4 \\
+    Median Income (\$1000s) & 72.0  & 72.1  & 72.3  & 74.8  & 72.6  & 73.2  & 72.6 \\
+    Elem. Test Scores & 364.8 & 364.8 & 365.2 & 363.5 & 362.3 & 366.1 & 364.5 \\
+    Dist. to CBD (km) & 14.7  & 14.6  & 14.8  & 15.0  & 14.3  & 14.5  & 14.7 \\
+    Dist. to Park (km) & 2.6   & 2.6   & 2.6   & 2.8   & 2.6   & 2.6   & 2.6 \\
+    Dist. to Lake (km) & 0.9   & 0.9   & 0.9   & 0.9   & 0.9   & 0.9   & 0.9 \\
+    Dist. to Shop (km) & 1.9   & 1.9   & 1.8   & 2.0   & 1.9   & 1.9   & 1.9 \\ \hline
+    Number of Observations &  10,991  & 8,885  &  6,549  &
+    \end{tabular}%
+\end{center}
 \end{table}

### 2013-09-30 analysis/Data Description/CorMatrix.R

@@ -3,7 +3,7 @@ library (foreign)
 workingdata <- read.dbf("../Data/R2GIS/CleanData/Sales20052010.dbf")
 
 
-quantVars = c("logSALE_VA", "FIN_SQ_FT", "ACRES_POLY", "YEAR_BUILT", 
+quantVars = c("SALE_VALUE", "FIN_SQ_FT", "ACRES_POLY", "YEAR_BUILT", 
               "MAX", "MED_INCOME", "MCA3", "CBD_dist", "PARK_dist", "LAKE_dist",  "SHOP_dist")
 
 corMat = cor(workingdata[, quantVars])
@@ -13,7 +13,7 @@ corMat = round(corMat, 2)
 corMat[upper.tri(corMat)] <- ""
 corMat
 
-rownames(corMat) = c("ln Sale Price", "House Size", "Lot Size", "Year Built", "Noise", "Income", "Elementary Test Scores",
+rownames(corMat) = c("Sale Price", "House Size", "Lot Size", "Year Built", "Noise", "Income", "Elementary Test Scores",
                      "Distance to CBD", "Distance to Park", "Distance to Lake", "Distance to Shop")
 colnames(corMat) = c("Price", "House", "Lot", "Built", "Noise", "Income", "Test", "CBD", "Park", "Lake", "Shop")
 

### 2013-09-30 reports/Draft.Rnw

@@
 
-In this paper, we seek to contribute to the noise hedonic literature by examining the relationship between single family home prices from 2005 to 2010 and variation in road traffic noise exposure in the St.\ Paul, Minnesota urban area.
-Our work makes multiple contributions to the field.
+In this paper, we contribute to the noise hedonic literature by examining the relationship between single family home prices from 2005 to 2010 and variation in road traffic noise exposure in the St.\ Paul, Minnesota urban area across 44 different cities.
 First, we utilize new estimates of traffic noise that have never before been used in the hedonic literature.

### 2013-10-08 reports/Draft.Rnw
updated study overview figure
further edits... close to submission?

@@
 One consequence of the expanding road network and its associated traffic is increased levels of traffic noise.
-While the hedonic literature has consistently shown a negative effect of this phenomenon on the real estate market, the relationship between housing prices and automobile traffic noise has rarely been explored at landscape level, especially in the United States.
-Here, we show this relationship by modeling the propagation of traffic noise over the landscape and by analyzing the extent of its impact on single-family home transactions in the urban area surrounding St.\ Paul, Minnesota using spatially explicit local regression techniques.
-Our estimate of the negative relationship between traffic noise levels and house prices is smaller in magnitude than most of the relevant published literature.
-We find no evidence that the effect of traffic noise varies significantly by geography, nor by traffic noise levels.
-We find significant differences in the impact of traffic noise before and after the economic recession of 2008-09.
-Our results suggest that an increase in traffic noise of one decibel decreases house prices by an average of 0.19 percent before September 2008, and an average of 0.37 percent after September 2008.
+While the hedonic literature has consistently shown a negative effect of this phenomenon on the real estate market, research in the United States has often relied on crude measures of traffic noise.
+Here, we reduce the measurement error of traffic noise exposure through a detailed model of noise propagation over the landscape.
+Additionally, we estimate the impact on single-family home transactions throughout the St.\ Paul, Minnesota, urban area using spatially explicit local regression techniques to allow for spatial non-stationarity in the hedonic function.
+Contrary to previous work, we find no evidence that the effect of traffic noise varies significantly across the several hundred square miles of our study region, nor by traffic noise levels.
+We do find significant differences in the impact of traffic noise before and after the economic recession of 2008-09.
+Our results suggest that an increase in traffic noise of one decibel decreases house prices by an average of 0.19 percent before September 2008 and an average of 0.37 percent after September 2008.
 \end{abstract}
@@
 
-\section{Introduction and Past Research}\label{sec:lit}
+\newpage
+\section{Motivation and Past Research}\label{sec:lit}
 Prolonged exposure to traffic noise affects people in a number of ways, ranging from simple annoyance \citep{Miedema2001, Ouis2001, Ohrstrom2007, DeKluizenaar2013, Weinhold2013}, to sleep disturbance \citepalias{Netherlands2004}, to increasing risk for stroke \citep{Sorensen2011}, hypertension \citep{Jarup2008, Bodin2009}, myocardial infarction \citep{Babisch2005}, and overall quality of life \citep{Shepherd2013}.
@@
 
-Policies at the local, state, and federal level can influence the level and effect of traffic noise.
-For instance, the US Federal Highway Admistration reports that 47 states have constructed noise barriers to reduce noise propagation, spending over a half a billion dollars from 2008-2010 \citepalias{USFHA2012}.
-The efficiency of such projects requires an understanding of the economic cost of traffic noise.
-
 One way to estimate some of the costs of traffic noise (and therefore the economic benefits of policies that reduce noise) is through hedonic regression, examining the relationship between house prices and noise levels.
@@
 Reviews of the research by \citet{Bateman2001} found that the negative effect of traffic noise on house prices ranged from 0.08 to 2.22 percent per decibel with a mean around 0.55 percent per decibel, while \citet{Navrud2002} found an average decrease of 0.64 percent per decibel.
-Much of the research in this literature has tended to focus on the European experience with noise, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Switzerland \citep{Baranzini2010}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, Netherlands \citep{Theebe2004a}, and Germany \citep{Brandt2011}.
+Much of the recent research in this literature has tended to focus on the European experience with noise, often due to the availability of high quality traffic noise data made available from the government, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Switzerland \citep{Baranzini2010}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, Netherlands \citep{Theebe2004a}, and Germany \citep{Brandt2011}.
 
-Instead of focusing on the impact of automobile traffic, work in the United States has tended to concentrate on noise from airports \citep{Espey2000, McMillen2004, Cohen2008a} or indirect effects of traffic noise, such as proximity to highways \citep{Matthews2007, Chernobai2009, Li2012}, or traffic counts \citep{HughesJr.1992, Larsen2012}.
-One exception is \citet{Cheng2008}, which, using micro data in Louisville, TN during 2007, finds that an additional decibel of traffic noise reduced house prices by 0.34 percent.
-However, this research is based on less than a thousand transactions in just one city.
+Instead of focusing on the impact of automobile traffic, hedonic work in the United States has tended to concentrate on noise from airports \citep{Espey2000, McMillen2004, Cohen2008a} or indirect effects of traffic noise, such as proximity to highways \citep{Matthews2007, Chernobai2009, Li2012}, or traffic counts \citep{HughesJr.1992, Larsen2012}.
+One exception is \citet{Cheng2008}, which finds that an additional decibel of traffic noise reduced house prices in Louisville, Tennessee, by 0.34 percent during the year 2007.
+However, the generalizability of this research is limited given that it is based on less than a thousand house transactions in just one city.
 
+A major reason for the thinness of the scholarly literature on this topic in the US lies in the difficulty of modeling traffic noise propagation over the landscape.
+To properly analyze the spatial association between real estate prices and exposure to traffic noise, it is necessary to create a noise surface map at sufficiently detailed spatial resolution to account for the complex and heterogeneous interaction between the noise source and the resistance of the landscape to noise propagation.
+Implementing such a model can be very difficult.
+The data needed for the model is very extensive and may not even be readily available (e.g., building footprint and height data).
+Furthermore, it is computationally very intensive.
+Fortunately, recent developments in Geographic Information Systems and distributive computing have reduced these difficulties, making it much easier to create a noise surface map at landscape level with high spatial resolution.
+
+In this paper, we estimate the relationship between house prices and traffic noise across 44 cities and several hundred square miles in the St.\ Paul, Minnesota, urban region by taking advantage of uniquely detailed set of noise estimates that have never before been used in the hedonic literature.
+The data represent perhaps the most accurate regional noise estimates ever used in the hedonic literature in the United States to date due to the high spatial resolution of the estimates (10 m x 10 m) and the incorporation of the effects of nearby buildings and landcover on noise propagation.
+More detail about the noise model inputs and procedures are presented in the next section of the paper.
+
+%Precise estimates of the impact of traffic noise are important for efficient implementation of noise mitigation projects.
+The US Federal Highway Admistration reports that 47 states have constructed noise barriers to reduce noise propagation, spending over a half a billion dollars from 2008-2010 \citepalias{USFHA2012}.
 \citet{Delucchi1998} used an estimate of 0.85 percent reduction in house prices per additional decibel in their cost-benefit analysis of traffic noise.
@@
 
-One major reason for the thinness of the scholarly literature on this topic in the US lies in the difficulty of modeling traffic noise propagation over the landscape.
-To properly analyze the spatial association between real estate prices and exposure to traffic noise at a landscape level, it is necessary to create a noise surface map at sufficiently detailed spatial resolution to account for the complex and heterogeneous interaction between the noise source and the resistance of the landscape to noise propagation.
-Implementing such a model can be very difficult.
-For one thing, the data needed for the model is very extensive and may not even be readily available (e.g., building footprint and height data).
-Furthermore, it is computationally very intensive.
-Fortunately, recent developments in Geographic Information Systems and distributive computing have reduced these difficulties, making it much easier to create a noise surface map at landscape level with high spatial resolution.
+Work from Europe suggests that the relationship between traffic noise and house prices varies across housing submarkets \citep{Day2007, MarmolejoDuarteCarlos;GonzalezTamez2009}, by level of traffic noise \citep{Theebe2004a, Brandt2011}, and over time \cite{Wilhelmsson2000}.
+As such, we construct a flexible hedonic model that allows for a non-stationary relationship between house prices and our explanatory variables over geography and time.
+Such Locally Weighted Regression (LWR) models have become increasingly common in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than other common spatial econometric models under common real world circumtances \citep{McMillen2012}.
+Thus, in addition to using new data that reduces the measurement error of the impact of traffic noise, the spatial and temporal variation in our data and hedonic modeling allow us to present the first estimates in the United States of how the impact of traffic noise varies over space, time, and by noise level.
 
-In this paper, we contribute to the noise hedonic literature by examining the relationship between single family home prices from 2005 to 2010 and variation in road traffic noise exposure in the St.\ Paul, Minnesota urban area across 44 different cities.
-First, we utilize new estimates of traffic noise that have never before been used in the hedonic literature.
-The noise propagation model estimates traffic noise levels at a high spatial resolution (10m x 10m) while also incorporating the effects of nearby buildings and landcover.
+We find that while the impact of other important control variables in the hedonic function vary significantly over space, the impact of traffic noise does not.
+Such results are contradictory to recent work by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} which found evidence of a spatially non-stationary relationship between traffic noise and housing prices using a LWR model in Barcelona, Spain.
+Our paper also presents the first estimates of the implicit price of traffic noise after the housing market collapse and economic recession of 2008-09.
+Contrary to work such as \citet{Cho2011b}, which found that environmental amenities mattered \emph{less} after the housing crash, our estimated effect of traffic noise mattered \emph{almost twice as much more} after the recession (0.19 percent reduction in house prices per additional decibel beforehand compared to 0.37 percent per decibel afterwards).
+We conclude with a discussion of how future research can expand and improve upon this work.
 
-We also construct a flexible hedonic model that allows for a non-stationary relationship between house prices and our explanatory variables over geography and time.
-Such Locally Weighted Regression (LWR) models have become increasingly common in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than other spatial econometric models under common circumstances \citep{McMillen2012}.
-\citet{MarmolejoDuarteCarlos;GonzalezTamez2009} used a LWR model to estimate the impact of traffic noise on housing prices in Barcelona, Spain and found evidence of a non-stationary relationship over the study area.
-We find that while the impact of other important control variables in the hedonic function vary over space, the impact of traffic noise does not.
-
-Lastly, we present the first estimates of the implicit price of traffic noise after the housing market collapse and Great Recession of 2008-09.
-Contrary to work such as \citet{Cho2011b}, which found that environmental amenities mattered less after the housing crash, our estimated effect of traffic noise mattered more after the recession (0.37 percent reduction in house prices per additional decibel) compared to beforehand (0.19 percent per decibel).
-
-\section{Data}
+\section{Study Area and Data}
 The 2010 US Census lists the population of the Twin Cities Metropolitan Region (Minneapolis and St.
@@
 This study examines single family residential home transactions in the Census-defined urban areas of three of the seven counties: Dakota, Ramsey and Washington County (see Figure \ref{fig:overview}).
-We obtained data from approximately forty thousand sales transactions between 2005 and 2010 (n=42,095) from the 2010 MetroGIS Regional Parcel Dataset published by the Metropolitan Council.
+We obtained sales data from approximately forty thousand transactions between 2005 and 2010 (n=42,095) from the 2010 MetroGIS Regional Parcel Dataset published by the Metropolitan Council.
 Figure \ref{fig:overview} shows an overview of the study area as well as the spatial distribution of the house sales prices.
-In addition to the geographic location and date of the house sale, we collected or calculated structural and locational variables commonly used in the hedonic literature.
+
+In addition to the geographic location and date of the house sale, we collected or calculated structural and locational variables commonly used in the hedonic literature, such as the size of the house, lot size, and architectural style of the house, as well as distances to amenities like the Central Business District, parks, and lakes.
 Table \ref{tab:sumStats} provides a brief description of the variables in our data and some basic summary statistics.
@@
 \begin{figure}
-\makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/StudyArea_SaleValueDistribution}}
+\makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/StudyAreaSaleValueDist}}
 \caption{This figure shows the spatial extent of our study area as well as the significant spatial variation in single family house sales prices.}\label{fig:overview}
@@
 
-\subsection{Structural Attributes}
-According to a review by \cite{Wilhelmsson2000}, the most common structural attributes included in real-estate hedonic pricing studies are living area, number of bathrooms, age, garage and lot size.
-Although the 2010 MetroGIS Regional Parcel Dataset includes structural data on living area, age, garage presence, lot size, owner-occupancy and house architectural style for every transaction, we have variables for the number of bedrooms, bathrooms, and size of the garage for house sales in one county.
-We feel confident in our results even without these independent variables for most of our study data because sensitivity analysis conducted in areas with the additional structural variables revealed very similar estimates when the variables were included and excluded.
-These results are in section \ref{Discussion} of the the paper.
-Additionally, other hedonic work has been published using a similar set of explanatory variables in this area, see for instance, \citet{Sander2009b}.
-
 \subsection{Noise Data}
-Should we cite previous work that uses these data?
-
-To determine the relationship between real estate price and road traffic noise levels, we first created a traffic noise exposure surface for the entire Twin Cities Metro Region (TCMR) by calculating the propagation of traffic noise over the landscape using the FHWA (Federal Highway Authority) 1978 standard \citep{Barry1978}.
+To determine the relationship between real estate price and road traffic noise levels, we first created a traffic noise exposure surface by calculating the propagation of traffic noise over the landscape using the FHWA (Federal Highway Authority) 1978 standard \citep{Barry1978}.
 Following \citet{Barry1978}, the traffic noise level at any given location on the landscape is given by:
@@
 \end{eqnarray}
-where $L_{EQ}(i)$ is A-weighted hourly energy equivalent noise level in dBA, which is calculated for each class $i$ of vehicle (automobile and trucks); $\bar{L}_0(i)$ is the mean Sound Pressure Level (SPL) at the reference distance for class $i$; $\sigma _i$ is the standard deviation of the SPL for each class of vehicle; $N_i$ is the number of vehicles of the $i^{th}$ class passing during the relevant hour; $D_0$ is the reference distance (usually 15 m); $D$ is the perpendicular distance from the road center line to the receiver; $\alpha$ is a site parameter (soft and hard surface), $0 < \alpha < 1$; $S_i$ is the mean speed of the $i^{th}$ class; $T$ is the duration, usually 1 hour; $\phi _1$ and $\phi _2$ are the angles from the perpendicular of the limits of the observer's view of a section of the road.
+where $L_{EQ}(i)$ is A-weighted hourly energy equivalent noise level in decibels (dBA), which is calculated for each class $i$ of vehicle (automobile and trucks); $\bar{L}_0(i)$ is the mean Sound Pressure Level (SPL) at the reference distance for class $i$; $\sigma _i$ is the standard deviation of the SPL for each class of vehicle; $N_i$ is the number of vehicles of the $i^{th}$ class passing during the relevant hour; $D_0$ is the reference distance (usually 15 m); $D$ is the perpendicular distance from the road center line to the receiver; $\alpha$ is a site parameter (soft and hard surface), $0 < \alpha < 1$; $S_i$ is the mean speed of the $i^{th}$ class; $T$ is the duration, usually 1 hour; $\phi _1$ and $\phi _2$ are the angles from the perpendicular of the limits of the observer's view of a section of the road.
 They are used to account for only the energy coming from a portion of the roadway; $\Delta _{gradient}$ is an adjustment for road surface gradient; $\Delta _{shielding}$ is a shielding adjustment (land cover, buildings, noise barriers).
@@
 For all roads without recorded traffic volume (i.e., residential), we assigned 100 vehicles/day as a minimum estimate.
-This estimate was based on factors identified in the literature as important for estimating traffic volume, such as census data on commuting population, tract area, the size of a standard street block, and road type \citep{Cheng1992, Fricker1986}.\footnote{In order to assess the sensitivity of our results to our estimate of traffic volume for local roads, we also ran the model using 200 and 300 vehicles/day for one of the counties that make up the TCMR.
+This estimate was based on factors identified in the literature as important for estimating traffic volume, such as census data on commuting population, tract area, the size of a standard street block, and road type \citep{Cheng1992, Fricker1986}.\footnote{In order to assess the sensitivity of our results to our estimate of traffic volume for local roads, we also ran the model using 200 and 300 vehicles/day for one county.
 With the exception of a few areas in the rural part of the county, there was less than 0.05 dBA difference at 30 m from the road centerline.}
@@
 
-The locations chosen for the traffic noise levels were the 818,500 buildings in the TCMR.
+The locations chosen for the traffic noise levels were the 818,500 buildings in the entire urban area.
 Thus, we used the perimeter and height of these buildings to account for the shielding effect of buildings.
@@
 
-We used the SoundPlan$^{TM}$ noise modeling software to implement the model given by Equation \ref{eq:noise}.
+We used the SoundPlan$^{TM}$ noise modeling software to implement the model given by Equation~\eqref{eq:noise}.
 Predicted traffic noise output is calculated at a grid resolution of 10 m$^2$.\footnote{We conducted a preliminary validation of the model output by comparing it with observed noise levels at 134 locations that were sampled along major highways.
@@
 
+\subsection{Structural Attributes}
+According to a review by \cite{Wilhelmsson2000}, the most common structural attributes included in real-estate hedonic pricing studies are living area, number of bathrooms, age, garage and lot size.
+Although the 2010 MetroGIS Regional Parcel Dataset includes structural data on living area, age, garage presence, lot size, owner-occupancy and house architectural style for every transaction, we only have variables for the number of bedrooms, bathrooms, and size of the garage for house sales in one county.
+We feel confident in our results even without these independent variables for most of our study data because sensitivity analysis conducted in areas with the additional structural variables revealed very similar estimates when the variables were included and excluded.
+Section \ref{Discussion} provides a more detailed description of these results.
+%Additionally, other hedonic work has been published using a similar set of explanatory variables in this area, see for instance, \citet{Sander2009b}.
+
 \subsection{Other Locational Attributes}
@@
 For instance, using GIS software we are able to calculate the Euclidean distance to numerous points of interest within the dataset, such as the nearest central business district, shopping centers, parks, and lakes.
-Additionally, a variable denoting the median household income for the surrounding census tract is created through the use of TIGER shapefiles from the 2010 Census Bureau and data from the 2010 American Community Survey (ACS).
+Additionally, a variable denoting the median household income for the surrounding census tract is created through the use of TIGER shapefiles from the 2010 Census Bureau and data from the 2010 American Community Survey.
 Lastly, we associate each transaction with its elementary school and include the average 3rd grade Minnesota Comprehensive Assessment (MCA) score for the local elementary school during the year of purchase.\footnote{Test scores were obtained from the Minnesota Department of Education website.
@@
     Sales Value (\$1000s) & 279   & 282   & 275   & 263   & 231   & 233   & 266 \\
+    Traffic Noise (dB) & 58.5  & 58.6  & 58.6  & 52.5  & 52.8  & 52.8  & 56.4 \\
     House Size (ft$^2$) & 1737  & 1736  & 1743  & 1813  & 1727  & 1775  & 1750 \\
@@
     Year Built  & 1967  & 1966  & 1966  & 1971  & 1968  & 1968  & 1967 \\
-    Traffic Noise (dB) & 58.5  & 58.6  & 58.6  & 52.5  & 52.8  & 52.8  & 56.4 \\
     Median Income (\$1000s) & 72.0  & 72.1  & 72.3  & 74.8  & 72.6  & 73.2  & 72.6 \\
@@
     Dist. to Shop (km) & 1.9   & 1.9   & 1.8   & 2.0   & 1.9   & 1.9   & 1.9 \\ \hline
-    Number of Observations &  10,991  & 8,885  &  6,549  &  5,503  &  5,961  & 4,206  & 42,095  \\
+    Number of Observations &  10,991  & 8,885  &  6,549  & 5,503  &  5,961  & 4,206  & 42,095  \\
     \end{tabular}%
@@
 \section{Basic Econometric Model}\label{basicModel}
+Our aim is to estimate the marginal willingness to pay for different attributes, in particular changes in the traffic noise associated with the house.
 Consistent with past research, this study implements a semi-logarithmic hedonic pricing model.
-Our aim is to estimate the marginal willingness to pay for different attributes, in particular changes in the traffic noise associated with the house.
-Equation~\eqref{eq:model} expresses the basic hedonic model.
+Before implementing the Locally Weighted Regression model, we present the results of a simpler econometric model given by equation~\eqref{eq:model}.
 \begin{equation}\label{eq:model}	
@@
 \end{equation}
-Where Noise$_i$ is the noise level for house $i$, $S_i$ is a vector of the house's structural attributes, $N_i$ is a vector of the neighborhood attributes, and $T_i$ is a vector of time fixed effects.
-We can interpret the regression model coefficients as the price semi-elasticities of the underlying attributes.
+Noise$_i$ is the noise level for house $i$, $S_i$ is a vector of the house's structural attributes, $N_i$ is a vector of the neighborhood attributes, and $T_i$ is a vector of time fixed effects.
+Due to the semi-logarithmic functional form of the model, we can interpret the regression model coefficients as the price semi-elasticities of the underlying attributes.
 For instance, we can interpret the coefficient on noise as the percentage increase in price for a one decibel increase in the traffic noise associated with the transaction in our dataset.
@@
    & (1)   &       &       & (2)   &       &       & Pre-Crash   &       &       & Post-Crash   &  \\ \hline
+\T  Traffic Noise & -2.02E-03 & *** &   & -2.00E-03 & ***   &   & -1.63E-03 & ***  & & -3.08E-03 & *** \\
+          & (1.32E-04) &   &   & (1.32E-04) &       &       & (1.38E-04) &       &       & (3.29E-04) &  \\
 \T  Intercept & 9.37E+00 & ***   & \hspace{.5cm} & 9.49E+00 & ***   & \hspace{.5cm}   & 8.55E+00 & ***   & \hspace{.5cm}   & 1.10E+01 & *** \\
@@
           & (4.57E-05) &       &       & (4.65E-05) &   &   & (5.06E-05) &    &   & (1.05E-04) &  \\
-\T  Traffic Noise & -2.02E-03 & *** &   & -2.00E-03 & ***   &   & -1.63E-03 & ***  & & -3.08E-03 & *** \\
-          & (1.32E-04) &   &   & (1.32E-04) &       &       & (1.38E-04) &       &       & (3.29E-04) &  \\
 \T  Median Income & 3.03E-06 & ***  & & 3.31E-06 & ***  &   & 2.86E-06 & ***   &       & 4.06E-06 & *** \\
@@
 Standard urban economic theory \citep{Alonso1964, Mills1967, Muth1969} predicts that the price of land will vary over space within our dataset to account for locational amenities.
-As such, we add an interaction term between lot size and distance to the nearest central business district to account for spatial variation in the price of land.
-The second column in Table \ref{tab:globalRegression} shows the results of this regression.
+As such, the other columns include an interaction term between lot size and distance to the nearest central business district to account for spatial variation in the price of land.
 The significant coefficients on the lot size interaction terms suggest that the value of land varies over space.
@@
 Table \ref{tab:globalRegression} also attempts to begin to understand how the economic recession may have influenced the hedonic function in our study area.
-Columns three and four estimate the same regression as (2) but subset the sales before and after September of 2008 (the month that Lehman Brothers filed for bankruptcy, the US Federal government took over Fannie Mae and Freddie Mac, and the American International Group (AIG) narrowly avoided bankruptcy only through a \$85 billion loan from the US Federal government).\footnote{\url{http://www.federalreserve.gov/newsevents/press/other/20080916a.htm}} The coefficients for some of the hedonic variables of interest (noise, schools, land, for instance) appear different across the two time periods.
+The third and fourth columns estimate the same regression as (2) but subset the sales before and after September of 2008 (the month that Lehman Brothers filed for bankruptcy, the US Federal government took over Fannie Mae and Freddie Mac, and the American International Group (AIG) narrowly avoided bankruptcy only through a \$85 billion loan from the US Federal government).\footnote{\url{http://www.federalreserve.gov/newsevents/press/other/20080916a.htm}} The coefficients for some of the hedonic variables of interest (noise, schools, land, for instance) appear different across the two time periods.
 
-Taken in aggregate, the results in Table \ref{tab:globalRegression} suggest that the hedonic price function likely varies over space and time.
+The results in Table \ref{tab:globalRegression} and previous work \citep[such as][]{Day2007, MarmolejoDuarteCarlos;GonzalezTamez2009} suggests that the relationship between prices and many other hedonic characteristics may vary over space.
 While methods exist for parameterizing this variation \citep[such as spatial expansion as suggested by][]{Casetti1972}, we have no a priori knowledge of how to parameterize the variation over space and time.
 As such, we turn to a semi-parametric form of hedonic regression, a flexible modeling approach which lets the data reveal how relationships vary, rather than specifying them beforehand.
+Such a modeling choice will allow us to test the hypotheses of spatial and temporal stationarity in the regression model.
 
@@
 The GCV score is a convenient model selection metric that rewards models that provide a good fit to the data, while penalizing models with a greater number of model parameters \citep{Loader1999, McMillen2010}.
-Such semi-parametric models have been shown to discern whether spatially varying relationships exist, accurately estimate spatially varying coefficients, even outperform other spatial econometric techniques, and do so without wasting degrees of freedom \citep{Paez2011, McMillen2010, McMillen2012}.
+Model selection via this strategy has been shown to discern whether spatially varying relationships exist, accurately estimate spatially varying coefficients, even outperform other spatial econometric techniques, and do so without wasting degrees of freedom \citep{Paez2011, McMillen2010, McMillen2012}.
 
-\section{Results}
+%\section{Results}
 Similar to the basic econometric model described in Section \ref{basicModel}, the LWR model estimates the logged sales price of a house as a function of structural, locational and temporal variables.
@@
 
-Figure \ref{fig:GCVmodel} shows the relationship between the number of nearest houses receiving positive weights in the Locally Weighted Regression and the Generalized Cross Validation score across three different models.
-The first model simply uses the basic structural characteristics as the explanatory variables (size of the house in square feet, size of the lot in acres, a categorical variable denoting the architectural style of the house, and whether or not the house is owner-occupied).
-The second model adds locational variables to the previously described model (test scores at the local elementary school, census tract median income, and distances to the central business district, nearest park, nearest shopping center, and nearest lake).
+\subsection{Improved Model Performance}
+The use of the Locally Weighted Regression model significantly increases model performance.
+Figure \ref{fig:GCVmodel} displays the Generalized Cross Validation score for three different model specifications with varying number of observations included in the regression bandwidth.
+Two important conclusions can be drawn from the results.
+First, local analysis (bandwidths of a couple hundred observations) perform significantly better than global models, and second, performance improves with the inclusion of locational variables.
+The minimum GCV score is obtained using a bandwidth of 200 nearest houses and a model including structural, locational, and city fixed-effects.
+
+We estimate three different models.
+Model (1) uses only the basic structural characteristics as the explanatory variables (size of the house in square feet, size of the lot in acres, a categorical variable denoting the architectural style of the house, and whether or not the house is owner-occupied).
+Model (2) adds locational variables to the previously described model (test scores at the local elementary school, census tract median income, and distances to the central business district, nearest park, nearest shopping center, and nearest lake).
 The third model adds city fixed effects.
-Generally speaking, the third model performs slightly better than the second model, which performs better than the first model.
-The minimum GCV score is obtained using a bandwidth of 200 nearest houses and Model (3).
+Generally speaking, the third model performs slightly better than the second model, which performs substantially better than the first model.
 \begin{figure}
@@
 
-Figure \ref{fig:GCVmodel} also displays the GCV scores for the three models estimated at the global scale.
-The GCV scores for the global models follow a similar patter as the LWR models, with Model (3) performing better than Model (2) and Model (1) having the highest GCV score.
+We also estimate each of the three models at varying levels of local analysis, with bandwidths ranging from the nearest 50 observations to the nearest 10,000.
+Models with bandwidths of only a couple hundred observations have substantially smaller GCV scores, suggesting that, conditional on control variables included in the model, model performance still improves by performing the analysis at the local level.
 It is also worth noting that the LWR models have significantly lower GCV scores for a range of bandwidths when compared to the global models.
 These results suggest that it is important to model our data in a spatially explicit manner.
-Table \ref{tab:mainresults} displays a summary of the results of LWR Model 3 and a similar regression model run without allowing for spatial variation in the regression coefficients.
-Again, note that the LWR model yields a substantially smaller GCV score (0.027 vs.\ 0.041).
+
+Table \ref{tab:mainresults} displays a summary of the results of LWR Model (3) and a similar regression model run without allowing for spatial variation in the regression coefficients.
+Again, note that the LWR model yields a substantially smaller GCV score (0.027 vs.\ 0.041) signifying a substantial improvement in model performance.
+In addition to the significant reduction in the GCV score obtained with the use of LWR, we also see a substantal reduction in the degree of spatial autocorrelation in the model residuals.
+We calculate Moran’s I statistic to be 0.199 for the global model while our prefered LWR specification yields 0.012, a more than ten-fold reduction.
 
@@
 
-Table \ref{tab:mainresults} presents the results of our preferred LWR model as well as a basic global OLS model for comparison.
-The first two columns display the estimates and standard errors from a basic semi-log OLS regression with traffic noise, structural characteristics, location-based amenities, and both city and year of sale dummy variables.
-The third column displays the mean estimated coefficients from the LWR model.
-In this model coefficients are estimated at each observation within the dataset using the nearest 200 house sales within the past 12 months.
-The fourth column displays the standard deviation of the estimated coefficients to give a sense of how the coefficients vary when allowed to do so through the use of locally weighted regression techniques.
-In addition to the significant reduction in the GCV score (0.041 vs.
-0.027) obtained with the use of LWR, we also see a substantal reduction in the degree of spatial autocorrlation in the model residuals.
-We calculate the Moran’s I statistic to be 0.199 for the global model while our prefered LWR specification reduces the Moran's I statistic to 0.012, a nearly twenty-fold reduction.
+The first two columns of Table \ref{tab:mainresults} display the estimates and standard errors from a basic semi-log OLS regression with traffic noise, structural characteristics, location-based amenities, and both city and year of sale dummy variables.
+The third and fourth columns summarize the results of the LWR model when coefficients are estimated at each observation within the dataset using the nearest 200 house sales within the past 12 months.
+The third column presents the mean of these estimates while the fourth column displays the standard deviation of the estimates to give a measure of variation in the estimates across the dataset.
+Most of the mean LWR coefficients, including traffic noise, are similar to the coefficients obtained with the global OLS model.
+However, the large standard deviations of the LWR coefficients suggest that there is significant variation in the estimated coefficients with the more flexible model.
+We now try to determine the source of this variation.
 
@@
 Roughly half of the regressions estimated an impact of traffic noise statistically different from zero, while approximately one-third of the local regressions estimated statistically significant estimates of the locational variables (school test scores, census tract median income, distance to local amenities).
-
 The lack of statistical significance for many of the local regression coefficients could be due to multiple factors.
-First, because we are estimating local regressions with only the nearest 200 data points, rather than over 30,000 sales as in the global model, we might be estimating the coefficients with less precision and are unable to differentiate the coefficients from zero.
-Alternatively, the coefficients themselves might vary, sometimes being close to zero and other times not.
+First, because we are estimating local regressions with only the nearest 200 data points, rather than tens of thousands of sales as in the global model, we might be estimating the coefficients with less precision and are unable to differentiate the coefficients from zero.
+Alternatively, the coefficients themselves might vary, sometimes being close to zero and other times farther away.
 This variation might be due to random chance (after all, we have estimated tens of thousands of regressions), or it could be the result of true spatial non-stationarity on the part of the coefficients.
 
+We test three hypotheses regarding the spatially and temporally flexible model results.
+We have seen that the model allows us to substantially improve our prediction of the logged house sales prices in our study.
+Why?
+Is there spatial non-stationarity in the hedonic model?
+If so, does the spatial non-stationarity hold for all of the explanatory variables or just a subset?
+In particular, do we see spatial non-stationarity in the impact of traffic noise as suggested in previous research such as \citet{MarmolejoDuarteCarlos;GonzalezTamez2009}?
+We will also use these results to test the hypothesis of temporal stationarity in the hedonic function.
+In particular, is the impact of traffic noise different before and after the negative shock of the economic recession and associated collapse of the housing market?
+Lastly, we will examine our results for evidence of threshold effects of noise.
+
 \subsection{Does the Hedonic Function Vary over Space?}
-We believe the hedonic function varies significantly over space and the use of a LWR estimation procedure is appropriate.
-We conducted two different Monte Carlo simulations with the data as described in \citet{Fotheringham2002}.
+We believe the hedonic function varies significantly over space and the use of a LWR estimation procedure is an appropriate modeling strategy.
+Our conclusions are based on the results of two different Monte Carlo simulations with the data as described in \citet{Fotheringham2002}.
 In each simulation we resampled (without replacement) the location of each house in the study and then re-estimated the LWR model with the locationally ``shuffled'' data.
@@
 
-In the first simulation we estimated the LWR model using bandwidths ranging from the nearest 50 to 10,000 sales just as before.
+In the first simulation we estimated the LWR model using bandwidths ranging from the nearest 50 to 10,000 sales just as before, but with the spatially reshuffled data (so the nearest 50 observations in the simulations are not the same 50 observations in reality).
 In 100 consecutive simulations, the smallest Generalized Cross-Validation score was obtained at the largest bandwidth.
@@
 In other words, after running thousands of regressions on the shuffled data, we never obtained model performance anywhere near the LWR model with our true locational data.
-This seems to be strong evidence that the increased ability to predict house prices with a local model is not due to chance.
+This seems to be strong evidence that the increased ability to predict house prices with a local model is not due to chance and that there is spatial non-stationarity in the hedonic function.
 
+\subsubsection{Does the impact of traffic noise vary over space?}
 In the previous simulation we found that the hedonic regression function indeed exhibits spatial non-stationarity.
@@
 Using a bandwidth of the nearest 200 houses and a temporal lag of 12 months not only yielded significantly smaller GCV scores compared to other bandwidths and model specifications, but such performance does not seem to be a result of a chance spatial arrangement of the data.
+However, contrary to previous work, these simulations show no evidence for spatial variation in the effect of traffic noise on house prices.
 
@@
 \begin{equation}\label{eq:LWRinteraction}
-\hat{\beta}_{LWR} = \alpha _0 + \alpha _1 \texttt{*Month} + \alpha _2  \texttt{*Post} + \alpha _3 \texttt{*Post*Month} + \epsilon.
+\hat{\beta}_{LWR} = \alpha _0 + \alpha _1 \texttt{*Months since Sep. 2008} + \alpha _2  \texttt{*Post} + \alpha _3 \texttt{*Post*Months since Sep. 2008} + \epsilon.
 \end{equation}
@@
 (Intercept) & -1.7e-03 &  4.1e-05 &  -43.4   \\
-Month       & 6.9e-06 &  2.0e-06  &   3.5    \\
+Months since Sep 2008       & 6.9e-06 &  2.0e-06  &   3.5    \\
 Post        &-8.0e-04 &  7.2e-05  & -11.1    \\
-Month*Post  &-8.9e-05 &  4.5e-06  & -19.7    \\ \hline
+Post*Months since Sep 2008  &-8.9e-05 &  4.5e-06  & -19.7    \\ \hline
 \multicolumn{4}{l}{Residual standard error: 0.003} \\
@@
 
-Our data lack some important structural variables that are commonly used in the housing hedonic literature.
+Our previously reported results lack some important control variables in the hedonic function.
 To the extent that structural variables like the number of bedrooms, bathrooms, garage size, or construction quality covary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias.
-We are somewhat comforted, however, because we do have some additional variables for a subset of our data.
+We are comforted, however, because we do have some of these important additional variables for a subset of our data.
 We obtained the number of bedrooms, bathrooms, and garage area for our houses located within Dakota County from the Dakota County Assessor's Office.
-Our analysis (Models 1, 2, and 3 described earlier) was repeated on this geographic subset of the data and the results were compared to the estimates obtained from the same analysis when these additional structural variables were omitted.
-We found strikingly similar estimates of the impact of traffic noise.
+Our LWR analysis (Models 1, 2, and 3 described earlier) was repeated on this geographic subset of the data and the results were compared to the estimates obtained from the same analysis when these additional structural variables were omitted.
+We found strikingly similar estimates of the impact of traffic noise suggesting that our results may be robust to the omission of these variables from our analysis.
 
@@
 \begin{center}
-\caption{Noise Regression Coefficient Estimates in Dakota County with and without Additional Structural Variables}\label{tab:Dak}
+\caption{Noise Coefficient Estimates in Dakota County with and without Additional Structural Variables}\label{tab:Dak}
 \begin{tabular}{lll}
@@
 
-The timing of our independent variable collection is also a potential problem.
+The timing of our independent variable collection is also a potential weakness.
 While our house sales data are collected over the course of six years, some of our other variables were collected at specific points in time and assumed to be constant over the study period.
-In particular, the traffic noise estimates taken from \citet{Nega2012} are for the year 2007.
-To the extent that traffic flows and composition signicantly changed over time, our traffic noise variables may be inaccurate for those time periods.
+In particular, the traffic noise estimates are for the year 2007.
+To the extent that traffic flows and composition signicantly changed over time, our traffic noise variables may be inaccurate for those other time periods.
 For instance, the US Department of Transportation reports that total vehicle miles travelled decreased by up to 4 percent year-on-year during the Great Recession.\footnote{\url{http://www.fhwa.dot.gov/ohim/tvtw/08dectvt}} Thus, our noise estimates may be inaccurate for later time periods and this may bias our estimates of the impact of noise on house values.
@@
 \section{Conclusion}
-
-We estimated the impact of traffic noise on housing prices using Locally Weighted Regression techniques in the St.\ Paul, Minnesota urban area.
-Specifically, we estimate semi-logarithmic regressions at each house within our dataset using only information contained in ``local'' house sales (where local is defined both geographically and temporally).
-We find strong evidence that the hedonic function in our study area varies over space and time.
+We estimated the impact of traffic noise on housing prices using Locally Weighted Regression techniques in the St.\ Paul, Minnesota, urban area.
+Specifically, we estimate semi-logarithmic regressions at each house within our dataset using only information contained in ``local'' (both geographically and temporally) house sales.
+We find strong evidence that the hedonic function in our study area varies over space and time and such flexible models represent significant improvements over convential parametric models.
 
@@
 
-Finally, the results of this work suggest multiple areas of fruitful future research to better help policymakers weigh the costs and benefits of traffic noise.
-First, we suggest research be conducted in more housing markets, as the potential to apply the results of analysis in one set of geographical and economic circumstances may be limited.
+Precise estimates of the impact of traffic noise are important for efficient implementation of noise mitigation projects.
+The US Federal Highway Admistration reports that 47 states have constructed noise barriers to reduce noise propagation, spending over a half a billion dollars from 2008-2010 \citepalias{USFHA2012}.
+\citet{Delucchi1998} used an estimate of 0.85 percent reduction in house prices per additional decibel in their cost-benefit analysis of traffic noise.
+While their preferred estimate of the total damage cost to the United States in 1991 is \$3 billion, they report a possible range of less than \$100 million to over \$40 billion due in part to uncertainty surrounding the degree of noise propagation over space in the urban built environment and the effect of noise on house prices.
+Indeed, one of the main conclusions of their work is that more research should be done to better understand the impact of noise on house prices and that better noise data are needed for such work to occur.
+
+Future research should be conducted in more housing markets, as the potential to apply the results of analysis in one set of geographical and economic circumstances may be limited.
 Second, ``mixed'' regression techniques (in which some regression coefficients are constrained to remain constant across the study area while others are alowed to vary) may allow researchers to obtain more precise estimates of the impact of hedonic characteristics by increasing the degrees of freedom in the regression.

### 2013-10-08 reports/Draft.tex
updated study overview figure
further edits... close to submission?

@@
     Dist. to Shop (km) & 1.9   & 1.9   & 1.8   & 2.0   & 1.9   & 1.9   & 1.9 \\ \hline
-    Number of Observations &  10,991  & 8,885  &  6,549  &
+    Number of Observations &  10,991  & 8,885  &  6,549  & 5,503  &  5,961  & 4,206  & 42,095  \\
     \end{tabular}%

### 2013-10-08 reports/Draft.Rnw
spellcheck and copy to Tsegaye

@@
 Here, we reduce the measurement error of traffic noise exposure through a detailed model of noise propagation over the landscape.
-Additionally, we estimate the impact on single-family home transactions throughout the St.\ Paul, Minnesota, urban area using spatially explicit local regression techniques to allow for spatial non-stationarity in the hedonic function.
+Additionally, we estimate the impact on single family home transactions throughout the St.\ Paul, Minnesota, urban area using spatially explicit local regression techniques to allow for spatial non-stationarity in the hedonic function.
 Contrary to previous work, we find no evidence that the effect of traffic noise varies significantly across the several hundred square miles of our study region, nor by traffic noise levels.
@@
 Automobiles are already perhaps the greatest source of noise in residential neighborhoods \citep{Barber2010} and traffic noise was estimated to cause around three billion dollars worth of external damage to the United States economy alone in 1991 \citep{Delucchi1998}.
-Traffic noise and its attendent problems are greater now than they were in the 1990s and predicted to worsen in the future \citep{Goines2007}.
-With the exception of a slight dip during the economic recession in the late 2000s, the number of vehicle miles traveled in the United States has steadily increased for the past 50 years.\footnote{\url{http://www.fhwa.dot.gov/policyinformation/statistics/2011/pdf/rc1c.pdf}} Globally, \citet{Dargay2007} predict the number of personal vehicles to grow from roughly 800 million in 2002 to over two billion units by 2030.
+Traffic noise and its attendant problems are greater now than they were in the 1990s and predicted to worsen in the future \citep{Goines2007}.
+%With the exception of a slight dip during the economic recession in the late 2000s, the number of vehicle miles traveled in the United States has steadily increased for the past 50 years.\footnote{\url{http://www.fhwa.dot.gov/policyinformation/statistics/2011/pdf/rc1c.pdf}}
+Globally, \citet{Dargay2007} predict the number of personal vehicles to grow from roughly 800 million in 2002 to over two billion units by 2030.
 Additionally, the global trend of increased urbanization is expected to continue, with the proportion of the population living in cities growing from roughly half now to over two-thirds by the middle of the century \citepalias{UNDESA2012}.
@@
 
-Instead of focusing on the impact of automobile traffic, hedonic work in the United States has tended to concentrate on noise from airports \citep{Espey2000, McMillen2004, Cohen2008a} or indirect effects of traffic noise, such as proximity to highways \citep{Matthews2007, Chernobai2009, Li2012}, or traffic counts \citep{HughesJr.1992, Larsen2012}.
+Instead of focusing on the impact of automobile traffic noise, hedonic work in the United States has tended to concentrate on noise from airports \citep{Espey2000, McMillen2004, Cohen2008a} or indirect measures of traffic noise, such as proximity to highways \citep{Matthews2007, Chernobai2009, Li2012}, or traffic counts \citep{HughesJr.1992, Larsen2012}.
 One exception is \citet{Cheng2008}, which finds that an additional decibel of traffic noise reduced house prices in Louisville, Tennessee, by 0.34 percent during the year 2007.
@@
 
-In this paper, we estimate the relationship between house prices and traffic noise across 44 cities and several hundred square miles in the St.\ Paul, Minnesota, urban region by taking advantage of uniquely detailed set of noise estimates that have never before been used in the hedonic literature.
-The data represent perhaps the most accurate regional noise estimates ever used in the hedonic literature in the United States to date due to the high spatial resolution of the estimates (10 m x 10 m) and the incorporation of the effects of nearby buildings and landcover on noise propagation.
+In this paper, we estimate the relationship between traffic noise and single family house prices across 44 cities and several hundred square miles in the St.\ Paul, Minnesota, urban region by taking advantage of a uniquely detailed set of noise estimates.
+The data represent perhaps the most accurate regional noise estimates ever used in the hedonic literature in the United States to date due to the high spatial resolution of the estimates (10 m x 10 m) and the incorporation of the effects of nearby buildings and land cover on noise propagation.
 More detail about the noise model inputs and procedures are presented in the next section of the paper.
@@
 As such, we construct a flexible hedonic model that allows for a non-stationary relationship between house prices and our explanatory variables over geography and time.
-Such Locally Weighted Regression (LWR) models have become increasingly common in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than other common spatial econometric models under common real world circumtances \citep{McMillen2012}.
+Such Locally Weighted Regression (LWR) models have become increasingly common in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than other common spatial econometric models under common real world circumstances \citep{McMillen2012}.
 Thus, in addition to using new data that reduces the measurement error of the impact of traffic noise, the spatial and temporal variation in our data and hedonic modeling allow us to present the first estimates in the United States of how the impact of traffic noise varies over space, time, and by noise level.
@@
 \section{Study Area and Data}
-The 2010 US Census lists the population of the Twin Cities Metropolitan Region (Minneapolis and St.
-Paul and their surrounding areas) as almost 3 million residents spread over seven counties.
+The 2010 US Census lists the population of the Twin Cities Metropolitan Region (Minneapolis and St.\ Paul and their surrounding areas) as almost 3 million residents spread over seven counties.
 This study examines single family residential home transactions in the Census-defined urban areas of three of the seven counties: Dakota, Ramsey and Washington County (see Figure \ref{fig:overview}).
@@
 
- & min & 25\% & 50\% & mean & 75\% & max & st. dev. \\ 
+ & min & 25\% & 50\% & mean & 75\% & max & st.\ dev.\ \\ 
   \hline
@@
 Values for ground absorption were chosen by assuming that all road surfaces consisted of impervious bitumen.
-For computational simplicity, we created the road surface gradient by re-sampling U.S.
-Geological Survey 30 m resolution Digital Elevation Model (DEM) to 100 m resolution.
+For computational simplicity, we created the road surface gradient by re-sampling US Geological Survey 30 m resolution Digital Elevation Model (DEM) to 100 m resolution.
 
@@
 \subsection{Structural Attributes}
-According to a review by \cite{Wilhelmsson2000}, the most common structural attributes included in real-estate hedonic pricing studies are living area, number of bathrooms, age, garage and lot size.
-Although the 2010 MetroGIS Regional Parcel Dataset includes structural data on living area, age, garage presence, lot size, owner-occupancy and house architectural style for every transaction, we only have variables for the number of bedrooms, bathrooms, and size of the garage for house sales in one county.
-We feel confident in our results even without these independent variables for most of our study data because sensitivity analysis conducted in areas with the additional structural variables revealed very similar estimates when the variables were included and excluded.
-Section \ref{Discussion} provides a more detailed description of these results.
+According to a review by \cite{Wilhelmsson2000}, the five most common structural attributes included in real estate hedonic pricing studies are living area, number of bathrooms, age, garage and lot size.
+The 2010 MetroGIS Regional Parcel Dataset includes structural data on living area, age, garage presence, lot size, owner-occupancy and house architectural style for every transaction.
+However, standard additional control variables like the number of bathrooms, bedrooms, and size of garage were not available through this source.
+We were able to obtain additional data for the number of bedrooms, bathrooms, and size of the garage for a subset of our house sales from the Dakota County Assessor's Office.
+In section \ref{Discussion} we show that the inclusion of these variables in our model does not significantly change our results for these areas.
+Therefore, we feel confident in our results even without these independent variables for most of our study area.
 %Additionally, other hedonic work has been published using a similar set of explanatory variables in this area, see for instance, \citet{Sander2009b}.
@@
 \subsection{Other Locational Attributes}
-A common real estate addage states that the three most important real estate attributes are: location, location and location.
+A common real estate adage states that the three most important real estate attributes are: location, location and location.
 Knowing where each house is located allows us to also construct a vector of other attributes associated with the sales transaction.
@@
 Lastly, we associate each transaction with its elementary school and include the average 3rd grade Minnesota Comprehensive Assessment (MCA) score for the local elementary school during the year of purchase.\footnote{Test scores were obtained from the Minnesota Department of Education website.
-The school district and elementary school attendance boundary spatial information was taken from the Minnesota Geospatial Information Office Clearinghouse Data Catalog.}
+The school district and elementary school attendance boundary spatial information were obtained from the Minnesota Geospatial Information Office Clearinghouse Data Catalog.}
 
@@
     Elem. Test Scores & 364.8 & 364.8 & 365.2 & 363.5 & 362.3 & 366.1 & 364.5 \\
-    Dist. to CBD (km) & 14.7  & 14.6  & 14.8  & 15.0  & 14.3  & 14.5  & 14.7 \\
-    Dist. to Park (km) & 2.6   & 2.6   & 2.6   & 2.8   & 2.6   & 2.6   & 2.6 \\
-    Dist. to Lake (km) & 0.9   & 0.9   & 0.9   & 0.9   & 0.9   & 0.9   & 0.9 \\
-    Dist. to Shop (km) & 1.9   & 1.9   & 1.8   & 2.0   & 1.9   & 1.9   & 1.9 \\ \hline
+    Dist.\ to CBD (km) & 14.7  & 14.6  & 14.8  & 15.0  & 14.3  & 14.5  & 14.7 \\
+    Dist.\ to Park (km) & 2.6   & 2.6   & 2.6   & 2.8   & 2.6   & 2.6   & 2.6 \\
+    Dist.\ to Lake (km) & 0.9   & 0.9   & 0.9   & 0.9   & 0.9   & 0.9   & 0.9 \\
+    Dist.\ to Shop (km) & 1.9   & 1.9   & 1.8   & 2.0   & 1.9   & 1.9   & 1.9 \\ \hline
     Number of Observations &  10,991  & 8,885  &  6,549  & 5,503  &  5,961  & 4,206  & 42,095  \\
@@
 \begin{table}
-\caption{Basic Regression Results- Dependent Variable = $ln$ Sale Price}\label{tab:globalRegression}
+\caption{Basic Regression Results (dependent variable = $ln(\textrm{Sale Price})$)}\label{tab:globalRegression}
 
@@
 Column (1) in Table \ref{tab:globalRegression} displays the results of our basic regression model.
-All coefficients but one are significantly different from zero at convential significance levels.
+All coefficients but one are significantly different from zero at conventional significance levels.
 The traffic noise coefficient suggests that a one decibel increase traffic noise is on average associated with a 0.2 percent reduction in housing sales prices.
@@
 The significant coefficients on the lot size interaction terms suggest that the value of land varies over space.
+Other regressions (results available upon request) show similar variation in the implicit prices of house characteristics over space.
 
@@
 %\section{Results}
-Similar to the basic econometric model described in Section \ref{basicModel}, the LWR model estimates the logged sales price of a house as a function of structural, locational and temporal variables.
-In order to account for changing market conditions over time in our data, when estimating LWR coefficients we use only houses sold within the past 12 months.
+Similar to the basic econometric model described in Section \ref{basicModel}, the LWR model estimates the logged sales price of a house as a function of structural variables, location and time.
+In order to account for changing market conditions in our data, when estimating LWR coefficients we use only houses sold within the past 12 months.
 Thus, the coefficient estimates at a particular house are estimated using data from other sales nearby in both time and geography.
@@
 Two important conclusions can be drawn from the results.
-First, local analysis (bandwidths of a couple hundred observations) perform significantly better than global models, and second, performance improves with the inclusion of locational variables.
+First, local analysis (bandwidths of a couple hundred observations) perform significantly better than global models, and second, conditional on the bandwidth, performance improves with the inclusion of more locational variables.
 The minimum GCV score is obtained using a bandwidth of 200 nearest houses and a model including structural, locational, and city fixed-effects.
@@
 Again, note that the LWR model yields a substantially smaller GCV score (0.027 vs.\ 0.041) signifying a substantial improvement in model performance.
-In addition to the significant reduction in the GCV score obtained with the use of LWR, we also see a substantal reduction in the degree of spatial autocorrelation in the model residuals.
-We calculate Moran’s I statistic to be 0.199 for the global model while our prefered LWR specification yields 0.012, a more than ten-fold reduction.
+In addition to the significant reduction in the GCV score obtained with the use of LWR, we also see a substantial reduction in the degree of spatial autocorrelation in the model residuals.
+We calculate Moran's I statistic to be 0.199 for the global model while our preferred LWR specification yields 0.012, a more than ten-fold reduction.
 
@@
 }
- \caption*{\footnotesize Column (5) displays the proportion of $\hat{\beta}_{LWR}$ that can reject the null hypthesis of $\beta =0$.\\ Column (6) displays the proportion of Monte Carlo simulations with larger standard deviations of the LWR coefficients than $\sigma_{\hat{\beta}}$}
+ \caption*{\footnotesize Column (5) displays the proportion of $\hat{\beta}_{LWR}$ that can reject the null hypothesis of $\beta =0$.\\ Column (6) displays the proportion of Monte Carlo simulations with larger standard deviations of the LWR coefficients than $\sigma_{\hat{\beta}}$}
 \end{table}
@@
 Most of the mean LWR coefficients, including traffic noise, are similar to the coefficients obtained with the global OLS model.
-However, the large standard deviations of the LWR coefficients suggest that there is significant variation in the estimated coefficients with the more flexible model.
+However, the large standard deviations of the LWR coefficients suggest non-stationarity in the estimated coefficients with the more flexible model.
 We now try to determine the source of this variation.
@@
 Our conclusions are based on the results of two different Monte Carlo simulations with the data as described in \citet{Fotheringham2002}.
-In each simulation we resampled (without replacement) the location of each house in the study and then re-estimated the LWR model with the locationally ``shuffled'' data.
+In each simulation we re-sampled (without replacement) the location of each house in the study and then re-estimated the LWR model with the locationally ``shuffled'' data.
 In both cases the results strongly suggest spatial non-stationarity in the hedonic function.
@@
 
-After 100 iterations of this second simulation, the minimum GCV score for these resampled LWR models is 0.060, substantially larger than all models (global and local) with the actual data.
+After 100 iterations of this second simulation, the minimum GCV score for these re-sampled LWR models is 0.060, substantially larger than all models (global and local) with the actual data.
 The fourth column in Table \ref{tab:mainresults} displays the standard deviations of the LWR regression coefficients obtained with our data.
-Column (6) displays the proportion of Monte Carlo simulatons that yielded larger standard deviations of LWR coefficient estimates than those shown in column $\sigma_{\hat{\beta}}$.
+Column (6) displays the proportion of Monte Carlo simulations that yielded larger standard deviations of LWR coefficient estimates than those shown in column $\sigma_{\hat{\beta}}$.
 For most variables, we never obtained a larger standard deviation in the simulation than we obtained from the LWR model with the actual data.
@@
 Figure \ref{fig:MCsds} visualizes the results of the second simulation.
-Each subfigure displays the distribution of LWR coefficient standard deviations obtained from the 100 iterations of the Monte Carlo simulation and the standard deviation obtained with the actual data (in red).
+Each sub-figure displays the distribution of LWR coefficient standard deviations obtained from the 100 iterations of the Monte Carlo simulation and the standard deviation obtained with the actual data (in red).
 Note that it is the case that the standard deviations obtained with the actual data are typically substantially larger than those obtained in the simulation for most of the variables.
@@
 Our previously reported results lack some important control variables in the hedonic function.
-To the extent that structural variables like the number of bedrooms, bathrooms, garage size, or construction quality covary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias.
+To the extent that structural variables like the number of bedrooms, bathrooms, garage size, or construction quality co-vary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias.
 We are comforted, however, because we do have some of these important additional variables for a subset of our data.
@@
 In particular, the traffic noise estimates are for the year 2007.
-To the extent that traffic flows and composition signicantly changed over time, our traffic noise variables may be inaccurate for those other time periods.
-For instance, the US Department of Transportation reports that total vehicle miles travelled decreased by up to 4 percent year-on-year during the Great Recession.\footnote{\url{http://www.fhwa.dot.gov/ohim/tvtw/08dectvt}} Thus, our noise estimates may be inaccurate for later time periods and this may bias our estimates of the impact of noise on house values.
+To the extent that traffic flows and composition significantly changed over time, our traffic noise variables may be inaccurate for those other time periods.
+For instance, the US Department of Transportation reports that total vehicle miles traveled decreased by up to 4 percent year-on-year during the Great Recession.\footnote{\url{http://www.fhwa.dot.gov/ohim/tvtw/08dectvt}} Thus, our noise estimates may be inaccurate for later time periods and this may bias our estimates of the impact of noise on house values.
 Future work may seek to create time-series noise data in order to obtain even better estimates of the impact of traffic noise over time.
@@
 Specifically, we estimate semi-logarithmic regressions at each house within our dataset using only information contained in ``local'' (both geographically and temporally) house sales.
-We find strong evidence that the hedonic function in our study area varies over space and time and such flexible models represent significant improvements over convential parametric models.
+We find strong evidence that the hedonic function in our study area varies over space and time and such flexible models represent significant improvements over conventional parametric models.
 
 Monte Carlo simulations suggest that the better goodness-of-fit provided by the local models are not due to chance and that many hedonic implicit prices vary over space within our study area.
-When the location of our data was randomly assigned and our LWR model was re-estimated across more than a dozen diferent bandwidths, in 100 consecutive simulations the smallest GCV score was obtained when the data were analyzed at a pooled/global level rather than local.
+When the location of our data was randomly assigned and our LWR model was re-estimated across more than a dozen different bandwidths, in 100 consecutive simulations the smallest GCV score was obtained when the data were analyzed at a pooled/global level rather than local.
 That is, after trying thousands of different combinations of varying levels of local analysis with the spatially redistributed data, we never came close to estimating our observed housing sales prices as well as we can with the local analysis on the actual data.
@@
 Precise estimates of the impact of traffic noise are important for efficient implementation of noise mitigation projects.
-The US Federal Highway Admistration reports that 47 states have constructed noise barriers to reduce noise propagation, spending over a half a billion dollars from 2008-2010 \citepalias{USFHA2012}.
+The US Federal Highway Administration reports that 47 states have constructed noise barriers to reduce noise propagation, spending over a half a billion dollars from 2008-2010 \citepalias{USFHA2012}.
 \citet{Delucchi1998} used an estimate of 0.85 percent reduction in house prices per additional decibel in their cost-benefit analysis of traffic noise.
@@
 Future research should be conducted in more housing markets, as the potential to apply the results of analysis in one set of geographical and economic circumstances may be limited.
-Second, ``mixed'' regression techniques (in which some regression coefficients are constrained to remain constant across the study area while others are alowed to vary) may allow researchers to obtain more precise estimates of the impact of hedonic characteristics by increasing the degrees of freedom in the regression.
+Second, ``mixed'' regression techniques (in which some regression coefficients are constrained to remain constant across the study area while others are allowed to vary) may allow researchers to obtain more precise estimates of the impact of hedonic characteristics by increasing the degrees of freedom in the regression.
 Future work may also seek to re-estimate traffic noise models over time to better account for changes in traffic flows associated with macroeconomic conditions.

### 2013-10-15 reports/Draft.Rnw
final edits. submitted DraftAdobe and TitlePageAdobe to the Journal of Regional Science

@@
 \usepackage[round]{natbib}
+\usepackage[nolists]{endfloat}
+\usepackage[width = 5in]{geometry}
 \usepackage{caption, amsmath, graphicx, setspace, multirow, color, hyperref, array}
+
+%\renewcommand{\efloatseparator}{\mbox{}}
 
@@
 \title{The Negative Effect of Traffic Noise on House Prices: A Landscape Hedonic Analysis}
-\date{\today}
+\date{}
 
@@
 \maketitle
+\pagenumbering{roman}
 \begin{singlespace}
@@
 
-\newpage
+\clearpage
+\pagenumbering{arabic}
+
 \section{Motivation and Past Research}\label{sec:lit}
@@
 
-\begin{table}[htb]
+\begin{table}
 \caption{Variable Description and Summary Statistics}\label{tab:sumStats}
@@
 
-\subsubsection{Does the impact of traffic noise vary over space?}
+\subsection{Does the Implicit Price of Traffic Noise Change over Space?}
 In the previous simulation we found that the hedonic regression function indeed exhibits spatial non-stationarity.
@@
 The linear regression results presented in Table \ref{tab:betaMAX} show that there the estimated LWR coefficients for traffic noise are significantly smaller after September 2008.
-\begin{table}[htb]
+\begin{table}
 \caption{Dependent Variable = Traffic Noise LWR Coefficients}\label{tab:betaMAX}
@@
 
-\begin{table}[ht]
+\begin{table}
 \begin{center}
@@
 
+\newpage
 \begin{singlespace}

### 2014-03-01 analysis/00DescriptiveStats/DensityPlotsByYearMaker.R
starting some updates after adding new variables for the revise-and-resubmit

@@ -1,0 +1,32 @@
+
+
+# goal of this file is to create a figure showing the density plot of each variable by year
+# to chekc for substantial changes over time
+
+require(foreign)
+DATAFRAME = read.dbf("~/NoiseHedonicProject/Data/R2GIS/CleanData/Sales20052010.dbf")
+
+myvars = c("SALE_VALUE", "FIN_SQ_FT", "ACRES_POLY", "OWNOCC", "YEAR_BUILT", "MAX", 
+           "MED_INCOME", "MCA3", "CBD_dist", "PARK_dist", "LAKE_dist", "SHOP_dist")
+
+mynames = c("Sale Price (thousands)", "House Size (thousands square feet)", "Lot Size (acres)", "Owner Occupancy Dummy",
+            "Year House was Built", "Traffic Noise (dB)", "Median Income in Census Tract (thousands)", 
+            "Elementary Test Scores", "Distance to Central Business District (km)",
+            "Distance to nearest Park (km)", "Distance to nearest Lake (km)", "Distance to nearest Shopping Center (km)")
+
+
+require("sm")
+require("RColorBrewer")
+
+my.col = brewer.pal(6, "Set2")
+year.f = factor(DATAFRAME$SALE_YR)
+table(year.f)
+
+pdf("graphs/DensityPlotsByYear.pdf", width = 8, height = 8)
+for (i in myvars) {
+  sm.density.compare(DATAFRAME[, as.character(i)], year.f, 
+                     col = my.col, lwd = 3, lty = rep(1, 6),
+                     xlab = as.character(i))
+  legend("topright", levels(year.f), fill=my.col)
+}
+dev.off()

### 2014-03-01 analysis/01GlobalRegression/GlobalRegression_2013_09_12.R

@@ -6,7 +6,7 @@ workingdata20052010$PostCrash = 0
 crashobs <- which(workingdata20052010$TimePeriod>46)
 workingdata20052010$PostCrash[crashobs] = 1
 
-myModel = "logSALE_VA ~ FIN_SQ_FT + ACRES_POLY +  HOMESTEAD +  YEAR_BUILT + MAX +
+myModel = "logSALE_VA ~ FIN_SQ_FT + ACRES_POLY +  HOMESTEAD +  YEAR_BUILT + MAX + PercU18 + PercWhite +
  MED_INCOME + MCA3 + CBD_dist + LAKE_dist + PARK_dist + SHOP_dist  + COUNTY_ID +  factor(SALE_YR) + SALE_MO"
 
 #ACRES_POLY * CBD_dist I(ACRES_POLY^2)* I(CBD_dist ^2)

### 2014-03-01 analysis/02LWRComparisons/gcvFiguresAcrossModels.R

@@ -13,13 +13,13 @@ obs2run = which(DATAFRAME$TimePeriod>11)
 dataPath = "../Data/R2GIS/LWRoutput/"
 filelist = list.files(path = dataPath)
 
-files2open = filelist[which(substr(filelist, 1, 26) == "Sales20052010LWRoutput2013")]
+files2open = filelist[which(substr(filelist, 1, 21) == "Sales20052010LWRmodel")]
 
-pdf("analysis/02LWRComparisons/GCVplots.pdf")
+pdf("analysis/02LWRComparisons/GCVplot.pdf")
 for (myFile in 1:length(files2open)) {
   load(paste0(dataPath, files2open[myFile], sep = ""))
   if (dim(output[[1]])[1] == 42095) gcvs = GCV(output$leverages[obs2run, ], output$yhats[obs2run, ], DATAFRAME$logSALE_VA[obs2run])
-  if (dim(output[[1]])[1] == 31748) gcvs = GCV(output$leverages, output$yhats, DATAFRAME$logSALE_VA[obs2run])
+  if (dim(output[[1]])[1] == 31737) gcvs = GCV(output$leverages, output$yhats, DATAFRAME$logSALE_VA[obs2run])
 #   print(files2open[myFile])
 #   print(min(gcvs))
   ks = as.numeric(substr(colnames(output[[1]]), 2, 5))
@@ -28,9 +28,10 @@ for (myFile in 1:length(files2open)) {
   title(paste0("N = ", dim(output[[1]])[1]), line = .5)
   title(paste("data: ", substr(files2open[myFile], 28, nchar(files2open[myFile]))), line = -1)
   lmreg = lm(MYMODEL, data = DATAFRAME[obs2run, ])
-  levs = lm.influence(lmreg)$hat
+  levs = lm.influence(lmreg, do.coef=FALSE)$hat
   globalGCV = GCV(cbind(levs), cbind(lmreg$fitted.values), DATAFRAME$logSALE_VA[obs2run])
   title(paste("global model gcv:", round(globalGCV, 3)), line = -2)
   title(paste("min gcv:", round(min(gcvs), 4)), line = -3)
+  title(paste("at bandwidth =", ks[which.min(gcvs)]), line = -4)
 }
 dev.off()

### 2014-03-01 analysis/05LWRModelExplorer/LWRMCmodels.R

@@ -7,9 +7,10 @@ require(fields, quietly = TRUE)
 # the following command loads up some functions we'll use
 source("helper/LWRfunctions.R")
 
-MYMODELS = c("logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+HOME_STYLE+OWNOCC+MED_INCOME+MCA3+LAKE_dist+PARK_dist+SHOP_dist+CBD_dist",
-             "logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+HOME_STYLE+OWNOCC+MED_INCOME+MCA3+LAKE_dist+PARK_dist+SHOP_dist+CBD_dist+CITY")
-KVECTOR = c(25, 50, 75, 100, 125, 150, 175, 200, 225, 400, 600, 800, 1000)
+MYMODELS = c(#"logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+HOME_STYLE+OWNOCC+factor(TimePeriod)",
+             "logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+HOME_STYLE+OWNOCC+PercWhite+PercU18+MED_INCOME+MCA3+LAKE_dist+PARK_dist+SHOP_dist+CBD_dist+factor(TimePeriod)",
+             "logSALE_VA~MAX+FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+HOME_STYLE+OWNOCC+PercWhite+PercU18+MED_INCOME+MCA3+LAKE_dist+PARK_dist+SHOP_dist+CBD_dist+factor(TimePeriod)+CITY")
+KVECTOR = c(25, 50, 75, 100, 125, 150, 175, 200, 225, 400, 600, 800, 1000, 1500)
 
 filePrefix = "../Data/R2GIS/CleanData/"
 inputFile = "Sales20052010.dbf"
@@ -26,7 +27,7 @@ for (modelNum in 1:length(MYMODELS)) { #
                         LWRtimelag,
                         Data.Frame = DATAFRAME,
                         my.model = MYMODEL, 
[…]

### 2014-03-01 munge/Sales20052010_munge.R

@@ -1,17 +1,18 @@
 library (foreign)
-sales0510 <- read.dbf("../Data/GIS2R/Sales20052010.dbf")
+sales0510 <- read.dbf("../Data/GIS2R/Sales20052010_airport_and_demographics.dbf")
 summary(sales0510) #found that some observations have a 0 or negative sales value
-t <- which(sales0510$SALE_VALUE < 1)
-sales0510 = sales0510 [-t, ] #Excludes observations without sales value information
+# No need to do the following...
+# t <- which(sales0510$SALE_VALUE < 1)
+# sales0510 = sales0510 [-t, ] #Excludes observations without sales value information
 
 #Pulling the variables we WANT into a new, working dataframe.
-sales0510$GARSQFT <- as.numeric(as.character(sales0510$GARAGESQFT)) #Converting factor to numeric
-sales0510$SALE_SEASON <- factor(sales0510$SALE_QRT)
-sales0510$SALE_MO <- factor(sales0510$SALE_MONTH)
+# sales0510$GARSQFT <- as.numeric(as.character(sales0510$GARAGESQFT)) #Converting factor to numeric
+# sales0510$SALE_SEASON <- factor(sales0510$SALE_QRT)
+# sales0510$SALE_MO <- factor(sales0510$SALE_MONTH)
 sales0510$OWNOCC <- as.numeric(sales0510$HOMESTEAD)-1
 #Creating a time period variable so we can pull data in LWR from a time lag of a 12 month window for each parcel
-sales0510$YEARtemp <- sales0510$SALE_YR - 2005
-sales0510$TimePeriod <- sales0510$YEARtemp*12+sales0510$SALE_MONTH
+# sales0510$YEARtemp <- sales0510$SALE_YR - 2005
+# sales0510$TimePeriod <- sales0510$YEARtemp*12+sales0510$SALE_MONTH
 
 #Cleaning HOME_STYLE independent variable
 table(sales0510$HOME_STYLE)
@@ -65,20 +66,44 @@ bung.home <- sales0510[x1, ]
 bung <- c(x,x1)
 sales0510$HOME_STYLE[bung] <- bung.home$HOME_STYLE[1]
 
-dataNames <- names (sales0510)
[…]

### 2014-03-01 reports/TitlePage.Rnw

--- 2013-10-15 reports/Draft.Rnw
@@
 \date{}
+\author{Aaron Swoboda, Maxwell Timm, and Tsegaye Nega}
 
@@
 
-\clearpage
-\pagenumbering{arabic}
-
-\section{Motivation and Past Research}\label{sec:lit}
-Prolonged exposure to traffic noise affects people in a number of ways, ranging from simple annoyance \citep{Miedema2001, Ouis2001, Ohrstrom2007, DeKluizenaar2013, Weinhold2013}, to sleep disturbance \citepalias{Netherlands2004}, to increasing risk for stroke \citep{Sorensen2011}, hypertension \citep{Jarup2008, Bodin2009}, myocardial infarction \citep{Babisch2005}, and overall quality of life \citep{Shepherd2013}.
-The noise level at which such effects are observed does not have to be high.
-It has been shown that people exposed to traffic noise with a 24-hour average of 55 decibels (dBA) are found to be at a higher risk for hypertension \citep{Barregard2009, Bodin2009}, and those exposed to 60 dBA or greater are found to be at a higher risk for stroke \citep{Sorensen2011}.
-
-Automobiles are already perhaps the greatest source of noise in residential neighborhoods \citep{Barber2010} and traffic noise was estimated to cause around three billion dollars worth of external damage to the United States economy alone in 1991 \citep{Delucchi1998}.
-Traffic noise and its attendant problems are greater now than they were in the 1990s and predicted to worsen in the future \citep{Goines2007}.
-%With the exception of a slight dip during the economic recession in the late 2000s, the number of vehicle miles traveled in the United States has steadily increased for the past 50 years.\footnote{\url{http://www.fhwa.dot.gov/policyinformation/statistics/2011/pdf/rc1c.pdf}}
-Globally, \citet{Dargay2007} predict the number of personal vehicles to grow from roughly 800 million in 2002 to over two billion units by 2030.
-Additionally, the global trend of increased urbanization is expected to continue, with the proportion of the population living in cities growing from roughly half now to over two-thirds by the middle of the century \citepalias{UNDESA2012}.
-
-One way to estimate some of the costs of traffic noise (and therefore the economic benefits of policies that reduce noise) is through hedonic regression, examining the relationship between house prices and noise levels.
-\citet{Nelson1982} was the first to review some of the earliest noise hedonic work in the United States and Canada.
-The review of nine studies found an average estimated impact of traffic noise to be a reduction in house prices of approximately 0.4 percent per additional decibel.
-More recently, \citet{Nelson2008} notes that many of these early studies \citep[such as][]{Gamble1974, Langley1976} are plagued by issues of small sample sizes (in the hundreds) and limited spatial extents (one or a handful of cities).
-
-Reviews of the research by \citet{Bateman2001} found that the negative effect of traffic noise on house prices ranged from 0.08 to 2.22 percent per decibel with a mean around 0.55 percent per decibel, while \citet{Navrud2002} found an average decrease of 0.64 percent per decibel.
-Much of the recent research in this literature has tended to focus on the European experience with noise, often due to the availability of high quality traffic noise data made available from the government, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Switzerland \citep{Baranzini2010}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, Netherlands \citep{Theebe2004a}, and Germany \citep{Brandt2011}.
-
-Instead of focusing on the impact of automobile traffic noise, hedonic work in the United States has tended to concentrate on noise from airports \citep{Espey2000, McMillen2004, Cohen2008a} or indirect measures of traffic noise, such as proximity to highways \citep{Matthews2007, Chernobai2009, Li2012}, or traffic counts \citep{HughesJr.1992, Larsen2012}.
-One exception is \citet{Cheng2008}, which finds that an additional decibel of traffic noise reduced house prices in Louisville, Tennessee, by 0.34 percent during the year 2007.
-However, the generalizability of this research is limited given that it is based on less than a thousand house transactions in just one city.
-
-A major reason for the thinness of the scholarly literature on this topic in the US lies in the difficulty of modeling traffic noise propagation over the landscape.
-To properly analyze the spatial association between real estate prices and exposure to traffic noise, it is necessary to create a noise surface map at sufficiently detailed spatial resolution to account for the complex and heterogeneous interaction between the noise source and the resistance of the landscape to noise propagation.
-Implementing such a model can be very difficult.
-The data needed for the model is very extensive and may not even be readily available (e.g., building footprint and height data).
-Furthermore, it is computationally very intensive.
-Fortunately, recent developments in Geographic Information Systems and distributive computing have reduced these difficulties, making it much easier to create a noise surface map at landscape level with high spatial resolution.
-
-In this paper, we estimate the relationship between traffic noise and single family house prices across 44 cities and several hundred square miles in the St.\ Paul, Minnesota, urban region by taking advantage of a uniquely detailed set of noise estimates.
-The data represent perhaps the most accurate regional noise estimates ever used in the hedonic literature in the United States to date due to the high spatial resolution of the estimates (10 m x 10 m) and the incorporation of the effects of nearby buildings and land cover on noise propagation.
-More detail about the noise model inputs and procedures are presented in the next section of the paper.
-
-%Precise estimates of the impact of traffic noise are important for efficient implementation of noise mitigation projects.
-The US Federal Highway Admistration reports that 47 states have constructed noise barriers to reduce noise propagation, spending over a half a billion dollars from 2008-2010 \citepalias{USFHA2012}.
-\citet{Delucchi1998} used an estimate of 0.85 percent reduction in house prices per additional decibel in their cost-benefit analysis of traffic noise.
-While their preferred estimate of the total damage cost to the United States in 1991 is \$3 billion, they report a possible range of less than \$100 million to over \$40 billion due in part to uncertainty surrounding the degree of noise propagation over space in the urban built environment and the effect of noise on house prices.
-Indeed, one of the main conclusions of their work is that more research should be done to better understand the impact of noise on house prices and that better noise data are needed for such work to occur.
-
-Work from Europe suggests that the relationship between traffic noise and house prices varies across housing submarkets \citep{Day2007, MarmolejoDuarteCarlos;GonzalezTamez2009}, by level of traffic noise \citep{Theebe2004a, Brandt2011}, and over time \cite{Wilhelmsson2000}.
-As such, we construct a flexible hedonic model that allows for a non-stationary relationship between house prices and our explanatory variables over geography and time.
-Such Locally Weighted Regression (LWR) models have become increasingly common in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than other common spatial econometric models under common real world circumstances \citep{McMillen2012}.
-Thus, in addition to using new data that reduces the measurement error of the impact of traffic noise, the spatial and temporal variation in our data and hedonic modeling allow us to present the first estimates in the United States of how the impact of traffic noise varies over space, time, and by noise level.
-
-We find that while the impact of other important control variables in the hedonic function vary significantly over space, the impact of traffic noise does not.
-Such results are contradictory to recent work by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} which found evidence of a spatially non-stationary relationship between traffic noise and housing prices using a LWR model in Barcelona, Spain.
-Our paper also presents the first estimates of the implicit price of traffic noise after the housing market collapse and economic recession of 2008-09.
-Contrary to work such as \citet{Cho2011b}, which found that environmental amenities mattered \emph{less} after the housing crash, our estimated effect of traffic noise mattered \emph{almost twice as much more} after the recession (0.19 percent reduction in house prices per additional decibel beforehand compared to 0.37 percent per decibel afterwards).
-We conclude with a discussion of how future research can expand and improve upon this work.
-
-\section{Study Area and Data}
-The 2010 US Census lists the population of the Twin Cities Metropolitan Region (Minneapolis and St.\ Paul and their surrounding areas) as almost 3 million residents spread over seven counties.
-This study examines single family residential home transactions in the Census-defined urban areas of three of the seven counties: Dakota, Ramsey and Washington County (see Figure \ref{fig:overview}).
-We obtained sales data from approximately forty thousand transactions between 2005 and 2010 (n=42,095) from the 2010 MetroGIS Regional Parcel Dataset published by the Metropolitan Council.
-Figure \ref{fig:overview} shows an overview of the study area as well as the spatial distribution of the house sales prices.
-
-In addition to the geographic location and date of the house sale, we collected or calculated structural and locational variables commonly used in the hedonic literature, such as the size of the house, lot size, and architectural style of the house, as well as distances to amenities like the Central Business District, parks, and lakes.
-Table \ref{tab:sumStats} provides a brief description of the variables in our data and some basic summary statistics.
-Table \ref{tab:cor} displays a simple correlation matrix of the quantitative variables.
-
-\begin{figure}
-\makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/StudyAreaSaleValueDist}}
-\caption{This figure shows the spatial extent of our study area as well as the significant spatial variation in single family house sales prices.}\label{fig:overview}
-\end{figure}
-
-\begin{table}
-\caption{Variable Description and Summary Statistics}\label{tab:sumStats}
-\makebox[\linewidth][c]{
-\small
-\begin{tabular}{lrrrrrrr}
-
- & min & 25\% & 50\% & mean & 75\% & max & st.\ dev.\ \\ 
-  \hline
-  Sale Price (\$1,000s) & 98.8 & 195.0 & 241.0 & 265.5 & 314.9 & 675.0 & 102.8 \\ 
-  House Size (square feet) & 390 & 1158 & 1628 & 1750 & 2188 & 4000 & 704 \\ 
-  Lot Size (acres) & 0.02 & 0.17 & 0.25 & 0.25 & 0.31 & 0.60 & 0.11 \\ 
-  Owner Occupancy (no = 0, yes = 1) & 0.0 & 1.0 & 1.0 & 0.8 & 1.0 & 1.0 & 0.4 \\ 
-  Year of House Construction & 1850 & 1950 & 1973 & 1967 & 1993 & 2010 & 32 \\ 
-  Traffic Noise (dB) & 25.1 & 50.5 & 55.3 & 56.4 & 62.2 & 91.5 & 8.8 \\ 
-  Median Income in Census Tract (\$1,000s) & 13.9 & 54.6 & 69.1 & 72.6 & 89.7 & 143.3 & 23.6 \\ 
-  Average 3rd Grade Standardized Test Scores & 335.6 & 359.8 & 365.4 & 364.5 & 370.4 & 551.7 & 10.6 \\ 
-  Distance to Central Business District (km) & 1.1 & 6.8 & 13.2 & 14.7 & 21.8 & 37.1 & 8.9 \\ 
-  Distance to nearest Park (km) & 0.0 & 1.1 & 2.2 & 2.6 & 3.8 & 9.7 & 1.9 \\ 
-  Distance to nearest Lake (km) & 0.0 & 0.4 & 0.8 & 0.9 & 1.3 & 4.4 & 0.7 \\ 
-  Distance to nearest Shopping Center (km) & 0.0 & 0.9 & 1.5 & 1.9 & 2.3 & 10.8 & 1.6 \\ 
-   \hline
-\end{tabular}
-}
-\end{table}
-
-\begin{table}
-\caption{Matrix of Pearson Correlation Coefficients for Quantitative Variables}\label{tab:cor}
-%\includegraphics[width = \textwidth]{../graphs/CorrelationMatrix}
-\begin{center}
-\small
-\tabcolsep=0.05cm
-\makebox[\linewidth][c]{
-\begin{tabular}{l|rrrrrrrrrrr}
- & \multicolumn{1}{x{.35in}}{Price} & \multicolumn{1}{x{.38in}}{House} & \multicolumn{1}{x{.35in}}{Lot} & 
- \multicolumn{1}{x{.35in}}{Built} & \multicolumn{1}{x{.35in}}{Noise} & \multicolumn{1}{x{.35in}}{Inc.} & 
- \multicolumn{1}{x{.35in}}{Test} & \multicolumn{1}{x{.35in}}{CBD} & \multicolumn{1}{x{.35in}}{Park} & \multicolumn{1}{x{.35in}}{Lake} & \multicolumn{1}{x{.35in}}{Shop} \tabularnewline 
-  \hline
-Sale Price & 1 &  &  &  &  &  &  &  &  &  &  \tabularnewline 
-  House Size & 0.74 & 1 &  &  &  &  &  &  &  &  &  \tabularnewline
-  Lot Size & 0.38 & 0.45 & 1 &  &  &  &  &  &  &  &  \tabularnewline
-  Year Built & 0.45 & 0.52 & 0.47 & 1 &  &  &  &  &  &  &  \tabularnewline
-  Noise & -0.13 & -0.07 & 0.00 & -0.19 & 1 &  &  &  &  &  &  \tabularnewline
-  Income & 0.52 & 0.50 & 0.41 & 0.57 & -0.18 & 1 &  &  &  &  &  \tabularnewline
-  Elem.\ Test Scores & 0.29 & 0.28 & 0.29 & 0.34 & -0.04 & 0.44 & 1 &  &  &  &  \tabularnewline 
-  Distance to CBD & 0.31 & 0.45 & 0.43 & 0.58 & -0.04 & 0.53 & 0.35 & 1 &  &  &  \tabularnewline
-  Distance to Park & 0.25 & 0.28 & 0.22 & 0.42 & -0.13 & 0.38 & 0.22 & 0.57 & 1 &  &  \tabularnewline
-  Distance to Lake & -0.04 & -0.10 & -0.25 & -0.17 & -0.03 & -0.12 & -0.10 & -0.09 & 0.20 & 1 &  \tabularnewline
-  Distance to Shop & 0.27 & 0.27 & 0.15 & 0.37 & -0.19 & 0.36 & 0.18 & 0.46 & 0.38 & 0.15 & 1 \tabularnewline
-\end{tabular} }
-\end{center} 
-\end{table}
-
-\subsection{Noise Data}
-To determine the relationship between real estate price and road traffic noise levels, we first created a traffic noise exposure surface by calculating the propagation of traffic noise over the landscape using the FHWA (Federal Highway Authority) 1978 standard \citep{Barry1978}.
-Following \citet{Barry1978}, the traffic noise level at any given location on the landscape is given by:
-\begin{eqnarray}\label{eq:noise}
-L_{EQ}(i) &=& \bar{L}_0(i) + 0.115 \sigma _i^2 + 10 log \frac{N_i \pi D_0}{T*S_i} + 10 log \left[ \frac{D_0}{D}\right]^{1 + \alpha}  \nonumber \\
-&& + 10 log \left( \frac{\psi _{\alpha (\phi _1, \phi _2)}}{\pi}\right) + \Delta _{gradient} + \Delta _{shielding}
-\end{eqnarray}
-where $L_{EQ}(i)$ is A-weighted hourly energy equivalent noise level in decibels (dBA), which is calculated for each class $i$ of vehicle (automobile and trucks); $\bar{L}_0(i)$ is the mean Sound Pressure Level (SPL) at the reference distance for class $i$; $\sigma _i$ is the standard deviation of the SPL for each class of vehicle; $N_i$ is the number of vehicles of the $i^{th}$ class passing during the relevant hour; $D_0$ is the reference distance (usually 15 m); $D$ is the perpendicular distance from the road center line to the receiver; $\alpha$ is a site parameter (soft and hard surface), $0 < \alpha < 1$; $S_i$ is the mean speed of the $i^{th}$ class; $T$ is the duration, usually 1 hour; $\phi _1$ and $\phi _2$ are the angles from the perpendicular of the limits of the observer's view of a section of the road.
-They are used to account for only the energy coming from a portion of the roadway; $\Delta _{gradient}$ is an adjustment for road surface gradient; $\Delta _{shielding}$ is a shielding adjustment (land cover, buildings, noise barriers).
-
-To calculate the traffic noise map for the region using the above model, several data sources were used.
-A 2007 road centerline and the associated traffic characteristics (volume and proportion of trucks and vehicles) for the region were obtained from the Minnesota Department of Transportation (MNDoT).
-We converted the posted speed of each road into a GIS layer.
-For all roads without recorded traffic volume (i.e., residential), we assigned 100 vehicles/day as a minimum estimate.
-This estimate was based on factors identified in the literature as important for estimating traffic volume, such as census data on commuting population, tract area, the size of a standard street block, and road type \citep{Cheng1992, Fricker1986}.\footnote{In order to assess the sensitivity of our results to our estimate of traffic volume for local roads, we also ran the model using 200 and 300 vehicles/day for one county.
-With the exception of a few areas in the rural part of the county, there was less than 0.05 dBA difference at 30 m from the road centerline.}
-
-Data on traffic volume and the proportion of trucks and vehicles on each segment of the road were averaged over a 24-hour period, making it impossible to account for a day and night time variation in traffic noise.
-Following \citet{Arditi2007}, we divided the total traffic volume into day and nighttime periods by assuming that 80 percent of vehicles and 65 percent of trucks are driven during the daytime (6am -- 10pm) and 35 percent of trucks and 20 percent of vehicles are driven during the nighttime (10pm--6am).
-Values for ground absorption were chosen by assuming that all road surfaces consisted of impervious bitumen.
-For computational simplicity, we created the road surface gradient by re-sampling US Geological Survey 30 m resolution Digital Elevation Model (DEM) to 100 m resolution.
-
-We used three data sources for the shielding adjustment: buildings, foliage, and noise barriers.
-We extracted the perimeter and height of 818,500 buildings using aerial photography and LiDAR data.
-For the areas where LiDAR data are available, we used LiDAR Analyst$^{TM}$ software to extract buildings’ footprints.
-For the areas of the region where only aerial photos are available, we used Feature Analyst$^{TM}$ software to extract building footprints.
-For measurements extracted using aerial photography, height was determined using a combination of parcel data and field measurements.
-
-The locations chosen for the traffic noise levels were the 818,500 buildings in the entire urban area.
-Thus, we used the perimeter and height of these buildings to account for the shielding effect of buildings.
-To account for foliage shielding (and to make the computation manageable), we assumed that only forest patches that are at least 10 m high and have an area greater than 10,000 m$^2$ will have a significant effect on noise attenuation.
-Accordingly, we extracted forest polygons with these characteristics using a combination of year 2005 land use data and 2001 National Land Cover Data (NLCD).
-To account for noise barrier shielding, we used a noise barrier layer obtained from MNDoT, which contains the locations, width, and height of noise barriers in the region.
-
-We used the SoundPlan$^{TM}$ noise modeling software to implement the model given by Equation~\eqref{eq:noise}.
-Predicted traffic noise output is calculated at a grid resolution of 10 m$^2$.\footnote{We conducted a preliminary validation of the model output by comparing it with observed noise levels at 134 locations that were sampled along major highways.
-For each location, two readings were taken very close to the highway, one between 9am and 10am and another between 1pm and 2pm.
-The noise level for each location is then determined by averaging the two observed values, and this average is then compared with the predicted noise level.
-The relationship between the mean observed and predicted noise levels is linear and moderately strong with a correlation of 0.76.
-It is not surprising that the relationship is not stronger given the size and complexity of the model.
-In particular, the traffic volume data that we used for modeling traffic noise propagation is a 24-hour average, which requires more time-interval sampling per location than just the two used in the validation.
-Still, this preliminary comparison serves as a good indicator of how well this model captures traffic noise levels.} Once the noise surface for the entire region was developed, we extracted the noise surface for the present study area by overlaying the housing parcel boundaries and calculating the maximum noise level within the parcel.
-
-\subsection{Structural Attributes}
-According to a review by \cite{Wilhelmsson2000}, the five most common structural attributes included in real estate hedonic pricing studies are living area, number of bathrooms, age, garage and lot size.
-The 2010 MetroGIS Regional Parcel Dataset includes structural data on living area, age, garage presence, lot size, owner-occupancy and house architectural style for every transaction.
-However, standard additional control variables like the number of bathrooms, bedrooms, and size of garage were not available through this source.
-We were able to obtain additional data for the number of bedrooms, bathrooms, and size of the garage for a subset of our house sales from the Dakota County Assessor's Office.
-In section \ref{Discussion} we show that the inclusion of these variables in our model does not significantly change our results for these areas.
-Therefore, we feel confident in our results even without these independent variables for most of our study area.
-%Additionally, other hedonic work has been published using a similar set of explanatory variables in this area, see for instance, \citet{Sander2009b}.
-
-\subsection{Other Locational Attributes}
-A common real estate adage states that the three most important real estate attributes are: location, location and location.
-Knowing where each house is located allows us to also construct a vector of other attributes associated with the sales transaction.
-For instance, using GIS software we are able to calculate the Euclidean distance to numerous points of interest within the dataset, such as the nearest central business district, shopping centers, parks, and lakes.
-Additionally, a variable denoting the median household income for the surrounding census tract is created through the use of TIGER shapefiles from the 2010 Census Bureau and data from the 2010 American Community Survey.
-Lastly, we associate each transaction with its elementary school and include the average 3rd grade Minnesota Comprehensive Assessment (MCA) score for the local elementary school during the year of purchase.\footnote{Test scores were obtained from the Minnesota Department of Education website.
-The school district and elementary school attendance boundary spatial information were obtained from the Minnesota Geospatial Information Office Clearinghouse Data Catalog.}
-
-\subsection{Time}
-Given that we have data from before and after the recession of 2008-09, we subset the data in Table \ref{tab:SumStatsTime} by year of sale to look for differences over time.
-In addition to the noticeable decline in nominal sales values, there is also a drop in the number of sales across years.
-For example, in 2010 there were only 4,206 property sales within the dataset, less than half as many in 2005.
-While the mean sale price declined from roughly \$280,000 pre-crash to \$230,000 post-crash, most of the structural and neighborhood variables are relatively consistent across years.
-However, traffic noise displays a noticeable difference in the pre- and post-crash market transactions (the mean drops from over 58 dB to less than 53 dB).
-
-\begin{table}
-\begin{center}
-\caption{Mean Variable Values by Year}\label{tab:SumStatsTime}
-\small
-%\includegraphics[width = \textwidth]{../graphs/DescriptiveStatsByYear}
-% Table generated by Excel2LaTeX from sheet 'Descriptive StatisticsYear'
-    \begin{tabular}{lrrrrrr|r}
-    Variable & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2005-10\\ \hline
-    Sales Value (\$1000s) & 279   & 282   & 275   & 263   & 231   & 233   & 266 \\
-    Traffic Noise (dB) & 58.5  & 58.6  & 58.6  & 52.5  & 52.8  & 52.8  & 56.4 \\
-    House Size (ft$^2$) & 1737  & 1736  & 1743  & 1813  & 1727  & 1775  & 1750 \\
-    Lot Size (acres) & 0.25  & 0.25  & 0.25  & 0.26  & 0.25  & 0.26  & 0.25 \\
-    Year Built  & 1967  & 1966  & 1966  & 1971  & 1968  & 1968  & 1967 \\
-    Median Income (\$1000s) & 72.0  & 72.1  & 72.3  & 74.8  & 72.6  & 73.2  & 72.6 \\
-    Elem. Test Scores & 364.8 & 364.8 & 365.2 & 363.5 & 362.3 & 366.1 & 364.5 \\
-    Dist.\ to CBD (km) & 14.7  & 14.6  & 14.8  & 15.0  & 14.3  & 14.5  & 14.7 \\
-    Dist.\ to Park (km) & 2.6   & 2.6   & 2.6   & 2.8   & 2.6   & 2.6   & 2.6 \\
-    Dist.\ to Lake (km) & 0.9   & 0.9   & 0.9   & 0.9   & 0.9   & 0.9   & 0.9 \\
-    Dist.\ to Shop (km) & 1.9   & 1.9   & 1.8   & 2.0   & 1.9   & 1.9   & 1.9 \\ \hline
-    Number of Observations &  10,991  & 8,885  &  6,549  & 5,503  &  5,961  & 4,206  & 42,095  \\
-    \end{tabular}%
-\end{center}
-\end{table}
-
-\section{Basic Econometric Model}\label{basicModel}
-Our aim is to estimate the marginal willingness to pay for different attributes, in particular changes in the traffic noise associated with the house.
-Consistent with past research, this study implements a semi-logarithmic hedonic pricing model.
-Before implementing the Locally Weighted Regression model, we present the results of a simpler econometric model given by equation~\eqref{eq:model}.
-\begin{equation}\label{eq:model}	
-ln \textrm{ Sale Price}_i = \beta _0 + \beta _1 \textrm{Noise}_i+ \beta _2 S_i+ \beta _3 N_i + \beta _4 T_i + \textrm{error}_i
-\end{equation}
-Noise$_i$ is the noise level for house $i$, $S_i$ is a vector of the house's structural attributes, $N_i$ is a vector of the neighborhood attributes, and $T_i$ is a vector of time fixed effects.
-Due to the semi-logarithmic functional form of the model, we can interpret the regression model coefficients as the price semi-elasticities of the underlying attributes.
-For instance, we can interpret the coefficient on noise as the percentage increase in price for a one decibel increase in the traffic noise associated with the transaction in our dataset.
-
-\begin{table}
-\caption{Basic Regression Results (dependent variable = $ln(\textrm{Sale Price})$)}\label{tab:globalRegression}
-
-\makebox[\textwidth][c]{%\includegraphics[width = 1.3\textwidth]{../graphs/GlobalRegression}}
-% Table generated by Excel2LaTeX from sheet 'Sheet1'
-  \centering
-  \tabcolsep=0.03cm
-    \begin{tabular}{lclcclcclccl}
-   & (1)   &       &       & (2)   &       &       & Pre-Crash   &       &       & Post-Crash   &  \\ \hline
-\T  Traffic Noise & -2.02E-03 & *** &   & -2.00E-03 & ***   &   & -1.63E-03 & ***  & & -3.08E-03 & *** \\
-          & (1.32E-04) &   &   & (1.32E-04) &       &       & (1.38E-04) &       &       & (3.29E-04) &  \\
-\T  Intercept & 9.37E+00 & ***   & \hspace{.5cm} & 9.49E+00 & ***   & \hspace{.5cm}   & 8.55E+00 & ***   & \hspace{.5cm}   & 1.10E+01 & *** \\
-          & (9.48E-02) &    &   & (9.62E-02) &   &   & (1.11E-01) &       &       & (2.12E-01) &  \\
-\T   House Size & 3.38E-04 & ***   &   & 3.39E-04 & ***   &   & 3.35E-04 & ***   &   & 3.50E-04 & *** \\
-          & (1.85E-06) &   &   & (1.86E-06) &       &       & (1.99E-06) &       &       & (4.26E-06) &  \\
-\T  Lot Size & 1.42E-01 & ***   &    & 2.74E-01 & ***   &   & 2.31E-01 & ***   &      & 2.74E-01 & *** \\
-          & (1.14E-02) &     &   & (2.12E-02) &     &      & (2.29E-02) &       &       & (4.99E-02) &  \\
-\T  Owner Occupancy & 3.22E-02 & ***   &   & 3.23E-02 & ***   &     & 3.38E-02 & ***  & & 2.61E-02 & *** \\
-          & (2.80E-03) &  &   & (2.79E-03) &       &       & (3.24E-03) &       &       & (6.41E-03) &  \\
-\T  Year Built & 7.82E-04 & ***   &   & 7.17E-04 & ***   &    & 9.68E-04 & ***   &   & 2.15E-06 &  \\
-          & (4.57E-05) &       &       & (4.65E-05) &   &   & (5.06E-05) &    &   & (1.05E-04) &  \\
-\T  Median Income & 3.03E-06 & ***  & & 3.31E-06 & ***  &   & 2.86E-06 & ***   &       & 4.06E-06 & *** \\
-          & (5.87E-08) &       &       & (5.87E-08) &   &   & (6.56E-08) &       &       & (1.35E-07) &  \\
-\T  Elem. Test Scores & 1.88E-03 & *** &   & 1.81E-03 & ***   &   & 3.11E-03 & *** & & 1.21E-03 & *** \\
-          & (1.06E-04) &  &   & (1.06E-04) &   &       & (1.75E-04) &       &       & (1.55E-04) &  \\
-\T  Distance to CBD & -1.56E-06 & ***  &  & 7.46E-07 & *     &  & -1.57E-07 &   &       & 1.40E-06 &  \\
-          & (1.97E-07) &       &       & (3.70E-07) &       &       & (3.95E-07) &   &   & (8.98E-07) &  \\
-\T  Distance to Park & -2.38E-07 &   &    & -5.48E-07 &    &   & -6.37E-07 &  &   & -4.01E-07 &  \\
-          & (6.82E-07) & &   & (6.83E-07) &       &       & (7.33E-07) &       &       & (1.58E-06) &  \\
-\T  Distance to Lake & 2.12E-05 & ***   &   & 2.36E-05 & ***   &   & 2.22E-05 & ***   & & 2.79E-05 & *** \\
-          & (1.68E-06) &       &    & (1.71E-06) &   &    & (1.83E-06) & &  & (4.03E-06) &  \\
-\T  Distance to Shop & 3.01E-06 & ***   &    & 3.12E-06 & ***   & & 4.16E-06 & ***   &    & 1.88E-06 &  \\
-          & (7.67E-07) &       &       & (7.66E-07) &       &       & (8.17E-07) &  & & (1.82E-06) &  \\
-\T  Lot Size * Distance to CBD &  &   & & -8.81E-06 & *** & & -6.66E-06 & ***   &       & -9.55E-06 & ** \\
-          &   &   &   & (1.19E-06) &       &       & (1.27E-06) &       &       & (2.94E-06) &  \\
-\T  County Fixed Effects & yes   &   &   & yes   &       &       & yes   &       &       & yes   &  \\
-    Year of Sale Fixed Effects & yes   &   &   & yes   &   &       & yes   &       &       & yes   &  \\
-    Month of Sale Fixed Effects & yes   &   &   & yes   &   &       & yes   &       &       & yes   &  \\ \hline
-\T  Number of Observations &        42,095  &   &  &    42,095  & & &   31,253  & & &    10,842  &  \\
-    R$^2$   & 0.696 &       &       & 0.696 &       &       & 0.714 &       &       & 0.613 &  \\
- \multicolumn{12}{l}{(standard errors) ***$p<.001$; **$p<.01$; *$p<.05$}  \\
-    \end{tabular}%
-}
-\end{table}
-
-Column (1) in Table \ref{tab:globalRegression} displays the results of our basic regression model.
-All coefficients but one are significantly different from zero at conventional significance levels.
-The traffic noise coefficient suggests that a one decibel increase traffic noise is on average associated with a 0.2 percent reduction in housing sales prices.
-Standard urban economic theory \citep{Alonso1964, Mills1967, Muth1969} predicts that the price of land will vary over space within our dataset to account for locational amenities.
-As such, the other columns include an interaction term between lot size and distance to the nearest central business district to account for spatial variation in the price of land.
-The significant coefficients on the lot size interaction terms suggest that the value of land varies over space.
-Other regressions (results available upon request) show similar variation in the implicit prices of house characteristics over space.
-
-Table \ref{tab:globalRegression} also attempts to begin to understand how the economic recession may have influenced the hedonic function in our study area.
-The third and fourth columns estimate the same regression as (2) but subset the sales before and after September of 2008 (the month that Lehman Brothers filed for bankruptcy, the US Federal government took over Fannie Mae and Freddie Mac, and the American International Group (AIG) narrowly avoided bankruptcy only through a \$85 billion loan from the US Federal government).\footnote{\url{http://www.federalreserve.gov/newsevents/press/other/20080916a.htm}} The coefficients for some of the hedonic variables of interest (noise, schools, land, for instance) appear different across the two time periods.
-
-The results in Table \ref{tab:globalRegression} and previous work \citep[such as][]{Day2007, MarmolejoDuarteCarlos;GonzalezTamez2009} suggests that the relationship between prices and many other hedonic characteristics may vary over space.
-While methods exist for parameterizing this variation \citep[such as spatial expansion as suggested by][]{Casetti1972}, we have no a priori knowledge of how to parameterize the variation over space and time.
-As such, we turn to a semi-parametric form of hedonic regression, a flexible modeling approach which lets the data reveal how relationships vary, rather than specifying them beforehand.
-Such a modeling choice will allow us to test the hypotheses of spatial and temporal stationarity in the regression model.
-
-\section{Locally Weighted Regression Model}
-Locally Weighted Regression (LWR) techniques (also known as Geographically Weighted Regression) are described in detail by \citet{Cleveland1988}, \citet{Brunsdon1998b}, \citet{Fotheringham2002}, and others.
-It is a weighted least squares methodology in which regression coefficients are estimated over space as a function of the local data as described in Equation~\eqref{eq:LWRbeta},
-\begin{equation}\label{eq:LWRbeta}
-\hat{\beta}_i = (X'W_iX)^{-1}X'W_iY,
-\end{equation}
-where X is a $n \times m$ matrix of independent variables, $W_i$ is the $n \times n$ weights matrix, and Y is the $n \times 1$ vector of dependent variable values.
-The weights matrix, $W_i$ is a diagonal matrix where element $w_{jj}$ denotes the weight that the $j^{th}$ data point will receive in the regression coefficients estimated at location $i$ in the dataset.
-We employ a bi-square weights function and a k-nearest neighbor bandwidth approach as described in equation~\eqref{eq:weights},
-\begin{equation}\label{eq:weights}
-w_{jj}=\left[1-\left(\frac{d_{ij}}{d_{k}}\right)^2 \right]^2 \textrm{ if  }d_{ij}<d_{ik}\textrm{, otherwise = 0},
-\end{equation}
-where $d_{ij}$ denotes the distance between observations $i$ and $j$, and $d_{ik}$ is the distance from observation $i$ to the $k^{th}$ nearest observation.
-This function assigns weights close to 1 for data points near observation $i$, weights positive but closer to zero for observations farther away, and zero for all $n-k$ observations farther away than the $k^{th}$ nearest observation.
-We estimate LWR coefficients using bandwidths ranging from as small as $k=50$ observations and as large as 10,000 observations.
-We choose the LWR bandwidth my minimizing the Generalized Cross Validation score as detailed in equation~\eqref{eq:GCV},
-\begin{equation}\label{eq:GCV}
-n*\sum_{i=1}^{n}\frac{(y_i-\hat{y}_i)^2}{(n-v_1)^2}, 
-\end{equation} 
-where $y_i$ is the dependent variable value, $\hat{y}_i$ is the predicted dependent variable value for observation $i$, and $v_1$ is the ``effective number of model parameters.''
-$v_1=$tr(\textbf{S}), where the matrix \textbf{S} is the ``hat matrix'' which maps $y$ onto $\hat{y}$,
-                   \begin{equation*}
-                   \hat{y}=\textbf{S}y,
-                   \end{equation*}
-                   and each row of \textbf{S}, $r_i$ is given by:
-                     \begin{equation*}
-                   r_i=X_i(X'W_iX)^{-1}X'W_i.
-                   \end{equation*}
-The GCV score is a convenient model selection metric that rewards models that provide a good fit to the data, while penalizing models with a greater number of model parameters \citep{Loader1999, McMillen2010}.
-Model selection via this strategy has been shown to discern whether spatially varying relationships exist, accurately estimate spatially varying coefficients, even outperform other spatial econometric techniques, and do so without wasting degrees of freedom \citep{Paez2011, McMillen2010, McMillen2012}.
-
-%\section{Results}
-Similar to the basic econometric model described in Section \ref{basicModel}, the LWR model estimates the logged sales price of a house as a function of structural variables, location and time.
-In order to account for changing market conditions in our data, when estimating LWR coefficients we use only houses sold within the past 12 months.
-Thus, the coefficient estimates at a particular house are estimated using data from other sales nearby in both time and geography.
-
-\subsection{Improved Model Performance}
-The use of the Locally Weighted Regression model significantly increases model performance.
-Figure \ref{fig:GCVmodel} displays the Generalized Cross Validation score for three different model specifications with varying number of observations included in the regression bandwidth.
-Two important conclusions can be drawn from the results.
-First, local analysis (bandwidths of a couple hundred observations) perform significantly better than global models, and second, conditional on the bandwidth, performance improves with the inclusion of more locational variables.
-The minimum GCV score is obtained using a bandwidth of 200 nearest houses and a model including structural, locational, and city fixed-effects.
-
-We estimate three different models.
-Model (1) uses only the basic structural characteristics as the explanatory variables (size of the house in square feet, size of the lot in acres, a categorical variable denoting the architectural style of the house, and whether or not the house is owner-occupied).
-Model (2) adds locational variables to the previously described model (test scores at the local elementary school, census tract median income, and distances to the central business district, nearest park, nearest shopping center, and nearest lake).
-The third model adds city fixed effects.
-Generally speaking, the third model performs slightly better than the second model, which performs substantially better than the first model.
-\begin{figure}
-  \makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/GCVbyModel}}
-\caption{This figure shows the relationship between bandwidth size and the GCV score for three different Locally Weighted Regression (LWR) models.
-For comparison, the GCV scores for each model when estimated at a global scale are also shown.
-Note that the LWR models all have significantly smaller GCV scores than the global models.
-The minimum GCV score is obtained by LWR Model (3) at a bandwidth of 200 nearest houses.}\label{fig:GCVmodel}
-\end{figure}
-
-We also estimate each of the three models at varying levels of local analysis, with bandwidths ranging from the nearest 50 observations to the nearest 10,000.
-Models with bandwidths of only a couple hundred observations have substantially smaller GCV scores, suggesting that, conditional on control variables included in the model, model performance still improves by performing the analysis at the local level.
-It is also worth noting that the LWR models have significantly lower GCV scores for a range of bandwidths when compared to the global models.
-These results suggest that it is important to model our data in a spatially explicit manner.
-
-Table \ref{tab:mainresults} displays a summary of the results of LWR Model (3) and a similar regression model run without allowing for spatial variation in the regression coefficients.
-Again, note that the LWR model yields a substantially smaller GCV score (0.027 vs.\ 0.041) signifying a substantial improvement in model performance.
-In addition to the significant reduction in the GCV score obtained with the use of LWR, we also see a substantial reduction in the degree of spatial autocorrelation in the model residuals.
-We calculate Moran's I statistic to be 0.199 for the global model while our preferred LWR specification yields 0.012, a more than ten-fold reduction.
-
-% latex table generated in R 2.15.2 by xtable 1.7-0 package
-% Mon Jun 24 16:36:58 2013
-
-\begin{table}[bp]
-\caption{Hedonic Regression Results (dependent variable = $ln(\textrm{Sale Price})$)} \label{tab:mainresults} 
-\makebox[\linewidth]{
-\small
-\begin{tabular}{lrrrrrr} \\
- & \multicolumn{2}{c}{Global Model} & \multicolumn{4}{c}{Locally Weighted Regression Model} \\
- & \multicolumn{1}{c}{$\hat{\beta}$} & \multicolumn{1}{c}{$\hat{\sigma}_{\hat{\beta}}$} & mean $\hat{\beta}$ & \multicolumn{1}{c}{$\sigma_{\hat{\beta}}$} & (5) & (6) \\ 
-  \hline
-(Intercept) & 8.4E+00 & 1.3E-01 & 2.9E+00 & 1.5E+01 & 0.64 & 0.00 \\ 
-  Traffic Noise & -2.6E-03 & 1.6E-04 & -2.5E-03 & 3.0E-03 & 0.47 & 0.67 \\ 
-  House Size & 3.0E-04 & 2.7E-06 & 2.6E-04 & 9.1E-05 & 1.00 & 0.00 \\ 
-  Lot Size & 2.6E-01 & 1.5E-02 & 4.0E-01 & 3.7E-01 & 0.67 & 0.00 \\ 
-  Year Built & 1.2E-03 & 6.5E-05 & 4.5E-03 & 5.4E-03 & 0.79 & 0.00 \\ 
-  Owner Occupancy & 2.7E-02 & 3.2E-03 & 2.3E-02 & 6.4E-02 & 0.37 & 1.00 \\ 
-  Elem.\ Test Scores & 1.5E-03 & 1.2E-04 & 2.4E-04 & 3.1E-02 & 0.30 & 0.00 \\ 
-  Median Income & 3.3E-06 & 7.7E-08 & 9.6E-07 & 8.1E-06 & 0.35 & 0.00 \\ 
-  Dist.\ to CBD & 1.3E-05 & 6.3E-07 & 1.1E-05 & 1.0E-04 & 0.30 & 0.00 \\ 
-  Dist.\ to Park & -3.7E-07 & 1.1E-06 & -1.6E-05 & 1.3E-04 & 0.32 & 0.00 \\ 
-  Dist.\ to Lake & 2.5E-05 & 2.1E-06 & -2.8E-05 & 1.4E-04 & 0.35 & 0.00 \\ 
-  Dist.\ to Shop & -5.3E-06 & 1.3E-06 & 1.5E-05 & 8.8E-05 & 0.29 & 0.00 \\  
-  Location of Sale & \multicolumn{2}{c}{city fixed effects} & \multicolumn{4}{c}{\footnotesize city fixed effects and nearest 200 sales} \\
-  Timing of Sale & \multicolumn{2}{c}{year fixed effects} & \multicolumn{4}{c}{within last 12 months} \\
- \hline
-  GCV score & \multicolumn{2}{c}{0.041} & \multicolumn{2}{c}{0.027}  &  & \\
-  Moran's I statistic & \multicolumn{2}{c}{0.199} & \multicolumn{2}{c}{0.012} & & \\
-\end{tabular}
-}
- \caption*{\footnotesize Column (5) displays the proportion of $\hat{\beta}_{LWR}$ that can reject the null hypothesis of $\beta =0$.\\ Column (6) displays the proportion of Monte Carlo simulations with larger standard deviations of the LWR coefficients than $\sigma_{\hat{\beta}}$}
-\end{table}
-
-The first two columns of Table \ref{tab:mainresults} display the estimates and standard errors from a basic semi-log OLS regression with traffic noise, structural characteristics, location-based amenities, and both city and year of sale dummy variables.
-The third and fourth columns summarize the results of the LWR model when coefficients are estimated at each observation within the dataset using the nearest 200 house sales within the past 12 months.
-The third column presents the mean of these estimates while the fourth column displays the standard deviation of the estimates to give a measure of variation in the estimates across the dataset.
-Most of the mean LWR coefficients, including traffic noise, are similar to the coefficients obtained with the global OLS model.
-However, the large standard deviations of the LWR coefficients suggest non-stationarity in the estimated coefficients with the more flexible model.
-We now try to determine the source of this variation.
-
-Column (5) in Table \ref{tab:mainresults} shows the percentage of the local regressions for which the coefficient's p-value is less than 0.1.
-All regressions contained statistically significant estimates of the impact of increased living space and a majority contained significant estimates for lot size and year of construction.
-Roughly half of the regressions estimated an impact of traffic noise statistically different from zero, while approximately one-third of the local regressions estimated statistically significant estimates of the locational variables (school test scores, census tract median income, distance to local amenities).
-The lack of statistical significance for many of the local regression coefficients could be due to multiple factors.
-First, because we are estimating local regressions with only the nearest 200 data points, rather than tens of thousands of sales as in the global model, we might be estimating the coefficients with less precision and are unable to differentiate the coefficients from zero.
-Alternatively, the coefficients themselves might vary, sometimes being close to zero and other times farther away.
-This variation might be due to random chance (after all, we have estimated tens of thousands of regressions), or it could be the result of true spatial non-stationarity on the part of the coefficients.
-
-We test three hypotheses regarding the spatially and temporally flexible model results.
-We have seen that the model allows us to substantially improve our prediction of the logged house sales prices in our study.
-Why?
-Is there spatial non-stationarity in the hedonic model?
-If so, does the spatial non-stationarity hold for all of the explanatory variables or just a subset?
-In particular, do we see spatial non-stationarity in the impact of traffic noise as suggested in previous research such as \citet{MarmolejoDuarteCarlos;GonzalezTamez2009}?
-We will also use these results to test the hypothesis of temporal stationarity in the hedonic function.
-In particular, is the impact of traffic noise different before and after the negative shock of the economic recession and associated collapse of the housing market?
-Lastly, we will examine our results for evidence of threshold effects of noise.
-
-\subsection{Does the Hedonic Function Vary over Space?}
-We believe the hedonic function varies significantly over space and the use of a LWR estimation procedure is an appropriate modeling strategy.
-Our conclusions are based on the results of two different Monte Carlo simulations with the data as described in \citet{Fotheringham2002}.
-In each simulation we re-sampled (without replacement) the location of each house in the study and then re-estimated the LWR model with the locationally ``shuffled'' data.
-In both cases the results strongly suggest spatial non-stationarity in the hedonic function.
-
-In the first simulation we estimated the LWR model using bandwidths ranging from the nearest 50 to 10,000 sales just as before, but with the spatially reshuffled data (so the nearest 50 observations in the simulations are not the same 50 observations in reality).
-In 100 consecutive simulations, the smallest Generalized Cross-Validation score was obtained at the largest bandwidth.
-The smallest of these GCV scores was 0.041, just as was the case with the global (non-LWR) model.
-In other words, after running thousands of regressions on the shuffled data, we never obtained model performance anywhere near the LWR model with our true locational data.
-This seems to be strong evidence that the increased ability to predict house prices with a local model is not due to chance and that there is spatial non-stationarity in the hedonic function.
-
-\subsection{Does the Implicit Price of Traffic Noise Change over Space?}
-In the previous simulation we found that the hedonic regression function indeed exhibits spatial non-stationarity.
-However, we have not yet established which variables have spatially varying coefficients.
-In the second simulation, we seek to explore which of the hedonic regression coefficients exhibit spatial non-stationarity.
-We repeat the Monte Carlo simulation described earlier, but only at the optimal bandwidth from the original LWR model.
-We collected the standard deviation of the estimated LWR coefficients for each variable in each iteration of the simulation.
-The intuition of this simulation is as follows: a variable might truly exert a spatially \emph{stationary} effect on house prices, but our estimates vary over space due to chance.
-If this is the case, by shuffling the location of our observations and rerunning the LWR model, we should see a similar dispersion in regression coefficients over space with the reshuffled data as with our actual data.
-However, if the coefficient exhibits true spatial \emph{non-stationarity}, it is unlikely that we will see such a large of a standard deviation in the coefficient estimates after having reshuffled the data (because now the houses for which a coefficient exerts a strong effect are probably no longer near each other).
-
-After 100 iterations of this second simulation, the minimum GCV score for these re-sampled LWR models is 0.060, substantially larger than all models (global and local) with the actual data.
-The fourth column in Table \ref{tab:mainresults} displays the standard deviations of the LWR regression coefficients obtained with our data.
-Column (6) displays the proportion of Monte Carlo simulations that yielded larger standard deviations of LWR coefficient estimates than those shown in column $\sigma_{\hat{\beta}}$.
-For most variables, we never obtained a larger standard deviation in the simulation than we obtained from the LWR model with the actual data.
-However, the values associated with the traffic noise and owner occupancy variables suggest that the variation in LWR coefficients in our data may have been due to random chance.
-These coefficients may in fact be stationary across the study area, while the other coefficients appear to be non-stationary.
-Future work may want to estimate a mixed-LWR model in which the coefficients on traffic noise and owner occupancy remain stationary while the other coefficients are allowed to vary over space.
-See \citet{Fotheringham2002} for a description of a mixed-LWR estimation algorithm.
-
-Figure \ref{fig:MCsds} visualizes the results of the second simulation.
-Each sub-figure displays the distribution of LWR coefficient standard deviations obtained from the 100 iterations of the Monte Carlo simulation and the standard deviation obtained with the actual data (in red).
-Note that it is the case that the standard deviations obtained with the actual data are typically substantially larger than those obtained in the simulation for most of the variables.
-However, the variation obtained in the traffic noise coefficients simulations is similar with our actual LWR results, suggesting that the spatial non-stationarity exhibited in this coefficient is likely due to chance and not true spatial non-stationarity in the effect of traffic noise on house prices.
-
-\begin{figure}
- \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{../graphs/MCsimResultsSDsClean}}
- \caption{Actual LWR Coefficient Standard Deviations \textcolor{red}{(red line)} vs.\ Distribution of Monte Carlo Simulation Standard Deviations by Variable.
-Figures in which the red line is to the right of the black distribution suggest spatial non-stationarity in effect of the variable on house prices in our study region.}\label{fig:MCsds}
-\end{figure}
-
-The results of these simulations suggest that spatial non-stationarity exists in the hedonic function and that LWR techniques are able to capture a significant portion of the non-stationarity.
-Using a bandwidth of the nearest 200 houses and a temporal lag of 12 months not only yielded significantly smaller GCV scores compared to other bandwidths and model specifications, but such performance does not seem to be a result of a chance spatial arrangement of the data.
-However, contrary to previous work, these simulations show no evidence for spatial variation in the effect of traffic noise on house prices.
-
-\subsection{Does the Implicit Price of Traffic Noise Change over Time?}
-
-Previous research has suggested that the impact of noise can change with time and economic conditions.
-For instance, \citet{Wilhelmsson2000} found that the traffic noise penalty to be stronger in the 1990s near Stockholm, Sweden compared to the 1980s.
-\citet{Cohen2009} also found the (airport) noise penalty to be larger in the early 2000s compared to the late 1990s in Atlanta, Georgia.
-We know that house prices in the United States fell dramatically during and after the Great Recession of 2008-09.
-We know less about the patterns of change in the hedonic price functions during and after the fall in house prices.
-\citet{Cho2011b} found evidence from hedonic analysis in Nashville, Tennessee,  that consumers' willingness to pay for environmental amenities (such as proximity to open space and water views) decreased during the recession as compared to the previous economic boom.
-
-In this section we look for evidence of temporal non-stationarity in the hedonic coefficient on traffic noise within our data.
-Specifically, we create two new variables, ``\texttt{months since September 2008}'' and a dummy variable ``\texttt{post}=1'' for all sales after September 2008.
-We then regress our LWR noise coefficients on these two variables and their interaction term as shown in equation \eqref{eq:LWRinteraction},
-\begin{equation}\label{eq:LWRinteraction}
-\hat{\beta}_{LWR} = \alpha _0 + \alpha _1 \texttt{*Months since Sep. 2008} + \alpha _2  \texttt{*Post} + \alpha _3 \texttt{*Post*Months since Sep. 2008} + \epsilon.
-\end{equation}
-The results of this regression will help us understand the patterns of change in the implicit price of traffic noise.
-In particular, $\alpha_1 \neq 0$ suggests a linear temporal trend in the marginal willingness to pay to avoid traffic noise, while $\alpha_2 \neq 0$ suggests that there was a structural break after September 2008, and $\alpha_3 \neq 0$ will imply a change in the temporal trend after September 2008.
-The linear regression results presented in Table \ref{tab:betaMAX} show that there the estimated LWR coefficients for traffic noise are significantly smaller after September 2008.
-\begin{table}
-\caption{Dependent Variable = Traffic Noise LWR Coefficients}\label{tab:betaMAX}
-\begin{center}
-\begin{tabular}{lrrr}
-           & Estimate & Std.\ Err. & t-stat  \\  \hline
-(Intercept) & -1.7e-03 &  4.1e-05 &  -43.4   \\
-Months since Sep 2008       & 6.9e-06 &  2.0e-06  &   3.5    \\
-Post        &-8.0e-04 &  7.2e-05  & -11.1    \\
-Post*Months since Sep 2008  &-8.9e-05 &  4.5e-06  & -19.7    \\ \hline
-\multicolumn{4}{l}{Residual standard error: 0.003} \\
-\multicolumn{4}{l}{N = 31,748, R$^2$: 0.093} \\ %,  Adjusted R$^2$: 0.093
-%\multicolumn{4}{l}{Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1}
-\end{tabular}
-\end{center}
-\end{table}
-
-The results in Table \ref{tab:betaMAX} contradict the expectation that environmental amenities will ``matter'' less during and after the Great Recession compared to the housing boom.
-In fact, these results suggest that the penalty for homes exposed to higher levels of traffic noise became more severe.
-That is, the negative hedonic coefficients on traffic noise got more negative after September 2008.
-
-\subsection{Are There Threshold Effects of Traffic Noise?}
-
-Some researchers conclude that the semi-elasticity of noise varies with the level of noise \citep{Andersson2010, MarmolejoDuarteCarlos;GonzalezTamez2009, Theebe2004a, Miedema2001, Wilhelmsson2000}, such as a ``threshold''' effect at 70dB \citep{Wilhelmsson2000, Cohen2009}.
-Other researchers report no evidence of varying impacts at higher or lower noise intensities \citep{Blanco2011, Baranzini2010, Kim2007, Huang;Palmquist2001}.
-In this section we compare our mean LWR noise coefficient estimates across noise levels to look for threshold effects of traffic noise.
-
-\begin{table}
-\begin{center}
-\caption{LWR Noise Coefficients vs.\ Noise Levels}\label{tab:LWRnonlinear}
-\begin{tabular}{lrrr}
-         &   Estimate & Std.\ Err. & t-value \\ \hline
-(Intercept) & -1.8e-03 & 1.3e-04  &-13.3 \\
-Noise       & -2.8e-06 & 2.3e-06  & -1.2 \\  
-Post        & -3.6e-03 & 2.2e-04  &-16.2 \\
-Noise*Post  &  3.4e-05 & 4.0e-06  &  8.5 \\ \hline
-\multicolumn{4}{l}{Residual standard error: 0.003} \\
-\multicolumn{4}{l}{N: 31,748, R$^2$: 0.083} \\
-%F-statistic: 961.4 on 3 and 31744 DF,  p-value: < 2.2e-16 
-\end{tabular}
-\end{center}
-\end{table}
-
-Table \ref{tab:LWRnonlinear} reports the results of a simple linear regression of the LWR noise coefficients on the noise levels and whether or not the sale took place before or after September 2008 (as well as their interaction).
-The table reveals no statistically measurable linear relationship between the noise coefficient and the noise level for sales before September 2008.
-That is, the semi-elasticity is no different in our data at low levels of noise than at high levels of noise.
-The positive and significant interaction term suggests that the impact may be different for high vs.\ low levels of noise post-September 2008, but the difference in the predicted marginal effects is so small that it works about to be a roughly \$25 difference for a \$300,000 house at 50 vs.\ 75 dB.
-Thus, while other researchers report finding impact thresholds at 70dB, we cannot corroborate such findings with our data.
-
-Figure \ref{fig:betaMAXvCat} visually displays the estimated relationship between the level of traffic noise, time, and the estimated LWR traffic noise coefficients.
-We categorize the traffic noise data in 5 dB wide bins like \citet{Theebe2004a} and then estimate the mean LWR traffic noise coefficients in each category while also controlling for whether the sales took place pre- or post-September 2008.
-We see little to suggest any meaningful non-linearities in the regression coefficients of traffic noise on house prices, once we have controlled for the timing of the sales.
-
-\begin{figure}
-\makebox[\textwidth][c]{\includegraphics[width = 1.1\textwidth]{../graphs/LWRbetaMAXbyCatTime}}
-\caption{The mean LWR traffic noise coefficient by 5 decibel category and pre- vs.\ post-September 2008.
-The vertical lines denote the standard error of the estimated mean by time and level category.
-Note that over 99 percent of our data have Noise levels between 35 and 80 dB and no houses were sold post-September 2008 with noise levels above 85 dB.}\label{fig:betaMAXvCat}
-\end{figure}
-
-\section{Discussion}\label{Discussion}
-
-The hedonic analysis results presented suggest that traffic noise exhibits a significant negative effect on house prices and that the hedonic function varies over space and time.
-These results and analysis rest on important assumptions, which if violated, may change the results.
-This section describes two assumptions that we think are most noteworthy of discussion: lack of omitted variable bias and temporal non-stationarity in the level of several variables across the region during our study period.
-
-Our previously reported results lack some important control variables in the hedonic function.
-To the extent that structural variables like the number of bedrooms, bathrooms, garage size, or construction quality co-vary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias.
-We are comforted, however, because we do have some of these important additional variables for a subset of our data.
-We obtained the number of bedrooms, bathrooms, and garage area for our houses located within Dakota County from the Dakota County Assessor's Office.
-Our LWR analysis (Models 1, 2, and 3 described earlier) was repeated on this geographic subset of the data and the results were compared to the estimates obtained from the same analysis when these additional structural variables were omitted.
-We found strikingly similar estimates of the impact of traffic noise suggesting that our results may be robust to the omission of these variables from our analysis.
-
-\begin{table}
-\begin{center}
-\caption{Noise Coefficient Estimates in Dakota County with and without Additional Structural Variables}\label{tab:Dak}
-\begin{tabular}{lll}
- & \multicolumn{2}{p{1.25in}}{Additional Variables Included in LWR?} \\
-Locally Weighted Regression Model & \multicolumn{1}{c}{no} & \multicolumn{1}{c}{yes} \\ \cline{1-3}
-\multirow{2}{*}{Model (1) = Structural Variables} & -0.0015 & -0.0015 \\ 
-   & (0.0023) & (0.0031)  \\[.2cm]
-\multirow{2}{*}{Model (2) = Model (1) + Locational Variables} & -0.0014 & -0.0014  \\ 
-   & (0.0018) & (0.0022)  \\[.2cm] 
-\multirow{2}{*}{Model (3) = Model (2) + City Fixed Effects} & -0.0014 & -0.0014 \\ 
-   & (0.0022) & (0.0018) \\[.2cm] \cline{1-3}
-\multicolumn{3}{p{4.25in}}{Mean and (standard deviation) LWR traffic noise coefficients when the number of bedrooms, bathrooms, and garage size are included as additional control variables in the regression.}
-\end{tabular}
-\end{center}
-\end{table}
-
-Table \ref{tab:Dak} shows that the traffic noise coefficients estimated by our LWR models are similar regardless of whether the additional structural variables were included or not.
-Welch two-sample t-tests fail to reject the null hypothesis of zero mean differences across our three models (comparing LWR estimates with vs.\ without the additional structural variables included in the model).
-Paired t-tests find differences for Model 2 and 3, but the estimated differences are zero to four decimal places and in one case the noise impact estimates with the additional variables are slightly larger and in the other case they are slightly smaller.
-We also conducted simple linear regressions of the noise coefficients without the additional structural variables on the noise coefficients obtained with the additional structural variables for each of our three models.
-In all cases the model intercept estimates were close zero, the slopes almost exactly equal to one, and $R^2$ values over 0.7.
-These results suggest the hedonic coefficients for traffic noise are unaffected by omitted variable bias from common structural variables.
-While we cannot confirm that this lack of omitted variable bias also occurs elsewhere in our data, the results from Dakota County are promising.
-
-The timing of our independent variable collection is also a potential weakness.
-While our house sales data are collected over the course of six years, some of our other variables were collected at specific points in time and assumed to be constant over the study period.
-In particular, the traffic noise estimates are for the year 2007.
-To the extent that traffic flows and composition significantly changed over time, our traffic noise variables may be inaccurate for those other time periods.
-For instance, the US Department of Transportation reports that total vehicle miles traveled decreased by up to 4 percent year-on-year during the Great Recession.\footnote{\url{http://www.fhwa.dot.gov/ohim/tvtw/08dectvt}} Thus, our noise estimates may be inaccurate for later time periods and this may bias our estimates of the impact of noise on house values.
-Future work may seek to create time-series noise data in order to obtain even better estimates of the impact of traffic noise over time.
-Given the computational complexity of re-estimating the landscape noise surface, such work is beyond the scope of this paper.
-
-\section{Conclusion}
-We estimated the impact of traffic noise on housing prices using Locally Weighted Regression techniques in the St.\ Paul, Minnesota, urban area.
-Specifically, we estimate semi-logarithmic regressions at each house within our dataset using only information contained in ``local'' (both geographically and temporally) house sales.
-We find strong evidence that the hedonic function in our study area varies over space and time and such flexible models represent significant improvements over conventional parametric models.
-
-Monte Carlo simulations suggest that the better goodness-of-fit provided by the local models are not due to chance and that many hedonic implicit prices vary over space within our study area.
-When the location of our data was randomly assigned and our LWR model was re-estimated across more than a dozen different bandwidths, in 100 consecutive simulations the smallest GCV score was obtained when the data were analyzed at a pooled/global level rather than local.
-That is, after trying thousands of different combinations of varying levels of local analysis with the spatially redistributed data, we never came close to estimating our observed housing sales prices as well as we can with the local analysis on the actual data.
-Additionally, re-estimating the LWR model using a local bandwidth of 200 nearest house sales but randomly assigned locations yielded substantially smaller standard deviations for the majority of our regression coefficients.
-Such differences suggest that the variation exhibited by most of our regression coefficients was not due to simple random chance, but instead is consistent with spatial non-stationarity.
-
-Contrary to the previous results presented by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} and \citet{Theebe2004a}, we find little evidence to suggest that the impact of traffic noise varies geographically or by the level of noise within our study area.
-The traffic noise coefficient was one of only two variables with regression coefficient standard deviations smaller than or similar to the simulated distributions obtained from Monte Carlo experiments.
-We do, however, find significant temporal variation in the impact of traffic noise in our data.
-The estimated impact of one additional decibel of traffic noise is a 0.19 percent reduction in the sale price of houses before September 2008, vs.\ 0.37 percent after September 2008.
-Lastly, after controlling for the Great Recession, we find no significant differences in the impact of traffic noise across the range of commonly seen noise levels (50-70 dB).
-
-Precise estimates of the impact of traffic noise are important for efficient implementation of noise mitigation projects.
-The US Federal Highway Administration reports that 47 states have constructed noise barriers to reduce noise propagation, spending over a half a billion dollars from 2008-2010 \citepalias{USFHA2012}.
-\citet{Delucchi1998} used an estimate of 0.85 percent reduction in house prices per additional decibel in their cost-benefit analysis of traffic noise.
-While their preferred estimate of the total damage cost to the United States in 1991 is \$3 billion, they report a possible range of less than \$100 million to over \$40 billion due in part to uncertainty surrounding the degree of noise propagation over space in the urban built environment and the effect of noise on house prices.
-Indeed, one of the main conclusions of their work is that more research should be done to better understand the impact of noise on house prices and that better noise data are needed for such work to occur.
-
-Future research should be conducted in more housing markets, as the potential to apply the results of analysis in one set of geographical and economic circumstances may be limited.
-Second, ``mixed'' regression techniques (in which some regression coefficients are constrained to remain constant across the study area while others are allowed to vary) may allow researchers to obtain more precise estimates of the impact of hedonic characteristics by increasing the degrees of freedom in the regression.
-Future work may also seek to re-estimate traffic noise models over time to better account for changes in traffic flows associated with macroeconomic conditions.
-Lastly, researchers should take advantage of the recent suggestions in \citet{Carruthers2010} and use the spatial variation in regression coefficients obtained from LWR models to estimate the second-stage hedonic regressions to identify consumer demand curves for these characteristics.
-
-\newpage
-\begin{singlespace}
-\bibliographystyle{plainnat}
-\bibliography{NoiseBibliography}
-\end{singlespace}
 \end{document}
-
-% \begin{table}
-% \caption{Data Description}\label{tab:descriptive}
-% \begin{tabular}{lp{3in}r}
-% Variable & Description  & Expected Hedonic Impact \\ \
-% 
-% Sale Price &   Price of most recent sale  (in \$) & \\
-% 
-% Home Size	& Area of finished space in the home (in square feet)	& (+) \\
-% Lot Size	& Area of land house sits on (in acres)	& (+) \\
-% Year Built & Year home was constructed &	(+) \\
-% Owner	Occupancy & Does the owner occupy the house? (0 or 1) &	(+) \\
-% 
-% Traffic Noise	& Maximum decibel level of traffic noise (dB) measured within parcel &	(-) \\
-% MCA 3  & Average 3rd grade Minnesota Comprehensive Assessment (MCA) score for local elementary school &	(+) \\
-% Median Income	& Median household income (in dollars) for 2010 Census tract &	(+) \\
-% Dist. to CBD &	Distance (in meters) to nearest central business district	& (-) \\
-% Dist. to shop &	Distance (in meters) to nearest major shopping center	& (+)/(-) \\
-% Dist. to lake &	Distance (in meters) to nearest public lake	& (-) \\
-% Dist. to park	& Distance (in meters) to nearest public park	& (-) \\
-% City &	City a parcel resides in	& (+)/(-) \\ \hline
-% \multicolumn{3}{l}{Total number of house sales between 2005 and 2010 (n = 42,095) }
-% \end{tabular}
-% \end{table}

### 2014-06-11 analysis/03DakotaLWR/LWRscriptDakota.R
moving some files around for revised analysis

@@ -1,0 +1,54 @@
+# The goal of this script is to run a basic LWR model using the St. Paul working data...
+
+# What working directory will it be in?
+# Try to put it in an "LWR" folder inside analysis.
+# Remember to save the data to "Data/R2GIS"
+require(foreign)
+require(multicore, quietly = TRUE)
+require(fields, quietly = TRUE)
+
+# the following command loads up some functions we'll use
+source("helper/LWRfunctions.R")
+
+# BEDS + BATH + GARSQFT + get added or subtracted to compare the LWR model results with and without structural variables
+
+MYMODELS = c("logSALE_VA~Air_Mean+BEDS + BATH + GARSQFT +FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+HOME_STYLE+OWNOCC+factor(TimePeriod)",
+             "logSALE_VA~Air_Mean+BEDS + BATH + GARSQFT +FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+HOME_STYLE+OWNOCC+PercWhite+PercU18+MED_INCOME+MCA3+LAKE_dist+PARK_dist+SHOP_dist+CBD_dist+factor(TimePeriod)",
+             "logSALE_VA~Air_Mean+BEDS + BATH + GARSQFT +FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+HOME_STYLE+OWNOCC+PercWhite+PercU18+MED_INCOME+MCA3+LAKE_dist+PARK_dist+SHOP_dist+CBD_dist+factor(TimePeriod)+CITY")
+MYMODELsmall = "logSALE_VA~Air_Mean+BEDS + BATH + GARSQFT +FIN_SQ_FT+ACRES_POLY+YEAR_BUILT+HOME_STYLE+OWNOCC+factor(TimePeriod)"
+KVECTOR = c(25, 50, 75, 100, 150, 200, 400, 600, 800, 1000, 1500, 2000)
+
+filePrefix = "../Data/R2GIS/CleanData/"
+#   inputFile = "Sales20052010.dbf"
+#   DATAFRAME = read.dbf(paste0(filePrefix, inputFile))
+#   dakOBS = which(DATAFRAME$COUNTY_ID == "037" & DATAFRAME$BEDS > 0 &  DATAFRAME$BATH > 0 & DATAFRAME$GARSQFT>0 )
+#   dakDATA = DATAFRAME[dakOBS, ]
[…]

### 2014-06-11 analysis/06Dakota/MAXcoeffsPlotter.R

@@ -1,44 +1,44 @@
-# GOAL: compare LWR MAX coefficients across Dakota County under alternative specifications
+# GOAL: compare LWR Noise coefficients across Dakota County under alternative specifications
 
 # Load all the .RData files for Dakota County
-# Grab the MAX coefficients for the optimal bandwith in the given model output
-# plot the Max coefficients for the three paired specifications (with beds/baths/garagesqft vs. without)
+# Grab the Noise coefficients for the optimal bandwith in the given model output
+# plot the Noise coefficients for the three paired specifications (with beds/baths/garagesqft vs. without)
 
-setwd("~/Noise Hedonic Project/Noise-Hedonic/analysis/06Dakota/") #assume I'm in the project default working directory "Noise Hedonic Project"
+setwd("~/NoiseHedonicProject/Noise-Hedonic/analysis/06Dakota/") #assume I'm in the project default working directory "Noise Hedonic Project"
 require(foreign)
 source("../../helper/LWRfunctions.R")
 
-DATAFRAME = read.dbf("~/Noise Hedonic Project/Data/R2GIS/CleanData/Sales20052010.dbf")
-obs2run = which(DATAFRAME$COUNTY_ID == "037" & DATAFRAME$BATH>.8 & DATAFRAME$TimePeriod>11)
+DATAFRAME = read.dbf("~/NoiseHedonicProject/Data/R2GIS/CleanData/Sales20052010.dbf")
+obs2run = which(DATAFRAME$COUNTY_ID == "037" & DATAFRAME$BEDS > 0 &  DATAFRAME$BATH > 0 & DATAFRAME$GARSQFT>0 & DATAFRAME$TimePeriod>11)
 
-#dataPath = "../Data/R2GIS/CleanData/"
-filelist = list.files()
-files2open = filelist[which(substr(filelist, 1, 6) == "Dakota")]
+dataPath = "../../../Data/R2GIS/CleanData/Dakota/"
+filelist = list.files(dataPath)
[…]

### 2014-06-11 analysis/06Dakota/gcvFiguresAcrossModelsDakota.R

@@ -13,21 +13,21 @@ require(foreign)
 source("../../helper/LWRfunctions.R")
 
 DATAFRAME = read.dbf("~/NoiseHedonicProject/Data/R2GIS/CleanData/Sales20052010.dbf")
-obs2run = which(DATAFRAME$COUNTY_ID == "037" & DATAFRAME$BATH>.8 & DATAFRAME$TimePeriod>11)
+obs2run = which(DATAFRAME$COUNTY_ID == "037" & DATAFRAME$BEDS > 0 &  DATAFRAME$BATH > 0 & DATAFRAME$GARSQFT>0 & DATAFRAME$TimePeriod>11)
 
-#dataPath = "../Data/R2GIS/CleanData/"
-filelist = list.files()
-files2open = filelist[which(substr(filelist, 1, 6) == "Dakota")]
+dataPath = "../../../Data/R2GIS/CleanData/Dakota/"
+filelist = list.files(dataPath)
+files2open = filelist[which(substr(filelist, 1, 9) == "dakotaLWR")]
 # mymat = c()
 pdf("GCVplotsAll.pdf")
 for (myFile in 1:length(files2open)) {
-  load(files2open[myFile])
-  if (dim(output[[1]])[1] == 9140) gcvs = GCV(output$leverages, output$yhats, DATAFRAME$logSALE_VA[obs2run])
+  load(paste0(dataPath, files2open[myFile]))
+  if (dim(output[[1]])[1] == 8751) gcvs = GCV(output$leverages, output$yhats, DATAFRAME$logSALE_VA[obs2run])
   ks = as.numeric(substr(colnames(output[[1]]), 2, 5))
   plot(ks, gcvs, type = "l", main = "")
   title(MYMODEL, cex.main = .5)
   title(paste0("N = ", dim(output[[1]])[1]), line = .5)
-  title(paste("data: ", substr(files2open[myFile], 22, nchar(files2open[myFile]))), line = -1)
+  title(paste("data: ", substr(files2open[myFile], 16, nchar(files2open[myFile])-6)), line = -1)
   lmreg = lm(MYMODEL, data = DATAFRAME[obs2run, ])
   levs = lm.influence(lmreg, do.coef = FALSE)$hat
   globalGCV = GCV(cbind(levs), cbind(lmreg$fitted.values), DATAFRAME$logSALE_VA[obs2run])

### 2014-06-11 analysis/SandboxAaron/aaronSandbox.R

@@ -1,65 +1,88 @@
-# Run a Monte Carlo experiment to see whether coefficients really vary over space
+
+
+# goal is to export the results of our LWR model to eventually create some maps in ArcMAP...
+
+# 1 - open the appropriate R data file
+load("~/NoiseHedonicProject/Data/R2GIS/CleanData/TimeLag12months/Sales20052010LWRmodelAirMean3-2014-03-19.RData")
+
+# 2 - select the appropriate variables to export 
+# remember the structure of "output" is a list of the 279 things we calculated...
+# > names(output)
+# [1] "beta.(Intercept)"             "beta.Air_Mean"                "beta.FIN_SQ_FT"              
+# [4] "beta.ACRES_POLY"              "beta.YEAR_BUILT"              "beta.HOME_STYLE1-1/4 STRY"      
+# [16] "beta.OWNOCC"                  "beta.PercWhite"               "beta.PercU18"                
+# [19] "beta.MED_INCOME"              "beta.MCA3"                    "beta.LAKE_dist"              
+# [22] "beta.PARK_dist"               "beta.SHOP_dist"               "beta.CBD_dist"  
+# [139] "ses.(Intercept)"              "ses.Air_Mean"                 "ses.FIN_SQ_FT"               
+# [142] "ses.ACRES_POLY"               "ses.YEAR_BUILT"               "ses.HOME_STYLE1-1/4 STRY"    
+# [154] "ses.OWNOCC"                   "ses.PercWhite"                "ses.PercU18"                 
+# [157] "ses.MED_INCOME"               "ses.MCA3"                     "ses.LAKE_dist"               
+# [160] "ses.PARK_dist"                "ses.SHOP_dist"                "ses.CBD_dist" 
+
+data2xport = data.frame(output$beta.Air_Mean[,"k650"])
+names(data2xport) = "bnoise"
+data2xport$bfinsqft = output$beta.FIN_SQ_FT[,"k650"]
+data2xport$bacres = output$beta.ACRES_POLY[,"k650"]
+data2xport$senoise = output$ses.Air_Mean[, "k650"]
+data2xport$sefinsqft = output$ses.FIN_SQ_FT[,"k650"]
+data2xport$seacres = output$ses.ACRES_POLY[,"k650"]
[…]

### 2014-06-11 reports/NoiseHedonicRaR.Rnw

--- 2013-10-15 reports/Draft.Rnw
@@
 \documentclass{article}
+
 \usepackage[round]{natbib}
@@
 \usepackage{caption, amsmath, graphicx, setspace, multirow, color, hyperref, array}
-
+\usepackage[modulo]{lineno}
 %\renewcommand{\efloatseparator}{\mbox{}}
@@
 \date{}
+\author{}%Aaron Swoboda, Tsegaye Nega and Maxwell Timm}
 
@@
 Additionally, we estimate the impact on single family home transactions throughout the St.\ Paul, Minnesota, urban area using spatially explicit local regression techniques to allow for spatial non-stationarity in the hedonic function.
-Contrary to previous work, we find no evidence that the effect of traffic noise varies significantly across the several hundred square miles of our study region, nor by traffic noise levels.
-We do find significant differences in the impact of traffic noise before and after the economic recession of 2008-09.
-Our results suggest that an increase in traffic noise of one decibel decreases house prices by an average of 0.19 percent before September 2008 and an average of 0.37 percent after September 2008.
 \end{abstract}
@@
 \pagenumbering{arabic}
+
+\linenumbers
 
@@
 Instead of focusing on the impact of automobile traffic noise, hedonic work in the United States has tended to concentrate on noise from airports \citep{Espey2000, McMillen2004, Cohen2008a} or indirect measures of traffic noise, such as proximity to highways \citep{Matthews2007, Chernobai2009, Li2012}, or traffic counts \citep{HughesJr.1992, Larsen2012}.
-One exception is \citet{Cheng2008}, which finds that an additional decibel of traffic noise reduced house prices in Louisville, Tennessee, by 0.34 percent during the year 2007.
+One exception is \citet{Cheng2008}, who estimated that year 2007 housing prices in Louisville, Tennessee were, on avarege, 0.34 percent lower for each additional decibel of traffic noise.
 However, the generalizability of this research is limited given that it is based on less than a thousand house transactions in just one city.
@@
 
-In this paper, we estimate the relationship between traffic noise and single family house prices across 44 cities and several hundred square miles in the St.\ Paul, Minnesota, urban region by taking advantage of a uniquely detailed set of noise estimates.
+In this paper, we estimate a hedonic relationship between traffic noise and single family house prices across 44 cities and several hundred square miles in the St.\ Paul, Minnesota, urban region by taking advantage of a uniquely detailed set of noise estimates.
 The data represent perhaps the most accurate regional noise estimates ever used in the hedonic literature in the United States to date due to the high spatial resolution of the estimates (10 m x 10 m) and the incorporation of the effects of nearby buildings and land cover on noise propagation.
@@
 Such Locally Weighted Regression (LWR) models have become increasingly common in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than other common spatial econometric models under common real world circumstances \citep{McMillen2012}.
-Thus, in addition to using new data that reduces the measurement error of the impact of traffic noise, the spatial and temporal variation in our data and hedonic modeling allow us to present the first estimates in the United States of how the impact of traffic noise varies over space, time, and by noise level.
+Thus, in addition to using new data that reduces the measurement error of the impact of traffic noise, the spatial and temporal variation in our data and hedonic modeling allow us to present the first estimates in the United States of how the marginal effect of traffic noise varies over space and time.
+
+What do we think now?
 

### 2014-06-23 reports/Draft.Rnw
added names to title
june 2014 revisions - draft to Tsegaye

@@
 \begin{tabular}{lrrrrrrr}
-
  & min & 25\% & 50\% & mean & 75\% & max & st.\ dev.\ \\ 
   \hline
-  Sale Price (\$1,000s) & 98.8 & 195.0 & 241.0 & 265.5 & 314.9 & 675.0 & 102.8 \\ 
-  House Size (square feet) & 390 & 1158 & 1628 & 1750 & 2188 & 4000 & 704 \\ 
+% latex table generated in R 2.15.2 by xtable 1.7-0 package
+% Tue Jun 10 21:29:25 2014
+Sale Price (\$ 1,000s) & 99 & 195 & 241 & 266 & 315 & 675 & 103 \\ 
+  House Size (square feet) & 390 & 1158 & 1628 & 1750 & 2189 & 4000 & 704 \\ 
   Lot Size (acres) & 0.02 & 0.17 & 0.25 & 0.25 & 0.31 & 0.60 & 0.11 \\ 
-  Owner Occupancy (no = 0, yes = 1) & 0.0 & 1.0 & 1.0 & 0.8 & 1.0 & 1.0 & 0.4 \\ 
-  Year of House Construction & 1850 & 1950 & 1973 & 1967 & 1993 & 2010 & 32 \\ 
-  Traffic Noise (dB) & 25.1 & 50.5 & 55.3 & 56.4 & 62.2 & 91.5 & 8.8 \\ 
-  Median Income in Census Tract (\$1,000s) & 13.9 & 54.6 & 69.1 & 72.6 & 89.7 & 143.3 & 23.6 \\ 
-  Average 3rd Grade Standardized Test Scores & 335.6 & 359.8 & 365.4 & 364.5 & 370.4 & 551.7 & 10.6 \\ 
+  Year House was Built & 1850 & 1950 & 1973 & 1967 & 1993 & 2010 & 32 \\ 
+  Owner Occupancy (Yes = 1, No = 0) & 0.0 & 1.0 & 1.0 & 0.8 & 1.0 & 1.0 & 0.4 \\ 
+  Traffic Noise (dB) & 24.5 & 49.0 & 54.0 & 54.3 & 59.5 & 81.6 & 7.5 \\ 
   Distance to Central Business District (km) & 1.1 & 6.8 & 13.2 & 14.7 & 21.8 & 37.1 & 8.9 \\ 
@@
   Distance to nearest Shopping Center (km) & 0.0 & 0.9 & 1.5 & 1.9 & 2.3 & 10.8 & 1.6 \\ 
+  Percent of Census Block Population Race = White & 0 & 80 & 90 & 85 & 96 & 100 & 17 \\ 
+  Percent of Census Block Population Under Age 18 & 0 & 21 & 27 & 27 & 33 & 67 & 9 \\ 
+  Median Income in Census Tract (\$ 1,000s) & 14 & 55 & 69 & 73 & 90 & 143 & 24 \\ 
+  Elementary Test Scores & 336 & 360 & 365 & 364 & 370 & 552 & 11 \\ 
    \hline

### 2014-06-23 reports/NoiseHedonicRaR.Rnw
june 2014 revisions - draft to Tsegaye

@@
 \usepackage[round]{natbib}
+\usepackage{dcolumn}
 \usepackage[nolists]{endfloat}
@@
 
-Work from Europe suggests that the relationship between traffic noise and house prices varies across housing submarkets \citep{Day2007, MarmolejoDuarteCarlos;GonzalezTamez2009}, by level of traffic noise \citep{Theebe2004a, Brandt2011}, and over time \cite{Wilhelmsson2000}.
-As such, we construct a flexible hedonic model that allows for a non-stationary relationship between house prices and our explanatory variables over geography and time.
+We construct a flexible hedonic model that allows for a non-stationary relationship between house prices and our explanatory variables over geography and time.
 Such Locally Weighted Regression (LWR) models have become increasingly common in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than other common spatial econometric models under common real world circumstances \citep{McMillen2012}.
@@
 
-What do we think now?
-
-We find that while the impact of other important control variables in the hedonic function vary significantly over space, the impact of traffic noise does not.
-Such results are contradictory to recent work by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} which found evidence of a spatially non-stationary relationship between traffic noise and housing prices using a LWR model in Barcelona, Spain.
+We find strong evidence to support hedonic modeling choices that allow for spatial and temporal heterogeneity.
 Our paper also presents the first estimates of the implicit price of traffic noise after the housing market collapse and economic recession of 2008-09.
-Contrary to work such as \citet{Cho2011b}, which found that environmental amenities mattered \emph{less} after the housing crash, our estimated effect of traffic noise mattered \emph{almost twice as much more} after the recession (0.19 percent reduction in house prices per additional decibel beforehand compared to 0.37 percent per decibel afterwards).
+Contrary to work such as \citet{Cho2011b}, which found that environmental amenities mattered \emph{less} after the housing crash, our estimated noise coefficients roughly double in magnitude after the recession compared to before.
 We conclude with a discussion of how future research can expand and improve upon this work.
@@
 \small
-\begin{tabular}{lrrrrrrr}
+\begin{tabular}{lD{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}}
 
- & min & 25\% & 50\% & mean & 75\% & max & st.\ dev.\ \\ 
+ & min & 25\% & 50\% & mean & 75\% & max & st dev \\ 
   \hline
-  Sale Price (\$1,000s) & 98.8 & 195.0 & 241.0 & 265.5 & 314.9 & 675.0 & 102.8 \\ 
-  House Size (square feet) & 390 & 1158 & 1628 & 1750 & 2188 & 4000 & 704 \\ 
+% latex table generated in R 2.15.2 by xtable 1.7-0 package
+% Tue Jun 10 21:29:25 2014
+Sale Price (\$1,000s) & 99 & 195 & 241 & 266 & 315 & 675 & 103 \\ 
+  Year House was Built & 1850 & 1950 & 1973 & 1967 & 1993 & 2010 & 32 \\ 
+  House Size (square feet) & 390 & 1158 & 1628 & 1750 & 2189 & 4000 & 704 \\ 
   Lot Size (acres) & 0.02 & 0.17 & 0.25 & 0.25 & 0.31 & 0.60 & 0.11 \\ 
-  Owner Occupancy (no = 0, yes = 1) & 0.0 & 1.0 & 1.0 & 0.8 & 1.0 & 1.0 & 0.4 \\ 
-  Year of House Construction & 1850 & 1950 & 1973 & 1967 & 1993 & 2010 & 32 \\ 
-  Traffic Noise (dB) & 25.1 & 50.5 & 55.3 & 56.4 & 62.2 & 91.5 & 8.8 \\ 
-  Median Income in Census Tract (\$1,000s) & 13.9 & 54.6 & 69.1 & 72.6 & 89.7 & 143.3 & 23.6 \\ 
-  Average 3rd Grade Standardized Test Scores & 335.6 & 359.8 & 365.4 & 364.5 & 370.4 & 551.7 & 10.6 \\ 
+  Owner Occupancy (Yes = 1, No = 0) & 0.0 & 1.0 & 1.0 & 0.8 & 1.0 & 1.0 & 0.4 \\ 
+  Traffic Noise (dB) & 24.5 & 49.0 & 54.0 & 54.3 & 59.5 & 81.6 & 7.5 \\ 
   Distance to Central Business District (km) & 1.1 & 6.8 & 13.2 & 14.7 & 21.8 & 37.1 & 8.9 \\ 
@@
   Distance to nearest Shopping Center (km) & 0.0 & 0.9 & 1.5 & 1.9 & 2.3 & 10.8 & 1.6 \\ 
+  Percent of Census Block Population Race = White & 0 & 80 & 90 & 85 & 96 & 100 & 17 \\ 
+  Percent of Census Block Population Under Age 18 & 0 & 21 & 27 & 27 & 33 & 67 & 9 \\ 
+  Median Income in Census Tract (\$1,000s) & 14 & 55 & 69 & 73 & 90 & 143 & 24 \\ 
+  Elementary Test Scores & 336 & 360 & 365 & 364 & 370 & 552 & 11 \\ 
    \hline
@@
 \makebox[\linewidth][c]{
-\begin{tabular}{l|rrrrrrrrrrr}
+\begin{tabular}{l|rrrrrrrrrrrrr}
  & \multicolumn{1}{x{.35in}}{Price} & \multicolumn{1}{x{.38in}}{House} & \multicolumn{1}{x{.35in}}{Lot} & 
- \multicolumn{1}{x{.35in}}{Built} & \multicolumn{1}{x{.35in}}{Noise} & \multicolumn{1}{x{.35in}}{Inc.} & 
- \multicolumn{1}{x{.35in}}{Test} & \multicolumn{1}{x{.35in}}{CBD} & \multicolumn{1}{x{.35in}}{Park} & \multicolumn{1}{x{.35in}}{Lake} & \multicolumn{1}{x{.35in}}{Shop} \tabularnewline 
+ \multicolumn{1}{x{.35in}}{Built} & \multicolumn{1}{x{.35in}}{Noise} & \multicolumn{1}{x{.35in}}{CBD} & \multicolumn{1}{x{.35in}}{Park} & \multicolumn{1}{x{.35in}}{Lake} & \multicolumn{1}{x{.35in}}{Shop} & \multicolumn{1}{x{.35in}}{White} &
+ \multicolumn{1}{x{.35in}}{U18} & \multicolumn{1}{x{.35in}}{Inc.} & 
+ \multicolumn{1}{x{.35in}}{Test} \tabularnewline 
   \hline
-Sale Price & 1 &  &  &  &  &  &  &  &  &  &  \tabularnewline 
-  House Size & 0.74 & 1 &  &  &  &  &  &  &  &  &  \tabularnewline
-  Lot Size & 0.38 & 0.45 & 1 &  &  &  &  &  &  &  &  \tabularnewline
-  Year Built & 0.45 & 0.52 & 0.47 & 1 &  &  &  &  &  &  &  \tabularnewline
-  Noise & -0.13 & -0.07 & 0.00 & -0.19 & 1 &  &  &  &  &  &  \tabularnewline
-  Income & 0.52 & 0.50 & 0.41 & 0.57 & -0.18 & 1 &  &  &  &  &  \tabularnewline
-  Elem.\ Test Scores & 0.29 & 0.28 & 0.29 & 0.34 & -0.04 & 0.44 & 1 &  &  &  &  \tabularnewline 
-  Distance to CBD & 0.31 & 0.45 & 0.43 & 0.58 & -0.04 & 0.53 & 0.35 & 1 &  &  &  \tabularnewline
-  Distance to Park & 0.25 & 0.28 & 0.22 & 0.42 & -0.13 & 0.38 & 0.22 & 0.57 & 1 &  &  \tabularnewline
-  Distance to Lake & -0.04 & -0.10 & -0.25 & -0.17 & -0.03 & -0.12 & -0.10 & -0.09 & 0.20 & 1 &  \tabularnewline
-  Distance to Shop & 0.27 & 0.27 & 0.15 & 0.37 & -0.19 & 0.36 & 0.18 & 0.46 & 0.38 & 0.15 & 1 \tabularnewline
+Sale Price & 1 &  &  &  &  &  &  &  &  &  &  &  &  \tabularnewline
+House Size & 0.74 & 1 &  &  &  &  &  &  &  &  &  &  &  \tabularnewline
+Lot Size  & 0.38 & 0.45 & 1 &  &  &  &  &  &  &  &  &  &  \tabularnewline
+Year Built  & 0.45 & 0.52 & 0.47 & 1 &  &  &  &  &  &  &  &  &  \tabularnewline
+Noise & -0.24 & -0.12 & -0.04 & -0.25 & 1 &  &  &  &  &  &  &  &  \tabularnewline
+Distance to CBD  & 0.31 & 0.45 & 0.43 & 0.58 & -0.09 & 1 &  &  &  &  &  &  &  \tabularnewline
+Distance to Park  & 0.25 & 0.28 & 0.22 & 0.42 & -0.17 & 0.57 & 1 &  &  &  &  &  &  \tabularnewline
+Distance to Lake & -0.04 & -0.10 & -0.25 & -0.17 & -0.01 & -0.09 & 0.20 & 1 &  &  &  &  &  \tabularnewline
+Distance to Shop  & 0.27 & 0.27 & 0.15 & 0.37 & -0.24 & 0.46 & 0.38 & 0.15 & 1 &  &  &  &  \tabularnewline
+Percent White & 0.24 & 0.15 & 0.25 & 0.15 & -0.09 & 0.34 & 0.16 & -0.14 & 0.14 & 1 &  &  &  \tabularnewline
+Percent Under 18 & 0.26 & 0.30 & 0.11 & 0.36 & -0.19 & 0.29 & 0.32 & 0.09 & 0.32 & -0.22 & 1 &  &  \\ 
+Income & 0.52 & 0.50 & 0.41 & 0.57 & -0.24 & 0.53 & 0.38 & -0.12 & 0.36 & 0.35 & 0.32 & 1 &  \tabularnewline
+Elem.\ Test Scores & 0.29 & 0.28 & 0.29 & 0.34 & -0.09 & 0.35 & 0.22 & -0.10 & 0.18 & 0.31 & 0.10 & 0.44 & 1 \tabularnewline 
 \end{tabular} }
@@
 To determine the relationship between real estate price and road traffic noise levels, we first created a traffic noise exposure surface by calculating the propagation of traffic noise over the landscape using the FHWA (Federal Highway Authority) 1978 standard \citep{Barry1978}.
-Following \citet{Barry1978}, the traffic noise level at any given location on the landscape is given by:
+The entire methodology has already been explained in detail in (CITE two NEGA PAPERS) What follows is a summary.
+The modeling of traffic noise has three key components: choosing the mathematical function for noise propagation, assembling the input data, and assessing the accuracy of the model prediction.
+These will be briefly discussed.
+Because it is currently used by the state of Minnesota, we used the FHWA 1978 standard model for calculating the noise level.
+According to this standard, the noise level at any given location on the landscape can be expressed:
 \begin{eqnarray}\label{eq:noise}
@@
 
-To calculate the traffic noise map for the region using the above model, several data sources were used.
+We used several data sources as inputs in the study.
 A 2007 road centerline and the associated traffic characteristics (volume and proportion of trucks and vehicles) for the region were obtained from the Minnesota Department of Transportation (MNDoT).
-We converted the posted speed of each road into a GIS layer.
-For all roads without recorded traffic volume (i.e., residential), we assigned 100 vehicles/day as a minimum estimate.
-This estimate was based on factors identified in the literature as important for estimating traffic volume, such as census data on commuting population, tract area, the size of a standard street block, and road type \citep{Cheng1992, Fricker1986}.\footnote{In order to assess the sensitivity of our results to our estimate of traffic volume for local roads, we also ran the model using 200 and 300 vehicles/day for one county.
-With the exception of a few areas in the rural part of the county, there was less than 0.05 dBA difference at 30 m from the road centerline.}
+We converted the posted speed of each road segment into a GIS layer.
+We used three data sources for the shielding adjustment: buildings, foliage, and noise barriers.
+We extracted the perimeter and height of 818,500 buildings using a combination of LiDAR data and aerial photography.
+Foliage shielding is accounted by extracting forest polygons that are at least 10 m high and have an area $\geq 10,000 m^2$ from a 2005 land use and 2001 National Land Cover Data.
+We obtained a noise barrier layer from the MNDoT that contains the locations, width, and height of each noise barriers to account for its shielding effect.
 
-Data on traffic volume and the proportion of trucks and vehicles on each segment of the road were averaged over a 24-hour period, making it impossible to account for a day and night time variation in traffic noise.
-Following \citet{Arditi2007}, we divided the total traffic volume into day and nighttime periods by assuming that 80 percent of vehicles and 65 percent of trucks are driven during the daytime (6am -- 10pm) and 35 percent of trucks and 20 percent of vehicles are driven during the nighttime (10pm--6am).
-Values for ground absorption were chosen by assuming that all road surfaces consisted of impervious bitumen.
-For computational simplicity, we created the road surface gradient by re-sampling US Geological Survey 30 m resolution Digital Elevation Model (DEM) to 100 m resolution.
+We used the SoundPlanTM noise modeling software to implement equation\ref{eq:noise}.
+Predicted noise output is calculated at a grid resolution of 10 m$^2$.
+We conducted a preliminary validation of the model output by comparing it with observed noise levels, which were sampled at 134 locations along a major highway.
+The relationship between the mean observed and predicted noise levels was linear and moderately strong with a correlation of 0.76.
 
-We used three data sources for the shielding adjustment: buildings, foliage, and noise barriers.
-We extracted the perimeter and height of 818,500 buildings using aerial photography and LiDAR data.
-For the areas where LiDAR data are available, we used LiDAR Analyst$^{TM}$ software to extract buildings’ footprints.
-For the areas of the region where only aerial photos are available, we used Feature Analyst$^{TM}$ software to extract building footprints.
-For measurements extracted using aerial photography, height was determined using a combination of parcel data and field measurements.
+In order to incorporate noise produced by aircraft into the overall noise exposure, we obtained the aircraft noise contour lines of the region from the Twin Cities Metropolitan Airports Commission.
+The contour line noise values coincident with the traffic noise surface then were added following rules of logarithmic addition.
+For example, adding 52 dBA from aircraft contour line into the noise surface where the noise value is 51 yields 53.5 dBA.
 
-The locations chosen for the traffic noise levels were the 818,500 buildings in the entire urban area.
-Thus, we used the perimeter and height of these buildings to account for the shielding effect of buildings.
-To account for foliage shielding (and to make the computation manageable), we assumed that only forest patches that are at least 10 m high and have an area greater than 10,000 m$^2$ will have a significant effect on noise attenuation.
-Accordingly, we extracted forest polygons with these characteristics using a combination of year 2005 land use data and 2001 National Land Cover Data (NLCD).
-To account for noise barrier shielding, we used a noise barrier layer obtained from MNDoT, which contains the locations, width, and height of noise barriers in the region.
-
-We used the SoundPlan$^{TM}$ noise modeling software to implement the model given by Equation~\eqref{eq:noise}.
-Predicted traffic noise output is calculated at a grid resolution of 10 m$^2$.\footnote{We conducted a preliminary validation of the model output by comparing it with observed noise levels at 134 locations that were sampled along major highways.
-For each location, two readings were taken very close to the highway, one between 9am and 10am and another between 1pm and 2pm.
-The noise level for each location is then determined by averaging the two observed values, and this average is then compared with the predicted noise level.
-The relationship between the mean observed and predicted noise levels is linear and moderately strong with a correlation of 0.76.
-It is not surprising that the relationship is not stronger given the size and complexity of the model.
-In particular, the traffic volume data that we used for modeling traffic noise propagation is a 24-hour average, which requires more time-interval sampling per location than just the two used in the validation.
-Still, this preliminary comparison serves as a good indicator of how well this model captures traffic noise levels.} Once the noise surface for the entire region was developed, we extracted the noise surface for the present study area by overlaying the housing parcel boundaries and calculating the maximum noise level within the parcel.
+A map of our noise surface can be seen in Figure~???
+Once the noise surface for the entire region was developed, we extracted the noise surface for the present study area by overlaying the housing parcel boundaries and calculating the mean noise level within the parcel.
 
@@
 For instance, using GIS software we are able to calculate the Euclidean distance to numerous points of interest within the dataset, such as the nearest central business district, shopping centers, parks, and lakes.
-Additionally, a variable denoting the median household income for the surrounding census tract is created through the use of TIGER shapefiles from the 2010 Census Bureau and data from the 2010 American Community Survey.
+Additionally, three demographic variables denoting the median household income for the surrounding census tract, the percentage of the population that identified their race as ``white'', and the percentage of the population that is under the age of 18 were created through the use of TIGER shapefiles from the 2010 Census Bureau and data from the 2010 American Community Survey.
 Lastly, we associate each transaction with its elementary school and include the average 3rd grade Minnesota Comprehensive Assessment (MCA) score for the local elementary school during the year of purchase.\footnote{Test scores were obtained from the Minnesota Department of Education website.
@@
 \subsection{Time}
-Given that we have data from before and after the recession of 2008-09, we subset the data in Table \ref{tab:SumStatsTime} by year of sale to look for differences over time.
-In addition to the noticeable decline in nominal sales values, there is also a drop in the number of sales across years.
-For example, in 2010 there were only 4,206 property sales within the dataset, less than half as many in 2005.
-While the mean sale price declined from roughly \$280,000 pre-crash to \$230,000 post-crash, most of the structural and neighborhood variables are relatively consistent across years.
-However, traffic noise displays a noticeable difference in the pre- and post-crash market transactions (the mean drops from over 58 dB to less than 53 dB).
+We have sales transactions across six years (from 2005 to 2010) for our study area.
+Such temporal variation will allow us to estimate the hedonic price function over time and test for differences before, during, and after the economic recession.
+Table \ref{tab:SumStatsTime} displays the mean variable values by year of sale to look for differences over time.
+The mean sale price in 2009 (roughly \$230,000) is almost 20 percent lower than the mean sale price in 2006 (roughly \$280,000) and the number of sales transactions in 2009-10 is less than the number of transactions in 2005.
+However, most other variables have small or no differences across time.
+Additionally, univariate density plots of the variables over time also reveal no differences in the shape or spread of the distributions over time.\footnote{See Appendix A} For instance, it is not the case that after the recession the distribution ``hollowed out'' in the middle and became bimodal with many high- and low-priced houses selling with few mid-priced homes selling.
+Additionally, maps of the locations of sales transactions over time reveal no discernable patterns, either.
+The geographic dispersion of sales in earlier years look surprisingly similar to those in later years.
+Thus, we can find no evidence of only certain types or locations of houses transacting in later years compared to earlier years in our data.
 
 \begin{table}
-\begin{center}
 \caption{Mean Variable Values by Year}\label{tab:SumStatsTime}
-\small
-%\includegraphics[width = \textwidth]{../graphs/DescriptiveStatsByYear}
-% Table generated by Excel2LaTeX from sheet 'Descriptive StatisticsYear'
-    \begin{tabular}{lrrrrrr|r}
-    Variable & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2005-10\\ \hline
-    Sales Value (\$1000s) & 279   & 282   & 275   & 263   & 231   & 233   & 266 \\
-    Traffic Noise (dB) & 58.5  & 58.6  & 58.6  & 52.5  & 52.8  & 52.8  & 56.4 \\
-    House Size (ft$^2$) & 1737  & 1736  & 1743  & 1813  & 1727  & 1775  & 1750 \\
+\makebox[\textwidth][c]{
+\scriptsize
+  \centering
+    \begin{tabular}{lD{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}|D{.}{.}{1}}
+    \\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+    & \multicolumn{6}{c}{Year of House Sale} & \\
+    Variable & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & \multicolumn{1}{r}{All Years}\\ \hline
+Sale Price (\$1,000s) & 279 & 282 & 275 & 262 & 231 & 233 & 266 \\ 
+  Year House was Built & 1967 & 1966 & 1966 & 1971 & 1968 & 1968 & 1967 \\ 
+  House Size (feet$^2$) & 1737 & 1736 & 1743 & 1813 & 1727 & 1775 & 1750 \\ 
   Lot Size (acres) & 0.25 & 0.25 & 0.25 & 0.26 & 0.25 & 0.26 & 0.25 \\ 
-    Year Built  & 1967  & 1966  & 1966  & 1971  & 1968  & 1968  & 1967 \\
-    Median Income (\$1000s) & 72.0  & 72.1  & 72.3  & 74.8  & 72.6  & 73.2  & 72.6 \\
-    Elem. Test Scores & 364.8 & 364.8 & 365.2 & 363.5 & 362.3 & 366.1 & 364.5 \\
-    Dist.\ to CBD (km) & 14.7  & 14.6  & 14.8  & 15.0  & 14.3  & 14.5  & 14.7 \\
-    Dist.\ to Park (km) & 2.6   & 2.6   & 2.6   & 2.8   & 2.6   & 2.6   & 2.6 \\
-    Dist.\ to Lake (km) & 0.9   & 0.9   & 0.9   & 0.9   & 0.9   & 0.9   & 0.9 \\
-    Dist.\ to Shop (km) & 1.9   & 1.9   & 1.8   & 2.0   & 1.9   & 1.9   & 1.9 \\ \hline
-    Number of Observations &  10,991  & 8,885  &  6,549  & 5,503  &  5,961  & 4,206  & 42,095  \\
+  Owner Occ (Y = 1, N = 0) & 0.87 & 0.87 & 0.92 & 0.86 & 0.60 & 0.77 & 0.83 \\ 
+  Traffic Noise (dB) & 54.4 & 54.5 & 54.6 & 53.7 & 54.0 & 54.0 & 54.3 \\ 
+  Dist CBD (km) & 14.7 & 14.6 & 14.8 & 15.0 & 14.3 & 14.5 & 14.7 \\ 
+  Dist to  Park (km) & 2.6 & 2.6 & 2.6 & 2.8 & 2.6 & 2.6 & 2.6 \\ 
+  Dist to Lake (km) & 0.9 & 0.9 & 0.9 & 0.9 & 0.9 & 0.9 & 0.9 \\ 
+  Dist to  Shop (km) & 1.9 & 1.9 & 1.8 & 2.0 & 1.9 & 1.9 & 1.9 \\ 
+  Percent Race = White & 84 & 84 & 85 & 86 & 85 & 86 & 85 \\ 
+  Percent Under Age 18 & 28 & 28 & 27 & 28 & 27 & 27 & 27 \\ 
+  Income (\$1,000s) & 72 & 72 & 72 & 75 & 73 & 73 & 73 \\ 
+  Elementary Test Scores & 365 & 365 & 365 & 364 & 362 & 366 & 364 \\  \hline
+  Number of Observations &  10,990  & 8,885  &  6,549  & 5,498  &  5,961  & 4,200  & 42,083  \\
     \end{tabular}%
-\end{center}
+}
 \end{table}
+
+[Map of sales prices over time about here]
 
@@
 \begin{table}
-\caption{Basic Regression Results (dependent variable = $ln(\textrm{Sale Price})$)}\label{tab:globalRegression}
-
-\makebox[\textwidth][c]{%\includegraphics[width = 1.3\textwidth]{../graphs/GlobalRegression}}
-% Table generated by Excel2LaTeX from sheet 'Sheet1'
+\caption{Basic Global Regression Results}\label{tab:globalRegression}
+\makebox[\textwidth][c]{
+\scriptsize
   \centering
-  \tabcolsep=0.03cm
-    \begin{tabular}{lclcclcclccl}
-   & (1)   &       &       & (2)   &       &       & Pre-Crash   &       &       & Post-Crash   &  \\ \hline
-\T  Traffic Noise & -2.02E-03 & *** &   & -2.00E-03 & ***   &   & -1.63E-03 & ***  & & -3.08E-03 & *** \\
-          & (1.32E-04) &   &   & (1.32E-04) &       &       & (1.38E-04) &       &       & (3.29E-04) &  \\
-\T  Intercept & 9.37E+00 & ***   & \hspace{.5cm} & 9.49E+00 & ***   & \hspace{.5cm}   & 8.55E+00 & ***   & \hspace{.5cm}   & 1.10E+01 & *** \\
-          & (9.48E-02) &    &   & (9.62E-02) &   &   & (1.11E-01) &       &       & (2.12E-01) &  \\
-\T   House Size & 3.38E-04 & ***   &   & 3.39E-04 & ***   &   & 3.35E-04 & ***   &   & 3.50E-04 & *** \\
-          & (1.85E-06) &   &   & (1.86E-06) &       &       & (1.99E-06) &       &       & (4.26E-06) &  \\
-\T  Lot Size & 1.42E-01 & ***   &    & 2.74E-01 & ***   &   & 2.31E-01 & ***   &      & 2.74E-01 & *** \\
-          & (1.14E-02) &     &   & (2.12E-02) &     &      & (2.29E-02) &       &       & (4.99E-02) &  \\
-\T  Owner Occupancy & 3.22E-02 & ***   &   & 3.23E-02 & ***   &     & 3.38E-02 & ***  & & 2.61E-02 & *** \\
-          & (2.80E-03) &  &   & (2.79E-03) &       &       & (3.24E-03) &       &       & (6.41E-03) &  \\
-\T  Year Built & 7.82E-04 & ***   &   & 7.17E-04 & ***   &    & 9.68E-04 & ***   &   & 2.15E-06 &  \\
-          & (4.57E-05) &       &       & (4.65E-05) &   &   & (5.06E-05) &    &   & (1.05E-04) &  \\
-\T  Median Income & 3.03E-06 & ***  & & 3.31E-06 & ***  &   & 2.86E-06 & ***   &       & 4.06E-06 & *** \\
-          & (5.87E-08) &       &       & (5.87E-08) &   &   & (6.56E-08) &       &       & (1.35E-07) &  \\
-\T  Elem. Test Scores & 1.88E-03 & *** &   & 1.81E-03 & ***   &   & 3.11E-03 & *** & & 1.21E-03 & *** \\
-          & (1.06E-04) &  &   & (1.06E-04) &   &       & (1.75E-04) &       &       & (1.55E-04) &  \\
-\T  Distance to CBD & -1.56E-06 & ***  &  & 7.46E-07 & *     &  & -1.57E-07 &   &       & 1.40E-06 &  \\
-          & (1.97E-07) &       &       & (3.70E-07) &       &       & (3.95E-07) &   &   & (8.98E-07) &  \\
-\T  Distance to Park & -2.38E-07 &   &    & -5.48E-07 &    &   & -6.37E-07 &  &   & -4.01E-07 &  \\
-          & (6.82E-07) & &   & (6.83E-07) &       &       & (7.33E-07) &       &       & (1.58E-06) &  \\
-\T  Distance to Lake & 2.12E-05 & ***   &   & 2.36E-05 & ***   &   & 2.22E-05 & ***   & & 2.79E-05 & *** \\
-          & (1.68E-06) &       &    & (1.71E-06) &   &    & (1.83E-06) & &  & (4.03E-06) &  \\
-\T  Distance to Shop & 3.01E-06 & ***   &    & 3.12E-06 & ***   & & 4.16E-06 & ***   &    & 1.88E-06 &  \\
-          & (7.67E-07) &       &       & (7.66E-07) &       &       & (8.17E-07) &  & & (1.82E-06) &  \\
-\T  Lot Size * Distance to CBD &  &   & & -8.81E-06 & *** & & -6.66E-06 & ***   &       & -9.55E-06 & ** \\
-          &   &   &   & (1.19E-06) &       &       & (1.27E-06) &       &       & (2.94E-06) &  \\
-\T  County Fixed Effects & yes   &   &   & yes   &       &       & yes   &       &       & yes   &  \\
-    Year of Sale Fixed Effects & yes   &   &   & yes   &   &       & yes   &       &       & yes   &  \\
-    Month of Sale Fixed Effects & yes   &   &   & yes   &   &       & yes   &       &       & yes   &  \\ \hline
-\T  Number of Observations &        42,095  &   &  &    42,095  & & &   31,253  & & &    10,842  &  \\
-    R$^2$   & 0.696 &       &       & 0.696 &       &       & 0.714 &       &       & 0.613 &  \\
- \multicolumn{12}{l}{(standard errors) ***$p<.001$; **$p<.01$; *$p<.05$}  \\
-    \end{tabular}%
+\begin{tabular}{@{\extracolsep{-1pt}}lD{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} D{.}{.}{-4} } 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable: ln Sale Price}} \\ 
+\cline{2-5} \\[-1.8ex] 
+& \multicolumn{1}{r}{Model (A)} & \multicolumn{1}{r}{Model (B)} & \multicolumn{1}{r}{Model (C)} & \multicolumn{1}{r}{Model (D)}\\ 
+& \multicolumn{1}{r}{All Years} & \multicolumn{1}{r}{Year=2006} & \multicolumn{1}{r}{Year=2008} & \multicolumn{1}{r}{Year=2010}\\
+\hline \\[-1.8ex] 
+Noise (dB) & -0.0027^{***} & -0.0020^{***} & -0.0033^{***} & -0.0040^{***} \\ 
+  & (0.0001) & (0.0003) & (0.0005) & (0.0006) \\ 
+  & & & & \\ 
+ House Size (1,000s ft$^2$) & 0.2914^{***} & 0.2847^{***} & 0.2810^{***} & 0.3066^{***} \\ 
+  & (0.0022) & (0.0043) & (0.0067) & (0.0084) \\ 
+  & & & & \\ 
+ Lot Size (acres) & 0.2493^{***} & 0.2719^{***} & 0.2799^{***} & 0.2135^{***} \\ 
+  & (0.0118) & (0.0221) & (0.0359) & (0.0447) \\ 
+  & & & & \\ 
+ Owner Occupancy Dummy & 0.0222^{***} & -0.0027 & 0.0478^{***} & 0.0298^{***} \\ 
+  & (0.0026) & (0.0050) & (0.0085) & (0.0097) \\ 
+  & & & & \\ 
+ Year House Built & 0.0020^{***} & 0.0025^{***} & 0.0018^{***} & 0.0011^{***} \\ 
+  & (0.0001) & (0.0001) & (0.0002) & (0.0002) \\ 
+  & & & & \\ 
+ Percent Under 18 & -0.0001 & 0.00002 & -0.0002 & -0.0006 \\ 
+  & (0.0001) & (0.0002) & (0.0004) & (0.0005) \\ 
+  & & & & \\ 
+ Percent White & 0.0037^{***} & 0.0031^{***} & 0.0040^{***} & 0.0040^{***} \\ 
+  & (0.0001) & (0.0001) & (0.0002) & (0.0003) \\ 
+  & & & & \\ 
+ Median Income (\$1,000s) & 0.0023^{***} & 0.0021^{***} & 0.0023^{***} & 0.0029^{***} \\ 
+  & (0.0001) & (0.0001) & (0.0002) & (0.0003) \\ 
+  & & & & \\ 
+ Elementary Test Scores & 0.0009^{***} & 0.0023^{***} & 0.0040^{***} & 0.0001 \\ 
+  & (0.0001) & (0.0003) & (0.0005) & (0.0002) \\ 
+  & & & & \\ 
+ Dist to CBD (km) & 0.0078^{***} & 0.0083^{***} & 0.0053^{***} & 0.0101^{***} \\ 
+  & (0.0005) & (0.0010) & (0.0016) & (0.0020) \\ 
+  & & & & \\ 
+ Dist to Lake (km) & 0.0230^{***} & 0.0246^{***} & 0.0021 & 0.0343^{***} \\ 
+  & (0.0017) & (0.0032) & (0.0054) & (0.0067) \\ 
+  & & & & \\ 
+ Dist to Park (km) & 0.0014 & -0.0027 & 0.0099^{***} & 0.0064^{*} \\ 
+  & (0.0009) & (0.0017) & (0.0027) & (0.0034) \\ 
+  & & & & \\ 
+ Dist to Shop (km) & -0.0019^{*} & -0.0020 & -0.0063^{*} & -0.0020 \\ 
+  & (0.0010) & (0.0019) & (0.0033) & (0.0041) \\ 
+  & & & & \\ 
+\hline \\[-1.8ex] 
+Home Style Fixed Effects & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} \\ 
+Month*Year Fixed Effects & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} \\ 
+City Fixed Effects & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} \\ 
+\hline \\[-1.8ex] 
+Observations & \multicolumn{1}{c}{42,083} & \multicolumn{1}{c}{8,885} & \multicolumn{1}{c}{5,498} & \multicolumn{1}{c}{4,200} \\ 
+R$^{2}$ & \multicolumn{1}{c}{0.742} & \multicolumn{1}{c}{0.785} & \multicolumn{1}{c}{0.691} & \multicolumn{1}{c}{0.668} \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
 }
@@
 
-Column (1) in Table \ref{tab:globalRegression} displays the results of our basic regression model.
-All coefficients but one are significantly different from zero at conventional significance levels.
-The traffic noise coefficient suggests that a one decibel increase traffic noise is on average associated with a 0.2 percent reduction in housing sales prices.
-Standard urban economic theory \citep{Alonso1964, Mills1967, Muth1969} predicts that the price of land will vary over space within our dataset to account for locational amenities.
-As such, the other columns include an interaction term between lot size and distance to the nearest central business district to account for spatial variation in the price of land.
-The significant coefficients on the lot size interaction terms suggest that the value of land varies over space.
-Other regressions (results available upon request) show similar variation in the implicit prices of house characteristics over space.
+Model (A) in Table \ref{tab:globalRegression} displays the results of a basic Ordinary Least Squares regression model.
+In addition to the important structural and neighborhood variables, we also include fixed effects for each city and month of sale in the dataset to allow for month-to-month shocks to prices.
+The traffic noise coefficient suggests houses in our data that are similar in all respects but a one decibel difference in noise will, on average, have sales prices roughly 0.27 percent lower at the noisier location.
 
-Table \ref{tab:globalRegression} also attempts to begin to understand how the economic recession may have influenced the hedonic function in our study area.
-The third and fourth columns estimate the same regression as (2) but subset the sales before and after September of 2008 (the month that Lehman Brothers filed for bankruptcy, the US Federal government took over Fannie Mae and Freddie Mac, and the American International Group (AIG) narrowly avoided bankruptcy only through a \$85 billion loan from the US Federal government).\footnote{\url{http://www.federalreserve.gov/newsevents/press/other/20080916a.htm}} The coefficients for some of the hedonic variables of interest (noise, schools, land, for instance) appear different across the two time periods.
+Further exploratory analysis suggests the assumption of temporal and geographic stationarity of the hedonic price function is overly restrictive and needs to be relaxed.
+We first tested for temporal changes in the coefficients for house size, lot size, and noise by creating interaction terms with these variables and the month*year year fixed effects.
+In all three cases the improved model fit was significantly more than expected due to random chance.\footnote{The results of specific hypothesis tests are available upon request.} Columns (B) - (D) of Table \ref{tab:globalRegression} show the results of restimating Model (A) using only sales within three separate years of data.
+Subsequent analysis also suggests that many of the important regression coefficients vary across the different cities within our data.
+We are able to reject the null hypothesis that the interaction terms between cities and important variables (house size, lot size, noise, etc.) are zero, even after limiting the analysis to only houses sold within a given year (for instance, by adding the interaction terms to model specifications (B) - (D)).\footnote{Results of specific F-tests are available upon request.}
 
-The results in Table \ref{tab:globalRegression} and previous work \citep[such as][]{Day2007, MarmolejoDuarteCarlos;GonzalezTamez2009} suggests that the relationship between prices and many other hedonic characteristics may vary over space.
-While methods exist for parameterizing this variation \citep[such as spatial expansion as suggested by][]{Casetti1972}, we have no a priori knowledge of how to parameterize the variation over space and time.
+These results should be taken with appropriate skepticism, as the models are simple Ordinary Least Squares regressions and the spatial and temporal nature of the data likely violate assumptions of the Classical Linear Regression Model.
+However, the initial findings seem to suggest that the relationship between house prices and many other hedonic characteristics may vary over space and time.
+While methods exist for parameterizing this variation \citep[such as spatial expansion as suggested by][]{Casetti1972}, we have no a priori knowledge of how to parameterize the variation.
 As such, we turn to a semi-parametric form of hedonic regression, a flexible modeling approach which lets the data reveal how relationships vary, rather than specifying them beforehand.
-Such a modeling choice will allow us to test the hypotheses of spatial and temporal stationarity in the regression model.
+Such a modeling choice will allow us to perform additional tests of the hypotheses of spatial and temporal stationarity in the regression model.
 
@@
 \end{equation} 
-where $y_i$ is the dependent variable value, $\hat{y}_i$ is the predicted dependent variable value for observation $i$, and $v_1$ is the ``effective number of model parameters.''
+where $y_i$ is the dependent variable value, $\hat{y}_i$ is the predicted dependent variable value for observation $i$, and $v_1$ is the ``effective number of model parameters.'' The value  
 $v_1=$tr(\textbf{S}), where the matrix \textbf{S} is the ``hat matrix'' which maps $y$ onto $\hat{y}$,
@@
 %\section{Results}
-Similar to the basic econometric model described in Section \ref{basicModel}, the LWR model estimates the logged sales price of a house as a function of structural variables, location and time.
-In order to account for changing market conditions in our data, when estimating LWR coefficients we use only houses sold within the past 12 months.
+Similar to the basic econometric model described in Section \ref{basicModel}, the LWR model estimates the logged sales price of a house as a function of structural and neighborhood variables, location and time.
+In order to account for changing market conditions in our data as manifested in regression coefficients that vary over time, when estimating LWR coefficients we use only houses sold within the past 12 months and also include month fixed effects to account for seasonality.
 Thus, the coefficient estimates at a particular house are estimated using data from other sales nearby in both time and geography.
@@
 \subsection{Improved Model Performance}
-The use of the Locally Weighted Regression model significantly increases model performance.
-Figure \ref{fig:GCVmodel} displays the Generalized Cross Validation score for three different model specifications with varying number of observations included in the regression bandwidth.
-Two important conclusions can be drawn from the results.
-First, local analysis (bandwidths of a couple hundred observations) perform significantly better than global models, and second, conditional on the bandwidth, performance improves with the inclusion of more locational variables.
-The minimum GCV score is obtained using a bandwidth of 200 nearest houses and a model including structural, locational, and city fixed-effects.
+The use of the Locally Weighted Regression model significantly increases model performance as measured by the generalized cross validation score.
+Figure \ref{fig:GCVmodel} displays the Generalized Cross Validation score for three different model specifications estimated at the ``global'' level as well as with varying numbers of observations included in the regression bandwidth.
+We estimate three different hedonic function specifications with different levels of additional spatial control variables.
+Model (1) includes the noise variable, the basic structural characteristics (size of the house in square feet, size of the lot in acres, a categorical variable denoting the architectural style of the house, and whether or not the house is owner-occupied) plus month of sale*year fixed effects.
+Model (2) includes all of the str adds neighborhood and locational variables to the previously described model (test scores at the local elementary school, census tract median income, percent of the census block population that is white, percentage of the census block that is under age 18 and distances to the central business district, nearest park, nearest shopping center, and nearest lake).
+The third model adds city fixed effects to the second model.
+Thus Model (3) explicitly includes both common important characteristics of neighborhood quality while also allowing for spatial heterogeneity in the regression coefficients, and even city-level fixed effects to control for omitted variables that vary at the municipal level.
 
-We estimate three different models.
-Model (1) uses only the basic structural characteristics as the explanatory variables (size of the house in square feet, size of the lot in acres, a categorical variable denoting the architectural style of the house, and whether or not the house is owner-occupied).
-Model (2) adds locational variables to the previously described model (test scores at the local elementary school, census tract median income, and distances to the central business district, nearest park, nearest shopping center, and nearest lake).
-The third model adds city fixed effects.
-Generally speaking, the third model performs slightly better than the second model, which performs substantially better than the first model.
+Two important conclusions can be drawn from these results.
+Model (3) consistently outperforms the other two models-- slightly better than Model (2) and considerably better than Model (1).
+Thus, even conditional on having modeled the data with local regression, the inclusion of more neighborhood-level variables substantially improves the model fit.
+Second, local analyses perform significantly better than global models.
+The minimum GCV score is obtained using a bandwidth of 500 nearest houses and a model including structural, neighborhood, and locational variables in addition to time and city fixed-effects.
+
 \begin{figure}
@@
 Note that the LWR models all have significantly smaller GCV scores than the global models.
-The minimum GCV score is obtained by LWR Model (3) at a bandwidth of 200 nearest houses.}\label{fig:GCVmodel}
+The minimum GCV score is obtained by LWR Model (3) at a bandwidth of 500 nearest houses.}\label{fig:GCVmodel}
 \end{figure}
 
-We also estimate each of the three models at varying levels of local analysis, with bandwidths ranging from the nearest 50 observations to the nearest 10,000.
-Models with bandwidths of only a couple hundred observations have substantially smaller GCV scores, suggesting that, conditional on control variables included in the model, model performance still improves by performing the analysis at the local level.
-It is also worth noting that the LWR models have significantly lower GCV scores for a range of bandwidths when compared to the global models.
-These results suggest that it is important to model our data in a spatially explicit manner.
-
-Table \ref{tab:mainresults} displays a summary of the results of LWR Model (3) and a similar regression model run without allowing for spatial variation in the regression coefficients.
-Again, note that the LWR model yields a substantially smaller GCV score (0.027 vs.\ 0.041) signifying a substantial improvement in model performance.
+%Table \ref{tab:LWR} summarizes the results of LWR Model (3) at three different bandwidth sizes plus the same model estimated at the ``global'' level.
+run without allowing for spatial variation in the regression coefficients.
+Again, note that the LWR model yields a substantially smaller GCV score (0.027 vs.\ 0.038) signifying a substantial improvement in model performance.
 In addition to the significant reduction in the GCV score obtained with the use of LWR, we also see a substantial reduction in the degree of spatial autocorrelation in the model residuals.
@@
 
-% latex table generated in R 2.15.2 by xtable 1.7-0 package
-% Mon Jun 24 16:36:58 2013
+% Table created by stargazer v.5.1 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Sat, Jun 21, 2014 - 10:37:00 AM
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp]
+  \caption{LWR Results: Dependent Variable = ln(Sales Price)} 
+  \label{tab:LWR} 
+  \makebox[\textwidth][c]{
+\scriptsize
+  \centering
+\begin{tabular}{@{\extracolsep{-1pt}} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{-4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{-4} D{.}{.}{3} D{.}{.}{3} } 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex]
+ & \multicolumn{3}{c}{Nearest 500 sales$^*$} & \multicolumn{3}{c}{Nearest 650 sales} & \multicolumn{3}{c}{Nearest 1000 sales} \\
+ & \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$}  & 
+ \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$}  & 
+ \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$} \\
+ \cline{2-4} \cline{8-10} \cline{5-7}
+\multicolumn{1}{l}{Noise (dB)} & -0.0034 & -0.0064 & -0.0006 & -0.0034 & -0.0061 & -0.0009 & -0.0033 & -0.0057 & -0.0013 \\ 
+\multicolumn{1}{l}{House Size (1,000s ft)} & 0.2700 & 0.1800 & 0.3900 & 0.2700 & 0.1900 & 0.3900 & 0.2700 & 0.2000 & 0.4000 \\ 
+\multicolumn{1}{l}{Lot Size (acres)} & 0.4200 & 0.1700 & 0.7300 & 0.4200 & 0.1900 & 0.7100 & 0.4200 & 0.2100 & 0.6700 \\ 
+\multicolumn{1}{l}{Year House Built} & 0.0046 & 0.0004 & 0.0100 & 0.0045 & 0.0005 & 0.0096 & 0.0043 & 0.0005 & 0.0090 \\ 
+\multicolumn{1}{l}{Owner Occupancy} & 0.0230 & -0.0290 & 0.0800 & 0.0240 & -0.0240 & 0.0760 & 0.0230 & -0.0180 & 0.0680 \\ 
+\multicolumn{1}{l}{Percent White} & 0.0012 & -0.0003 & 0.0029 & 0.0013 & -0.0001 & 0.0028 & 0.0014 & 0.0001 & 0.0028 \\ 
+\multicolumn{1}{l}{Percent Under 18} & 0.0005 & -0.0016 & 0.0025 & 0.0004 & -0.0014 & 0.0022 & 0.0004 & -0.0011 & 0.0019 \\ 
+\multicolumn{1}{l}{Median Income (\$1,000s)} & 0.0007 & -0.0014 & 0.0033 & 0.0008 & -0.0010 & 0.0033 & 0.0010 & -0.0006 & 0.0037 \\ 
+\multicolumn{1}{l}{Elementary Test Scores} & 0.0000 & -0.0056 & 0.0055 & 0.0001 & -0.0050 & 0.0049 & 0.0003 & -0.0040 & 0.0042 \\ 
+\multicolumn{1}{l}{Dist to Lake (km)} & -0.0150 & -0.0910 & 0.0580 & -0.0110 & -0.0770 & 0.0550 & -0.0076 & -0.0630 & 0.0520 \\ 
+\multicolumn{1}{l}{Dist to Park (km)} & -0.0110 & -0.0600 & 0.0330 & -0.0110 & -0.0490 & 0.0250 & -0.0085 & -0.0370 & 0.0160 \\ 
+\multicolumn{1}{l}{Dist to Shop (km)} & 0.0092 & -0.0330 & 0.0520 & 0.0096 & -0.0270 & 0.0470 & 0.0100 & -0.0210 & 0.0440 \\ 
+\multicolumn{1}{l}{Dist to CBD (km)} & 0.0084 & -0.0190 & 0.0440 & 0.0094 & -0.0140 & 0.0400 & 0.0100 & -0.0099 & 0.0380 \\ 
+\hline \\[-1.8ex] 
+\multicolumn{10}{p{6 in}}{$^*$ A bandwidth of 500 implies that the nearest 500 houses sold within the past 12 months are included.} \\
+\multicolumn{10}{p{6 in}}{Note: Each model also includes a categorical variable for architectural style, month*year fixed effects, and city-level fixed effects. }
 
-\begin{table}[bp]
-\caption{Hedonic Regression Results (dependent variable = $ln(\textrm{Sale Price})$)} \label{tab:mainresults} 
-\makebox[\linewidth]{
-\small
-\begin{tabular}{lrrrrrr} \\
- & \multicolumn{2}{c}{Global Model} & \multicolumn{4}{c}{Locally Weighted Regression Model} \\
- & \multicolumn{1}{c}{$\hat{\beta}$} & \multicolumn{1}{c}{$\hat{\sigma}_{\hat{\beta}}$} & mean $\hat{\beta}$ & \multicolumn{1}{c}{$\sigma_{\hat{\beta}}$} & (5) & (6) \\ 
-  \hline
-(Intercept) & 8.4E+00 & 1.3E-01 & 2.9E+00 & 1.5E+01 & 0.64 & 0.00 \\ 
-  Traffic Noise & -2.6E-03 & 1.6E-04 & -2.5E-03 & 3.0E-03 & 0.47 & 0.67 \\ 
-  House Size & 3.0E-04 & 2.7E-06 & 2.6E-04 & 9.1E-05 & 1.00 & 0.00 \\ 
-  Lot Size & 2.6E-01 & 1.5E-02 & 4.0E-01 & 3.7E-01 & 0.67 & 0.00 \\ 
-  Year Built & 1.2E-03 & 6.5E-05 & 4.5E-03 & 5.4E-03 & 0.79 & 0.00 \\ 
-  Owner Occupancy & 2.7E-02 & 3.2E-03 & 2.3E-02 & 6.4E-02 & 0.37 & 1.00 \\ 
-  Elem.\ Test Scores & 1.5E-03 & 1.2E-04 & 2.4E-04 & 3.1E-02 & 0.30 & 0.00 \\ 
-  Median Income & 3.3E-06 & 7.7E-08 & 9.6E-07 & 8.1E-06 & 0.35 & 0.00 \\ 
-  Dist.\ to CBD & 1.3E-05 & 6.3E-07 & 1.1E-05 & 1.0E-04 & 0.30 & 0.00 \\ 
-  Dist.\ to Park & -3.7E-07 & 1.1E-06 & -1.6E-05 & 1.3E-04 & 0.32 & 0.00 \\ 
-  Dist.\ to Lake & 2.5E-05 & 2.1E-06 & -2.8E-05 & 1.4E-04 & 0.35 & 0.00 \\ 
-  Dist.\ to Shop & -5.3E-06 & 1.3E-06 & 1.5E-05 & 8.8E-05 & 0.29 & 0.00 \\  
-  Location of Sale & \multicolumn{2}{c}{city fixed effects} & \multicolumn{4}{c}{\footnotesize city fixed effects and nearest 200 sales} \\
-  Timing of Sale & \multicolumn{2}{c}{year fixed effects} & \multicolumn{4}{c}{within last 12 months} \\
- \hline
-  GCV score & \multicolumn{2}{c}{0.041} & \multicolumn{2}{c}{0.027}  &  & \\
-  Moran's I statistic & \multicolumn{2}{c}{0.199} & \multicolumn{2}{c}{0.012} & & \\
 \end{tabular} 
 }
- \caption*{\footnotesize Column (5) displays the proportion of $\hat{\beta}_{LWR}$ that can reject the null hypothesis of $\beta =0$.\\ Column (6) displays the proportion of Monte Carlo simulations with larger standard deviations of the LWR coefficients than $\sigma_{\hat{\beta}}$}
 \end{table}
 
-The first two columns of Table \ref{tab:mainresults} display the estimates and standard errors from a basic semi-log OLS regression with traffic noise, structural characteristics, location-based amenities, and both city and year of sale dummy variables.
-The third and fourth columns summarize the results of the LWR model when coefficients are estimated at each observation within the dataset using the nearest 200 house sales within the past 12 months.
-The third column presents the mean of these estimates while the fourth column displays the standard deviation of the estimates to give a measure of variation in the estimates across the dataset.
-Most of the mean LWR coefficients, including traffic noise, are similar to the coefficients obtained with the global OLS model.
-However, the large standard deviations of the LWR coefficients suggest non-stationarity in the estimated coefficients with the more flexible model.
-We now try to determine the source of this variation.
+Table~\ref{tab:LWR} shows the results for our LWR Model (3) with three different bandwidths: the GCV minimizing bandwidth of 500 nearest sales as well as two larger values, 650 and 1,000 nearest sales.
+For each bandwidth, we display the mean LWR coefficient as well as the 10$^{th}$ and 90$^{th}$ percentile values.
+The mean LWR coefficient for the noise variable is similar across the three different bandwidths (approximately a third of a percent difference in house sales prices for each additional decibel of noise, all other varibles held constant).
+Unsurprisingly, the spread of the coefficient distribution is greater for the smaller bandwidths.
+We now turn to investigating whether this increased dispersion appears from the stochastic nature of smaller sample sizes, or due to heterogeneity in the hedonic function.
 
-Column (5) in Table \ref{tab:mainresults} shows the percentage of the local regressions for which the coefficient's p-value is less than 0.1.
-All regressions contained statistically significant estimates of the impact of increased living space and a majority contained significant estimates for lot size and year of construction.
-Roughly half of the regressions estimated an impact of traffic noise statistically different from zero, while approximately one-third of the local regressions estimated statistically significant estimates of the locational variables (school test scores, census tract median income, distance to local amenities).
-The lack of statistical significance for many of the local regression coefficients could be due to multiple factors.
-First, because we are estimating local regressions with only the nearest 200 data points, rather than tens of thousands of sales as in the global model, we might be estimating the coefficients with less precision and are unable to differentiate the coefficients from zero.
-Alternatively, the coefficients themselves might vary, sometimes being close to zero and other times farther away.
-This variation might be due to random chance (after all, we have estimated tens of thousands of regressions), or it could be the result of true spatial non-stationarity on the part of the coefficients.
-
-We test three hypotheses regarding the spatially and temporally flexible model results.
-We have seen that the model allows us to substantially improve our prediction of the logged house sales prices in our study.
-Why?
-Is there spatial non-stationarity in the hedonic model?
-If so, does the spatial non-stationarity hold for all of the explanatory variables or just a subset?
-In particular, do we see spatial non-stationarity in the impact of traffic noise as suggested in previous research such as \citet{MarmolejoDuarteCarlos;GonzalezTamez2009}?
-We will also use these results to test the hypothesis of temporal stationarity in the hedonic function.
-In particular, is the impact of traffic noise different before and after the negative shock of the economic recession and associated collapse of the housing market?
-Lastly, we will examine our results for evidence of threshold effects of noise.
+We believe the hedonic function varies significantly over space and time and that the use of a LWR estimation procedure is an appropriate and beneficial modeling strategy.
+In the next three subsections we describe the results of hypothesis tests that lead us to these conclusions.
 
 \subsection{Does the Hedonic Function Vary over Space?}
-We believe the hedonic function varies significantly over space and the use of a LWR estimation procedure is an appropriate modeling strategy.
-Our conclusions are based on the results of two different Monte Carlo simulations with the data as described in \citet{Fotheringham2002}.
-In each simulation we re-sampled (without replacement) the location of each house in the study and then re-estimated the LWR model with the locationally ``shuffled'' data.
-In both cases the results strongly suggest spatial non-stationarity in the hedonic function.
 
-In the first simulation we estimated the LWR model using bandwidths ranging from the nearest 50 to 10,000 sales just as before, but with the spatially reshuffled data (so the nearest 50 observations in the simulations are not the same 50 observations in reality).
-In 100 consecutive simulations, the smallest Generalized Cross-Validation score was obtained at the largest bandwidth.
-The smallest of these GCV scores was 0.041, just as was the case with the global (non-LWR) model.
-In other words, after running thousands of regressions on the shuffled data, we never obtained model performance anywhere near the LWR model with our true locational data.
+We first conduct a Monte Carlo simulation recommended in \citet{Fotheringham2002} to see if the improved model fit with our LWR model was due to random chance.
+The intuition of the test is as follows - if the improved model fit isn't significant, then we should be able to see similar improvements in model fit by using the LWR model with the same houses but in a different spatial arrangement.
+Failing to recreate a spatial arrangement that yields a similar model fit as to that obtained with our actual data is then evidence that our spatial arrangement and the improved model fit obtained from a spatially heterogeneous model is significant.
+
+We conducted 100 different experiments in which we randomly swapped the locations of our house transactions.
+In each case we then estimated the LWR model using 10 different bandwidths ranging from the nearest 100 to 4,000 sales just as before and calculated the GCV score.
+Every single time the smallest Generalized Cross-Validation score was obtained at the largest bandwidth.
+That is, in 100 consecutive opportunities to fit our data at a local level of a couple hundred nearest sales up to a couple thousand nearby sales, the GCV score was always smallest for the largest possible bandwidth.
+In other words, after running a thousand different local regression models on the shuffled data, we never obtained model performance anywhere near the LWR model with our true locational data.
 This seems to be strong evidence that the increased ability to predict house prices with a local model is not due to chance and that there is spatial non-stationarity in the hedonic function.
@@
 \subsection{Does the Implicit Price of Traffic Noise Change over Space?}
-In the previous simulation we found that the hedonic regression function indeed exhibits spatial non-stationarity.
+In the previous simulation we found that the hedonic regression function seems to exhibit spatial non-stationarity.
 However, we have not yet established which variables have spatially varying coefficients.
 In the second simulation, we seek to explore which of the hedonic regression coefficients exhibit spatial non-stationarity.
-We repeat the Monte Carlo simulation described earlier, but only at the optimal bandwidth from the original LWR model.
-We collected the standard deviation of the estimated LWR coefficients for each variable in each iteration of the simulation.
-The intuition of this simulation is as follows: a variable might truly exert a spatially \emph{stationary} effect on house prices, but our estimates vary over space due to chance.
-If this is the case, by shuffling the location of our observations and rerunning the LWR model, we should see a similar dispersion in regression coefficients over space with the reshuffled data as with our actual data.
-However, if the coefficient exhibits true spatial \emph{non-stationarity}, it is unlikely that we will see such a large of a standard deviation in the coefficient estimates after having reshuffled the data (because now the houses for which a coefficient exerts a strong effect are probably no longer near each other).
 
-After 100 iterations of this second simulation, the minimum GCV score for these re-sampled LWR models is 0.060, substantially larger than all models (global and local) with the actual data.
-The fourth column in Table \ref{tab:mainresults} displays the standard deviations of the LWR regression coefficients obtained with our data.
-Column (6) displays the proportion of Monte Carlo simulations that yielded larger standard deviations of LWR coefficient estimates than those shown in column $\sigma_{\hat{\beta}}$.
-For most variables, we never obtained a larger standard deviation in the simulation than we obtained from the LWR model with the actual data.
-However, the values associated with the traffic noise and owner occupancy variables suggest that the variation in LWR coefficients in our data may have been due to random chance.
-These coefficients may in fact be stationary across the study area, while the other coefficients appear to be non-stationary.
-Future work may want to estimate a mixed-LWR model in which the coefficients on traffic noise and owner occupancy remain stationary while the other coefficients are allowed to vary over space.
-See \citet{Fotheringham2002} for a description of a mixed-LWR estimation algorithm.
+The mechanics of the second simulation are very similar to the those described in the previous section.
+We will randomly change the spatial arrangment of our house sales and estimate the LWR model.
+However, this simulation we will restrict the model to small bandwidths and compare the spread of the regression coefficient estimates under the random arrangment of the data to the spread found in our original LWR models with the actual spatial arrangement.
+If an independent variable in our hedonic regression function exhibits a stationary relationship with sales prices, then we should see similar levels of dispersion in the randomly arranged data as in our true data.
+However, if the dispersion we see in our random data is \emph{smaller} than the spread we observed in our actual data, that is evidence consistent with the variable having a non-stationary relationship.
+That is, the variation in regression coefficients obtained in our data is higher than we would observe from random chance.
 
-Figure \ref{fig:MCsds} visualizes the results of the second simulation.
+We present the results of this simulation for the same three different bandwidths in Table~\ref{tab:LWR}- 500, 650, and 1,000 nearest observations.
+Figures~\ref{fig:MCsds500} and \ref{fig:MCsds500} visualize the results of the second simulation for different bandwidths.
 Each sub-figure displays the distribution of LWR coefficient standard deviations obtained from the 100 iterations of the Monte Carlo simulation and the standard deviation obtained with the actual data (in red).
 Note that it is the case that the standard deviations obtained with the actual data are typically substantially larger than those obtained in the simulation for most of the variables.
-However, the variation obtained in the traffic noise coefficients simulations is similar with our actual LWR results, suggesting that the spatial non-stationarity exhibited in this coefficient is likely due to chance and not true spatial non-stationarity in the effect of traffic noise on house prices.
+However, the variation obtained in the noise coefficients simulations is not dissimilar to our actual LWR results, suggesting that the spatial non-stationarity exhibited in this coefficient is perhaps due to chance and not true spatial non-stationarity in the noise coefficient.
 
 \begin{figure}
- \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{../graphs/MCsimResultsSDsClean}}
- \caption{Actual LWR Coefficient Standard Deviations \textcolor{red}{(red line)} vs.\ Distribution of Monte Carlo Simulation Standard Deviations by Variable.
-Figures in which the red line is to the right of the black distribution suggest spatial non-stationarity in effect of the variable on house prices in our study region.}\label{fig:MCsds}
+ \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{../graphs/MCsimResultsSDs500}}
+ \caption{Simulation Results for nearest 500 observations.
+Actual LWR Coefficient Standard Deviations \textcolor{red}{(red line)} vs.\ Distribution of Monte Carlo Simulation Standard Deviations by Variable.
+Figures in which the red line is to the right of the black distribution suggest spatial non-stationarity in effect of the variable on house prices in our study region.}\label{fig:MCsds500}
 \end{figure}
 
-The results of these simulations suggest that spatial non-stationarity exists in the hedonic function and that LWR techniques are able to capture a significant portion of the non-stationarity.
-Using a bandwidth of the nearest 200 houses and a temporal lag of 12 months not only yielded significantly smaller GCV scores compared to other bandwidths and model specifications, but such performance does not seem to be a result of a chance spatial arrangement of the data.
-However, contrary to previous work, these simulations show no evidence for spatial variation in the effect of traffic noise on house prices.
+\begin{figure}
+ \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{../graphs/MCsimResultsSDs650}}
+ \caption{Simulation Results for nearest 650 observations.
+Actual LWR Coefficient Standard Deviations \textcolor{red}{(red line)} vs.\ Distribution of Monte Carlo Simulation Standard Deviations by Variable.
+Figures in which the red line is to the right of the black distribution suggest spatial non-stationarity in effect of the variable on house prices in our study region.}\label{fig:MCsds650}
+\end{figure}
+
+[Insert figure with nearest 1,000 observations here]
+
+[Insert maps showing the spatial variation in the most important regression coefficients]
 
@@
 
-In this section we look for evidence of temporal non-stationarity in the hedonic coefficient on traffic noise within our data.
-Specifically, we create two new variables, ``\texttt{months since September 2008}'' and a dummy variable ``\texttt{post}=1'' for all sales after September 2008.
-We then regress our LWR noise coefficients on these two variables and their interaction term as shown in equation \eqref{eq:LWRinteraction},
-\begin{equation}\label{eq:LWRinteraction}
-\hat{\beta}_{LWR} = \alpha _0 + \alpha _1 \texttt{*Months since Sep. 2008} + \alpha _2  \texttt{*Post} + \alpha _3 \texttt{*Post*Months since Sep. 2008} + \epsilon.
-\end{equation}
-The results of this regression will help us understand the patterns of change in the implicit price of traffic noise.
-In particular, $\alpha_1 \neq 0$ suggests a linear temporal trend in the marginal willingness to pay to avoid traffic noise, while $\alpha_2 \neq 0$ suggests that there was a structural break after September 2008, and $\alpha_3 \neq 0$ will imply a change in the temporal trend after September 2008.
-The linear regression results presented in Table \ref{tab:betaMAX} show that there the estimated LWR coefficients for traffic noise are significantly smaller after September 2008.
-\begin{table}
-\caption{Dependent Variable = Traffic Noise LWR Coefficients}\label{tab:betaMAX}
-\begin{center}
-\begin{tabular}{lrrr}
-           & Estimate & Std.\ Err. & t-stat  \\  \hline
-(Intercept) & -1.7e-03 &  4.1e-05 &  -43.4   \\
-Months since Sep 2008       & 6.9e-06 &  2.0e-06  &   3.5    \\
-Post        &-8.0e-04 &  7.2e-05  & -11.1    \\
-Post*Months since Sep 2008  &-8.9e-05 &  4.5e-06  & -19.7    \\ \hline
-\multicolumn{4}{l}{Residual standard error: 0.003} \\
-\multicolumn{4}{l}{N = 31,748, R$^2$: 0.093} \\ %,  Adjusted R$^2$: 0.093
-%\multicolumn{4}{l}{Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1}
+In this section we look for patterns in our noise coefficients over time.
+We find evidence consistent with the estimated noise coefficients being more negative in the later time periods (housing bust) of our study than in the earlier periods (housing boom).
+This finding is robust to multiple different formulations and specifications.
+Table~\ref{tab:noisebetatime} presents the results of regressions using our estimated LWR noise coefficient as the dependent variable and time and spatial characteristics as explanatory variables.
+
+Column (1) finds evidence of a negative linear trend in the LWR noise coefficients over time - predicting a LWR noise coefficient of approximately twice the magnitude for the end of our study period as for the beginning.
+Column (2) includes a quadratic term and again predicts noise coefficients much more negative towards the end of our study period compared to the beginning.
+We repeat the regressions from (1) and (2) in (3) and (4) but this time also include city fixed effects in order to control for any potential locational differences of house transactions over time.
+Again, we see very similar results - the noise coefficient is more negative in later time periods.
+We also limit our analysis to just the city of St.\ Paul and repeat the analysis from (1) and (2) in columns (5) and (6).
+Again, we estimate the noise coefficient to be more negative in later time periods.
+
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{LWR Noise Coefficient Over Time} 
+  \label{tab:noisebetatime} 
+\scriptsize 
+\begin{tabular}{@{\extracolsep{-1pt}}lD{.}{.}{6} D{.}{.}{7} D{.}{.}{7} D{.}{.}{7} D{.}{.}{7} D{.}{.}{7} } 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{Dependent variable: LWR Noise Coefficient}} \\ 
+\cline{2-7} 
+\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)} & \multicolumn{1}{c}{(5)} & \multicolumn{1}{c}{(6)}\\ 
+\hline \\[-1.8ex] 
+ Months since Jan 2005 & -0.00005^{***} & 0.00004^{***} & -0.00005^{***} & 0.00004^{***} & -0.0001^{***} & 0.0001^{***} \\ 
+  & (0.000001) & (0.000003) & (0.000001) & (0.000003) & (0.000001) & (0.00001) \\ 
+  & & & & & & \\ 
+ (Months since Jan 2005)$^2$ &  & -0.000001^{***} &  & -0.000001^{***} &  & -0.000001^{***} \\ 
+  &  & (0.00000004) &  & (0.00000004) &  & (0.0000001) \\ 
+  & & & & & & \\ 
+ Constant & -0.0016^{***} & -0.0029^{***} & -0.0021^{***} & -0.0034^{***} & -0.0016^{***} & -0.0035^{***} \\ 
+  & (0.00003) & (0.0001) & (0.00003) & (0.0001) & (0.0001) & (0.0001) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+City Fixed Effects & \multicolumn{1}{c}{No} & \multicolumn{1}{c}{No} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{No} & \multicolumn{1}{c}{No} \\ 
+\hline \\[-1.8ex] 
+Observations & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{8,003} & \multicolumn{1}{c}{8,003} \\ 
+R$^{2}$ & \multicolumn{1}{c}{0.1566} & \multicolumn{1}{c}{0.1722} & \multicolumn{1}{c}{0.3298} & \multicolumn{1}{c}{0.3446} & \multicolumn{1}{c}{0.1700} & \multicolumn{1}{c}{0.1915} \\ 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 
-\end{center}
 \end{table}
-
-The results in Table \ref{tab:betaMAX} contradict the expectation that environmental amenities will ``matter'' less during and after the Great Recession compared to the housing boom.
-In fact, these results suggest that the penalty for homes exposed to higher levels of traffic noise became more severe.
-That is, the negative hedonic coefficients on traffic noise got more negative after September 2008.
-
-\subsection{Are There Threshold Effects of Traffic Noise?}
-
-Some researchers conclude that the semi-elasticity of noise varies with the level of noise \citep{Andersson2010, MarmolejoDuarteCarlos;GonzalezTamez2009, Theebe2004a, Miedema2001, Wilhelmsson2000}, such as a ``threshold''' effect at 70dB \citep{Wilhelmsson2000, Cohen2009}.
-Other researchers report no evidence of varying impacts at higher or lower noise intensities \citep{Blanco2011, Baranzini2010, Kim2007, Huang;Palmquist2001}.
-In this section we compare our mean LWR noise coefficient estimates across noise levels to look for threshold effects of traffic noise.
-
-\begin{table}
-\begin{center}
-\caption{LWR Noise Coefficients vs.\ Noise Levels}\label{tab:LWRnonlinear}
-\begin{tabular}{lrrr}
-         &   Estimate & Std.\ Err. & t-value \\ \hline
-(Intercept) & -1.8e-03 & 1.3e-04  &-13.3 \\
-Noise       & -2.8e-06 & 2.3e-06  & -1.2 \\  
-Post        & -3.6e-03 & 2.2e-04  &-16.2 \\
-Noise*Post  &  3.4e-05 & 4.0e-06  &  8.5 \\ \hline
-\multicolumn{4}{l}{Residual standard error: 0.003} \\
-\multicolumn{4}{l}{N: 31,748, R$^2$: 0.083} \\
-%F-statistic: 961.4 on 3 and 31744 DF,  p-value: < 2.2e-16 
-\end{tabular}
-\end{center}
-\end{table}
-
-Table \ref{tab:LWRnonlinear} reports the results of a simple linear regression of the LWR noise coefficients on the noise levels and whether or not the sale took place before or after September 2008 (as well as their interaction).
-The table reveals no statistically measurable linear relationship between the noise coefficient and the noise level for sales before September 2008.
-That is, the semi-elasticity is no different in our data at low levels of noise than at high levels of noise.
-The positive and significant interaction term suggests that the impact may be different for high vs.\ low levels of noise post-September 2008, but the difference in the predicted marginal effects is so small that it works about to be a roughly \$25 difference for a \$300,000 house at 50 vs.\ 75 dB.
-Thus, while other researchers report finding impact thresholds at 70dB, we cannot corroborate such findings with our data.
-
-Figure \ref{fig:betaMAXvCat} visually displays the estimated relationship between the level of traffic noise, time, and the estimated LWR traffic noise coefficients.
-We categorize the traffic noise data in 5 dB wide bins like \citet{Theebe2004a} and then estimate the mean LWR traffic noise coefficients in each category while also controlling for whether the sales took place pre- or post-September 2008.
-We see little to suggest any meaningful non-linearities in the regression coefficients of traffic noise on house prices, once we have controlled for the timing of the sales.
-
-\begin{figure}
-\makebox[\textwidth][c]{\includegraphics[width = 1.1\textwidth]{../graphs/LWRbetaMAXbyCatTime}}
-\caption{The mean LWR traffic noise coefficient by 5 decibel category and pre- vs.\ post-September 2008.
-The vertical lines denote the standard error of the estimated mean by time and level category.
-Note that over 99 percent of our data have Noise levels between 35 and 80 dB and no houses were sold post-September 2008 with noise levels above 85 dB.}\label{fig:betaMAXvCat}
-\end{figure}
 
@@
 These results and analysis rest on important assumptions, which if violated, may change the results.
-This section describes two assumptions that we think are most noteworthy of discussion: lack of omitted variable bias and temporal non-stationarity in the level of several variables across the region during our study period.
+This section describes three important considerations needed to contextualize our results and worthy of discussion: causation vs.\ correlation, potential temporal problems with our data, and omitted variable bias.
 
-Our previously reported results lack some important control variables in the hedonic function.
-To the extent that structural variables like the number of bedrooms, bathrooms, garage size, or construction quality co-vary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias.
-We are comforted, however, because we do have some of these important additional variables for a subset of our data.
-We obtained the number of bedrooms, bathrooms, and garage area for our houses located within Dakota County from the Dakota County Assessor's Office.
-Our LWR analysis (Models 1, 2, and 3 described earlier) was repeated on this geographic subset of the data and the results were compared to the estimates obtained from the same analysis when these additional structural variables were omitted.
-We found strikingly similar estimates of the impact of traffic noise suggesting that our results may be robust to the omission of these variables from our analysis.
+First and foremost, we need to be cautious about claims of causality.
+In an ideal research design, we would observe the same houses over time and randomly ``treat'' some houses with more or less noise to observe the change in price relative to the control houses.
+Such a study is not feasible and we are therefore limited to a hedonic analysis with observational data.
+Our conclusions, then, should be interpretted like most other hedonic analysis results and while we find a strong negative correlation between noise and house prices, stronger in some areas of our study area than others and stronger in some time periods than others, we cannot definitely state that noise causes lower sales prices.
 
-\begin{table}
-\begin{center}
-\caption{Noise Coefficient Estimates in Dakota County with and without Additional Structural Variables}\label{tab:Dak}
-\begin{tabular}{lll}
- & \multicolumn{2}{p{1.25in}}{Additional Variables Included in LWR?} \\
-Locally Weighted Regression Model & \multicolumn{1}{c}{no} & \multicolumn{1}{c}{yes} \\ \cline{1-3}
-\multirow{2}{*}{Model (1) = Structural Variables} & -0.0015 & -0.0015 \\ 
-   & (0.0023) & (0.0031)  \\[.2cm]
-\multirow{2}{*}{Model (2) = Model (1) + Locational Variables} & -0.0014 & -0.0014  \\ 
-   & (0.0018) & (0.0022)  \\[.2cm] 
-\multirow{2}{*}{Model (3) = Model (2) + City Fixed Effects} & -0.0014 & -0.0014 \\ 
-   & (0.0022) & (0.0018) \\[.2cm] \cline{1-3}
-\multicolumn{3}{p{4.25in}}{Mean and (standard deviation) LWR traffic noise coefficients when the number of bedrooms, bathrooms, and garage size are included as additional control variables in the regression.}
-\end{tabular}
-\end{center}
-\end{table}
-
-Table \ref{tab:Dak} shows that the traffic noise coefficients estimated by our LWR models are similar regardless of whether the additional structural variables were included or not.
-Welch two-sample t-tests fail to reject the null hypothesis of zero mean differences across our three models (comparing LWR estimates with vs.\ without the additional structural variables included in the model).
-Paired t-tests find differences for Model 2 and 3, but the estimated differences are zero to four decimal places and in one case the noise impact estimates with the additional variables are slightly larger and in the other case they are slightly smaller.
-We also conducted simple linear regressions of the noise coefficients without the additional structural variables on the noise coefficients obtained with the additional structural variables for each of our three models.
-In all cases the model intercept estimates were close zero, the slopes almost exactly equal to one, and $R^2$ values over 0.7.
-These results suggest the hedonic coefficients for traffic noise are unaffected by omitted variable bias from common structural variables.
-While we cannot confirm that this lack of omitted variable bias also occurs elsewhere in our data, the results from Dakota County are promising.
-
-The timing of our independent variable collection is also a potential weakness.
-While our house sales data are collected over the course of six years, some of our other variables were collected at specific points in time and assumed to be constant over the study period.
-In particular, the traffic noise estimates are for the year 2007.
+Our work also faces data limitations.
+Notably, while our house sales data are collected over the course of six years, the traffic noise estimates are for the year 2007.
 To the extent that traffic flows and composition significantly changed over time, our traffic noise variables may be inaccurate for those other time periods.
-For instance, the US Department of Transportation reports that total vehicle miles traveled decreased by up to 4 percent year-on-year during the Great Recession.\footnote{\url{http://www.fhwa.dot.gov/ohim/tvtw/08dectvt}} Thus, our noise estimates may be inaccurate for later time periods and this may bias our estimates of the impact of noise on house values.
-Future work may seek to create time-series noise data in order to obtain even better estimates of the impact of traffic noise over time.
+However, Table VM2 from the US.
+Department of Transportation Office of Highway Policy Information website reports that in the year 2007 there were approximately 30 million vehicle miles traveled in the urban areas of the state of MN, while for years 2008, 2009, and 2010 the respective values were 32.5, 32.3, and 32.0.
+Overall, this represents a change of less than 10 percent.
+\footnote{\url{http://www.fhwa.dot.gov/policyinformation/quickfinddata/qftravel.cfm}} Such small changes in total vehicle miles traveled are unlikely to yield significant differences in noise levels.
+Additionally, we do not believe the changes are likely to manifest in significant spatial variation in traffic noise, which is ultimately responsible for our identification of the noise regression coefficient.
+However, given enough time for changes in driving habits and technological advancements to gain significant market penetration (for instance, quieter hybrid cars), future work should seek to create time-series noise data in order to obtain even better estimates of the impact of traffic noise over time.
 Given the computational complexity of re-estimating the landscape noise surface, such work is beyond the scope of this paper.
 
+Our previously reported results also lack some important control variables in the hedonic function.
+For instance, locations exposed to more noise due to their proximity to high traffic areas may also be less safe due to the potential for accidents.
+Without including a proxy variable for safety, our noise coefficient could be biased - making it appear that home prices are reflecting noise exposure when in fact it could be safety issues.
+Future research aimed at measuring the impact of noise should continue to seek out and control for other confounding variables.
+
+Our data also omits other variables and to the extent that structural variables like the number of bedrooms, bathrooms, garage size, or construction quality co-vary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias.
+We are comforted, however, because we do have some of these important additional variables for a subset of our data.
+We were able to obtain the number of bedrooms, bathrooms, and garage area for our houses located within Dakota County from the Dakota County Assessor's Office.
+Our LWR analysis was then repeated on this geographic subset of the data in order to compare our noise coefficients across the different models.
+We found strikingly similar traffic noise coefficient estimates when these additional structural variables were included and omitted.
+As shown in Figure~\ref{fig:DAK}, a simple linear regression of the noise coefficient estimates obtained when these additional structural variables were excluded on the estimates obtained when these variables were included yields a line of best fit that is almost indiscernable from the 45 degree line and has $R^2 = 0.96$.
+%Additionally, a paired t-test of the roughly 9,000 (n = 8,751) coefficient estimates yields a 95 percent confidence interval for the true difference between our estimates without the additional variables and with as -0.000175 to -0.000159.
+That is, the estimated difference is, on average, more than an order of magnitude smaller than our typical coefficient estimates  suggesting that our results may be robust to the omission of these variables from our analysis.
+
+\begin{figure}
+\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/DakotaResults}}
+\caption{This figure shows the similarity between the LWR coefficients we obtained from our model in Dakota County when additional structural variables were excluded vs.\ included in the hedonic regression function.
+The black line shows the 45 degree line, while the red dashed line shows the estimated line of best fit, which yields a simple $R^2$ of 0.96}\label{fig:DAK}
+\end{figure}
+
 \section{Conclusion}
-We estimated the impact of traffic noise on housing prices using Locally Weighted Regression techniques in the St.\ Paul, Minnesota, urban area.
-Specifically, we estimate semi-logarithmic regressions at each house within our dataset using only information contained in ``local'' (both geographically and temporally) house sales.
+We estimated a hedonic price function for single family houses using Locally Weighted Regression techniques in the St.\ Paul, Minnesota, urban area.
+Specifically, we estimated semi-logarithmic regressions at each house within our dataset using only information contained in ``local'' (both geographically and temporally) house sales.
 We find strong evidence that the hedonic function in our study area varies over space and time and such flexible models represent significant improvements over conventional parametric models.
@@
 That is, after trying thousands of different combinations of varying levels of local analysis with the spatially redistributed data, we never came close to estimating our observed housing sales prices as well as we can with the local analysis on the actual data.
-Additionally, re-estimating the LWR model using a local bandwidth of 200 nearest house sales but randomly assigned locations yielded substantially smaller standard deviations for the majority of our regression coefficients.
+Additionally, re-estimating the LWR model using local bandwidths but randomly assigned locations yielded substantially smaller standard deviations for the majority of our regression coefficients.
 Such differences suggest that the variation exhibited by most of our regression coefficients was not due to simple random chance, but instead is consistent with spatial non-stationarity.
 
-Contrary to the previous results presented by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} and \citet{Theebe2004a}, we find little evidence to suggest that the impact of traffic noise varies geographically or by the level of noise within our study area.
-The traffic noise coefficient was one of only two variables with regression coefficient standard deviations smaller than or similar to the simulated distributions obtained from Monte Carlo experiments.
+While our results show very strong evidence that the coefficients on lot size and living space vary over space, the noise coefficient was one of a few variables to exhibit similar standard deviations to the simulated distributions obtained from Monte Carlo experiments.
 We do, however, find significant temporal variation in the impact of traffic noise in our data.
-The estimated impact of one additional decibel of traffic noise is a 0.19 percent reduction in the sale price of houses before September 2008, vs.\ 0.37 percent after September 2008.
-Lastly, after controlling for the Great Recession, we find no significant differences in the impact of traffic noise across the range of commonly seen noise levels (50-70 dB).
 

### 2014-06-23 reports/NoiseHedonicRaR.tex
june 2014 revisions - draft to Tsegaye

--- 2013-10-15 reports/Draft.tex
@@
 \usepackage{alltt}
+
 \usepackage[round]{natbib}
+\usepackage{dcolumn}
 \usepackage[nolists]{endfloat}
@@
 
-Work from Europe suggests that the relationship between traffic noise and house prices varies across housing submarkets \citep{Day2007, MarmolejoDuarteCarlos;GonzalezTamez2009}, by level of traffic noise \citep{Theebe2004a, Brandt2011}, and over time \cite{Wilhelmsson2000}.
-As such, we construct a flexible hedonic model that allows for a non-stationary relationship between house prices and our explanatory variables over geography and time.
+We construct a flexible hedonic model that allows for a non-stationary relationship between house prices and our explanatory variables over geography and time.
 Such Locally Weighted Regression (LWR) models have become increasingly common in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than other common spatial econometric models under common real world circumstances \citep{McMillen2012}.
-Thus, in addition to using new data that reduces the measurement error of the impact of traffic noise, the spatial and temporal variation in our data and hedonic modeling allow us to present the first estimates in the United States of how the impact of traffic noise varies over space, time, and by noise level.
+Thus, in addition to using new data that reduces the measurement error of the impact of traffic noise, the spatial and temporal variation in our data and hedonic modeling allow us to present the first estimates in the United States of how the marginal effect of traffic noise varies over space and time.
 
-We find that while the impact of other important control variables in the hedonic function vary significantly over space, the impact of traffic noise does not.
-Such results are contradictory to recent work by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009} which found evidence of a spatially non-stationary relationship between traffic noise and housing prices using a LWR model in Barcelona, Spain.
+We find strong evidence to support hedonic modeling choices that allow for spatial and temporal heterogeneity.
 Our paper also presents the first estimates of the implicit price of traffic noise after the housing market collapse and economic recession of 2008-09.
-Contrary to work such as \citet{Cho2011b}, which found that environmental amenities mattered \emph{less} after the housing crash, our estimated effect of traffic noise mattered \emph{almost twice as much more} after the recession (0.19 percent reduction in house prices per additional decibel beforehand compared to 0.37 percent per decibel afterwards).
+Contrary to work such as \citet{Cho2011b}, which found that environmental amenities mattered \emph{less} after the housing crash, our estimated noise coefficients roughly double in magnitude after the recession compared to before.
 We conclude with a discussion of how future research can expand and improve upon this work.
@@
 These results and analysis rest on important assumptions, which if violated, may change the results.
-This section describes two assumptions that we think are most noteworthy of discussion: lack of omitted variable bias and temporal non-stationarity in the level of several variables across the region during our study period.
+This section describes three important considerations needed to contextualize our results and worthy of discussion: causation vs.\ correlation, potential temporal problems with our data, and omitted variable bias.
 
-Our previously reported results lack some important control variables in the hedonic function.
-To the extent that structural variables like the number of bedrooms, bathrooms, garage size, or construction quality co-vary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias.
-We are comforted, however, because we do have some of these important additional variables for a subset of our data.
-We obtained the number of bedrooms, bathrooms, and garage area for our houses located within Dakota County from the Dakota County Assessor's Office.
-Our LWR analysis (Models 1, 2, and 3 described earlier) was repeated on this geographic subset of the data and the results were compared to the estimates obtained from the same analysis when these additional structural variables were omitted.
-We found strikingly similar estimates of the impact of traffic noise suggesting that our results may be robust to the omission of these variables from our analysis.
+First and foremost, we need to be cautious about claims of causality.
+In an ideal research design, we would observe the same houses over time and randomly ``treat'' some houses with more or less noise to observe the change in price relative to the control houses.
+Such a study is not feasible and we are therefore limited to a hedonic analysis with observational data.
+Our conclusions, then, should be interpretted like most other hedonic analysis results and while we find a strong negative correlation between noise and house prices, stronger in some areas of our study area than others and stronger in some time periods than others, we cannot definitely state that noise causes lower sales prices.
 
-\begin{table}
-\begin{center}
-\caption{Noise Coefficient Estimates in Dakota County with and without Additional Structural Variables}\label{tab:Dak}
-\begin{tabular}{lll}
- & \multicolumn{2}{p{1.25in}}{Additional Variables Included in LWR?} \\
-Locally Weighted Regression Model & \multicolumn{1}{c}{no} & \multicolumn{1}{c}{yes} \\ \cline{1-3}
-\multirow{2}{*}{Model (1) = Structural Variables} & -0.0015 & -0.0015 \\ 
-   & (0.0023) & (0.0031)  \\[.2cm]
-\multirow{2}{*}{Model (2) = Model (1) + Locational Variables} & -0.0014 & -0.0014  \\ 
-   & (0.0018) & (0.0022)  \\[.2cm] 
-\multirow{2}{*}{Model (3) = Model (2) + City Fixed Effects} & -0.0014 & -0.0014 \\ 
-   & (0.0022) & (0.0018) \\[.2cm] \cline{1-3}
-\multicolumn{3}{p{4.25in}}{Mean and (standard deviation) LWR traffic noise coefficients when the number of bedrooms, bathrooms, and garage size are included as additional control variables in the regression.}
-\end{tabular}
-\end{center}
-\end{table}
-
-Table \ref{tab:Dak} shows that the traffic noise coefficients estimated by our LWR models are similar regardless of whether the additional structural variables were included or not.
-Welch two-sample t-tests fail to reject the null hypothesis of zero mean differences across our three models (comparing LWR estimates with vs.\ without the additional structural variables included in the model).
-Paired t-tests find differences for Model 2 and 3, but the estimated differences are zero to four decimal places and in one case the noise impact estimates with the additional variables are slightly larger and in the other case they are slightly smaller.
-We also conducted simple linear regressions of the noise coefficients without the additional structural variables on the noise coefficients obtained with the additional structural variables for each of our three models.
-In all cases the model intercept estimates were close zero, the slopes almost exactly equal to one, and $R^2$ values over 0.7.
-These results suggest the hedonic coefficients for traffic noise are unaffected by omitted variable bias from common structural variables.
-While we cannot confirm that this lack of omitted variable bias also occurs elsewhere in our data, the results from Dakota County are promising.
-
-The timing of our independent variable collection is also a potential weakness.
-While our house sales data are collected over the course of six years, some of our other variables were collected at specific points in time and assumed to be constant over the study period.
-In particular, the traffic noise estimates are for the year 2007.
+Our work also faces some serious data limitations.
+Notably, while our house sales data are collected over the course of six years, the traffic noise estimates are for the year 2007.
 To the extent that traffic flows and composition significantly changed over time, our traffic noise variables may be inaccurate for those other time periods.
-For instance, the US Department of Transportation reports that total vehicle miles traveled decreased by up to 4 percent year-on-year during the Great Recession.\footnote{\url{http://www.fhwa.dot.gov/ohim/tvtw/08dectvt}} Thus, our noise estimates may be inaccurate for later time periods and this may bias our estimates of the impact of noise on house values.
-Future work may seek to create time-series noise data in order to obtain even better estimates of the impact of traffic noise over time.
+However, Table VM2 from the US.
+Department of Transportation Office of Highway Policy Information website reports that in the year 2007 there were approximately 30 million vehicle miles traveled in the urban areas of the state of MN, while for years 2008, 2009, and 2010 the respective values were 32.5, 32.3, and 32.0.
+Overall, this represents a change of less than 10 percent.
+\footnote{\url{http://www.fhwa.dot.gov/policyinformation/quickfinddata/qftravel.cfm}} Such small changes in total vehicle miles traveled are unlikely to yield significant differences in noise levels.
+Additionally, we do not believe the changes are likely to manifest in significant spatial variation in traffic noise, which is ultimately responsible for our identification of the noise regression coefficient.
+However, given enough time for changes in driving habits and technological advancements to gain significant market penetration (for instance, quieter hybrid cars), future work should seek to create time-series noise data in order to obtain even better estimates of the impact of traffic noise over time.
 Given the computational complexity of re-estimating the landscape noise surface, such work is beyond the scope of this paper.
 
+Our previously reported results also lack some important control variables in the hedonic function.
+For instance, locations exposed to more noise due to their proximity to high traffic areas may also be less safe due to the potential for accidents.
+Without including a proxy variable for safety, our noise coefficient could be biased - making it appear that home prices are reflecting noise exposure when in fact it could be safety issues.
+Future research aimed at measuring the impact of noise should continue to seek out and control for other confounding variables.
+
+Our data also omits other variables and to the extent that structural variables like the number of bedrooms, bathrooms, garage size, or construction quality co-vary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias.
+We are comforted, however, because we do have some of these important additional variables for a subset of our data.
+We were able to obtain the number of bedrooms, bathrooms, and garage area for our houses located within Dakota County from the Dakota County Assessor's Office.
+Our LWR analysis was then repeated on this geographic subset of the data in order to compare our noise coefficients across the different models.
+We found strikingly similar traffic noise coefficient estimates when these additional structural variables were included and omitted.
+As shown in Figure~\ref{fig:DAK}, a simple linear regression of the noise coefficient estimates obtained when these additional structural variables were excluded on the estimates obtained when these variables were included yields a line of best fit that is almost indiscernable from the 45 degree line and has $R^2 = 0.96$.
+%Additionally, a paired t-test of the roughly 9,000 (n = 8,751) coefficient estimates yields a 95 percent confidence interval for the true difference between our estimates without the additional variables and with as -0.000175 to -0.000159.
+That is, the estimated difference is, on average, more than an order of magnitude smaller than our typical coefficient estimates  suggesting that our results may be robust to the omission of these variables from our analysis.
+
+\begin{figure}
+\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/DakotaResults}}
+\caption{This figure shows the similarity between the LWR coefficients we obtained from our model in Dakota County when additional structural variables were excluded vs.\ included in the hedonic regression function.
+The black line shows the 45 degree line, while the red dashed line shows the estimated line of best fit, which yields a simple $R^2$ of 0.96}\label{fig:DAK}
+\end{figure}
+
 \section{Conclusion}
-We estimated the impact of traffic noise on housing prices using Locally Weighted Regression techniques in the St.\ Paul, Minnesota, urban area.
-Specifically, we estimate semi-logarithmic regressions at each house within our dataset using only information contained in ``local'' (both geographically and temporally) house sales.
+We estimated a hedonic price function for single family houses using Locally Weighted Regression techniques in the St.\ Paul, Minnesota, urban area.
+Specifically, we estimated semi-logarithmic regressions at each house within our dataset using only information contained in ``local'' (both geographically and temporally) house sales.
 We find strong evidence that the hedonic function in our study area varies over space and time and such flexible models represent significant improvements over conventional parametric models.

### 2014-06-23 analysis/00DescriptiveStats/CorMatrix.R

@@ -1,0 +1,24 @@
+
+library (foreign)
+workingdata <- read.dbf("../Data/R2GIS/CleanData/Sales20052010.dbf")
+
+
+quantVars = c("SALE_VALUE", "FIN_SQ_FT", "ACRES_POLY", "YEAR_BUILT", 
+              "Air_Mean", "CBD_dist", "PARK_dist", "LAKE_dist",  "SHOP_dist",
+              "PercWhite", "PercU18",
+              "MED_INCOME", "MCA3")
+
+corMat = cor(workingdata[, quantVars])
+
+corMat = round(corMat, 2)
+
+corMat[upper.tri(corMat)] <- ""
+corMat
+
+rownames(corMat) = c("Sale Price", "House Size", "Lot Size", "Year Built", "Noise", 
+                     "Distance to CBD", "Distance to Park", "Distance to Lake", "Distance to Shop",
+                     "Percent Pop White", "Percent Under 18",   "Income", "Elementary Test Scores",)
+colnames(corMat) = c("Price", "House", "Lot", "Built", "Noise", "CBD", "Park", "Lake", "Shop", "White", "U18", "Income", "Test")
+
+require(xtable)
+print(xtable(corMat, align = "lrrrrrrrrrrrrr"))

### 2014-06-23 analysis/00DescriptiveStats/DescriptiveMaker.R

@@ -5,46 +5,29 @@
 require(foreign)
 DATAFRAME = read.dbf("~/NoiseHedonicProject/Data/R2GIS/CleanData/Sales20052010.dbf")
 
-myvars = c("SALE_VALUE", "FIN_SQ_FT", "ACRES_POLY", "OWNOCC", "YEAR_BUILT", "MAX", 
-           "MED_INCOME", "MCA3", "CBD_dist", "PARK_dist", "LAKE_dist", "SHOP_dist")
+myvars = c("SALE_VALUE", "YEAR_BUILT", "FIN_SQ_FT", "ACRES_POLY", "OWNOCC", "Air_Mean", 
+           "CBD_dist", "PARK_dist", "LAKE_dist", "SHOP_dist", 
+           "PercWhite", "PercU18", "MED_INCOME", "MCA3")
 
-mynames = c("Sale Price (thousands)", "House Size (thousands square feet)", "Lot Size (acres)", "Owner Occupancy Dummy",
-            "Year House was Built", "Traffic Noise (dB)", "Median Income in Census Tract (thousands)", 
-            "Elementary Test Scores", "Distance to Central Business District (km)",
-            "Distance to nearest Park (km)", "Distance to nearest Lake (km)", "Distance to nearest Shopping Center (km)")
+mynames = c("Sale Price (thousands)", "Year House was Built", "House Size (square feet)", 
+            "Lot Size (acres)", "Owner Occupancy (Yes = 1, No = 0)", "Traffic Noise (dB)", 
+            "Distance to Central Business District (km)",
+            "Distance to nearest Park (km)", "Distance to nearest Lake (km)", "Distance to nearest Shopping Center (km)",
+            "Percent of Census Block Population Race = White", "Percent of Census Block Population Under Age 18",
+            "Median Income in Census Tract (thousands)", "Elementary Test Scores")
 
 sumStats = matrix(NA, length(myvars), 7)
-
 for (i in 1:length(myvars)) {
   sumStats[i, 1:6] = summary(DATAFRAME[ , myvars[i]])  
   sumStats[i, 7] = sd(DATAFRAME[ , myvars[i]])
 }
-
 sumStats
-
 sumStats = sumStats/c(1000, 1, 1, 1, 1, 1, 
[…]

### 2014-06-23 analysis/00DescriptiveStats/MeansByYearMaker.R

@@ -1,0 +1,32 @@
+
+myvars = c("SALE_VALUE", "YEAR_BUILT", "FIN_SQ_FT", "ACRES_POLY", "OWNOCC", "Air_Mean", 
+           "CBD_dist", "PARK_dist", "LAKE_dist", "SHOP_dist", 
+           "PercWhite", "PercU18", "MED_INCOME", "MCA3")
+divisor = c(1000, 1, 1, 1, 1, 1, 1000, 1000, 1000, 1000, 1, 1, 1000, 1)
+
+
+yearstats = matrix(NA, length(myvars)+1, 7)
+
+for (i in 1:length(myvars)) {
+  yearstats[i, 1:6] = tapply(DATAFRAME[, myvars[i]], DATAFRAME$SALE_YR, mean)/divisor[i]
+  yearstats[i, 7] = mean(DATAFRAME[, myvars[i]]/divisor[i])
+}
+
+i = i + 1
+yearstats[i, 1:6] = tapply(DATAFRAME[, myvars[i-1]], DATAFRAME$SALE_YR, length)
+yearstats[i, 7] = length(DATAFRAME[, myvars[i-1]])
+
+yearstats
+mynames = c("Sale Price (thousands)", "Year House was Built", "House Size (square feet)", 
+            "Lot Size (acres)", "Owner Occupancy (Yes = 1, No = 0)", "Traffic Noise (dB)", 
+            "Distance to Central Business District (km)",
+            "Distance to nearest Park (km)", "Distance to nearest Lake (km)", "Distance to nearest Shopping Center (km)",
+            "Percent of Census Block Population Race = White", "Percent of Census Block Population Under Age 18",
+            "Median Income in Census Tract (thousands)", "Elementary Test Scores",
+            "Number of Sales")
+rownames(yearstats) = mynames
+
+mydig = matrix(rep(c(0, 0, 0, 2, 2, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0), 8), length(myvars)+1, 8)
+
+require(xtable)
+xtable(yearstats, digits = mydig)

### 2014-06-23 analysis/04MonteCarloSim/MonteCarloScript2AssesSpatialNonStationarity.R

@@ -12,7 +12,7 @@ myVars = c("Air_Mean", "FIN_SQ_FT", "ACRES_POLY", "YEAR_BUILT", "OWNOCC", "MED_I
 RHS = paste(myVars, collapse = "+")
 MYMODEL = paste("logSALE_VA", RHS, sep = "~")
 MYMODELsmall = substr(MYMODEL, 1, nchar(MYMODEL)-5)
-KVECTOR = c(650) # c(200, 400, 650, 1000, 2000, 4000)
+KVECTOR = c(1000) # c(200, 400, 650, 1000, 2000, 4000)
 
 # How many times am I going to reshuffle?
 iterations = 50 #100
@@ -20,10 +20,12 @@ iterations = 50 #100
 # mean and sd of each coefficient i care about + intercept + GCV score + min bandwidth
 vars2keep = c("Intercept", myVars[c(1:(length(myVars)-3))])
 numMCstats = 2 + 2*length(vars2keep)
-MCstats = matrix(NA, iterations, numMCstats)
+MCstats = matrix(NA, 100, numMCstats)
 colnames(MCstats) = c("minGCV", "optimalBandwidth", 
                       paste0("meanBeta.", vars2keep),
                       paste0("sterBeta.", vars2keep))
+# mcstats = read.csv("analysis/04MonteCarloSim/Revision/Model3/CopyOfLWRMonteCarloStats2014-06-20.csv")
+# MCstats = as.matrix(mcstats)
 
 filePrefix = "../Data/R2GIS/CleanData/"
 inputFile = "Sales20052010.dbf"

### 2014-06-23 analysis/04MonteCarloSim/Revision/MCsimVisualizer.R

@@ -1,0 +1,50 @@
+# Assess the Monte Carlo simulation results
+# goal is to assess whether/which variables exhibit spatial non-stationarity
+
+# load the results of the true data analysis
+# calculate some statistics
+# load the monte carlo data
+# create distributions of the MC stats
+# add the true statistic to the distribution
+
+load("../Data/R2GIS/CleanData/TimeLag12months/Sales20052010LWRmodelAirMean3-2014-03-19.RData") # LWR output from model run with real data
+
+# LWRMonteCarloStats2014.03.29 <- read.csv("~/NoiseHedonicProject/Noise-Hedonic/analysis/04MonteCarloSim/Revision/Model3/LWRMonteCarloStats2014-03-29.csv")
+# LWRMonteCarloStats2014.04.18 <- read.csv("~/NoiseHedonicProject/Noise-Hedonic/analysis/04MonteCarloSim/Revision/Model3/LWRMonteCarloStats2014-04-18.csv")
+# MCMaster <- rbind(LWRMonteCarloStats2014.03.29, LWRMonteCarloStats2014.04.18)
+MCMaster = read.csv("~/NoiseHedonicProject/Noise-Hedonic/analysis/04MonteCarloSim/Revision/Model3/LWRMonteCarloStats2014-06-20.csv")
+MCMaster = MCMaster[1:40,]
+
+MCplotter = function(outputcoefficient, statcoefficient, meanORsd = "mean") {
+  if (meanORsd == "mean") actual = mean(output[[outputcoefficient]][, "k500"], na.rm =T)
+  if (meanORsd == "sd")   actual = sd(output[[outputcoefficient]][, "k500"], na.rm =T)
+  
+  temp = density(MCMaster[, statcoefficient])
+  plot(temp, 
+       xlim = c(min(c(range(temp$x), actual), na.rm = T), max(c(range(temp$x), actual), na.rm = T)),
+       main = paste(meanORsd, sub("beta.", "", outputcoefficient)),
+       axes = F, ylab = "", xlab = "")
+  axis(1)
+  mtext("relative frequency", 2, 1, cex = .7)
+  abline(v = actual, col = "red")
+}
+
+outputCOEFS = rep(names(output)[c(1:5, 16, 19, 20, 21, 22, 23, 24, 17, 18)], 2)
+statCOEFS = names(MCMaster)[3:30]
[…]

### 2014-06-23 analysis/SandboxAaron/LWRcoeffsByBW.R

@@ -1,0 +1,30 @@
+
+# How much do our noise coefficients change as we increase the bandwidth to something "much larger" if we are 
+# concerned with inference/accuracy of marginal effects.
+
+# Correlation of coefficients by bandwidth? 500, 650, 1000, 2000
+
+load("~/NoiseHedonicProject/Data/R2GIS/CleanData/TimeLag12months/Sales20052010LWRmodelAirMean3-2014-03-19.RData")
+
+# make a dataset of the regression coefficients for noise with different bandwidths
+
+noisebetabyk = data.frame(output[["beta.Air_Mean"]][, c("k500", "k650", "k1000", "k2000")])
+names(noisebetabyk)
+
+cor(noisebetabyk)
+
+require(graphics)
+smoothScatter(noisebetabyk$k650, noisebetabyk$k500,
+              xlim = c(-0.015, 0.005), ylim = c(-0.015, 0.005))
+abline(0, 1)
+abline(lm(k500 ~ k650, data = noisebetabyk), col = "red")
+
+smoothScatter(noisebetabyk$k1000, noisebetabyk$k500,
+              xlim = c(-0.015, 0.005), ylim = c(-0.015, 0.005))
+abline(0, 1)
+abline(lm(k500 ~ k1000, data = noisebetabyk), col = "red")
+
+smoothScatter(noisebetabyk$k2000, noisebetabyk$k500,
+              xlim = c(-0.015, 0.005), ylim = c(-0.015, 0.005))
+abline(0, 1)
+abline(lm(k500 ~ k2000, data = noisebetabyk), col = "red")

### 2014-06-23 analysis/SandboxAaron/aaronSandbox.R

@@ -20,14 +20,30 @@ load("~/NoiseHedonicProject/Data/R2GIS/CleanData/TimeLag12months/Sales20052010LW
 # [160] "ses.PARK_dist"                "ses.SHOP_dist"                "ses.CBD_dist" 
 
 data2xport = data.frame(output$beta.Air_Mean[,"k650"])
-names(data2xport) = "bnoise"
-data2xport$bfinsqft = output$beta.FIN_SQ_FT[,"k650"]
-data2xport$bacres = output$beta.ACRES_POLY[,"k650"]
-data2xport$senoise = output$ses.Air_Mean[, "k650"]
-data2xport$sefinsqft = output$ses.FIN_SQ_FT[,"k650"]
-data2xport$seacres = output$ses.ACRES_POLY[,"k650"]
+names(data2xport) = "bnoise65"
+data2xport$bfinft65 = output$beta.FIN_SQ_FT[,"k650"]
+data2xport$bacres65 = output$beta.ACRES_POLY[,"k650"]
+data2xport$senoise65 = output$ses.Air_Mean[, "k650"]
+data2xport$sefinft65 = output$ses.FIN_SQ_FT[,"k650"]
+data2xport$seacres65 = output$ses.ACRES_POLY[,"k650"]
+data2xport$yhats65 = output$yhats[, "k650"]
 data2xport$UNIQID = as.numeric(rownames(data2xport))
 
+data2xport$bnoise50 = output$beta.Air_Mean[,"k500"]
+data2xport$bfinft50 = output$beta.FIN_SQ_FT[,"k500"]
+data2xport$bacres50 = output$beta.ACRES_POLY[,"k500"]
+data2xport$senoise50 = output$ses.Air_Mean[, "k500"]
+data2xport$sefinft50 = output$ses.FIN_SQ_FT[,"k500"]
+data2xport$seacres50 = output$ses.ACRES_POLY[,"k500"]
+data2xport$yhats50 = output$yhats[, "k500"]
+
+require(foreign)
+DATAFRAME = read.dbf("../Data/R2GIS/CleanData/Sales20052010.dbf")
+obs2run = which(DATAFRAME$TimePeriod>11)
+lm.global = lm(MYMODEL, data = DATAFRAME[obs2run, ])
+head(DATAFRAME$UNIQID[obs2run])
+head(rownames(data2xport))
+data2xport$yhatsglob = lm.global$fitted.values
 
 # 3 - create a flat table of the variables (make sure they have names <10 characters long)
 

### 2014-06-23 reports/code/DakotaComparison.R

@@ -1,0 +1,122 @@
+# GOAL: compare LWR Noise coefficients across Dakota County under alternative specifications
+
+# Load all the .RData files for Dakota County
+# Grab the Noise coefficients for the optimal bandwith in the given model output
+# plot the Noise coefficients for the three paired specifications (with beds/baths/garagesqft vs. without)
+
+setwd("~/NoiseHedonicProject/Noise-Hedonic/") #assume I'm in the project default working directory "Noise Hedonic Project"
+require(foreign)
+source("helper/LWRfunctions.R")
+
+DATAFRAME = read.dbf("~/NoiseHedonicProject/Data/R2GIS/CleanData/Sales20052010.dbf")
+obs2run = which(DATAFRAME$COUNTY_ID == "037" & DATAFRAME$BEDS > 0 &  DATAFRAME$BATH > 0 & DATAFRAME$GARSQFT>0 & DATAFRAME$TimePeriod>11)
+
+dataPath = "../Data/R2GIS/CleanData/Dakota/"
+filelist = list.files(dataPath)
+files2open = filelist[which(substr(filelist, 1, 9) == "dakotaLWR")]
+
+numFiles = length(files2open)
+
+Noisecoeffs = matrix(NA, length(obs2run), numFiles)
+models = c()
+gcvs = matrix(NA, 12, numFiles)
+
+for (myFile in 1:numFiles) {
+  load(paste0(dataPath, files2open[myFile]))
+  models = c(models, MYMODEL)
+  gcvs[, myFile] = GCV(output$leverages, output$yhats, DATAFRAME$logSALE_VA[obs2run])
+  print(gcvs)
+  ks = colnames(output[[1]])
+  Noisecoeffs[, myFile] = output$beta.Air_Mean[, which.min(gcvs[, myFile])] #
+  #colnames(Noisecoeffs)[myFile] = paste0("Mod", myFile, ks[which.min(gcvs)])
+}
+
+Noisecoeffs.d = as.data.frame(Noisecoeffs)
+
+par(mfrow = c(3, 1))
+par(mar = c(4, 5, 4, 2))
+lm.structural = lm(V1 ~ V4, data = Noisecoeffs.d)
+plot(Noisecoeffs.d$V4, Noisecoeffs.d$V1, cex = .2, 
[…]

### 2014-06-23 reports/code/NoiseBetaOverTimeAnalysis.R

@@ -1,0 +1,49 @@
+
+getwd()
+LWRresults = read.dbf("../Data/R2GIS/CleanData/TimeLag12months/AirMean3LWRresults.dbf")
+DATAFRAME <- read.dbf("../Data/R2GIS/CleanData/Sales20052010.dbf")
+
+bigDATA = merge(LWRresults, DATAFRAME, sort= FALSE)
+
+bigDATA$CITY = relevel(bigDATA$CITY, "ST. PAUL")
+lm0 = lm(bnoise ~ TimePeriod, data = bigDATA)
+summary(lm0)
+lm02 = lm(bnoise ~ TimePeriod + I(TimePeriod^2), data = bigDATA)
+summary(lm02)
+lm1 = lm(bnoise ~ TimePeriod + CITY, data = bigDATA)
+summary(lm1)
+lm12 = lm(bnoise ~ TimePeriod + I(TimePeriod^2) + CITY, data = bigDATA)
+summary(lm12)
+
+lm0st = lm(bnoise ~ TimePeriod, data = bigDATA, subset = (CITY == "ST. PAUL"))
+summary(lm0st)
+lm02st = lm(bnoise ~ TimePeriod + I(TimePeriod^2), data = bigDATA, subset = (CITY == "ST. PAUL"))
+summary(lm02st)
+require(stargazer)
+
+indvarlabels = c("Months since Jan 2005", "(Months since Jan 2005)$^2$",
+                 "Constant")
+
+stargazer(lm0, lm02, lm1, lm12, lm0st, lm02st,
+          digits.extra = 4, digits = 4,
+          align = TRUE,
+          omit.stat=c("adj.rsq","ser","f"),
+          omit = c("CITY"),
+          omit.labels = c("City Fixed Effects"),
+          font.size = "scriptsize",
+          column.sep.width = "-1pt",
+          dep.var.labels = "Noise Beta",
+          covariate.labels = indvarlabels)
+
+
+require(graphics)
+smoothScatter(bigDATA$TimePeriod, bigDATA$bnoise)
+newdata = data.frame(TimePeriod = 1:72, CITY = "ST. PAUL")
+lines(1:72, predict(lm0, newdata), col = "red")
+lines(1:72, predict(lm02, newdata), col = "red")
+lines(1:72, predict(lm1, newdata), col = "red")
+lines(1:72, predict(lm12, newdata), col = "red")
+
[…]

### 2014-06-23 reports/code/mainResultsTablesOld.R

@@ -1,10 +1,10 @@
 # Goal is to make a table of LWR results for the paper...
 
-# mega columns (for each bandwidth: 500, 650, 1000)
-# for each bandwidth 
+# columns
+# global model coefficients and se's
 # mean LWR Beta hats
-# 25th and 75th percentile of LWR beta hats
-
+# sd of LWR beta hats
+# monte carlo p-value
 
 # load the dataframe and helper functions
 require(foreign)
@@ -15,37 +15,10 @@ source("~/NoiseHedonicProject/Noise-Hedonic/helper/LWRfunctions.R")
 # load the LWR results
 # load the Monte Carlo Results
 ####################
-# Model 3
+# Kitchen Sink Model
 ####################
-load("~/NoiseHedonicProject/Data/R2GIS/CleanData/TimeLag12months/Sales20052010LWRmodelAirMean3-2014-03-19.RData")
-
-BWs = c("k500", "k650", "k1000")
-variableOrder = c(2:5, 16:24)
-names(output)[variableOrder]
-# [1] "beta.Air_Mean"   "beta.FIN_SQ_FT"  "beta.ACRES_POLY" "beta.YEAR_BUILT" "beta.OWNOCC"     "beta.PercWhite" 
-# [7] "beta.PercU18"    "beta.MED_INCOME" "beta.MCA3"       "beta.LAKE_dist"  "beta.PARK_dist"  "beta.SHOP_dist" 
-# [13] "beta.CBD_dist"
-unitsAdjuster = c(1, 1000, 1, 1, 1, 1, 1, 1000, 1, 1000, 1000, 1000, 1000)
-numvars = length(variableOrder)
-LWRtable = matrix(NA, numvars, 9)
-for (BW in 1:length(BWs)) {
-  for (i in 1:numvars) {
-    LWRtable[i, (BW-1)*3+1] = signif(mean(output[[variableOrder[i]]][,BWs[BW]]), 2)
-    LWRtable[i, (BW-1)*3+2:3] = signif(quantile(output[[variableOrder[i]]][,BWs[BW]], c(.1, .9)), 2)
-  }
-}
-
-niceTable = LWRtable*unitsAdjuster
-require(stargazer)
-varlabels = c("Noise (dB)", "House Size (1,000s ft2)", "Lot Size (acres)", "Year House Built",
-                 "Owner Occupancy Dummy", "Percent White", "Percent Under 18",
[…]

### 2014-07-02 reports/NoiseHedonicRaR.Rnw
nervous update

@@
 \usepackage{dcolumn}
+\usepackage{rotating}
+\usepackage{graphicx}
 \usepackage[nolists]{endfloat}
@@
 \begin{figure}
-\makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/StudyAreaSaleValueDist}}
-\caption{This figure shows the spatial extent of our study area as well as the significant spatial variation in single family house sales prices.}\label{fig:overview}
+\makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/Overview2column}}
+\caption{This figure shows the spatial extent of our study area, the significant spatial variation in single family house sales prices, as well as our noise data.}\label{fig:overview}
 \end{figure}
@@
 
-A map of our noise surface can be seen in Figure~???
+A map of our noise surface can be seen in Figure~\ref{fig:overview}.
 Once the noise surface for the entire region was developed, we extracted the noise surface for the present study area by overlaying the housing parcel boundaries and calculating the mean noise level within the parcel.
@@
 However, most other variables have small or no differences across time.
-Additionally, univariate density plots of the variables over time also reveal no differences in the shape or spread of the distributions over time.\footnote{See Appendix A} For instance, it is not the case that after the recession the distribution ``hollowed out'' in the middle and became bimodal with many high- and low-priced houses selling with few mid-priced homes selling.
-Additionally, maps of the locations of sales transactions over time reveal no discernable patterns, either.
-The geographic dispersion of sales in earlier years look surprisingly similar to those in later years.
-Thus, we can find no evidence of only certain types or locations of houses transacting in later years compared to earlier years in our data.
 
@@
 
-[Map of sales prices over time about here]
+We also created univariate density plots of the variables over time to check for differences in the shape or spread of the distributions over time (see Figure~\ref{fig:DensityPlots}).
+It is not the case that after the recession the distribution ``hollowed out'' in the middle and became bimodal with many high- and low-priced houses selling with few mid-priced homes selling.
+Additionally, maps of the locations of sales transactions over time reveal no discernable patterns, either (see Figure~\ref{fig:SalesYear}).
+The geographic dispersion of sales in earlier years looks surprisingly similar to that of later years.
+Thus, we can find no evidence of only certain types or locations of houses transacting in later years compared to earlier years in our data.
+
+\begin{figure}
+\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/DensityPlotsByYear}}
+\caption{This figure shows }\label{fig:DensityPlots}
+\end{figure}
+
+\begin{figure}
+\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/SaleValue_with05}}
+\caption{This figure shows }\label{fig:SalesYear}
+\end{figure}
 
@@
 
-We first conduct a Monte Carlo simulation recommended in \citet{Fotheringham2002} to see if the improved model fit with our LWR model was due to random chance.
+We first conducted a Monte Carlo simulation recommended in \citet{Fotheringham2002} to see if the improved model fit with our LWR model was due to random chance.
 The intuition of the test is as follows - if the improved model fit isn't significant, then we should be able to see similar improvements in model fit by using the LWR model with the same houses but in a different spatial arrangement.
@@
 
-\subsection{Does the Implicit Price of Traffic Noise Change over Space?}
-In the previous simulation we found that the hedonic regression function seems to exhibit spatial non-stationarity.
+\subsection{Which Coefficients Vary over Space?}
+
+The previous section presented evidence in support of the claim that there exists significant spatial variation in the hedonic function.
 However, we have not yet established which variables have spatially varying coefficients.
-In the second simulation, we seek to explore which of the hedonic regression coefficients exhibit spatial non-stationarity.
+Figures~\ref{fig:AcreBetas} -- \ref{fig:NoiseBetas} show the spatial variation in the estimated LWR coefficients for three important variables, lot size, house size, and noise.
+For comparison, we present the results across four different levels of local analysis, ranging from LWR bandwidths of 500 nearest houses to the nearest 2,000 sales.
 
+A few patterns are clear in Figures~\ref{fig:AcreBetas} -- \ref{fig:NoiseBetas}.
+For instance, across all four bandwidths we see that the hedonic\footnote{Remember that the dependent variable is the log of sales price.} coefficient on lot size (measured in acres) is largest near the central business district of St.\ Paul.
+Thus, consistent with standard urban economic theory, to the extent that the hedonic coefficient is correlated with the price of land, our results suggest the price of land is highest near the central business district and declines with distance from the CBD.
+This tendency is consistent across the four different bandwidths presented (other specific results available upon request).
+The LWR coefficients on house size (measured in thousands of square feet of finished space) also seem to exhibit spatial variation across the different bandwidths.
+In the west-central portion of our study area (a collection of notably desirable neighborhoods) we see a cluster of large LWR coefficients, while those areas in the southernmost portion of our region (suburban areas) have the smallest coefficients.
+
+In Figure~\ref{fig:NoiseBetas} we map the estimated LWR noise coefficients from four different bandwidths.
+In this figure the red areas represent large negative coefficients, while yellow areas are characterized by values closer to zero.
+It is interesting to note that for the smaller bandwidths, the area with the most negative noise coefficients is ringed by some of the coefficients closest to zero (and even greater than zero in some cases).
+As the bandwidth increases to 1000 or 2000 nearest houses, the variation in noise coefficients decreases substantially.
+In contrast to the previous two figures, we have largely eliminated the ``hot spots'' that appear in the smaller bandwidths.
+
+\begin{figure}
+ \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/AcreBeta_allBandwidth}}
+ \caption{Simula.}\label{fig:AcreBetas}
+\end{figure}
+
+\begin{figure}
+ \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/FinSqFtBeta_allBandwidth}}
+ \caption{Simula.}\label{fig:HouseBetas}
+\end{figure}
+
+\begin{figure}
+ \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/NoiseBeta_allBandwidth}}
+ \caption{Simula.}\label{fig:NoiseBetas}
+\end{figure}
+
+We now conduct a second series of simulation experiments aimed at testing whether the spatial variation exhibited in particular coefficients is significant or due to random chance.
 The mechanics of the second simulation are very similar to the those described in the previous section.
-We will randomly change the spatial arrangment of our house sales and estimate the LWR model.
-However, this simulation we will restrict the model to small bandwidths and compare the spread of the regression coefficient estimates under the random arrangment of the data to the spread found in our original LWR models with the actual spatial arrangement.
+We randomly change the spatial arrangment of our house sales and estimate the LWR model.
+However, in this simulation we restrict the model to small bandwidths and compare the spread of the regression coefficient estimates under the random arrangment of the data to the spread found in our original LWR models with the actual spatial arrangement.
 If an independent variable in our hedonic regression function exhibits a stationary relationship with sales prices, then we should see similar levels of dispersion in the randomly arranged data as in our true data.
@@
 
-[Insert maps showing the spatial variation in the most important regression coefficients]
-
-\subsection{Does the Implicit Price of Traffic Noise Change over Time?}
+\subsection{Does the Noise Coefficient Change over Time?}
 
@@
 
-In this section we look for patterns in our noise coefficients over time.
-We find evidence consistent with the estimated noise coefficients being more negative in the later time periods (housing bust) of our study than in the earlier periods (housing boom).
+Figures~\ref{fig:AcreTime}--\ref{fig:NoiseTime} show the spatial distribution of some our LWR hedonic coefficients for bandwidths of 500 and 2,000 nearest sales within the last year for the sale years 2006--2010.
+Regardless of bandwidth, the figures show that the estimated LWR coefficients are different over time.
+In particular, the lot size and house size coefficients tend to decrease over time.
+What is surprising, however, is that the negative noise coefficient estimates tend to be more negative in later years of our study.
+Figure~\ref{fig:NoiseTime} shows that the spatial patterns are similar across years (the most negative coefficients tend to be in the same locations across years), but the average noise coefficient tends to be more negative for the later years.
+
+\begin{sidewaysfigure}
+ \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/Acre_50_200_ByYear}
+ \caption{Simula.}
+ \label{fig:AcreTime}
+\end{sidewaysfigure}
+
+\begin{sidewaysfigure}
+ \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/FinFt_50_200_ByYear}
+ \caption{Simula.}
+ \label{fig:HouseTime}
+\end{sidewaysfigure}
+
+\begin{sidewaysfigure}
+ \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/Noise_50_200_ByYear}
+ \caption{Simula.}
+ \label{fig:NoiseTime}
+\end{sidewaysfigure}
+
+We also find statistical evidence consistent with the estimated noise coefficients being more negative in the later time periods.
 This finding is robust to multiple different formulations and specifications.
-Table~\ref{tab:noisebetatime} presents the results of regressions using our estimated LWR noise coefficient as the dependent variable and time and spatial characteristics as explanatory variables.
+Tables~\ref{tab:noisebetatime500} and \ref{tab:noisebetatime2000} present the results of regressions using our estimated LWR noise coefficient as the dependent variable and time and spatial characteristics as explanatory variables for LWR bandwidths of 500 and 2,000 nearest sales.
 
+Both tables are structured similarly.
 Column (1) finds evidence of a negative linear trend in the LWR noise coefficients over time - predicting a LWR noise coefficient of approximately twice the magnitude for the end of our study period as for the beginning.
@@
 \begin{table}[!htbp] \centering 
-  \caption{LWR Noise Coefficient Over Time} 
-  \label{tab:noisebetatime} 
+  \label{tab:noisebetatime500} 
 \scriptsize 
@@
 \hline \\[-1.8ex] 
- & \multicolumn{6}{c}{\textit{Dependent variable: LWR Noise Coefficient}} \\ 
+ & \multicolumn{6}{c}{\textit{Dependent variable: LWR Noise Coefficients (bandwidth = 500 nearest sales)}} \\ 
 \cline{2-7} 
@@
 \hline \\[-1.8ex] 
- Months since Jan 2005 & -0.00005^{***} & 0.00004^{***} & -0.00005^{***} & 0.00004^{***} & -0.0001^{***} & 0.0001^{***} \\ 
-  & (0.000001) & (0.000003) & (0.000001) & (0.000003) & (0.000001) & (0.00001) \\ 
+Months since Jan 2005 & -0.00005^{***} & 0.00003^{***} & -0.00005^{***} & 0.00003^{***} & -0.0001^{***} & 0.00004^{***} \\ 
+  & (0.000001) & (0.000004) & (0.000001) & (0.000004) & (0.000002) & (0.00001) \\ 
   & & & & & & \\ 
  (Months since Jan 2005)$^2$ &  & -0.000001^{***} &  & -0.000001^{***} &  & -0.000001^{***} \\ 
-  &  & (0.00000004) &  & (0.00000004) &  & (0.0000001) \\ 
+  &  & (0.00000005) &  & (0.00000004) &  & (0.0000001) \\ 
   & & & & & & \\ 
- Constant & -0.0016^{***} & -0.0029^{***} & -0.0021^{***} & -0.0034^{***} & -0.0016^{***} & -0.0035^{***} \\ 
-  & (0.00003) & (0.0001) & (0.00003) & (0.0001) & (0.0001) & (0.0001) \\ 
+ Constant & -0.0016^{***} & -0.0028^{***} & -0.0021^{***} & -0.0033^{***} & -0.0015^{***} & -0.0032^{***} \\ 
+  & (0.00003) & (0.0001) & (0.00003) & (0.0001) & (0.0001) & (0.0002) \\ 
   & & & & & & \\ 
@@
 Observations & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{8,003} & \multicolumn{1}{c}{8,003} \\ 
-R$^{2}$ & \multicolumn{1}{c}{0.1566} & \multicolumn{1}{c}{0.1722} & \multicolumn{1}{c}{0.3298} & \multicolumn{1}{c}{0.3446} & \multicolumn{1}{c}{0.1700} & \multicolumn{1}{c}{0.1915} \\ 
+R$^{2}$ & \multicolumn{1}{c}{0.1273} & \multicolumn{1}{c}{0.1377} & \multicolumn{1}{c}{0.2931} & \multicolumn{1}{c}{0.3028} & \multicolumn{1}{c}{0.1566} & \multicolumn{1}{c}{0.1704} \\ 
 \hline 
 \hline \\[-1.8ex]  
-\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 
+  \caption{LWR Noise Coefficient Over Time} 
 \end{table}
+
+% Requires LaTeX packages: dcolumn 
+\begin{sidewaystable}[!htbp] \centering 
+  \caption{LWR Noise Coefficient Over Time} 
+  \label{tab:noisebetatime2000} 
+\scriptsize 
+\begin{tabular}{@{\extracolsep{-1pt}}lD{.}{.}{6} D{.}{.}{7} D{.}{.}{7} D{.}{.}{7} D{.}{.}{7} D{.}{.}{7} } 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{6}{c}{\textit{LWR bandwidth = 2,000 nearest sales}} \\ 
+\cline{2-7} 
+\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)} & \multicolumn{1}{c}{(5)} & \multicolumn{1}{c}{(6)}\\ 
+\hline \\[-1.8ex] 
+Months since Jan 2005 & -0.00005^{***} & 0.00003^{***} & -0.00005^{***} & 0.00003^{***} & -0.00005^{***} & 0.0001^{***} \\ 
+  & (0.0000003) & (0.000002) & (0.0000003) & (0.000002) & (0.000001) & (0.000004) \\ 
+  & & & & & & \\ 
+ (Months since Jan 2005)$^2$ &  & -0.000001^{***} &  & -0.000001^{***} &  & -0.000001^{***} \\ 
+  &  & (0.00000002) &  & (0.00000002) &  & (0.0000001) \\ 
+  & & & & & & \\ 
+ Constant & -0.0014^{***} & -0.0026^{***} & -0.0016^{***} & -0.0028^{***} & -0.0016^{***} & -0.0033^{***} \\ 
+  & (0.00001) & (0.00003) & (0.00002) & (0.00003) & (0.00003) & (0.0001) \\ 
+  & & & & & & \\ 
+\hline \\[-1.8ex] 
+City Fixed Effects & \multicolumn{1}{c}{No} & \multicolumn{1}{c}{No} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{No} & \multicolumn{1}{c}{No} \\ 
+\hline \\[-1.8ex] 
+Observations & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{8,003} & \multicolumn{1}{c}{8,003} \\ 
+R$^{2}$ & \multicolumn{1}{c}{0.3828} & \multicolumn{1}{c}{0.4142} & \multicolumn{1}{c}{0.5128} & \multicolumn{1}{c}{0.5435} & \multicolumn{1}{c}{0.3454} & \multicolumn{1}{c}{0.3988} \\ 
+\hline 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{sidewaystable}
 
@@
 
-First and foremost, we need to be cautious about claims of causality.
-In an ideal research design, we would observe the same houses over time and randomly ``treat'' some houses with more or less noise to observe the change in price relative to the control houses.
+In a stronger research design, we would observe the same houses over time and randomly ``treat'' some houses with more or less noise to observe the change in price relative to the control houses.
 Such a study is not feasible and we are therefore limited to a hedonic analysis with observational data.
-Our conclusions, then, should be interpretted like most other hedonic analysis results and while we find a strong negative correlation between noise and house prices, stronger in some areas of our study area than others and stronger in some time periods than others, we cannot definitely state that noise causes lower sales prices.
+Our conclusions, then, should be interpretted like most other hedonic analysis results and, while we find a strong negative correlation between noise and house prices, we cannot definitely state that noise causes lower sales prices.
 
-Our work also faces data limitations.
+Future work may want to further investigate this correlation for more evidence consistent with causation.
+For instance, by collecting data on the quality of house windows one could test for differential effects of more soundproof windows in noisier areas vs.
+quieter areas.
+Unfortunately, such house characteristics are unavailable for this study.
+
+Our work faces other data limitations.
 Notably, while our house sales data are collected over the course of six years, the traffic noise estimates are for the year 2007.
@@
 However, given enough time for changes in driving habits and technological advancements to gain significant market penetration (for instance, quieter hybrid cars), future work should seek to create time-series noise data in order to obtain even better estimates of the impact of traffic noise over time.
-Given the computational complexity of re-estimating the landscape noise surface, such work is beyond the scope of this paper.
+Given the computational complexity of re-estimating the landscape noise surface, such work is beyond the scope of this paper, but may be a worthwhile investment for future work seeking to test the robustness of our results.
 

### 2014-07-02 reports/NoiseHedonicRaR.tex
nervous update

@@
 
-First and foremost, we need to be cautious about claims of causality.
-In an ideal research design, we would observe the same houses over time and randomly ``treat'' some houses with more or less noise to observe the change in price relative to the control houses.
+In a stronger research design, we would observe the same houses over time and randomly ``treat'' some houses with more or less noise to observe the change in price relative to the control houses.
 Such a study is not feasible and we are therefore limited to a hedonic analysis with observational data.
-Our conclusions, then, should be interpretted like most other hedonic analysis results and while we find a strong negative correlation between noise and house prices, stronger in some areas of our study area than others and stronger in some time periods than others, we cannot definitely state that noise causes lower sales prices.
+Our conclusions, then, should be interpretted like most other hedonic analysis results and, while we find a strong negative correlation between noise and house prices, we cannot definitely state that noise causes lower sales prices.
 
-Our work also faces some serious data limitations.
+Future work may want to further investigate this correlation for more evidence consistent with causation.
+For instance, by collecting data on the quality of house windows one could test for differential effects of more soundproof windows in noisier areas vs.
+quieter areas.
+Unfortunately, such house characteristics are unavailable for this study.
+
+Our work faces other data limitations.
 Notably, while our house sales data are collected over the course of six years, the traffic noise estimates are for the year 2007.

### 2014-07-02 analysis/00DescriptiveStats/DensityPlotsByYearMaker.R

@@ -5,14 +5,16 @@
 
 require(foreign)
 DATAFRAME = read.dbf("~/NoiseHedonicProject/Data/R2GIS/CleanData/Sales20052010.dbf")
+names(DATAFRAME)
+myvars = c("SALE_VALUE", "Air_Mean", "FIN_SQ_FT", "ACRES_POLY", "YEAR_BUILT",  
+           "MED_INCOME", "MCA3", "PercWhite", "PercU18", 
+           "CBD_dist", "PARK_dist", "LAKE_dist", "SHOP_dist")
 
-myvars = c("SALE_VALUE", "FIN_SQ_FT", "ACRES_POLY", "OWNOCC", "YEAR_BUILT", "MAX", 
-           "MED_INCOME", "MCA3", "CBD_dist", "PARK_dist", "LAKE_dist", "SHOP_dist")
-
-mynames = c("Sale Price (thousands)", "House Size (thousands square feet)", "Lot Size (acres)", "Owner Occupancy Dummy",
-            "Year House was Built", "Traffic Noise (dB)", "Median Income in Census Tract (thousands)", 
-            "Elementary Test Scores", "Distance to Central Business District (km)",
-            "Distance to nearest Park (km)", "Distance to nearest Lake (km)", "Distance to nearest Shopping Center (km)")
+mynames = c("Sale Price", "Noise", "House Size", "Lot Size", "Year Built",
+            "Median Income in Census Tract", "Elementary Test Scores", 
+            "Percent of Census Block Race = White", "Percent of Census Block Under Age 18",
+            "Distance to Central Business District", "Distance to nearest Park", 
+            "Distance to nearest Lake", "Distance to nearest Shopping Center")
 
 
 require("sm")
@@ -22,11 +24,20 @@ my.col = brewer.pal(6, "Set2")
 year.f = factor(DATAFRAME$SALE_YR)
 table(year.f)
 
-pdf("graphs/DensityPlotsByYear.pdf", width = 8, height = 8)
-for (i in myvars) {
-  sm.density.compare(DATAFRAME[, as.character(i)], year.f, 
+pdf("graphs/DensityPlotsByYear.pdf", width = 9, height = 15)
+par(mfrow = c(5, 3))
+par(oma = c(1, 1, 3, 1))
+par(mar = c(3, 4, 3, 1))
+plot(0, 0, type = "n", ylab = "", xlab = "", axes = F)
[…]

### 2014-07-02 analysis/04MonteCarloSim/MonteCarloScript2AssesSpatialNonStationarity.R

@@ -12,20 +12,20 @@ myVars = c("Air_Mean", "FIN_SQ_FT", "ACRES_POLY", "YEAR_BUILT", "OWNOCC", "MED_I
 RHS = paste(myVars, collapse = "+")
 MYMODEL = paste("logSALE_VA", RHS, sep = "~")
 MYMODELsmall = substr(MYMODEL, 1, nchar(MYMODEL)-5)
-KVECTOR = c(1000) # c(200, 400, 650, 1000, 2000, 4000)
+KVECTOR = c(2000) # c(200, 400, 650, 1000, 2000, 4000)
 
 # How many times am I going to reshuffle?
-iterations = 50 #100
+iterations = 100
 # How many things am I keeping track of each reshuffle? 
 # mean and sd of each coefficient i care about + intercept + GCV score + min bandwidth
 vars2keep = c("Intercept", myVars[c(1:(length(myVars)-3))])
 numMCstats = 2 + 2*length(vars2keep)
-MCstats = matrix(NA, 100, numMCstats)
-colnames(MCstats) = c("minGCV", "optimalBandwidth", 
-                      paste0("meanBeta.", vars2keep),
-                      paste0("sterBeta.", vars2keep))
-# mcstats = read.csv("analysis/04MonteCarloSim/Revision/Model3/CopyOfLWRMonteCarloStats2014-06-20.csv")
-# MCstats = as.matrix(mcstats)
+# MCstats = matrix(NA, 100, numMCstats)
+# colnames(MCstats) = c("minGCV", "optimalBandwidth", 
+#                       paste0("meanBeta.", vars2keep),
+#                       paste0("sterBeta.", vars2keep))
+mcstats = read.csv("analysis/04MonteCarloSim/Revision/Model3/k2000/CopyOfLWRMonteCarloStats2014-06-29.csv")
+MCstats = as.matrix(mcstats)
 
 filePrefix = "../Data/R2GIS/CleanData/"
 inputFile = "Sales20052010.dbf"
@@ -33,7 +33,7 @@ DATAFRAME = read.dbf(paste0(filePrefix, inputFile))
 simDATA = DATAFRAME
 N = dim(simDATA)[1]
 obs2run = which(simDATA$TimePeriod>11)
-for (iter in 1:iterations) {
+for (iter in 51:iterations) {
   # Do a reshuffle
   rowShuffle = sample(1:N)
   simDATA[, c("Long_X", "Lat_Y")] = DATAFRAME[rowShuffle, c("Long_X", "Lat_Y")]

### 2014-07-02 analysis/04MonteCarloSim/Revision/MCsimVisualizer.R

@@ -12,12 +12,12 @@ load("../Data/R2GIS/CleanData/TimeLag12months/Sales20052010LWRmodelAirMean3-2014
 # LWRMonteCarloStats2014.03.29 <- read.csv("~/NoiseHedonicProject/Noise-Hedonic/analysis/04MonteCarloSim/Revision/Model3/LWRMonteCarloStats2014-03-29.csv")
 # LWRMonteCarloStats2014.04.18 <- read.csv("~/NoiseHedonicProject/Noise-Hedonic/analysis/04MonteCarloSim/Revision/Model3/LWRMonteCarloStats2014-04-18.csv")
 # MCMaster <- rbind(LWRMonteCarloStats2014.03.29, LWRMonteCarloStats2014.04.18)
-MCMaster = read.csv("~/NoiseHedonicProject/Noise-Hedonic/analysis/04MonteCarloSim/Revision/Model3/LWRMonteCarloStats2014-06-20.csv")
-MCMaster = MCMaster[1:40,]
+MCMaster = read.csv("~/NoiseHedonicProject/Noise-Hedonic/analysis/04MonteCarloSim/Revision/Model3/k2000/LWRMonteCarloStats2014-06-29.csv")
+MCMaster = MCMaster[1:50,]
 
 MCplotter = function(outputcoefficient, statcoefficient, meanORsd = "mean") {
-  if (meanORsd == "mean") actual = mean(output[[outputcoefficient]][, "k500"], na.rm =T)
-  if (meanORsd == "sd")   actual = sd(output[[outputcoefficient]][, "k500"], na.rm =T)
+  if (meanORsd == "mean") actual = mean(output[[outputcoefficient]][, "k2000"], na.rm =T)
+  if (meanORsd == "sd")   actual = sd(output[[outputcoefficient]][, "k2000"], na.rm =T)
   
   temp = density(MCMaster[, statcoefficient])
   plot(temp, 
@@ -33,7 +33,7 @@ outputCOEFS = rep(names(output)[c(1:5, 16, 19, 20, 21, 22, 23, 24, 17, 18)], 2)
 statCOEFS = names(MCMaster)[3:30]
 meanORsds = rep(c("mean", "sd"), c(14, 14))
 
-pdf("analysis/04MonteCarloSim/Revision/MCsimResultsk500.pdf", height = 6, width = 24)
[…]

### 2014-07-02 analysis/SandboxAaron/aaronSandbox.R

@@ -37,6 +37,16 @@ data2xport$sefinft50 = output$ses.FIN_SQ_FT[,"k500"]
 data2xport$seacres50 = output$ses.ACRES_POLY[,"k500"]
 data2xport$yhats50 = output$yhats[, "k500"]
 
+data2xport$bnoise100 = output$beta.Air_Mean[,"k1000"]
+data2xport$bfinft100 = output$beta.FIN_SQ_FT[,"k1000"]
+data2xport$bacres100 = output$beta.ACRES_POLY[,"k1000"]
+data2xport$yhats100 = output$yhats[, "k1000"]
+
+data2xport$bnoise200 = output$beta.Air_Mean[,"k2000"]
+data2xport$bfinft200 = output$beta.FIN_SQ_FT[,"k2000"]
+data2xport$bacres200 = output$beta.ACRES_POLY[,"k2000"]
+data2xport$yhats200 = output$yhats[, "k2000"]
+
 require(foreign)
 DATAFRAME = read.dbf("../Data/R2GIS/CleanData/Sales20052010.dbf")
 obs2run = which(DATAFRAME$TimePeriod>11)

### 2014-07-02 reports/code/GlobalRegression.R

@@ -18,23 +18,29 @@ ModelBig = paste0(myModel, "+ CITY")
 lm.big = lm(ModelBig, data = workingdata20052010)#, subset = (SALE_YR == 2010))
 #summary(lm.big)
 
-ModelMonsterLot = paste0(myModel, "+ CITY*ACRES_POLY")
+ModelMonsterLot = paste0(ModelBig, "+ CITY*ACRES_POLY")
 lm.monsterLot = lm(ModelMonsterLot, data = workingdata20052010)#, subset = (SALE_YR == 2010))
 #summary(lm.monsterLot)
 # F test of ModelMonster vs. ModelBig
 anova(lm.monsterLot, lm.big)
 
-ModelMonsterSqft = paste0(myModel, "+ CITY*FIN_SQ_FT")
+ModelMonsterSqft = paste0(ModelBig, "+ CITY*FIN_SQ_FT")
 lm.monsterSqft = lm(ModelMonsterSqft, data = workingdata20052010)#, subset = (SALE_YR == 2010))
 #summary(lm.monsterSqft)
 anova(lm.monsterSqft, lm.big)
 
-ModelMonsterNoise = paste0(myModel, "+ CITY*Air_Mean")
+ModelMonsterNoise = paste0(ModelBig, "+ CITY*Air_Mean")
 lm.monsterNoise = lm(ModelMonsterNoise, data = workingdata20052010)#, subset = (SALE_YR == 2010))
 #summary(lm.monsterNoise)
 anova(lm.monsterNoise, lm.big)
 
-ModelMonster = paste0(myModel, "+ CITY*ACRES_POLY + CITY*FIN_SQ_FT + CITY*Air_Mean")
+ModelMonsterBuilt = paste0(ModelBig, "+ Air_Mean*YEAR_BUILT")
+lm.monsterBuilt = lm(ModelMonsterBuilt, data = workingdata20052010)
+summary(lm.monsterBuilt)
+anova(lm.monsterBuilt, lm.big)
+
+
+ModelMonster = paste0(ModelBig, "+ CITY*ACRES_POLY + CITY*FIN_SQ_FT + CITY*Air_Mean")
 lm.monster = lm(ModelMonster, data = workingdata20052010)#, subset = (SALE_YR == 2010))
 #summary(lm.monster)
 anova(lm.big, lm.monster)

### 2014-07-02 reports/code/NoiseBetaOverTimeAnalysis.R

@@ -6,25 +6,43 @@ DATAFRAME <- read.dbf("../Data/R2GIS/CleanData/Sales20052010.dbf")
 bigDATA = merge(LWRresults, DATAFRAME, sort= FALSE)
 
 bigDATA$CITY = relevel(bigDATA$CITY, "ST. PAUL")
-lm0 = lm(bnoise ~ TimePeriod, data = bigDATA)
-summary(lm0)
-lm02 = lm(bnoise ~ TimePeriod + I(TimePeriod^2), data = bigDATA)
-summary(lm02)
-lm1 = lm(bnoise ~ TimePeriod + CITY, data = bigDATA)
-summary(lm1)
-lm12 = lm(bnoise ~ TimePeriod + I(TimePeriod^2) + CITY, data = bigDATA)
-summary(lm12)
 
-lm0st = lm(bnoise ~ TimePeriod, data = bigDATA, subset = (CITY == "ST. PAUL"))
-summary(lm0st)
-lm02st = lm(bnoise ~ TimePeriod + I(TimePeriod^2), data = bigDATA, subset = (CITY == "ST. PAUL"))
-summary(lm02st)
+# 500 bandwidth
+lm0.50 = lm(bnoise50 ~ TimePeriod, data = bigDATA)
+#summary(lm0.50)
+lm02.50 = lm(bnoise50 ~ TimePeriod + I(TimePeriod^2), data = bigDATA)
+#summary(lm02.50)
+lm1.50 = lm(bnoise50 ~ TimePeriod + CITY, data = bigDATA)
+#summary(lm1.50)
+lm12.50 = lm(bnoise50 ~ TimePeriod + I(TimePeriod^2) + CITY, data = bigDATA)
+#summary(lm12.50)
+
+lm0st.50 = lm(bnoise50 ~ TimePeriod, data = bigDATA, subset = (CITY == "ST. PAUL"))
+#summary(lm0st.50)
+lm02st.50 = lm(bnoise50 ~ TimePeriod + I(TimePeriod^2), data = bigDATA, subset = (CITY == "ST. PAUL"))
+#summary(lm02st.50)
+
+# 2000 bandwidth
+lm0.200 = lm(bnoise200 ~ TimePeriod, data = bigDATA)
+summary(lm0.200)
+lm02.200 = lm(bnoise200 ~ TimePeriod + I(TimePeriod^2), data = bigDATA)
+summary(lm02.200)
[…]

### 2014-07-07 reports/NoiseHedonicRaR.Rnw
added GCVsFromMCSim figure, added captions to remaining figures in paper

@@
 \makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/Overview2column}}
-\caption{This figure shows the spatial extent of our study area, the significant spatial variation in single family house sales prices, as well as our noise data.}\label{fig:overview}
+\caption{This figure shows the spatial extent of our study area, the significant spatial variation in single family house sales prices, as well as our noise data.}
+\label{fig:overview}
 \end{figure}
@@
 \begin{table}
-\caption{Variable Description and Summary Statistics}\label{tab:sumStats}
+\caption{Variable Description and Summary Statistics}
+\label{tab:sumStats}
 \makebox[\linewidth][c]{
@@
   Year House was Built & 1850 & 1950 & 1973 & 1967 & 1993 & 2010 & 32 \\ 
-  House Size (square feet) & 390 & 1158 & 1628 & 1750 & 2189 & 4000 & 704 \\ 
+  House Size (ft$^2$) & 390 & 1158 & 1628 & 1750 & 2189 & 4000 & 704 \\ 
   Lot Size (acres) & 0.02 & 0.17 & 0.25 & 0.25 & 0.31 & 0.60 & 0.11 \\ 
@@
 \caption{Matrix of Pearson Correlation Coefficients for Quantitative Variables}\label{tab:cor}
-%\includegraphics[width = \textwidth]{../graphs/CorrelationMatrix}
 \begin{center}
@@
 \makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/DensityPlotsByYear}}
-\caption{This figure shows }\label{fig:DensityPlots}
+\caption{This figure shows the distribution of our variables over time.
+Note that there are no discernable differences in mean, standard deviation, or shape of the distribution for most variables other than sales price.}
+\label{fig:DensityPlots}
 \end{figure}
@@
 \makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/SaleValue_with05}}
-\caption{This figure shows }\label{fig:SalesYear}
+\caption{This figure shows the spatial distribution of observed sales prices over time.
+The change in color from 2005 to 2010 denotes the dramatic drop in sales prices associated with the recession of 2008-09.
+There are clear spatial patterns in  house prices that persist over time (locations with relatively high vs.
+low prices in one year tend to be the same in other years).
+However, we see no evidence that sales shifted from one area of our study region to another (neighborhoods with many sales in 2005 also tend to have many sales in 2010).
+}
+\label{fig:SalesYear}
 \end{figure}
@@
 
-%Table \ref{tab:LWR} summarizes the results of LWR Model (3) at three different bandwidth sizes plus the same model estimated at the ``global'' level.
-run without allowing for spatial variation in the regression coefficients.
-Again, note that the LWR model yields a substantially smaller GCV score (0.027 vs.\ 0.038) signifying a substantial improvement in model performance.
-In addition to the significant reduction in the GCV score obtained with the use of LWR, we also see a substantial reduction in the degree of spatial autocorrelation in the model residuals.
-We calculate Moran's I statistic to be 0.199 for the global model while our preferred LWR specification yields 0.012, a more than ten-fold reduction.
+% % Table created by stargazer v.5.1 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% % Date and time: Sat, Jun 21, 2014 - 10:37:00 AM
+% % Requires LaTeX packages: dcolumn 
+% \begin{table}[!htbp]
+%   \caption{LWR Results: Dependent Variable = ln(Sales Price)} 
+%   \label{tab:LWR} 
+%   \makebox[\textwidth][c]{
+% \scriptsize
+%   \centering
+% \begin{tabular}{@{\extracolsep{-1pt}} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{-4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{-4} D{.}{.}{3} D{.}{.}{3} } 
+% \\[-1.8ex]\hline 
+% \hline \\[-1.8ex]
+%  & \multicolumn{3}{c}{Nearest 500 sales$^*$} & \multicolumn{3}{c}{Nearest 650 sales} & \multicolumn{3}{c}{Nearest 1000 sales} \\
+%  & \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$}  & 
+%  \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$}  & 
+%  \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$} \\
+%  \cline{2-4} \cline{8-10} \cline{5-7}
+% \multicolumn{1}{l}{Noise (dB)} & -0.0034 & -0.0064 & -0.0006 & -0.0034 & -0.0061 & -0.0009 & -0.0033 & -0.0057 & -0.0013 \\ 
+% \multicolumn{1}{l}{House Size (1,000s ft)} & 0.2700 & 0.1800 & 0.3900 & 0.2700 & 0.1900 & 0.3900 & 0.2700 & 0.2000 & 0.4000 \\ 
+% \multicolumn{1}{l}{Lot Size (acres)} & 0.4200 & 0.1700 & 0.7300 & 0.4200 & 0.1900 & 0.7100 & 0.4200 & 0.2100 & 0.6700 \\ 
+% \multicolumn{1}{l}{Year House Built} & 0.0046 & 0.0004 & 0.0100 & 0.0045 & 0.0005 & 0.0096 & 0.0043 & 0.0005 & 0.0090 \\ 
+% \multicolumn{1}{l}{Owner Occupancy} & 0.0230 & -0.0290 & 0.0800 & 0.0240 & -0.0240 & 0.0760 & 0.0230 & -0.0180 & 0.0680 \\ 
+% \multicolumn{1}{l}{Percent White} & 0.0012 & -0.0003 & 0.0029 & 0.0013 & -0.0001 & 0.0028 & 0.0014 & 0.0001 & 0.0028 \\ 
+% \multicolumn{1}{l}{Percent Under 18} & 0.0005 & -0.0016 & 0.0025 & 0.0004 & -0.0014 & 0.0022 & 0.0004 & -0.0011 & 0.0019 \\ 
+% \multicolumn{1}{l}{Median Income (\$1,000s)} & 0.0007 & -0.0014 & 0.0033 & 0.0008 & -0.0010 & 0.0033 & 0.0010 & -0.0006 & 0.0037 \\ 
+% \multicolumn{1}{l}{Elementary Test Scores} & 0.0000 & -0.0056 & 0.0055 & 0.0001 & -0.0050 & 0.0049 & 0.0003 & -0.0040 & 0.0042 \\ 
+% \multicolumn{1}{l}{Dist to Lake (km)} & -0.0150 & -0.0910 & 0.0580 & -0.0110 & -0.0770 & 0.0550 & -0.0076 & -0.0630 & 0.0520 \\ 
+% \multicolumn{1}{l}{Dist to Park (km)} & -0.0110 & -0.0600 & 0.0330 & -0.0110 & -0.0490 & 0.0250 & -0.0085 & -0.0370 & 0.0160 \\ 
+% \multicolumn{1}{l}{Dist to Shop (km)} & 0.0092 & -0.0330 & 0.0520 & 0.0096 & -0.0270 & 0.0470 & 0.0100 & -0.0210 & 0.0440 \\ 
+% \multicolumn{1}{l}{Dist to CBD (km)} & 0.0084 & -0.0190 & 0.0440 & 0.0094 & -0.0140 & 0.0400 & 0.0100 & -0.0099 & 0.0380 \\ 
+% \hline \\[-1.8ex] 
+% \multicolumn{10}{p{6 in}}{$^*$ A bandwidth of 500 implies that the nearest 500 houses sold within the past 12 months are included.} \\
+% \multicolumn{10}{p{6 in}}{Note: Each model also includes a categorical variable for architectural style, month*year fixed effects, and city-level fixed effects. }
+% 
+% \end{tabular} 
+% }
+% \end{table}
 
 % Table created by stargazer v.5.1 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Sat, Jun 21, 2014 - 10:37:00 AM
+% Date and time: Sat, Jul 05, 2014 - 09:41:55 PM
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp]   
-  \caption{LWR Results: Dependent Variable = ln(Sales Price)} 
+  \caption{\mbox{LWR Coefficient Mean and (10$^{th}$ to 90$^{th}$ Percentile) Values for Selected Bandwidths} }
   \label{tab:LWR} 
@@
   \centering
-\begin{tabular}{@{\extracolsep{-1pt}} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{-4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{-4} D{.}{.}{3} D{.}{.}{3} } 
+\begin{tabular}{@{\extracolsep{-1pt}} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} } 
 \\[-1.8ex]\hline 
 \hline \\[-1.8ex] 
- & \multicolumn{3}{c}{Nearest 500 sales$^*$} & \multicolumn{3}{c}{Nearest 650 sales} & \multicolumn{3}{c}{Nearest 1000 sales} \\
- & \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$}  & 
- \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$}  & 
- \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$} \\
- \cline{2-4} \cline{8-10} \cline{5-7}
-\multicolumn{1}{l}{Noise (dB)} & -0.0034 & -0.0064 & -0.0006 & -0.0034 & -0.0061 & -0.0009 & -0.0033 & -0.0057 & -0.0013 \\ 
-\multicolumn{1}{l}{House Size (1,000s ft)} & 0.2700 & 0.1800 & 0.3900 & 0.2700 & 0.1900 & 0.3900 & 0.2700 & 0.2000 & 0.4000 \\ 
-\multicolumn{1}{l}{Lot Size (acres)} & 0.4200 & 0.1700 & 0.7300 & 0.4200 & 0.1900 & 0.7100 & 0.4200 & 0.2100 & 0.6700 \\ 
-\multicolumn{1}{l}{Year House Built} & 0.0046 & 0.0004 & 0.0100 & 0.0045 & 0.0005 & 0.0096 & 0.0043 & 0.0005 & 0.0090 \\ 
-\multicolumn{1}{l}{Owner Occupancy} & 0.0230 & -0.0290 & 0.0800 & 0.0240 & -0.0240 & 0.0760 & 0.0230 & -0.0180 & 0.0680 \\ 
-\multicolumn{1}{l}{Percent White} & 0.0012 & -0.0003 & 0.0029 & 0.0013 & -0.0001 & 0.0028 & 0.0014 & 0.0001 & 0.0028 \\ 
-\multicolumn{1}{l}{Percent Under 18} & 0.0005 & -0.0016 & 0.0025 & 0.0004 & -0.0014 & 0.0022 & 0.0004 & -0.0011 & 0.0019 \\ 
-\multicolumn{1}{l}{Median Income (\$1,000s)} & 0.0007 & -0.0014 & 0.0033 & 0.0008 & -0.0010 & 0.0033 & 0.0010 & -0.0006 & 0.0037 \\ 
-\multicolumn{1}{l}{Elementary Test Scores} & 0.0000 & -0.0056 & 0.0055 & 0.0001 & -0.0050 & 0.0049 & 0.0003 & -0.0040 & 0.0042 \\ 
-\multicolumn{1}{l}{Dist to Lake (km)} & -0.0150 & -0.0910 & 0.0580 & -0.0110 & -0.0770 & 0.0550 & -0.0076 & -0.0630 & 0.0520 \\ 
-\multicolumn{1}{l}{Dist to Park (km)} & -0.0110 & -0.0600 & 0.0330 & -0.0110 & -0.0490 & 0.0250 & -0.0085 & -0.0370 & 0.0160 \\ 
-\multicolumn{1}{l}{Dist to Shop (km)} & 0.0092 & -0.0330 & 0.0520 & 0.0096 & -0.0270 & 0.0470 & 0.0100 & -0.0210 & 0.0440 \\ 
-\multicolumn{1}{l}{Dist to CBD (km)} & 0.0084 & -0.0190 & 0.0440 & 0.0094 & -0.0140 & 0.0400 & 0.0100 & -0.0099 & 0.0380 \\ 
+& \multicolumn{4}{c}{Dependent Variable = ln(Sales Price)} \\ \\
+ & \multicolumn{1}{c}{Nearest 500$^*$ sales} & \multicolumn{1}{c}{Nearest 650 sales} & \multicolumn{1}{c}{Nearest 1,000 sales} & \multicolumn{1}{c}{Nearest 2,000 sales} \\ \hline \\
+\multicolumn{1}{l}{Noise (dB)} & \multicolumn{1}{c}{-0.0034} & \multicolumn{1}{c}{-0.0034} & \multicolumn{1}{c}{-0.0033} & \multicolumn{1}{c}{-0.0032} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.0064 to -0.0007)} & \multicolumn{1}{c}{(-0.0061 to -0.0009)} & \multicolumn{1}{c}{(-0.0057 to -0.0013)} & \multicolumn{1}{c}{(-0.0049 to -0.0017)} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
+\multicolumn{1}{l}{House Size (1,000s ft$^2$)} & \multicolumn{1}{c}{0.27} & \multicolumn{1}{c}{0.27} & \multicolumn{1}{c}{0.27} & \multicolumn{1}{c}{0.28} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.18 to 0.39)} & \multicolumn{1}{c}{(0.19 to 0.39)} & \multicolumn{1}{c}{(0.20 to 0.40)} & \multicolumn{1}{c}{(0.20 to 0.37)} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
+\multicolumn{1}{l}{Lot Size (acres)} & \multicolumn{1}{c}{0.42} & \multicolumn{1}{c}{0.42} & \multicolumn{1}{c}{0.42} & \multicolumn{1}{c}{0.40} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.17 to 0.73)} & \multicolumn{1}{c}{(0.19 to 0.71)} & \multicolumn{1}{c}{(0.21 to 0.67)} & \multicolumn{1}{c}{(0.25 to 0.58)} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
+\multicolumn{1}{l}{Year House Built} & \multicolumn{1}{c}{0.0046} & \multicolumn{1}{c}{0.0045} & \multicolumn{1}{c}{0.0043} & \multicolumn{1}{c}{0.0038} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{(0.0004 to 0.010)} & \multicolumn{1}{c}{(0.0005 to 0.0096)} & \multicolumn{1}{c}{(0.0005 to 0.0090)} & \multicolumn{1}{c}{(0.0004 to 0.0080)} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
+\multicolumn{1}{l}{Owner Occupancy} & \multicolumn{1}{c}{0.023} & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.023} & \multicolumn{1}{c}{0.021} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.029 to 0.080)} & \multicolumn{1}{c}{(-0.024 to 0.076)} & \multicolumn{1}{c}{(-0.018 to 0.068)} & \multicolumn{1}{c}{(-0.012 to 0.056)} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
+\multicolumn{1}{l}{Percent White} & \multicolumn{1}{c}{0.0012} & \multicolumn{1}{c}{0.0013} & \multicolumn{1}{c}{0.0014} & \multicolumn{1}{c}{0.0016} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.0003 to 0.0029)} & \multicolumn{1}{c}{(-0.0001 to 0.0028)} & \multicolumn{1}{c}{(0.0001 to 0.0028)} & \multicolumn{1}{c}{(0.0003 to 0.0032)} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
+\multicolumn{1}{l}{Percent Under Age 18} & \multicolumn{1}{c}{0.00047} & \multicolumn{1}{c}{0.00045} & \multicolumn{1}{c}{0.00040} & \multicolumn{1}{c}{0.00034} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.0016 to 0.0025)} & \multicolumn{1}{c}{(-0.0014 to 0.0022)} & \multicolumn{1}{c}{(-0.0011 to 0.0019)} & \multicolumn{1}{c}{(-0.0008 to 0.0015)} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
+\multicolumn{1}{l}{Median Income (\$1,000s)} & \multicolumn{1}{c}{0.0006} & \multicolumn{1}{c}{0.0008} & \multicolumn{1}{c}{0.0010} & \multicolumn{1}{c}{0.0014} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.0014 to 0.0033)} & \multicolumn{1}{c}{(-0.0010 to 0.0033)} & \multicolumn{1}{c}{(-0.0006 to 0.0037)} & \multicolumn{1}{c}{(-0.0002 to 0.0042)} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
+\multicolumn{1}{l}{Elementary Test Scores} & \multicolumn{1}{c}{-0.00002} & \multicolumn{1}{c}{0.00008} & \multicolumn{1}{c}{0.00029} & \multicolumn{1}{c}{0.00044} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.0056 to 0.0055)} & \multicolumn{1}{c}{(-0.0050 to 0.0049)} & \multicolumn{1}{c}{(-0.0040 to 0.0042)} & \multicolumn{1}{c}{(-0.0025 to 0.0037)} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
+\multicolumn{1}{l}{Distance to Lake (km)} & \multicolumn{1}{c}{-0.0150} & \multicolumn{1}{c}{-0.0110} & \multicolumn{1}{c}{-0.0076} & \multicolumn{1}{c}{-0.0051} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.091 to 0.058)} & \multicolumn{1}{c}{(-0.077 to 0.055)} & \multicolumn{1}{c}{(-0.063 to 0.052)} & \multicolumn{1}{c}{(-0.048 to 0.043)} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
+\multicolumn{1}{l}{Distance to Park (km)} & \multicolumn{1}{c}{-0.011} & \multicolumn{1}{c}{-0.011} & \multicolumn{1}{c}{-0.009} & \multicolumn{1}{c}{-0.002} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.060 to 0.033)} & \multicolumn{1}{c}{(-0.049 to 0.025)} & \multicolumn{1}{c}{(-0.037 to 0.016)} & \multicolumn{1}{c}{(-0.018 to 0.011)} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
+\multicolumn{1}{l}{Distance to Shop (km)} & \multicolumn{1}{c}{0.0092} & \multicolumn{1}{c}{0.0096} & \multicolumn{1}{c}{0.0100} & \multicolumn{1}{c}{0.0078} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.033 to 0.052)} & \multicolumn{1}{c}{(-0.027 to 0.047)} & \multicolumn{1}{c}{(-0.021 to 0.044)} & \multicolumn{1}{c}{(-0.014 to 0.036)} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\ 
+\multicolumn{1}{l}{Distance to CBD (km)} & \multicolumn{1}{c}{0.0084} & \multicolumn{1}{c}{0.0094} & \multicolumn{1}{c}{0.0100} & \multicolumn{1}{c}{0.0095} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{(-0.019 to 0.044)} & \multicolumn{1}{c}{(-0.014 to 0.040)} & \multicolumn{1}{c}{(-0.010 to 0.038)} & \multicolumn{1}{c}{(-0.005 to 0.037)} \\ 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
+
+\multicolumn{1}{l}{Home Style Fixed Effects} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} \\ 
+\multicolumn{1}{l}{Month*Year Fixed Effects} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} \\ 
+\multicolumn{1}{l}{City Fixed Effects} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} & \multicolumn{1}{c}{Yes} \\ 
 \hline \\[-1.8ex] 
-\multicolumn{10}{p{6 in}}{$^*$ A bandwidth of 500 implies that the nearest 500 houses sold within the past 12 months are included.} \\
-\multicolumn{10}{p{6 in}}{Note: Each model also includes a categorical variable for architectural style, month*year fixed effects, and city-level fixed effects. }
-
+\multicolumn{1}{l}{Observations} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} \\ 
+\multicolumn{1}{l}{GCV score} & \multicolumn{1}{c}{0.0271} & \multicolumn{1}{c}{0.0271} & \multicolumn{1}{c}{0.0274} & \multicolumn{1}{c}{0.0283} \\ 
+\multicolumn{1}{l}{Moran's I statistic$^{**}$} & \multicolumn{1}{c}{0.027} & \multicolumn{1}{c}{0.031} & \multicolumn{1}{c}{0.037} & \multicolumn{1}{c}{0.049} \\ \hline \hline
+\multicolumn{5}{p{5.5 in}}{$^*$ A bandwidth of 500 implies that the nearest 500 houses sold within the past 12 months are included.} \\
+\multicolumn{5}{p{5.5 in}}{$^{**}$ For comparison, the Moran's I statistic for Model A in Table~\ref{tab:globalRegression} is 0.188.} \\
 \end{tabular} 
@@
 
-Table~\ref{tab:LWR} shows the results for our LWR Model (3) with three different bandwidths: the GCV minimizing bandwidth of 500 nearest sales as well as two larger values, 650 and 1,000 nearest sales.
+Table~\ref{tab:LWR} shows the results for our LWR Model (3) with four different bandwidths: the GCV minimizing bandwidth of 500 nearest sales as well as three larger bandwidths: 650, 1,000, and 2,000 nearest sales.
 For each bandwidth, we display the mean LWR coefficient as well as the 10$^{th}$ and 90$^{th}$ percentile values.
-The mean LWR coefficient for the noise variable is similar across the three different bandwidths (approximately a third of a percent difference in house sales prices for each additional decibel of noise, all other varibles held constant).
+In addition to having smaller GCV scores than the global model, the LWR models substantially reduce the amount of spatial autocorrelation in our regression residuals (the Moran's I statistic for the global model is seven times larger than for the 500 nearest sales model).
+
+The mean LWR coefficient for the noise variable is similar across the different bandwidths (approximately a third of a percent difference in house sales prices for each additional decibel of noise, all other varibles held constant).
 Unsurprisingly, the spread of the coefficient distribution is greater for the smaller bandwidths.
 We now turn to investigating whether this increased dispersion appears from the stochastic nature of smaller sample sizes, or due to heterogeneity in the hedonic function.
-
-We believe the hedonic function varies significantly over space and time and that the use of a LWR estimation procedure is an appropriate and beneficial modeling strategy.
-In the next three subsections we describe the results of hypothesis tests that lead us to these conclusions.
+In the next three subsections we describe the results of hypothesis tests that lead us to believe that LWR modeling is an appropriate and beneficial research strategy.
 
@@
 
-We first conducted a Monte Carlo simulation recommended in \citet{Fotheringham2002} to see if the improved model fit with our LWR model was due to random chance.
+We first conducted a Monte Carlo simulation recommended in \citet{Fotheringham2002} to see if the improved model fit with our LWR models was due to random chance.
 The intuition of the test is as follows - if the improved model fit isn't significant, then we should be able to see similar improvements in model fit by using the LWR model with the same houses but in a different spatial arrangement.
@@
 
-We conducted 100 different experiments in which we randomly swapped the locations of our house transactions.
+We conducted 100 different experiments in which we randomly resampled (without replacement) the locations of our house transactions.
 In each case we then estimated the LWR model using 10 different bandwidths ranging from the nearest 100 to 4,000 sales just as before and calculated the GCV score.
-Every single time the smallest Generalized Cross-Validation score was obtained at the largest bandwidth.
+Figure~\ref{fig:GCVSIM} shows the distribution of the GCV scores we obtained for the simulated data for four selected bandwidths relative to the score we obtained with our actual data.
+Note that the GCV distributions for the simulated data a strongly related their bandwidth - smaller bandwidths have larger GCV scores.
+That is, with our randomized location data, the GCV score is inversely proportional to the bandwidth.
+Additionally, note that no GCV scores from the simulated data are near our GCV score with the actual data.
+In every single instance the smallest Generalized Cross-Validation score was obtained at the largest bandwidth.
 That is, in 100 consecutive opportunities to fit our data at a local level of a couple hundred nearest sales up to a couple thousand nearby sales, the GCV score was always smallest for the largest possible bandwidth.
@@
 This seems to be strong evidence that the increased ability to predict house prices with a local model is not due to chance and that there is spatial non-stationarity in the hedonic function.
+
+\begin{figure}
+ \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/GCVsFromMCsim}}
+ \caption{This figure shows the distribution of GCV scores obtained from simulations with spatially randomized data and the GCV score from our data.
+Each solid curve represents the smoothed density plot of 100 different instances of the simulation.
+The dashed line suggests that our actual minimum GCV score was not obtained by random chance as no other GCV scores come close.}
+ \label{fig:GCVSIM}
+\end{figure}
 
@@
 A few patterns are clear in Figures~\ref{fig:AcreBetas} -- \ref{fig:NoiseBetas}.
-For instance, across all four bandwidths we see that the hedonic\footnote{Remember that the dependent variable is the log of sales price.} coefficient on lot size (measured in acres) is largest near the central business district of St.\ Paul.
+For instance, across all four bandwidths we see that the hedonic coefficient\footnote{Remember that the dependent variable is the log of sales price.} on lot size (measured in acres) is largest near the central business district of St.\ Paul.
 Thus, consistent with standard urban economic theory, to the extent that the hedonic coefficient is correlated with the price of land, our results suggest the price of land is highest near the central business district and declines with distance from the CBD.
@@
  \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/AcreBeta_allBandwidth}}
- \caption{Simula.}\label{fig:AcreBetas}
+ \caption{This figure shows an interpolated surface (using Inverse Distance Weighting) for the estimated LWR coefficients (dependent variable = ln(sales price)) for the lot size variable (in acres) obtained across four different bandwidths: 500, 650, 1,000, and 2,000 nearest observations.
+In all cases there is a clear inverse relationship between the coefficient magnitudes and distance to the central business district.}
+ \label{fig:AcreBetas}
 \end{figure}
@@
  \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/FinSqFtBeta_allBandwidth}}
- \caption{Simula.}\label{fig:HouseBetas}
+ \caption{This figure shows an interpolated surface (using Inverse Distance Weighting) for the estimated LWR coefficients (dependent variable = ln(sales price)) for the finished house size variable (in 1,000s of square feet) obtained across four different bandwidths: 500, 650, 1,000, and 2,000 nearest observations.
+In all cases some of the highest coefficient values are in the west-central portion of our study area and the lowest coefficients tend to be in the far south.}
+ \label{fig:HouseBetas}
 \end{figure}
@@
  \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/NoiseBeta_allBandwidth}}
- \caption{Simula.}\label{fig:NoiseBetas}
+ \caption{This figure shows an interpolated surface (using Inverse Distance Weighting) for the estimated LWR coefficients (dependent variable = ln(sales price)) for the noise variable (in dB) obtained across four different bandwidths: 500, 650, 1,000, and 2,000 nearest observations.
+In all cases some of the most negative coefficient values are in the west-central portion of our study area with the smallest in magnitude coefficients tending to be near the central business district.}
+ \label{fig:NoiseBetas}
 \end{figure}
@@
 We randomly change the spatial arrangment of our house sales and estimate the LWR model.
-However, in this simulation we restrict the model to small bandwidths and compare the spread of the regression coefficient estimates under the random arrangment of the data to the spread found in our original LWR models with the actual spatial arrangement.
-If an independent variable in our hedonic regression function exhibits a stationary relationship with sales prices, then we should see similar levels of dispersion in the randomly arranged data as in our true data.
-However, if the dispersion we see in our random data is \emph{smaller} than the spread we observed in our actual data, that is evidence consistent with the variable having a non-stationary relationship.
-That is, the variation in regression coefficients obtained in our data is higher than we would observe from random chance.
+However, in this simulation we compare the \emph{spread} (rather than the degree of model fit) of the regression coefficient estimates under the random arrangment of the data to the spread found in our original LWR models with the actual spatial arrangement, conditional on bandwidth.
+If an explanatory variable in our hedonic regression function exhibits a stationary relationship with sales prices, then we should see similar levels of dispersion in the randomly arranged data as in our true data.
+However, if the dispersion we see in our randomized data is \emph{smaller} than the spread we observed in our actual data, that is evidence consistent with the variable having a non-stationary relationship.
+That is, the variation in regression coefficients obtained in our data is higher than we observe from random chance.
 
-We present the results of this simulation for the same three different bandwidths in Table~\ref{tab:LWR}- 500, 650, and 1,000 nearest observations.
-Figures~\ref{fig:MCsds500} and \ref{fig:MCsds500} visualize the results of the second simulation for different bandwidths.
-Each sub-figure displays the distribution of LWR coefficient standard deviations obtained from the 100 iterations of the Monte Carlo simulation and the standard deviation obtained with the actual data (in red).
-Note that it is the case that the standard deviations obtained with the actual data are typically substantially larger than those obtained in the simulation for most of the variables.
-However, the variation obtained in the noise coefficients simulations is not dissimilar to our actual LWR results, suggesting that the spatial non-stationarity exhibited in this coefficient is perhaps due to chance and not true spatial non-stationarity in the noise coefficient.
+We conducted this simulation 100 times for the same four different bandwidths in Table~\ref{tab:LWR}- 500, 650, 1,000 and 2,000 nearest observations.
+Across all bandwidths we obtain similar results, so for brevity's sake we present the results for the 500 and 2,000 bandwidth sizes\footnote{Additional results available on request.} in Figure~\ref{fig:MCsim2}.
+The solid red (blue) lines show the distribution of the coefficient standard deviations we obtained from the 100 simulations for the 2,000 (500) nearest sale bandwidths.
+Across all variables it is the case the the distribution of standard deviations is significantly larger for the smaller bandwidth.
+That is, when we use smaller bandwidths we tend to see greater dispersion in regression coefficients.
+We also plot the standard deviation of our coefficients from our actual data as vertical dashed lines (again, color denotes the bandwidth size (red=2,000 and blue=500).
+For most variables, the standard deviation of the LWR coefficients obtained with our actual data is significantly greater than any standard deviation obtained with the randomized simulated data.
+That is, across our simulated data we never saw anywhere near the level of dispersion in regression coefficients for house size, lot size, etc.
+that we observe with our actual data.
+This seems to be strong evidence that many of our regression coefficients in our hedonic function exhibit spatial non-stationarity.
+However, for some variables (note the distributions for noise, owner occupancy and percent under age 18) for which our observed spread in the LWR coefficients is similar when we used the simulated data.
+This simulation does not present evidence that these variables exhibit a non-stationary relationship in our hedonic function.
 
 \begin{figure}
- \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{../graphs/MCsimResultsSDs500}}
- \caption{Simulation Results for nearest 500 observations.
-Actual LWR Coefficient Standard Deviations \textcolor{red}{(red line)} vs.\ Distribution of Monte Carlo Simulation Standard Deviations by Variable.
-Figures in which the red line is to the right of the black distribution suggest spatial non-stationarity in effect of the variable on house prices in our study region.}\label{fig:MCsds500}
+ \makebox[\textwidth][c]{\includegraphics[height=.9\textheight]{../graphs/MCsimResultsSDsk500and2000final}}
+ \caption{This figure shows the actual standard deviation in LWR coefficients as compared to those obtained from 100 different instances of spatial randomization.
+Results are presented for two different bandwidths (nearest 500 and 2,000) for our regression variables.
+In all cases the distribution of standard deviations for the smaller bandwidth is larger.
+In most cases the standard deviation of LWR coefficients for the actual data (the dashed line) is substantially higher than any standard deviation obtained with simulated data.}
+ \label{fig:MCsim2}
 \end{figure}
-
-\begin{figure}
- \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{../graphs/MCsimResultsSDs650}}
- \caption{Simulation Results for nearest 650 observations.
-Actual LWR Coefficient Standard Deviations \textcolor{red}{(red line)} vs.\ Distribution of Monte Carlo Simulation Standard Deviations by Variable.
-Figures in which the red line is to the right of the black distribution suggest spatial non-stationarity in effect of the variable on house prices in our study region.}\label{fig:MCsds650}
-\end{figure}
-
-[Insert figure with nearest 1,000 observations here]
 
@@
 
+We know that house prices in the United States fell dramatically during and after the Great Recession of 2008-09.
+We know less about the patterns of change in the hedonic price functions during and after the fall in house prices.
+\citet{Cho2011b} found evidence from hedonic analysis in Nashville, Tennessee, that consumers' willingness to pay for environmental amenities (such as proximity to open space and water views) decreased during the recession as compared to the previous economic boom.
 Previous research has suggested that the impact of noise can change with time and economic conditions.
@@
 \citet{Cohen2009} also found the (airport) noise penalty to be larger in the early 2000s compared to the late 1990s in Atlanta, Georgia.
-We know that house prices in the United States fell dramatically during and after the Great Recession of 2008-09.
-We know less about the patterns of change in the hedonic price functions during and after the fall in house prices.
-\citet{Cho2011b} found evidence from hedonic analysis in Nashville, Tennessee, that consumers' willingness to pay for environmental amenities (such as proximity to open space and water views) decreased during the recession as compared to the previous economic boom.
 
 Figures~\ref{fig:AcreTime}--\ref{fig:NoiseTime} show the spatial distribution of some our LWR hedonic coefficients for bandwidths of 500 and 2,000 nearest sales within the last year for the sale years 2006--2010.
-Regardless of bandwidth, the figures show that the estimated LWR coefficients are different over time.
+For both bandwidths presented\footnote{Additional results available upon request.}, the figures show that the estimated LWR coefficients are different over time.
 In particular, the lot size and house size coefficients tend to decrease over time.
-What is surprising, however, is that the negative noise coefficient estimates tend to be more negative in later years of our study.
+These results are consistent with standard economic theory, as wealth and income decrease, consumer willingness to pay for normal goods decreases.
+What is surprising, however, is that the negative noise coefficient estimates also tend to be more negative in later years of our study.
 Figure~\ref{fig:NoiseTime} shows that the spatial patterns are similar across years (the most negative coefficients tend to be in the same locations across years), but the average noise coefficient tends to be more negative for the later years.
@@
  \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/Acre_50_200_ByYear}
- \caption{Simula.}
+ \caption{This figure shows the interpolated LWR lot size coefficients across space and time for two bandwidths (nearest 500 and 2,000).
+Note that the spatial pattern obtained is similar across time periods, but the average value tends to decline over time.}
  \label{fig:AcreTime}
@@
  \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/FinFt_50_200_ByYear}
- \caption{Simula.}
+ \caption{This figure shows the interpolated LWR finished house size coefficients across space and time for two bandwidths (nearest 500 and 2,000).
+Note that the spatial pattern obtained is similar across time periods, but the average value tends to decline over time.}
  \label{fig:HouseTime}
@@
  \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/Noise_50_200_ByYear}
- \caption{Simula.}
+ \caption{This figure shows the interpolated LWR noise coefficients across space and time for two bandwidths (nearest 500 and 2,000).
+Note that the spatial pattern obtained is similar across time periods, but the average value tends to decline over time.}
  \label{fig:NoiseTime}
@@
 Tables~\ref{tab:noisebetatime500} and \ref{tab:noisebetatime2000} present the results of regressions using our estimated LWR noise coefficient as the dependent variable and time and spatial characteristics as explanatory variables for LWR bandwidths of 500 and 2,000 nearest sales.
-
 Both tables are structured similarly.
@@
 We also limit our analysis to just the city of St.\ Paul and repeat the analysis from (1) and (2) in columns (5) and (6).
-Again, we estimate the noise coefficient to be more negative in later time periods.
+Again, we estimate the noise coefficient to be substantially more negative in later time periods.
 
@@
   \label{tab:noisebetatime500} 
+  \caption{LWR Noise Coefficient Over Time (bandwidth = 500 nearest sales)} 
 \scriptsize 
@@
 \hline \\[-1.8ex] 
- & \multicolumn{6}{c}{\textit{Dependent variable: LWR Noise Coefficients (bandwidth = 500 nearest sales)}} \\ 
+ & \multicolumn{6}{c}{\textit{Dependent variable: LWR Noise Coefficient (bandwidth = 500 nearest sales)}} \\ 
 \cline{2-7} 
@@
 \end{tabular} 
-  \caption{LWR Noise Coefficient Over Time} 
 \end{table}
@@
 % Requires LaTeX packages: dcolumn 
-\begin{sidewaystable}[!htbp] \centering 
-  \caption{LWR Noise Coefficient Over Time} 
+\begin{table}[!htbp] \centering 
+  \caption{LWR Noise Coefficient Over Time (bandwidth = 2,000 nearest sales)} 
   \label{tab:noisebetatime2000} 
@@
 \hline \\[-1.8ex] 
- & \multicolumn{6}{c}{\textit{LWR bandwidth = 2,000 nearest sales}} \\ 
+ & \multicolumn{6}{c}{\textit{Dependent variable: LWR Noise Coefficient (bandwidth = 2,000 nearest sales)}} \\ 
 \cline{2-7} 
@@
 \end{tabular} 
-\end{sidewaystable}
+\end{table}
 
@@
 
-The hedonic analysis results presented suggest that traffic noise exhibits a significant negative effect on house prices and that the hedonic function varies over space and time.
+The hedonic analysis results presented suggest that noise exhibits a significant negative effect on house prices and that the hedonic function varies over space and time.
 These results and analysis rest on important assumptions, which if violated, may change the results.
-This section describes three important considerations needed to contextualize our results and worthy of discussion: causation vs.\ correlation, potential temporal problems with our data, and omitted variable bias.
+This section describes three important considerations worthy of discussion and needed to contextualize our results: causation vs.\ correlation, potential temporal problems with our data, and omitted variable bias.
 
@@
 Such a study is not feasible and we are therefore limited to a hedonic analysis with observational data.
-Our conclusions, then, should be interpretted like most other hedonic analysis results and, while we find a strong negative correlation between noise and house prices, we cannot definitely state that noise causes lower sales prices.
+Our conclusions, then, should be interpretted like most other hedonic analysis results and, while we find a strong negative correlation between noise and house prices, we cannot definitely state that noise \emph{causes} lower sales prices.
 
@@
 However, Table VM2 from the US.
-Department of Transportation Office of Highway Policy Information website reports that in the year 2007 there were approximately 30 million vehicle miles traveled in the urban areas of the state of MN, while for years 2008, 2009, and 2010 the respective values were 32.5, 32.3, and 32.0.
+Department of Transportation Office of Highway Policy Information website reports that in the year 2007 there were approximately 30 million vehicle miles traveled in the urban areas of the state of MN, while for years 2008, 2009, and 2010 the respective values were 32.5, 32.3, and 32.0 million vehicle miles.
 Overall, this represents a change of less than 10 percent.
 \footnote{\url{http://www.fhwa.dot.gov/policyinformation/quickfinddata/qftravel.cfm}} Such small changes in total vehicle miles traveled are unlikely to yield significant differences in noise levels.
-Additionally, we do not believe the changes are likely to manifest in significant spatial variation in traffic noise, which is ultimately responsible for our identification of the noise regression coefficient.
+Additionally, we do not believe the changes are likely to manifest significant spatial variation in traffic noise, which is ultimately responsible for our identification of the noise regression coefficient.
 However, given enough time for changes in driving habits and technological advancements to gain significant market penetration (for instance, quieter hybrid cars), future work should seek to create time-series noise data in order to obtain even better estimates of the impact of traffic noise over time.
@@
 Our previously reported results also lack some important control variables in the hedonic function.
-For instance, locations exposed to more noise due to their proximity to high traffic areas may also be less safe due to the potential for accidents.
+As mentioned previously, we do not have data on the actual level of noise purchasers were exposed to inside the house, which could be altered depending on the quality of insulation, windows, and even time of day, or day of week.
+Locations exposed to more noise due to their proximity to high traffic areas may also be less safe due to the potential for accidents.
 Without including a proxy variable for safety, our noise coefficient could be biased - making it appear that home prices are reflecting noise exposure when in fact it could be safety issues.
@@
 
-Our data also omits other variables and to the extent that structural variables like the number of bedrooms, bathrooms, garage size, or construction quality co-vary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias.
+Our data also omits other structural characteristics and to the extent that variables like the number of bedrooms, bathrooms, garage size, or construction quality co-vary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias.
 We are comforted, however, because we do have some of these important additional variables for a subset of our data.

### 2014-07-07 analysis/00DescriptiveStats/DensityPlotsByYearMaker.R

@@ -24,7 +24,7 @@ my.col = brewer.pal(6, "Set2")
 year.f = factor(DATAFRAME$SALE_YR)
 table(year.f)
 
-pdf("graphs/DensityPlotsByYear.pdf", width = 9, height = 15)
+pdf("graphs/DensityPlotsByYear.pdf", width = 9, height = 15, family = "Palatino")
 par(mfrow = c(5, 3))
 par(oma = c(1, 1, 3, 1))
 par(mar = c(3, 4, 3, 1))
@@ -37,7 +37,7 @@ for (i in 1:length(myvars)) {
                      ylab = "relative frequency",
                      main = "",
                      axes = FALSE)
-  title(mynames[i], line = 1)
+  title(mynames[i], line = 1, cex.main = 1)
 }
-mtext("Univariate Density Plots by Year of Sale", outer = TRUE)
+mtext("Univariate Density Plots by Year of Sale", outer = TRUE, cex = 1.7)
 dev.off()

### 2014-07-07 analysis/04MonteCarloSim/MonteCarloScript2AssesSpatialNonStationarity.R

@@ -12,7 +12,7 @@ myVars = c("Air_Mean", "FIN_SQ_FT", "ACRES_POLY", "YEAR_BUILT", "OWNOCC", "MED_I
 RHS = paste(myVars, collapse = "+")
 MYMODEL = paste("logSALE_VA", RHS, sep = "~")
 MYMODELsmall = substr(MYMODEL, 1, nchar(MYMODEL)-5)
-KVECTOR = c(500) # c(200, 400, 650, 1000, 2000, 4000)
+KVECTOR = c(4000) # c(200, 400, 650, 1000, 2000, 4000)
 
 # How many times am I going to reshuffle?
 iterations = 100
@@ -24,7 +24,7 @@ numMCstats = 2 + 2*length(vars2keep)
 # colnames(MCstats) = c("minGCV", "optimalBandwidth", 
 #                       paste0("meanBeta.", vars2keep),
 #                       paste0("sterBeta.", vars2keep))
-mcstats = read.csv("analysis/04MonteCarloSim/Revision/Model3/k500/LWRMonteCarloStats2014-06-21.csv")
+mcstats = read.csv("analysis/04MonteCarloSim/Revision/Model3/k4000/LWRMonteCarloStats2014-07-06.csv")
 MCstats = as.matrix(mcstats)
 
 filePrefix = "../Data/R2GIS/CleanData/"
@@ -33,7 +33,7 @@ DATAFRAME = read.dbf(paste0(filePrefix, inputFile))
 simDATA = DATAFRAME
 N = dim(simDATA)[1]
 obs2run = which(simDATA$TimePeriod>11)
-for (iter in 51:iterations) {
+for (iter in 36:100) { # change to ``iterations'' to get the script to run all the way
   # Do a reshuffle
   rowShuffle = sample(1:N)
   simDATA[, c("Long_X", "Lat_Y")] = DATAFRAME[rowShuffle, c("Long_X", "Lat_Y")]

### 2014-07-07 analysis/04MonteCarloSim/Revision/FinalMCsimVisualizer.R

@@ -1,0 +1,62 @@
+# Assess the Monte Carlo simulation results for both k = 500 and k = 2,000 all in one graph
+# goal is to assess whether/which variables exhibit spatial non-stationarity
+
+# load the results of the true data analysis
+# calculate some statistics
+# load the monte carlo data
+# create distributions of the MC stats
+# add the true statistic to the distribution
+
+load("../Data/R2GIS/CleanData/TimeLag12months/Sales20052010LWRmodelAirMean3-2014-03-19.RData") # LWR output from model run with real data
+
+# LWRMonteCarloStats2014.03.29 <- read.csv("~/NoiseHedonicProject/Noise-Hedonic/analysis/04MonteCarloSim/Revision/Model3/LWRMonteCarloStats2014-03-29.csv")
+# LWRMonteCarloStats2014.04.18 <- read.csv("~/NoiseHedonicProject/Noise-Hedonic/analysis/04MonteCarloSim/Revision/Model3/LWRMonteCarloStats2014-04-18.csv")
+# MCMaster <- rbind(LWRMonteCarloStats2014.03.29, LWRMonteCarloStats2014.04.18)
+MCMaster2000 = read.csv("~/NoiseHedonicProject/Noise-Hedonic/analysis/04MonteCarloSim/Revision/Model3/k2000/LWRMonteCarloStats2014-07-03.csv")
+MCMaster2000 = MCMaster2000[1:100, ]
+
+MCMaster500 = read.csv("~/NoiseHedonicProject/Noise-Hedonic/analysis/04MonteCarloSim/Revision/Model3/LWRMonteCarloStats2014-07-05.csv")
+MCMaster500 = MCMaster500[1:80, ]
+
+MCplotter = function(outputcoefficient, statcoefficient) {
+  actual = sd(output[[outputcoefficient]][, c("k500", "k2000")], na.rm =T)
+  
+  temp500 = density(MCMaster500[, statcoefficient])
+  temp2000 = density(MCMaster2000[, statcoefficient])
+  
+  plot(temp500, type = "n",
+       xlim = c(0, max(c(temp500$x, temp2000$x, actual), na.rm = T)),
+       ylim = 1.2*c(0, max(c(temp500$y, temp2000$y), na.rm = T)),
+       main = "", axes = F, 
+       ylab = "", xlab = "")
+  axis(1, at = c(0, max(c(temp500$x, temp2000$x, actual))), 
[…]

### 2014-07-07 analysis/04MonteCarloSim/Revision/Model3/k4000/k4000aggregator.R

@@ -1,0 +1,15 @@
+
+# get the previous examples of the k = 4,000 MC simulation results together...
+
+MCstats0109 = read.csv("analysis/04MonteCarloSim/Revision/Model3/k4000/LWRMonteCarloStats2014-04-09.csv")
+MCstats1034 = read.csv("analysis/04MonteCarloSim/Revision/Model3/k4000/LWRMonteCarloStats2014-04-13.csv")
+MCstats = rbind(MCstats0109, MCstats1034)
+temp = as.matrix(MCstats)
+temp2 = matrix(NA, 100, 30)
+temp2[1:34, ] = temp
+
+colnames(temp2) = names(MCstats0109)
+write.csv(temp2, "analysis/04MonteCarloSim/Revision/Model3/k4000/LWRMonteCarloStatsTemp.csv", row.names = FALSE)
+
+temp3 = read.csv("analysis/04MonteCarloSim/Revision/Model3/k4000/LWRMonteCarloStatsTemp.csv")
+summary(temp3)

### 2014-07-07 reports/code/GCVsFromMCsimMaker.R

@@ -1,0 +1,69 @@
+# make a figure showing the distribution of GCV scores for MC simulation 1
+
+# idea is to show the distribution of GCV scores (as density plots) by bandwidth from reshuffled data
+# then show our GCV score on the same plot
+
+# conclusions: 
+# - our GCV score is different from the simulated values
+# - GCV scores tend to DECREASE as we INCREASE bandwidths for simulated data
+
+
+# load up the simulation results
+
+# 500
+mcstats500 = read.csv("analysis/04MonteCarloSim/Revision/Model3/k500/LWRMonteCarloStats2014-07-06.csv")
+mcstats500Density = density(mcstats500$minGCV)
+
+# 1000
+mcstats1000 = read.csv("analysis/04MonteCarloSim/Revision/Model3/k1000/LWRMonteCarloStats2014-06-25.csv")
+mcstats1000Density = density(mcstats1000$minGCV[1:50])
+
+# 2000
+mcstats2000 = read.csv("analysis/04MonteCarloSim/Revision/Model3/k2000/LWRMonteCarloStats2014-07-03.csv")
+mcstats2000Density = density(mcstats2000$minGCV)
+
+# 4000
+mcstats4000 = read.csv("analysis/04MonteCarloSim/Revision/Model3/k4000/LWRMonteCarloStatsTemp.csv")
+mcstats4000Density = density(mcstats4000$V1[1:34]) # HAVE TO FIX THIS - WHY ARENT THE NAMES HERE???
+
+
+maxX = max(mcstats500Density$x, mcstats1000Density$x, mcstats2000Density$x, mcstats4000Density$x)
+# > maxX
+# [1] 0.04649656
+maxY = max(mcstats500Density$y, mcstats1000Density$y, mcstats2000Density$y, mcstats4000Density$y)
+# > maxY
+# [1] 7755.237
+
+pdf("graphs/GCVsFromMCsim.pdf", width = 6, height = 4, family = "Palatino")
+par(mar = c(4, 1, 4, 1))
+par(oma = c(.5, .5, 3, .5))
+layout(matrix(c(1, 1, 2), 1, 3))
+plot(0, 0, type = "n",
+     xlim = c(0.02, 0.05), 
+     ylim = c(0, maxY),
+     xlab = "",
+     ylab = "",
+     main = "",
+     axes = F)
+axis(1)
+mtext("relative frequency", side = 2)
+mtext("GCV score", side = 1, line = 3)
[…]

### 2014-07-07 reports/code/ModelGCVvisualizer.R

@@ -35,6 +35,8 @@ for (i in 1:3) {
                                    dep.var = DATAFRAME$logSALE_VA[obs2run]))
 }
 
+# gcvs.global = c(0.04830468, 0.04093458, 0.03753716)
+
 ks = c(100,  200,  300,  350,  400,  450,  500,  550,  600,  650,  700,  800, 1000, 1500, 2000, 3000, 4000)
 gcv1 = c(0.03390767, 0.02991290, 0.02941916, 0.02938722, 0.02944322, 0.02953900, 0.02964363, 0.02977173, 
          0.02990581, 0.03005645, 0.03020745, 0.03049779, 0.03105754, 0.03245082, 0.03364512, 0.03614031, 
@@ -62,7 +64,7 @@ axis(1, at = 500)
 axis(2, at = round(min(gcvs), 3), las = 1)
 title("Generalized Cross Validation Scores Across Models")
 
-text(500, .031, "LWR Model (1) = Structural Variables + Month Fixed Effects",  
+text(500, .031, "LWR Model (1) = Structural Variables + Month*Year Fixed Effects",  
      srt = 13, pos = 4, col = "black", cex = .8)
 
 text(500, .028, "LWR Model (2) = LWR Model (1) + Locational Variables",

### 2014-07-07 reports/code/mainResultsTables.R

@@ -1,9 +1,9 @@
 # Goal is to make a table of LWR results for the paper...
 
-# mega columns (for each bandwidth: 500, 650, 1000)
+# mega columns (for each bandwidth: 500, 650, 1000, 2000)
 # for each bandwidth 
 # mean LWR Beta hats
-# 25th and 75th percentile of LWR beta hats
+# 10th and 90th percentile of LWR beta hats
 
 
 # load the dataframe and helper functions
@@ -12,13 +12,12 @@ DATAFRAME = read.dbf("~/NoiseHedonicProject/Data/R2GIS/CleanData/Sales20052010.d
 obs2run = which(DATAFRAME$TimePeriod>11)
 source("~/NoiseHedonicProject/Noise-Hedonic/helper/LWRfunctions.R")
 
-# load the LWR results
-# load the Monte Carlo Results
 ####################
 # Model 3
 ####################
 load("~/NoiseHedonicProject/Data/R2GIS/CleanData/TimeLag12months/Sales20052010LWRmodelAirMean3-2014-03-19.RData")
 
+# right now I make the table have three columns for each bandwidth - mean, 10th, 90th percentile
 BWs = c("k500", "k650", "k1000")
 variableOrder = c(2:5, 16:24)
 names(output)[variableOrder]
@@ -47,150 +46,38 @@ stargazer(niceTable,
           digits = 4, column.sep.width = "-1pt"
           )
 
-lm.global = lm(paste0(MYMODEL, "+factor(SALE_YR)"), data = DATAFRAME[obs2run, ])
-GlobalModel = summary(lm.global)
-global.leverages = lm.influence(lm.global, do.coef = FALSE)$hat
-
-vars = c("(Intercept)", "MAX", "FIN_SQ_FT", "ACRES_POLY", "YEAR_BUILT", "OWNOCC", 
-         "MCA3", "MED_INCOME", "CBD_dist", "PARK_dist", "LAKE_dist", "SHOP_dist" )
-
-numvars = length(vars)
-LWRtable = matrix(NA, numvars+2, 6)
-rownames(LWRtable) = c("(Intercept)", "Traffic Noise", "House Size", "Lot Size", "Year of Construction", 
-                       "Owner Occupancy", "Elementary Test Scores", "Median Income", 
-                       "distance to CBD", "distance to nearest Park", "distance to nearest Lake", 
[…]

### 2014-07-11 reports/NoiseHedonicRaR.Rnw
another round of edits to RaR - including removing page numbers from figure pages

@@
 \documentclass{article}
-
+\usepackage{floatpag} %floatpag.sty file is just in the reports folder - commands to remove page nos are in first figure
 \usepackage[round]{natbib}
 \usepackage{dcolumn}
+\usepackage{pifont}
 \usepackage{rotating}
@@
 \usepackage[nolists]{endfloat}
-\usepackage[width = 5in]{geometry}
+\usepackage[width = 5.5in]{geometry}
 \usepackage{caption, amsmath, graphicx, setspace, multirow, color, hyperref, array}
 \usepackage[modulo]{lineno}
-%\renewcommand{\efloatseparator}{\mbox{}}
 
-\newcommand\T{\rule{0pt}{2.6ex}}       % Top strut
-\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} % Bottom strut
 \newcolumntype{x}[1]{%
@@
 
-\title{The Negative Effect of Traffic Noise on House Prices: A Landscape Hedonic Analysis}
+\title{Traffic Noise and House Prices: A Hedonic Analysis over Time and Space}
 \date{}
@@
 One consequence of the expanding road network and its associated traffic is increased levels of traffic noise.
-While the hedonic literature has consistently shown a negative effect of this phenomenon on the real estate market, research in the United States has often relied on crude measures of traffic noise.
+While the hedonic literature has consistently found a negative effect of this phenomenon on the real estate market, research in the United States has often relied on crude measures of traffic noise.
 Here, we reduce the measurement error of traffic noise exposure through a detailed model of noise propagation over the landscape.
-Additionally, we estimate the impact on single family home transactions throughout the St.\ Paul, Minnesota, urban area using spatially explicit local regression techniques to allow for spatial non-stationarity in the hedonic function.
+We then estimate the hedonic relationship between noise and house prices using over 40,000 single family home transactions throughout the St.\ Paul, Minnesota, urban area from 2005-2010.
+We implement spatially and temporally flexible local regression techniques and find significant non-stationarity in the hedonic function over time and space.
 \end{abstract}
@@
 
-Automobiles are already perhaps the greatest source of noise in residential neighborhoods \citep{Barber2010} and traffic noise was estimated to cause around three billion dollars worth of external damage to the United States economy alone in 1991 \citep{Delucchi1998}.
+% Automobiles are already perhaps the greatest source of noise in residential neighborhoods \citep{Barber2010} and traffic noise was estimated to cause around three billion dollars worth of external damage to the United States economy alone in 1991 \citep{Delucchi1998}.
 Traffic noise and its attendant problems are greater now than they were in the 1990s and predicted to worsen in the future \citep{Goines2007}.
 %With the exception of a slight dip during the economic recession in the late 2000s, the number of vehicle miles traveled in the United States has steadily increased for the past 50 years.\footnote{\url{http://www.fhwa.dot.gov/policyinformation/statistics/2011/pdf/rc1c.pdf}}
-Globally, \citet{Dargay2007} predict the number of personal vehicles to grow from roughly 800 million in 2002 to over two billion units by 2030.
+% Globally, \citet{Dargay2007} predict the number of personal vehicles to grow from roughly 800 million in 2002 to over two billion units by 2030.
 Additionally, the global trend of increased urbanization is expected to continue, with the proportion of the population living in cities growing from roughly half now to over two-thirds by the middle of the century \citepalias{UNDESA2012}.
@@
 One way to estimate some of the costs of traffic noise (and therefore the economic benefits of policies that reduce noise) is through hedonic regression, examining the relationship between house prices and noise levels.
-\citet{Nelson1982} was the first to review some of the earliest noise hedonic work in the United States and Canada.
-The review of nine studies found an average estimated impact of traffic noise to be a reduction in house prices of approximately 0.4 percent per additional decibel.
-More recently, \citet{Nelson2008} notes that many of these early studies \citep[such as][]{Gamble1974, Langley1976} are plagued by issues of small sample sizes (in the hundreds) and limited spatial extents (one or a handful of cities).
+\citet{Nelson1982} reviewed nine of the earliest noise hedonic articles in the United States and Canada and found an average reduction in house prices of approximately 0.4 percent per additional decibel.
+Many of these early studies \citep[such as][]{Gamble1974, Langley1976} are plagued by issues of small sample sizes (in the hundreds) and limited spatial extents (one or a handful of cities).
+Recent hedonic research has tended to focus on the European experience, often due to the availability of high quality traffic noise data made available from the government, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Switzerland \citep{Baranzini2010}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, Netherlands \citep{Theebe2004a}, and Germany \citep{Brandt2011}.
 
-Reviews of the research by \citet{Bateman2001} found that the negative effect of traffic noise on house prices ranged from 0.08 to 2.22 percent per decibel with a mean around 0.55 percent per decibel, while \citet{Navrud2002} found an average decrease of 0.64 percent per decibel.
-Much of the recent research in this literature has tended to focus on the European experience with noise, often due to the availability of high quality traffic noise data made available from the government, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Switzerland \citep{Baranzini2010}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, Netherlands \citep{Theebe2004a}, and Germany \citep{Brandt2011}.
+%Reviews of the research by \citet{Bateman2001} found that the negative effect of traffic noise on house prices ranged from 0.08 to 2.22 percent per decibel with a mean around 0.55 percent per decibel, while \citet{Navrud2002} found an average decrease of 0.64 percent per decibel.
+Much of the
 
-Instead of focusing on the impact of automobile traffic noise, hedonic work in the United States has tended to concentrate on noise from airports \citep{Espey2000, McMillen2004, Cohen2008a} or indirect measures of traffic noise, such as proximity to highways \citep{Matthews2007, Chernobai2009, Li2012}, or traffic counts \citep{HughesJr.1992, Larsen2012}.
-One exception is \citet{Cheng2008}, who estimated that year 2007 housing prices in Louisville, Tennessee were, on avarege, 0.34 percent lower for each additional decibel of traffic noise.
+Although automobiles are perhaps the greatest source of noise in residential neighborhoods \citep{Barber2010}, research in the United States has concentrated on noise from airports \citep{Espey2000, McMillen2004, Cohen2008a}.
+Other work has typically used indirect measures of traffic noise, such as proximity to highways \citep{Matthews2007, Chernobai2009, Li2012}, or traffic counts \citep{HughesJr.1992, Larsen2012}.
+An exception is \citet{Cheng2008}, who estimated that year 2007 housing prices in Louisville, Tennessee were, on average, 0.34 percent lower for each additional decibel of traffic noise, holding all other variables constant.
 However, the generalizability of this research is limited given that it is based on less than a thousand house transactions in just one city.
 
-A major reason for the thinness of the scholarly literature on this topic in the US lies in the difficulty of modeling traffic noise propagation over the landscape.
+One major reason for the thinness of the scholarly literature on this topic in the United States lies in the difficulty of modeling traffic noise propagation over the landscape.
 To properly analyze the spatial association between real estate prices and exposure to traffic noise, it is necessary to create a noise surface map at sufficiently detailed spatial resolution to account for the complex and heterogeneous interaction between the noise source and the resistance of the landscape to noise propagation.
@@
 Furthermore, it is computationally very intensive.
-Fortunately, recent developments in Geographic Information Systems and distributive computing have reduced these difficulties, making it much easier to create a noise surface map at landscape level with high spatial resolution.
+Fortunately, recent developments in Geographic Information Systems and distributive computing have reduced these difficulties, making it much easier to create a noise surface map for large areas with high spatial resolution.
 
@@
 
-%Precise estimates of the impact of traffic noise are important for efficient implementation of noise mitigation projects.
-The US Federal Highway Admistration reports that 47 states have constructed noise barriers to reduce noise propagation, spending over a half a billion dollars from 2008-2010 \citepalias{USFHA2012}.
-\citet{Delucchi1998} used an estimate of 0.85 percent reduction in house prices per additional decibel in their cost-benefit analysis of traffic noise.
-While their preferred estimate of the total damage cost to the United States in 1991 is \$3 billion, they report a possible range of less than \$100 million to over \$40 billion due in part to uncertainty surrounding the degree of noise propagation over space in the urban built environment and the effect of noise on house prices.
-Indeed, one of the main conclusions of their work is that more research should be done to better understand the impact of noise on house prices and that better noise data are needed for such work to occur.
+In addition to using new data that reduces the measurement error of traffic noise, we construct a flexible hedonic model that allows for non-stationary relationships between house prices and our explanatory variables over geography and time.
+Such Locally Weighted Regression (LWR) models have become increasingly prevalent in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, McMillen2010, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than other standard spatial econometric models under common real world circumstances \citep{McMillen2012}.
+Our results confirm the importance of a spatially- and temporally-flexible modeling approach and reject the still too often used assumptions of spatial and temporal stationarity in the hedonic function.
 
-We construct a flexible hedonic model that allows for a non-stationary relationship between house prices and our explanatory variables over geography and time.
-Such Locally Weighted Regression (LWR) models have become increasingly common in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than other common spatial econometric models under common real world circumstances \citep{McMillen2012}.
-Thus, in addition to using new data that reduces the measurement error of the impact of traffic noise, the spatial and temporal variation in our data and hedonic modeling allow us to present the first estimates in the United States of how the marginal effect of traffic noise varies over space and time.
-
-We find strong evidence to support hedonic modeling choices that allow for spatial and temporal heterogeneity.
-Our paper also presents the first estimates of the implicit price of traffic noise after the housing market collapse and economic recession of 2008-09.
-Contrary to work such as \citet{Cho2011b}, which found that environmental amenities mattered \emph{less} after the housing crash, our estimated noise coefficients roughly double in magnitude after the recession compared to before.
+Given the timing of our study period, the strength of our data, and the flexible modeling strategy, we present the first estimates in the United States of how the marginal effect of traffic noise varies over space and time, in particular, before, during, and after the  economic recession of 2008-09.
+Contrary to work such as \citet{Cho2011b}, which found that environmental amenities mattered less after the housing crash, our estimated noise coefficients roughly double in magnitude after the recession compared to before.
+Also, while most of our variables exhibit spatial non-stationarity, we do not find evidence of a spatially varying relationship between noise and house prices, in direct contrast to recent work in Spain by \citet{MarmolejoDuarteCarlos;GonzalezTamez2009}.
 We conclude with a discussion of how future research can expand and improve upon this work.
@@
 \section{Study Area and Data}
-The 2010 US Census lists the population of the Twin Cities Metropolitan Region (Minneapolis and St.\ Paul and their surrounding areas) as almost 3 million residents spread over seven counties.
-This study examines single family residential home transactions in the Census-defined urban areas of three of the seven counties: Dakota, Ramsey and Washington County (see Figure \ref{fig:overview}).
-We obtained sales data from approximately forty thousand transactions between 2005 and 2010 (n=42,095) from the 2010 MetroGIS Regional Parcel Dataset published by the Metropolitan Council.
-Figure \ref{fig:overview} shows an overview of the study area as well as the spatial distribution of the house sales prices.
+The 2010 United States Census lists the population of the Twin Cities Metropolitan Region (Minneapolis and St.\ Paul and their surrounding areas) as almost 3 million residents spread over seven counties.
+This study examines single family residential home transactions in the Census-defined urban areas of three of the seven counties: Dakota, Ramsey and Washington County.
+We obtained sales data from approximately forty thousand transactions between 2005 and 2010 (n=42,083) from the 2010 MetroGIS Regional Parcel Dataset published by the Metropolitan Council.
+Figure \ref{fig:overview} shows an overview of the study area as well as the spatial distribution of the house sales prices and noise values.
 
-In addition to the geographic location and date of the house sale, we collected or calculated structural and locational variables commonly used in the hedonic literature, such as the size of the house, lot size, and architectural style of the house, as well as distances to amenities like the Central Business District, parks, and lakes.
+In addition to the geographic location and date of the house sale, we collected or calculated structural and locational variables commonly used in the hedonic literature, such as the size of the house, lot size, and architectural style of the house, local demographic characteristics, as well as distances to amenities like the Central Business District, shopping centers, parks, and lakes.
 Table \ref{tab:sumStats} provides a brief description of the variables in our data and some basic summary statistics.
@@
 \begin{figure}
-\makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/Overview2column}}
+\floatpagestyle{empty}
+\rotfloatpagestyle{empty}
+\makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/Overview2columnAnnotatedPDF}}
 \caption{This figure shows the spatial extent of our study area, the significant spatial variation in single family house sales prices, as well as our noise data.}
@@
 \small
-\begin{tabular}{lD{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}}
-
+\begin{tabular}{lccccccc}%D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}}
+  \hline \hline
  & min & 25\% & 50\% & mean & 75\% & max & st dev \\ 
@@
 % Tue Jun 10 21:29:25 2014
-Sale Price (\$1,000s) & 99 & 195 & 241 & 266 & 315 & 675 & 103 \\ 
-  Year House was Built & 1850 & 1950 & 1973 & 1967 & 1993 & 2010 & 32 \\ 
-  House Size (ft$^2$) & 390 & 1158 & 1628 & 1750 & 2189 & 4000 & 704 \\ 
-  Lot Size (acres) & 0.02 & 0.17 & 0.25 & 0.25 & 0.31 & 0.60 & 0.11 \\ 
-  Owner Occupancy (Yes = 1, No = 0) & 0.0 & 1.0 & 1.0 & 0.8 & 1.0 & 1.0 & 0.4 \\ 
-  Traffic Noise (dB) & 24.5 & 49.0 & 54.0 & 54.3 & 59.5 & 81.6 & 7.5 \\ 
-  Distance to Central Business District (km) & 1.1 & 6.8 & 13.2 & 14.7 & 21.8 & 37.1 & 8.9 \\ 
-  Distance to nearest Park (km) & 0.0 & 1.1 & 2.2 & 2.6 & 3.8 & 9.7 & 1.9 \\ 
-  Distance to nearest Lake (km) & 0.0 & 0.4 & 0.8 & 0.9 & 1.3 & 4.4 & 0.7 \\ 
-  Distance to nearest Shopping Center (km) & 0.0 & 0.9 & 1.5 & 1.9 & 2.3 & 10.8 & 1.6 \\ 
-  Percent of Census Block Population Race = White & 0 & 80 & 90 & 85 & 96 & 100 & 17 \\ 
-  Percent of Census Block Population Under Age 18 & 0 & 21 & 27 & 27 & 33 & 67 & 9 \\ 
-  Median Income in Census Tract (\$1,000s) & 14 & 55 & 69 & 73 & 90 & 143 & 24 \\ 
-  Elementary Test Scores & 336 & 360 & 365 & 364 & 370 & 552 & 11 \\ 
-   \hline
+Sale Price (\$1,000s) & 99 & 195 & 241 & 266 & 315 & 675 & 103 \\ \\
+  Year House was Built & 1850 & 1950 & 1973 & 1967 & 1993 & 2010 & 32 \\ \\
+  House Size (ft$^2$) & 390 & 1158 & 1628 & 1750 & 2189 & 4000 & 704 \\ \\
+  Lot Size (acres) & 0.02 & 0.17 & 0.25 & 0.25 & 0.31 & 0.60 & 0.11 \\ \\
+  Owner Occupancy (Yes = 1, No = 0) & 0.0 & 1.0 & 1.0 & 0.8 & 1.0 & 1.0 & 0.4 \\ \\
+  Traffic Noise (dB) & 24.5 & 49.0 & 54.0 & 54.3 & 59.5 & 81.6 & 7.5 \\  \\
+  Distance to Central Business District (km) & 1.1 & 6.8 & 13.2 & 14.7 & 21.8 & 37.1 & 8.9 \\ \\
+  Distance to Nearest Park (km) & 0.0 & 1.1 & 2.2 & 2.6 & 3.8 & 9.7 & 1.9 \\ \\
+  Distance to Nearest Lake (km) & 0.0 & 0.4 & 0.8 & 0.9 & 1.3 & 4.4 & 0.7 \\ \\
+  Distance to Nearest Shopping Center (km) & 0.0 & 0.9 & 1.5 & 1.9 & 2.3 & 10.8 & 1.6 \\ \\
+  Percent of Census Block Population Race = White & 0 & 80 & 90 & 85 & 96 & 100 & 17 \\ \\
+  Percent of Census Block Population Under Age 18 & 0 & 21 & 27 & 27 & 33 & 67 & 9 \\ \\
+  Median Income in Census Tract (\$1,000s) & 14 & 55 & 69 & 73 & 90 & 143 & 24 \\ \\
+  Nearest Elementary School Test Scores & 336 & 360 & 365 & 364 & 370 & 552 & 11 \\ 
+   \hline \hline
 \end{tabular}
@@
 \begin{tabular}{l|rrrrrrrrrrrrr}
+\hline \hline
  & \multicolumn{1}{x{.35in}}{Price} & \multicolumn{1}{x{.38in}}{House} & \multicolumn{1}{x{.35in}}{Lot} & 
@@
  \multicolumn{1}{x{.35in}}{U18} & \multicolumn{1}{x{.35in}}{Inc.} & 
- \multicolumn{1}{x{.35in}}{Test} \tabularnewline 
+ \multicolumn{1}{x{.35in}}{Test} \\
   \hline
-Sale Price & 1 &  &  &  &  &  &  &  &  &  &  &  &  \tabularnewline
-House Size & 0.74 & 1 &  &  &  &  &  &  &  &  &  &  &  \tabularnewline
-Lot Size  & 0.38 & 0.45 & 1 &  &  &  &  &  &  &  &  &  &  \tabularnewline
-Year Built  & 0.45 & 0.52 & 0.47 & 1 &  &  &  &  &  &  &  &  &  \tabularnewline
-Noise & -0.24 & -0.12 & -0.04 & -0.25 & 1 &  &  &  &  &  &  &  &  \tabularnewline
-Distance to CBD  & 0.31 & 0.45 & 0.43 & 0.58 & -0.09 & 1 &  &  &  &  &  &  &  \tabularnewline
-Distance to Park  & 0.25 & 0.28 & 0.22 & 0.42 & -0.17 & 0.57 & 1 &  &  &  &  &  &  \tabularnewline
-Distance to Lake & -0.04 & -0.10 & -0.25 & -0.17 & -0.01 & -0.09 & 0.20 & 1 &  &  &  &  &  \tabularnewline
-Distance to Shop  & 0.27 & 0.27 & 0.15 & 0.37 & -0.24 & 0.46 & 0.38 & 0.15 & 1 &  &  &  &  \tabularnewline
-Percent White & 0.24 & 0.15 & 0.25 & 0.15 & -0.09 & 0.34 & 0.16 & -0.14 & 0.14 & 1 &  &  &  \tabularnewline
-Percent Under 18 & 0.26 & 0.30 & 0.11 & 0.36 & -0.19 & 0.29 & 0.32 & 0.09 & 0.32 & -0.22 & 1 &  &  \\ 
-Income & 0.52 & 0.50 & 0.41 & 0.57 & -0.24 & 0.53 & 0.38 & -0.12 & 0.36 & 0.35 & 0.32 & 1 &  \tabularnewline
-Elem.\ Test Scores & 0.29 & 0.28 & 0.29 & 0.34 & -0.09 & 0.35 & 0.22 & -0.10 & 0.18 & 0.31 & 0.10 & 0.44 & 1 \tabularnewline 
+Sale Price & 1 &  &  &  &  &  &  &  &  &  &  &  &  \\ \\
+House Size & 0.74 & 1 &  &  &  &  &  &  &  &  &  &  &  \\ \\
+Lot Size  & 0.38 & 0.45 & 1 &  &  &  &  &  &  &  &  &  &  \\ \\
+Year Built  & 0.45 & 0.52 & 0.47 & 1 &  &  &  &  &  &  &  &  &  \\ \\
+Noise & -0.24 & -0.12 & -0.04 & -0.25 & 1 &  &  &  &  &  &  &  &  \\ \\
+Distance to CBD  & 0.31 & 0.45 & 0.43 & 0.58 & -0.09 & 1 &  &  &  &  &  &  &  \\ \\
+Distance to Park  & 0.25 & 0.28 & 0.22 & 0.42 & -0.17 & 0.57 & 1 &  &  &  &  &  &  \\ \\
+Distance to Lake & -0.04 & -0.10 & -0.25 & -0.17 & -0.01 & -0.09 & 0.20 & 1 &  &  &  &  &  \\ \\
+Distance to Shop  & 0.27 & 0.27 & 0.15 & 0.37 & -0.24 & 0.46 & 0.38 & 0.15 & 1 &  &  &  &  \\ \\
+Percent White & 0.24 & 0.15 & 0.25 & 0.15 & -0.09 & 0.34 & 0.16 & -0.14 & 0.14 & 1 &  &  &  \\ \\
+Percent Under 18 & 0.26 & 0.30 & 0.11 & 0.36 & -0.19 & 0.29 & 0.32 & 0.09 & 0.32 & -0.22 & 1 &  & \\  \\ 
+Income & 0.52 & 0.50 & 0.41 & 0.57 & -0.24 & 0.53 & 0.38 & -0.12 & 0.36 & 0.35 & 0.32 & 1 &  \\ \\ 
+Elem.\ Test Scores & 0.29 & 0.28 & 0.29 & 0.34 & -0.09 & 0.35 & 0.22 & -0.10 & 0.18 & 0.31 & 0.10 & 0.44 & 1 \\ \hline \hline 
 \end{tabular} }
@@
 \subsection{Noise Data}
-To determine the relationship between real estate price and road traffic noise levels, we first created a traffic noise exposure surface by calculating the propagation of traffic noise over the landscape using the FHWA (Federal Highway Authority) 1978 standard \citep{Barry1978}.
-The entire methodology has already been explained in detail in (CITE two NEGA PAPERS) What follows is a summary.
+To determine the relationship between real estate prices and road traffic noise levels, we first created a traffic noise exposure surface by calculating the propagation of traffic noise over the landscape using the Federal Highway Authority (FHWA) 1978 standard \citep{Barry1978}.
+Methodological details of the process can be found in \citet{Nega2012} and \citet{Nega2013}.
+Here we provide a brief summary.
+
 The modeling of traffic noise has three key components: choosing the mathematical function for noise propagation, assembling the input data, and assessing the accuracy of the model prediction.
-These will be briefly discussed.
-Because it is currently used by the state of Minnesota, we used the FHWA 1978 standard model for calculating the noise level.
+We used the FHWA 1978 standard model for calculating the noise level because it is currently used by the state of Minnesota.
 According to this standard, the noise level at any given location on the landscape can be expressed:
@@
 \end{eqnarray}
-where $L_{EQ}(i)$ is A-weighted hourly energy equivalent noise level in decibels (dBA), which is calculated for each class $i$ of vehicle (automobile and trucks); $\bar{L}_0(i)$ is the mean Sound Pressure Level (SPL) at the reference distance for class $i$; $\sigma _i$ is the standard deviation of the SPL for each class of vehicle; $N_i$ is the number of vehicles of the $i^{th}$ class passing during the relevant hour; $D_0$ is the reference distance (usually 15 m); $D$ is the perpendicular distance from the road center line to the receiver; $\alpha$ is a site parameter (soft and hard surface), $0 < \alpha < 1$; $S_i$ is the mean speed of the $i^{th}$ class; $T$ is the duration, usually 1 hour; $\phi _1$ and $\phi _2$ are the angles from the perpendicular of the limits of the observer's view of a section of the road.
-They are used to account for only the energy coming from a portion of the roadway; $\Delta _{gradient}$ is an adjustment for road surface gradient; $\Delta _{shielding}$ is a shielding adjustment (land cover, buildings, noise barriers).
+where 
+\begin{itemize}
+\item[] $L_{EQ}(i)$ is A-weighted hourly energy equivalent noise level in decibels (dBA), which is calculated for each class $i$ of vehicle (automobile and trucks); 
+\item[] $\bar{L}_0(i)$ is the mean Sound Pressure Level (SPL) at the reference distance for class $i$; \item[] $\sigma _i$ is the standard deviation of the SPL for each class of vehicle; 
+\item[] $N_i$ is the number of vehicles of the $i^{th}$ class passing during the relevant hour; 
+\item[] $D_0$ is the reference distance (usually 15 m); 
+\item[] $D$ is the perpendicular distance from the road center line to the receiver; 
+\item[] $\alpha$ is a site parameter (soft and hard surface), $0 < \alpha < 1$; 
+\item[] $S_i$ is the mean speed of the $i^{th}$ class; 
+\item[] $T$ is the duration, usually 1 hour; 
+\item[] $\phi _1$ and $\phi _2$ are the angles from the perpendicular of the limits of the observer's view of a section of the road.
+They are used to account for only the energy coming from a portion of the roadway;
+\item[] $\Delta _{gradient}$ is an adjustment for road surface gradient; and 
+\item[] $\Delta _{shielding}$ is a shielding adjustment (land cover, buildings, noise barriers).
+\end{itemize}
 
-We used several data sources as inputs in the study.
+We used the SoundPlan\texttrademark noise modeling software to implement equation~\ref{eq:noise} using several data sources as inputs.
 A 2007 road centerline and the associated traffic characteristics (volume and proportion of trucks and vehicles) for the region were obtained from the Minnesota Department of Transportation (MNDoT).
@@
 We extracted the perimeter and height of 818,500 buildings using a combination of LiDAR data and aerial photography.
-Foliage shielding is accounted by extracting forest polygons that are at least 10 m high and have an area $\geq 10,000 m^2$ from a 2005 land use and 2001 National Land Cover Data.
-We obtained a noise barrier layer from the MNDoT that contains the locations, width, and height of each noise barriers to account for its shielding effect.
-
-We used the SoundPlanTM noise modeling software to implement equation\ref{eq:noise}.
-Predicted noise output is calculated at a grid resolution of 10 m$^2$.
-We conducted a preliminary validation of the model output by comparing it with observed noise levels, which were sampled at 134 locations along a major highway.
-The relationship between the mean observed and predicted noise levels was linear and moderately strong with a correlation of 0.76.
+Foliage shielding was accounted for by extracting forest polygons that are at least 10 m high and have an area $\geq$10,000 m$^2$ from a 2005 land use and 2001 National Land Cover Data.
+We obtained a noise barrier layer from the MNDoT containing the locations, width, and height of each noise barriers to account for its shielding effect.
 
 In order to incorporate noise produced by aircraft into the overall noise exposure, we obtained the aircraft noise contour lines of the region from the Twin Cities Metropolitan Airports Commission.
-The contour line noise values coincident with the traffic noise surface then were added following rules of logarithmic addition.
-For example, adding 52 dBA from aircraft contour line into the noise surface where the noise value is 51 yields 53.5 dBA.
+The contour line noise values coincident with the traffic noise surface were then added following rules of logarithmic addition.
+For example, adding 52 dBA from aircraft contour line into the noise surface where the noise value was 51 dBA yielded 53.5 dBA.
 
-A map of our noise surface can be seen in Figure~\ref{fig:overview}.
-Once the noise surface for the entire region was developed, we extracted the noise surface for the present study area by overlaying the housing parcel boundaries and calculating the mean noise level within the parcel.
+Predicted noise output was calculated at a grid resolution of 10 m$^2$.
+We conducted a validation of the model output by comparing it with observed noise levels, which were sampled at 134 locations along a major highway.
+The relationship between the mean observed and predicted noise levels was found to be linear and moderately strong with a correlation of 0.76.
+A map of our noise surface and the validation sites can be seen in Figure~\ref{fig:overview}.
+Once the noise surface for the entire region was developed, we extracted the noise surface for the present study by overlaying the housing parcel boundaries and calculating the mean noise level within the parcel.
 
-\subsection{Structural Attributes}
+\subsection{House Structural Attributes}\label{structural}
 According to a review by \cite{Wilhelmsson2000}, the five most common structural attributes included in real estate hedonic pricing studies are living area, number of bathrooms, age, garage and lot size.
@@
 A common real estate adage states that the three most important real estate attributes are: location, location and location.
-Knowing where each house is located allows us to also construct a vector of other attributes associated with the sales transaction.
-For instance, using GIS software we are able to calculate the Euclidean distance to numerous points of interest within the dataset, such as the nearest central business district, shopping centers, parks, and lakes.
-Additionally, three demographic variables denoting the median household income for the surrounding census tract, the percentage of the population that identified their race as ``white'', and the percentage of the population that is under the age of 18 were created through the use of TIGER shapefiles from the 2010 Census Bureau and data from the 2010 American Community Survey.
-Lastly, we associate each transaction with its elementary school and include the average 3rd grade Minnesota Comprehensive Assessment (MCA) score for the local elementary school during the year of purchase.\footnote{Test scores were obtained from the Minnesota Department of Education website.
+Knowing where each house is located allowed us to construct a vector of other attributes associated with the sales transaction.
+Using GIS software we calculated the Euclidean distance to numerous points of interest within the dataset, such as the nearest central business district, shopping centers, parks, and lakes.
+Additionally, three local demographic variables denoting the median household income for the surrounding census tract, the percentage of the population that identified their race as ``white'', and the percentage of the population that is under the age of 18 (both at the census block group level) were created through the use of TIGER shapefiles from the 2010 Census Bureau and data from the 2010 American Community Survey.
+Lastly, we associated each transaction with its nearest elementary school and included the average 3rd grade Minnesota Comprehensive Assessment (MCA) score for the local elementary school during the year of purchase.\footnote{Test scores were obtained from the Minnesota Department of Education website.
 The school district and elementary school attendance boundary spatial information were obtained from the Minnesota Geospatial Information Office Clearinghouse Data Catalog.}
@@
 \subsection{Time}
-We have sales transactions across six years (from 2005 to 2010) for our study area.
-Such temporal variation will allow us to estimate the hedonic price function over time and test for differences before, during, and after the economic recession.
+We collected sales transactions from 2005 to 2010 to estimate the hedonic price function over time and test for differences before, during, and after the economic recession.
+We are concerned about issues of sample selection bias over time, however we find no evidence of only certain types or locations of houses transacting in later years compared to earlier years in our data.
 Table \ref{tab:SumStatsTime} displays the mean variable values by year of sale to look for differences over time.
-The mean sale price in 2009 (roughly \$230,000) is almost 20 percent lower than the mean sale price in 2006 (roughly \$280,000) and the number of sales transactions in 2009-10 is less than the number of transactions in 2005.
-However, most other variables have small or no differences across time.
+The mean sale price in 2009 (roughly \$230,000) was almost 20 percent lower than the mean sale price in 2006 (roughly \$280,000).
+However, most other variable means have small or no differences in the across time.\footnote{We also created univariate density plots of the variables by year to check for differences in the shape and spread of the distributions over time.
+With the exception of house prices, we found no differences in the variable distributions over time.
+Figures available upon request.} We also mapped the locations of sales transactions to check for differences in geographic dispersion of sales over time, but found none (see Figure~\ref{fig:SalesYear}).
+Thus, with the exception of lower sales prices in later years, house characteristics in our sample appear similar before, during, and after the economics recession.
 
@@
   \centering
-    \begin{tabular}{lD{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}|D{.}{.}{1}}
+    \begin{tabular}{lcccccc|c}%D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}|D{.}{.}{1}}
     \\[-1.8ex]\hline 
@@
     Variable & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & \multicolumn{1}{r}{All Years}\\ \hline 
-Sale Price (\$1,000s) & 279 & 282 & 275 & 262 & 231 & 233 & 266 \\ 
-  Year House was Built & 1967 & 1966 & 1966 & 1971 & 1968 & 1968 & 1967 \\ 
-  House Size (feet$^2$) & 1737 & 1736 & 1743 & 1813 & 1727 & 1775 & 1750 \\ 
-  Lot Size (acres) & 0.25 & 0.25 & 0.25 & 0.26 & 0.25 & 0.26 & 0.25 \\ 
-  Owner Occ (Y = 1, N = 0) & 0.87 & 0.87 & 0.92 & 0.86 & 0.60 & 0.77 & 0.83 \\ 
-  Traffic Noise (dB) & 54.4 & 54.5 & 54.6 & 53.7 & 54.0 & 54.0 & 54.3 \\ 
-  Dist CBD (km) & 14.7 & 14.6 & 14.8 & 15.0 & 14.3 & 14.5 & 14.7 \\ 
-  Dist to  Park (km) & 2.6 & 2.6 & 2.6 & 2.8 & 2.6 & 2.6 & 2.6 \\ 
-  Dist to Lake (km) & 0.9 & 0.9 & 0.9 & 0.9 & 0.9 & 0.9 & 0.9 \\ 
-  Dist to  Shop (km) & 1.9 & 1.9 & 1.8 & 2.0 & 1.9 & 1.9 & 1.9 \\ 
-  Percent Race = White & 84 & 84 & 85 & 86 & 85 & 86 & 85 \\ 
-  Percent Under Age 18 & 28 & 28 & 27 & 28 & 27 & 27 & 27 \\ 
-  Income (\$1,000s) & 72 & 72 & 72 & 75 & 73 & 73 & 73 \\ 
+Sale Price (\$1,000s) & 279 & 282 & 275 & 262 & 231 & 233 & 266 \\ \\
+  Year House was Built & 1967 & 1966 & 1966 & 1971 & 1968 & 1968 & 1967 \\ \\
+  House Size (feet$^2$) & 1737 & 1736 & 1743 & 1813 & 1727 & 1775 & 1750 \\ \\
+  Lot Size (acres) & 0.25 & 0.25 & 0.25 & 0.26 & 0.25 & 0.26 & 0.25 \\ \\
+  Owner Occ (Y = 1, N = 0) & 0.87 & 0.87 & 0.92 & 0.86 & 0.60 & 0.77 & 0.83 \\ \\
+  Traffic Noise (dB) & 54.4 & 54.5 & 54.6 & 53.7 & 54.0 & 54.0 & 54.3 \\ \\
+  Dist CBD (km) & 14.7 & 14.6 & 14.8 & 15.0 & 14.3 & 14.5 & 14.7 \\ \\
+  Dist to  Park (km) & 2.6 & 2.6 & 2.6 & 2.8 & 2.6 & 2.6 & 2.6 \\ \\
+  Dist to Lake (km) & 0.9 & 0.9 & 0.9 & 0.9 & 0.9 & 0.9 & 0.9 \\ \\
+  Dist to  Shop (km) & 1.9 & 1.9 & 1.8 & 2.0 & 1.9 & 1.9 & 1.9 \\ \\
+  Percent Race = White & 84 & 84 & 85 & 86 & 85 & 86 & 85 \\ \\
+  Percent Under Age 18 & 28 & 28 & 27 & 28 & 27 & 27 & 27 \\ \\
+  Income (\$1,000s) & 72 & 72 & 72 & 75 & 73 & 73 & 73 \\ \\
   Elementary Test Scores & 365 & 365 & 365 & 364 & 362 & 366 & 364 \\  \hline
-  Number of Observations &  10,990  & 8,885  &  6,549  & 5,498  &  5,961  & 4,200  & 42,083  \\
+  Number of Observations &  10,990  & 8,885  &  6,549  & 5,498  &  5,961  & 4,200  & 42,083  \\ \hline \hline
     \end{tabular}%
@@
 
-We also created univariate density plots of the variables over time to check for differences in the shape or spread of the distributions over time (see Figure~\ref{fig:DensityPlots}).
-It is not the case that after the recession the distribution ``hollowed out'' in the middle and became bimodal with many high- and low-priced houses selling with few mid-priced homes selling.
-Additionally, maps of the locations of sales transactions over time reveal no discernable patterns, either (see Figure~\ref{fig:SalesYear}).
-The geographic dispersion of sales in earlier years looks surprisingly similar to that of later years.
-Thus, we can find no evidence of only certain types or locations of houses transacting in later years compared to earlier years in our data.
-
-\begin{figure}
-\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/DensityPlotsByYear}}
-\caption{This figure shows the distribution of our variables over time.
+% \begin{figure}
+% \makebox[\textwidth][c]{\includegraphics[height = \textheight]{../graphs/DensityPlotsByYear}}
+% \caption{This figure shows the distribution of our variables over time.
 Note that there are no discernable differences in mean, standard deviation, or shape of the distribution for most variables other than sales price.}
-\label{fig:DensityPlots}
-\end{figure}
+% \label{fig:DensityPlots}
+% \end{figure}
 
@@
 \caption{This figure shows the spatial distribution of observed sales prices over time.
-The change in color from 2005 to 2010 denotes the dramatic drop in sales prices associated with the recession of 2008-09.
+The change in color from 2005 to 2010 denotes the drop in sales prices associated with the recession of 2008-09.
 There are clear spatial patterns in  house prices that persist over time (locations with relatively high vs.
@@
 \section{Basic Econometric Model}\label{basicModel}
-Our aim is to estimate the marginal willingness to pay for different attributes, in particular changes in the traffic noise associated with the house.
-Consistent with past research, this study implements a semi-logarithmic hedonic pricing model.
+Consistent with past research, this study estimates a semi-logarithmic hedonic price functon.
 Before implementing the Locally Weighted Regression model, we present the results of a simpler econometric model given by equation~\eqref{eq:model}.
@@
 Noise$_i$ is the noise level for house $i$, $S_i$ is a vector of the house's structural attributes, $N_i$ is a vector of the neighborhood attributes, and $T_i$ is a vector of time fixed effects.
-Due to the semi-logarithmic functional form of the model, we can interpret the regression model coefficients as the price semi-elasticities of the underlying attributes.
-For instance, we can interpret the coefficient on noise as the percentage increase in price for a one decibel increase in the traffic noise associated with the transaction in our dataset.
+Model (A) in Table \ref{tab:globalRegression} displays the results of this basic Ordinary Least Squares regression model.
+In addition to the important structural and neighborhood variables, we also include fixed effects for each city and an interaction term between month and year of sale in the dataset to allow for unique month-to-month price shocks.
+The traffic noise coefficient suggests houses in our data that are similar in all respects but a one decibel difference in noise will, on average, have sales prices roughly 0.27 percent lower at the noisier location.
 
@@
   & & & & \\ 
- Percent Under 18 & -0.0001 & 0.00002 & -0.0002 & -0.0006 \\ 
+ Percent Under Age 18 & -0.0001 & 0.00002 & -0.0002 & -0.0006 \\ 
   & (0.0001) & (0.0002) & (0.0004) & (0.0005) \\ 
@@
 \hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\multicolumn{5}{l}{Note: (Standard errors) and $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 \end{tabular} 
@@
 
-Model (A) in Table \ref{tab:globalRegression} displays the results of a basic Ordinary Least Squares regression model.
-In addition to the important structural and neighborhood variables, we also include fixed effects for each city and month of sale in the dataset to allow for month-to-month shocks to prices.
-The traffic noise coefficient suggests houses in our data that are similar in all respects but a one decibel difference in noise will, on average, have sales prices roughly 0.27 percent lower at the noisier location.
+Further exploratory analysis suggests the assumption of temporal and geographic stationarity of the hedonic price function is inappropriate.
+We first tested for temporal changes in the coefficients for house size, lot size, and noise by creating interaction terms between these variables and the month*year fixed effects.
+In all three cases the improved model fit was significantly more than expected due to random chance.
+Columns (B)--(D) of Table~\ref{tab:globalRegression} show the results of restimating model (A) using only sales within three separate years of data to allow all coefficients to vary over time.
+Subsequent work with models (B)--(D) also suggested that many of the important regression coefficients vary across the different cities within our sample.
+We rejected the null hypothesis that interaction terms between cities and house size, lot size, noise, etc.
+are zero.\footnote{Results of specific hypothesis tests are available upon request.}  These results should be taken with appropriate skepticism, as the models are simple Ordinary Least Squares regressions and the spatial and temporal nature of the data likely violate assumptions of the Classical Linear Regression Model.
+However, the initial findings suggest the relationship between house prices and many other hedonic characteristics in our data vary over space and time.
 
-Further exploratory analysis suggests the assumption of temporal and geographic stationarity of the hedonic price function is overly restrictive and needs to be relaxed.
-We first tested for temporal changes in the coefficients for house size, lot size, and noise by creating interaction terms with these variables and the month*year year fixed effects.
-In all three cases the improved model fit was significantly more than expected due to random chance.\footnote{The results of specific hypothesis tests are available upon request.} Columns (B) - (D) of Table \ref{tab:globalRegression} show the results of restimating Model (A) using only sales within three separate years of data.
-Subsequent analysis also suggests that many of the important regression coefficients vary across the different cities within our data.
-We are able to reject the null hypothesis that the interaction terms between cities and important variables (house size, lot size, noise, etc.) are zero, even after limiting the analysis to only houses sold within a given year (for instance, by adding the interaction terms to model specifications (B) - (D)).\footnote{Results of specific F-tests are available upon request.}
-
-These results should be taken with appropriate skepticism, as the models are simple Ordinary Least Squares regressions and the spatial and temporal nature of the data likely violate assumptions of the Classical Linear Regression Model.
-However, the initial findings seem to suggest that the relationship between house prices and many other hedonic characteristics may vary over space and time.
-While methods exist for parameterizing this variation \citep[such as spatial expansion as suggested by][]{Casetti1972}, we have no a priori knowledge of how to parameterize the variation.
-As such, we turn to a semi-parametric form of hedonic regression, a flexible modeling approach which lets the data reveal how relationships vary, rather than specifying them beforehand.
-Such a modeling choice will allow us to perform additional tests of the hypotheses of spatial and temporal stationarity in the regression model.
+While methods exist for parameterizing variation in the hedonic function \citep[such as spatial expansion as suggested by][]{Casetti1972}, we have no a priori knowledge of how to parameterize the variation and therefore turn to a semi-parametric form of hedonic regression estimation.
+This flexible modeling approach lets the data reveal how relationships vary, rather than requiring the researcher to specify them beforehand.
 
@@
 This function assigns weights close to 1 for data points near observation $i$, weights positive but closer to zero for observations farther away, and zero for all $n-k$ observations farther away than the $k^{th}$ nearest observation.
-We estimate LWR coefficients using bandwidths ranging from as small as $k=50$ observations and as large as 10,000 observations.
-We choose the LWR bandwidth my minimizing the Generalized Cross Validation score as detailed in equation~\eqref{eq:GCV},
+We estimate LWR coefficients using bandwidths ranging from as small as $k=100$ observations and as large as 4,000 observations.
+
+We measure the LWR model fit by calculating the Generalized Cross Validation score as detailed in equation~\eqref{eq:GCV},
 \begin{equation}\label{eq:GCV}
@@
 %\section{Results}
-Similar to the basic econometric model described in Section \ref{basicModel}, the LWR model estimates the logged sales price of a house as a function of structural and neighborhood variables, location and time.
-In order to account for changing market conditions in our data as manifested in regression coefficients that vary over time, when estimating LWR coefficients we use only houses sold within the past 12 months and also include month fixed effects to account for seasonality.
-Thus, the coefficient estimates at a particular house are estimated using data from other sales nearby in both time and geography.
+Similar to the basic econometric model described in Section \ref{basicModel}, we estimated the LWR model with logged sales price as a function of structural and neighborhood variables, location and time.
+In order to account for changing market conditions over time, when estimating the LWR model for a particular observation in our data, we used only houses sold within the past 12 months and also included month fixed effects to account for seasonality and other changes such as tax credits for home purchases.
+Thus, the coefficient estimates at a particular house were estimated using data from other sales nearby in both time and geography.
 
 \subsection{Improved Model Performance}
-The use of the Locally Weighted Regression model significantly increases model performance as measured by the generalized cross validation score.
-Figure \ref{fig:GCVmodel} displays the Generalized Cross Validation score for three different model specifications estimated at the ``global'' level as well as with varying numbers of observations included in the regression bandwidth.
-We estimate three different hedonic function specifications with different levels of additional spatial control variables.
-Model (1) includes the noise variable, the basic structural characteristics (size of the house in square feet, size of the lot in acres, a categorical variable denoting the architectural style of the house, and whether or not the house is owner-occupied) plus month of sale*year fixed effects.
-Model (2) includes all of the str adds neighborhood and locational variables to the previously described model (test scores at the local elementary school, census tract median income, percent of the census block population that is white, percentage of the census block that is under age 18 and distances to the central business district, nearest park, nearest shopping center, and nearest lake).
-The third model adds city fixed effects to the second model.
-Thus Model (3) explicitly includes both common important characteristics of neighborhood quality while also allowing for spatial heterogeneity in the regression coefficients, and even city-level fixed effects to control for omitted variables that vary at the municipal level.
+The use of the Locally Weighted Regression model significantly improved model performance.
+Figure \ref{fig:GCVmodel} displays the GCV score for three different model specifications estimated at the ``global'' level as well as with varying numbers of observations included in the regression bandwidth.
+We estimated three different hedonic function specifications with different levels of additional spatial control variables.
+Model (1) included the noise variable, the basic structural characteristics (size of the house in square feet, size of the lot in acres, a categorical variable denoting the architectural style of the house, and whether or not the house is owner-occupied) plus month of sale*year fixed effects.
+Model (2) added neighborhood and locational variables (test scores at the local elementary school, census tract median income, percent of the census block population that is white, percentage of the census block that is under age 18 and distances to the central business district, nearest park, nearest shopping center, and nearest lake).
+Model (3) added city fixed effects to Model (2), thus explicitly including both common important characteristics of neighborhood quality while also allowing for spatial heterogeneity in the regression coefficients, and even city-level fixed effects to control for omitted variables that vary at the municipal level.
 
 Two important conclusions can be drawn from these results.
-Model (3) consistently outperforms the other two models-- slightly better than Model (2) and considerably better than Model (1).
-Thus, even conditional on having modeled the data with local regression, the inclusion of more neighborhood-level variables substantially improves the model fit.
-Second, local analyses perform significantly better than global models.
-The minimum GCV score is obtained using a bandwidth of 500 nearest houses and a model including structural, neighborhood, and locational variables in addition to time and city fixed-effects.
+First, local analyses performed significantly better than global models.
+All three models have significantly lower GCV scores across a range of local bandwidths compared to their global counterparts.
+Secondly, even conditional on having performed local analysis, adding additional explanatory neighborhood and locational variables still improved model fit.
+Overall, Model (3) consistently outperformed the other two models-- albeit only slightly better than Model (2).
+The minimum GCV score was obtained using a bandwidth of 500 nearest houses and a model including structural, neighborhood, and locational variables in addition to time and city fixed-effects.
 
@@
 & \multicolumn{4}{c}{Dependent Variable = ln(Sales Price)} \\ \\
- & \multicolumn{1}{c}{Nearest 500$^*$ sales} & \multicolumn{1}{c}{Nearest 650 sales} & \multicolumn{1}{c}{Nearest 1,000 sales} & \multicolumn{1}{c}{Nearest 2,000 sales} \\ \hline \\
+ & \multicolumn{1}{c}{Nearest 500 sales\ding{105}} & \multicolumn{1}{c}{Nearest 650 sales} & \multicolumn{1}{c}{Nearest 1,000 sales} & \multicolumn{1}{c}{Nearest 2,000 sales} \\ \hline \\
 \multicolumn{1}{l}{Noise (dB)} & \multicolumn{1}{c}{-0.0034} & \multicolumn{1}{c}{-0.0034} & \multicolumn{1}{c}{-0.0033} & \multicolumn{1}{c}{-0.0032} \\ 
@@
 \hline \\[-1.8ex] 
-\multicolumn{1}{l}{Observations} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} \\ 
+\multicolumn{1}{l}{Observations\ding{61}} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} & \multicolumn{1}{c}{31,737} \\ 
 \multicolumn{1}{l}{GCV score} & \multicolumn{1}{c}{0.0271} & \multicolumn{1}{c}{0.0271} & \multicolumn{1}{c}{0.0274} & \multicolumn{1}{c}{0.0283} \\ 
-\multicolumn{1}{l}{Moran's I statistic$^{**}$} & \multicolumn{1}{c}{0.027} & \multicolumn{1}{c}{0.031} & \multicolumn{1}{c}{0.037} & \multicolumn{1}{c}{0.049} \\ \hline \hline
-\multicolumn{5}{p{5.5 in}}{$^*$ A bandwidth of 500 implies that the nearest 500 houses sold within the past 12 months are included.} \\
-\multicolumn{5}{p{5.5 in}}{$^{**}$ For comparison, the Moran's I statistic for Model A in Table~\ref{tab:globalRegression} is 0.188.} \\
+\multicolumn{1}{l}{Moran's I statistic\ding{71}} & \multicolumn{1}{c}{0.027} & \multicolumn{1}{c}{0.031} & \multicolumn{1}{c}{0.037} & \multicolumn{1}{c}{0.049} \\ \hline \hline
+\multicolumn{5}{p{5.5 in}}{\ding{105} A bandwidth of X implies that only the nearest X houses sold within the past 12 months receive positive weights in the locally weighted regression.} \\
+\multicolumn{5}{p{5.5 in}}{\ding{61} Fewer LWR coefficient estimates are obtained than the total sample size because we only estimate the regression for houses that have 12 months of previous sales to include in the local regression.} \\
+\multicolumn{5}{p{5.5 in}}{\ding{71} For comparison, the Moran's I statistic for Model A in Table~\ref{tab:globalRegression} is 0.188.} \\
 \end{tabular} 
@@
 
-Table~\ref{tab:LWR} shows the results for our LWR Model (3) with four different bandwidths: the GCV minimizing bandwidth of 500 nearest sales as well as three larger bandwidths: 650, 1,000, and 2,000 nearest sales.
-For each bandwidth, we display the mean LWR coefficient as well as the 10$^{th}$ and 90$^{th}$ percentile values.
-In addition to having smaller GCV scores than the global model, the LWR models substantially reduce the amount of spatial autocorrelation in our regression residuals (the Moran's I statistic for the global model is seven times larger than for the 500 nearest sales model).
+Table~\ref{tab:LWR} shows the results from LWR Model (3) with four different bandwidths: the GCV minimizing bandwidth of 500 nearest sales as well as three larger bandwidths: 650, 1,000, and 2,000 nearest sales.
+For each bandwidth, we display the mean LWR coefficient as well as the 10$^{th}$ and 90$^{th}$ percentile values in parentheses to give a sense of the variation.
+In addition to having smaller GCV scores than the global model, the LWR models substantially reduced the amount of spatial autocorrelation in our regression residuals (the Moran's I statistic for the global model was seven times larger than for the 500 nearest sales model).
 
-The mean LWR coefficient for the noise variable is similar across the different bandwidths (approximately a third of a percent difference in house sales prices for each additional decibel of noise, all other varibles held constant).
-Unsurprisingly, the spread of the coefficient distribution is greater for the smaller bandwidths.
-We now turn to investigating whether this increased dispersion appears from the stochastic nature of smaller sample sizes, or due to heterogeneity in the hedonic function.
-In the next three subsections we describe the results of hypothesis tests that lead us to believe that LWR modeling is an appropriate and beneficial research strategy.
+The mean LWR coefficient for the noise variable is similar across the different bandwidths (approximately a third of a percent difference in house sales prices for each additional decibel of noise, all other varibles held constant) and also more negative than the OLS value presented previously.
+Unsurprisingly, the dispersion of the coefficient distributions are greater for the smaller bandwidths.
+We now turn to investigating whether this increased spread is due to the stochastic nature of smaller sample sizes or spatial heterogeneity in the hedonic function.
+In the next three subsections we describe the results of hypothesis tests that lead us to believe that LWR modeling is an appropriate and beneficial research strategy due to significant spatial and temporal variation in the hedonic function.
 
@@
 
-We first conducted a Monte Carlo simulation recommended in \citet{Fotheringham2002} to see if the improved model fit with our LWR models was due to random chance.
-The intuition of the test is as follows - if the improved model fit isn't significant, then we should be able to see similar improvements in model fit by using the LWR model with the same houses but in a different spatial arrangement.
-Failing to recreate a spatial arrangement that yields a similar model fit as to that obtained with our actual data is then evidence that our spatial arrangement and the improved model fit obtained from a spatially heterogeneous model is significant.
+We first conducted a Monte Carlo simulation recommended by \citet{Fotheringham2002}.
+We repeatedly resampled (without replacement) the locations of our house transactions and calculated the GCV scores for multiple different LWR model bandwidths.
+By comparing the actual GCV scores from our data to those with the simulated data we can test the hypothesis that our improved model fit was due to random chance.
+The intuition of the test is as follows - if we observe similar improvements in model fit with different spatial arrangements of our data, we conclude that the improved model fit in our actual data could have been due to random chance.
+Failing to recreate a spatial arrangement that yields a similar model fit as to that obtained with our actual data is then evidence that our spatial arrangement and the improved model fit obtained from a spatially heterogeneous model is unique.
 
-We conducted 100 different experiments in which we randomly resampled (without replacement) the locations of our house transactions.
-In each case we then estimated the LWR model using 10 different bandwidths ranging from the nearest 100 to 4,000 sales just as before and calculated the GCV score.
+We conducted 100 different experiments using 10 different bandwidths ranging from the nearest 100 to 4,000 sales (within the past 12 months).
+After running a thousand different local regression models with the simulated data, we never obtained model performance anywhere near our actual model fit at a bandwidth of 500 nearest sales.
+Second, the simulated data consistently produced an inverse relationship between GCV scores and bandwidth size: in every single experimental iteration the smallest GCV score was obtained at the largest bandwidth.
+This is in stark contrast to our results with the actual data which had a significant reduction in GCV score for local analysis.
+
 Figure~\ref{fig:GCVSIM} shows the distribution of the GCV scores we obtained for the simulated data for four selected bandwidths relative to the score we obtained with our actual data.
-Note that the GCV distributions for the simulated data a strongly related their bandwidth - smaller bandwidths have larger GCV scores.
-That is, with our randomized location data, the GCV score is inversely proportional to the bandwidth.
-Additionally, note that no GCV scores from the simulated data are near our GCV score with the actual data.
-In every single instance the smallest Generalized Cross-Validation score was obtained at the largest bandwidth.
-That is, in 100 consecutive opportunities to fit our data at a local level of a couple hundred nearest sales up to a couple thousand nearby sales, the GCV score was always smallest for the largest possible bandwidth.
-In other words, after running a thousand different local regression models on the shuffled data, we never obtained model performance anywhere near the LWR model with our true locational data.
-This seems to be strong evidence that the increased ability to predict house prices with a local model is not due to chance and that there is spatial non-stationarity in the hedonic function.
+Note the distinctly smaller GCV score obtained with our actual data at the bandwidth of 500 nearest sales compared to all others.
+The results of this simulation present strong evidence that spatially stationary hedonic functions would be inappropriate for these data.
+The increased ability to predict the house prices in our data suggests local models allowing for spatially varying relationships are needed.
 
@@
 However, we have not yet established which variables have spatially varying coefficients.
-Figures~\ref{fig:AcreBetas} -- \ref{fig:NoiseBetas} show the spatial variation in the estimated LWR coefficients for three important variables, lot size, house size, and noise.
+Figures~\ref{fig:AcreBetas}--\ref{fig:NoiseBetas} show the spatial variation in the estimated LWR coefficients for three important variables, lot size, house size, and noise.
 For comparison, we present the results across four different levels of local analysis, ranging from LWR bandwidths of 500 nearest houses to the nearest 2,000 sales.
 
-A few patterns are clear in Figures~\ref{fig:AcreBetas} -- \ref{fig:NoiseBetas}.
-For instance, across all four bandwidths we see that the hedonic coefficient\footnote{Remember that the dependent variable is the log of sales price.} on lot size (measured in acres) is largest near the central business district of St.\ Paul.
-Thus, consistent with standard urban economic theory, to the extent that the hedonic coefficient is correlated with the price of land, our results suggest the price of land is highest near the central business district and declines with distance from the CBD.
-This tendency is consistent across the four different bandwidths presented (other specific results available upon request).
-The LWR coefficients on house size (measured in thousands of square feet of finished space) also seem to exhibit spatial variation across the different bandwidths.
-In the west-central portion of our study area (a collection of notably desirable neighborhoods) we see a cluster of large LWR coefficients, while those areas in the southernmost portion of our region (suburban areas) have the smallest coefficients.
+A few patterns are clear.
+Figure~\ref{fig:AcreBetas} shows that the hedonic coefficient on lot size is largest near the central business district of St.\ Paul.
+Consistent with standard urban economic theory, to the extent that the hedonic coefficient is correlated with the price of land, our results suggest the price of land is highest near the central business district and declines with distance from the CBD.
+This tendency is consistent across the four different bandwidths, whenever our model ``allowed'' the lot size coefficient to vary over space we saw patterns like these.\footnote{Results for other bandwidths available upon request.}
+
+The LWR coefficients on house size (measured in thousands of square feet of finished space) also seem to exhibit spatial variation in Figure~\ref{fig:HouseBetas}.
+In the west-central portion of our study area (a collection of notably desirable neighborhoods nestled between the Minneapolis and St.\ Paul CBDs) we see a cluster of large LWR coefficients, while those areas in the southernmost portion of our region (suburban areas) have the smallest coefficients.
 
@@
 In this figure the red areas represent large negative coefficients, while yellow areas are characterized by values closer to zero.
-It is interesting to note that for the smaller bandwidths, the area with the most negative noise coefficients is ringed by some of the coefficients closest to zero (and even greater than zero in some cases).
-As the bandwidth increases to 1000 or 2000 nearest houses, the variation in noise coefficients decreases substantially.
+The area with the most negative noise coefficients is ringed by some of the coefficients closest to zero (and even greater than zero in some cases) for smaller bandwidths.
+As the bandwidth increases to 1,000 or 2,000 nearest houses, the variation in noise coefficients decreases substantially.
 In contrast to the previous two figures, we have largely eliminated the ``hot spots'' that appear in the smaller bandwidths.
@@
 
-We now conduct a second series of simulation experiments aimed at testing whether the spatial variation exhibited in particular coefficients is significant or due to random chance.
+We conducted a second series of simulation experiments aimed at testing whether the spatial variation exhibited in particular coefficients was significant or due to random chance.
 The mechanics of the second simulation are very similar to the those described in the previous section.
-We randomly change the spatial arrangment of our house sales and estimate the LWR model.
-However, in this simulation we compare the \emph{spread} (rather than the degree of model fit) of the regression coefficient estimates under the random arrangment of the data to the spread found in our original LWR models with the actual spatial arrangement, conditional on bandwidth.
-If an explanatory variable in our hedonic regression function exhibits a stationary relationship with sales prices, then we should see similar levels of dispersion in the randomly arranged data as in our true data.
-However, if the dispersion we see in our randomized data is \emph{smaller} than the spread we observed in our actual data, that is evidence consistent with the variable having a non-stationary relationship.
-That is, the variation in regression coefficients obtained in our data is higher than we observe from random chance.
+We randomly changed the spatial arrangement of our house sales and re-estimated the LWR model.
+However, in this simulation we compared the \emph{spread} of the regression coefficients (as measured by the standard deviation).\footnote{Whereas in the first simulation we compared the model fit.} If we observed similar levels of dispersion for variable coefficients in the randomly arranged data as in our true data, then we cannot reject the null hypothesis of a stationary relationship.
+However, significantly \emph{greater} dispersion of regression coefficients with our actual data would provide evidence consistent with the variable having a non-stationary relationship.
 
-We conducted this simulation 100 times for the same four different bandwidths in Table~\ref{tab:LWR}- 500, 650, 1,000 and 2,000 nearest observations.
-Across all bandwidths we obtain similar results, so for brevity's sake we present the results for the 500 and 2,000 bandwidth sizes\footnote{Additional results available on request.} in Figure~\ref{fig:MCsim2}.
-The solid red (blue) lines show the distribution of the coefficient standard deviations we obtained from the 100 simulations for the 2,000 (500) nearest sale bandwidths.
-Across all variables it is the case the the distribution of standard deviations is significantly larger for the smaller bandwidth.
-That is, when we use smaller bandwidths we tend to see greater dispersion in regression coefficients.
-We also plot the standard deviation of our coefficients from our actual data as vertical dashed lines (again, color denotes the bandwidth size (red=2,000 and blue=500).
-For most variables, the standard deviation of the LWR coefficients obtained with our actual data is significantly greater than any standard deviation obtained with the randomized simulated data.
-That is, across our simulated data we never saw anywhere near the level of dispersion in regression coefficients for house size, lot size, etc.
-that we observe with our actual data.
-This seems to be strong evidence that many of our regression coefficients in our hedonic function exhibit spatial non-stationarity.
-However, for some variables (note the distributions for noise, owner occupancy and percent under age 18) for which our observed spread in the LWR coefficients is similar when we used the simulated data.
-This simulation does not present evidence that these variables exhibit a non-stationary relationship in our hedonic function.
+We conducted this experiment 100 times and obtained similar results for several different bandwidths.
+For most variables, the standard deviation of the LWR coefficients obtained with our actual data was significantly greater than any standard deviation obtained with the randomized simulated data.
+We never observed a level of coefficient dispersion anywhere near the actual coefficient standard deviations for variables like house size, lot size, and most others.
+This can be seen in Figure~\ref{fig:MCsim2} by comparing the dashed lines of a given color to the respective solid colored distributions.\footnote{For brevity's sake we present the results for the 500 and 2,000 bandwidth sizes in Figure~\ref{fig:MCsim2}.
+Additional results available on request.} However, for variables like noise, owner occupancy and percent of the census block population under age 18, our observed spread in the actual LWR coefficients is similar to the simulated data.
+In these cases we therefore do not reject the null hypothesis of spatial stationarity.
+Overall, this simulation suggests that most of our variables seem to exhibit a significant non-stationary relationship with logged sales prices, but noise does not seem to be one of them.
 
@@
  \makebox[\textwidth][c]{\includegraphics[height=.9\textheight]{../graphs/MCsimResultsSDsk500and2000final}}
- \caption{This figure shows the actual standard deviation in LWR coefficients as compared to those obtained from 100 different instances of spatial randomization.
-Results are presented for two different bandwidths (nearest 500 and 2,000) for our regression variables.
+ \caption{This figure shows the actual standard deviation in LWR coefficients (dashed line) compared to standard deviations obtained from 100 different instances of spatial randomization (solid lines).
+Results are presented for two different bandwidths (nearest 500 and 2,000 denoted by color) for each explanatory variable.
 In all cases the distribution of standard deviations for the smaller bandwidth is larger.
-In most cases the standard deviation of LWR coefficients for the actual data (the dashed line) is substantially higher than any standard deviation obtained with simulated data.}
+In most cases the standard deviation of LWR coefficients for the actual data is substantially higher than any standard deviation obtained with the simulated data, but not for the noise variable.}
  \label{fig:MCsim2}
@@
 
-We know that house prices in the United States fell dramatically during and after the Great Recession of 2008-09.
-We know less about the patterns of change in the hedonic price functions during and after the fall in house prices.
-\citet{Cho2011b} found evidence from hedonic analysis in Nashville, Tennessee, that consumers' willingness to pay for environmental amenities (such as proximity to open space and water views) decreased during the recession as compared to the previous economic boom.
-Previous research has suggested that the impact of noise can change with time and economic conditions.
-For instance, \citet{Wilhelmsson2000} found that the traffic noise penalty to be stronger in the 1990s near Stockholm, Sweden compared to the 1980s.
-\citet{Cohen2009} also found the (airport) noise penalty to be larger in the early 2000s compared to the late 1990s in Atlanta, Georgia.
-
-Figures~\ref{fig:AcreTime}--\ref{fig:NoiseTime} show the spatial distribution of some our LWR hedonic coefficients for bandwidths of 500 and 2,000 nearest sales within the last year for the sale years 2006--2010.
-For both bandwidths presented\footnote{Additional results available upon request.}, the figures show that the estimated LWR coefficients are different over time.
-In particular, the lot size and house size coefficients tend to decrease over time.
+House prices fell dramatically in the United States during and after the Great Recession of 2008-09.
+We know little about the patterns of change in the hedonic price functions during and after the fall in house prices.
+Figures~\ref{fig:AcreTime}--\ref{fig:NoiseTime} show the spatial distribution of some our LWR hedonic coefficients for bandwidths of 500 and 2,000 nearest sales for the years 2006--2010.
+The estimated LWR coefficients are different over time.
+In particular, the positive lot size and house size coefficients tend to decrease over time.
 These results are consistent with standard economic theory, as wealth and income decrease, consumer willingness to pay for normal goods decreases.
@@
 
-We also find statistical evidence consistent with the estimated noise coefficients being more negative in the later time periods.
-This finding is robust to multiple different formulations and specifications.
+We also found significant statistical evidence across multiple different formulations and specifications consistent with the estimated noise coefficients being more negative in the later time periods.
 Tables~\ref{tab:noisebetatime500} and \ref{tab:noisebetatime2000} present the results of regressions using our estimated LWR noise coefficient as the dependent variable and time and spatial characteristics as explanatory variables for LWR bandwidths of 500 and 2,000 nearest sales.
 Both tables are structured similarly.
-Column (1) finds evidence of a negative linear trend in the LWR noise coefficients over time - predicting a LWR noise coefficient of approximately twice the magnitude for the end of our study period as for the beginning.
-Column (2) includes a quadratic term and again predicts noise coefficients much more negative towards the end of our study period compared to the beginning.
-We repeat the regressions from (1) and (2) in (3) and (4) but this time also include city fixed effects in order to control for any potential locational differences of house transactions over time.
-Again, we see very similar results - the noise coefficient is more negative in later time periods.
-We also limit our analysis to just the city of St.\ Paul and repeat the analysis from (1) and (2) in columns (5) and (6).
-Again, we estimate the noise coefficient to be substantially more negative in later time periods.
+Column (1) shows a significant negative linear trend in the LWR noise coefficients over time - predicting a LWR noise coefficient of approximately twice the magnitude for the end of our study period as for the beginning.
+Column (2) includes a significant quadratic term and again predicts noise coefficients much more negative towards the end of our study period compared to the beginning.
+We repeat the regressions from (1) and (2) in (3) and (4) but this time also included city fixed effects to control for  potential locational differences of house transactions over time.
+Again, we found very similar results - the noise coefficient is more negative in later time periods.
+We also limited our analysis to just the city of St.\ Paul and repeated the analysis from (1) and (2) in columns (5) and (6).
+Again, the noise coefficients were found to be substantially more negative in later time periods.
 
@@
 
-The hedonic analysis results presented suggest that noise exhibits a significant negative effect on house prices and that the hedonic function varies over space and time.
-These results and analysis rest on important assumptions, which if violated, may change the results.
-This section describes three important considerations worthy of discussion and needed to contextualize our results: causation vs.\ correlation, potential temporal problems with our data, and omitted variable bias.
+Our results have shown a significant negative relationship between house prices and noise, all other things equal.
+This section describes three important considerations worthy of discussion to help contextualize our results: causation vs.\ correlation, potential temporal problems with our data, and omitted variable bias.
 
-In a stronger research design, we would observe the same houses over time and randomly ``treat'' some houses with more or less noise to observe the change in price relative to the control houses.
-Such a study is not feasible and we are therefore limited to a hedonic analysis with observational data.
-Our conclusions, then, should be interpretted like most other hedonic analysis results and, while we find a strong negative correlation between noise and house prices, we cannot definitely state that noise \emph{causes} lower sales prices.
+In order to make claims that noise causes a change in house prices, we would ideally observe the same houses over time and randomly ``treat'' some houses with more or less noise to observe the change in price relative to the control houses.
+Such a study is not feasible with our data and we are therefore limited to a hedonic analysis with observational data.
+Our conclusions, then, should be interpretted like most other hedonic analysis results and, while we find a strong negative correlation between noise and house prices, we cannot state that noise \emph{causes} lower sales prices.
 
-Future work may want to further investigate this correlation for more evidence consistent with causation.
-For instance, by collecting data on the quality of house windows one could test for differential effects of more soundproof windows in noisier areas vs.
-quieter areas.
-Unfortunately, such house characteristics are unavailable for this study.
+Our noise variable is also a model estimate, not a direct measurement of the noise levels encountered by house purchasers.
+The model controls for the most important determinants of average noise exposure-- the level of the noise source, the distance and elevation change from the source, the intervening buildings, sound barriers, and foliage, but of course there is undoubtedly error.
+House purchasers may have visited the property on particularly busy traffic days, or on days with weather conditions more or less conducive to noise propagation across the landscape.
+Future researchers may seek to collect actual noise exposure data, but this will be a daunting task.
 
-Our work faces other data limitations.
-Notably, while our house sales data are collected over the course of six years, the traffic noise estimates are for the year 2007.
-To the extent that traffic flows and composition significantly changed over time, our traffic noise variables may be inaccurate for those other time periods.
-However, Table VM2 from the US.
+Our work faces other notable data limitations.
+While our house sales data were collected over the course of six years, the noise estimates are for the year 2007.
+To the extent that traffic flows changed with the economic recession, our noise variable could be inaccurate for other years.
+However, we believe these potential changes are miniscule.
+Table~VM2 from the US.
 Department of Transportation Office of Highway Policy Information website reports that in the year 2007 there were approximately 30 million vehicle miles traveled in the urban areas of the state of MN, while for years 2008, 2009, and 2010 the respective values were 32.5, 32.3, and 32.0 million vehicle miles.
 Overall, this represents a change of less than 10 percent.
-\footnote{\url{http://www.fhwa.dot.gov/policyinformation/quickfinddata/qftravel.cfm}} Such small changes in total vehicle miles traveled are unlikely to yield significant differences in noise levels.
-Additionally, we do not believe the changes are likely to manifest significant spatial variation in traffic noise, which is ultimately responsible for our identification of the noise regression coefficient.
-However, given enough time for changes in driving habits and technological advancements to gain significant market penetration (for instance, quieter hybrid cars), future work should seek to create time-series noise data in order to obtain even better estimates of the impact of traffic noise over time.
+\footnote{\url{http://www.fhwa.dot.gov/policyinformation/quickfinddata/qftravel.cfm}} Such small changes in total vehicle miles traveled will not yield significant differences in noise level estimates from our model.
 Given the computational complexity of re-estimating the landscape noise surface, such work is beyond the scope of this paper, but may be a worthwhile investment for future work seeking to test the robustness of our results.
 
-Our previously reported results also lack some important control variables in the hedonic function.
-As mentioned previously, we do not have data on the actual level of noise purchasers were exposed to inside the house, which could be altered depending on the quality of insulation, windows, and even time of day, or day of week.
-Locations exposed to more noise due to their proximity to high traffic areas may also be less safe due to the potential for accidents.
+Our model may suffer from omitted variable bias.
+For instance, locations exposed to more noise due to their proximity to high traffic areas may also be less safe due to the potential for accidents.
 Without including a proxy variable for safety, our noise coefficient could be biased - making it appear that home prices are reflecting noise exposure when in fact it could be safety issues.
 Future research aimed at measuring the impact of noise should continue to seek out and control for other confounding variables.
+Another identification strategy suggested by an anonymous referee is to collect data on the quality of windows in the house, which would allow for a test of interaction effects between noise and window quality.
+Unfortunately, such house characteristics were not available for this study.
 
-Our data also omits other structural characteristics and to the extent that variables like the number of bedrooms, bathrooms, garage size, or construction quality co-vary with other variables in our dataset, our regression coefficients will suffer from omitted variable bias.
+Our data also omits other common structural characteristics and to the extent that variables like the number of bedrooms, bathrooms, garage size, or construction quality co-vary with other variables in our dataset, our regression coefficients will be biased.
 We are comforted, however, because we do have some of these important additional variables for a subset of our data.
@@
 \section{Conclusion}
+Precise estimates of the impact of traffic noise are important for efficient implementation of noise mitigation projects.
+The United  States Federal Highway Administration reports that 47 states have constructed noise barriers to reduce noise propagation, spending over a half a billion dollars from 2008-2010 \citepalias{USFHA2012}.
+\citet{Delucchi1998} used an estimate of 0.85 percent reduction in house prices per additional decibel in their cost-benefit analysis of traffic noise.
+While their preferred estimate of the total damage cost to the United States in 1991 is \$3 billion, they report a possible range of less than \$100 million to over \$40 billion due in part to uncertainty surrounding the degree of noise propagation over space in the urban built environment and the effect of noise on house prices.
+Indeed, one of the main conclusions of their work is that more research should be done to better understand the impact of noise on house prices and that better noise data are needed for such work to occur.
+
 We estimated a hedonic price function for single family houses using Locally Weighted Regression techniques in the St.\ Paul, Minnesota, urban area.
@@
 
-Monte Carlo simulations suggest that the better goodness-of-fit provided by the local models are not due to chance and that many hedonic implicit prices vary over space within our study area.
-When the location of our data was randomly assigned and our LWR model was re-estimated across more than a dozen different bandwidths, in 100 consecutive simulations the smallest GCV score was obtained when the data were analyzed at a pooled/global level rather than local.
-That is, after trying thousands of different combinations of varying levels of local analysis with the spatially redistributed data, we never came close to estimating our observed housing sales prices as well as we can with the local analysis on the actual data.
+Monte Carlo simulation results suggest that the better goodness-of-fit provided by the local models were not due to chance and that many hedonic implicit prices vary over space within our study area.
+When the location of our data was randomly assigned and our LWR model was re-estimated across multiple different bandwidths, in 100 consecutive simulations the smallest GCV score was obtained when the data were analyzed at a pooled/global level rather than local.
+That is, after trying thousands of different combinations of varying levels of local analysis with the spatially redistributed data, local analysis never fit the randomized data better than global analysis and we never came close to estimating our observed house sales prices as well as we did with the local analysis on the actual data.
+
 Additionally, re-estimating the LWR model using local bandwidths but randomly assigned locations yielded substantially smaller standard deviations for the majority of our regression coefficients.
-Such differences suggest that the variation exhibited by most of our regression coefficients was not due to simple random chance, but instead is consistent with spatial non-stationarity.
+Such differences suggest that the variation exhibited by most of our regression coefficients was indeed spatial non-stationarity and not due to random chance.
+While our results show very strong evidence that the coefficients on lot size and living space vary over space, the noise coefficient was one of a few variables to have  a standard deviation in the spatially randomized data similar to that obtained with the actual data.
 
-While our results show very strong evidence that the coefficients on lot size and living space vary over space, the noise coefficient was one of a few variables to exhibit similar standard deviations to the simulated distributions obtained from Monte Carlo experiments.
-We do, however, find significant temporal variation in the impact of traffic noise in our data.
-
-Precise estimates of the impact of traffic noise are important for efficient implementation of noise mitigation projects.
-The US Federal Highway Administration reports that 47 states have constructed noise barriers to reduce noise propagation, spending over a half a billion dollars from 2008-2010 \citepalias{USFHA2012}.
-\citet{Delucchi1998} used an estimate of 0.85 percent reduction in house prices per additional decibel in their cost-benefit analysis of traffic noise.
-While their preferred estimate of the total damage cost to the United States in 1991 is \$3 billion, they report a possible range of less than \$100 million to over \$40 billion due in part to uncertainty surrounding the degree of noise propagation over space in the urban built environment and the effect of noise on house prices.
-Indeed, one of the main conclusions of their work is that more research should be done to better understand the impact of noise on house prices and that better noise data are needed for such work to occur.
+We do, however, find significant temporal variation in the noise coefficients-- roughly doubling from a quarter percent per decibel in early 2006 to a half percent per decibel in 2010.
+Such temporal non-stationarity is consistent with previous work like \citet{Wilhelmsson2000} which found the traffic noise penalty to be stronger in the 1990s near Stockholm, Sweden compared to the 1980s and \citet{Cohen2009} which found the (airport) noise penalty to be larger in the early 2000s compared to the late 1990s in Atlanta, Georgia.
+However, the significant increase in magnitude is surprising given the severe economic recession and evidence presented by \citet{Cho2011b} that consumers' willingness to pay for environmental amenities (such as proximity to open space and water views) decreased during the recession as compared to the previous economic boom in Nashville, Tennessee.
 
@@
 
-\newpage
+%\newpage
 \begin{singlespace}

### 2014-07-11 reports/NoiseHedonicRaR.tex
another round of edits to RaR - including removing page numbers from figure pages

@@
 \usepackage{alltt}
-
+\usepackage{floatpag} %floatpag.sty file is just in the reports folder - commands to remove page nos are in first figure
 \usepackage[round]{natbib}
 \usepackage{dcolumn}
+\usepackage{pifont}
 \usepackage{rotating}
@@
 \begin{figure}
-\makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/Overview2column}}
-\caption{This figure shows the spatial extent of our study area, the significant spatial variation in single family house sales prices, as well as our noise data.}\label{fig:overview}
+\floatpagestyle{empty}
+\rotfloatpagestyle{empty}
+\makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/Overview2columnAnnotatedPDF}}
+\caption{This figure shows the spatial extent of our study area, the significant spatial variation in single family house sales prices, as well as our noise data.}
+\label{fig:overview}
 \end{figure}
@@
 \begin{table}
-\caption{Variable Description and Summary Statistics}\label{tab:sumStats}
+\caption{Variable Description and Summary Statistics}
+\label{tab:sumStats}
 \makebox[\linewidth][c]{
 \small
-\begin{tabular}{lD{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}}
-
+\begin{tabular}{lccccccc}%D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}}
+  \hline \hline
  & min & 25\% & 50\% & mean & 75\% & max & st dev \\ 
@@
 % Tue Jun 10 21:29:25 2014
-Sale Price (\$1,000s) & 99 & 195 & 241 & 266 & 315 & 675 & 103 \\ 
-  Year House was Built & 1850 & 1950 & 1973 & 1967 & 1993 & 2010 & 32 \\ 
-  House Size (square feet) & 390 & 1158 & 1628 & 1750 & 2189 & 4000 & 704 \\ 
-  Lot Size (acres) & 0.02 & 0.17 & 0.25 & 0.25 & 0.31 & 0.60 & 0.11 \\ 
-  Owner Occupancy (Yes = 1, No = 0) & 0.0 & 1.0 & 1.0 & 0.8 & 1.0 & 1.0 & 0.4 \\ 
-  Traffic Noise (dB) & 24.5 & 49.0 & 54.0 & 54.3 & 59.5 & 81.6 & 7.5 \\ 
-  Distance to Central Business District (km) & 1.1 & 6.8 & 13.2 & 14.7 & 21.8 & 37.1 & 8.9 \\ 
-  Distance to nearest Park (km) & 0.0 & 1.1 & 2.2 & 2.6 & 3.8 & 9.7 & 1.9 \\ 
-  Distance to nearest Lake (km) & 0.0 & 0.4 & 0.8 & 0.9 & 1.3 & 4.4 & 0.7 \\ 
-  Distance to nearest Shopping Center (km) & 0.0 & 0.9 & 1.5 & 1.9 & 2.3 & 10.8 & 1.6 \\ 
-  Percent of Census Block Population Race = White & 0 & 80 & 90 & 85 & 96 & 100 & 17 \\ 
-  Percent of Census Block Population Under Age 18 & 0 & 21 & 27 & 27 & 33 & 67 & 9 \\ 
-  Median Income in Census Tract (\$1,000s) & 14 & 55 & 69 & 73 & 90 & 143 & 24 \\ 
-  Elementary Test Scores & 336 & 360 & 365 & 364 & 370 & 552 & 11 \\ 
-   \hline
+Sale Price (\$1,000s) & 99 & 195 & 241 & 266 & 315 & 675 & 103 \\ \\
+  Year House was Built & 1850 & 1950 & 1973 & 1967 & 1993 & 2010 & 32 \\ \\
+  House Size (ft$^2$) & 390 & 1158 & 1628 & 1750 & 2189 & 4000 & 704 \\ \\
+  Lot Size (acres) & 0.02 & 0.17 & 0.25 & 0.25 & 0.31 & 0.60 & 0.11 \\ \\
+  Owner Occupancy (Yes = 1, No = 0) & 0.0 & 1.0 & 1.0 & 0.8 & 1.0 & 1.0 & 0.4 \\ \\
+  Traffic Noise (dB) & 24.5 & 49.0 & 54.0 & 54.3 & 59.5 & 81.6 & 7.5 \\  \\
+  Distance to Central Business District (km) & 1.1 & 6.8 & 13.2 & 14.7 & 21.8 & 37.1 & 8.9 \\ \\
+  Distance to Nearest Park (km) & 0.0 & 1.1 & 2.2 & 2.6 & 3.8 & 9.7 & 1.9 \\ \\
+  Distance to Nearest Lake (km) & 0.0 & 0.4 & 0.8 & 0.9 & 1.3 & 4.4 & 0.7 \\ \\
+  Distance to Nearest Shopping Center (km) & 0.0 & 0.9 & 1.5 & 1.9 & 2.3 & 10.8 & 1.6 \\ \\
+  Percent of Census Block Population Race = White & 0 & 80 & 90 & 85 & 96 & 100 & 17 \\ \\
+  Percent of Census Block Population Under Age 18 & 0 & 21 & 27 & 27 & 33 & 67 & 9 \\ \\
+  Median Income in Census Tract (\$1,000s) & 14 & 55 & 69 & 73 & 90 & 143 & 24 \\ \\
+  Nearest Elementary School Test Scores & 336 & 360 & 365 & 364 & 370 & 552 & 11 \\ 
+   \hline \hline
 \end{tabular}

### 2014-08-18 TestFile.R
testing

@@ -1,0 +1,1 @@
+# random new file

### 2014-08-18 reports/NoiseHedonicRaR.Rnw
contains the final version of NoiseHedonicRaR that was (re)submitted to JoRS

@@
 
-\title{Traffic Noise and House Prices: A Hedonic Analysis over Time and Space}
+\title{Hedonic Analysis over Time and Space:\\ The Case of House Prices and Traffic Noise}
 \date{}
@@
 One consequence of the expanding road network and its associated traffic is increased levels of traffic noise.
-While the hedonic literature has consistently found a negative effect of this phenomenon on the real estate market, research in the United States has often relied on crude measures of traffic noise.
+While the hedonic literature has consistently found a negative relationship between real estate prices and noise levels, research in the United States has typically relied on crude measures of traffic noise.
 Here, we reduce the measurement error of traffic noise exposure through a detailed model of noise propagation over the landscape.
-We then estimate the hedonic relationship between noise and house prices using over 40,000 single family home transactions throughout the St.\ Paul, Minnesota, urban area from 2005-2010.
+We then estimate the hedonic relationship between noise and single family house prices using over 40,000 transactions throughout the St.\ Paul, Minnesota, urban area from 2005-2010.
 We implement spatially and temporally flexible local regression techniques and find significant non-stationarity in the hedonic function over time and space.
@@
 
-% Automobiles are already perhaps the greatest source of noise in residential neighborhoods \citep{Barber2010} and traffic noise was estimated to cause around three billion dollars worth of external damage to the United States economy alone in 1991 \citep{Delucchi1998}.
-Traffic noise and its attendant problems are greater now than they were in the 1990s and predicted to worsen in the future \citep{Goines2007}.
-%With the exception of a slight dip during the economic recession in the late 2000s, the number of vehicle miles traveled in the United States has steadily increased for the past 50 years.\footnote{\url{http://www.fhwa.dot.gov/policyinformation/statistics/2011/pdf/rc1c.pdf}}
-% Globally, \citet{Dargay2007} predict the number of personal vehicles to grow from roughly 800 million in 2002 to over two billion units by 2030.
-Additionally, the global trend of increased urbanization is expected to continue, with the proportion of the population living in cities growing from roughly half now to over two-thirds by the middle of the century \citepalias{UNDESA2012}.
-
-One way to estimate some of the costs of traffic noise (and therefore the economic benefits of policies that reduce noise) is through hedonic regression, examining the relationship between house prices and noise levels.
-\citet{Nelson1982} reviewed nine of the earliest noise hedonic articles in the United States and Canada and found an average reduction in house prices of approximately 0.4 percent per additional decibel.
+Hedonic analysis is one way to estimate some of the costs of traffic noise (and therefore the economic benefits of policies that reduce noise) by examining the relationship between house prices and noise levels.
+\citet{Nelson1982} reviewed nine of the earliest hedonic studies in the United States and Canada and found an average reduction in house prices of approximately 0.4 percent per additional decibel.
 Many of these early studies \citep[such as][]{Gamble1974, Langley1976} are plagued by issues of small sample sizes (in the hundreds) and limited spatial extents (one or a handful of cities).
 Recent hedonic research has tended to focus on the European experience, often due to the availability of high quality traffic noise data made available from the government, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Switzerland \citep{Baranzini2010}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, Netherlands \citep{Theebe2004a}, and Germany \citep{Brandt2011}.
-
-%Reviews of the research by \citet{Bateman2001} found that the negative effect of traffic noise on house prices ranged from 0.08 to 2.22 percent per decibel with a mean around 0.55 percent per decibel, while \citet{Navrud2002} found an average decrease of 0.64 percent per decibel.
-Much of the
 
@@
 
-In this paper, we estimate a hedonic relationship between traffic noise and single family house prices across 44 cities and several hundred square miles in the St.\ Paul, Minnesota, urban region by taking advantage of a uniquely detailed set of noise estimates.
+In this paper, we take advantage of a uniquely detailed set of noise data to estimate the hedonic price function for over 40,000 single family house transactions across several hundred square miles in the St.\ Paul, Minnesota, urban region from 2005-2010.
 The data represent perhaps the most accurate regional noise estimates ever used in the hedonic literature in the United States to date due to the high spatial resolution of the estimates (10 m x 10 m) and the incorporation of the effects of nearby buildings and land cover on noise propagation.
@@
 Such Locally Weighted Regression (LWR) models have become increasingly prevalent in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, McMillen2010, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than other standard spatial econometric models under common real world circumstances \citep{McMillen2012}.
-Our results confirm the importance of a spatially- and temporally-flexible modeling approach and reject the still too often used assumptions of spatial and temporal stationarity in the hedonic function.
+Our results confirm the importance of a spatially- and temporally-flexible hedonic modeling approach and reject the still too often used assumptions of spatial and temporal stationarity in the regression function.
 
@@
 \subsection{Time}
-We collected sales transactions from 2005 to 2010 to estimate the hedonic price function over time and test for differences before, during, and after the economic recession.
-We are concerned about issues of sample selection bias over time, however we find no evidence of only certain types or locations of houses transacting in later years compared to earlier years in our data.
-Table \ref{tab:SumStatsTime} displays the mean variable values by year of sale to look for differences over time.
+Due to concerns of sample selection bias before, during, and after the economic recession, we compared the characteristics of our data by year to look for important differences.
+Table \ref{tab:SumStatsTime} displays the mean variable values by year of sale.
 The mean sale price in 2009 (roughly \$230,000) was almost 20 percent lower than the mean sale price in 2006 (roughly \$280,000).
-However, most other variable means have small or no differences in the across time.\footnote{We also created univariate density plots of the variables by year to check for differences in the shape and spread of the distributions over time.
+However, most other variable means show small or no differences across years.\footnote{We also created univariate density plots of the variables by year to check for differences in the shape and spread of the distributions over time.
 With the exception of house prices, we found no differences in the variable distributions over time.
 Figures available upon request.} We also mapped the locations of sales transactions to check for differences in geographic dispersion of sales over time, but found none (see Figure~\ref{fig:SalesYear}).
-Thus, with the exception of lower sales prices in later years, house characteristics in our sample appear similar before, during, and after the economics recession.
+Thus, with the exception of lower sales prices in later years, house characteristics in our sample appear similar before, during, and after the economic recession.
+Of course, it is still possible that the houses differed over time in unobserved characteristics.
 
@@
 
-% \begin{figure}
-% \makebox[\textwidth][c]{\includegraphics[height = \textheight]{../graphs/DensityPlotsByYear}}
-% \caption{This figure shows the distribution of our variables over time.
-Note that there are no discernable differences in mean, standard deviation, or shape of the distribution for most variables other than sales price.}
-% \label{fig:DensityPlots}
-% \end{figure}
-
 \begin{figure}
@@
 Model (A) in Table \ref{tab:globalRegression} displays the results of this basic Ordinary Least Squares regression model.
-In addition to the important structural and neighborhood variables, we also include fixed effects for each city and an interaction term between month and year of sale in the dataset to allow for unique month-to-month price shocks.
+In addition to the important structural and neighborhood variables, we also included fixed effects for each city and an interaction term between month and year of sale.
 The traffic noise coefficient suggests houses in our data that are similar in all respects but a one decibel difference in noise will, on average, have sales prices roughly 0.27 percent lower at the noisier location.
@@
 Locally Weighted Regression (LWR) techniques (also known as Geographically Weighted Regression) are described in detail by \citet{Cleveland1988}, \citet{Brunsdon1998b}, \citet{Fotheringham2002}, and others.
-It is a weighted least squares methodology in which regression coefficients are estimated over space as a function of the local data as described in Equation~\eqref{eq:LWRbeta},
+LWR is a weighted least squares methodology in which regression coefficients are estimated over space as a function of the local data as described in Equation~\eqref{eq:LWRbeta},
 \begin{equation}\label{eq:LWRbeta}
@@
 Similar to the basic econometric model described in Section \ref{basicModel}, we estimated the LWR model with logged sales price as a function of structural and neighborhood variables, location and time.
-In order to account for changing market conditions over time, when estimating the LWR model for a particular observation in our data, we used only houses sold within the past 12 months and also included month fixed effects to account for seasonality and other changes such as tax credits for home purchases.
+In order to account for changing market conditions over time, when estimating the LWR model for a particular observation in our data, we used only houses sold within the past 12 months and also included month fixed effects to account for seasonality and other policy changes such as tax credits for home purchases.
 Thus, the coefficient estimates at a particular house were estimated using data from other sales nearby in both time and geography.
@@
 \begin{figure}
-  \makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/GCVbyModel}}
+  \makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/GCVbyModelFinal}}
 \caption{This figure shows the relationship between bandwidth size and the GCV score for three different Locally Weighted Regression (LWR) models.
@@
 Note that the LWR models all have significantly smaller GCV scores than the global models.
-The minimum GCV score is obtained by LWR Model (3) at a bandwidth of 500 nearest houses.}\label{fig:GCVmodel}
+The minimum GCV score is obtained by LWR Model (3) at a bandwidth of 500 nearest houses.}
+\label{fig:GCVmodel}
 \end{figure}
@@
 The mean LWR coefficient for the noise variable is similar across the different bandwidths (approximately a third of a percent difference in house sales prices for each additional decibel of noise, all other varibles held constant) and also more negative than the OLS value presented previously.
-Unsurprisingly, the dispersion of the coefficient distributions are greater for the smaller bandwidths.
-We now turn to investigating whether this increased spread is due to the stochastic nature of smaller sample sizes or spatial heterogeneity in the hedonic function.
 In the next three subsections we describe the results of hypothesis tests that lead us to believe that LWR modeling is an appropriate and beneficial research strategy due to significant spatial and temporal variation in the hedonic function.
@@
 We first conducted a Monte Carlo simulation recommended by \citet{Fotheringham2002}.
-We repeatedly resampled (without replacement) the locations of our house transactions and calculated the GCV scores for multiple different LWR model bandwidths.
-By comparing the actual GCV scores from our data to those with the simulated data we can test the hypothesis that our improved model fit was due to random chance.
-The intuition of the test is as follows - if we observe similar improvements in model fit with different spatial arrangements of our data, we conclude that the improved model fit in our actual data could have been due to random chance.
-Failing to recreate a spatial arrangement that yields a similar model fit as to that obtained with our actual data is then evidence that our spatial arrangement and the improved model fit obtained from a spatially heterogeneous model is unique.
+We repeatedly resampled (without replacement) the locations of our house transactions and calculated the GCV scores for LWR models across multiple bandwidths.
+We then compared the GCV scores obtained with our actual data to those from the simulated data to see if other spatial arrangements of the data could yield similar model fit.
 
-We conducted 100 different experiments using 10 different bandwidths ranging from the nearest 100 to 4,000 sales (within the past 12 months).
-After running a thousand different local regression models with the simulated data, we never obtained model performance anywhere near our actual model fit at a bandwidth of 500 nearest sales.
-Second, the simulated data consistently produced an inverse relationship between GCV scores and bandwidth size: in every single experimental iteration the smallest GCV score was obtained at the largest bandwidth.
-This is in stark contrast to our results with the actual data which had a significant reduction in GCV score for local analysis.
+We conducted 100 different experiments in which we estimated LWR models across 10 different bandwidths each time.
+In a thousand different local regression models with the simulated data, we never obtained model performance anywhere near our actual model fit at a bandwidth of 500 nearest sales.
+Second, in constrast to the clear positive relationship between bandwidth size and GCV score in Figure~\ref{fig:GCVmodel}, the simulated data consistently produced an inverse relationship between GCV scores and bandwidth size (in every single experimental iteration the smallest GCV score was obtained at the largest bandwidth).
 
@@
 Figures~\ref{fig:AcreBetas}--\ref{fig:NoiseBetas} show the spatial variation in the estimated LWR coefficients for three important variables, lot size, house size, and noise.
-For comparison, we present the results across four different levels of local analysis, ranging from LWR bandwidths of 500 nearest houses to the nearest 2,000 sales.
+For comparison, we present the results across four different LWR bandwidths ranging from 500 to 2,000 nearest sales.
 
@@
 Consistent with standard urban economic theory, to the extent that the hedonic coefficient is correlated with the price of land, our results suggest the price of land is highest near the central business district and declines with distance from the CBD.
-This tendency is consistent across the four different bandwidths, whenever our model ``allowed'' the lot size coefficient to vary over space we saw patterns like these.\footnote{Results for other bandwidths available upon request.}
+This tendency is consistent across the different bandwidths, whenever our model ``allowed'' the lot size coefficient to vary over space we saw patterns like these.\footnote{Results for other bandwidths available upon request.}
 
-The LWR coefficients on house size (measured in thousands of square feet of finished space) also seem to exhibit spatial variation in Figure~\ref{fig:HouseBetas}.
+The LWR coefficients on house size also seem to exhibit spatial variation in Figure~\ref{fig:HouseBetas}.
 In the west-central portion of our study area (a collection of notably desirable neighborhoods nestled between the Minneapolis and St.\ Paul CBDs) we see a cluster of large LWR coefficients, while those areas in the southernmost portion of our region (suburban areas) have the smallest coefficients.
@@
 We randomly changed the spatial arrangement of our house sales and re-estimated the LWR model.
-However, in this simulation we compared the \emph{spread} of the regression coefficients (as measured by the standard deviation).\footnote{Whereas in the first simulation we compared the model fit.} If we observed similar levels of dispersion for variable coefficients in the randomly arranged data as in our true data, then we cannot reject the null hypothesis of a stationary relationship.
+However, instead of examining the model fit, we compared the \emph{spread} of the regression coefficients (as measured by the standard deviation).
+If we observed similar levels of dispersion for variable coefficients in the randomly arranged data as in our true data, then we cannot reject the null hypothesis of a stationary relationship.
 However, significantly \emph{greater} dispersion of regression coefficients with our actual data would provide evidence consistent with the variable having a non-stationary relationship.
 
-We conducted this experiment 100 times and obtained similar results for several different bandwidths.
+We implemented this experiment 100 times for several different bandwidths and obtained consistent results.
 For most variables, the standard deviation of the LWR coefficients obtained with our actual data was significantly greater than any standard deviation obtained with the randomized simulated data.
@@
 \begin{figure}
- \makebox[\textwidth][c]{\includegraphics[height=.9\textheight]{../graphs/MCsimResultsSDsk500and2000final}}
+ \makebox[\textwidth][c]{\includegraphics[height=.9\textheight]{../graphs/MCsim2FinalResults}}
  \caption{This figure shows the actual standard deviation in LWR coefficients (dashed line) compared to standard deviations obtained from 100 different instances of spatial randomization (solid lines).
@@
 
-House prices fell dramatically in the United States during and after the Great Recession of 2008-09.
+House prices fell dramatically in the United States and in our dataset during and after the Great Recession of 2008-09.
 We know little about the patterns of change in the hedonic price functions during and after the fall in house prices.
@@
 
-Our noise variable is also a model estimate, not a direct measurement of the noise levels encountered by house purchasers.
+Our noise variable is also a model estimate, not a direct measurement of the noise levels encountered by potential house buyers when deciding on their willingness to pay for the property.
 The model controls for the most important determinants of average noise exposure-- the level of the noise source, the distance and elevation change from the source, the intervening buildings, sound barriers, and foliage, but of course there is undoubtedly error.
@@
 Table~VM2 from the US.
-Department of Transportation Office of Highway Policy Information website reports that in the year 2007 there were approximately 30 million vehicle miles traveled in the urban areas of the state of MN, while for years 2008, 2009, and 2010 the respective values were 32.5, 32.3, and 32.0 million vehicle miles.
+Department of Transportation Office of Highway Policy Information website\footnote{\url{http://www.fhwa.dot.gov/policyinformation/quickfinddata/qftravel.cfm}} reports that in the year 2007 there were approximately 30 million vehicle miles traveled in the urban areas of the state of MN, while for years 2008, 2009, and 2010 the respective values were 32.5, 32.3, and 32.0 million vehicle miles.
 Overall, this represents a change of less than 10 percent.
-\footnote{\url{http://www.fhwa.dot.gov/policyinformation/quickfinddata/qftravel.cfm}} Such small changes in total vehicle miles traveled will not yield significant differences in noise level estimates from our model.
+Such small changes in total vehicle miles traveled will not yield significant differences in noise level estimates from our model.
 Given the computational complexity of re-estimating the landscape noise surface, such work is beyond the scope of this paper, but may be a worthwhile investment for future work seeking to test the robustness of our results.
@@
 
-Monte Carlo simulation results suggest that the better goodness-of-fit provided by the local models were not due to chance and that many hedonic implicit prices vary over space within our study area.
-When the location of our data was randomly assigned and our LWR model was re-estimated across multiple different bandwidths, in 100 consecutive simulations the smallest GCV score was obtained when the data were analyzed at a pooled/global level rather than local.
-That is, after trying thousands of different combinations of varying levels of local analysis with the spatially redistributed data, local analysis never fit the randomized data better than global analysis and we never came close to estimating our observed house sales prices as well as we did with the local analysis on the actual data.
-
-Additionally, re-estimating the LWR model using local bandwidths but randomly assigned locations yielded substantially smaller standard deviations for the majority of our regression coefficients.
-Such differences suggest that the variation exhibited by most of our regression coefficients was indeed spatial non-stationarity and not due to random chance.
-While our results show very strong evidence that the coefficients on lot size and living space vary over space, the noise coefficient was one of a few variables to have  a standard deviation in the spatially randomized data similar to that obtained with the actual data.
+Monte Carlo simulation results suggest that the better goodness-of-fit provided by the local models were not due to chance and that many regression coefficients vary over space within our study area.
+In over a thousand different trials LWR models with spatially randomized data never fit better than global analysis and we never came close to estimating our observed house sales prices as well as we did with the local analysis on the actual data.
+Subsequent analysis showed that the standard deviations of most LWR coefficients with the randomized data tended to be much smaller than obtained with our actual data.
+While our results show very strong evidence that the coefficients on lot size and living space vary over space, the noise coefficient was one of only a few variables to not show evidence of spatial non-stationarity.
 
@@
 Second, ``mixed'' regression techniques (in which some regression coefficients are constrained to remain constant across the study area while others are allowed to vary) may allow researchers to obtain more precise estimates of the impact of hedonic characteristics by increasing the degrees of freedom in the regression.
-Future work may also seek to re-estimate traffic noise models over time to better account for changes in traffic flows associated with macroeconomic conditions.
-Lastly, researchers should take advantage of the recent suggestions in \citet{Carruthers2010} and use the spatial variation in regression coefficients obtained from LWR models to estimate the second-stage hedonic regressions to identify consumer demand curves for these characteristics.
+Lastly, researchers should seek to leverage improvements in spatial hedonic modelling with the advice of  \citet{Carruthers2010} and use the spatial variation in regression coefficients obtained from LWR models to estimate the second-stage hedonic regressions to identify consumer demand curves for these characteristics, thereby further improving our undertanding of the value of local amenities.
 

### 2014-08-18 reports/NoiseHedonicRaR.tex
contains the final version of NoiseHedonicRaR that was (re)submitted to JoRS

@@
 
-One way to estimate some of the costs of traffic noise (and therefore the economic benefits of policies that reduce noise) is through hedonic regression, examining the relationship between house prices and noise levels.
-\citet{Nelson1982} reviewed nine of the earliest noise hedonic articles in the United States and Canada and found an average reduction in house prices of approximately 0.4 percent per additional decibel.
+Hedonic analysis is one way to estimate some of the costs of traffic noise (and therefore the economic benefits of policies that reduce noise) by examining the relationship between house prices and noise levels.
+\citet{Nelson1982} reviewed nine of the earliest hedonic studies in the United States and Canada and found an average reduction in house prices of approximately 0.4 percent per additional decibel.
 Many of these early studies \citep[such as][]{Gamble1974, Langley1976} are plagued by issues of small sample sizes (in the hundreds) and limited spatial extents (one or a handful of cities).

### 2014-08-18 analysis/04MonteCarloSim/Revision/FinalMCsimVisualizer.R

@@ -15,8 +15,8 @@ load("../Data/R2GIS/CleanData/TimeLag12months/Sales20052010LWRmodelAirMean3-2014
 MCMaster2000 = read.csv("~/NoiseHedonicProject/Noise-Hedonic/analysis/04MonteCarloSim/Revision/Model3/k2000/LWRMonteCarloStats2014-07-03.csv")
 MCMaster2000 = MCMaster2000[1:100, ]
 
-MCMaster500 = read.csv("~/NoiseHedonicProject/Noise-Hedonic/analysis/04MonteCarloSim/Revision/Model3/LWRMonteCarloStats2014-07-05.csv")
-MCMaster500 = MCMaster500[1:80, ]
+MCMaster500 = read.csv("~/NoiseHedonicProject/Noise-Hedonic/analysis/04MonteCarloSim/Revision/Model3/k500/LWRMonteCarloStats2014-07-06.csv")
+MCMaster500 = MCMaster500[1:100, ]
 
 MCplotter = function(outputcoefficient, statcoefficient) {
   actual = sd(output[[outputcoefficient]][, c("k500", "k2000")], na.rm =T)
@@ -37,7 +37,7 @@ MCplotter = function(outputcoefficient, statcoefficient) {
 }
 
 outputCOEFS = rep(names(output)[c(2:5, 16, 19, 20, 21, 22, 23, 24, 17, 18)], 2)
-statCOEFS = names(MCMaster)[c(-(1:3),-17)]
+statCOEFS = names(MCMaster500)[c(-(1:3),-17)]
 titles = c("Noise", "House Size", "Lot Size", "Year Built", "Owner Occupancy",
            "Median Income", "School Test Scores", "Distance to Lake", "Distance to Park", "Distance to Shop",
            "Distance to CBD", "Percent White", "Percent Under Age 18")

### 2014-08-18 reports/code/GCVsFromMCsimMaker.R

@@ -16,15 +16,15 @@ mcstats500Density = density(mcstats500$minGCV)
 
 # 1000
 mcstats1000 = read.csv("analysis/04MonteCarloSim/Revision/Model3/k1000/LWRMonteCarloStats2014-06-25.csv")
-mcstats1000Density = density(mcstats1000$minGCV[1:50])
+mcstats1000Density = density(mcstats1000$minGCV[1:50]) # need to run the other 50 just to be sure..
 
 # 2000
 mcstats2000 = read.csv("analysis/04MonteCarloSim/Revision/Model3/k2000/LWRMonteCarloStats2014-07-03.csv")
 mcstats2000Density = density(mcstats2000$minGCV)
 
 # 4000
-mcstats4000 = read.csv("analysis/04MonteCarloSim/Revision/Model3/k4000/LWRMonteCarloStatsTemp.csv")
-mcstats4000Density = density(mcstats4000$V1[1:34]) # HAVE TO FIX THIS - WHY ARENT THE NAMES HERE???
+mcstats4000 = read.csv("analysis/04MonteCarloSim/Revision/Model3/k4000/LWRMonteCarloStats2014-07-11.csv")
+mcstats4000Density = density(mcstats4000$minGCV) 
 
 
 maxX = max(mcstats500Density$x, mcstats1000Density$x, mcstats2000Density$x, mcstats4000Density$x)

### 2014-08-18 reports/code/ModelGCVvisualizer.R

@@ -35,7 +35,7 @@ for (i in 1:3) {
                                    dep.var = DATAFRAME$logSALE_VA[obs2run]))
 }
 
-# gcvs.global = c(0.04830468, 0.04093458, 0.03753716)
+gcvs.global = c(0.04830468, 0.04093458, 0.03753716)
 
 ks = c(100,  200,  300,  350,  400,  450,  500,  550,  600,  650,  700,  800, 1000, 1500, 2000, 3000, 4000)
 gcv1 = c(0.03390767, 0.02991290, 0.02941916, 0.02938722, 0.02944322, 0.02953900, 0.02964363, 0.02977173, 
@@ -49,7 +49,7 @@ gcv3 = c(0.03515802, 0.02876113, 0.02754652, 0.02728218, 0.02715732, 0.02709864,
          0.03065546)
 gcvs = cbind(gcv1, gcv2, gcv3)
   
-pdf("~/NoiseHedonicProject/Noise-Hedonic/graphs/GCVbyModel.pdf", 
+pdf("~/NoiseHedonicProject/Noise-Hedonic/graphs/GCVbyModelFinal.pdf", 
     family = "Palatino", height = 6, width = 8)
 matplot(ks, gcvs, type = "o", pch = 16, cex = .5, las = 1,
         ylim = c(.025, .05), xlim = c(0, 4000), lty = 1,
@@ -62,7 +62,7 @@ lines(c(500, 500), c(0, min(gcvs)), col = "gray80")
 lines(c(500, -200), rep(min(gcvs), 2), col = "gray80")
 axis(1, at = 500)
 axis(2, at = round(min(gcvs), 3), las = 1)
-title("Generalized Cross Validation Scores Across Models")
+title("Generalized Cross Validation Scores Across Models", cex.main = 1.5)
 
 text(500, .031, "LWR Model (1) = Structural Variables + Month*Year Fixed Effects",  
      srt = 13, pos = 4, col = "black", cex = .8)

### 2014-10-12 JRSarticle/text/NoiseHedonicFinal.Rnw
making the final edits after the Revise-and-resubmission positive results

--- 2014-08-18 reports/NoiseHedonicRaR.Rnw
@@
 \usepackage[width = 5.5in]{geometry}
-\usepackage{caption, amsmath, graphicx, setspace, multirow, color, hyperref, array}
-\usepackage[modulo]{lineno}
+\usepackage{caption, amsmath, graphicx, setspace, multirow, color, array}
+\usepackage[hidelinks]{hyperref}
 
@@
 \defcitealias{Netherlands2004}{Netherlands, 2004}
-\defcitealias{UNDESA2012}{United Nations, 2012}
 \defcitealias{USFHA2012}{USFHWA, 2012}
@@
 \date{}
-\author{}%Aaron Swoboda, Tsegaye Nega and Maxwell Timm}
+\author{Aaron Swoboda, Tsegaye Nega and Maxwell Timm}
 
@@
 We implement spatially and temporally flexible local regression techniques and find significant non-stationarity in the hedonic function over time and space.
+
+\vspace{.3in}
+\noindent
+JEL Codes: C21, R21, R41
+
+\vspace{.15in}
+\noindent
+Keywords: Housing Demand, Automobile Traffic Noise, Highways, Hedonic Analysis, Semiparametric Regression, Locally Weighted Regression, Geographically Weighted Regression, Spatial Analysis
 \end{abstract}
@@
 \pagenumbering{arabic}
-
-\linenumbers
 
@@
 \rotfloatpagestyle{empty}
-\makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/Overview2columnAnnotatedPDF}}
+\makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/Figure01}}
 \caption{This figure shows the spatial extent of our study area, the significant spatial variation in single family house sales prices, as well as our noise data.}
@@
 \small
-\begin{tabular}{lccccccc}%D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}}
+\begin{tabular}{lccccccc}
   \hline \hline
@@
   \hline
-% latex table generated in R 2.15.2 by xtable 1.7-0 package
-% Tue Jun 10 21:29:25 2014
 Sale Price (\$1,000s) & 99 & 195 & 241 & 266 & 315 & 675 & 103 \\ \\
@@
 
-\subsection{Noise Data}
+\subsection*{Noise Data}
 To determine the relationship between real estate prices and road traffic noise levels, we first created a traffic noise exposure surface by calculating the propagation of traffic noise over the landscape using the Federal Highway Authority (FHWA) 1978 standard \citep{Barry1978}.
@@
 
-\subsection{House Structural Attributes}\label{structural}
+\subsection*{House Structural Attributes}\label{structural}
 According to a review by \cite{Wilhelmsson2000}, the five most common structural attributes included in real estate hedonic pricing studies are living area, number of bathrooms, age, garage and lot size.
@@
 Therefore, we feel confident in our results even without these independent variables for most of our study area.
-%Additionally, other hedonic work has been published using a similar set of explanatory variables in this area, see for instance, \citet{Sander2009b}.
 
-\subsection{Other Locational Attributes}
+\subsection*{Other Locational Attributes}
 A common real estate adage states that the three most important real estate attributes are: location, location and location.
@@
 
-\subsection{Time}
+\subsection*{Time}
 Due to concerns of sample selection bias before, during, and after the economic recession, we compared the characteristics of our data by year to look for important differences.
@@
   \centering
-    \begin{tabular}{lcccccc|c}%D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}D{.}{.}{1}|D{.}{.}{1}}
+    \begin{tabular}{lcccccc|c}
     \\[-1.8ex]\hline 
@@
 \begin{figure}
-\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/SaleValue_with05}}
+\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/Figure02}}
 \caption{This figure shows the spatial distribution of observed sales prices over time.
@@
 \section{Basic Econometric Model}\label{basicModel}
-Consistent with past research, this study estimates a semi-logarithmic hedonic price functon.
+Consistent with past research, this study estimates a semi-logarithmic hedonic price function.
 Before implementing the Locally Weighted Regression model, we present the results of a simpler econometric model given by equation~\eqref{eq:model}.
@@
 Model (A) in Table \ref{tab:globalRegression} displays the results of this basic Ordinary Least Squares regression model.
-In addition to the important structural and neighborhood variables, we also included fixed effects for each city and an interaction term between month and year of sale.
-The traffic noise coefficient suggests houses in our data that are similar in all respects but a one decibel difference in noise will, on average, have sales prices roughly 0.27 percent lower at the noisier location.
+In addition to the important structural and neighborhood variables, we also included fixed effects for each city and an interaction term between month and year of sale.\footnote{We'd like to thank an anonymous referee for suggesting this interaction fixed effect specification as a means of controlling for government policies like the First-Time Homebuyer Tax Credit that also may have affected the sales price of houses during our study period.
+} The traffic noise coefficient suggests houses in our data that are similar in all respects but a one decibel difference in noise will, on average, have sales prices roughly 0.27 percent lower at the noisier location.
 
 \begin{table}
-\caption{Basic Global Regression Results}\label{tab:globalRegression}
+\caption{Basic Global Regression Results}
+\label{tab:globalRegression}
 \makebox[\textwidth][c]{
@@
 In all three cases the improved model fit was significantly more than expected due to random chance.
-Columns (B)--(D) of Table~\ref{tab:globalRegression} show the results of restimating model (A) using only sales within three separate years of data to allow all coefficients to vary over time.
+Columns (B)--(D) of Table~\ref{tab:globalRegression} show the results of re-estimating model (A) using only sales within three separate years of data to allow all coefficients to vary over time.
 Subsequent work with models (B)--(D) also suggested that many of the important regression coefficients vary across the different cities within our sample.
@@
 \section{Locally Weighted Regression Model}
-Locally Weighted Regression (LWR) techniques (also known as Geographically Weighted Regression) are described in detail by \citet{Cleveland1988}, \citet{Brunsdon1998b}, \citet{Fotheringham2002}, and others.
-LWR is a weighted least squares methodology in which regression coefficients are estimated over space as a function of the local data as described in Equation~\eqref{eq:LWRbeta},
+Locally Weighted Regression (LWR) techniques are described in detail by \citet{Cleveland1988} and use weighted least squares to estimate regression coefficients as a function of the local data.
+\citet{Brunsdon1998b}, \citet{Fotheringham2002}, and others have since popularized the application of LWR in a geographic context (referring to the technique as Geographically Weighted Regression).
+The basic formulation can be described in equation \eqref{eq:LWRbeta},
 \begin{equation}\label{eq:LWRbeta}
@@
 
-\subsection{Improved Model Performance}
+\subsection*{Improved Model Performance}
 The use of the Locally Weighted Regression model significantly improved model performance.
@@
 \begin{figure}
-  \makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/GCVbyModelFinal}}
+  \makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/Figure03}}
 \caption{This figure shows the relationship between bandwidth size and the GCV score for three different Locally Weighted Regression (LWR) models.
@@
 
-% % Table created by stargazer v.5.1 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% % Date and time: Sat, Jun 21, 2014 - 10:37:00 AM
-% % Requires LaTeX packages: dcolumn 
-% \begin{table}[!htbp]
-%   \caption{LWR Results: Dependent Variable = ln(Sales Price)} 
-%   \label{tab:LWR} 
-%   \makebox[\textwidth][c]{
-% \scriptsize
-%   \centering
-% \begin{tabular}{@{\extracolsep{-1pt}} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{-4} D{.}{.}{4} D{.}{.}{4} D{.}{.}{-4} D{.}{.}{3} D{.}{.}{3} } 
-% \\[-1.8ex]\hline 
-% \hline \\[-1.8ex]
-%  & \multicolumn{3}{c}{Nearest 500 sales$^*$} & \multicolumn{3}{c}{Nearest 650 sales} & \multicolumn{3}{c}{Nearest 1000 sales} \\
-%  & \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$}  & 
-%  \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$}  & 
-%  \multicolumn{1}{r}{mean $\hat{\beta}$} & \multicolumn{1}{c}{10$^{th}$} & \multicolumn{1}{c}{90$^{th}$} \\
-%  \cline{2-4} \cline{8-10} \cline{5-7}
-% \multicolumn{1}{l}{Noise (dB)} & -0.0034 & -0.0064 & -0.0006 & -0.0034 & -0.0061 & -0.0009 & -0.0033 & -0.0057 & -0.0013 \\ 
-% \multicolumn{1}{l}{House Size (1,000s ft)} & 0.2700 & 0.1800 & 0.3900 & 0.2700 & 0.1900 & 0.3900 & 0.2700 & 0.2000 & 0.4000 \\ 
-% \multicolumn{1}{l}{Lot Size (acres)} & 0.4200 & 0.1700 & 0.7300 & 0.4200 & 0.1900 & 0.7100 & 0.4200 & 0.2100 & 0.6700 \\ 
-% \multicolumn{1}{l}{Year House Built} & 0.0046 & 0.0004 & 0.0100 & 0.0045 & 0.0005 & 0.0096 & 0.0043 & 0.0005 & 0.0090 \\ 
-% \multicolumn{1}{l}{Owner Occupancy} & 0.0230 & -0.0290 & 0.0800 & 0.0240 & -0.0240 & 0.0760 & 0.0230 & -0.0180 & 0.0680 \\ 
-% \multicolumn{1}{l}{Percent White} & 0.0012 & -0.0003 & 0.0029 & 0.0013 & -0.0001 & 0.0028 & 0.0014 & 0.0001 & 0.0028 \\ 
-% \multicolumn{1}{l}{Percent Under 18} & 0.0005 & -0.0016 & 0.0025 & 0.0004 & -0.0014 & 0.0022 & 0.0004 & -0.0011 & 0.0019 \\ 
-% \multicolumn{1}{l}{Median Income (\$1,000s)} & 0.0007 & -0.0014 & 0.0033 & 0.0008 & -0.0010 & 0.0033 & 0.0010 & -0.0006 & 0.0037 \\ 
-% \multicolumn{1}{l}{Elementary Test Scores} & 0.0000 & -0.0056 & 0.0055 & 0.0001 & -0.0050 & 0.0049 & 0.0003 & -0.0040 & 0.0042 \\ 
-% \multicolumn{1}{l}{Dist to Lake (km)} & -0.0150 & -0.0910 & 0.0580 & -0.0110 & -0.0770 & 0.0550 & -0.0076 & -0.0630 & 0.0520 \\ 
-% \multicolumn{1}{l}{Dist to Park (km)} & -0.0110 & -0.0600 & 0.0330 & -0.0110 & -0.0490 & 0.0250 & -0.0085 & -0.0370 & 0.0160 \\ 
-% \multicolumn{1}{l}{Dist to Shop (km)} & 0.0092 & -0.0330 & 0.0520 & 0.0096 & -0.0270 & 0.0470 & 0.0100 & -0.0210 & 0.0440 \\ 
-% \multicolumn{1}{l}{Dist to CBD (km)} & 0.0084 & -0.0190 & 0.0440 & 0.0094 & -0.0140 & 0.0400 & 0.0100 & -0.0099 & 0.0380 \\ 
-% \hline \\[-1.8ex] 
-% \multicolumn{10}{p{6 in}}{$^*$ A bandwidth of 500 implies that the nearest 500 houses sold within the past 12 months are included.} \\
-% \multicolumn{10}{p{6 in}}{Note: Each model also includes a categorical variable for architectural style, month*year fixed effects, and city-level fixed effects. }
-% 
-% \end{tabular} 
-% }
-% \end{table}
-
-% Table created by stargazer v.5.1 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Sat, Jul 05, 2014 - 09:41:55 PM
-% Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp]   
@@
 
-The mean LWR coefficient for the noise variable is similar across the different bandwidths (approximately a third of a percent difference in house sales prices for each additional decibel of noise, all other varibles held constant) and also more negative than the OLS value presented previously.
+The mean LWR coefficient for the noise variable is similar across the different bandwidths (approximately a third of a percent difference in house sales prices for each additional decibel of noise, all other variables held constant) and also more negative than the OLS value presented previously.
 In the next three subsections we describe the results of hypothesis tests that lead us to believe that LWR modeling is an appropriate and beneficial research strategy due to significant spatial and temporal variation in the hedonic function.
 
-\subsection{Does the Hedonic Function Vary over Space?}
+\subsection*{Does the Hedonic Function Vary over Space?}
 
@@
 In a thousand different local regression models with the simulated data, we never obtained model performance anywhere near our actual model fit at a bandwidth of 500 nearest sales.
-Second, in constrast to the clear positive relationship between bandwidth size and GCV score in Figure~\ref{fig:GCVmodel}, the simulated data consistently produced an inverse relationship between GCV scores and bandwidth size (in every single experimental iteration the smallest GCV score was obtained at the largest bandwidth).
+Second, in contrast to the clear positive relationship between bandwidth size and GCV score in Figure~\ref{fig:GCVmodel}, the simulated data consistently produced an inverse relationship between GCV scores and bandwidth size (in every single experimental iteration the smallest GCV score was obtained at the largest bandwidth).
 
@@
 \begin{figure}
- \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/GCVsFromMCsim}}
+ \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/Figure04}}
  \caption{This figure shows the distribution of GCV scores obtained from simulations with spatially randomized data and the GCV score from our data.
@@
 
-\subsection{Which Coefficients Vary over Space?}
+\subsection*{Which Coefficients Vary over Space?}
 
@@
 \begin{figure}
- \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/AcreBeta_allBandwidth}}
+ \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/Figure05}}
  \caption{This figure shows an interpolated surface (using Inverse Distance Weighting) for the estimated LWR coefficients (dependent variable = ln(sales price)) for the lot size variable (in acres) obtained across four different bandwidths: 500, 650, 1,000, and 2,000 nearest observations.
@@
 \begin{figure}
- \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/FinSqFtBeta_allBandwidth}}
+ \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/Figure06}}
  \caption{This figure shows an interpolated surface (using Inverse Distance Weighting) for the estimated LWR coefficients (dependent variable = ln(sales price)) for the finished house size variable (in 1,000s of square feet) obtained across four different bandwidths: 500, 650, 1,000, and 2,000 nearest observations.
@@
 \begin{figure}
- \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/NoiseBeta_allBandwidth}}
+ \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/Figure07}}
  \caption{This figure shows an interpolated surface (using Inverse Distance Weighting) for the estimated LWR coefficients (dependent variable = ln(sales price)) for the noise variable (in dB) obtained across four different bandwidths: 500, 650, 1,000, and 2,000 nearest observations.
@@
 \begin{figure}
- \makebox[\textwidth][c]{\includegraphics[height=.9\textheight]{../graphs/MCsim2FinalResults}}
+ \makebox[\textwidth][c]{\includegraphics[height=.9\textheight]{../graphs/Figure08}}
  \caption{This figure shows the actual standard deviation in LWR coefficients (dashed line) compared to standard deviations obtained from 100 different instances of spatial randomization (solid lines).
@@
 
-\subsection{Does the Noise Coefficient Change over Time?}
+\subsection*{Does the Noise Coefficient Change over Time?}
 
@@
 \begin{sidewaysfigure}
- \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/Acre_50_200_ByYear}
+ \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/Figure09}
  \caption{This figure shows the interpolated LWR lot size coefficients across space and time for two bandwidths (nearest 500 and 2,000).
@@
 \begin{sidewaysfigure}
- \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/FinFt_50_200_ByYear}
+ \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/Figure10}
  \caption{This figure shows the interpolated LWR finished house size coefficients across space and time for two bandwidths (nearest 500 and 2,000).
@@
 \begin{sidewaysfigure}
- \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/Noise_50_200_ByYear}
+ \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/Figure11}
  \caption{This figure shows the interpolated LWR noise coefficients across space and time for two bandwidths (nearest 500 and 2,000).
@@
 \begin{table}[!htbp] \centering 
+  \caption{LWR Noise Coefficient Over Time (bandwidth = 500 nearest sales)} 
     \label{tab:noisebetatime500} 
-  \caption{LWR Noise Coefficient Over Time (bandwidth = 500 nearest sales)} 
 \scriptsize 
@@
 Such a study is not feasible with our data and we are therefore limited to a hedonic analysis with observational data.
-Our conclusions, then, should be interpretted like most other hedonic analysis results and, while we find a strong negative correlation between noise and house prices, we cannot state that noise \emph{causes} lower sales prices.
+Our conclusions, then, should be interpreted like most other hedonic analysis results and, while we find a strong negative correlation between noise and house prices, we cannot state that noise \emph{causes} lower sales prices.
 
@@
 To the extent that traffic flows changed with the economic recession, our noise variable could be inaccurate for other years.
-However, we believe these potential changes are miniscule.
+However, we believe these potential changes are minuscule.
 Table~VM2 from the US.
@@
 We found strikingly similar traffic noise coefficient estimates when these additional structural variables were included and omitted.
-As shown in Figure~\ref{fig:DAK}, a simple linear regression of the noise coefficient estimates obtained when these additional structural variables were excluded on the estimates obtained when these variables were included yields a line of best fit that is almost indiscernable from the 45 degree line and has $R^2 = 0.96$.
-%Additionally, a paired t-test of the roughly 9,000 (n = 8,751) coefficient estimates yields a 95 percent confidence interval for the true difference between our estimates without the additional variables and with as -0.000175 to -0.000159.
-That is, the estimated difference is, on average, more than an order of magnitude smaller than our typical coefficient estimates  suggesting that our results may be robust to the omission of these variables from our analysis.
+As shown in Figure~\ref{fig:DAK}, a simple linear regression of the noise coefficient estimates obtained when these additional structural variables were excluded on the estimates obtained when these variables were included yields a line of best fit that is almost indiscernible from the 45 degree line and has $R^2 = 0.96$.
 
 \begin{figure}
-\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/DakotaResults}}
+\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/Figure12}}
 \caption{This figure shows the similarity between the LWR coefficients we obtained from our model in Dakota County when additional structural variables were excluded vs.\ included in the hedonic regression function.
@@
 Second, ``mixed'' regression techniques (in which some regression coefficients are constrained to remain constant across the study area while others are allowed to vary) may allow researchers to obtain more precise estimates of the impact of hedonic characteristics by increasing the degrees of freedom in the regression.
-Lastly, researchers should seek to leverage improvements in spatial hedonic modelling with the advice of  \citet{Carruthers2010} and use the spatial variation in regression coefficients obtained from LWR models to estimate the second-stage hedonic regressions to identify consumer demand curves for these characteristics, thereby further improving our undertanding of the value of local amenities.
+Lastly, researchers should seek to leverage improvements in spatial hedonic modelling with the advice of  \citet{Carruthers2010} and use the spatial variation in regression coefficients obtained from LWR models to estimate the second-stage hedonic regressions to identify consumer demand curves for these characteristics, thereby further improving our understanding of the value of local amenities.
 
-%\newpage
+\newpage
 \begin{singlespace}
-\bibliographystyle{plainnat}
-\bibliography{NoiseBibliography}
+
+\input{NoiseHedonicFinalBib.bbl}
 \end{singlespace}

### 2014-10-12 reports/NoiseHedonicFinal.Rnw
making the final edits after the Revise-and-resubmission positive results

--- 2014-10-12 JRSarticle/text/NoiseHedonicFinal.Rnw
@@
 \rotfloatpagestyle{empty}
-\makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/Figure01}}
+\makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/Overview2columnAnnotatedPDF}}
 \caption{This figure shows the spatial extent of our study area, the significant spatial variation in single family house sales prices, as well as our noise data.}
@@
 \begin{figure}
-\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/Figure02}}
+\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/SaleValue_with05}}
 \caption{This figure shows the spatial distribution of observed sales prices over time.
@@
 \begin{figure}
-  \makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/Figure03}}
+  \makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/GCVbyModelFinal}}
 \caption{This figure shows the relationship between bandwidth size and the GCV score for three different Locally Weighted Regression (LWR) models.
@@
 \begin{figure}
- \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/Figure04}}
+ \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/GCVsFromMCsim}}
  \caption{This figure shows the distribution of GCV scores obtained from simulations with spatially randomized data and the GCV score from our data.
@@
 \begin{figure}
- \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/Figure05}}
+ \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/AcreBeta_allBandwidth}}
  \caption{This figure shows an interpolated surface (using Inverse Distance Weighting) for the estimated LWR coefficients (dependent variable = ln(sales price)) for the lot size variable (in acres) obtained across four different bandwidths: 500, 650, 1,000, and 2,000 nearest observations.
@@
 \begin{figure}
- \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/Figure06}}
+ \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/FinSqFtBeta_allBandwidth}}
  \caption{This figure shows an interpolated surface (using Inverse Distance Weighting) for the estimated LWR coefficients (dependent variable = ln(sales price)) for the finished house size variable (in 1,000s of square feet) obtained across four different bandwidths: 500, 650, 1,000, and 2,000 nearest observations.
@@
 \begin{figure}
- \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/Figure07}}
+ \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{../graphs/NoiseBeta_allBandwidth}}
  \caption{This figure shows an interpolated surface (using Inverse Distance Weighting) for the estimated LWR coefficients (dependent variable = ln(sales price)) for the noise variable (in dB) obtained across four different bandwidths: 500, 650, 1,000, and 2,000 nearest observations.
@@
 \begin{figure}
- \makebox[\textwidth][c]{\includegraphics[height=.9\textheight]{../graphs/Figure08}}
+ \makebox[\textwidth][c]{\includegraphics[height=.9\textheight]{../graphs/MCsim2FinalResults}}
  \caption{This figure shows the actual standard deviation in LWR coefficients (dashed line) compared to standard deviations obtained from 100 different instances of spatial randomization (solid lines).
@@
 \begin{sidewaysfigure}
- \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/Figure09}
+ \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/Acre_50_200_ByYear}
  \caption{This figure shows the interpolated LWR lot size coefficients across space and time for two bandwidths (nearest 500 and 2,000).
@@
 \begin{sidewaysfigure}
- \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/Figure10}
+ \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/FinFt_50_200_ByYear}
  \caption{This figure shows the interpolated LWR finished house size coefficients across space and time for two bandwidths (nearest 500 and 2,000).
@@
 \begin{sidewaysfigure}
- \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/Figure11}
+ \includegraphics[trim = 0cm 2cm 0cm 0cm, clip = true, width = \textwidth]{../graphs/Noise_50_200_ByYear}
  \caption{This figure shows the interpolated LWR noise coefficients across space and time for two bandwidths (nearest 500 and 2,000).
@@
 \begin{figure}
-\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/Figure12}}
+\makebox[\textwidth][c]{\includegraphics[width = \textwidth]{../graphs/DakotaResults}}
 \caption{This figure shows the similarity between the LWR coefficients we obtained from our model in Dakota County when additional structural variables were excluded vs.\ included in the hedonic regression function.
@@
 \begin{singlespace}
-
+% \bibliographystyle{plainnat}
+% \bibliography{NoiseBibliography}
 \input{NoiseHedonicFinalBib.bbl}

### 2014-10-12 reports/NoiseHedonicFinal.tex
making the final edits after the Revise-and-resubmission positive results

--- 2014-10-12 JRSarticle/text/NoiseHedonicFinal.Rnw
@@
-\documentclass{article}
+\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 \usepackage{floatpag} %floatpag.sty file is just in the reports folder - commands to remove page nos are in first figure
@@
 \doublespacing
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}

### 2014-10-16 JRSarticle/text/NoiseHedonicFinal.tex
making the final edits after the Revise-and-resubmission positive results
made the changes JRS asked for and resubmitted!

--- 2014-10-12 JRSarticle/text/NoiseHedonicFinal.Rnw
@@
-\documentclass{article}
-\usepackage{floatpag} %floatpag.sty file is just in the reports folder - commands to remove page nos are in first figure
+\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
+
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
+\usepackage{floatpag} %floatpag.sty file is in the text folder - commands to remove page nos are in first figure
 \usepackage[round]{natbib}
@@
 \date{}
-\author{Aaron Swoboda, Tsegaye Nega and Maxwell Timm}
+\author{}%Aaron Swoboda, Tsegaye Nega and Maxwell Timm}
 
 \doublespacing
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 
-We used the SoundPlan\texttrademark noise modeling software to implement equation~\ref{eq:noise} using several data sources as inputs.
+We used the SoundPlan\texttrademark noise modeling software to implement equation~\eqref{eq:noise} using several data sources as inputs.
 A 2007 road centerline and the associated traffic characteristics (volume and proportion of trucks and vehicles) for the region were obtained from the Minnesota Department of Transportation (MNDoT).
@@
 \input{NoiseHedonicFinalBib.bbl} 
+% This file contains the bibliography with proper Journal of Regional Science Formatting
 \end{singlespace}

### 2014-10-26 JRSarticle/text/NoiseHedonicFinal.tex
final edits? moved equation #s to left hand side and removed colons from bibliography

@@
-\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
-
+\documentclass[leqno]{article}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
 \makeatletter
@@
 \usepackage{alltt}
-\usepackage{floatpag} %floatpag.sty file is in the text folder - commands to remove page nos are in first figure
+\usepackage{floatpag} %floatpag.sty file is just in the reports folder - commands to remove page nos are in first figure
 \usepackage[round]{natbib}
@@
 
-We used the SoundPlan\texttrademark noise modeling software to implement equation~\eqref{eq:noise} using several data sources as inputs.
+We used the SoundPlan\texttrademark noise modeling software to implement equation~\ref{eq:noise} using several data sources as inputs.
 A 2007 road centerline and the associated traffic characteristics (volume and proportion of trucks and vehicles) for the region were obtained from the Minnesota Department of Transportation (MNDoT).
@@
 \input{NoiseHedonicFinalBib.bbl}
-% This file contains the bibliography with proper Journal of Regional Science Formatting
 \end{singlespace}

### 2014-11-11 JRSarticle/text/NoiseHedonicFinal.Rnw
final edits? moved equation #s to left hand side and removed colons from bibliography
added acknowledgement of editor and referees plus Carleton College affiliation.

@@
-\documentclass{article}
+\documentclass[leqno]{article}
 \usepackage{floatpag} %floatpag.sty file is just in the reports folder - commands to remove page nos are in first figure
@@
 \date{}
-\author{Aaron Swoboda, Tsegaye Nega and Maxwell Timm}
+\author{Aaron Swoboda, Tsegaye Nega and Maxwell Timm\thanks{The authors would like to thank Professor Steven Brakman and three anonymous referees for their helpful advice and comments.}
+  \\ Carleton College \\  Northfield, MN 55057 \\
+  aswoboda@carleton.edu \\
+  tnega@carleton.edu \\
+  maxgtimm@gmail.com
+}
 
